### 2019-10-07 tesis_hiram/Abstract/abstract.tex
tesis

% ************************** Thesis Abstract *****************************
% Use `abstract' as an option in the document class to print only the titlepage and the abstract.
\begin{abstract}
I present a study on the  production of tH in same sign dimuon channel $\mu\pm \mu\pm$ 
 A likelihood scan is performed to show the probability of observation of the signal.  By studying this process , I explore a Higgs production mechanism ,which it has not been observed yet experimentally. Simulation is used to predict sensitivity for the LHC high luminosity phase. This could help to obtain better limits for the production of tH. I also include the model $k_t=-1$, where $k_t$ is the top higgs coupling parameter,  for compare it with the standard model.

\end{abstract}

### 2019-10-07 tesis_hiram/Appendix2/appendix2.tex
tesis

%!TEX root = ../thesis.tex
% ******************************* Thesis Appendix B ********************************

\chapter{Scattering and cross section}
In classical mechanics, scattering is  a set of particles which deviate from their original trajectory to one or many ways. Examples of scattering are particle collisions and particles that deviates in a potential field.\\  
The cross section in a scattering is the area transverse to the relative motion between two object to scatter from each other.\cite{goldstein}
For a particle which deviates from its original way due to a potential whose center is at rest, the scattering angle is given by
\begin{align}
    \theta =\pi - 2\phi_0
\end{align}
with 
\begin{align}\label{sc1}
\phi_0 = \int_{r_0}^\infty \frac{M/r^2 d r}{\sqrt{2m(E-U(r)-M^2/r^2}}
\end{align}
with $r_0$ the nearest position to the center of potential and $U(r)$ is the potential. Now for great velocity , if we change $E=\frac{1}{2}mv^2$ and  $M=mpv$ and substitute in \ref{sc1}, we have \begin{align}
    \phi_0 = \int_{r_0}^\infty \frac{\rho /r^2 d r}{\sqrt{1-\frac{\rho^2}{r^2}-2U(r)/mv^2}}
\end{align} 
in terms of parameter of impact $\rho$ and the position\cite{landau}.
\begin{figure}[ht!] 
    \centering
    \includegraphics[scale=0.8]{Chapter1/sc.png}
    \caption{Diagram of scattering for a particle in a potential field\cite{landau}}
    \label{sc2}
\end{figure}
In a scattering of a beam of identical particles with velocity of $v$ , let $dN$ the number of particles scattered per unit of time through the angles $\theta$ and $\theta +d\theta$
The effective cross section is 
\begin{align}
    d\sigma=\frac{dN}{n}
\end{align}
n represents the number of particles passing in unit of time in a unit area of beam cross section. If $\rho$ is $\theta$ dependient, then the effective cross section is 
\begin{align}
    dN=2\phi \rho n d\rho \qquad d\sigma=2\phi \rho d\rho
\end{align}
rewriting $d\sigma$

\begin{align}
    d\sigma=2\phi \rho \left| \frac{d\rho}{d\theta} \right| d\theta
\end{align}
the derivative $\frac{d\rho}{d\theta}$ can be negative ,so it is necessary the modulus \cite{landau}. In a three dimension model, $d\sigma$ is related to the solid angle, instead of $d\theta$ , so the solid angle between the angles $\theta$ and $\theta+d\theta$ is
\begin{align}
    d\Omega=2\pi \sin{\theta}d\theta
\end{align}
thus, the cross section is 
\begin{align}
     d\sigma=   \frac{\rho(\theta)}{\sin{\theta}} \left| \frac{d\rho}{d\theta} \right| d\Omega
\end{align}
\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.7]{Chapter1/cs1.png}
 \caption{Drawing of an idealized scattering process showing the differential solid angle $\Delta\Omega$ and the
scattering angle $\theta$ \cite{gross} }
\label{sc}
\end{figure}

let N be the number of events. In terms of of solid angle
\begin{align}
    dN=\text{L} d\sigma=\text{L} \frac{d\sigma}{d\Omega} d\Omega \qquad \frac{d\sigma}{d\Omega}=\frac{dN}{\text{L}d\Omega}
\end{align}
For a collision of two particles that produce many particles, the cross section is given by 
\begin{align}\label{sc3}
\sigma=\frac{S\hbar^2 }{4\sqrt{(p_1 \cdot p_2)^2 -(m_1 m_2 c^2)^2} }\int \left| M \right|^2 (2\pi)^4 \delta^4(p_1-p_2-...p_n)\times \prod_{j=2}^n 2\pi \delta (p_j^2-m_j^2 c^2)\theta (p_j^0)\frac{d^4 p_j}{(2\pi)^4}
\end{align} 
the structure of the equation \ref{sc3} is similar to the equation \ref{dm}\cite{griff}.\\

Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}

### 2019-10-07 tesis_hiram/Appendix3/appendix3.tex
tesis

\chapter{P-value}
To quantify the level of disagreement we compute the P-value
\begin{align}
	P_\mu =\int_{t_\mu}^{\infty}f(t_\mu |\mu) dt_\mu
\end{align}
where $t_\mu$  is the value of the statistic $t_\mu$ observed from the data and $f(t\mu |\mu)$ denotes
the PDF (Probability density function) of t$_\mu$ under the assumption of the signal strength $\mu$
\begin{align}
	f(t\mu |\mu)=\frac{1}{\sqrt{2\pi}} \frac{1}{\sqrt{t_\mu}}e^\frac{-t_\mu}{2}
\end{align}

\begin{figure}
	\centering
	\includegraphics[width=9cm,height=6	cm]{Chapter3/nos.png}
	\caption{Prueba estad\'istica de $t_\mu$ y P valor para $t_\mu$}
\end{figure}
%valores de sigma en 1,4, 9 corresponden a las areas de una gaussiana en isigma,2sigma y 3 sigma

\begin{figure}
	\centering
	\includegraphics[width=9cm,height=6cm]{Chapter3/normal-curve.jpg}
	\caption{Distribuci\'on gaussiana que ilustra los valores de significancia y su probabilidad}
\end{figure}

### 2019-10-07 tesis_hiram/Appendix4/appendix4.tex
tesis

\chapter{Fitting algorithm}

\begin{verbatim}
#include "RooWorkspace.h"
#include "RooStats/ModelConfig.h"
#include "RooRealVar.h"
#include "RooMinimizerFcn.h"
#include "RooNLLVar.h"
#include "TFile.h"
#include "minimize.C"
#include <iostream>
#include "eps.h"

using namespace std;
using namespace RooFit;
using namespace RooStats;

void qw(TH1* ht)
{
for (int i=1;i<=16;i++){
ht->SetBinError(i,sqrt(ht->GetBinContent(i)));
}
}

void simpleFit(string version, int strategy=0)
{
  //Open the file, grab the workspace
  TFile* f = new TFile(Form("_combined_kinMVA_model.root",
  version.c_str(),version.c_str()));

  RooWorkspace* w = (RooWorkspace*)f->Get("combined");
  if (!w)
  {
    cout << "ERROR::Workspace doesn't exist! Check file name" << endl;
    exit(1);
  }
  //Grab the ModelConfig and the data
  ModelConfig* mc = (ModelConfig*)w->obj("ModelConfig");
  RooDataSet* data = (RooDataSet*)w->data("obsData");

  //Configure MINUIT
  ROOT::Math::MinimizerOptions::SetDefaultMinimizer("Minuit2");
  ROOT::Math::MinimizerOptions::SetDefaultStrategy(strategy);
  ROOT::Math::MinimizerOptions::SetDefaultPrintLevel(1);

  //Put the NPs and POIs into one set to send to the NLL
RooArgSet params(*mc->GetNuisanceParameters(),*mc->GetParametersOfInterest());

  //Build the NLL
  RooNLLVar* nll = (RooNLLVar*)mc->GetPdf()->createNLL(*data, Constrain(params),
						       GlobalObservables(*mc->GetGlobalObservables()),
						       RooFit::Offset(1));
////////////////////////////////////////////////////////////////////////////////
RooAbsArg* a1 =params.find("alpha_sample_ttz_sys");
RooAbsArg* a2 =params.find("alpha_sample_fakes_sys");
RooAbsArg* a3 =params.find("alpha_sample_tth_sys");
RooAbsArg* a4 =params.find("alpha_sample_ttw_sys");
RooAbsArg* a5 =params.find("alpha_sample_wz_sys");
RooAbsArg* a6 =params.find("alpha_sample_tz_sys");
RooAbsArg* a7 =params.find("mu");
RooAbsArg* a8 =params.find("Lumi");

RooRealVar* alpha_ttz=(RooRealVar*)a1; //ttz
RooRealVar* alpha_fakes=(RooRealVar*)a2; //non prompt /fakes
RooRealVar* alpha_tth=(RooRealVar*)a3; //tth
RooRealVar* alpha_ttw=(RooRealVar*)a4;  //ttw
RooRealVar* alpha_wz=(RooRealVar*)a5; //wz
RooRealVar* alpha_tz=(RooRealVar*)a6;  //tz
RooRealVar* alpha_mu=(RooRealVar*)a7; //signal
RooRealVar* lumi=(RooRealVar*)a8;
//////////////////////////////////////////////////////////////

 //Do the minimization and save the RooFitResult
// get RooArgSet containing the nuisance parameters (return NULL if not existing)
 GetWS()->set(fNuisParamsName.c_str()) : 0; }

//Definition in macros/minimize.C:
RooFitResult* minimize(RooAbsReal* fcn, bool save=0, int retry_mode=3, int* ret_status=NULL);

RooFitResult* result = minimize(nll, true, 0);
//////////////////////////////////
////RooPlot

RooAbsPdf* mf= mc->GetPdf();
RooArgSet spdf(*mf->getComponents());
RooHistFunc* th_SR_nominal=(RooHistFunc*)spdf.find("th_SR_nominal");
RooHistFunc* tth_SR_nominal=(RooHistFunc*)spdf.find("tth_SR_nominal");
RooHistFunc* ttz_SR_nominal=(RooHistFunc*)spdf.find("ttz_SR_nominal");
RooHistFunc* ttw_SR_nominal=(RooHistFunc*)spdf.find("ttw_SR_nominal");
RooHistFunc* wz_SR_nominal=(RooHistFunc*)spdf.find("wz_SR_nominal");
RooHistFunc* tz_SR_nominal=(RooHistFunc*)spdf.find("tz_SR_nominal");
RooHistFunc* fakes_SR_nominal=(RooHistFunc*)spdf.find("fakes_SR_nominal");

RooArgSet * parSet = (RooArgSet*)mc->GetObservables();
RooRealVar * x_obs = (RooRealVar*)parSet->find("obs_x_SR"); //variable

RooDataHist sth=th_SR_nominal->dataHist(); //signal thq
RooDataHist stth=tth_SR_nominal->dataHist(); //tth
RooDataHist sttz=ttz_SR_nominal->dataHist(); //ttz
RooDataHist sttw=ttw_SR_nominal->dataHist();//ttw
RooDataHist sfakes=fakes_SR_nominal->dataHist();//fakes
RooDataHist swz=wz_SR_nominal->dataHist();//wz
RooDataHist stz=tz_SR_nominal->dataHist();//tz
/////////////////////////////////////////////////////////////

TH1* data1=data->createHistogram("obs_x_SR",16);
TH1* th=sth.createHistogram("obs_x_SR",16); //th
TH1* tth=stth.createHistogram("obs_x_SR",16);  //tth
TH1* ttz=sttz.createHistogram("obs_x_SR",16);  //ttz
TH1* ttw=sttw.createHistogram("obs_x_SR",16);  ///ttw
TH1* fakes=sfakes.createHistogram("obs_x_SR",16);  ///non prompt/fakes
TH1* wz=swz.createHistogram("obs_x_SR",16); ///wz
TH1* tz=stz.createHistogram("obs_x_SR",16); /// tz

qw(data1);

////////////////////////////////////////
tth->SetFillColor(kOrange+7);
th->SetFillColor(kRed+1);
ttz->SetFillColor(kSpring+2);
ttw->SetFillColor(kSpring+3);
wz->SetFillColor(kMagenta-3);
tz->SetFillColor(kCyan);
fakes->SetFillStyle(3005);
fakes->SetFillColor(kBlue-3);
data1->SetMarkerStyle(8);
data1->SetLineColor(kBlack);
///////////////////////////////////////////////
//number of events post fit//

float i1 =(fakes->Integral())*(1.0+eps_fakes*alpha_fakes->getVal())*lumi->getVal(); //fakes eps=0.4
float i2 =(tz->Integral())*(1.0+ eps_tz*alpha_tz->getVal())*lumi->getVal();  //tz    eps=0.5
float i3=(wz->Integral())*(1.0+ eps_wz*alpha_wz->getVal())*lumi->getVal(); //wz   eps=0.5
float i4=(ttz->Integral())*(1.0+ eps_ttz*alpha_ttz->getVal())*lumi->getVal(); //ttz  double  eps_ttz = sqrt(pow(0.04,2)+pow(0.1,2));
float i5=(ttw->Integral())*(1.0+ eps_ttw*alpha_ttw->getVal())*lumi->getVal(); //ttw   double eps_ttw= sqrt(pow(0.04,2)+pow(0.12,2));
float i6=(th->Integral())*(alpha_mu->getVal())*lumi->getVal();  //signal (kt--1 mu=6.12861e-01)
float i7=(tth->Integral())*(1.0+ eps_tth*alpha_tth->getVal())*lumi->getVal(); //tth    eps=0.05
float id=data1->Integral(); //data

fakes->Scale(i1/fakes->Integral()); //fakes eps=0.4
tz->Scale(i2/tz->Integral());  //tz    eps=0.5
wz->Scale(i3/wz->Integral()); //wz   eps=0.5
ttz->Scale(i4/ttz->Integral()); //ttz  double  eps_ttz = sqrt(pow(0.04,2)+pow(0.1,2));
ttw->Scale(i5/ttw->Integral()); //ttw   double eps_ttw= sqrt(pow(0.04,2)+pow(0.12,2));
th->Scale(i6/th->Integral());  //signal (kt--1 mu=6.12861e-01)
tth->Scale(i7/tth->Integral()); //tth    eps=0.05

/////////////////////////////////////////////////////////////
THStack *hs = new THStack("hs","");
hs->Add(fakes,"hist");
hs->Add(tz,"hist");
hs->Add(wz,"hist");
hs->Add(ttz,"hist");
hs->Add(ttw,"hist");
hs->Add(tth,"hist");
hs->Add(th,"hist");

///////////////////////////////////////////
TCanvas *cs = new TCanvas("cs","cs",100,100,700,900);
TPad *pad1 = new TPad("pad1", "pad1", 0, 0.3, 1, 1.0);
cs->SetCanvasSize(900,900);
pad1->SetBottomMargin(0.01); // Upper and lower plot are joined
//pad1->SetGridx();         // Vertical grid
pad1->Draw();             // Draw the upper pad: pad1
pad1->cd();               // pad1 becomes the current pad]

data1->Draw();
hs->Draw("same");
data1->Draw("same");
data1->SetStats(0);
data1->SetAxisRange(0,70,"Y");
data1->SetTitle("CMs preliminary Test               35.9f/b (13TeV)");
data1->GetYaxis()->SetTitle("Events/bin");

TLegend* legend1 = new TLegend(0.6,0.6,0.89,0.89);
//legend->SetHeader("Test","C"); // option "C" allows to center the header
legend1->AddEntry(data1,"Data Obs","lep");
legend1->AddEntry(th,"th","f");
legend1->AddEntry(tth,"tth","f");
legend1->AddEntry(ttw,"ttw","f");
legend1->AddEntry(ttz,"ttz","f");
legend1->AddEntry(wz,"Wz","f");
legend1->AddEntry(tz,"Rares SM","f");
legend1->AddEntry(fakes,"fakes","f");
legend1->SetBorderSize(0);
legend1->Draw();
pad1->RedrawAxis();

// Draw the ratio plot
TH1F *data_obs = (TH1F*)data1->Clone("data_obs");
TH1F *sum =(TH1F*)fakes->Clone("sum");
sum->Add(th);
sum->Add(tth);
sum->Add(ttw);
sum->Add(ttz);
sum->Add(wz);
sum->Add(tz);
data_obs->Divide(sum);
cout<<sum->Integral()<<endl;
data_obs->SetLineColor(kBlack);
data_obs->SetMarkerStyle(8);
cs->cd();          // Go back to the main canvas before defining pad2
/////////////////////////////////////////
TPad *pad2 = new TPad("pad2", "pad2", 0, 0.05, 1, 0.3);
pad2->SetTopMargin(0.1);
pad2->SetBottomMargin(0.2);
pad2->SetLeftMargin(0.1);
pad2->Draw();
pad2->cd();       // pad2 becomes the current pad
data_obs->Draw();       // Draw the ratio plot
data_obs->SetTitle(" ");
///////////////////////////////////
data_obs->GetXaxis()->SetTitle("KinMVA tHq vs ttV");
data_obs->GetXaxis()->SetTitleOffset(1.0);
data_obs->GetXaxis()->SetTitleSize(0.1);
data_obs->GetXaxis()->SetLabelSize(0.1);
/////////////////////////////////////
data_obs->GetYaxis()->SetTitle("Data/Pred");
data_obs->GetYaxis()->SetTitleOffset(0.4);
data_obs->GetYaxis()->SetTitleSize(0.1);
data_obs->GetYaxis()->SetLabelSize(0.1);
data_obs->SetAxisRange(0, 2,"Y");
data_obs->SetStats(0);
data_obs->GetYaxis()->SetNdivisions(5);

////////////////////////////
TLine *line = new TLine(-1.0,1,1,1.0);
line->SetLineColor(kRed);
line->Draw("same");

cs->SaveAs("simple.png");
  //Save to file
  system(Form("mkdir -vp root-files/%s",version.c_str()));
  result->SetName("result");
  result->SaveAs(Form("root-files/%s/fit.root",version.c_str()));
}

\end{verbatim}

### 2019-10-07 tesis_hiram/Chapter1/chapter1.tex
tesis

%!TEX root = ../thesis.tex
%*******************************************************************************
%*********************************** First Chapter *****************************
%*******************************************************************************
\renewcommand{\baselinestretch}{1.5}

\begin{chapter}{Introduction}
\begin{linenumbers}
\section{General objetive and motivations}

Particle physics is a field of study of physics that studies the particles that create matter and its interactions to very small scale, even smaller than atoms. The particles analized in particle physics are the fundamental particles that compose the matter and the responsibles for all forces of nature. All thoses particles  and their properties are grouped in a theory called the Standard Model. Standard Model (SM) is a theory that describes the fundamental forces (except gravity) and classify the elementary particles in bosons (entire spin) and fermions (half spin).
The SM , created almost 50 years ago, has been the most successul theory in explain the phenomena in the subatomic world.
\\

One of the particles of the SM, the Higgs Boson , was recently discovered in 2012 in the ATLAS and CMS experiments at CERN. The discovery of Higgs boson in  proton proton collisions  marked a new era in the particle physics due to its characteristic  of giving the matter the property of mass, according to previous theories and predictions . Since then, people around the world are working in the Large Hadron Collider at CERN  in order to detect the Higgs bosons in higher energies and differents Higgs production processes. 
Also the impact of Higgs is also  important in cosmology,  where theoretical investigations relate the Higgs boson and the cosmic inflation.\\

In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions , such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes. 
In this work, we will analize the production of Higgs boson in association with a
single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC. 
The motivation of the work is this mechanism of production of the Higgs boson has not been observed before by any experiment. The exploration of Higgs production on the tH channel is subject relatively new. %The SM is used to study the tH channel and compare it with other Higgs production mechanisms results.
\\
Many channels are yet out of
reach experimentally. At the same time, many theoretical
proposals are yet to be put on test. It is possible that studies on the Higgs boson give evidence of small deviations from the SM  and test new physics that are beyond SM such as String Theory and  Supersymmetry. \\
%********************************** % Third Section  *************************************

\section{The Standard Model}  %Section - 1.3 
The SM, created in the decade of seventies, is a successful theory that explains the structure of matter and the interactions of three of the four fundamental forces which are electromagnetic, strong and weak forces. The gravitational force is yet to be included due to the scale of interaction with respect to the other 3.  All the matter is composed of three kinds of particles: leptons, quarks and bosons, also called mediators.\\

For the leptons we have electrons ($e$), muons ($\mu$), and taus ($\tau$) with charge -1 and their neutrinos $\nu_e, \nu_\mu,\nu_\tau$, 	are chargeless particles. Leptons have their respective antiparticle; same structure with opposite charge. 
 All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$. \cite{griff}.% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless. \\
\\

 Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. \\
Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell. \cite{griff}
Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.
\\

Quarks were first theorized by Murray Gell-Mann and 
George Zweig in 1964, were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until scattering experiments at the Stanford Linear Accelerator Center in 1968.\cite{griff}
There are 6 of them: up (1968), down (1968), strange (1968), charm (theorized in 1970, discovered 1974), bottom (theorized 1973, discovered 1977), top (theorized 1973, discovered 1995).
\\

Quarks have characteristics such as  electric charge, mass, color charge, and spin. The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down , strange and bottom quarks have charge of $-\frac{1}{3}$. Among them , the top quark is the most massive of all, while the up and down are the least massive. 
The lepton and quarks have their respective antiparticle, which have the same mass, but inverted charge.\\  
Some of the particles in the SM are not stable, so they decays and form particles with lower masses. Other particles do not decay or their lifetimes are very long. The final states can be represented with a Feynman diagram according to the SM vertices. \cite{mark}

\begin{center}
    \begin{figure}[!htbp]
        \centering
        \includegraphics[scale=0.3]{Chapter1/sm1.png}
        \caption{Standard Model to date\protect \footnotemark }
        \label{sm1}
    \end{figure}
\end{center}
\footnotetext{Taken from Wikimedia. \small \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}}

The last group of the family are the bosons,which have a spin 1 and 0. 
There are 5 bosons: $W^{\pm}$ , $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered , is in charge of give the property of mass to particles via Higgs mechanism. Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}. 
\\
The $W$,$Z$  and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
Those bosons act as mediators in decays and creation of complex
particles, as mesons and baryons.\\

%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force. In case of its existance, it should have a spin 2 and mass 0.

\begin{center}
    \begin{figure}[!htbp]
        \centering
        \includegraphics[scale=0.35]{Chapter1/sm.png}
        \caption{Particle interactions in Standard model}
        \label{sm}
    \end{figure}
\end{center}

There are experiments that detects particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab  in United States of America, KEK in Japan, etc. More information about the LHC will be described in the next chapters.
\\
Since quarks and gluons only exist in bound states, it is imposible to observe isolated quarks except the top quark, which decays before it has time to form a
bound state. As two quarks are separated, the strong force between them increases
which is equivalent to the potential energy increasing. This energy transforms into
quark-anti-quark pairs. \\

The table \ref{SM table} contains the characteristics of each particle in the SM. Note the distance column refers to particles moving with speeds near light speed. This column visualize the distance traveled in the predicted lifetime of the particle. And also give us a perspective of how hard is the detection of the particles due to lifetime. Stable lifetime means that the particles do not decay or can exist until they can interact with detectors. \\

\begin{table}[!htbp]
\caption{Table of particles in SM\cite{pd}. Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
\hline 
Particle	& Mass (MeV/$c^2$)  &Charge  & spin &Lifetime (s)  & Distance in lifetime (meters) \\ 
	\hline 
Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable &  -\\ 
	\hline 
Charm ($c$)	& 1280 &$\frac{2}{3}$  &  $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ &  5.21$\times 10^{-3}$ \\ 
	\hline 
Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$  & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$   \\ 
	\hline 
Down ($d$)	& 4.6 &$-\frac{1}{3}$  & $\frac{1}{2}$  & Stable & - \\ 
	\hline 
Strange ($s$)	& 96 &$-\frac{1}{3}$  & $\frac{1}{2}$  &$1.24 \times 10^{-8}$  & 58.7 \\ 
	\hline

Bottom ($b$)	& 4180 &$-\frac{1}{3}$  &  $\frac{1}{2}$ &$1.3 \times 10^{-12}$   & 6.16 $\times 10^{-3}$\\ 
	\hline 
$W$ 	& 80379 &$\pm$1  & 1 & 3$\times$ 10$^{-25}$ &  1.42$\times 10^{-15}$\\ 
	\hline 
$Z$ & 91187.6 &0  & 1 & 3$\times$ 10$^{-25}$  &1.42$\times 10^{-15}$ \\ 
\hline
Photon ($\gamma$) & 0 &0  &  1&Stable  & - \\ 
\hline
Gluon ($g$)	& 0 &0  &  1&Stable  & - \\ 
	\hline 
Higgs ($H$)	& 125.18 &0  &  0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
	\hline 
Electron ($e$)& 0.511 & -1 &   $\frac{1}{2}$& Stable & - \\ 
	\hline 
Muon ($\mu$)	& 105.7 & -1  &  $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
	\hline 
$\tau$	& 1776.86 &-1  &  $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 
	\hline 
$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 &  $\frac{1}{2}$ & Stable &  -\\
	\hline 
\end{tabular} 
\label{SM table}
\end{table}
\newpage

\section{Higgs Boson}
The Higgs is a boson with spin 0 and chargeless. First theorized in 1964 by a group of theoretical physicist composed by Peter Higgs, Fran\c cois Englert, Robert Brout, Gerald Guralnik, C. Richard Hagen, and Tom Kibble in separated groups. They formulated the Higgs mechanism that explain the generation of mass for the particles . \\

The theory also explains Higgs bosons give the mass to the particles via Higgs Field and the mass of Higgs boson itself.  The Higgs boson was discovered recently on year 2012 in the experiments ATLAS and CMS at CERN. The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV ,where investigators worked on the data and detecting various decay modes that generates final states such  as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}. \\
The mass of this boson has been  measured and its production and decay
rates are  consistent with the SM prediction. The mass of the Higgs boson measured is 
approximately 125 MeV. The Higgs boson lifetime is 1.56 $\times$ $10^{-22}$. That is why the Higgs boson was very difficult to detect in the particle detectors. \\

\pagebreak

\section{Top quark}
The top quark  is the most massive particle  with a charge of 2/3 with spin of 1/2. First proposed by  M. Kobayashi and T. Maskawa in 1973 to explain observed CP violations in Kaon decay\cite{griff}. On 1995, in the Tevatron at Fermilab in Illinois, the top quark  was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top} .
Since then,the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.\\
However, the top quark often receives special attention in new physics models because its mass requires near unity coupling to the Higgs boson \cite{top}.
As shown in table \ref{SM table}, the top quark lifetime is so small that they decay before they can hadronise, that is to say, the process to create hadrons from quarks and gluons.\\

One of  interesting the properties of top quark is its mass.
The top quark mass is a free parameter in the SM and was extracted using indirect measurements and relying on SM calculations. The measured value of top quark mass is of 173 Gev\cite{pd}.
The top quark mass is a very important
parameter that puts a constraint in the Higgs boson mass and also takes an important role in electroweak symmetry breaking\cite{top}.\\

The production of top quark can be generated in differents ways. In tevatron and LHC, the production of $t\bar{t}$ comes from ggF (gluon gluon fusion) via strong force. Even it is posible to create a single top quark in the LHC via electroweak interactions (with a W boson) \cite{th1}.  
The top quark, due to its big mass, always decays into a W boson and a b quark. But since the W boson have various decays, the top quark can generate many posible particles, acording to W boson decays. Some posible decays of top quark is the decay to a lepton such as muon, electron or tau and their neutrinos . %The antitop, antiparticle of top quark, can decay to W$^{-1} \bar{b}$ and its decay is the same as top, but with inverse signal.

\pagebreak

\section{Higgs mechanism}
In the SM, mathematically the particles are described in form of fields. The SM for electroweak interactions is described as a gauge theory with a symmetry group SU(2)$\otimes$U(1)
that describes the weak and electromagnetic interactions
due to the exchange of spin 1 gauge fields($W^{\pm}$,$Z$) for the weak part and a photon for the electromagnetic part. The Higgs mechanism give bosons and fermions their mass.

The lagrangian for the electroweak part of SM
\begin{align}\label{sml}
\mathcal{L_{\text{EW}}}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{Higgs} + \mathcal{L}_\text{Yukawa}
\end{align}
The first term of the lagrangian refers to gauge bosons  
 \begin{align}\label{smg}
 \mathcal{L}_\text{gauge}=-\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[\sum_{i}G^{i\mu\nu}G^i_{\mu\nu}\right]
 \end{align}
where  the  F and G  are 
\begin{align}
F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu \\
G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu 
\end{align}

$W^i$ (i=1,2,3) are three  SU(2) gauge bosons and B is a U(1) gauge boson.\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
	+1 \quad  \text{for even permutation} \\
	-1 \quad \text{for odd permutation}\\
	0 \quad \text{i=j, or j=k, or k=i } 
	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$ , $Z$ and $\gamma$ vector boson \cite{ew1,ew2}. %Z bosons  and photons will be formed by a combination of W and B fields.\\
\\

The second term refers to kinematic energy of fermions 
\begin{align}
\mathcal{L}_f=\sum_{m=1}^{3} \left(\bar{q}^m_{L}i \cancel{D}_L q^m_{L}+  
\bar{l}^m_{L}i \cancel{D}_L l^m_{L} +\bar{u}_{R}^m i \cancel{D}_R u_{R}^m
+\bar{d}_{R}^m i \cancel{D}_R d_{R}^m+\bar{e}_{R}^m i \cancel{D}_R e_{R}^m \right)
\end{align}
where  m is the family index, and L(R)
refer to the left (right) handed particles.\footnote{$\bar{\psi}$ denotes the adjoint spinor $\bar{\psi}=\psi^\dagger \gamma^0$.
	$\cancel{D}=\gamma^\mu D_\mu$.
$\gamma$ are the Dirac matrices}. 
The gauge covariant derivatives  are given by
\begin{align}
{D}_L =\left(\partial_\mu+ig\sigma^iW^i_\mu +ig'Y B_\mu\right)\\
{D}_R =\left(\partial_\mu +ig' Y B_\mu\right)
\end{align}
where $\sigma^i$ are the pauli matrices. L and R refers to left and right handed fields.
The left handed fields for the first family are defined by the following doublets
\begin{align}
    q_L=\left(\begin{array}{c}
 u_L \\
d_L
\end{array} \right) \qquad   l_L=\left(\begin{array}{c}
 \nu_{eL} \\
e^-_L
\end{array} \right)
\end{align}
and the right handed fields
\begin{align}
   u_R,d_R,e^-_R 
\end{align}

%The  charge of particle Q is given by $Q=T^3+Y$ with $Y$ the hypercharge and $T$ the third component of the weak isospin . For  left handed doublets $T^3=\pm 1/2$  and $T^3=0$ for right handed singlets and the coefficients.
%g and g' are boson coupling constants\cite{ew2}\\
The hypercharges Y depend of the particle type. For left handed 
\begin{align}
    Y(l_L)=-\frac{1}{2} \quad Y(q_L)=\frac{1}{6} 
 \end{align}
 for right handed 
 \begin{align}
Y(e_R)=-1  \quad Y(u_R)=\frac{2}{3} \quad Y(d_R)=-\frac{1}{3}
\end{align}
The lagrangian for Higgs field
\begin{align}
\mathcal{L}_{\text{Higgs}}=(D_\mu \Phi)^\dagger (D^\mu \Phi)-V(\Phi^\dagger \Phi)
\end{align}

where $D_\mu$ is a operator 
 \begin{align}
D_\mu = \left(\partial_\mu+i\frac{1}{2}\sigma^igW^i_\mu+i\frac{1}{2} g' B_\mu \right) 
 \end{align}
and the Higgs potential  $V(\Phi^\dagger \Phi)$
\begin{align}
 V(\Phi^\dagger \Phi)=\mu^2 \Phi^\dagger \Phi +\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2     
\end{align}

 %is Higgs field which is a complex scalar field that exists in a vacuum and the potential is symmetric under rotations in $\Phi$ space. 
 $\Phi=\left(\begin{array}{c}
 \phi^+ \\
\phi^0
\end{array} \right)  $ is a SU(2) doublet of  scalar fields. V is symmetrical under rotations in $\Phi$ space
and parameters  $\lambda $ and $\mu^2$ are  parameters of the potential. The Higgs potential for $\mu^2 <0$ and $\lambda>0$ can be visualized in the figure \ref{hat}

%The $\lambda $  term describes self-interactions among the scalar fields. Vacuum stability requires $\lambda $  to be greater than zero. The $\mu$ parameter is a mass parameter for field $\Phi$. $\mu$ and $\lambda$ are Higgs coupling parameters.  %If $\mu > 0$, preserve  the symmetries of the Lagrangian.
%In the vacuum, the lowest  state of energy will be for $\Phi=0$  and the theory is reduced to 
%quantum electrodynamics with a massless photon and a charged scalar
%field $\Phi$ with mass $\mu$.\\
%For $\mu < 0$, the ground state is degenerate and this results in a spontaneous symmetry breaking.

%\begin{figure}[ht!]
%\centering
 %   \begin{tikzpicture}[scale=1.75]
  %      \begin{axis}[
   %         hide axis,
    %        samples=30,
     %       domain=0:360,
      %      y domain=0:1.25
       % ]
        %\addplot3 [surf, shader=flat, draw=blue, fill=white, z buffer=sort] ({sin(x)*y}, {cos(x)*y}, {(y^2-1)^2});
        %\end{axis}
    %\end{tikzpicture}
%    \caption{Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu>0$, also called the mexican hat potential. At the top, for $\mu=0$, there is no mass for the particle.}
%\end{figure}

\begin{figure}[ht!]
    \centering
    \begin{tikzpicture}[scale=1.75]
        \begin{axis}[
            hide axis,
            %axis lines=middle,
%            axis on top,
%            axis line style={blue,dashed,thick},
%            ymin=-2,ymax=2,
%            xmin=-2,xmax=2,
%            zmin=-2,zmax=2,
            samples=30,
            domain=0:360,
            y domain=0:1.25,clip=false
        ]
        \addplot3 [surf, shader=flat, draw=black, fill=white, z buffer=sort]
           ({sin(x)*y}, {cos(x)*y}, {(y^2-1)^2});
        \draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:1,0,0)
                    node[below,font=\footnotesize]{$\Phi_{\text{IM}}$};
        \draw[blue,thick,-stealth] (axis cs:1,0,0) -- (axis cs:1.3,0,0)
                    node[above,font=\footnotesize]{};
        \draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,-1,0)
                    node[left=2mm,font=\footnotesize]{$\Phi_{\text{RE}}$};
        \draw[blue,thick,-stealth] (axis cs:0,-1,0) -- (axis cs:0,-1.5,0)
                    node[right=1mm,font=\footnotesize]{};
        \draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,0,1)
                    %node[left=2mm,font=\footnotesize]{$\phi_{\text{RE}}$}
                    ;
        \draw[blue,thick,-stealth] (axis cs:0,0,1) -- (axis cs:0,0,1.3)
                    node[right,font=\footnotesize]{$V(\Phi)$};
        \end{axis}
    \end{tikzpicture}
    \caption{Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu^2<0$ and $\lambda>0$ also called the mexican hat potential.}
    \label{hat}
\end{figure}

Electroweak symmetry breaking refers to the choice of ground state
\begin{align}\label{vmin}
	\Phi_0=\frac{1}{\sqrt{2}}\left(\begin{array}{c}
		0 \\
		v
	\end{array} \right)
	% \Phi =\sqrt{-\frac{\mu^2}{2\lambda}}=\frac{v}{\sqrt{2}}  \qquad \lambda >0
\end{align}
where $v=-\frac{\mu^2}{\sqrt{2}}$  is called the vacuum expectation value.\\

%Now, since the potential depends on $\Phi^\dagger \Phi$, We can select  $\Phi$ in the form 
%\begin{align}\label{doublet}
 %\Phi=\frac{1}{\sqrt{2}}\left(\begin{array}{c}
%0 \\
%v+h
%\end{array} \right) %\equiv v
%\end{align}
%here $\phi^+=0$ and h is a Higgs field  with respect to the minimal value v.

%Due to the conservation of electric charge,  only a neutral scalar field can acquire a vacuum expectation value.
%With this choice the scalar doublet has U (1)Y charge (hypercharge) $Y_\Phi$= 1
%and the electromagnetic charge is 
%\begin{align}
 %   Q=\frac{1}{2}(\sigma_3+Y)
%\end{align}
%so Q($\phi$) = 0. That is, electromagnetism is unbroken by the scalar VEV. The equation \ref{doublet} breaks the symmetry
%\begin{align}
%SU(2)_L  \otimes U(1)_Y \rightarrow U(1)_{em}
%\end{align}
Taking \ref{vmin} and substituting in $\mathcal{L}_\text{Higgs}$, we get 
\begin{align}\label{W}
\begin{split}
%(D_\mu \Phi)^\dagger (D^\mu \Phi) &=\left| \left(\partial_\mu+(ig/2)\sigma^iW^i_\mu+i\frac{1}{2} g' B_\mu \right)\frac{1}{\sqrt{2}}\left(\begin{array}{c}
%0 \\
%v
%\end{array} \right) \right|^2 \notag\\
%&=\frac{v^2}{8}\left| \left(g\sigma^i W^i_\mu + g' B_\mu \right) \left(\begin{array}{c}
%0 \\
%1
%\end{array} \right)        \right|^2 \notag\\
%&=\frac{v^2}{8}\left(\begin{array}{c}
 %    gW^1_\mu-igW^2_\mu \\
  %    -gW^3_\mu+g'B_\mu
%\end{array} \right) \notag\\
(D_\mu \Phi)^\dagger (D^\mu \Phi)& =\frac{v^2}{8} \left(g^2 ((W^1_\mu)^2 +(W^2_\mu)^2 )+( gW^3_\mu -g'B_\mu)^2 \right)
\end{split}
\end{align}

we define the physical vector boson $W^-_\mu$. $W^+_\mu$ and $Z$ 
\begin{align} 
W^{\pm}_\mu=\frac{1}{\sqrt{2}} (W^1_\mu \mp iW^2_\mu) \label{smo}\\ 
Z_\mu=\frac{1}{\sqrt{g^2+g'^2}}\left(gW^3_\mu -g'B_\mu   \right) \label{zboson}
\end{align}

%From equation \ref{smo}, we can express $W^1_\mu$ and $W^2_\mu$ in terms of $W^{+}_\mu$ and $W^{-}_\mu$
%\begin{align}\label{s2}
%W^{1}_\mu=\frac{W^{+}_\mu+W^{-}_\mu}{\sqrt{2}} \qquad  W^{2}_\mu=i\frac{W^{+}_\mu - W^{-}_\mu}{\sqrt{2}}
%\end{align}

%and the mass term
%\begin{align}   
 %    \frac{v^2}{8}g^2 W^\dagger_\mu W^\mu \rightarrow \frac{1}{2} \left( \frac{g v}{2} \right)^2      \notag
%\end{align}
Now introducing \ref{smo} and \ref{zboson} in \ref{W},
\begin{align}
(D_\mu \Phi)^\dagger (D^\mu \Phi)=\frac{v^2}{8}\left(2g^2 W_\mu^+ W^{\mu-} + (g^2+g'^2)Z_\mu Z^\mu  \right)  
\end{align}
from the coeficients, we get the $W$ and $Z$ mass  
\begin{align}
m_W=\frac{gv}{2} \qquad  m_Z=\frac{v}{2}\sqrt{g^2+g'^2}
\end{align}

%and the photon that in this case is the field A
%\begin{align}
 %       A_\mu=\frac{1}{\sqrt{g^2+g'^2}}\left(g'W^3_\mu +gB_\mu   \right)
%\end{align}
%with mass 
%\begin{align}
 %       m_A=0
%\end{align}

The last part of the lagrangian is the Yukawa lagrangian
\begin{align}
\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
\end{align}
The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between Higgs doublet $\Phi$ and the fermions.\footnote{Here $
	\tilde{\Phi}=i\sigma^2 \Phi^\dagger =\left(\begin{array}{c}
	\phi^{0^\dagger} \\
	-\phi^-
	\end{array} \right)
	% \Phi =\sqrt{-\frac{\mu^2}{2\lambda}}=\frac{v}{\sqrt{2}}  \qquad \lambda >0
	$ is necessary for the correct transformation in the case of up quarks. \\
h.c refers to hermitian conjugate terms.  }  The indices  m and n mean sum over the families. \\
%It is required to have two representations of Higgs fields
%with $Y=\frac{1}{2}$  and $\frac{1}{2}$ to give masses to  quarks and electrons.

By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$,  it is obtained for $u$ quark
\begin{align*}
\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
\end{align*}
from which the masses for the fermions shown to be proportional to the Yukawa couplings
\begin{align*}
m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
\end{align*}

\pagebreak

\section{Higgs production mechanisms}
During a particle collision, there are various ways that the Higgs boson can be created. The most common is the gluon gluon fusion process ($gg$F) which is the process which involve two gluons  mediated by the exchange of a virtual, heavy top
quarks.  Another process  is vector boson fusion (VBF), where two fermions interact via a vector boson ($W$ or $Z$ ) and create a Higgs along with other particles. There is also the vector higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}. These processes are shown in the figure \ref{psu} \\

In the recent years, people have studied the top anti top Higgs  ($t\bar{t}H$) process, in order to detect a Higgs boson, via multilepton signals \cite{th1}.
In this process, the creation of a Higgs boson comes from a intection via $t\bar{t}$. In the figure \ref{psu}, the $t\bar{t}H$ starts with 2 gluons which decay to two $t\bar{t}$ pairs and after that , the interaction $t\bar{t}$  generates a Higgs. The last process, subject of study in this thesis, is the top Higgs ($tH$) process. This process is a rare expected process with a very small production rate\cite{pd}.  In the figure \ref{thw}, is another way to produce $tH$, in association with a $W$.

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.5]{Chapter1/pg.png}
\caption{Different Higgs production mechanism, from the most likely to least likely}
\label{psu}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.7]{Chapter1/thw.png}
\caption{$tHW$ mechanism}
\label{thw}
\end{figure}

In tH process, Higgs boson is radiated from a single top quark as shown in \ref{psu}. tH process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens to new discoveries.
\\

In particle physics, cross section ($\sigma$) describes the likelihood of two particles interacting under certain conditions.
 Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{2}$ .
\\
The cross section is important in the evaluation of events for specific processes. In order to get the number of events for a specific process,  the reaction rate $N$ is determined by the total cross section $\sigma$ and the luminosity L.\\
%L is called luminosity, that is the number of particle interactions can be produced in a detector per second . 
The unit of measurement of luminosity is  cm$^{-2}$s$^{-1}$.  Therefore, The reaction rate is

\begin{align} \label{nr}
N_R=\sigma \text{L}
\end{align}
In practice, the luminosity is measured by counting the number of events for a well known process.

\begin{table}[ht]
\centering
\caption{	Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2 \protect \cite{pd}}
\begin{tabular}{|c|c|c|}
\hline
Production mechanism &
$\sigma$ (picobarns pb) & Number of events \\
\hline
$gg$F & 48.93 & 1756587\\
\hline
VBF & 3.78 & 135702\\
\hline
$WH$ & 1.35 & 48465\\
\hline
$ZH$ &0.88 & 31592\\
\hline
$t\bar{t}$H & 0.50 & 18255\\
\hline
$tH$	& 0.015 & 560.39\\
\hline
\end{tabular}
\label{crt}
\end{table}

In the table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$ , that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.

\begin{figure}
\centering
\includegraphics[width=12cm,height=7cm]{Chapter1/7-14xsec.eps}
\caption{
Cross section for different processes generated in a pp collision} \label{csp}
\end{figure}

Here we can see ggF process have the biggest cross section of all Higgs mechanism and generates the greatest number of events possibles. For the processes tH and $t\bar{t}$H, they have the smallest cross section, so the probability for the processes is low and generates a small number of events. 
\pagebreak

\section{Higgs decay rates}
In particle physics,two importatns properties are the lifetime and the decay rates of a particle. The lifetime is related to the total decay rate $\Gamma$, that is the probability per unit of time a particle decay, 
\begin{align}
    dN=-\Gamma N dt
\end{align}
with N the original number of particles before the decay. From here is evident that number of particles left in a decay is

\begin{align}
N(t)=N_0 e^{-\Gamma t}
\end{align}

%For a particle that decays into several particle , $\Gamma$ is given by
%\begin{align}\label{dm}
%\Gamma=\frac{S}{2\hbar m_n}\int \left| M \right|^2 (2\pi)^4 \delta^4(p_1-p_2-...p_n)\times \prod_{j=2}^n 2\pi \delta (p_j^2-m_j^2 c^2)\theta (p_j^0)\frac{d^4 p_j}{(2\pi)^4}
%\end{align}
%where $m_n$ and $p_n$ are the mass and momentum of the particle n with n=1,2,3,... . S is a statistical factor that avoid identical particles counting. If there are no identical particles, S=1 ,and for identical particles $S=\frac{1}{s!}$ with s is the number of identical particles. $\mathcal{M}$ is the amplitude which is a momenta function that is calculated acording to the Feynman diagrams.$\theta(p_j^0)$ is a Heaviside function,
%$p_j$ is the outgoing momentum and $p^0_j=E_j/c>0$.\cite{griff}

The number of particles decreases over time exponentially and this can be measured. With this, it is possible determinate the mean lifetime\cite{griff}
\begin{align}
\tau=\frac{1}{\Gamma}
\end{align}
In case of  the decay rate to a specific process, it is necessary get the branching fraction of the process. 
The branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.
\begin{align}
BR_i =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
\end{align}
Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds,it has the same dimension as mass (or energy)\footnote{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} . The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV , but has not yet been measured due to the detector resolution \cite{cms-manual}.
\\
\begin{table}[!htbp] 
\caption{SM Higgs boson branching ratios for  $M_H$ =125 GeV \protect \cite{pd}}
\centering
\begin{tabular}{|c|c|}
\hline
Higgs decay & Branching ratio (BR)\\
\hline
$H \rightarrow$ b$\bar{b}$ &$58.4\%$ \\
\hline
 $H \rightarrow$ $W^+W^-$ &$21.4\%$ \\
\hline
$H \rightarrow$ $\tau^+ \tau^-$ & $6.27\%$\\
\hline
$H \rightarrow$ ZZ &$2.62\%$\\
\hline
$H \rightarrow$ $\gamma\gamma$ &$0.227\%$\\
\hline
$H \rightarrow$ Z$\gamma$ &$0.153\%$\\
\hline
$H \rightarrow$ $\mu^+\mu^-$ &$0.0218\%$\\
\hline
\end{tabular}
\label{higgs1}
\end{table}
The decay  $H \rightarrow$ $b\bar{b}$ have a branching ratio a bit more than 50$\%$, therefore is the most likely decay Higgs boson can decay. Due to this,  $H\rightarrow b\bar{b}$ is a very studied process and most likely to detect a Higgs boson in the data after reconstruction. The decay  $H \rightarrow$ $\mu^+\mu^-$ has a very low branching ratio. This decay is very rare but not imposible to detect in the future.  In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$\\

\section{$tH$ production mechanism}
The production of $tH$, where a Higgs boson can be radiated
either from the top quark or from the exchanged $W$ boson in the two dominant leading order
diagrams in figure \ref{newth} provides a unique opportunity to study the relative sign of the coupling.
In SM , the two diagrams interfere negatively and thereby suppress the production cross section.
Any deviation from the SM can lead to a large enhancement of the event rate.
 $\kappa_t$ and $\kappa_V$ are the coupling parameters, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson. \\

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.5]{Chapter1/newtHq.png}
	\caption{tH mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
\end{figure}
\pagebreak

\end{linenumbers}

\end{chapter}

### 2019-10-07 tesis_hiram/Chapter2/chapter2 (hiram-HP-ProDesk-400-G3-SFF's conflicted copy 2019-09-02).tex
tesis

%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Second Chapter *********************************
%*******************************************************************************
\chapter{The LHC and CMS}

\section{The Large Hadron Collider}
\begin{linenumbers}
The Large Hadron Collider (LHC) is one the  largest and most powerful particle accelerator in the world. It came on operation on 10 September 2008 and it is the most recent addition from the  European Organization for Nuclear Research (CERN).  The LHC is a 27 kilometer ring composed of  superconducting magnets with accelerating structures to boost the energy of the particles. \\

The LHC is designed to accelerate particles to high energies and generate collisions. There are several
experiments installed along the LHC ring. One of them is ATLAS, located on Point 1 between the two injection lines , which is a general purpose detector. From ATLAS at point 5 is another general purpose detector,the compact muon solenoid  (CMS). A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
\\

Inside the accelerator, two high energy particles beams travel at
close to the speed of light before they collide. 
In order to make them collide, beams travel in opposite directions in separate beam pipes, 
two tubes kept at ultrahigh vacuum. 
By using of superconducting electromagnets that generates a powerful magnetic field , the beams are guided around the accelerator ring. \\
The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.For that, it is required to have  magnets to a temperature of  $‑271.3$ C. 
For reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}

\pagebreak

\begin{figure}[!htbp]
\centering
\includegraphics[width=17cm,height=11cm]{Chapter1/cern.jpg}
\caption{Large hadron collider from CERN} \label{lhc}
\end{figure}

The process for the beam collision comes on various stages inside of the collider, which also is composed of smaller particle accelerators.\\
Protons in the LHC start out as hydrogen atoms stripped of their electrons. The first accelerating stage the protons are subjected to is a linear accelerator, Linac2,
which accelerates them up to 50 MeV . The protons are then sent into the
Proton Synchotron Booster which accelerates them up to 1.4 GeV before sending them to the Proton Synchotron (PS). The protons leave the PS at 25 GeV before entering the Super Proton Synchotron (SPS), which accelerates them to the LHC injection energy of 450 GeV. After this stage, the beam is ready to be injected into
the LHC through one of two injection lines with 6.5 TeV.\cite{cern3}

\begin{table}[!htbp]
\centering
	\caption{Accelerator operation energies}
	\begin{tabular}{|c|c|}
		\hline
		Accelerator & Energy \\
		\hline
		Linac 2 &  50 MeV \\
		\hline
		PS Booster & 1.4 GeV \\
		\hline
		Proton Scyncroton (PS) & 25 GeV\\
		\hline
		SPS &  450 GeV\\
		\hline
		LHC & 6.5 TeV\\
		\hline
	\end{tabular}
\end{table}
\pagebreak
Inside the accelerator, collided protons generates an amount of particles such as pion and kaons, which are the most commons, created by the jet particles that were created after the collision. Besides of the particles created by the quarks of the proton shattered, gluons are also radiated and create new particles and photons are radiated too. \\
During the collision time, the main  detectors of LHC capture the energy signal
and save the data in supercomputers. Those high end computers starts to measure the energy signals in order to asign a type of events.
\\

The main objetive of the LHC is to study the nature of electroweak symmetry breaking for the Higgs mechanism is associated. 
The experimental study of the
Higgs mechanism can also  verify the mathematical results  the Standard Model at higher energy scales.\\
Alternatives to the Standard Model that involves different symmetries are also put on test. With the exploration of theses theories, people have hope for a discovery that guide them toward a unified theory, so the importance to accelerate particles to higher energy scales.
\\
For improve the results of experiments, the LHC has a schedule where there is a period of experiments that last for three years. Ending the experimental time, the engineers of the LHC start the maintenance time which last between three or four years.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{Chapter2/lum6.png}
\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. %
\cite{cern3}}
\label{lhc-lumi}
\end{figure}
From the figure \ref{lhc-lumi}, shows the Large Hadron Collider forecast for the increase of luminosity for the next years. Red dots are peak luminosity expected to reach and blue line is integrated luminosity.  \\
In the year 2018, the maximum integrated luminosity is around 150 $fb^{-10}$\cite{cern3}. From 2019 to 2021 the second phase of maintenance, where engineers increase the performance of the accelerator, give maintenance to the system and introduce new components to the complex. After that period, the LHC starts new collision experiments at even higher energies in order to explore new particle phenomena.

\pagebreak

\section{The Compact Muon Solenoid}	
The Compact Muon Solenoid (CMS) is a detector with multiple uses in the LHC and part of the main experiments at CERN. Located underground in the France Switzerland border , in the city of Cessy, France.
This detector was designed in the early 1990s, based on the mass limit of the Higgs boson,  and put on operation in 2008,  it is a big solenoid of  that generates a great magnetic field of 4 teslas with the objective to separate particles after a particle collision.
 The detector has 21 metres long, 15 metres wide and 15 metres high.
Inside of the complex, there are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easy, the complex is buried 100 meters underground.\\

The CMS experiment is composed of several detector layers called chambers that allow identify and save different types of energy signals (momentum) and it is saved in a powerful supercomputers that separate and classify the data according to certains variables. The general parts of the CMS are the Silicon tracker , an electromagnetic calorimeter,a hadron calorimeter, the solenoid (superconducting magnet) and the muon detector layer. \\

The magnet is a big superconducting solenoid that generates a magnetic field of 4 Teslas. The magnet is 13 m long and it has a diameter of 5.9 m with a weight of 12000 ton. The reason for such a strong magnetic field is for obtain a better momentum resolution combined with the alignment of the detectors.
The magnetic flux is returned via a 1.5 m thick saturated iron yoke instrumented with four stations of muon
chambers.

\begin{table}[ht]
	\caption{Characteristic of the CMS superconducting solenoid \cite{cms-manual}}
	\centering
	\begin{tabular}{|c|c|}
		\hline
		Field strength & 4 T \\
		Inner Bore & 5.9 m \\
		Length & 12.9 m\\
		Number of Turns & 2168\\
		Current & 19.5 kA\\
		Stored energy & 2.7 GJ\\
		Hoop stress & 64 atm\\
		\hline
	\end{tabular}
	\label{tab:my_label}
\end{table}

%The trigger or event selection process must reduce the approximately 1 billion interactions per second to more less than 100 events per second for storage and subsequent analysis.\\

 The objetives of the CMS experiment are numerous. One of them is
identification of muons by measuring the momenta and scattering angle. Search for evidence  and give proof of super symmetry  for show evidence of BSM (Beyond Standard Model). Detection of massive vector bosons $W^\pm$ and Z via $e^+e^-$ and $\mu^+ \mu^-$ decays.\\
Search for extra dimensions from BSM theory that could be related to production of particles and quantum gravity. Study of QCD, electroweak and flavor physics to detect new decays predicted by SM at higher energies. Heavy ions collision experiments for the study of production of  very strongly interacting nuclear matter\cite{cms-manual}.
This experiment along the ATLAS experiment discovered the Higgs boson in 2012.
\\

\subsection{Silicon Tracker}

\subsection{Electromagnetic calorimeter}

The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillanting crystals (emits light when particles interact with the crystal). These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps. The barrel section  of the ECAL covers the pseudorapidity range $|\eta| < 1.479$. The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face. The crystal length is 230 mm.  The crystals are stored in a thin walled glass-fibre alveola structures that have the same shape. These structures are assembled in modules  and arranged in arrays of four separated by aluminium webs.The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\

The endcaps cover have the  range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has  identically shaped crystals grouped in
mechanical units of 5×5 crystals (supercrystals, or SCs) consisting of a carbon-fibre alveola
structure. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$ , 28.62 $\times$ 28.62 mm$^2$ and a length of 220 mm.
\\

In the barrel, there photodetectors called avalanche photodiodes (APD), made of silicon with a active area of  5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal. These have a operating voltage of 5 V and paired they reach a voltage between 340 to 430 V. At the endcap , the photodetectors are vacum photodiodes (VPT) that are photomultipliers having a single gain stage , made of with an anode of copper mesh (10 $\mu m$) , allowing to operate in the magnetic field. VPT have a size of 25 mm in diameter , glued to the back of each crystal.\\

There is also a preshower detector , which principal function  is to identify neutral pions in the
endcaps within the region 1.653 < |$\eta$| < 2.6. It also helps the identification of electrons
against minimum ionizing particles, and improves the position determination of electrons and photons.  %The ES is a sampling calorimeter with 2 layers: lead
%radiators initiate electromagnetic showers from incoming photons/electrons whilst silicon
%strip sensors placed after each radiator measure the energy deposited and the transverse shower profiles.

\subsection{Hadron calorimeter}
The hadron calorimeter (HCAL) along the ECAL, form a complete calorimeter that allows to measure the jets and missing transverse energy. HCAL is located in the barrel and the endcaps, surrounding the ECAL and affected by the magnetic field generated by the solenoid.\\
The Barrel section (HB) and endcap section (HE)  cover the pseudorapity 0 < $|\eta|$ < 1.3 and  1.3 < $|\eta|$ < 3.0 respectively.\\
The HB is an assembly of two half barrels, composed of 18 parts of brass alloy plates in wedge shape. These absorber plates in the innermost and outermost are made of stainless steel and brass respectively.\\
The longitudinal profile in the barrel going from an inner radius of 1777 mm to an outer radius of 2876.5 mm, divided by 17 plastic scintillador between the brass and stainless plates. Each scintillator are instrumented with a single wave 
lenght shifting fibers (WLS). Those fibers allows to carry the light from the scintillator to the readout system.\\

There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5, designed to measure the energy of foward jets but optimized for

\subsection{Muon detector}
 The muon detector system in the Compact Muon Solenoid (CMS) experiment  has 3 primary functions: muon
triggering, identification, and momentum measurement\cite{cms7}. 
The process utilized in the CMS muon chamber systems is gas ionization. Those gas-ionization particle detectors are arranged in a cylindrical barrel region and planar endcaps, in order to meet the geometry of the solenoid.The barrel detector is built with 4 station of 250 chambers inside the magnet return yoke.\cite{cms-manual}
 There are three main detectors used in the muon chamber: the drift tubes chambers (DT), the cathode strips chambers and the resistive plate chamber (RPC).These detectors operate independent and assembled in the CMS muon system. \\

The drift tubes are composed of rectangular drift cells. Those cells have a transverse size of 42 $\times$ 13 mm$^2$ with a 50 $\mu m$ diameter gold-plate stainless steel anode wire at the center that operates at voltages of over 3600 V. The cell design uses 4 electrodes , two of the are cathode strips to shape the effectve drift field. Two located on the side walls of the tube and two above and below the wires on the ground planes. The gas used by the tubes is a mix of Ar and CO$_2$ with a proportion of 85 $\%$ and 15 $\%$. The DT chambers cover the pseudorapidity region of $|\eta|<1.2$ where $\eta=-\ln{\tan{\frac{\theta}{2}}}$\cite{cms7} .
\\

The cathode strip chambers are located in the endcap regions of CMS, where the magnetic field is strong and non-uniform. These strips cover the $|\eta|$ from 0.9 to 2.4. Each endcap has 4 stations of chambers installed on the faces of the endcap disks, made of steel, perpendicular to the beam.CSC is composed of 6 layers that measures the $\mu$ position in the r-$\phi$ coordinate plane. \\
These cathodes have 1.7 to 3.4 m length and for each layer have 80 cathode strips.Between the cathodes, there are anode wires with a diameter of 50 $\mu m$ separated 3.16 mm. 
The chambers uses a gas mixture of 50$\%$ CO$_2$ , 40 $\%$ Ar and 10$\%$ CF$_4$. \\

Together with DT, cover the $|\eta|< 2.4$. These systems can each identify the collision crossing that generated the muon and trigger on (recolect) the transverse momentum ($p_T$).  \cite{cms-manual,cms7}

\begin{figure}[!htbp]
\centering
\includegraphics[width=10cm,height=6cm]{Chapter2/cms2.png}
\caption{View of Compact muon solenoid (CMS)}\label{cms}
\end{figure}

The resistive plate chamber allows increase the measurement efficiency of the crossing beam at higher luminosities. The RPC are located in the barrel and endcap regions , and have a dedicated triggering detector system that can provide measurements in the range of $|\eta|<1.6$.\\
\pagebreak

RPC are structured in a double gap chambers.
Each gap has a 2 mm thick resistive bakelite separated by a 2mm gass gap that are coated with a conductive graphite layer. They operate a voltage of 9.6 kV . The gas mix used in the RPC consist of 95.2$\%$ Freon
($C_2 H_2 F_4$ ), 4.5$\%$ isobutane ($C_4 H_{10}$), and 0.3$\%$ sulphur hexafluoride (SF$_6$ ). The distribution of the RPC in the barrel and the endcap is similar to DT and CSC ; 4 stations in the barrel and 3 in the endcap.\cite{cms7}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=11cm,height=7cm]{Chapter2/csc}
	\caption{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$.}
	\label{dt}
\end{figure}

The array of the DT , CSC and RPC are shown in the figure \ref{dt}. The vertical lines represent the endgap and the horizontal the muon barrel. The orange sections are the DTs , where the 4 DTs are labeled MB,CSC marked in green are labeled ME or muon endcap and RPC are the blue lines that are located in the barrel and the endcap. RPC are labeled RB and RE respectively. 
\\

The produced muons are measured in three zones: in the inner tracker, after the coil, and in
the return flux. Measurement the momentum of muons in the muon detector is determined by the muon bending angle at the exit of the 4T coil with the interaction point as the origin of the muon.\cite{cms7}\cite{cms-manual}

\chapter{Statistical Analysis}

\section{Statistical model}
In particle physics experiments one often searches for processes that have been predicted
but not yet seen

\section{Previous results for  \texorpdfstring{${t\bar{t}H+tH}$}  production}
% Uncomment this line, when you have siunitx package loaded.
%The SI Units for dynamic viscosity is \si{\newton\second\per\metre\squared}.
The discovery of a Higgs boson by the CMS and ATLAS experiments in 2012 opened a new field for exploration in the realm of particle physics. It is critical to study the couplings of
this new particle to other elementary particles to test whether it is the Higgs boson as predicted
by the standard model (SM). Of particular interest is the Yukawa coupling of the Higgs boson
to top quarks,$y_t$, as the top quark is widely believed to play a special role in the mechanism
of electroweak symmetry breaking due to its large mass.

Direct searches for tHq production using all relevant Higgs decay modes have previously been
carried out by CMS in the 8 TeV dataset  and in the 2015 13 TeV dataset using the H $\rightarrow$
b$\bar{b}$ channel. In the full 2016 13 TeV dataset, a search for t$\bar{b}$H production in multilepton
final states recently produced first evidence for associated production of top quarks and Higgs
bosons.

\section{Event selection}
The main analysis strategy is to obtain a selection of events compatible with certain characteristics of the signal at pre-selection level.\\
It is required:
\begin{itemize}
\item The events are selected those that contain two leptons ($l^+l^-$)  with the same sign.
\item Transverse moment $p_{t}$ > 25 and 15 GeV, for the muons.
\item A foward jet with $p_t$ > 40 GeV, | $\eta$ | > 2.4
\item One or more b-jets with (| $\eta$ | <2.4)
\end{itemize}

\begin{itemize}
	\item Rare SM: tttt,WWW,WWZ,WZZ,WW,tZq
	\item WZ:WZ,ZZ
\end{itemize}

\section{Boosted decision tree}
BDT Variables

\begin{itemize}
\item	Trailing lepton $p_{t}$
\item 	Total charge of tight leptons
\item 	min $\Delta$R (lepton pairs)
\item 	$\Delta\phi$ between highest $p_t$ lepton pair
\item 	Number of jets with |$\eta$| < 2.4
\item	Number of non b-tagged jets with |$\eta$| > 1.0
\item	Maximum |$\eta$| for jets
\item	$\Delta\eta$ (most forward light jet, closest lepton)
\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{itemize}

Common uncertainties for MC :
\begin{itemize}
	\item Muon identificacion 6$\%$
	\item Dimuon Trigger  1$\%$ 
	\item Luminosity measurement: ~2.6$\%$.
\end{itemize}

The likelihood function is the product of Poisson probabilities for all bins
\begin{align}
L(\mu,\theta)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)}
\end{align}

\begin{itemize}
	\item	N=number of bins
	\item	$\mu$=parameter of signal
	\item	s=signal
	\item	b=background
	\item	n=number of events
\end{itemize}

To test a hypothesized value of $\mu$ we consider the profile likelihood ratio
\begin{align}
\lambda(\mu)=\frac{L(\mu,\hat{\hat{\theta}})}{L(\hat{\mu},\hat{\theta})}
\end{align}

	\begin{itemize}
		\item Here $\hat{\hat{\theta}} $ in the numerator denotes the value of $\theta$ that maximizes L for the specified $\mu$,
		it is the conditional maximum-likelihood (ML) estimator of $\hat{\theta}$ (and thus is a function of $\mu$).
		The denominator is the maximized (unconditional) likelihood function, i.e., $\hat{\mu}$ and $\hat{\theta}$ are
		their ML estimators 
		\item The presence of the nuisance parameters broadens the profile likelihood as a
		function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
		of information about $\mu$ due to the systematic uncertainties
	\end{itemize}

For purposes of establishing an upper limit on the strength parameter $\mu$ , we consider two
closely related test statistics. First, we may define
\begin{align} 
q_{\mu}=  \Big\{    \begin{array}{ll}
                 -2\ln\lambda(\mu) \qquad \hat{\mu} \leq \mu	\\
0  \qquad \qquad \qquad \hat{\mu}< 0 
                \end{array}
\end{align}
 The reason for setting $q_\mu = 0$
for $\hat{\mu}>\mu $ is that when setting an upper limit, one would not regard data with $\hat{\mu}>\mu $ as
representing less compatibility with $\mu$ than the data obtained, and therefore this is not taken
as part of the rejection region of the test. From the definition of the test statistic one sees that
higher values of $q_\mu$ represent greater incompatibility between the data and the hypothesized
value of $\mu$.

To quantify the level of disagreement we compute the P-value
\begin{align}
P_\mu =\int_{t_\mu}^{\infty}f(t_\mu |\mu) dt_\mu
\end{align}
where $t_\mu$  is the value of the statistic $t_\mu$ observed from the data and $f(t\mu |\mu)$ denotes
the PDF (Probability density function) of t$_\mu$ under the assumption of the signal strength $\mu$
\begin{align}
f(t\mu |\mu)=\frac{1}{\sqrt{2\pi}} \frac{1}{\sqrt{t_\mu}}e^\frac{-t_\mu}{2}
\end{align}

\begin{center}
\begin{figure}
\includegraphics[width=16cm,height=12cm]{Chapter2/nos.png}
\caption{Prueba estad\'istica de $t_\mu$ y P valor para $t_\mu$}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\includegraphics[width=11cm,height=11cm]{Chapter2/normal-curve.jpg}
\caption{Distribuci\'on gaussiana que ilustra los valores de significancia y su probabilidad}
\end{figure}
\end{center}

%Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake

%Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons   fakes are estimated data

\footnote[1]{Due to existence of many uncertainties, it is necessary to sum all the uncertainties. When there is no Correlation, the uncertainties must be summed as the square root of the squares of each uncertainty}

\section{Event selection}
\section{Main Backgrounds}
In the leptonic channels, the main backgrounds are expected to
arise from the production of top quarks
\begin{itemize}
\item In the dominant t$\bar{t}$ mode, where 
same-sign dilepton signatures can occur when a non-prompt lepton from heavy-flavor
decay passes the signal selection, or in associated production with a W/Z or Higgs boson.
\item Processes with single top quarks also contribute, mostly in the associated production with a Z boson (tZ) or when produced with both a W and a Z boson (WZ) 
\item t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V): Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
\item WZ: Diboson production with leptonic Z decays and additional jet radiation in the final state can
lead to signatures very similar to that of the signal. Due to the larger cross section, the main
contribution arises from WZ production.
\item t$\bar{t}$H: tHq production which decays to same sign deleptons.
\item Rare SM (tZ,VVV,WW,tttt): Due to small event yields, all these process are grouped as one.
\item Non prompt leptons b quark decays and spurious lepton signatures from hadronic jets.
\end{itemize}

\begin{itemize}
\item t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V): Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and inefficiencies in the same way as signal events. 
\item WZ: Diboson production with leptonic Z decays and additional jet radiation in the final state can
lead to signatures very similar to that of the signal. Due to the larger cross section, the main
contribution arises from WZ production.
\item t$\bar{t}$H: tHq production which decays to same sign deleptons.
\item Rare SM (tZ,VVV,WW,tttt): Due to small event yields, all these process are grouped as one.
\item Non prompt leptons b quark decays and spurious lepton signatures from hadronic jets.
\end{itemize}

\begin{table}
\caption{Main backgrounds and their same sign $\mu\mu$ decay process}
\centering
\begin{tabular}{|c|c|c|}
	\hline
	Background & $\sigma$[pb] & Decay process \\
	\hline
t$\bar{t}$H	& 0.2151 & t$\bar{t}$H $\rightarrow$ W$^+$b W$^- \bar{b}$ W$^+$W$^-$ $\rightarrow$ $\mu^+ \nu_\mu$b$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
\hline  
t$\bar{t}$W  &0.2043 &t$\bar{t}$W  $\rightarrow$  W$^+$bW$^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
\hline
 t$\bar{t}$Z & 0.2529 & t$\bar{t}$Z  $\rightarrow$ W$^+$b  W$^-$$\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$  \\
 \hline 
  W$^+$W$^-$  &1.64 & W$^+$W$^-$ $\rightarrow$$\mu^+\nu_\mu$$\mu^-\bar{\nu_\mu}$ \\
    \hline 
  tZq  &0.0758 & tZq$\rightarrow$W$^+$b$\mu^+ \mu^-$ q$\rightarrow$$\mu^+ \nu_\mu$b $\mu^+\mu^-$ q \\
    \hline 
  t$\bar{t}$t$\bar{t}$  & 0.0091&t$\bar{t}$t$\bar{t}$ $\rightarrow$ W$^+$b   W$^- \bar{b}$  W$^+$b  W$^- \bar{b}$   $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$b   $\mu^- \bar{\nu_\mu} \bar{b}$ \\
    \hline 
  W$^+$W$^-$Z  & 0.1651& W$^+$W$^-$Z$\rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
    \hline 
 ZZZ  &0.0139 & ZZZ$\rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$  \\
    \hline 
  W$^+$ZZ  & 0.0556&W$^+$ZZ$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
  \hline 
 W$^+$Z &4.42965 &W$^+$Z$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
 \hline
ZZ &  1.256 &ZZ$\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
 \hline
\end{tabular}
\end{table}

\begin{tabular}{|l|p{6cm}|l|}
\hline
{Background}& {Sources of systematic uncertainty}&{Total Systematic Uncertainty} \\
\hline
t$\bar{t}$H  & \begin{itemize}
 	\item PDF 4$\%$ 
 	\item QCD scale 5.8$\%$
 	\item Higgs BR  1$\%$ 
 	\end{itemize}
 & 9.36$\%$ \\
 \hline  
 t$\bar{t}$Z&\begin{itemize} 
 			\item PDF 4$\%$ 
 			\item QCD scale 10$\%$ 
 \end{itemize} & 12.36 $\%$ \\
 \hline
 t$\bar{t}$W&{\begin{itemize} { 
 			\item PDF 4$\%$ 
 			\item QCD scale 12$\%$ 
 		}
 \end{itemize}} &14.03 $\%$ \\
 \hline
 {Rares SM} & {\begin{itemize} 
				\item Rare SM 50$\%$ 
	\end{itemize}}&50.36 $\%$ \\
	\hline
	{WZ} & \begin{itemize}
				\item Sample modelling and statistics 50$\%$ 
	\end{itemize} & 50.36$\%$ \\
	\hline 
	{Non prompt leptons} & \begin{itemize} 
				\item Fake rate estimation 50$\%$
				\item Closure 7$\%$ 
	\end{itemize} 		 & 50.48$\%$ \\
	\hline 
\end{tabular}

\section{Systematic uncertainties}
\begin{itemize}
	\item Luminosity measurement: ~2.6$\%$.
	\item Data/MC scale factors for lepton selection (ID, iso) and trigger efficiencies ~5$\%$ per lepton.
	\item Choice of PDF set:
	\begin{itemize}
		\item 3.7$\%$ for tHq
		\item ~4$\%$ for tHW t$\bar{t}$W, t$\bar{t}$Z, t$\bar{t}$H 
		\item Scale uncertainties: 12$\%$, 4 for t$\bar{t}$W, 10$\%$ for t$\bar{t}$Z, +5.8/-9.2$\%$ for t$\bar{t}$H.
	\end{itemize}
	\item Background: WZ, ZZ sample modelling and statistics: ~50$\%$.
	\item Rare SM (tZ,tri-bosons, WWqq, tttt) : 50$\%$
	\item Fake rate estimation:
	The predicted event yield has a normalization uncertainty of ~30-50$\%$ 
\end{itemize}

Detector-simulation related uncertainty
\begin{itemize}
\item Calibrations (electron, jet energy scale)
\item Efficiencies (particle ID, reconstruction)
\item Resolutions (jet energy, muon momentum)
\end{itemize}
Theoretical uncertainties
\begin{itemize}
\item  Factorization/Normalization scale of MC generators
\item Choice of MC generator (ME and/or PS, e.g. Herwig vs Pythia)
\end{itemize}
Monte Carlo Statistical uncertainties
\begin{itemize}\item Statistical uncertainty of simulated samples 
\end{itemize}

\chapter{ tH process}  %Title of the First Chapter

\section{tH production mechanism}
The production of a single top quark in the t channel, where a Higgs boson can be radiated
either from the top quark or from the exchanged W boson in the two dominant leading order
diagrams  provides a unique opportunity to study the relative sign of the coupling.
Any deviation from the standard model coupling structure, where the two diagrams strongly
interfere negatively and thereby suppress the production cross section, can lead to a large enhancement of the event rate.
\begin{center}
\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{Chapter1/newtHq.png}
\caption{tH mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
\end{figure}
\end{center}

\section{Topology of tH}
\begin{center}
\begin{figure}[!htbp]
\centering
\includegraphics[scale=1.1]{Chapter1/jet.png}\caption{ tH process for $\mu \mu$ final state} \label{jet}
\end{figure}
\end{center}

 For the tH and
ttH processes, the largest contribution comes from Higgs decays to WW (about 75%), followed
by $\tau \tau$ (about 20%) and ZZ (about 5%).

Jets \\
Since quarks and gluons only exist in bound states, we don’t really observe
isolated bare quarks except the top quark, which decays before it has time to form a
bound state. As two quarks are separated, the strong force between them increases
which is equivalent to the potential energy increasing. This energy transforms into
quark-anti-quark pairs. This process of hadronization results in a collimated “jet”
of particles (thesis cms)

\begin{table}
\caption{Table of decay chains for tH.  Expected number of final events assuming 560 produced tH events.l represents $\mu^{\pm},e^- , \tau^\pm$.}
\renewcommand{\arraystretch}{0.55}
\begin{tabular}{|c|c|c|}
\hline
Decay chain & BR & Events\\
\hline 
\small{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} &  1.173  \\
\hline
\small{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
\hline
\small{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
\hline
\small{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105  \\
\hline
\small{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
\small{1.681 $\times$10$^{-4}$} & 0.094 \\
\hline
\small{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
\hline
\small{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
\hline 
\small{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} &  0.008  \\
\hline
\end{tabular}
\end{table}

\end{linenumbers}

### 2019-10-07 tesis_hiram/Chapter2/chapter2.tex
tesis

%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Second Chapter *********************************
%*******************************************************************************

\chapter{The LHC and CMS}

\section{The Large Hadron Collider}
\begin{linenumbers}
The Large Hadron Collider (LHC) is one the  largest and most powerful particle accelerator in the world. It came on operation on 10 September 2008 and it is the most recent addition from the  European Organization for Nuclear Research (CERN).  The LHC is a 27 kilometer ring composed of  superconducting magnets with accelerating structures to boost the energy of the particles. \\

The LHC is designed to accelerate particles to high energies and generate collisions. There are several
experiments installed along the LHC ring. One of them is ATLAS, located on Point 1 between the two injection lines , which is a general purpose detector. At point 5 is another general purpose detector: the compact muon solenoid  (CMS). A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
\\

Inside the accelerator, two high energy particles beams travel at
close to the speed of light before they collide. 
In order to make them collide, beams travel in opposite directions in separate beam pipes, 
two tubes kept at ultrahigh vacuum. 
By using of superconducting electromagnets that generates a powerful magnetic field , the beams are guided around the accelerator ring. 
The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.For that, it is required to have  magnets to a temperature of  $‑271.3$ C. 
To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}

\pagebreak

\begin{figure}[!htbp]
\centering
\includegraphics[width=17cm,height=11cm]{Chapter1/cern.jpg}
\caption{Large hadron collider from CERN} \label{lhc}
\end{figure}

Protons in the LHC start out as hydrogen atoms stripped of their electrons. The first accelerating stage the protons are subjected to is a linear accelerator, Linac2,
which accelerates them up to 50 MeV . The protons are then sent into the
Proton Synchotron Booster which accelerates them up to 1.4 GeV before sending them to the Proton Synchotron (PS). The protons leave the PS at 25 GeV before entering the Super Proton Synchotron (SPS), which accelerates them to the LHC injection energy of 450 GeV. After this stage, the beam is ready to be injected into
the LHC through one of two injection lines with 6.5 TeV.\cite{cern3}

\begin{table}[!htbp]
\centering
	\caption{Accelerator operation energies}
	\begin{tabular}{|c|c|}
		\hline
		Accelerator & Energy \\
		\hline
		Linac 2 &  50 MeV \\
		\hline
		PS Booster & 1.4 GeV \\
		\hline
		Proton Scyncroton (PS) & 25 GeV\\
		\hline
		SPS &  450 GeV\\
		\hline
		LHC & 6.5 TeV\\
		\hline
	\end{tabular}
\end{table}
\pagebreak
Inside the detectors, collided protons generates an amount of particles such as pion and kaons, which are the most commons, created by the jet particles that were created after the collision. Besides of the particles created by the quarks of the proton , gluons are also radiated and create new particles and photons are radiated too. \\
During the collision time, the main  detectors of LHC capture the energy 
and save the data in supercomputers. Those high end computers starts to measure the signals in order to assign a type of events.
\\

The main objetive of the LHC is to study the nature of electroweak symmetry breaking for the Higgs mechanism of the SM. 
Alternatives to the Standard Model that involves different symmetries are also put on test. With the exploration of theses theories, people hope for a discovery that guide them toward a unified theory, so the importance to accelerate particles to higher energy scales.
\\
The LHC has a schedule where there is a period of experiments that last for three or four years. Ending the experimental time, the engineers of the LHC start the maintenance.

\begin{figure}[!htbp]
\centering
\includegraphics[scale=0.5]{Chapter2/lum6.png}
\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods %
\cite{cern3}.}
\label{lhc-lumi}
\end{figure}
From the figure \ref{lhc-lumi}, shows the Large Hadron Collider forecast for the increase of luminosity for the next years. Red dots are peak luminosity expected to reach and blue line is integrated luminosity. In the year 2018, the maximum integrated luminosity is around 150 $fb^{-1}$\cite{cern3}. From 2019 to 2021 the second phase of maintenance, where engineers increase the performance of the accelerator, give maintenance to the system and introduce new components to the complex. After that period, the LHC starts new collision period at even higher energies in order to explore new particle phenomena.

\pagebreak

\section{The Compact Muon Solenoid}	
The Compact Muon Solenoid (CMS) is a detector with multiple uses in the LHC and part of the main experiments at CERN. Located underground in the France- Switzerland border , in the city of Cessy, France.
This detector was designed in the early 1990s, based on the mass limit of the Higgs boson,  and put on operation in 2008,  it has a big solenoid that generates a great magnetic field of 4 teslas with the objective to separate particles after a particle collision.
 The detector is 21 metres long, 15 meters wide, 15 meters high ,it has a diameter of 5.9 m with a weight of 12000 ton. The reason for such a strong magnetic field is to obtain a better momentum resolution .
 The magnetic flux is returned via a 1.5 m thick  iron yoke instrumented with four stations of muon
 chambers.

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/cms2.png}
	\caption{View of Compact muon solenoid (CMS)}\label{cms}
\end{figure}
There are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easy, the complex is buried 100 meters underground.\\

The CMS experiment is composed of several detector layers  that allow identify and save different types of energy signals  and it is saved in a powerful supercomputers that separate and classify the data according to certains variables. The general parts of the CMS are the Silicon Tracker , an Electromagnetic Calorimeter,a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector. \\

\begin{table}[ht]
	\caption{Characteristic of the CMS superconducting solenoid \cite{cms-manual}}
	\centering
	\begin{tabular}{|c|c|}
		\hline
		Field strength & 4 T \\
		Inner Bore & 5.9 m \\
		Length & 12.9 m\\
		Number of Turns & 2168\\
		Current & 19.5 kA\\
		Stored energy & 2.7 GJ\\
		\hline
	\end{tabular}
	\label{tab:my_label}
\end{table}

%The trigger or event selection process must reduce the approximately 1 billion interactions per second to more less than 100 events per second for storage and subsequent analysis.\\

 The objectives of the CMS experiment are numerous. One of them is
identification of muons by measuring the momenta and scattering angle. Muons can be produced in interesting events like Higgs, $W^{\pm}$ and $Z$ boson decays.%Search for evidence  and give proof of super symmetry  for show evidence of BSM (Beyond Standard Model). Detection of massive vector bosons $W^\pm$ and Z via $e^+e^-$ and $\mu^+ \mu^-$ decays.\\
%Search for extra dimensions from BSM theory that could be related to production of particles and quantum gravity. Study of QCD, electroweak and flavor physics to detect new decays predicted by SM at higher energies. Heavy ions collision experiments for the study of production of  very strongly interacting nuclear matter\cite{cms-manual}.
This experiment along the ATLAS experiment discovered the Higgs boson in 2012.
\\

\subsection{Silicon Tracker}
The Silicon Tracker is the first of the main subdetectors of CMS from inside to outside. The Tracker is composed of two sub components: Pixel and  Strip detectors.The outer radius of the  tracker is 110 cm, and its total length is 540 cm. The tracker coverage is $|\eta|<2.4$\footnote{$\eta$ , called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.\\

In the Pixel barrel section, there are 3 layers of pixel sensors with radii of 4.4, 7.3 and 10.2 cm with a length of 53 cm. Each pixel has an area of 100 $\times$ 150 $\mu m^2$.  The barrel section has 768 pixel modules.
%The barrel section of the silicon tracker is divided in inner and outer barrel, where the inner section is shorter than outer barrel along with 3 inner disk between the transition region between barrel and endcap sections because avoids shallow track crossing angles.  
The Pixel endcap has 2 disks on each side placed at 34.6 and 46.5 cm in the z axis. Each disk covers radii from 6 to 15 cm and is divided into 24 blades with 7 modules each blade.
They are assembled in a turbine-like geometry that contains a total of 672 pixel modules. %with 7
%different modules in each blade.
\\

 %The outer radius of the  tracker is 110 cm, and its total length is 540 cm. \\
 %Here, silicon microstrip detectors are placed in the r axis (cylindrical coordinates),  between 20 and 110 cm.
%In the endcap section 2 pixel and microstrip layers are placed in each endcap. The endcap have 2 disks of radii from 6 to 15 cm placed at 34.6 and 46.5 cm in the z axis.The endcap disks comprise 672 pixel modules with 7
%different modules in each blade.
The Strip Detector is divided in 4 sections: Tracker inner barrel (TIB), tracker outer barrel (TOB), tracker encap (TEC) and tracker inner disk (TID). The region that cover the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.The first two are composed  of silicon sensors layers of 4 and 6 layers respectively.  The TEC has 9 disk extending in the region 120 cm > $|z|$ > 280 cm .The 
TID comprises 3 small disks that fill the gap between the TIB and the TEC.

The Strip Detector have almost 15 400 modules, mounted on
carbon-fibre structures and housed inside by a temperature controlled outer support tube. The operating temperature must be around -$\ang{20}$C. 
The total area of the pixel detector is around 1 $m^2$ and the silicon strips is 200 m$^2$. 
The inner tracker comprises 66 million pixels and 9.6
million silicon strips \cite{cms-manual}.
A full coverage of the Tracker is shown in figure \ref{pixel2}
\\

\begin{figure}[ht]
	\centering
	\includegraphics[scale=0.7]{Chapter2/pixel2.png}
	\caption{The Tracker layout distributed in terms of $\eta$.}
	\label{pixel2}
\end{figure}
During the particle collision, it generates a lot of different particles that pass first through the inner tracker, interacting with the sensors layers and registering the particle path.
By reconstructing the path of the particles, it is possible to generate a track, which allows to measure the momentum of the particle by calculating its curvature. The tracker is used to reconstruct the path of charged particles (e.g. electrons, muons, pions). The most important objects of study are the momentum and the vertex (origin of the track). The efficiency of the tracker is estimated by using samples of muons and pions with $p_t$ of 1,10 and 100 GeV. 
For muons the efficiency of the tracker is shown in \ref{efi}
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/tracker.png}
	\caption{Total reconstruction efficiency for muons }\label{efi}
\end{figure}
\\
According to figure \ref{efi}, the efficiency of the tracker is around 98 $\%$ for $|\eta|<2$. The resolution of the tracker  for muons with $p_t$=100 GeV is around 1-2 $\%$.\\
Of course, this is a first stage of the measurement of particle momentum because the other detectors are used to increase and improve the measurement and reconstruction of the particle path.

\subsection{Electromagnetic calorimeter}

The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillanting crystals (emits light when particles interact with the crystal). These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps. The barrel section  of the ECAL covers the range $|\eta| < 1.479$. The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face. The crystal length is 230 mm.The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\

The endcaps cover have the  range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has  identically shaped crystals grouped in
mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$ ,and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/ecal.png}
	\caption{View of the ECAL}\label{ecal}
\end{figure}
In the barrel, there photo detectors called avalanche photo diodes (APD), made of silicon with a active area of  5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.  At the endcap , the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$) , allowing to operate in the magnetic field. VPT have a size of 25 mm in diameter , glued to the back of each crystal.\\

There is also a preshower detector , which principal function  is to identify neutral pions in the
endcaps within the region 1.653 < |$\eta$| < 2.6. It also helps the identification of electrons
against minimum ionizing particles, and improves the position determination of electrons and photons.
\\

As its name says, the ECAL is mainly used for the electron detection, but also detects, photons, and neutral pions. The charged particles reach the crystals that provokes the photo diodes detect energy.\\
The  resolution of the ECAL is estimated by using a test beam and registering the energy signals. The resolution for electrons with energies of 120 GeV, it has obtained a resolution of 0.5$\%$.

 %that a electron is separated, and regrouping in other place due to the electric field generated  by the voltage source. 
 %The ES is a sampling calorimeter with 2 layers: lead
%radiators initiate electromagnetic showers from incoming photons/electrons whilst silicon
%strip sensors placed after each radiator measure the energy deposited and the transverse shower profiles.

\subsection{Hadron calorimeter}
The hadron calorimeter (HCAL) along the ECAL, form a complete calorimeter that allows to measure the jets and missing transverse energy. HCAL is located in the barrel and the endcaps, surrounding the ECAL and affected by the magnetic field generated by the solenoid. The Barrel section (HB) and endcap section (HE)  cover the pseudorapity 0 < $|\eta|$ < 1.3 and  1.3 < $|\eta|$ < 3.0 respectively.\\

The HB is an assembly of two half barrels, composed of 18 wedges.Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel).Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087. Light of scintillator is collected by a single wave
length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm. 
\\

HE is composed by brass absorber plates ,with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.  HE is sectioned in 5 in $\phi$ to match the barrel wedges.
 . %HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is , the geometry of the barrel muon system. Divided by 5 rings of 2.54 wide, composed of the scintillators on either side of the tail catcher iron of 18cm thick at radial distances of 3850 and 4097 mm respectively. \cite{cms-manual} 
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=10cm,height=6cm]{Chapter2/hcal.png}
	\caption{View of the CMS HCAL showing the different layers and tower regions. In the endcap, the towers are defined with two longitudinal segments as shown by the colors}\label{hcal}
\end{figure}
The outer barrel hadron calorimeter (HO) consists of layers of scintillator with  thickness of 10 mm, located outside of the
magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.\\
There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
steel absorbers and embedded radiation hard quartz fibers,which collects 
Cherenkov light\cite{cms-manual}.% that is  when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 
%The length of the fibers are 1.65 m and 1.43 m, which are alterned with a 5 mm of separation. 
\\

The tiles are arranged in a tower pattern in the  $\eta-\phi$ space, projective to the interaction point.  In total there
are 4176 towers. The towers are used as input to several jet reconstruction algorithms.

The HCAL measures the energy of hadrons,such as the pions and kaons. 
The energy resolution of the HCAL was estimated using a test beam of pions. For 100 GeV pions, the resolution obtained is 12$\%$.
 %By using the info given by the HCAL, it is possible reconstruct the track in order to calculate the momentum of the particles.

\subsection{Muon Detector}
%The muon detector system  %has 3 primary functions: muon
%triggering, identification, and momentum measurement\cite{cms7}. 
%The process utilized in the CMS muon chamber systems is gas ionization. Those gas-ionization particle detectors are arranged in a cylindrical barrel region and planar endcaps, in order to meet the geometry of the solenoid.The barrel detector is built with 4 layers of 250 chambers inside the magnet return yoke.\cite{cms-manual}
The Muon Detector has three main subdetectors: the drift tubes chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
The  DT's, CSC's and RPC's are shown in the figure \ref{dt}.
 \\

The DT chambers cover the barrel section $|\eta|<1.2$, composed of rectangular gas filled active cells. Those cells have a transverse size of 42 $\times$ 13 mm$^2$ with a 50 $\mu m$ diameter anode wire at the center that operates at voltages of over 3600 V. The gas used in this cells is a mix of Ar and CO$_2$ with a proportion of 85 $\%$ and 15 $\%$. There are 250 chambers in 4 layers inside the magnet return yoke, with radii of approximately 4.0, 4.9, 5.9 and 7.0 m from the beam axis  and 12 sections covering  30$^\circ$ in $\phi$ each one.
\\
\begin{figure}[!htbp]
	\centering
	\includegraphics[width=11cm,height=7cm]{Chapter2/csc}
	\caption{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$.}
	\label{dt}
\end{figure}

The CSC's are located in the endcap regions 0.9 < $|\eta|$ < 2.4. The CSC's are installed on the face of steel disks perpendicular to the beam. 
Each CSC has a trapezoidal shape and consist of 6 gas gaps between 7 metal plates, where each gap contains  copper cathode strips and anode wires running almost perpendicularly to
the strips, with a diameter of 50 $\mu m$ separated by 3.16 mm.  
%CSC is composed of 6 layers that measures the $\mu$ position in the r-$\phi$ coordinate plane. 
The chambers use a gas mixture of 50$\%$ CO$_2$ , 40 $\%$ Ar and 10$\%$ CF$_4$. The muon endcap system comprises 468 CSCs in the 2 endcaps \cite{cms-manual,cms7}.
%Together with DT, cover the $|\eta|< 2.4$. These systems can each identify the collision crossing that generated the muon and trigger on (recolect) the transverse momentum ($p_T$). 
\\

The RPC are located in the barrel and endcap regions that covers the range o $|\eta|<1.6$. The main purpose is to trigger events with muons. 
RPC's are structured with a double gas filled gap and readout strips between the gaps .\\
 The gas mix used in the RPC consist of 95.2$\%$ Freon
($C_2 H_2 F_4$ ), 4.5$\%$ isobutane ($C_4 H_{10}$), and 0.3$\%$ sulphur hexafluoride (SF$_6$ )\cite{cms7}.\\

 %The vertical lines represent the endcap and the horizontal the muon barrel. The orange sections are the DTs , where the 4 DTs are labeled MB,CSC marked in green are labeled ME or muon endcap and RPC are the blue lines that are located in the barrel and the endcap. RPC are labeled RB and RE respectively.

%The produced muons are measured in three zones: in the inner tracker, after the coil, and in
%the return flux. Measurement the momentum of muons in the muon detector is determined by the muon bending angle at the exit of the 4T coil with the interaction point as the origin of the muon\cite{cms7}\cite{cms-manual}.
%The resolution of the muom detector is based on simulations taking account with the geometry and a test beam. 
The main purpose of the Muon System Detector is to identify muon tracks. 
The efficiency of the muon system is estimated by using single muon samples simulated with $p_t$=10, 50, 100, 500 and 1000 GeV. The results are shown in the figure \ref{mu-efi}.
\begin{figure}
	\centering
	\includegraphics[width=0.4\linewidth]{Chapter2/mu-efi}
	\caption{Muon reconstruction efficiency in terms of $\eta$ and $p_t$ \cite{cms-manual}}
	\label{mu-efi}
\end{figure}
The graph shows an efficiency of approximately 98$\%$ in the the fully instrumented regions. In the intersection regions, there are drops in efficiency  due to the separation of the chambers. % There is a reduction of the efficiency to 6$\%$, which corresponds to the $\eta$  position for the separation.
\end{linenumbers}

### 2019-10-07 tesis_hiram/Chapter3/chapter3 (hiram-pc's conflicted copy 2019-10-01).tex
tesis

%!TEX root = ../thesis.tex
%*******************************************************************************
%****************************** Third Chapter **********************************
%*******************************************************************************
\chapter{Event reconstruction and selection}
During the proton collision, many types of processes happen whose information are saved in the CMS data storage system. But the events are only saved if they fulfill certain conditions compatible with the signal. 
For the tH process , the search is based on the presence of  a pair of muons with the same sign. The rest of the processes that also generates a pair of muons with the same sign will be considered backgrounds.  
\section{Signal Event Topology} 
In this search, top quark decays to $Wb$ and from the $W$ boson decays to a muon and a neutrino. The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino. This is the main process that generates events with two same sign muons.The tH process topology is shown in the figure \ref{jet}.\\

Figure \ref{jet}, also shows a b-jet that comes from the tH process.  Finally there is a forward  quark jet (highest $\eta$ value) generated from the initial collision. Additional jets or leptons can be generated from the other $W$ boson.
\\

  %The W bosons can also decay to quarks that generate jets. 
Due to the small cross section of the $tH$ process, the amount of $tH$ events is low compared to other Higgs production processes. 
Table \ref{tdecay} shows several processes that generate same sign muon events for $t$H. These numbers do not consider the detection efficiency.
  %But also tH process can generate the final states from $\tau$ decays but with a low probability. Some of them have probability near zero , but not impossible . %In graphics, these low probability processes would be very small figures that barely manifest.

%For the tH process, the largest contribution comes from Higgs decays to WW (about 75$\%$), followed
 %y $\tau \tau$ (about 20$\%$) and ZZ (about 5$\%$).

	\begin{figure}[!htbp]
		\centering
		\includegraphics[scale=0.9]{Chapter1/jet.png}
		\caption{Topology of $t$H process which generates two same sign muons , a forward jet and a b-jet.} 
		\label{jet}
	\end{figure}
%Quarks and gluons only exist in bound states. Because of it, we cannot isolate quarks except the top quark because of their decay times that don't form a bound state. When two quarks are separated, the strong force interacting between them increases. The energy transforms into quark anti-quark pairs. The hadronization results in a jet of particles.

\begin{table}[!ht]
	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm , \tau^\pm$.}
	\begin{tabular}{|l|c|c|}
		\hline
		Decay chain & BR & Events\\
		\hline 
		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$  $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} &  1.173  \\
		\hline
		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$  $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
		\hline
		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$  $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105  \\
		\hline
		\small{$tH \rightarrow W^+ b \tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
		\small{1.681 $\times$10$^{-4}$} & 0.094 \\
		\hline
		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
		\hline
		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q}  b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
		\hline 
		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} &  0.008  \\
		\hline
	\end{tabular}
\label{tdecay}
\end{table}

\newpage

\section{Backgrounds}
Several processes contribute to the background in this search:
\begin{itemize}
		\item $\bm{t\bar{t}H}$: This Higgs  production mechanism is considered a background in this analysis. The muons in this cases comes from one top and Higgs decays. 
		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muons comes from a top and the other comes from the vector boson.
		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
		\item $\bm{tZq}$: Processes with single top quarks associated  with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
		\item $\bm{ZZZ}$, $\bm{W^{+}ZZ}$ and $\bm{W^{+}W^{-}Z}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
	\item $\bm{WZ}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
	\item $\bm{Fakes}$:This background refers to events where two muons come from  $b$ meson decays in jets.
\end{itemize}
Table \ref{back} show the decay chains and production cross section for background. 
\begin{table}
	\caption{Main backgrounds and their same sign $\mu\mu$ decay process }
	\centering
	\begin{tabular}{|c|l|}
		\hline
		Background &  Decay process \\
		\hline
		$t\bar{t}H$	& $t\bar{t}H$ $\rightarrow W^+b W^- \bar{b} W^+W^-$ $\rightarrow$ $\mu^+ \nu_\mu b$$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
		\hline  
		$t\bar{t}W$  &$t\bar{t}W$  $\rightarrow$  $W^+ b W^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
		\hline
		$t\bar{t} Z$ & $t\bar{t} Z$  $\rightarrow$ $W^+ b$  $W^-\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$  \\
		\hline 
		$W^\pm$ $W^\pm$  & $W^+W^+$ $\rightarrow$$\mu^+\nu_\mu$$\mu^+ {\nu_\mu}$ \\
		\hline 
		$tZq$  & $tZq$ $\rightarrow$ $W^+$ $ b\mu^+ \mu^- q$ $\rightarrow$$\mu^+ \nu_\mu b$ $\mu^+\mu^- q$ \\
		\hline 
		$t\bar{t}t\bar{t}$  &$t\bar{t}t\bar{t}$ $\rightarrow$ $W^+ b$   $W^- \bar{b}$  $W^+ b$  $W^- \bar{b}$   $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ \\
		\hline 
		$W^+ W^- Z$  &  $W^+ W^-$ $Z \rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
		\hline 
		$ZZZ$  & $ZZZ \rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$  \\
		\hline 
		$W^+ZZ$ &$W^+ZZ$ $\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
		\hline 
		$W^+ Z$ &$W^+ Z \rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
		\hline
		$tZW^+$ & $tZW^+ \rightarrow$ $W^+b \mu^+ \mu^- \mu^+ \nu_\mu \rightarrow \mu^+ \nu_\mu b \mu^+ \mu^- \mu^+ \nu_\mu$\\
		\hline
		$ZZ$ &  $ZZ\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
		\hline
	\end{tabular}
	\label{back}
\end{table} 
Due to small expected event yields, the processes $tZ$,$VVV$, $tzq$,$twz$ ,$W^\pm$ $W^\pm$ , $ZZ$ and $t\bar{t}t\bar{t}$ are grouped as one called Rares in the results below.
%Due to a large cross section, the main
%background contribution comes from WZ production.
\pagebreak

\section{Event Selection}
In order to detect signal events and reject background, the following selections are applied. 
\begin{itemize}
	\item The events must contain two muons with the same sign.
	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
	\item One or more b tagged jets with  $|\eta|$ < 2.4
\end{itemize}
%Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
The number of events that passed the event selection are shown in figure \ref{tth-table} which corresponds to  a integrated luminosity of 35.9 fb$^{-1}$ \cite{th1}.\\

\begin{table}[ht!]
	\centering
\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$}
	\begin{tabular}{|c|c|}
		\hline
		Process  & Number of events  \\
		\hline
			$tH$ & 2.14   \\
		\hline
		$t\bar{t}H$  &  24.18  \\
		\hline
		$t\bar{t}W$  &  68.03  \\
		\hline
		$t\bar{t}Z$  & 25.89 \\
		\hline
		Rares SM & 18.33  \\
		\hline
		$WZ$ & 15.07 \\
		\hline
		fakes  & 80.94 \\
		\hline
	\end{tabular}	
\label{tth-table}
\end{table}
The processes with the most events are $t\bar{t}$ $W^\pm$ and $t\bar{t}Z$. The number of events of Rares SM is the sum of the group of processes mentioned before. %$\kappa_t$ and $\kappa_V$ are coupling parameters. 
\pagebreak
%The fake rate corresponds to  non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks). But due to jet signature is reconstructed as leptons, some particular signatures or errors in reconstruction, passed as leptons and then they called fakes leptons. Rare SM is a group of other processes: t$\bar{t}$t$\bar{t}$,WWW,WWZ,WZZ,WW,$t$Zq. Due to low number of events, they grouped the events as one histogram. 
\section{Boosted Decision Tree}
The Boosted Decision Tree (BDT) is a multivariate method that takes a set of input features and splits input data recursively based on
those features.  The features can be a mix of categorical and continuous data.
\\

Due to small signal to background ratio caused by the cross section of $t$H, a BDT  employed to train a discriminator to separate
tHq signal events from background . The BDT training is performed using several event variables for signal and background. In this case, the training was  based on $t\bar{t}V$, in order to discriminate $tH$, given  $t\bar{t}V$ has a higher number of events respect to $tH$ .\\
The variables used for the BDT were the following:

\begin{itemize}
	\item	$p_t$ of muon with lower momentum
	\item 	Total charge of tight leptons
	\item 	min $\Delta$R (lepton pairs)
	\item 	$\Delta\phi$ between highest $p_t$ lepton pair
	\item 	Number of jets with |$\eta$| < 2.4
	\item	Number of non b-tagged jets with |$\eta$| > 1.0
	\item	Maximum |$\eta$| for jets
	\item	$\Delta\eta$ (most forward light jet, closest lepton)
	\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{itemize}

%Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake

%Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons   fakes are estimated data

### 2019-10-07 tesis_hiram/Chapter3/chapter3.tex
tesis

--- 2019-10-07 tesis_hiram/Chapter3/chapter3 (hiram-pc's conflicted copy 2019-10-01).tex
@@
 
+\pagebreak
+
+\section{Backgrounds}
+Several processes contribute to the background in this search:
+\begin{itemize}
+		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muons comes from a top and the other comes from the vector boson.
+			\item $\bm{W^{+}Z}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
+		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
+		\item $\bm{tZq}$: Processes with single top quarks associated  with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
+	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
+	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
+		\item$\bm{W^{+}W^{-}Z}$, $\bm{ZZZ}$ and $\bm{W^{+}ZZ}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
+	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
+	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
+			\item $\bm{t\bar{t}H}$: This Higgs  production mechanism is considered a background in this analysis. The muons in this cases comes from one top and Higgs decays. 
+	\item $\bm{Fakes}$:This background refers to events where two muons come from  $b$ meson decays in jets.
+\end{itemize}
+Table \ref{back} show the decay chains and production cross section for background.
+Due to small expected event yields, the processes $W^\pm$ $W^\pm$ ,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$   are grouped as one called Rares in the results below.
+
+\pagebreak
+
 \begin{table}[!ht]
@@
 
-\newpage
-
-\section{Backgrounds}
-Several processes contribute to the background in this search:
-\begin{itemize}
-		\item $\bm{t\bar{t}H}$: This Higgs  production mechanism is considered a background in this analysis. The muons in this cases comes from one top and Higgs decays. 
-		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muons comes from a top and the other comes from the vector boson.
-		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
-		\item $\bm{tZq}$: Processes with single top quarks associated  with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
-	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
-	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
-		\item $\bm{ZZZ}$, $\bm{W^{+}ZZ}$ and $\bm{W^{+}W^{-}Z}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
-	\item $\bm{WZ}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
-	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
-	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
-	\item $\bm{Fakes}$:This background refers to events where two muons come from  $b$ meson decays in jets.
-\end{itemize}
-Table \ref{back} show the decay chains and production cross section for background. 
-\begin{table}
+\begin{table}[!ht]
 	\caption{Main backgrounds and their same sign $\mu\mu$ decay process }
@@
 		\hline
-		$t\bar{t}H$	& $t\bar{t}H$ $\rightarrow W^+b W^- \bar{b} W^+W^-$ $\rightarrow$ $\mu^+ \nu_\mu b$$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
-		\hline  
 		$t\bar{t}W$  &$t\bar{t}W$  $\rightarrow$  $W^+ b W^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
@@
 		$t\bar{t} Z$ & $t\bar{t} Z$  $\rightarrow$ $W^+ b$  $W^-\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$  \\
+	    \hline
+        $W^+ Z$ &$W^+ Z \rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
 		\hline 
@@
 		\hline 
-		$W^+ Z$ &$W^+ Z \rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
-		\hline
 		$tZW^+$ & $tZW^+ \rightarrow$ $W^+b \mu^+ \mu^- \mu^+ \nu_\mu \rightarrow \mu^+ \nu_\mu b \mu^+ \mu^- \mu^+ \nu_\mu$\\
@@
 		\hline
+				$t\bar{t}H$	& $t\bar{t}H$ $\rightarrow W^+b W^- \bar{b} W^+W^-$ $\rightarrow$ $\mu^+ \nu_\mu b$$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
+		\hline  
 	\end{tabular}
@@
 \end{table}
-Due to small expected event yields, the processes $tZ$,$VVV$, $tzq$,$twz$ ,$W^\pm$ $W^\pm$ , $ZZ$ and $t\bar{t}t\bar{t}$ are grouped as one called Rares in the results below.
+
 %Due to a large cross section, the main
@@
 	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
-	\item One or more b tagged jets with  $|\eta|$ < 2.4
+	\item One or more b-tagged jets with  $|\eta|$ < 2.4
 \end{itemize}
 %Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
-The number of events that passed the event selection are shown in figure \ref{tth-table} which corresponds to  a integrated luminosity of 35.9 fb$^{-1}$ \cite{th1}.\\
-
+The number of events that passed the event selection are shown in table \ref{tth-table} which corresponds to  a integrated luminosity of 35.9 fb$^{-1}$ \cite{th1}.
+The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes.
+For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling  scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10.
+This event yields  will be used to estimate the signal sensitivity.The yields include statitical uncertanties due to the simulated samples and systematic uncertanties are described below. 
 \begin{table}[ht!]
 	\centering
-\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$}
-	\begin{tabular}{|c|c|}
+\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$. The uncertainties of yields include statistical and systematic}
+	\begin{tabular}{cc}
 	\hline
@@
 		\hline
-			$tH$ & 2.14   \\
+		$t\bar{t}W$  &  68 $\pm$ 10 \\
+		$t\bar{t}Z$  & 25.9 $\pm$ 3.9\\
+		$WZ$ & 15.1$\pm$7.7\\
+		Rares & 20.9 $\pm$   4.9\\
+		Fakes  & 80.9 $\pm$9.4\\
+	   $t\bar{t}H$  &  24.2 $\pm$ 2.1 \\
 		\hline
-		$t\bar{t}H$  &  24.18  \\
-		\hline
-		$t\bar{t}W$  &  68.03  \\
-		\hline
-		$t\bar{t}Z$  & 25.89 \\
-		\hline
-		Rares SM & 18.33  \\
-		\hline
-		$WZ$ & 15.07 \\
-		\hline
-		fakes  & 80.94 \\
-		\hline
+		$tH$ (SM) & 2.14 $\pm$ 0.13\\
+		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
 	\end{tabular}	
@@
 \end{table}
-The processes with the most events are $t\bar{t}$ $W^\pm$ and $t\bar{t}Z$.
-The number of events of Rares SM is the sum of the group of processes mentioned before.
-%$\kappa_t$ and $\kappa_V$ are coupling parameters.
+
+\section{Systematic uncertanties}
+The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections.
+The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region.
+In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria.
+For the Higgs processes $tH$ and $ttH$ , the uncertainty are due to the theoretical parameters used in that simulation.
+%control region: event selection with 3 leptons for compare simulation with real data. yield difference  in that region is 50 .is taken  and for wz is 50
+%selection that allows to isolate a background  respect to other backgrounds, that background allows to compare with real data
+
 \pagebreak
+
 %The fake rate corresponds to  non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks).
@@
 Due to low number of events, they grouped the events as one histogram.
-\section{Boosted Decision Tree}
-The Boosted Decision Tree (BDT) is a multivariate method that takes a set of input features and splits input data recursively based on
-those features.  The features can be a mix of categorical and continuous data.
+\section{Multivariable discriminant}
+Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminat, which separates signal from backgrounds, is necessary to optimize the signal sensitivity.
+The multivariable discriminant is a Boosted Decision Tree (BDT) that takes a set of input features and splits input data recursively based on those features.
+The features can be a mix of categorical and continuous data.
+The BDT training is performed using several event variables.
 \\
 
-Due to small signal to background ratio caused by the cross section of $t$H, a BDT  employed to train a discriminator to separate
-tHq signal events from background .
-The BDT training is performed using several event variables for signal and background.
-In this case, the training was  based on $t\bar{t}V$, in order to discriminate $tH$, given  $t\bar{t}V$ has a higher number of events respect to $tH$ .\\
+In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds.
 The variables used for the BDT were the following:
@@
 \begin{itemize}
+\item Number of jets with pT > 25 GeV, $|\eta|$ < 2.4
+\item Maximum $|\eta|$ of forward jet
+\item Sum of lepton charges
+\item Number of jets with $|\eta|$ > 1.0
+\item $\Delta\eta$ between forward  jet and b-jet with highest $p_t$
+\item $\Delta\eta$ between forward jet and  b-jet with lower $p_t$
+\item $\Delta\eta$ between forward jet and closest muon
+\item $\Delta\phi$ of highest $p_t$ same-sign muon pair
+\item min $\Delta$R (muon pairs)\footnote{$\Delta R =  \sqrt{ \Delta\eta^2  + \Delta\phi^2}$, where $\Delta R$ is the distance in the $\eta \phi$ plane}
 \item $p_t$ of muon with lower momentum
-	\item 	Total charge of tight leptons
-	\item 	min $\Delta$R (lepton pairs)
-	\item 	$\Delta\phi$ between highest $p_t$ lepton pair
-	\item 	Number of jets with |$\eta$| < 2.4
-	\item	Number of non b-tagged jets with |$\eta$| > 1.0
-	\item	Maximum |$\eta$| for jets
-	\item	$\Delta\eta$ (most forward light jet, closest lepton)
-	\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
-	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
 \end{itemize}
-
 %Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake
@@
 %Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons   fakes are estimated data
+
+%bdt trained with fakes is not possible, due no simulation with that process
+
+\begin{figure}[!tbp]
+	\centering
+	\begin{minipage}[b]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{Chapter3/kos.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.45\textwidth}
+		\includegraphics[width=\textwidth]{Chapter3/kos2.png}
+	\end{minipage}
+\caption{Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right)}
+\end{figure}

### 2019-10-07 tesis_hiram/Chapter4/chapter4 (hiram-HP-ProDesk-400-G3-SFF's conflicted copy 2019-10-07).tex
tesis

\chapter{Statistical analysis}
To estimate the sensibility of the $tH$ signal, we define an Asimov dataset. Asimov set is a set such that when one uses it to evaluate the estimators for
all parameters, one obtains the true parameter values. This is made by replacing the ensemble of simulated data sets by a single representative one. 
With this Asimov dataset, a fit was applied by using a statistical model built with the signal and backgrounds. In an numerical algorithm is applied a 	minimization for $-\log{(L)}$, where L is the probability from observing the data for the model. Also it is shown  extrapolations of the data for future predictions.

\section{Likelihood and fit procedure}
Suppose for each event in the signal sample one measures a variable x and constructs a histogram $n = (n1, . . . , nN )$ with those measured values. The expectation value of $n_i$ can be written as
$E[ni] = \mu s_i + b_i$

The likelihood function is the product of Poisson probabilities for all bins
\begin{align}
L(\mu,\theta)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)}
\end{align}

\begin{itemize}
	\item	N=number of bins
	\item	$\mu$=parameter of signal
	\item	s=signal
	\item	b=background
	\item	n=number of events
\end{itemize}

To test a hypothesized value of $\mu$ we consider the profile likelihood ratio
\begin{align}
\lambda(\mu)=\frac{L(\mu,\hat{\hat{\theta}})}{L(\hat{\mu},\hat{\theta})}
\end{align}

\begin{itemize}
	\item Here $\hat{\hat{\theta}} $ in the numerator denotes the value of $\theta$ that maximizes L for the specified $\mu$,
	it is the conditional maximum-likelihood (ML) estimator of $\hat{\theta}$ (and thus is a function of $\mu$).
	The denominator is the maximized (unconditional) likelihood function, i.e., $\hat{\mu}$ and $\hat{\theta}$ are
	their ML estimators 
	\item The presence of the nuisance parameters broadens the profile likelihood as a
	function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
	of information about $\mu$ due to the systematic uncertainties
\end{itemize}

For purposes of establishing an upper limit on the strength parameter $\mu$ , we consider two
closely related test statistics. First, we may define
\begin{align} 
q_{\mu}=  \Big\{    \begin{array}{ll}
-2\ln\lambda(\mu) \qquad \hat{\mu} \leq \mu	\\
0  \qquad \qquad \qquad \hat{\mu}< 0 
\end{array}
\end{align}
The reason for setting $q_\mu = 0$
for $\hat{\mu}>\mu $ is that when setting an upper limit, one would not regard data with $\hat{\mu}>\mu $ as
representing less compatibility with $\mu$ than the data obtained, and therefore this is not taken
as part of the rejection region of the test. From the definition of the test statistic one sees that
higher values of $q_\mu$ represent greater incompatibility between the data and the hypothesized
value of $\mu$.

\begin{table}
	\caption{Prefit and postfit table for each yield.Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.}
\begin{tabular}{ccc}
	\hline
	Process  & Number of events prefit    & Number of events Postfit \\
	\hline
$t\bar{t}W$  &  68 $\pm$ 10 & 68$\pm$8.94385\\
	$t\bar{t}Z$  & 25.9 $\pm$ 3.9 & 25.9$\pm$3.839\\
$WZ$ & 15.1$\pm$7.7 & 15.1$\pm$7.49851\\
Rares & 20.9 $\pm$   4.9& 20.86$\pm$4.80068\\
	Fakes  & 80.9 $\pm$9.4  & 80.9$\pm$9.05762\\
$t\bar{t}H$  &  24.2 $\pm$ 2.1 & 24.2$\pm$2.07614\\
\hline
$tH$ & 2.14 $\pm$ 0.13  & 2.14$\pm$16.3986
\end{tabular}	
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=11cm,height=11cm]{Chapter4/kin.png}
	\caption{Pre-fit signal and background yields for tH process for $k_t$=-1.\\
		In the box below each distribution, the ratio of the observed and predicted event yields is shown}
\end{figure}

\begin{table}
	\centering
	Prefit and postfit table for each yield  for . $k_{t}$ =-1..
	\begin{tabular}{|c|c|c|}
		\hline
		Process  & Number of events prefit    & Number of events Postfit\\
		\hline
		tH & 26.2 & 1.83 $\pm$ 26.63\\
		\hline
		t$\bar{t}$H  & 24.18 $\pm$ 2.26& 24.82 $\pm$ 2.27\\
		\hline
		t$\bar{t}$W  & 68.03  $\pm$ 9.54 & 77.07 $\pm$ 8.99\\
		\hline
		t$\bar{t}$Z  & 25.89  $\pm$  3.20& 26.76 $\pm$ 3.18\\
		\hline
		Rares SM & 17.17  $\pm$ 8.64 & 18.90 $\pm$ 8.37\\
		\hline
		WZ & 16.23  $\pm$ 8.17& 17.54 $\pm$ 8.15\\
		\hline
		Non prompt lepton & 80.94   $\pm$ 40.86& 102.97 $\pm$ 29.51\\
		\hline
	\end{tabular}
\end{table}

\begin{figure}
	\centering
	\includegraphics[width=11cm,height=11cm]{Chapter4/simple.png}
	\caption{Post fit signal and background yields for tH process for $k_t$=-1.
		In the box below each distribution, the ratio of the observed and predicted event yields is shown}
\end{figure}

Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.

\begin{figure}
	\centering
	\includegraphics[width=11cm,height=11cm]{Chapter4/kin-kt-1.png}
	\caption{Pre-fit signal and background yields for tH process for $k_t$=-1.\\
		In the box below each distribution, the ratio of the observed and predicted event yields is shown}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=11cm,height=11cm]{Chapter4/simple-kt-1.png}
	\caption{Post fit signal and background yields for tH process for $k_t$=-1.
		In the box below each distribution, the ratio of the observed and predicted event yields is shown}
\end{figure}

\section{Limit calculation}

\begin{table}[ht!]
	\caption{Estimation of $\mu$ and upper limits  for extrapolations}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Luminosity (fb$^{-1}$)	&$\mu$ &$\mu$ for $k_t=-1$ &$\mu$ upper limit &$\mu$ upper limit for $k_t=-1$ \\
		\hline
		35.9 & 1.00 $\pm$  8.32 & 1.00 $\pm$  0.249&	22.328 & 2.777   \\
		\hline
		150& 1.00 $\pm$  6.44 & 1.00 $\pm$  0.544  &12.619 &0.915 \\
		\hline
		300&1.00 $\pm$  4.83 &1.00 $\pm$  0.407 & 9.427&0.649 \\
		\hline
		3000&1.00 $\pm$  1.54 & 1.00 $\pm$  0.151&	 3.442 & 0.25
		\\
		\hline
	\end{tabular}
\end{table}

\section{title}

### 2019-10-07 tesis_hiram/Chapter4/chapter4.tex
tesis

\chapter{Statistical Analysis}
To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one. The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events. The uncertainty of the signal strength is estimated by applying a  fit to the Asimov dataset, where the model
is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and gaussian constraints for the systematical uncertainties in the model.

\section{Likelihood and fit procedure}
The likelihood function is the product of Poisson probabilities for all bins of the BDT distribution. The likelihood function has the form
\begin{align}
L(\mu,\alpha)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)} \prod_{k=1}^M e^{\frac{-\alpha^2_k}{2}}
\end{align}
where $N$ is the total number of bins, n is the number of events in a bin $j$,  $s_j$ is the number of signal events, $\mu$ is the parameter of signal strength and  $b_j$ is the number of background events.
$b_j$ is the sum of different background processes $k$
\begin{align}
b_j=\sum_k b_j^k(1+\sigma_k \alpha)
\end{align}
$\alpha$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. \\

The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$. The minimization is performed by using the package ROOFIT \cite{roofit}.
%log es usado para evitar valores extremadamente pequenos debido a los productos de los exponenciales
%negativo es para hacer una minimizacion, positivo es maximizacion
\pagebreak

\begin{table}[ht!]
	\centering
	\caption{Postfit for each yield.Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.}
\begin{tabular}{ccc}
	\hline
	Process  & SM    & $k_t=-1$ \\
	\hline
$t\bar{t}W$  &  68$\pm$8.9& 68 $\pm$8.9 \\
	$t\bar{t}Z$  & 25.9$\pm$3.8&25.9$\pm$3.8\\
$WZ$ &  15.1$\pm$7.4& 15.1$\pm$7.4\\
Rares &  20.8$\pm$4.8& 20.8$\pm$4.8 \\
	Fakes  &  80.9$\pm$9.0&  80.9$\pm$8.9 \\
	$t\bar{t}H$  &   24.2$\pm$2.0 &  24.2$\pm$2.0 \\
\hline
$tH$&  2.14$\pm$16.56 &26.22$\pm$13.11 
\end{tabular}
\label{table1}
\end{table}

In the figure \ref{simple} and table \ref{table1} , shows the results of the model fitting using the Asimov data for both models. As mentioned before, the  $k_t=-1$, the number of events for the $tH$ signal is more than ten times, compared to SM. This causes that the fit model have access to more data, and so improve the fit a bit. Due to low $tH$ number of events, the uncertainty after the fit is big, compared to the $k_t=-1$ model, where the uncertainty is around 50$\%$. Because of the model, the values of the backgrounds don't change.
\begin{figure}[!htbp]
	\centering
	\begin{minipage}[b]{0.48\textwidth}
		\includegraphics[width=\textwidth]{Chapter4/simple.png}
	\end{minipage}
	\hfill
	\begin{minipage}[b]{0.48\textwidth}
		\includegraphics[width=\textwidth]{Chapter4/simple-kt-1.png}
	\end{minipage}
	\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
		In the box below each distribution, the ratio of the observed and predicted event yields is shown}
\label{simple}
\end{figure}
In the table \ref{parameters}, shows the $\mu$ and $\alpha$ parameters. For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.After the fit,  $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed, but its uncertainty is also big.
However, in the model $k_t=-1$, the $\alpha$ parameters shows a slightly change, that indicates changes in the backgrounds, but with a great uncertainty. For the $\mu$, it shows the same size, but the uncertainty is estimated to be 50$\%$, corresponding to the results obtained for the events yields.
\begin{table}[ht]
	\centering
	\caption{$\alpha$ and $\mu$ values for 35.9 fb$^{-1}$}
	\begin{tabular}{ccc}
		\hline
		Parameter  & SM &kt\\
		$\mu$   & 1.00 $\pm$  7.74& 1.0 $\pm$  0.5\\
		$alpha_ttw$&  0.00 $\pm$  0.89&  6.32$\times 10^{-09}$ $\pm$  089\\
		$alpha_ttz$ &  0.00 $\pm$  0.98& 1.90$\times 10^{-09}$ $\pm$  0.98\\
		$alpha_wz$   & 0.00 $\pm$  0.97& -5.33$\times 10^{-09}$9 $\pm$  0.97\\
		$alpha_tz$   &0.00 $\pm$  0.95&-7.83$\times 10^{-09}$ $\pm$  0.98 \\
		$alpha_fakes$ &   0.00 $\pm$  0.96&  3.47 $\times 10^{-09}$ $\pm$  0.95\\
		$alpha_tth$ &0.00 $\pm$  0.98& 2.61$\times 10^{-09}$ $\pm$ 0.98\\
	\end{tabular}
\label{parameters}
\end{table}

For the analysis of the likelihood function,  we take likelihood ratio
\begin{align}
	\lambda(\mu,\theta(\mu))=\frac{L(\mu,\hat{\hat{\theta}}(\mu))}{L(\hat{\mu},\hat{\theta}(\mu))}
\end{align}
Where $\hat{\hat{\theta}}(\mu) $ in the numerator denotes the value of $\theta(\mu)$ that maximizes L for the specified $\mu$, that is , the conditional maximum-likelihood (ML) estimator of $\hat{\theta}(\mu)$ 
The denominator represents the  maximized  likelihood function, where $\hat{\mu}$ and $\hat{\theta}$ are
their ML estimators.
The presence of the nuisance parameters broadens the profile likelihood as a
function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
of information about $\mu$ due to the systematic uncertainties

\section{Limit calculation}
Due to the large background, the signal strength for the Asimov data with 35.9 $fb^{-1}$ is consistency with zero.
Therefore, we estimate an upper limit on the signal strenght at 95 $\%$ level of confidence.

For purposes of establishing an upper limit on the strength parameter $\mu$ , we consider two
closely related test statistics. First, we may define
\begin{align}
q_{\mu}=  \Big\{    \begin{array}{ll}
-2\ln\lambda(\mu) \qquad \hat{\mu} \leq \mu	\\
0  \qquad \qquad \qquad \hat{\mu}< 0
\end{array}
\end{align}
The reason for setting $q_\mu = 0$
for $\hat{\mu}>\mu $ is that when setting an upper limit, one would not regard data with $\hat{\mu}>\mu $ as
representing less compatibility with $\mu$ than the data obtained, and therefore this is not taken
as part of the rejection region of the test. From the definition of the test statistic one sees that
higher values of $q_\mu$ represent greater incompatibility between the data and the hypothesized
value of $\mu$.

\begin{table}[ht!]
	\caption{Estimation of $\mu$ and upper limits  for extrapolations}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		Luminosity (fb$^{-1}$)	&$\mu$ &$\mu$ for $k_t=-1$ &$\mu$ upper limit &$\mu$ upper limit for $k_t=-1$ \\
		\hline
		35.9 & 1.00 $\pm$  8.32 & 1.00 $\pm$  0.249&	22.328 & 2.777   \\
		\hline
		150& 1.00 $\pm$  6.44 & 1.00 $\pm$  0.544  &12.619 &0.915 \\
		\hline
		300&1.00 $\pm$  4.83 &1.00 $\pm$  0.407 & 9.427&0.649 \\
		\hline
		3000&1.00 $\pm$  1.54 & 1.00 $\pm$  0.151&	 3.442 & 0.25
		\\
		\hline
	\end{tabular}
\end{table}

### 2019-10-10 fit_2lss_2016/fit_workspace.C
algo

@@ -210,15 +210,15 @@ data1->Draw();
 hs->Draw("same");
 data1->Draw("same");
 data1->SetStats(0);
-data1->SetAxisRange(0,40,"Y");
+//data1->SetAxisRange(0,40,"Y");
 data1->SetTitle("");
 data1->GetYaxis()->SetTitle("Events/bin");
 
 TLegend* legend1 = new TLegend(0.6,0.6,0.89,0.89);
 //legend->SetHeader("Test","C"); // option "C" allows to center the header
 legend1->AddEntry(data1,"Data","lep");
-//legend1->AddEntry(th,"tH (SM)","f");
-legend1->AddEntry(th,"tH (k_{t}=-1)","f");
+legend1->AddEntry(th,"tH (SM)","f");
+//legend1->AddEntry(th,"tH (k_{t}=-1)","f");
 legend1->AddEntry(tth,"t#bar{t}H","f");
 legend1->AddEntry(ttw,"t#bar{t}W","f");
 legend1->AddEntry(ttz,"t#bar{t}Z","f");
@@ -272,8 +272,8 @@ TLine *line = new TLine(-1.0,1,1,1.0);
 line->SetLineColor(kRed);
 line->Draw("same");
 
-//cs->SaveAs("simple.png");
-cs->SaveAs("simple-kt-1.png");
+cs->SaveAs("simple-150.png");
+//cs->SaveAs("simple-kt-1.png");
   //Save to file
   system(Form("mkdir -vp root-files/%s",version.c_str()));
   result->SetName("result");

### 2019-10-10 fit_2lss_2016/limite.C

@@ -1,7 +1,7 @@
 
 /// Limits: number counting experiment with uncertainty on both the background rate and signal efficiency.
 /// The usage of a Confidence Interval Calculator to set a limit on the signal is illustrated
-/// \author Kyle Cranmer
+/// author Kyle Cranmer
 
 #include "RooProfileLL.h"
 #include "RooAbsPdf.h"
@@ -91,12 +91,13 @@ void limite()
    plc.SetTestSize(.05);  //confidence level, it means with  95%  the true value of the signal is within the range determined by this test
    ConfInterval *lrinterval = plc.GetInterval();
 
-////limite defino una region 
+////limite defino una region
 
    // Let's make a plot
    TCanvas *dataCanvas = new TCanvas("dataCanvas");
    LikelihoodIntervalPlot plotInt((LikelihoodInterval *)lrinterval);
-   plotInt.SetTitle("Profile Likelihood Ratio and Posterior for S");
+   plotInt.SetTitle("; #mu ; -2ln#lambda(#mu)");
+//   plotInt.SetTitle("Profile Likelihood Ratio and Posterior for S");
    plotInt.SetNPoints(300);
    plotInt.SetRange(0,60);
    plotInt.SetMaximum(4);
@@ -119,7 +120,7 @@ void limite()
    cout<<"Results:"<<endl;
    //cout<<"lower limit= "<<lowerlimit<<endl;
    cout<<"upper limit= "<<upperlimit<<endl;
-
+dataCanvas->SaveAs("limitsm.png");
 
 
 }

### 2019-10-10 fit_2lss_2016/make_workspace.C

@@ -217,7 +217,7 @@ hat->Draw("same");
 hat->SetStats(0);
 hat->GetYaxis()->SetRangeUser(0,40);
 hat->SetTitle("");
-hat->GetYaxis()->SetTitle("Events/bin");
+hat->GetYaxis()->SetTitle("Events");
 
 hat->GetXaxis()->SetLabelSize(0);
 TGaxis *axis = new TGaxis( -5, 20, -5, 220, 20,220,510,"");
@@ -294,6 +294,7 @@ line->SetLineColor(kBlue);
 /////////////////////////////////
 line->Draw("same");
 cs->SaveAs("kin.png");
+//cs->SaveAs("150fb.png");
 cs->Clear();
 ///////////////////////////////////////////
 TH1F *h = new TH1F("h","",16,-1,1);
@@ -309,7 +310,7 @@ h->GetXaxis()->SetTitle("BDT Discriminant");
 h->GetYaxis()->SetTitle("Events");
 legend->Draw();
 cs->RedrawAxis();
-cs->SaveAs("kos.png");
+//cs->SaveAs("kos.png");
 //cs-<SaveAs("kos2.png");
 
 }

### 2019-10-10 fit_2lss_2016/scanLikelihood.C

@@ -99,7 +99,7 @@ void scanLikelihood(string version, string parName="mu", double range=2, int nrP
   TGraph* graph = new TGraph(nrPoints+1, x_ary, y_ary);
   graph->Draw("alp*");
   graph->GetXaxis()->SetTitle(parName.c_str());
-  graph->GetYaxis()->SetTitle("-2 ln #Lambda");
+  graph->GetYaxis()->SetTitle("-2 ln #lambda(#mu)");
  graph->SetTitle();
  graph->GetXaxis()->SetLimits(0,50);
  graph->GetYaxis()->SetRangeUser(0,10);

### 2019-10-10 tesis_hiram/Chapter4/chapter4.tex
algo

@@
 \end{align}
-where $N$ is the total number of bins, n is the number of events in a bin $j$,  $s_j$ is the number of signal events, $\mu$ is the parameter of signal strength and  $b_j$ is the number of background events.
+where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$,  $s_j$ is the number of signal events, µ is a parameter that modifies the signal strength and  $b_j$ is the number of background events.
 $b_j$ is the sum of different background processes $k$
 \begin{align}
-b_j=\sum_k b_j^k(1+\sigma_k \alpha)
+b_j=\sum_k b_j^k(1+ \alpha_k \sigma_k)
 \end{align}
-$\alpha$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. \\
+$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. \\
 
@@
 %negativo es para hacer una minimizacion, positivo es maximizacion
-\pagebreak
 
@@
 	\centering
-	\caption{Postfit for each yield.Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.}
+	\caption{Postfit  yields for the fit to the Asimov data corresponding to 35.9 /fb. The uncertainty given is the combined statistical plus systematic.}
 \begin{tabular}{ccc}
@@
 \hline
-$tH$&  2.14$\pm$16.56 &26.22$\pm$13.11 
+$tH$&  2.1$\pm$16.5 &26.2$\pm$13.1 
 \end{tabular}
@@
 As mentioned before, the  $k_t=-1$, the number of events for the $tH$ signal is more than ten times, compared to SM.
-This causes that the fit model have access to more data, and so improve the fit a bit.
-Due to low $tH$ number of events, the uncertainty after the fit is big, compared to the $k_t=-1$ model, where the uncertainty is around 50$\%$.
-Because of the model, the values of the backgrounds don't change.
+This improves the sensitivity to the signal.
+Due to the small number of signal events the uncertainty for the SM is large compared to the $k_t$=-1 scenario, where the uncertainty is around 50$\%$.
+In this analysis only the signal is affected by the change $k_t$=1 (SM) $\rightarrow$  $k_t=-1$, therefore the backgrounds remain the same.
 \begin{figure}[!htbp]
@@
 In the table \ref{parameters}, shows the $\mu$ and $\alpha$ parameters.
-For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.After the fit,  $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed, but its uncertainty is also big.
-However, in the model $k_t=-1$, the $\alpha$ parameters shows a slightly change, that indicates changes in the backgrounds, but with a great uncertainty.
-For the $\mu$, it shows the same size, but the uncertainty is estimated to be 50$\%$, corresponding to the results obtained for the events yields.
+For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.After the fit,  $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed.
 \begin{table}[ht]
 	\centering
-	\caption{$\alpha$ and $\mu$ values for 35.9 fb$^{-1}$}
+	\caption{$\alpha$ and $\mu$ values  for the fit to Asimov data corresponding to 35.9 fb$^{-1}$}
 	\begin{tabular}{ccc}
@@
 		$\mu$   & 1.00 $\pm$  7.74& 1.0 $\pm$  0.5\\
-		$alpha_ttw$&  0.00 $\pm$  0.89&  6.32$\times 10^{-09}$ $\pm$  089\\
-		$alpha_ttz$ &  0.00 $\pm$  0.98& 1.90$\times 10^{-09}$ $\pm$  0.98\\
-		$alpha_wz$   & 0.00 $\pm$  0.97& -5.33$\times 10^{-09}$9 $\pm$  0.97\\
-		$alpha_tz$   &0.00 $\pm$  0.95&-7.83$\times 10^{-09}$ $\pm$  0.98 \\
-		$alpha_fakes$ &   0.00 $\pm$  0.96&  3.47 $\times 10^{-09}$ $\pm$  0.95\\
-		$alpha_tth$ &0.00 $\pm$  0.98& 2.61$\times 10^{-09}$ $\pm$ 0.98\\
+		$\alpha_{t\bar{t}W}$&  0.00 $\pm$  0.89&  0.00 $\pm$  089\\
+		$\alpha_{t\bar{t}Z}$ &  0.00 $\pm$  0.98& 0.00 $\pm$  0.98\\
+		$\alpha_{WZ}$   & 0.00 $\pm$  0.97& 0.00 $\pm$  0.97\\
+		$\alpha_{Rares}$   &0.00 $\pm$  0.95&0.00 $\pm$  0.98 \\
+		$\alpha_{Fakes}$ &   0.00 $\pm$  0.96& 0.00 $\pm$  0.95\\
+		$\alpha_{t\bar{t}H}$ &0.00 $\pm$  0.98& 0.00 $\pm$ 0.98\\
 	\end{tabular}
@@
 
-For the analysis of the likelihood function,  we take likelihood ratio
+\section{Limit calculation}
+Due to the large background, the signal strength for the Asimov data with 35.9 $fb^{-1}$ is consistent with zero.
+Therefore, we estimate an upper limit on the signal strength at 95$\%$  confidence level.\\
+
+We can define the likelihood ratio
 \begin{align}
-	\lambda(\mu,\theta(\mu))=\frac{L(\mu,\hat{\hat{\theta}}(\mu))}{L(\hat{\mu},\hat{\theta}(\mu))}
+\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
 \end{align}
-Where $\hat{\hat{\theta}}(\mu) $ in the numerator denotes the value of $\theta(\mu)$ that maximizes L for the specified $\mu$, that is , the conditional maximum-likelihood (ML) estimator of $\hat{\theta}(\mu)$
-The denominator represents the  maximized  likelihood function, where $\hat{\mu}$ and $\hat{\theta}$ are
-their ML estimators.
-The presence of the nuisance parameters broadens the profile likelihood as a
-function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
-of information about $\mu$ due to the systematic uncertainties
+Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
+To determine an upper limit on the strength parameter $\mu$ , we use the following statistical test
+\begin{align}
+q=  -2\ln{\lambda(\mu)} 
+\end{align}
+High values of $q$ represent greater incompatibility between the data and the fit model.
+$q$ is a random variable with a $\chi^2$ distribution \cite{asimov}.
 
-\section{Limit calculation}
-Due to the large background, the signal strength for the Asimov data with 35.9 $fb^{-1}$ is consistency with zero.
-Therefore, we estimate an upper limit on the signal strenght at 95 $\%$ level of confidence.
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[scale=0.5]{Chapter4/chi_squared.png}
+	\caption{Illustration of the $\chi^2$ distribution used for the limit estimation}
+\label{chi}
+\end{figure}
 
-For purposes of establishing an upper limit on the strength parameter $\mu$ , we consider two
-closely related test statistics. First, we may define
-\begin{align}
-q_{\mu}=  \Big\{    \begin{array}{ll}
--2\ln\lambda(\mu) \qquad \hat{\mu} \leq \mu	\\
-0  \qquad \qquad \qquad \hat{\mu}< 0
-\end{array}
-\end{align}
-The reason for setting $q_\mu = 0$
-for $\hat{\mu}>\mu $ is that when setting an upper limit, one would not regard data with $\hat{\mu}>\mu $ as
-representing less compatibility with $\mu$ than the data obtained, and therefore this is not taken
-as part of the rejection region of the test. From the definition of the test statistic one sees that
-higher values of $q_\mu$ represent greater incompatibility between the data and the hypothesized
-value of $\mu$.
+In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$  such that $q$ remains below the shaded region shown in \ref{chi}, where $\alpha$=0.05 in this case. 
+It is useful to scan $q$ as function of $\mu$ , which is normally a parabolic function as shown in \ref{scanl}.In the SM case, the scan has a wider shape in comparison to the $k_t$=-1.
+This is due to larger statistical uncertainty on the $\mu$ parameter.
+\\
+
+Using the above technique, we find an expected upper limit $\mu < $17.008 for SM model and $\mu < $ 2.378 for $k_t$=-1 model.
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
+	\end{minipage}
+	\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right)}
+	\label{scanl}
+\end{figure}
+
+\section{Extrapolation for higher luminosities}
 
 \begin{table}[ht!]
-	\caption{Estimation of $\mu$ and upper limits  for extrapolations}
+	\caption{Estimation of $\mu$ and upper limits for Asimov extrapolations}
 	\begin{tabular}{|c|c|c|c|c|}

### 2019-10-11 fit_2lss_2016/fit_workspace.C
nuevo

@@ -1,4 +1,4 @@
-#include "RooWorkspace.h"
+  #include "RooWorkspace.h"
 #include "RooStats/ModelConfig.h"
 #include "RooRealVar.h"
 #include "RooMinimizerFcn.h"
@@ -210,15 +210,15 @@ data1->Draw();
 hs->Draw("same");
 data1->Draw("same");
 data1->SetStats(0);
-//data1->SetAxisRange(0,40,"Y");
+//  data1->SetAxisRange(0,40,"Y");
 data1->SetTitle("");
-data1->GetYaxis()->SetTitle("Events/bin");
+data1->GetYaxis()->SetTitle("Events");
 
 TLegend* legend1 = new TLegend(0.6,0.6,0.89,0.89);
 //legend->SetHeader("Test","C"); // option "C" allows to center the header
 legend1->AddEntry(data1,"Data","lep");
-legend1->AddEntry(th,"tH (SM)","f");
-//legend1->AddEntry(th,"tH (k_{t}=-1)","f");
+//legend1->AddEntry(th,"tH (SM)","f");
+legend1->AddEntry(th,"tH (k_{t}=-1)","f");
 legend1->AddEntry(tth,"t#bar{t}H","f");
 legend1->AddEntry(ttw,"t#bar{t}W","f");
 legend1->AddEntry(ttz,"t#bar{t}Z","f");
@@ -272,8 +272,8 @@ TLine *line = new TLine(-1.0,1,1,1.0);
 line->SetLineColor(kRed);
 line->Draw("same");
 
-cs->SaveAs("simple-150.png");
-//cs->SaveAs("simple-kt-1.png");
+//cs->SaveAs("simple-3000.png");
+cs->SaveAs("simple-3000-kt-1.png");
   //Save to file
   system(Form("mkdir -vp root-files/%s",version.c_str()));
   result->SetName("result");

### 2019-10-11 fit_2lss_2016/limite.C

@@ -96,7 +96,7 @@ void limite()
    // Let's make a plot
    TCanvas *dataCanvas = new TCanvas("dataCanvas");
    LikelihoodIntervalPlot plotInt((LikelihoodInterval *)lrinterval);
-   plotInt.SetTitle("; #mu ; -2ln#lambda(#mu)");
+   plotInt.SetTitle("; #mu ; -2ln#lambda(#mu) ");
 //   plotInt.SetTitle("Profile Likelihood Ratio and Posterior for S");
    plotInt.SetNPoints(300);
    plotInt.SetRange(0,60);

### 2019-10-11 fit_2lss_2016/make_workspace.C

@@ -55,24 +55,23 @@ zz->Scale(1.16/zz->Integral()); //zz
 thq->Scale(18.5/thq->Integral());//thq
 thw->Scale(7.72/thw->Integral());//thw
 
-
 ////////////////////////////////////////////
 //for higher luminosities
 //////////////////////////////////
-//tzq->Scale(150.0/35.9); //tzq
-//vvv->Scale(150/35.9); //vvv
-//ww->Scale(150/35.9); //wwss
-//tttt->Scale(150/35.9); // tttt
-//fakes->Scale(150/35.9); //non prompt
-//wz->Scale(150/35.9); //WZ
-//ttz->Scale(150/35.9);//ttZ
-//ttw->Scale(150/35.9);//ttW
-//tth->Scale(150/35.9);//tth
-//thq->Scale(150/35.9);//thq
-//thw->Scale(150/35.9);//thw
-//tzw->Scale(150/35.9);//tzw
-//zz->Scale(150/35.9); //zz
-//ww2->Scale(150/35.9);//wwdps
+tzq->Scale(3000.0/35.9); //tzq
+vvv->Scale(3000/35.9); //vvv
+ww->Scale(3000/35.9); //wwss
+tttt->Scale(3000/35.9); // tttt
+fakes->Scale(3000/35.9); //non prompt
+wz->Scale(3000/35.9); //WZ
+ttz->Scale(3000/35.9);//ttZ
+ttw->Scale(3000/35.9);//ttW
+tth->Scale(3000/35.9);//tth
+thq->Scale(3000/35.9);//thq
+thw->Scale(3000/35.9);//thw
+tzw->Scale(3000/35.9);//tzw
+zz->Scale(3000/35.9); //zz
+ww2->Scale(3000/35.9);//wwdps
 
 
 TH1F *th=(TH1F*)thq->Clone("th");
@@ -127,7 +126,7 @@ normS.SetVal(1); // nominal value
 RooStats::HistFactory::Channel SR("SR");
 SR.SetData(hat);
 
-//add the signal and background samples
+//add the signal and background samples300
 RooStats::HistFactory::Sample sample_th("th"); //signal thq
 sample_th.SetHisto(th);
 sample_th.AddNormFactor(normS);
@@ -293,8 +292,8 @@ TLine *line = new TLine(-1.0,1,1,1.0);
 line->SetLineColor(kBlue);
 /////////////////////////////////
 line->Draw("same");
[…]

### 2019-10-11 fit_2lss_2016/scanLikelihood.C

@@ -146,7 +146,7 @@ hoto->GetYaxis()->SetRangeUser(0,1.1);
 fa2->DrawIntegral("same");
 
 
-TF1 *fa3 = new TF1("fa3","((1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.))/1.8",0,10);
+TF1 *fa3 = new TF1("fa3","((1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.))",0,10);
 fa3->SetLineColor(kBlue);
 fa3->Draw("same");
 ///////////////////////////////////////////
@@ -192,11 +192,8 @@ axis5->SetLabelSize(0.04);
 axis5->SetTitle("P_{#mu}");
 axis5->Draw();
 
-TGaxis *axis6 = new TGaxis(0,1.1,10.9,1.1,0,10.9,510,"-L");
-//axis5->SetLabelFont(0.5); // Absolute font size in pixel (precision 3)
-axis6->SetLabelSize(0.04);
-axis6->SetTitle("f(t_{#mu}|#mu)");
-axis6->Draw();
+
+cout<<fa3->Integral(0,4)<<endl;
 
 tm1->SaveAs("nos.png");
 

### 2019-10-11 tesis_hiram/Chapter4/chapter4.tex
nuevo

@@
 \chapter{Statistical Analysis}
+\begin{linenumbers}
 To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
@@
 \end{align}
-$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background. \\
+$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background.
+$\sigma_k$ for signal and backgrounds are shown in the table \ref{tth-table} \\
 
@@
 	\centering
-	\caption{$\alpha$ and $\mu$ values  for the fit to Asimov data corresponding to 35.9 fb$^{-1}$}
+	\caption{$\alpha$ and $\mu$ values  for the fit to Asimov data corresponding to 35.9 fb $^{-1}$}
 	\begin{tabular}{ccc}
@@
 		Parameter  & SM &kt\\
+		\hline
 		$\mu$   & 1.00 $\pm$  7.74& 1.0 $\pm$  0.5\\
@@
 This is due to larger statistical uncertainty on the $\mu$ parameter.
-\\
-
-Using the above technique, we find an expected upper limit $\mu < $17.008 for SM model and $\mu < $ 2.378 for $k_t$=-1 model.
+Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model.
 
@@
 	\end{minipage}
-	\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right)}
+	\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
 	\label{scanl}
@@
 
+%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
 \section{Extrapolation for higher luminosities}
+In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9fb $^{-1}$ is not significant.
+The LHC has already collected data for integrated luminosity of 150fb $^{-1}$ for run 2 finished in 2018.
+Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb .
+Therefore, is interesting to study the sensibility of the signal strength and backgrounds to higher luminosities.
+An extrapolation (scale) is applied to the Asimov data, where it generates new Asimov data that after it is applied an fit and a likelihood scan.
+For a integrated luminosity of 150$fb^{-1}$, 300$fb^{-1}$ and 3000$fb^{-1}$ in the SM model, the results are the following
+\pagebreak
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/150fb/simple-150.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/150fb/Likelihood.png}
+	\end{minipage}
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/300fb/simple-300.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/300fb/Likelihood.png}
+	\end{minipage}
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/3000fb/simple-3000.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/3000fb/Likelihood.png}
+	\end{minipage}
+	\caption{Fit and likelihood scan for 150 $fb^{-1}$, 300 $fb^{-1}$ and 3000 $fb^{-1}$ in SM model.}
+	\label{hm}
+\end{figure}
+\pagebreak
+
+In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities.
+As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1.
+But even with the increase of number of events, the ratio of signal and data is still very small, with a slightly increase in the ratio in the 3000 fb $^{-1}$ case.
+In the likelihood scan for higher luminosities, as the luminosity increases, the signal strength $\mu$ value starts to decrease and so its uncertainty.
+This is caused by the increased events available for the fit.
+\\
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/simple-150-kt-1.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/Likelihood.png}
+	\end{minipage}
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/simple-300-kt-1.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/Likelihood.png}
+	\end{minipage}
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/simple-3000-kt-1.png}
+	\end{minipage}
+	\hfill
+	\begin{minipage}[b]{0.48\textwidth}
+		\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/Likelihood.png}
+	\end{minipage}
+	\caption{Fit and likelihood scan for 150fb $^{-1}$, 300fb $^{-1}$ and 3000fb $^{-1}$ in SM model.}
+	\label{hm1}
+\end{figure}
+The same method is used for the model $k_t$=-1 in the figure \ref{hm1}.
+In this case, the number of events for the signal is more appreciable in comparison with the SM model, same as the 35.9fb $^{-1}$ case.
+However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case.
+For the 3000 fb $^{-1}$ case, the curve closes in $\mu \approx $2.
+Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the table \ref{upper}
 
 \begin{table}[ht!]
-	\caption{Estimation of $\mu$ and upper limits for Asimov extrapolations}
+	\caption{Estimation of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
 	\begin{tabular}{|c|c|c|c|c|}
 		\hline
-		Luminosity (fb$^{-1}$)	&$\mu$ &$\mu$ for $k_t=-1$ &$\mu$ upper limit &$\mu$ upper limit for $k_t=-1$ \\
+		Luminosity (fb $^{-1}$)	&$\mu$ &$\mu$ upper limit    &   $\mu$ for $k_t=-1$ &$\mu$ upper limit for $k_t=-1$ \\
 		\hline
-		35.9 & 1.00 $\pm$  8.32 & 1.00 $\pm$  0.249&	22.328 & 2.777   \\
+		35.9 & 1.00 $\pm$  7.7 &  17.0  & 1.0 $\pm$  0.5 & 2.3  \\
 		\hline
-		150& 1.00 $\pm$  6.44 & 1.00 $\pm$  0.544  &12.619 &0.915 \\
+		150& 1.00 $\pm$  6.7& 10.7  &  1.0 $\pm$  0.4 &1.8\\
 		\hline
-		300&1.00 $\pm$  4.83 &1.00 $\pm$  0.407 & 9.427&0.649 \\
+		300&1.00 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
 		\hline
-		3000&1.00 $\pm$  1.54 & 1.00 $\pm$  0.151&	 3.442 & 0.25
-		\\
+		3000&1.00 $\pm$  1.75 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
 		\hline
 	\end{tabular}
+\label{upper}
 \end{table}
+
+The table shows the upper limits of $\mu$ for both models and different luminosities.
+For the SM case, the uncertainties in $\mu$ are greater than the $k_t$=-1 case.
+The increase of luminosity reduces the uncertainty of $\mu$ that is visualized in the likelihood graphs.
+The upper limits reduces as the luminosity increases; from 150 to 3000 fb $^{-1}$, the upper limit reduces in $\Delta\mu$=12.7 with $\Delta\mu$ the change of $\mu$ .
+However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$ and increase the signal data ratio .
+\\
+\\
+In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data.
+Changing upper limit values are less notorious than SM case; the value decreases in around $\Delta \mu$=1.2.
+This is caused by the fact that the uncertainty of $k_t$=-1 model has a lower uncertainty than the SM model and the number of events for the $tH$ signal is greater.
+\end{linenumbers}

### 2019-10-14 tesis_hiram/Chapter4/chapter4.tex
algo

@@
 	\begin{align}
-b_j=\sum_k b_j^k(1+ \alpha_k \sigma_k)
+		b_j=\sum_k^M b_j^k(1+ \alpha_k \sigma_k)
 	\end{align}
 	$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background.
-$\sigma_k$ for signal and backgrounds are shown in the table \ref{tth-table} \\
-
-The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$. The minimization is performed by using the package ROOFIT \cite{roofit}.
+$\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.
+	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
+The minimization is performed by using the package ROOFIT \cite{roofit}.
+In the figure \ref{simple} and Table \ref{table1} , shows the results of the model fitting using the Asimov data for both models.
+\\
 	%log es usado para evitar valores extremadamente pequenos debido a los productos de los exponenciales
 	%negativo es para hacer una minimizacion, positivo es maximizacion
+	As mentioned before, for the $k_t$=-1 the number of events for signal is more than ten times compared to SM.
+This improves the sensitivity to the signal.
+Due to the small number of signal events the uncertainty for the SM is large compared to the $k_t$=-1 scenario, where the uncertainty is around 50$\%$.
+In this analysis only the signal is affected by the change $k_t$=1 (SM) $\rightarrow$  $k_t=-1$, therefore the backgrounds remain the same.
+
+	In the Table \ref{parameters}, shows the $\mu$ and $\alpha$ parameters.
+For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.
+After the fit, $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed.
+	\pagebreak
 
@@
 			\hline
-	Process  & SM    & $k_t=-1$ \\
+			Process  & SM    & $k_{t}$=-1 \\
 			\hline
@@
 
-In the figure \ref{simple} and table \ref{table1} , shows the results of the model fitting using the Asimov data for both models.
-As mentioned before, the  $k_t=-1$, the number of events for the $tH$ signal is more than ten times, compared to SM.
-This improves the sensitivity to the signal.
-Due to the small number of signal events the uncertainty for the SM is large compared to the $k_t$=-1 scenario, where the uncertainty is around 50$\%$.
-In this analysis only the signal is affected by the change $k_t$=1 (SM) $\rightarrow$  $k_t=-1$, therefore the backgrounds remain the same.
 	\begin{figure}[!htbp]
@@
 		\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
-		In the box below each distribution, the ratio of the observed and predicted event yields is shown}
+			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
+		}
 		\label{simple}
 	\end{figure}
-In the table \ref{parameters}, shows the $\mu$ and $\alpha$ parameters.
-For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.After the fit,  $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed.
-\begin{table}[ht]
+
+	\begin{table}[ht!]
+		\small
 		\centering
@@
 			\hline
-		Parameter  & SM &kt\\
+			Parameter  & SM &$k_t$=-1\\
 			\hline
@@
 
+	\pagebreak
 	\section{Limit calculation}
@@
 	\begin{align}
-q=  -2\ln{\lambda(\mu)} 
+		q(\mu,\alpha)= -2\ln{\lambda} 
 	\end{align}
@@
 	$q$ is a random variable with a $\chi^2$ distribution \cite{asimov}.
+	In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$  such that $q$ remains below the shaded region shown in Fig. \ref{chi}, where $\alpha$=0.05 in this case. 
+	It is useful to scan $q$ as function of $\mu$ , which is normally a parabolic function as shown in \ref{scanl}.
+In the SM case, the scan has a wider shape in comparison to the $k_t$=-1.
+This is due to larger statistical uncertainty on the $\mu$ parameter.
+	Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model.
 
@@
 		\includegraphics[scale=0.5]{Chapter4/chi_squared.png}
-	\caption{Illustration of the $\chi^2$ distribution used for the limit estimation}
+		\caption{Illustration of the $\chi^2$  distribution with number of degrees of freedom of 7 used for the limit estimation}
 		\label{chi}
 	\end{figure}
-
-In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$  such that $q$ remains below the shaded region shown in \ref{chi}, where $\alpha$=0.05 in this case. 
-It is useful to scan $q$ as function of $\mu$ , which is normally a parabolic function as shown in \ref{scanl}.In the SM case, the scan has a wider shape in comparison to the $k_t$=-1.
-This is due to larger statistical uncertainty on the $\mu$ parameter.
-Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model.
 
@@
 Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb .
-Therefore, is interesting to study the sensibility of the signal strength and backgrounds to higher luminosities.
-An extrapolation (scale) is applied to the Asimov data, where it generates new Asimov data that after it is applied an fit and a likelihood scan.
-For a integrated luminosity of 150$fb^{-1}$, 300$fb^{-1}$ and 3000$fb^{-1}$ in the SM model, the results are the following
+Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities.
+	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
+For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same
 	\pagebreak
@@
 		\end{minipage}
-	\caption{Fit and likelihood scan for 150 $fb^{-1}$, 300 $fb^{-1}$ and 3000 $fb^{-1}$ in SM model.}
+		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in SM model.}
 		\label{hm}
@@
 But even with the increase of number of events, the ratio of signal and data is still very small, with a slightly increase in the ratio in the 3000 fb $^{-1}$ case.
-In the likelihood scan for higher luminosities, as the luminosity increases, the signal strength $\mu$ value starts to decrease and so its uncertainty.
+In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
 This is caused by the increased events available for the fit.
@@
 		\end{minipage}
-	\caption{Fit and likelihood scan for 150fb $^{-1}$, 300fb $^{-1}$ and 3000fb $^{-1}$ in SM model.}
+		\caption{Fit and likelihood scan for 150fb $^{-1}$, 300fb $^{-1}$ and 3000fb $^{-1}$ in $k_t$=-1 model.}
 		\label{hm1}
@@
 For the 3000 fb $^{-1}$ case, the curve closes in $\mu \approx $2.
-Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the table \ref{upper}
+	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}
 
 	\begin{table}[ht!]
-	\caption{Estimation of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
+		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
 		\begin{tabular}{|c|c|c|c|c|}
 			\hline
-		Luminosity (fb $^{-1}$)	&$\mu$ &$\mu$ upper limit    &   $\mu$ for $k_t=-1$ &$\mu$ upper limit for $k_t=-1$ \\
+			Luminosity (fb $^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
 			\hline
-		35.9 & 1.00 $\pm$  7.7 &  17.0  & 1.0 $\pm$  0.5 & 2.3  \\
+			35.9 & 1.00 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
 			\hline
@@
 			\hline
-		3000&1.00 $\pm$  1.75 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
+			3000&1.00 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
 			\hline
@@
 
-The table shows the upper limits of $\mu$ for both models and different luminosities.
+	%The Table shows the upper limits of $\mu$ for both models and different luminosities.
 For the SM case, the uncertainties in $\mu$ are greater than the $k_t$=-1 case.
 The increase of luminosity reduces the uncertainty of $\mu$ that is visualized in the likelihood graphs.
-The upper limits reduces as the luminosity increases; from 150 to 3000 fb $^{-1}$, the upper limit reduces in $\Delta\mu$=12.7 with $\Delta\mu$ the change of $\mu$ .
+	%The upper limits reduces as the luminosity increases; from 150 to 3000 fb $^{-1}$, the upper limit reduces in $\Delta\mu$=12.7 with $\Delta\mu$ the change of $\mu$ .
+
 	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$ and increase the signal data ratio .
-\\
-\\
 	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data.
-Changing upper limit values are less notorious than SM case; the value decreases in around $\Delta \mu$=1.2.
 This is caused by the fact that the uncertainty of $k_t$=-1 model has a lower uncertainty than the SM model and the number of events for the $tH$ signal is greater.
+For 3000 fb$^{-1}$ the uncertainty on mu is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.
+
 \end{linenumbers}

### 2019-10-14 tesis_hiram/Chapter5/chapter5.tex
algo

\chapter{Conclusion and outlook}

\chapter{Conclusion and outlook}
In this work, we explored the $tH$ processes and its different decay rates, including the Higgs mechanism that generate the bosons involved in theses processes. 
The $tH$ process is one of the processes that comes from the proton-proton collisions inside the accelerators. But due to the maintenance schedule of the LHC, many researchers uses Monte Carlo simulation and real data or even only MC for analyze the results and create predictions. In our case, by using MC simulations with an Asimov data, it was obtained a fit for the Asimov data with a model of signal and background events with systematic uncertainties according to the decay of processes to a pair of same sign muons $\mu$. \\

In the results for SM case, we got for the actual luminosities that the signal strength for the signal $tH$ is very low and that generates a signal-data ratio very small in comparison to the backgrounds, generating great uncertainties. For that, it was used extrapolations of the model by increasing the luminosity according to the LHC schedule, and discovered that by increasing the number of events, the signal uncertainties was decreasing, and improving the fit. In the likelihood scans in higher luminosities, the curves were closing, indicating that the model and the data incompatibility was decreasing in lower values of $\mu$. 
\\

However, for the $k_t$=-1, the uncertainty for the model after the fit was less than the SM case, so by increasing the luminosity the compatibility of model and the data was decreasing for higher luminosities, given that the $\mu$ in the likelihood scan w

All the research made in the CMS at CERN has let us discover the nature of the matter and try to answer questions about the origin of the universe, including the origin of the mass of the things. \\

### 2019-10-14 fit_2lss_2016/fit_workspace.C

@@ -217,8 +217,8 @@ data1->GetYaxis()->SetTitle("Events");
 TLegend* legend1 = new TLegend(0.6,0.6,0.89,0.89);
 //legend->SetHeader("Test","C"); // option "C" allows to center the header
 legend1->AddEntry(data1,"Data","lep");
-//legend1->AddEntry(th,"tH (SM)","f");
-legend1->AddEntry(th,"tH (k_{t}=-1)","f");
+legend1->AddEntry(th,"tH (SM)","f");
+//legend1->AddEntry(th,"tH (k_{t}=-1)","f");
 legend1->AddEntry(tth,"t#bar{t}H","f");
 legend1->AddEntry(ttw,"t#bar{t}W","f");
 legend1->AddEntry(ttz,"t#bar{t}Z","f");
@@ -272,8 +272,8 @@ TLine *line = new TLine(-1.0,1,1,1.0);
 line->SetLineColor(kRed);
 line->Draw("same");
 
-//cs->SaveAs("simple-3000.png");
-cs->SaveAs("simple-3000-kt-1.png");
+cs->SaveAs("simple-3000.png");
+//cs->SaveAs("simple-3000-kt-1.png");
   //Save to file
   system(Form("mkdir -vp root-files/%s",version.c_str()));
   result->SetName("result");

### 2019-10-14 fit_2lss_2016/make_workspace.C

@@ -48,12 +48,12 @@ zz->Scale(1.16/zz->Integral()); //zz
 //////////////////////////////////////////////
 //for sm
 /////////////////////////////////////////////
-//thq->Scale(1.43/thq->Integral());//thq
-//thw->Scale(0.71/thw->Integral());//thw
+thq->Scale(1.43/thq->Integral());//thq
+thw->Scale(0.71/thw->Integral());//thw
 
 //for kt=-1
-thq->Scale(18.5/thq->Integral());//thq
-thw->Scale(7.72/thw->Integral());//thw
+//thq->Scale(18.5/thq->Integral());//thq
+//thw->Scale(7.72/thw->Integral());//thw
 
 ////////////////////////////////////////////
 //for higher luminosities

### 2019-10-15 tesis_hiram/Chapter4/chapter4.tex
algo

@@
 	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
-For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same
+For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same.
+	\\
+
+	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities.
+As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1.
+But even with the increase of number of events, the ratio of signal and data is still very small.
+In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
+This is caused by the increased events available for the fit.
 	\pagebreak
@@
 	\pagebreak
-
-	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities.
-As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1.
-But even with the increase of number of events, the ratio of signal and data is still very small, with a slightly increase in the ratio in the 3000 fb $^{-1}$ case.
-In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
-This is caused by the increased events available for the fit.
-\\
 
@@
 			\hline
-			35.9 & 1.00 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
+			35.9 & 1.0 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
 			\hline
-			150& 1.00 $\pm$  6.7& 10.7  &  1.0 $\pm$  0.4 &1.8\\
+			150& 1.0 $\pm$  6.7& 11  &  1.0 $\pm$  0.4 &1.8\\
 			\hline
-			300&1.00 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
+			300&1.0 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
 			\hline
-			3000&1.00 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
+			3000&1.0 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
 			\hline
@@
 
-	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$ and increase the signal data ratio .
+	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$.
 	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data.

### 2019-10-15 tesis_hiram/Chapter3/chapter3.tex
algo

@@
 For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling  scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10.
-This event yields  will be used to estimate the signal sensitivity.The yields include statitical uncertanties due to the simulated samples and systematic uncertanties are described below. 
+This event yields  will be used to estimate the signal sensitivity.
+The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertanties are described below.
 \begin{table}[ht!]

### 2019-10-15 tesis_hiram/Chapter4/chapter4.tex
algo

@@
 
+		\begin{figure}[!htbp]
+		\centering
+		\begin{minipage}[b]{0.48\textwidth}
+			\includegraphics[width=\textwidth]{Chapter4/simple.png}
+		\end{minipage}
+		\hfill
+		\begin{minipage}[b]{0.48\textwidth}
+			\includegraphics[width=\textwidth]{Chapter4/simple-kt-1.png}
+		\end{minipage}
+		\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
+			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
+		}
+		\label{simple}
+	\end{figure}
+
 	\begin{table}[ht!]
 		\centering
-		\caption{Postfit  yields for the fit to the Asimov data corresponding to 35.9 /fb. The uncertainty given is the combined statistical plus systematic.}
+		\caption{Postfit  yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
 		\begin{tabular}{ccc}
@@
 	\end{table}
-
-	\begin{figure}[!htbp]
-		\centering
-		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/simple.png}
-		\end{minipage}
-		\hfill
-		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/simple-kt-1.png}
-		\end{minipage}
-		\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
-			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
-		}
-		\label{simple}
-	\end{figure}
 
@@
 	\section{Limit calculation}
-	Due to the large background, the signal strength for the Asimov data with 35.9 $fb^{-1}$ is consistent with zero.
+	Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
 	Therefore, we estimate an upper limit on the signal strength at 95$\%$  confidence level.\\
@@
 
+	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
+	\section{Extrapolation for higher luminosities}
+	In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9 fb$^{-1}$ is not significant.
+The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 finished in 2018.
+Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb .
+Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities.
+	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
+For this analysis we assume the systematic uncertainties assigned to the background are the same.
+	\\
+
+	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities.
+As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1.
+But even with the increase of number of events, the statistical uncertainty of the data is too large with respect to the expected signal.
+In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
+This is caused by the increased events available for the fit.
+\\
+
+	The same method is used for the model $k_t$=-1 in the figure \ref{hm1}.
+In this case, the number of events for the signal is more appreciable in comparison with the SM model.
+However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case.
+	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}\\
+
+	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 170$\%$ in the 3000 fb$^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results to reduce the uncertainty on $\mu$ for a possible observation of the signal.
+	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small.
+This is caused by the fact that the number of events for the $tH$ signal is greater.
+For 3000 fb$^{-1}$ the uncertainty on $\mu$ is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.
+
+	\begin{table}[ht!]
+		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
+		\begin{tabular}{|c|c|c|c|c|}
+			\hline
+			Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
+			\hline
+			35.9 & 1.0 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
+			\hline
+			150& 1.0 $\pm$  6.7& 11  &  1.0 $\pm$  0.4 &1.8\\
+			\hline
+			300&1.0 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
+			\hline
+			3000&1.0 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
+			\hline
+		\end{tabular}
+		\label{upper}
+	\end{table}
+
+	\pagebreak
+
 		\begin{figure}[ht!]
 		\centering
-		\includegraphics[scale=0.5]{Chapter4/chi_squared.png}
+		\includegraphics[scale=0.65]{Chapter4/chi_squared.png}
 		\caption{Illustration of the $\chi^2$  distribution with number of degrees of freedom of 7 used for the limit estimation}
@@
 		\centering
-		\begin{minipage}[b]{0.48\textwidth}
+		\begin{minipage}[b]{0.55\textwidth}
 			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
@@
 		\hfill
-		\begin{minipage}[b]{0.48\textwidth}
+		\begin{minipage}[b]{0.55\textwidth}
 			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
 		\end{minipage}
-		\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
+		\caption{Likelihood scan for SM (up) and $k_t$=-1 (Down).}
 		\label{scanl}
 	\end{figure}
-
-	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
-	\section{Extrapolation for higher luminosities}
-	In the past section, it was shown that the signal strength  with an integrated luminosity of 35.9fb $^{-1}$ is not significant.
-The LHC has already collected data for integrated luminosity of 150fb $^{-1}$ for run 2 finished in 2018.
-Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb .
-Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities.
-	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
-For this analysis we assume the systematic uncertainties assigned to the background are assumed to be the same.
-	\\
-
-	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities.
-As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1.
-But even with the increase of number of events, the ratio of signal and data is still very small.
-In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
-This is caused by the increased events available for the fit.
 	\pagebreak
@@
 		\end{minipage}
-		\caption{Fit and likelihood scan for 150fb $^{-1}$, 300fb $^{-1}$ and 3000fb $^{-1}$ in $k_t$=-1 model.}
+		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in $k_t$=-1 model.}
 		\label{hm1}
 	\end{figure}
-	The same method is used for the model $k_t$=-1 in the figure \ref{hm1}.
-In this case, the number of events for the signal is more appreciable in comparison with the SM model, same as the 35.9fb $^{-1}$ case.
-However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case.
-For the 3000 fb $^{-1}$ case, the curve closes in $\mu \approx $2.
-	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}
-
-	\begin{table}[ht!]
-		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
-		\begin{tabular}{|c|c|c|c|c|}
-			\hline
-			Luminosity (fb $^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit    &   $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit   \\
-			\hline
-			35.9 & 1.0 $\pm$  7.7 &  17  & 1.0 $\pm$  0.5 & 2.3  \\
-			\hline
-			150& 1.0 $\pm$  6.7& 11  &  1.0 $\pm$  0.4 &1.8\\
-			\hline
-			300&1.0 $\pm$  4.3 &8.7 &  1.0 $\pm$  0.3 &1.5 \\
-			\hline
-			3000&1.0 $\pm$  1.7 & 4.3  &	 1.0 $\pm$  0.1 & 1.1\\
-			\hline
-		\end{tabular}
-		\label{upper}
-	\end{table}
 
@@
 
-	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 75 $\%$ in the 3000 fb $^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results and reduce the uncertainty of $\mu$.
-	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities  giving better results; upper limits in this models are small , so reducing the incompatibility of model with the data.
-This is caused by the fact that the uncertainty of $k_t$=-1 model has a lower uncertainty than the SM model and the number of events for the $tH$ signal is greater.
-For 3000 fb$^{-1}$ the uncertainty on mu is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.
-
 \end{linenumbers}

### 2019-10-15 tesis_hiram/Chapter5/chapter5.tex
algo

@@
 \chapter{Conclusion and outlook}
-
-\chapter{Conclusion and outlook}
-In this work, we explored the $tH$ processes and its different decay rates, including the Higgs mechanism that generate the bosons involved in theses processes. 
-The $tH$ process is one of the processes that comes from the proton-proton collisions inside the accelerators.
-But due to the maintenance schedule of the LHC, many researchers uses Monte Carlo simulation and real data or even only MC for analyze the results and create predictions.
-In our case, by using MC simulations with an Asimov data, it was obtained a fit for the Asimov data with a model of signal and background events with systematic uncertainties according to the decay of processes to a pair of same sign muons $\mu$.
+In this work, we explored the $tH$ processes and its different decay rates. 
+The $tH$ process is one of the processes that comes from the proton-proton collisions in the LHC.
+This process has not been observed experimentally.
+Recently CMS published a search for $tH$ process using 35.9 fb$^{-1}$ from Run 2 in 2018.
 \\
 
-In the results for SM case, we got for the actual luminosities that the signal strength for the signal $tH$ is very low and that generates a signal-data ratio very small in comparison to the backgrounds, generating great uncertainties.
-For that, it was used extrapolations of the model by increasing the luminosity according to the LHC schedule, and discovered that by increasing the number of events, the signal uncertainties was decreasing, and improving the fit.
-In the likelihood scans in higher luminosities, the curves were closing, indicating that the model and the data incompatibility was decreasing in lower values of $\mu$.
+MC simulation and real data or even only MC can be used to study sensitivity different signal processes.
+In this work we used the information from CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
+\\
+In the SM case, the signal strength for the signal $tH$ is very low in comparison to
+the backgrounds, resulting in large uncertainties.
+For the inverted coupling scenario ($k_t$=-1), the uncertainty for the model after the fit was better than the
+SM case, this is due to the larger expected number of signal events. However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels.
 \\
 
-However, for the $k_t$=-1, the uncertainty for the model after the fit was less than the SM case, so by increasing the luminosity the compatibility of model and the data was decreasing for higher luminosities, given that the $\mu$ in the likelihood scan w
-
-All the research made in the CMS at CERN has let us discover the nature of the matter and try to answer questions about the origin of the universe, including the origin of the mass of the things. \\
+We also studied the sensitivity for larger integrated luminosities expected in future runs of the LHC.
+We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
+In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb${-1}$.\\

### 2019-10-15 tesis_hiram/Abstract/abstract.tex
algo

@@
 \begin{abstract}
-I present a study on the  production of tH in same sign dimuon channel $\mu\pm \mu\pm$ 
- A likelihood scan is performed to show the probability of observation of the signal.
-By studying this process , I explore a Higgs production mechanism ,which it has not been observed yet experimentally.
-Simulation is used to predict sensitivity for the LHC high luminosity phase.
-This could help to obtain better limits for the production of tH.
-I also include the model $k_t=-1$, where $k_t$ is the top higgs coupling parameter,  for compare it with the standard model.
-
+I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
+process I explore a Higgs production mechanism which has not yet been observed
+experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ and is extrapolated  for the LHC high luminosity phase.
+The sensivity is also studied for the model with inverted Yukawa coupling ($k_t$=-1), where $k_t$ is the top-Higgs coupling parameter, for comparison with the Standard Model.
 \end{abstract}

### 2019-10-15 tesis_hiram/Chapter1/chapter1.tex
algo

@@
 \begin{chapter}{Introduction}
-\begin{linenumbers}
+
 \section{General objetive and motivations}
@@
 Leptons have their respective antiparticle; same structure with opposite charge.
- All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$.
-\cite{griff}.% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless.
+ All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$\cite{griff}.% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless.
 \\
@@
 Quarks were first theorized by Murray Gell-Mann and 
-George Zweig in 1964, were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until scattering experiments at the Stanford Linear Accelerator Center in 1968.\cite{griff}
+George Zweig in 1964, were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until scattering experiments at the Stanford Linear Accelerator Center in 1968\cite{griff}.
 There are 6 of them: up (1968), down (1968), strange (1968), charm (theorized in 1970, discovered 1974), bottom (theorized 1973, discovered 1977), top (theorized 1973, discovered 1995).
@@
 Other particles do not decay or their lifetimes are very long.
-The final states can be represented with a Feynman diagram according to the SM vertices.
-\cite{mark}
+The final states can be represented with a Feynman diagram according to the SM vertices\cite{mark}.
 
@@
 \caption{
-Cross section for different processes generated in a pp collision} \label{csp}
+Cross section for different processes generated in a pp collision \protect \footnote{Taken from \url{ https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWGCrossSectionsFigures}}
+} \label{csp}
 \end{figure}
@@
 
-\end{linenumbers}
-
 \end{chapter}

### 2019-10-15 tesis_hiram/Chapter2/chapter2.tex
algo

@@
 \section{The Large Hadron Collider}
-\begin{linenumbers}
+
 The Large Hadron Collider (LHC) is one the  largest and most powerful particle accelerator in the world.
@@
 \includegraphics[width=17cm,height=11cm]{Chapter1/cern.jpg}
-\caption{Large hadron collider from CERN} \label{lhc}
+\caption{Large hadron collider from CERN\cite{cern1}} \label{lhc}
 \end{figure}
@@
 \centering
-	\caption{Accelerator operation energies}
+	\caption{Accelerator operation energies\cite{cern3,cern1}}
 	\begin{tabular}{|c|c|}
@@
 \includegraphics[scale=0.5]{Chapter2/lum6.png}
-\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods %
-\cite{cern3}.}
+\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods \cite{cern3}.}
 \label{lhc-lumi}
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/cms2.png}
-	\caption{View of Compact muon solenoid (CMS)}\label{cms}
+	\caption{View of Compact muon solenoid (CMS)\cite{cms-manual}}\label{cms}
 \end{figure}
@@
 \begin{table}[ht]
-	\caption{Characteristic of the CMS superconducting solenoid \cite{cms-manual}}
+	\caption{Characteristic of the CMS superconducting solenoid\cite{cms-manual}}
 	\centering
@@
 	\includegraphics[scale=0.7]{Chapter2/pixel2.png}
-	\caption{The Tracker layout distributed in terms of $\eta$.}
+	\caption{The Tracker layout distributed in terms of $\eta$\cite{cms-manual}.}
 	\label{pixel2}
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/tracker.png}
-	\caption{Total reconstruction efficiency for muons }\label{efi}
+	\caption{Total reconstruction efficiency for muons\cite{cms-manual} }\label{efi}
 \end{figure}
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/ecal.png}
-	\caption{View of the ECAL}\label{ecal}
+	\caption{View of the ECAL\cite{cms-manual}}\label{ecal}
 \end{figure}
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/hcal.png}
-	\caption{View of the CMS HCAL showing the different layers and tower regions. In the endcap, the towers are defined with two longitudinal segments as shown by the colors}\label{hcal}
+	\caption{View of the CMS HCAL showing the different layers and tower regions. In the endcap, the towers are defined with two longitudinal segments as shown by the colors\cite{cms-manual}}\label{hcal}
 \end{figure}
@@
 	\includegraphics[width=11cm,height=7cm]{Chapter2/csc}
-	\caption{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$.}
+	\caption{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$\cite{cms-manual}.}
 	\label{dt}
@@
 % There is a reduction of the efficiency to 6$\%$, which corresponds to the $\eta$  position for the separation.
-\end{linenumbers}

### 2019-10-15 tesis_hiram/Chapter3/chapter3.tex
algo

@@
 This event yields  will be used to estimate the signal sensitivity.
-The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertanties are described below.
-\begin{table}[ht!]
-	\centering
-\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$. The uncertainties of yields include statistical and systematic}
-	\begin{tabular}{cc}
-	\hline
-		Process  & Number of events  \\
-		\hline
-		$t\bar{t}W$  &  68 $\pm$ 10 \\
-		$t\bar{t}Z$  & 25.9 $\pm$ 3.9\\
-		$WZ$ & 15.1$\pm$7.7\\
-		Rares & 20.9 $\pm$   4.9\\
-		Fakes  & 80.9 $\pm$9.4\\
-	   $t\bar{t}H$  &  24.2 $\pm$ 2.1 \\
-		\hline
-		$tH$ (SM) & 2.14 $\pm$ 0.13\\
-		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
-	\end{tabular}	
-\label{tth-table}
-\end{table}
+The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertanties are described in table \ref{tth-table}.
 
 \section{Systematic uncertanties}
-The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections.
-The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region.
-In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
-The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria.
-For the Higgs processes $tH$ and $ttH$ , the uncertainty are due to the theoretical parameters used in that simulation.
+\begin{itemize}
+\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
+\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
+\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
+\item For the Higgs processes $tH$ and $ttH$ , the uncertainty are due to the theoretical parameters used in that simulation.
+\end{itemize}
+
 %control region: event selection with 3 leptons for compare simulation with real data. yield difference  in that region is 50 .is taken  and for wz is 50
@@
 \pagebreak
-
 %The fake rate corresponds to  non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks).
@@
 \section{Multivariable discriminant}
-Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminat, which separates signal from backgrounds, is necessary to optimize the signal sensitivity.
+Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminant, which separates signal from backgrounds, is necessary to optimize the signal sensitivity.
 The multivariable discriminant is a Boosted Decision Tree (BDT) that takes a set of input features and splits input data recursively based on those features.
@@
 \end{itemize}
+
+Figure \ref{bdt2} shows the BDT distribution for signal and backgrounds.
+\pagebreak
 %Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake
@@
 
-\begin{figure}[!tbp]
+\begin{table}[ht!]
 	\centering
-	\begin{minipage}[b]{0.45\textwidth}
+	\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$. The uncertainties of yields include statistical and systematic\cite{th1}}
+	\begin{tabular}{cc}
+		\hline
+		Process  & Number of events  \\
+		\hline
+		$t\bar{t}W$  &  68 $\pm$ 10 \\
+		$t\bar{t}Z$  & 25.9 $\pm$ 3.9\\
+		$WZ$ & 15.1$\pm$7.7\\
+		Rares & 20.9 $\pm$   4.9\\
+		Fakes  & 80.9 $\pm$9.4\\
+		$t\bar{t}H$  &  24.2 $\pm$ 2.1 \\
+		\hline
+		$tH$ (SM) & 2.14 $\pm$ 0.13\\
+		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
+	\end{tabular}	
+	\label{tth-table}
+\end{table}
+
+\begin{figure}[!htbp]
+	\centering
+	\begin{minipage}[b]{0.48\textwidth}
 		\includegraphics[width=\textwidth]{Chapter3/kos.png}
@@
 	\hfill
-	\begin{minipage}[b]{0.45\textwidth}
+	\begin{minipage}[b]{0.48\textwidth}
 		\includegraphics[width=\textwidth]{Chapter3/kos2.png}
 	\end{minipage}
-\caption{Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right)}
+\caption{Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right) \cite{th1}}
+\label{bdt2}
 \end{figure}

### 2019-10-15 tesis_hiram/Chapter4/chapter4.tex
algo

@@
 \chapter{Statistical Analysis}
-\begin{linenumbers}
 	To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
@@
 The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 finished in 2018.
-Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb $^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb .
+Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb$^{-1}$ .
 Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities.
@@
 	%The upper limits reduces as the luminosity increases; from 150 to 3000 fb $^{-1}$, the upper limit reduces in $\Delta\mu$=12.7 with $\Delta\mu$ the change of $\mu$ .
-
-\end{linenumbers}

### 2019-10-15 tesis_hiram/Chapter5/chapter5.tex
algo

@@
 \chapter{Conclusion and outlook}
-In this work, we explored the $tH$ processes and its different decay rates. 
+In this work, we explored the sensitivity to the tH production process.
 The $tH$ process is one of the processes that comes from the proton-proton collisions in the LHC.
@@
 
-MC simulation and real data or even only MC can be used to study sensitivity different signal processes.
-In this work we used the information from CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
-\\
+MC simulation and real data or even only MC can be used to study sensitivity different signal processes.In this work we used the information published by CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
 In the SM case, the signal strength for the signal $tH$ is very low in comparison to
@@
 We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
-In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb${-1}$.\\
+In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb$^{-1}$.\\

### 2019-10-15 fit_2lss_2016/make_workspace.C

@@ -58,20 +58,20 @@ thw->Scale(0.71/thw->Integral());//thw
 ////////////////////////////////////////////
 //for higher luminosities
 //////////////////////////////////
-tzq->Scale(3000.0/35.9); //tzq
-vvv->Scale(3000/35.9); //vvv
-ww->Scale(3000/35.9); //wwss
-tttt->Scale(3000/35.9); // tttt
-fakes->Scale(3000/35.9); //non prompt
-wz->Scale(3000/35.9); //WZ
-ttz->Scale(3000/35.9);//ttZ
-ttw->Scale(3000/35.9);//ttW
-tth->Scale(3000/35.9);//tth
-thq->Scale(3000/35.9);//thq
-thw->Scale(3000/35.9);//thw
-tzw->Scale(3000/35.9);//tzw
-zz->Scale(3000/35.9); //zz
-ww2->Scale(3000/35.9);//wwdps
+//tzq->Scale(3000.0/35.9); //tzq
+//vvv->Scale(3000/35.9); //vvv
+//ww->Scale(3000/35.9); //wwss
+//tttt->Scale(3000/35.9); // tttt
+//fakes->Scale(3000/35.9); //non prompt
+//wz->Scale(3000/35.9); //WZ
+//ttz->Scale(3000/35.9);//ttZ
+//ttw->Scale(3000/35.9);//ttW
+//tth->Scale(3000/35.9);//tth
+//thq->Scale(3000/35.9);//thq
+//thw->Scale(3000/35.9);//thw
+//tzw->Scale(3000/35.9);//tzw
+//zz->Scale(3000/35.9); //zz
+//ww2->Scale(3000/35.9);//wwdps
 
 
 TH1F *th=(TH1F*)thq->Clone("th");
@@ -237,7 +237,7 @@ axis5->Draw();
 
 auto legend = new TLegend(0.6,0.6,0.89,0.89);
 //legend->SetHeader("Test","C"); // option "C" allows to center the header
-legend->AddEntry(hat,"Data","lep");
+//legend->AddEntry(hat,"Data","lep");
 //legend->AddEntry("th (k_t=-1)","f");
 legend->AddEntry(th,"tH (SM)","f");
 legend->AddEntry(tth,"t#bar{t}H","f");
@@ -309,7 +309,7 @@ h->GetXaxis()->SetTitle("BDT Discriminant");
 h->GetYaxis()->SetTitle("Events");
[…]

### 2019-10-15 tesis_hiram/Chapter1/chapter1.tex
algo

@@
         \includegraphics[scale=0.3]{Chapter1/sm1.png}
-        \caption{Standard Model to date\protect \footnotemark }
+        \caption{Standard Model to date \protect \footnotemark}
         \label{sm1}
@@
 \end{center}
-\footnotetext{Taken from Wikimedia. \small \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}}
+ \footnotetext{Taken from \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}
+}
 
@@
 \caption{
-Cross section for different processes generated in a pp collision \protect \footnote{Taken from \url{ https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWGCrossSectionsFigures}}
-} \label{csp}
+Cross section for different processes generated in a pp collision \protect \footnotemark }
+ \label{csp}
 \end{figure}
@@
 \pagebreak
-
+\footnotetext{Taken from \url{ https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWGCrossSectionsFigures}}
 \section{Higgs decay rates}

### 2019-10-15 tesis_hiram/Chapter1/chapter1.tex
algo

@@
  Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. \\
-Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell. \cite{griff}
+Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
 Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.
@@
 Since then,the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.\\
-However, the top quark often receives special attention in new physics models because its mass requires near unity coupling to the Higgs boson \cite{top}.
+However, the top quark often receives special attention in new physics models because its mass requires near unity coupling to the Higgs boson\cite{top}.
 As shown in table \ref{SM table}, the top quark lifetime is so small that they decay before they can hadronise, that is to say, the process to create hadrons from quarks and gluons.\\
@@
 In tevatron and LHC, the production of $t\bar{t}$ comes from ggF (gluon gluon fusion) via strong force.
-Even it is posible to create a single top quark in the LHC via electroweak interactions (with a W boson) \cite{th1}.
+Even it is posible to create a single top quark in the LHC via electroweak interactions (with a W boson)\cite{th1}.
 The top quark, due to its big mass, always decays into a W boson and a b quark.
@@
 	0 \quad \text{i=j, or j=k, or k=i } 
-	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$ , $Z$ and $\gamma$ vector boson \cite{ew1,ew2}.
-%Z bosons  and photons will be formed by a combination of W and B fields.\\
+	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$ , $Z$ and $\gamma$ vector boson
+\cite{ew1}\cite{ew2}. %Z bosons  and photons will be formed by a combination of W and B fields.\\
 \\
@@
 
-In the recent years, people have studied the top anti top Higgs  ($t\bar{t}H$) process, in order to detect a Higgs boson, via multilepton signals \cite{th1}.
+In the recent years, people have studied the top anti top Higgs  ($t\bar{t}H$) process, in order to detect a Higgs boson, via multilepton signals\cite{th1}.
 In this process, the creation of a Higgs boson comes from a intection via $t\bar{t}$.
@@
 Springer, Berlin, Heidelberg} .
-The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV , but has not yet been measured due to the detector resolution \cite{cms-manual}.
+The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV , but has not yet been measured due to the detector resolution\cite{cms-manual}.
 \\

### 2019-10-15 tesis_hiram/Chapter2/chapter2.tex
algo

@@
 \includegraphics[scale=0.5]{Chapter2/lum6.png}
-\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods \cite{cern3}.}
+\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods\cite{cern3}.}
 \label{lhc-lumi}
@@
 	\includegraphics[width=0.4\linewidth]{Chapter2/mu-efi}
-	\caption{Muon reconstruction efficiency in terms of $\eta$ and $p_t$ \cite{cms-manual}}
+	\caption{Muon reconstruction efficiency in terms of $\eta$ and $p_t$\cite{cms-manual}}
 	\label{mu-efi}

### 2019-10-15 tesis_hiram/Chapter1/chapter1.tex
algo

@@
 \centering
-\caption{	Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2 \protect \cite{pd}}
+\caption[Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2]{	Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2 \protect \cite{pd}}
 \begin{tabular}{|c|c|c|}
@@
 \begin{table}[!htbp] 
-\caption{SM Higgs boson branching ratios for  $M_H$ =125 GeV \protect \cite{pd}}
+\caption[SM Higgs boson branching ratios for  $M_H$ =125 GeV]{SM Higgs boson branching ratios for  $M_H$ =125 GeV \protect \cite{pd}}
 \centering
@@
 	\includegraphics[scale=0.5]{Chapter1/newtHq.png}
-	\caption{tH mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
+	\caption[$tH$ mechanism.
+Higgs radiated from a top quark (left).
+Higgs radiated from a W boson (right)]{$tH$ mechanism.
+Higgs radiated from a top quark (left).
+Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
 \end{figure}

### 2019-10-15 tesis_hiram/Acknowledgement/acknowledgement.tex
algo

% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}

And I would like to acknowledge Dr. Jos\'e Feliciano Ben\'itez Rubio for his contributions and advices in order to develop  and write this thesis. Also thank Dr. Dr. Javier Murillo and  Dr. Cristina Oropeza for their observations and advices in my formation. 
DR. Susana Alv\'arez for support

\end{acknowledgements}

### 2019-10-15 tesis_hiram/compile-thesis.sh
algo

@@ -25,22 +25,22 @@ if [ $1 = $clean ]; then
 	rm -rf *.out*
 	rm -rf *.nlo
 	rm -rf *.nls
-	rm -rf $filename.pdf
-	rm -rf $filename.ps
-	rm -rf $filename.dvi
+	rm -rf $thesis.pdf
+	rm -rf $thesis.ps
+	rm -rf $thesis.dvi
 	rm -rf *#* 
 	echo "Cleaning complete!"
 	exit
 else
 	echo "Shell script for compiling the PhD Thesis"
-	echo "Usage: sh ./compile-thesis.sh [OPTIONS] [filename]"
+	echo "Usage: sh ./compile-thesis.sh [OPTIONS] [thesis]"
 	echo "[option]  compile: Compiles the PhD Thesis"
-	echo "[option]  clean: removes temporary files no filename required"
+	echo "[option]  clean: removes temporary files no thesis required"
 	exit
 fi
 fi
 
-filename=$2;
+thesis=$2;
 
 if [ $1 = $clean ]; then
 	echo "Cleaning please wait ..."
@@ -60,22 +60,22 @@ if [ $1 = $clean ]; then
 	rm -rf *.out*
 	rm -rf *.nlo
 	rm -rf *.nls
-	rm -rf $filename.pdf
-	rm -rf $filename.ps
-	rm -rf $filename.dvi
+	rm -rf $thesis.pdf
+	rm -rf $thesis.ps
+	rm -rf $thesis.dvi
 	rm -rf *#* 
 	echo "Cleaning complete!"
 	exit
 elif [ $1 = $compile ]; then
 	echo "Compiling your PhD Thesis...please wait...!"
-	pdflatex -interaction=nonstopmode $filename.tex
-	bibtex $filename.aux 	
-	makeindex $filename.aux
-	makeindex $filename.idx
-	makeindex $filename.nlo -s nomencl.ist -o $filename.nls
-	pdflatex -interaction=nonstopmode $filename.tex
-	makeindex $filename.nlo -s nomencl.ist -o $filename.nls
-	pdflatex -interaction=nonstopmode $filename.tex
+	pdflatex -interaction=nonstopmode $thesis.tex
+	bibtex $thesis.aux 	
+	makeindex $thesis.aux
+	makeindex $thesis.idx
+	makeindex $thesis.nlo -s nomencl.ist -o $thesis.nls
[…]

### 2019-10-15 tesis_hiram/Abstract/abstract.tex
fixes

@@
 process I explore a Higgs production mechanism which has not yet been observed
-experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ and is extrapolated  for the LHC high luminosity phase.
-The sensivity is also studied for the model with inverted Yukawa coupling ($k_t$=-1), where $k_t$ is the top-Higgs coupling parameter, for comparison with the Standard Model.
+experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the LHC high luminosity phase.
+The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter, for comparison with the Standard Model.
 \end{abstract}

### 2019-10-16 tesis_hiram/Chapter1/chapter1.tex
algo
final

@@
 \renewcommand{\baselinestretch}{1.5}
-
 \begin{chapter}{Introduction}
@@
  Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. \\
-Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
+Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$). Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
 Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.
@@
         \includegraphics[scale=0.3]{Chapter1/sm1.png}
-        \caption{Standard Model to date \protect \footnotemark}
+        \caption[Standard Model to date]{Standard Model to date \protect \footnotemark}
         \label{sm1}
@@
 The last group of the family are the bosons,which have a spin 1 and 0. 
-There are 5 bosons: $W^{\pm}$ , $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered , is in charge of give the property of mass to particles via Higgs mechanism.
+There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered , is in charge of give the property of mass to particles via Higgs mechanism.
 Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}.
 \\
-The $W$,$Z$  and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
+The $W$, $Z$ and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
 Those bosons act as mediators in decays and creation of complex
@@
 
-There are experiments that detects particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab  in United States of America, KEK in Japan, etc.
+There are experiments that detects particles around the world, such as the Large Hadron Collider (LHC) in Europe, the Fermilab  in United States of America, KEK in Japan, etc.
 More information about the LHC will be described in the next chapters.
 \\
-Since quarks and gluons only exist in bound states, it is imposible to observe isolated quarks except the top quark, which decays before it has time to form a
+Since quarks and gluons only exist in bound states, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
 bound state. As two quarks are separated, the strong force between them increases
@@
 The Higgs boson was discovered recently on year 2012 in the experiments ATLAS and CMS at CERN.
-The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV ,where investigators worked on the data and detecting various decay modes that generates final states such  as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
+The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV ,where investigators worked on the data and detecting various decay modes that generates final states such  as $WW$, $\gamma \gamma$, $ZZ$, $b\bar{b}$ and $\tau \tau$ \cite{higgsd}.
 \\
@@
 
-The production of top quark can be generated in differents ways.
-In tevatron and LHC, the production of $t\bar{t}$ comes from ggF (gluon gluon fusion) via strong force.
-Even it is posible to create a single top quark in the LHC via electroweak interactions (with a W boson)\cite{th1}.
-The top quark, due to its big mass, always decays into a W boson and a b quark.
-But since the W boson have various decays, the top quark can generate many posible particles, acording to W boson decays.
+The production of top quark can be generated in different ways.
+In Tevatron and LHC, the production of $t\bar{t}$ comes from ggF (gluon gluon fusion) via strong force.
+Even it is possible to create a single top quark in the LHC via electroweak interactions (with a $W$ boson)\cite{th1}.
+The top quark, due to its big mass, always decays into a $W$ boson and a b quark.
+But since the $W$ boson have various decays, the top quark can generate many possible particles, according to $W$ boson decays.
 Some posible decays of top quark is the decay to a lepton such as muon, electron or tau and their neutrinos .
@@
 refer to the left (right) handed particles.\footnote{$\bar{\psi}$ denotes the adjoint spinor $\bar{\psi}=\psi^\dagger \gamma^0$.
-	$\cancel{D}=\gamma^\mu D_\mu$.
-$\gamma$ are the Dirac matrices}. 
+$\cancel{D}=\gamma^\mu D_\mu$. $\gamma$ are the Dirac matrices}. 
 The gauge covariant derivatives  are given by
@@
 \end{align}
-where $\sigma^i$ are the pauli matrices. L and R refers to left and right handed fields.
+where $\sigma^i$ are the Pauli matrices. L and R refers to left and right handed fields.
 The left handed fields for the first family are defined by the following doublets
@@
 %\end{align}
+
 Now introducing \ref{smo} and \ref{zboson} in \ref{W},
@@
 \end{align}
-
-%and the photon that in this case is the field A
-%\begin{align}
- %       A_\mu=\frac{1}{\sqrt{g^2+g'^2}}\left(g'W^3_\mu +gB_\mu   \right)
-%\end{align}
-%with mass 
-%\begin{align}
- %       m_A=0
-%\end{align}
 
@@
 Another process  is vector boson fusion (VBF), where two fermions interact via a vector boson ($W$ or $Z$ ) and create a Higgs along with other particles.
-There is also the vector higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}.
+There is also the vector Higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}.
 These processes are shown in the figure \ref{psu} \\
@@
 In the recent years, people have studied the top anti top Higgs  ($t\bar{t}H$) process, in order to detect a Higgs boson, via multilepton signals\cite{th1}.
-In this process, the creation of a Higgs boson comes from a intection via $t\bar{t}$.
+In this process, the creation of a Higgs boson comes from a interaction via $t\bar{t}$.
 In the figure \ref{psu}, the $t\bar{t}H$ starts with 2 gluons which decay to two $t\bar{t}$ pairs and after that , the interaction $t\bar{t}$  generates a Higgs.
@@
 \centering
-\caption[Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2]{	Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2 \protect \cite{pd}}
+\caption[Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2]{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2 \protect \cite{pd}}
 \begin{tabular}{|c|c|c|}
@@
 \includegraphics[width=12cm,height=7cm]{Chapter1/7-14xsec.eps}
-\caption{
+\caption[Cross section for different processes generated in a pp collision]{
 Cross section for different processes generated in a pp collision \protect \footnotemark }
@@
 \section{Higgs decay rates}
-In particle physics,two importatns properties are the lifetime and the decay rates of a particle.
+In particle physics,two important properties are the lifetime and the decay rates of a particle.
 The lifetime is related to the total decay rate $\Gamma$, that is the probability per unit of time a particle decay,
@@
 The decay  $H \rightarrow$ $\mu^+\mu^-$ has a very low branching ratio.
-This decay is very rare but not imposible to detect in the future.
+This decay is very rare but not impossible to detect in the future.
 In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$\\
@@
 Higgs radiated from a top quark (left).
-Higgs radiated from a W boson (right)]{$tH$ mechanism.
+Higgs radiated from a $W$ boson (right)]{$tH$ mechanism.
 Higgs radiated from a top quark (left).
-Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
+Higgs radiated from a $W$ boson (right) \protect \cite{bb}} \label{newth}
 \end{figure}

### 2019-10-16 tesis_hiram/Chapter2/chapter2.tex
final

@@
 \includegraphics[width=17cm,height=11cm]{Chapter1/cern.jpg}
-\caption{Large hadron collider from CERN\cite{cern1}} \label{lhc}
+\caption[Large hadron collider from CERN]{Large hadron collider from CERN\cite{cern1}} \label{lhc}
 \end{figure}
@@
 \centering
-	\caption{Accelerator operation energies\cite{cern3,cern1}}
+	\caption[Accelerator operation energies]{Accelerator operation energies\cite{cern1,cern3}}
 	\begin{tabular}{|c|c|}
@@
 
-The main objetive of the LHC is to study the nature of electroweak symmetry breaking for the Higgs mechanism of the SM. 
+The main objective of the LHC is to study the nature of electroweak symmetry breaking for the Higgs mechanism of the SM. 
 Alternatives to the Standard Model that involves different symmetries are also put on test.
@@
 \includegraphics[scale=0.5]{Chapter2/lum6.png}
-\caption{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods\cite{cern3}.}
+\caption[LHC schedule, including future plans for increase the center of mass energy and luminosity.
+The periods labeled LS are the maintenance periods]{LHC schedule, including future plans for increase the center of mass energy and luminosity.
+The periods labeled LS are the maintenance periods\cite{cern3}.}
 \label{lhc-lumi}
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/cms2.png}
-	\caption{View of Compact muon solenoid (CMS)\cite{cms-manual}}\label{cms}
+	\caption[View of Compact muon solenoid (CMS)]{View of Compact muon solenoid (CMS)\cite{cms-manual}}\label{cms}
 \end{figure}
@@
 
-The CMS experiment is composed of several detector layers  that allow identify and save different types of energy signals  and it is saved in a powerful supercomputers that separate and classify the data according to certains variables.
+The CMS experiment is composed of several detector layers  that allow identify and save different types of energy signals  and it is saved in a powerful supercomputers that separate and classify the data according to certain variables.
 The general parts of the CMS are the Silicon Tracker , an Electromagnetic Calorimeter,a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
@@
 \begin{table}[ht]
-	\caption{Characteristic of the CMS superconducting solenoid\cite{cms-manual}}
+	\caption[Characteristic of the CMS superconducting solenoid]{Characteristic of the CMS superconducting solenoid\cite{cms-manual}}
 	\centering
@@
 The Strip Detector have almost 15 400 modules, mounted on
-carbon-fibre structures and housed inside by a temperature controlled outer support tube. The operating temperature must be around -$\ang{20}$C. 
+carbon-fiber structures and housed inside by a temperature controlled outer support tube. The operating temperature must be around -$\ang{20}$C. 
 The total area of the pixel detector is around 1 $m^2$ and the silicon strips is 200 m$^2$. 
@@
 	\includegraphics[scale=0.7]{Chapter2/pixel2.png}
-	\caption{The Tracker layout distributed in terms of $\eta$\cite{cms-manual}.}
+	\caption[The Tracker layout distributed in terms of $\eta$]{The Tracker layout distributed in terms of $\eta$\cite{cms-manual}.}
 	\label{pixel2}
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/tracker.png}
-	\caption{Total reconstruction efficiency for muons\cite{cms-manual} }\label{efi}
+	\caption[Total reconstruction efficiency for muons]{Total reconstruction efficiency for muons\cite{cms-manual} }\label{efi}
 \end{figure}
@@
 
-The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillanting crystals (emits light when particles interact with the crystal).
+The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillating crystals (emits light when particles interact with the crystal).
 These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps.
 The barrel section  of the ECAL covers the range $|\eta| < 1.479$.
-The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
+The crystals in the barrel have a pyramid shape and their cross section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
 The crystal length is 230 mm.The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/ecal.png}
-	\caption{View of the ECAL\cite{cms-manual}}\label{ecal}
+	\caption[View of the ECAL]{View of the ECAL\cite{cms-manual}}\label{ecal}
 \end{figure}
@@
 HCAL is located in the barrel and the endcaps, surrounding the ECAL and affected by the magnetic field generated by the solenoid.
-The Barrel section (HB) and endcap section (HE)  cover the pseudorapity 0 < $|\eta|$ < 1.3 and  1.3 < $|\eta|$ < 3.0 respectively.\\
+The Barrel section (HB) and endcap section (HE)  cover the pseudorapidity 0 < $|\eta|$ < 1.3 and  1.3 < $|\eta|$ < 3.0 respectively.\\
 
-The HB is an assembly of two half barrels, composed of 18 wedges.Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel).Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087.
-Light of scintillator is collected by a single wave
+The HB is an assembly of two half barrels, composed of 18 wedges.Each wedge has 17 active layers composed of scintillator tiles with 16 layers of 
+absorbent metal (brass and stainless steel).Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087. Light of scintillator is collected by a single wave
 length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm. 
@@
 
-HE is composed by brass absorber plates ,with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.  HE is sectioned in 5 in $\phi$ to match the barrel wedges.
+HE is composed by brass absorbent plates ,with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.  HE is sectioned in 5 in $\phi$ to match the barrel wedges.
  .
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/hcal.png}
-	\caption{View of the CMS HCAL showing the different layers and tower regions. In the endcap, the towers are defined with two longitudinal segments as shown by the colors\cite{cms-manual}}\label{hcal}
+	\caption[View of the CMS HCAL showing the different layers and tower regions.
+In the endcap, the towers are defined with two longitudinal segments as shown by the colors]{View of the CMS HCAL showing the different layers and tower regions.
+In the endcap, the towers are defined with two longitudinal segments as shown by the colors\cite{cms-manual}}\label{hcal}
 \end{figure}
@@
 magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.\\
-There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
-steel absorbers and embedded radiation hard quartz fibers,which collects 
+There is also a forward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
+steel absorbent and embedded radiation hard quartz fibers,which collects 
 Cherenkov light\cite{cms-manual}.% that is  when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 
@@
 
-The tiles are arranged in a tower pattern in the  $\eta-\phi$ space, projective to the interaction point.  In total there
+The tiles are arranged in a tower pattern in the  $\eta-\phi$ space, projected to the interaction point.  In total there
 are 4176 towers. The towers are used as input to several jet reconstruction algorithms.
@@
 	\includegraphics[width=11cm,height=7cm]{Chapter2/csc}
-	\caption{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$\cite{cms-manual}.}
+	\caption[Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$]{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$\cite{cms-manual}.}
 	\label{dt}
@@
 	\includegraphics[width=0.4\linewidth]{Chapter2/mu-efi}
-	\caption{Muon reconstruction efficiency in terms of $\eta$ and $p_t$\cite{cms-manual}}
+	\caption[Muon reconstruction efficiency in terms of $\eta$ and $p_t$]{Muon reconstruction efficiency in terms of $\eta$ and $p_t$\cite{cms-manual}}
 	\label{mu-efi}

### 2019-10-16 tesis_hiram/Chapter3/chapter3.tex
final

@@
 This event yields  will be used to estimate the signal sensitivity.
-The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertanties are described in table \ref{tth-table}.
+The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertainties are described in table \ref{tth-table}.
 
@@
 	\centering
-	\caption{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$. The uncertainties of yields include statistical and systematic\cite{th1}}
+	\caption[Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
+The uncertainties of yields include statistical and systematic]{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
+The uncertainties of yields include statistical and systematic\cite{th1}}
 	\begin{tabular}{cc}
@@
 	\end{minipage}
-\caption{Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right) \cite{th1}}
+\caption[Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right)]{Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right) \cite{th1}}
 \label{bdt2}

### 2019-10-16 tesis_hiram/Chapter4/chapter4.tex
final

@@
 The uncertainty of the signal strength is estimated by applying a  fit to the Asimov dataset, where the model
-	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and gaussian constraints for the systematical uncertainties in the model.
+	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and Gaussian constraints for the systematical uncertainties in the model.
 
@@
 		\end{minipage}
-		\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
+		\caption{Post-fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
 			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
@@
 		\centering
-		\caption{Postfit  yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
+		\caption{Post-fit  yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
 		\begin{tabular}{ccc}

### 2019-10-16 tesis_hiram/Chapter1/chapter1.tex
final

@@
 Particle physics is a field of study of physics that studies the particles that create matter and its interactions to very small scale, even smaller than atoms.
-The particles analized in particle physics are the fundamental particles that compose the matter and the responsibles for all forces of nature.
-All thoses particles  and their properties are grouped in a theory called the Standard Model.
+The particles analyzed in particle physics are the fundamental particles that compose the matter and responsible for all forces of nature.
+All those particles  and their properties are grouped in a theory called the Standard Model.
 Standard Model (SM) is a theory that describes the fundamental forces (except gravity) and classify the elementary particles in bosons (entire spin) and fermions (half spin).
-The SM , created almost 50 years ago, has been the most successul theory in explain the phenomena in the subatomic world.
+The SM, created almost 50 years ago, has been the most successful theory in explain the phenomena in the subatomic world.
 \\
 
-One of the particles of the SM, the Higgs Boson , was recently discovered in 2012 in the ATLAS and CMS experiments at CERN.
-The discovery of Higgs boson in  proton proton collisions  marked a new era in the particle physics due to its characteristic  of giving the matter the property of mass, according to previous theories and predictions .
-Since then, people around the world are working in the Large Hadron Collider at CERN  in order to detect the Higgs bosons in higher energies and differents Higgs production processes.
+One of the particles of the SM, the Higgs Boson, was recently discovered in 2012 in the ATLAS and CMS experiments at CERN.
+The discovery of Higgs boson in  proton proton collisions marked a new era in the particle physics due to its characteristic of giving the matter the property of mass, according to previous theories and predictions.
+Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes.
 Also the impact of Higgs is also important in cosmology,  where theoretical investigations relate the Higgs boson and the cosmic inflation.\\
 
-In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions , such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes.
-In this work, we will analize the production of Higgs boson in association with a
-single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC. 
+In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions, such as gluon fusion ($gg$F), VBF, $WH$, $ZH$ and $t\bar{t}H$ and people have obtained consistent results in the search of Higgs in those processes.
+In this work, we will analyze the production of Higgs boson in association with a
+single top quark ($tH$) in proton-proton collisions with the CMS experiment of the LHC.
 The motivation of the work is this mechanism of production of the Higgs boson has not been observed before by any experiment.
 The exploration of Higgs production on the tH channel is subject relatively new.
-%The SM is used to study the tH channel and compare it with other Higgs production mechanisms results.
-\\
-Many channels are yet out of
-reach experimentally. At the same time, many theoretical
+Many channels are yet out of reach experimentally.
+At the same time, many theoretical
 proposals are yet to be put on test.
@@
 Leptons have their respective antiparticle; same structure with opposite charge.
- All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$\cite{griff}.% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless.
-\\
-\\
+All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$\cite{griff}.\\
 
- Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. \\
+ Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. 
 Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$). Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
-Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.
-\\
-
+Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.\\
 Quarks were first theorized by Murray Gell-Mann and 
@@
 There are 6 of them: up (1968), down (1968), strange (1968), charm (theorized in 1970, discovered 1974), bottom (theorized 1973, discovered 1977), top (theorized 1973, discovered 1995).
-\\
 
 Quarks have characteristics such as  electric charge, mass, color charge, and spin.
-The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down , strange and bottom quarks have charge of $-\frac{1}{3}$.
-Among them , the top quark is the most massive of all, while the up and down are the least massive.
+The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down, strange and bottom quarks have charge of $-\frac{1}{3}$.
+Among them, the top quark is the most massive of all, while the up and down are the least massive.
 The lepton and quarks have their respective antiparticle, which have the same mass, but inverted charge.\\  
@@
 The last group of the family are the bosons,which have a spin 1 and 0. 
-There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered , is in charge of give the property of mass to particles via Higgs mechanism.
+There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for electromagnetic force; gluons $g$ which also massless, is related to strong force and Higgs boson, recently discovered , is in charge of give the property of mass to particles via Higgs mechanism.
 Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}.
@@
 \begin{table}[!htbp]
-\caption{Table of particles in SM\cite{pd}. Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
+\caption[Table of particles in SM]{Table of particles in SM\cite{pd}. Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
 \renewcommand{\arraystretch}{1.5}
@@
 	\hline 
-
 Bottom ($b$)	& 4180 &$-\frac{1}{3}$  &  $\frac{1}{2}$ &$1.3 \times 10^{-12}$   & 6.16 $\times 10^{-3}$\\ 
@@
 Richard Hagen, and Tom Kibble in separated groups.
-They formulated the Higgs mechanism that explain the generation of mass for the particles .
+They formulated the Higgs mechanism that explain the generation of mass for the particles.
 \\
@@
 Maskawa in 1973 to explain observed CP violations in Kaon decay\cite{griff}.
-On 1995, in the Tevatron at Fermilab in Illinois, the top quark  was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top} .
+On 1995, in the Tevatron at Fermilab in Illinois, the top quark  was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
 Since then,the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.\\
@@
 \section{Higgs mechanism}
-In the SM, mathematically the particles are described in form of fields. The SM for electroweak interactions is described as a gauge theory with a symmetry group SU(2)$\otimes$U(1)
-that describes the weak and electromagnetic interactions
+In the SM, mathematically the particles are described in form of fields.
+The SM for electroweak interactions is described as a gauge theory with a symmetry group SU(2)$\otimes$U(1) that describes the weak and electromagnetic interactions
 due to the exchange of spin 1 gauge fields($W^{\pm}$,$Z$) for the weak part and a photon for the electromagnetic part. The Higgs mechanism give bosons and fermions their mass.
@@
 
-$W^i$ (i=1,2,3) are three  SU(2) gauge bosons and B is a U(1) gauge boson.\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
+$W^i$ (i=1,2,3) are three  SU(2) gauge bosons and B is a U(1) gauge boson\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
 	+1 \quad  \text{for even permutation} \\
@@
 	0 \quad \text{i=j, or j=k, or k=i } 
-	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$ , $Z$ and $\gamma$ vector boson
+	\end{dcases}$.}. In the end, those gauge bosons, after introduce the Higgs mechanism  become the $W^\pm$ , $Z$ and $\gamma$ vector boson
 \cite{ew1}\cite{ew2}. %Z bosons  and photons will be formed by a combination of W and B fields.\\
@@
 
-we define the physical vector boson $W^-_\mu$. $W^+_\mu$ and $Z$ 
+We define the physical vector boson $W^-_\mu$. $W^+_\mu$ and $Z$ 
 \begin{align} 
@@
 	-\phi^-
-	\end{array} \right)
+	\end{array} \right)$
 	% \Phi =\sqrt{-\frac{\mu^2}{2\lambda}}=\frac{v}{\sqrt{2}}  \qquad \lambda >0
-	$ is necessary for the correct transformation in the case of up quarks. \\
+	 is necessary for the correct transformation in the case of up quarks. \\
 h.c refers to hermitian conjugate terms.  }  The indices  m and n mean sum over the families. \\
@@
 In tH process, Higgs boson is radiated from a single top quark as shown in \ref{psu}.
-tH process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens to new discoveries.
+$tH$ process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens to new discoveries.
 \\
@@
 
-In the table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$ , that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
+In the table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of 35.9 fb$^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
 
@@
 Here we can see ggF process have the biggest cross section of all Higgs mechanism and generates the greatest number of events possibles.
-For the processes tH and $t\bar{t}$H, they have the smallest cross section, so the probability for the processes is low and generates a small number of events.
+For the processes $tH$ and $t\bar{t}H$, they have the smallest cross section, so the probability for the processes is low and generates a small number of events.
 \pagebreak
@@
 \end{align}
-with N the original number of particles before the decay. From here is evident that number of particles left in a decay is
-
+With N the original number of particles before the decay. From here is evident that number of particles left in a decay is 
 \begin{align}

### 2019-10-16 tesis_hiram/Chapter2/chapter2.tex
final

@@
 experiments installed along the LHC ring.
-One of them is ATLAS, located on Point 1 between the two injection lines , which is a general purpose detector.
+One of them is ATLAS, located on Point 1 between the two injection lines, which is a general purpose detector.
 At point 5 is another general purpose detector: the compact muon solenoid  (CMS).
-A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
+A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7\cite{cern1,cern2}.
 \\
@@
 two tubes kept at ultrahigh vacuum. 
-By using of superconducting electromagnets that generates a powerful magnetic field , the beams are guided around the accelerator ring. 
-The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.For that, it is required to have  magnets to a temperature of  $‑271.3$ C.
-To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}
+By using of superconducting electromagnets that generates a powerful magnetic field, the beams are guided around the accelerator ring. 
+The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
+For that, it is required to have  magnets to a temperature of  $‑271.3$ C.
+To reach such temperatures, a system of liquid helium is connected to the accelerator\cite{cern2}.
 
@@
 Protons in the LHC start out as hydrogen atoms stripped of their electrons. The first accelerating stage the protons are subjected to is a linear accelerator, Linac2,
-which accelerates them up to 50 MeV . The protons are then sent into the
+which accelerates them up to 50 MeV. The protons are then sent into the
 Proton Synchotron Booster which accelerates them up to 1.4 GeV before sending them to the Proton Synchotron (PS).
@@
 After this stage, the beam is ready to be injected into
-the LHC through one of two injection lines with 6.5 TeV.\cite{cern3}
+the LHC through one of two injection lines with 6.5 TeV\cite{cern3}.
 
@@
 Inside the detectors, collided protons generates an amount of particles such as pion and kaons, which are the most commons, created by the jet particles that were created after the collision.
-Besides of the particles created by the quarks of the proton , gluons are also radiated and create new particles and photons are radiated too.
+Besides of the particles created by the quarks of the proton, gluons are also radiated and create new particles and photons are radiated too.
 \\
@@
 The Compact Muon Solenoid (CMS) is a detector with multiple uses in the LHC and part of the main experiments at CERN.
-Located underground in the France- Switzerland border , in the city of Cessy, France.
+Located underground in the France- Switzerland border, in the city of Cessy, France.
 This detector was designed in the early 1990s, based on the mass limit of the Higgs boson,  and put on operation in 2008,  it has a big solenoid that generates a great magnetic field of 4 teslas with the objective to separate particles after a particle collision.
- The detector is 21 metres long, 15 meters wide, 15 meters high ,it has a diameter of 5.9 m with a weight of 12000 ton.
-The reason for such a strong magnetic field is to obtain a better momentum resolution .
+ The detector is 21 metres long, 15 meters wide, 15 meters high, it has a diameter of 5.9 m with a weight of 12000 ton.
+The reason for such a strong magnetic field is to obtain a better momentum resolution.
  The magnetic flux is returned via a 1.5 m thick  iron yoke instrumented with four stations of muon
@@
 The CMS experiment is composed of several detector layers  that allow identify and save different types of energy signals  and it is saved in a powerful supercomputers that separate and classify the data according to certain variables.
-The general parts of the CMS are the Silicon Tracker , an Electromagnetic Calorimeter,a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
+The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter,a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
 \\
@@
 The Silicon Tracker is the first of the main subdetectors of CMS from inside to outside.
-The Tracker is composed of two sub components: Pixel and  Strip detectors.The outer radius of the  tracker is 110 cm, and its total length is 540 cm.
-The tracker coverage is $|\eta|<2.4$\footnote{$\eta$ , called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.\\
+The Tracker is composed of two sub components: Pixel and  Strip detectors.
+The outer radius of the  tracker is 110 cm, and its total length is 540 cm.
+The tracker coverage is $|\eta|<2.4$\footnote{$\eta$, called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.\\
 
@@
 %In the endcap section 2 pixel and microstrip layers are placed in each endcap.
-The endcap have 2 disks of radii from 6 to 15 cm placed at 34.6 and 46.5 cm in the z axis.The endcap disks comprise 672 pixel modules with 7
+The endcap have 2 disks of radii from 6 to 15 cm placed at 34.6 and 46.5 cm in the z axis.
+The endcap disks comprise 672 pixel modules with 7
 %different modules in each blade.
 The Strip Detector is divided in 4 sections: Tracker inner barrel (TIB), tracker outer barrel (TOB), tracker encap (TEC) and tracker inner disk (TID).
-The region that cover the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.The first two are composed  of silicon sensors layers of 4 and 6 layers respectively.
-The TEC has 9 disk extending in the region 120 cm > $|z|$ > 280 cm .The
+The region that cover the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.
+The first two are composed  of silicon sensors layers of 4 and 6 layers respectively.
+The TEC has 9 disk extending in the region 120 cm > $|z|$ > 280 cm.
+The
 TID comprises 3 small disks that fill the gap between the TIB and the TEC.
@@
 The crystals in the barrel have a pyramid shape and their cross section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
-The crystal length is 230 mm.The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\
+The crystal length is 230 mm.
+The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\
 
 The endcaps cover have the  range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has  identically shaped crystals grouped in
-mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$ ,and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
+mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
 \\
@@
 In the barrel, there photo detectors called avalanche photo diodes (APD), made of silicon with a active area of  5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.
-At the endcap , the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$) , allowing to operate in the magnetic field.
-VPT have a size of 25 mm in diameter , glued to the back of each crystal.\\
+At the endcap, the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$), allowing to operate in the magnetic field.
+VPT have a size of 25 mm in diameter, glued to the back of each crystal.\\
 
-There is also a preshower detector , which principal function  is to identify neutral pions in the
+There is also a preshower detector, which principal function  is to identify neutral pions in the
 endcaps within the region 1.653 < |$\eta$| < 2.6. It also helps the identification of electrons
@@
 
-The HB is an assembly of two half barrels, composed of 18 wedges.Each wedge has 17 active layers composed of scintillator tiles with 16 layers of 
-absorbent metal (brass and stainless steel).Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087. Light of scintillator is collected by a single wave
+The HB is an assembly of two half barrels, composed of 18 wedges. Each wedge has 17 active layers composed of scintillator tiles with 16 layers of 
+absorbent metal (brass and stainless steel). Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087. Light of scintillator is collected by a single wave
 length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm. 
@@
 
-HE is composed by brass absorbent plates ,with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.  HE is sectioned in 5 in $\phi$ to match the barrel wedges.
- .
+HE is composed by brass absorbent plates, with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.
+HE is sectioned in 5 in $\phi$ to match the barrel wedges.
 %HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is , the geometry of the barrel muon system.
@@
 %CSC is composed of 6 layers that measures the $\mu$ position in the r-$\phi$ coordinate plane. 
-The chambers use a gas mixture of 50$\%$ CO$_2$ , 40 $\%$ Ar and 10$\%$ CF$_4$. The muon endcap system comprises 468 CSCs in the 2 endcaps \cite{cms-manual,cms7}.
+The chambers use a gas mixture of 50$\%$ CO$_2$, 40 $\%$ Ar and 10$\%$ CF$_4$. The muon endcap system comprises 468 CSCs in the 2 endcaps \cite{cms-manual,cms7}.
 %Together with DT, cover the $|\eta|< 2.4$. These systems can each identify the collision crossing that generated the muon and trigger on (recolect) the transverse momentum ($p_T$). 
@@
 The RPC are located in the barrel and endcap regions that covers the range o $|\eta|<1.6$. The main purpose is to trigger events with muons. 
-RPC's are structured with a double gas filled gap and readout strips between the gaps .\\
+RPC's are structured with a double gas filled gap and readout strips between the gaps.\\
  The gas mix used in the RPC consist of 95.2$\%$ Freon

### 2019-10-16 tesis_hiram/Chapter3/chapter3.tex
final

@@
 But the events are only saved if they fulfill certain conditions compatible with the signal.
-For the tH process , the search is based on the presence of  a pair of muons with the same sign.
+For the tH process, the search is based on the presence of  a pair of muons with the same sign.
 The rest of the processes that also generates a pair of muons with the same sign will be considered backgrounds.
@@
 The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino.
-This is the main process that generates events with two same sign muons.The tH process topology is shown in the figure \ref{jet}.\\
+This is the main process that generates events with two same sign muons.
+The tH process topology is shown in the figure \ref{jet}.\\
 
@@
   %But also tH process can generate the final states from $\tau$ decays but with a low probability.
-Some of them have probability near zero , but not impossible .
+Some of them have probability near zero, but not impossible .
 %In graphics, these low probability processes would be very small figures that barely manifest.
@@
 		\includegraphics[scale=0.9]{Chapter1/jet.png}
-		\caption{Topology of $t$H process which generates two same sign muons , a forward jet and a b-jet.} 
+		\caption{Topology of $t$H process which generates two same sign muons, a forward jet and a b-jet.} 
 		\label{jet}
@@
 Table \ref{back} show the decay chains and production cross section for background.
-Due to small expected event yields, the processes $W^\pm$ $W^\pm$ ,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$   are grouped as one called Rares in the results below.
+Due to small expected event yields, the processes $W^\pm$ $W^\pm$, $tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$   are grouped as one called Rares in the results below.
 
@@
 \item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-\item For the Higgs processes $tH$ and $ttH$ , the uncertainty are due to the theoretical parameters used in that simulation.
+\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
 \end{itemize}

### 2019-10-16 tesis_hiram/Chapter4/chapter4.tex
final

@@
 The minimization is performed by using the package ROOFIT \cite{roofit}.
-In the figure \ref{simple} and Table \ref{table1} , shows the results of the model fitting using the Asimov data for both models.
+In the figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models.
 \\
@@
 	Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
-	To determine an upper limit on the strength parameter $\mu$ , we use the following statistical test
+	To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
 	\begin{align}
@@
 	In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$  such that $q$ remains below the shaded region shown in Fig. \ref{chi}, where $\alpha$=0.05 in this case. 
-	It is useful to scan $q$ as function of $\mu$ , which is normally a parabolic function as shown in \ref{scanl}.
+	It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in \ref{scanl}.
 In the SM case, the scan has a wider shape in comparison to the $k_t$=-1.
@@
 The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 finished in 2018.
-Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC , is expected to collect 3000 fb$^{-1}$ .
+Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC, is expected to collect 3000 fb$^{-1}$ .
 Therefore, is interesting to study the sensibility of the signal  strength to higher luminosities.

### 2019-10-16 tesis_hiram/Chapter5/chapter5.tex
final

@@
 
-MC simulation and real data or even only MC can be used to study sensitivity different signal processes.In this work we used the information published by CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
+MC simulation and real data or even only MC can be used to study sensitivity different signal processes.
+In this work we used the information published by CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
 In the SM case, the signal strength for the signal $tH$ is very low in comparison to

### 2019-10-17 tesis_hiram/Chapter1/chapter1.tex
final

--- 2019-10-15 tesis_hiram/Chapter1/chapter1.tex
@@
-%!TEX root = ../thesis.tex
+%!TEX root =../thesis.tex
 %*******************************************************************************
@@
 \renewcommand{\baselinestretch}{1.5}
-
+\nocite{*}
 \begin{chapter}{Introduction}
@@
 Standard Model (SM) is a theory that describes the fundamental forces (except gravity) and classify the elementary particles in bosons (entire spin) and fermions (half spin).
-The SM , created almost 50 years ago, has been the most successul theory in explain the phenomena in the subatomic world.
+The SM, created almost 50 years ago, has been the most successul theory in explain the phenomena in the subatomic world.
 \\
 
-One of the particles of the SM, the Higgs Boson , was recently discovered in 2012 in the ATLAS and CMS experiments at CERN.
-The discovery of Higgs boson in  proton proton collisions  marked a new era in the particle physics due to its characteristic  of giving the matter the property of mass, according to previous theories and predictions .
+One of the particles of the SM, the Higgs Boson, was recently discovered in 2012 in the ATLAS and CMS experiments at CERN.
+The discovery of Higgs boson in proton proton collisions marked a new era in the particle physics due to its characteristic of giving the matter the property of mass, according to previous theories and predictions.
 Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and differents Higgs production processes.
@@
 
-In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions , such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes.
+In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes.
 In this work, we will analize the production of Higgs boson in association with a
@@
 
-For the leptons we have electrons ($e$), muons ($\mu$), and taus ($\tau$) with charge -1 and their neutrinos $\nu_e, \nu_\mu,\nu_\tau$, are chargeless particles.
+For the leptons we have electrons ($e$), muons ($\mu$), and taus ($\tau$) with charge -1 and their neutrinos $\nu_e, \nu_\mu, \nu_\tau$, are chargeless particles.
 Leptons have their respective antiparticle; same structure with opposite charge.
@@
  Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. \\
-Mesons , are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
+Mesons, are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
 Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.
@@
 Quarks have characteristics such as electric charge, mass, color charge, and spin.
-The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down , strange and bottom quarks have charge of $-\frac{1}{3}$.
-Among them , the top quark is the most massive of all, while the up and down are the least massive.
+The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down, strange and bottom quarks have charge of $-\frac{1}{3}$.
+Among them, the top quark is the most massive of all, while the up and down are the least massive.
 The lepton and quarks have their respective antiparticle, which have the same mass, but inverted charge.\\ 
@@
 The last group of the family are the bosons,which have a spin 1 and 0. 
-There are 5 bosons: $W^{\pm}$ , $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered , is in charge of give the property of mass to particles via Higgs mechanism.
+There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism.
 Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}.
@@
 The Higgs boson was discovered recently on year 2012 in the experiments ATLAS and CMS at CERN.
-The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV ,where investigators worked on the data and detecting various decay modes that generates final states such  as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
+The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV,where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
 \\
@@
 Maskawa in 1973 to explain observed CP violations in Kaon decay\cite{griff}.
-On 1995, in the Tevatron at Fermilab in Illinois, the top quark  was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top} .
+On 1995, in the Tevatron at Fermilab in Illinois, the top quark was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
 Since then,the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.\\
@@
 But since the W boson have various decays, the top quark can generate many posible particles, acording to W boson decays.
-Some posible decays of top quark is the decay to a lepton such as muon, electron or tau and their neutrinos .
+Some posible decays of top quark is the decay to a lepton such as muon, electron or tau and their neutrinos.
 %The antitop, antiparticle of top quark, can decay to W$^{-1} \bar{b}$ and its decay is the same as top, but with inverse signal.
@@
 	0 \quad \text{i=j, or j=k, or k=i } 
-	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$ , $Z$ and $\gamma$ vector boson
+	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
 \cite{ew1}\cite{ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\
@@
 refer to the left (right) handed particles.\footnote{$\bar{\psi}$ denotes the adjoint spinor $\bar{\psi}=\psi^\dagger \gamma^0$.
-	$\cancel{D}=\gamma^\mu D_\mu$.
-$\gamma$ are the Dirac matrices}. 
+$\cancel{D}=\gamma^\mu D_\mu$. $\gamma$ are the Dirac matrices}. 
 The gauge covariant derivatives are given by
@@
 
-%The  charge of particle Q is given by $Q=T^3+Y$ with $Y$ the hypercharge and $T$ the third component of the weak isospin .
+%The charge of particle Q is given by $Q=T^3+Y$ with $Y$ the hypercharge and $T$ the third component of the weak isospin.
 For left handed doublets $T^3=\pm 1/2$ and $T^3=0$ for right handed singlets and the coefficients.
@@
 In this process, the creation of a Higgs boson comes from a intection via $t\bar{t}$.
-In the figure \ref{psu}, the $t\bar{t}H$ starts with 2 gluons which decay to two $t\bar{t}$ pairs and after that , the interaction $t\bar{t}$  generates a Higgs.
+In the figure \ref{psu}, the $t\bar{t}H$ starts with 2 gluons which decay to two $t\bar{t}$ pairs and after that, the interaction $t\bar{t}$ generates a Higgs.
 The last process, subject of study in this thesis, is the top Higgs ($tH$) process.
@@
 In particle physics, cross section ($\sigma$) describes the likelihood of two particles interacting under certain conditions.
- Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{2}$ .
+ Cross sections are expressed in barns, where 1 barn=$10^{-34}$ cm$^{2}$.
 \\
@@
 In order to get the number of events for a specific process, the reaction rate $N$ is determined by the total cross section $\sigma$ and the luminosity L.\\
-%L is called luminosity, that is the number of particle interactions can be produced in a detector per second . 
+%L is called luminosity, that is the number of particle interactions can be produced in a detector per second. 
 The unit of measurement of luminosity is cm$^{-2}$s$^{-1}$. Therefore, The reaction rate is
@@
 
-In the table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$ , that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
+In the table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
 
@@
 
-%For a particle that decays into several particle , $\Gamma$ is given by
+%For a particle that decays into several particle, $\Gamma$ is given by
 %\begin{align}\label{dm}
@@
 %\end{align}
-%where $m_n$ and $p_n$ are the mass and momentum of the particle n with n=1,2,3,...
-.
+%where $m_n$ and $p_n$ are the mass and momentum of the particle n with n=1,2,3,....
 S is a statistical factor that avoid identical particles counting.
-If there are no identical particles, S=1 ,and for identical particles $S=\frac{1}{s!}$ with s is the number of identical particles.
+If there are no identical particles, S=1,and for identical particles $S=\frac{1}{s!}$ with s is the number of identical particles.
 $\mathcal{M}$ is the amplitude which is a momenta function that is calculated acording to the Feynman diagrams.$\theta(p_j^0)$ is a Heaviside function,
@@
 (eds) Encyclopedia of Astrobiology.
-Springer, Berlin, Heidelberg} .
-The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV , but has not yet been measured due to the detector resolution\cite{cms-manual}.
+Springer, Berlin, Heidelberg}.
+The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV, but has not yet been measured due to the detector resolution\cite{cms-manual}.
 \\
@@
 diagrams in figure \ref{newth} provides a unique opportunity to study the relative sign of the coupling.
-In SM , the two diagrams interfere negatively and thereby suppress the production cross section.
+In SM, the two diagrams interfere negatively and thereby suppress the production cross section.
 Any deviation from the SM can lead to a large enhancement of the event rate.

### 2019-10-17 tesis_hiram/Chapter2/chapter2.tex
final

--- 2019-10-15 tesis_hiram/Chapter2/chapter2.tex
@@
-%!TEX root = ../thesis.tex
+%!TEX root =../thesis. Tex
 %*******************************************************************************
@@
 experiments installed along the LHC ring.
-One of them is ATLAS, located on Point 1 between the two injection lines , which is a general purpose detector.
+One of them is ATLAS, located on Point 1 between the two injection lines, which is a general purpose detector.
 At point 5 is another general purpose detector: the compact muon solenoid (CMS).
@@
 two tubes kept at ultrahigh vacuum. 
-By using of superconducting electromagnets that generates a powerful magnetic field , the beams are guided around the accelerator ring. 
-The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.For that, it is required to have  magnets to a temperature of  $‑271.3$ C.
+By using of superconducting electromagnets that generates a powerful magnetic field, the beams are guided around the accelerator ring. 
+The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
+For that, it is required to have magnets to a temperature of $‑271.3$ C.
 To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}
@@
 The Compact Muon Solenoid (CMS) is a detector with multiple uses in the LHC and part of the main experiments at CERN.
-Located underground in the France- Switzerland border , in the city of Cessy, France.
+Located underground in the France- Switzerland border, in the city of Cessy, France.
 This detector was designed in the early 1990s, based on the mass limit of the Higgs boson, and put on operation in 2008, it has a big solenoid that generates a great magnetic field of 4 teslas with the objective to separate particles after a particle collision.
- The detector is 21 metres long, 15 meters wide, 15 meters high ,it has a diameter of 5.9 m with a weight of 12000 ton.
-The reason for such a strong magnetic field is to obtain a better momentum resolution .
+ The detector is 21 metres long, 15 meters wide, 15 meters high, it has a diameter of 5.9 m with a weight of 12000 ton.
+The reason for such a strong magnetic field is to obtain a better momentum resolution.
  The magnetic flux is returned via a 1.5 m thick iron yoke instrumented with four stations of muon
@@
 The CMS experiment is composed of several detector layers that allow identify and save different types of energy signals and it is saved in a powerful supercomputers that separate and classify the data according to certains variables.
-The general parts of the CMS are the Silicon Tracker , an Electromagnetic Calorimeter,a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
+The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter, a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
 \\
@@
 The Silicon Tracker is the first of the main subdetectors of CMS from inside to outside.
-The Tracker is composed of two sub components: Pixel and  Strip detectors.The outer radius of the  tracker is 110 cm, and its total length is 540 cm.
-The tracker coverage is $|\eta|<2.4$\footnote{$\eta$ , called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.\\
+The Tracker is composed of two sub components: Pixel and Strip detectors.
+The outer radius of the tracker is 110 cm, and its total length is 540 cm.
+The tracker coverage is $|\eta|<2.4$\footnote{$\eta$, called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.\\
 
@@
 %In the endcap section 2 pixel and microstrip layers are placed in each endcap.
-The endcap have 2 disks of radii from 6 to 15 cm placed at 34.6 and 46.5 cm in the z axis.The endcap disks comprise 672 pixel modules with 7
+The endcap have 2 disks of radii from 6 to 15 cm placed at 34.6 and 46.5 cm in the z axis.
+The endcap disks comprise 672 pixel modules with 7
 %different modules in each blade.
 The Strip Detector is divided in 4 sections: Tracker inner barrel (TIB), tracker outer barrel (TOB), tracker encap (TEC) and tracker inner disk (TID).
-The region that cover the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.The first two are composed  of silicon sensors layers of 4 and 6 layers respectively.
-The TEC has 9 disk extending in the region 120 cm > $|z|$ > 280 cm .The
+The region that cover the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.
+The first two are composed of silicon sensors layers of 4 and 6 layers respectively.
+The TEC has 9 disk extending in the region 120 cm > $|z|$ > 280 cm.
+The
 TID comprises 3 small disks that fill the gap between the TIB and the TEC.
@@
 The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
-The crystal length is 230 mm.The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\
+The crystal length is 230 mm.
+The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\
 
 The endcaps cover have the range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has identically shaped crystals grouped in
-mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$ ,and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
+mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
 \\
@@
 In the barrel, there photo detectors called avalanche photo diodes (APD), made of silicon with a active area of 5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.
-At the endcap , the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$) , allowing to operate in the magnetic field.
-VPT have a size of 25 mm in diameter , glued to the back of each crystal.\\
+At the endcap, the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$), allowing to operate in the magnetic field.
+VPT have a size of 25 mm in diameter, glued to the back of each crystal.\\
 
-There is also a preshower detector , which principal function  is to identify neutral pions in the
+There is also a preshower detector, which principal function is to identify neutral pions in the
 endcaps within the region 1.653 < |$\eta$| < 2.6. It also helps the identification of electrons
@@
 
-The HB is an assembly of two half barrels, composed of 18 wedges.Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel).Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087.
+The HB is an assembly of two half barrels, composed of 18 wedges.
+Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel).
+Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087.
 Light of scintillator is collected by a single wave
@@
 
-HE is composed by brass absorber plates ,with the thickness of 78 mm, and a total of  19 scintillator layers with a thickness of 3.7 mm.  HE is sectioned in 5 in $\phi$ to match the barrel wedges.
+HE is composed by brass absorber plates, with the thickness of 78 mm, and a total of 19 scintillator layers with a thickness of 3.7 mm. HE is sectioned in 5 in $\phi$ to match the barrel wedges.
 .
-%HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is , the geometry of the barrel muon system.
+%HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is, the geometry of the barrel muon system.
 Divided by 5 rings of 2.54 wide, composed of the scintillators on either side of the tail catcher iron of 18cm thick at radial distances of 3850 and 4097 mm respectively.
@@
 There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
-steel absorbers and embedded radiation hard quartz fibers,which collects 
+steel absorbers and embedded radiation hard quartz fibers, which collects 
 Cherenkov light\cite{cms-manual}.% that is when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 
@@
 
-The HCAL measures the energy of hadrons,such as the pions and kaons. 
+The HCAL measures the energy of hadrons, such as the pions and kaons. 
 The energy resolution of the HCAL was estimated using a test beam of pions. For 100 GeV pions, the resolution obtained is 12$\%$.
@@
 %The process utilized in the CMS muon chamber systems is gas ionization.
-Those gas-ionization particle detectors are arranged in a cylindrical barrel region and planar endcaps, in order to meet the geometry of the solenoid.The barrel detector is built with 4 layers of 250 chambers inside the magnet return yoke.\cite{cms-manual}
+Those gas-ionization particle detectors are arranged in a cylindrical barrel region and planar endcaps, in order to meet the geometry of the solenoid.
+The barrel detector is built with 4 layers of 250 chambers inside the magnet return yoke.\cite{cms-manual}
 The Muon Detector has three main subdetectors: the drift tubes chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
@@
  %The vertical lines represent the endcap and the horizontal the muon barrel.
-The orange sections are the DTs , where the 4 DTs are labeled MB,CSC marked in green are labeled ME or muon endcap and RPC are the blue lines that are located in the barrel and the endcap.
+The orange sections are the DTs, where the 4 DTs are labeled MB,CSC marked in green are labeled ME or muon endcap and RPC are the blue lines that are located in the barrel and the endcap.
 RPC are labeled RB and RE respectively.

### 2019-10-17 tesis_hiram/Chapter3/chapter3.tex
final

--- 2019-10-15 tesis_hiram/Chapter3/chapter3.tex
@@
 But the events are only saved if they fulfill certain conditions compatible with the signal.
-For the tH process , the search is based on the presence of  a pair of muons with the same sign.
+For the tH process, the search is based on the presence of a pair of muons with the same sign.
 The rest of the processes that also generates a pair of muons with the same sign will be considered backgrounds.
@@
  %But also tH process can generate the final states from $\tau$ decays but with a low probability.
-Some of them have probability near zero , but not impossible .
+Some of them have probability near zero, but not impossible.
 %In graphics, these low probability processes would be very small figures that barely manifest.
@@
 Table \ref{back} show the decay chains and production cross section for background.
-Due to small expected event yields, the processes $W^\pm$ $W^\pm$ ,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$   are grouped as one called Rares in the results below.
+Due to small expected event yields, the processes $W^\pm$ $W^\pm$,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$ are grouped as one called Rares in the results below.
 
@@
 \begin{table}[!ht]
-	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm , \tau^\pm$.}
+	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
 	\begin{tabular}{|l|c|c|}
@@
 \item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-\item For the Higgs processes $tH$ and $ttH$ , the uncertainty are due to the theoretical parameters used in that simulation.
+\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
 \end{itemize}
 
-%control region: event selection with 3 leptons for compare simulation with real data. yield difference  in that region is 50 .is taken  and for wz is 50
+%control region: event selection with 3 leptons for compare simulation with real data. yield difference in that region is 50. Is taken and for wz is 50
 %selection that allows to isolate a background respect to other backgrounds, that background allows to compare with real data

### 2019-10-17 tesis_hiram/Chapter4/chapter4.tex
final

@@
 The uncertainty of the signal strength is estimated by applying a fit to the Asimov dataset, where the model
-	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and Gaussian constraints for the systematical uncertainties in the model.
+	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and gaussian constraints for the systematical uncertainties in the model.
 
@@
 		\end{minipage}
-		\caption{Post-fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
+		\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
 			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
@@
 		\centering
-		\caption{Post-fit  yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
+		\caption{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
 		\begin{tabular}{ccc}
@@
 The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 finished in 2018.
-Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC, is expected to collect 3000 fb$^{-1}$ .
+Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC, is expected to collect 3000 fb$^{-1}$.
 Therefore, is interesting to study the sensibility of the signal strength to higher luminosities.
@@
 The increase of luminosity reduces the uncertainty of $\mu$ that is visualized in the likelihood graphs.
-	%The upper limits reduces as the luminosity increases; from 150 to 3000 fb $^{-1}$, the upper limit reduces in $\Delta\mu$=12.7 with $\Delta\mu$ the change of $\mu$ .
+	%The upper limits reduces as the luminosity increases; from 150 to 3000 fb $^{-1}$, the upper limit reduces in $\Delta\mu$=12.7 with $\Delta\mu$ the change of $\mu$.

### 2019-10-21 presentacion_hiram/presentacion-tesis.tex
presentacion

\documentclass[11pt]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{array}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{caption}
\usepackage{multicol}
\usepackage{listings}
\usepackage{alltt}
\usepackage{mathtools}
\usepackage[makeroom]{cancel}
\usetheme{Frankfurt}
\usepackage{tikz}
\usetikzlibrary{patterns}
\usetikzlibrary{plotmarks}
\titlegraphic{\vspace{8cm}}% to push the other text to the top
\addtobeamertemplate{navigation symbols}{}{%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber/\inserttotalframenumber
	\setbeamercolor{footline}{fg=blue}
	\setbeamerfont{footline}{series=\bfseries}
}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\begin{document}
	\author{
		Departamento de Investigacion en F\'isica \\
		Maestr\'ia en Ciencias (F\'isica)\\
		Hiram Ernesto Dami\'an}
	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
	%\subtitle{}
%	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
	\institute{Universidad de Sonora}
	%\date{}
	%\subject{}
	\newcommand{\subf}[2]{%
		{\small\begin{tabular}[t]{@{}c@{}}
				#1\\#2
		\end{tabular}}%
	}
	%\setbeamercovered{transparent}
	%\setbeamertemplate{navigation symbols}{}
	\begin{frame}
	\titlepage
\end{frame}

\begin{frame}
\tableofcontents
\frametitle{Contenido}
\end{frame}

\begin{frame}
\section{Overview and motivation}
\frametitle{Overview}
\begin{itemize}
\item Through this project we will investigate the production of Higgs boson in association with a
single top quark ($tH$) in proton-proton collisions. 
This mechanism of production of the Higgs boson has not been observed before by any
experiment.

\item Understanding the production of the Higgs boson, as well as its decays are an important part
of the physical program of the CERN international laboratory experiments that try to complete
the tests to verify the Standard Model, the theory of the fundamental particles
\item Making predictions for futures measurements.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Motivation  for single top Higgs (tH)}
\begin{itemize}
\item Coupling measurement is essential to establish the nature of the Higgs
\item The exploration of Higgs production on the $tH$ channel is subject relatively new. Measurements of CMS and ATLAS are compatible with SM predictions.
\item The $tH$ study explores the relative sign of top-Higgs  and W-Higgs couplings.\\ Small deviations from SM predictions could be associated with physics beyond the
standard model (BSM) such as String Theory and  Supersymmetry.
\end{itemize}
\end{frame}

\begin{frame}
\section{Higgs theory}
\frametitle{Standard Model}
\begin{center}
\begin{figure}
	\includegraphics[width=9cm,height=6.5cm]{figures/sm1.png}
\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Particles Properties}
Table of particles in SM
\begin{table}
\tiny{\renewcommand{\arraystretch}{1.5}
\begin{tabular}{|c|c|c|c|c|c|}
	\hline 
Particle	&Mass (MeV/$c^2$)  &Charge  & spin &Lifetime (s)  & Distance in lifetime (meters) \\ 
	\hline 
Up (u)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable &  -\\ 
	\hline 
Charm (c)	& 1280 &$\frac{2}{3}$  &  $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ &  5.21$\times 10^{-3}$ \\ 
	\hline 
Top	(t)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$  & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$   \\ 
	\hline 
Down (d)	& 4.6 &$-\frac{1}{3}$  & $\frac{1}{2}$  & Stable & - \\ 
	\hline 
Strange (s)	& 96 &$-\frac{1}{3}$  & $\frac{1}{2}$  &$1.24 \times 10^{-8}$  & 58.7 \\ 
	\hline 
Bottom (b)	& 4180 &$-\frac{1}{3}$  &  $\frac{1}{2}$ &$1.3 \times 10^{-12}$   & 6.16 $\times 10^{-3}$\\ 
	\hline 
W 	& 80379 &$\pm$1  & 1 & 3$\times$ 10$^{-25}$ &  1.42$\times 10^{-15}$\\ 
	\hline 
Z & 91187.6 &0  & 1 & 3$\times$ 10$^{-25}$  &1.42$\times 10^{-15}$ \\ 
\hline
Photon ($\gamma$) & 0 &0  &  1&Stable  & - \\ 
\hline
Gluon (g)	& 0 &0  &  1&Stable  & - \\ 
	\hline 
Higgs (H)	& 125.18 &0  &  0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
	\hline 
Electron (-e)& 0.511 & -1 &   $\frac{1}{2}$& Stable & - \\ 
	\hline 
Muon ($\mu$)	& 105.7 & -1  &  $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
	\hline 
$\tau$	& 1776.86 &-1  &  $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 
	\hline 
$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 &  $\frac{1}{2}$ & Stable &  -\\ 
	\hline 
\end{tabular} 
}
\end{table}
\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
\end{frame}

\begin{frame}
\frametitle{Electroweak SM Lagrangian}
The Standard Model is a theory of fields for particles with spins 0, $\frac{1}{2}$ and 1. 
The  SM lagrangian 	
\begin{align*}
\mathcal{L}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{higgs} + \mathcal{L}_\text{yukawa}
\end{align*}
donde 
\begin{itemize}
	\item $\mathcal{L}_\text{gauge}$=$ -\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[G^{i\mu\nu}G^i_{\mu\nu}\right]$ 
	\begin{itemize}
		\item  $F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu $
		\item  $G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu $
	\end{itemize}
	\item $\mathcal{L}_f=i\bar{\Psi}_L \cancel{D}{\Psi}_L+i\bar{\psi}_R \cancel{D}{\psi}_R  $ is the kinematic term for fermions 
\scriptsize{
	\begin{itemize}
		\item $D_\mu {\Psi}_L=\left(\partial_\mu+igW_\mu+ig'Y_LB_\mu\right)\Psi_L$
		\item $D_\mu \psi_R=\left(\partial_\mu +ig' Y_RB_\mu\right)\psi_R $
		\item g and g' are boson coupling constants.
%\footnote{\tiny{L(R) refers to Left and right fields.
%Y is the  weak hypercharge,Y=T$^3$-Q.Q is charge of particle field and T is weak isospin. $T^3=\pm 1/2$ for left handed doublets and $T^3=0$ for right handed singlets.} }
\item $W_\mu=\sigma^iW^i_\mu$, where $\sigma^i$ are the pauli matrices.
	\end{itemize}
}
\end{itemize}
%\begin{equation}
%\begin{split}
%\mathcal{L}=-\frac{1}{2}\text{Tr}\left[F^{\mu\nu}F_{\mu\nu} \right]+\bar{\Psi_L}i\gamma^\mu D_\mu \Psi_L  
%+\text{Tr}\left[(D_\mu \Phi)^\dagger (D^\mu \Phi)\right]+\mu^2 \Phi^\dagger \Phi  \\
%-\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2 & +\left(\frac{1}{2}\Psi_L^T Ch \Phi \Psi_L +h.c \right)
%\end{split}
%\end{equation}
%The matrix C in the last term is the charge conjugation matrix acting on the spinors, h is a matrix of Yukawa couplings
\end{frame}

\begin{frame}
\frametitle{Electroweak SM Lagrangian}
Higgs lagrangian 
\begin{align}
\mathcal{L}_{\text{Higgs}}=(D_\mu \Phi)^\dagger (D^\mu \Phi)-V(\Phi^\dagger \Phi)
\end{align}

with
\begin{itemize}
	\item $D_\mu \Phi = \left(\partial_\mu+(ig/2)\sigma^iW^i_\mu-i\frac{1}{2} g' B_\mu \right) \Phi $
	\item $V(\Phi^\dagger \Phi)=-\mu^2 \Phi^\dagger \Phi +\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2, \quad \mu^2>0  $ 
	\item $\Phi=\left(\begin{array}{c}
	\phi^+ \\
	\phi^0
	\end{array} \right)  $ is a SU(2) doublet.
	\item $\sigma^i$ are the Pauli matrices.
\end{itemize}

\begin{itemize}
	\item $\Phi$ is higgs field which is a complex scalar field. $\Phi$
	%\item  W$_\mu$ and B$_\mu$ are gauge bosons
	%\item g and g are boson coupling constants.
	\item $\lambda $ and $\mu^2$ are Higgs potential parameters
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SM Lagrangian}
Yukawa lagrangian
\begin{align}
\mathcal{L}_{yukawa}=\Gamma^u_{mn}q_{m\text{,}L} \tilde{\phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \phi e_{n\text{,}R}+h.c
\end{align}
\scriptsize{where h.c is hermitian conjugate. m and n are flavors of quarks and leptons.
\\
The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between higgs doublet $\phi$ and the fermions.\\
Choosing}
\begin{align*}
\Phi=-\frac{1}{2}\left(\begin{array}{c}
0 \\
v+h
\end{array} \right) \rightarrow  \Phi=\frac{1}{2}\left(\begin{array}{c}
0 \\
v
\end{array} \right) %\equiv v
\end{align*}
\scriptsize{
By using it on the first part of 
the lagrangian it is obtained for u quark} 
\begin{align*}
\mathcal{L}_{yukawa}=\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
\end{align*}
\scriptsize{
from here the mass of $u$ quark}
\begin{align*}
m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
\end{align*}
\end{frame}

\nologo{
\begin{frame}
\section{$tH$ mechanisms}
\frametitle{Higgs production mechanisms}
\begin{center}
\includegraphics[scale=0.4]{figures/pg.png}
\end{center}
\small{Different Higgs production mechanism, from the most likely to least likely}
\end{frame}
}
\begin{frame}
\frametitle{$tH$ production mechanisms}
\begin{center}
\begin{figure} 
\includegraphics[scale=0.4]{figures/tq.png} 
\caption{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
\label{th}
\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{$tH$ production mechanisms}
\begin{itemize}
\item In a proton proton collision, the production cross section of the single top plus Higgs boson process is driven by a
destructive interference of two main diagrams (see Fig. \ref{th}.), where the Higgs couples to either
the W boson or the top quark. 
\item  A second process, where the Higgs and top quark
are accompanied by a W boson ($tH$W) has similar behavior, albeit with a weaker interference
pattern.
\item However, in the presence of new physics, there may be relative opposite signs between the $tH$
and WH couplings which lead to constructive interference and enhance the cross sections by
an order of magnitude or more.
\end{itemize}
\end{frame}

\begin{frame}
\section{Production cross section}
\frametitle{Cross section}
\begin{itemize}
\item Classical definition: When two particles interact, cross section is the area transverse to their relative motion within
which they must meet in order to scatter from each other.
\item Quantum definition: Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
\item Experimentally
\begin{align}
d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
\end{align}
\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Cross section}
\begin{center}\begin{center}

	\end{center}
	\begin{figure}
		\includegraphics[scale=0.5]{figures/cs1.png}
		\caption{Drawing of an idealized scattering process showing the differential solid angle $\Delta\Omega$ and the
			scattering angle $\theta$}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Cross section}
The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
\begin{align}
N_R=\sigma \text{L}
\end{align}
\end{frame}

\begin{frame}
\frametitle{Higgs production Cross section}
\begin{table}
	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
	\begin{tabular}{|c|c|c|}
		\hline
		Production mechanism &
		$\sigma$ (picobarns pb)
		&Number of events \\
		\hline
		ggF &
		48.93 &
		1756587\\
		\hline
		VBF &
		3.78&
		135702\\
		\hline
		WH & 1.35 & 48465\\
		\hline
		ZH &0.88 & 31592\\
		\hline
		t$\bar{t}$H &
		0.50&
		18255\\
		\hline
		$tH$	(only)&
		0.015&
		560.39\\
		\hline
	\end{tabular}
\end{table}

\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}

\end{frame}

\begin{frame}
\frametitle{Higgs production cross section}
\begin{center}
\begin{figure}
\includegraphics[scale=0.42]{figures/7-14xsec.eps}
\caption{ Higgs boson production cross sections as a function of the centre-of-mass-energies}	
\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Branching ratio}
\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes. \footnotemark.}
\begin{align}
\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
\end{align}
\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
\end{frame}

\begin{frame}
\frametitle{Higgs Branching ratio}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.35]{figures/Higgs_BR_120-130_7.eps}
		\caption{Standard Model Higgs boson decay branching ratios}	
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\section{Higgs Branching ratios }
\frametitle{Higgs Branching ratios per channel}
\begin{table}
	\caption*{SM Higgs boson branching ratios for  $M_H$ =125 GeV}
\begin{center}
\begin{tabular}{|c|c|}
	\hline
	Higgs decay & Branching ratio (BR)\\
	\hline
	H $\rightarrow$ b$\bar{b}$ &
	$50.82\%$ \\
	\hline
	H $\rightarrow$ $W^+W^-$ &
	$21.5\%$ \\
	\hline
	H $\rightarrow$ $\tau^+ \tau^-$ &
	$6.27\%$\\
\hline
	H $\rightarrow$ ZZ &
$2.61\%$\\
\hline
	H $\rightarrow$ $\gamma\gamma$ &
$0.227\%$\\
\hline
	H $\rightarrow$ Z$\gamma$ &
$0.153\%$\\
\hline
	H $\rightarrow$ $\mu^+\mu^-$ &
$0.0217\%$\\
\hline
\end{tabular}
\end{center}
\end{table}

\end{frame}

\begin{frame}
\frametitle{$\mu\mu$ same sign decay rate}
\tiny{Table of decay chains for tH.  Expected number of final events assuming 560 produced $tH$ events.l represents $\mu^{\pm},e^- , \tau^\pm$. }
\begin{table}
\renewcommand{\arraystretch}{0.55}
\begin{tabular}{|p{8cm}|p{1.3cm}|c|}
\hline
Decay chain &BR&Events\\
\hline 
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  1.173  \\
\hline
\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.899 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.203 \\
\hline
\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.105  \\
\hline
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
\tiny{1.681 $\times$10$^{-4}$} & 0.094 \\
\hline
\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.017\\
\hline
\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.011\\
\hline 
\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.008  \\
\hline
%\tiny{$tH \rightarrow$W$^+$bZ$\gamma$ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- \gamma$} & \tiny{6.888$\times$10$^{-6}$}&0.003\\
%\hline 
%\tiny{$tH \rightarrow$W$^+$bZZ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- l^+l^-$} &\tiny{3.962$\times$10$^{-6}$ }&0.002\\
%\hline 
%%\tiny{$tH \rightarrow$ $\tau \nu_\tau $bZ$\gamma$ $\rightarrow$ $\mu^- \bar{\nu_\mu} \nu_\tau \nu_\tau$ b $\mu^+ \mu^- \gamma$} & 6.347$\times$10$^{-7}$ & 0.0003\\
%%\hline 
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{LHC}
\begin{center}
	\begin{figure}
	\includegraphics[scale=0.25]{figures/CERN's-accelerator-complex2013.jpg}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{LHC parameters}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.5]{figures/lhc-t.png}
		\caption*{Table. LHC characteristics for run 2.}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{LHC}
\begin{table}
	\caption*{Accelerator operation energies}
	\begin{tabular}{|c|c|}
		\hline
		Accelerator & Energy \\
		\hline
		Linac 2 &  50 MeV \\
		\hline
		PS Booster & 1.4 GeV \\
		\hline
		Proton Scyncroton (PS) & 25 GeV\\
		\hline
		SPS &  450 GeV\\
		\hline
		LHC & 6.5 TeV\\
		\hline
	\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{CMS detector}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.08]{figures/cms.png}
		\caption{Compact muon solenoid}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{CMS integrated luminosity}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.3]{figures/cms_lumi.png}
		\caption{Integrated luminosity for CMS experiment }
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Topology of events tH}
The characteristics of the signal $tH$:

\begin{multicols}{2}
\tiny{
\begin{itemize}
\item t$\rightarrow$W$^+$b$\rightarrow$ $l^+ \nu_\mu$b
\item H$\rightarrow$ W$^+$W$^-$

\begin{list}{--}{}
\item  \tiny{W$\rightarrow$ $l^\pm \nu$, where l can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
\item   \tiny{W$\rightarrow$ q$\bar{q}$}
\item \tiny{W bosons decay leptonically resulting in a signature of two same-sign leptons }
\end{list}
\item a light-flavor quark 
\item  b quark jet  \cite{2}
\end{itemize}
}
\columnbreak
\begin{figure}
	\centering
	\includegraphics[scale=0.5]{figures/jet.png}
\end{figure}
\end{multicols}
\end{frame}

\begin{frame}
\frametitle{Event selection}
The main analysis strategy is to obtain a selection of events compatible with
certain characteristics of the signal at pre-selection level.\\

It is required:
\begin{itemize}
\item The events are selected those that contain two leptons ($l^+l^-$)  with the same sign.
\item Transverse moment $p_{t}$ > 25 and 15 GeV, for the muons.
\item A foward jet with $p_t$ > 40 GeV, | $\eta$ | > 2.4
\item One or more b-jets with (| $\eta$ | <2.4)\cite{1}
\end{itemize}
\end{frame}

\nologo{
\begin{frame}
\frametitle{Previous results for t$\bar{t}$H+$tH$ production}
\begin{multicols}{2}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.4]{figures/tth-table.png}
		\caption*{}
	\end{figure}
\end{center}
\columnbreak
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.3]{figures/bdt.png}
		\caption*{\tiny{Post-fit categorized BDT classifier outputs as used in
			the maximum likelihood fit for the $\mu\mu$ channel for
			35.9 fb$^{-1}$.In the box below each distribution, the ratio
			of the observed and predicted event yields is shown.\cite{2}
		 }}
	\end{figure}
\end{center}
\end{multicols}
\end{frame}
}
\begin{frame}
	\begin{center}
		\begin{figure}
			\includegraphics[scale=0.3]{figures/sc.png}
			\caption{Observed and expected 95$\%$ C.L. upper limit on the $tH$ + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ . The expected limit is derived from a background-only MC dataset.}
		\end{figure}
	\end{center}
\end{frame}

\begin{frame}
\frametitle{Main backgrounds}
\begin{center}
\scriptsize{
\begin{tabular}{|c|c|p{7cm}|}
	\hline
	Background & $\sigma$[pb] & Decay process \\
	\hline
t$\bar{t}$H	& 0.2151 & t$\bar{t}$H $\rightarrow$ W$^+$b W$^- \bar{b}$ W$^+$W$^-$ $\rightarrow$ $\mu^+ \nu_\mu$b$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
\hline  
t$\bar{t}$W  &0.2043 &t$\bar{t}$W  $\rightarrow$  W$^+$bW$^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
\hline
 t$\bar{t}$Z & 0.2529 & t$\bar{t}$Z  $\rightarrow$ W$^+$b  W$^-$$\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$  \\
 \hline 
  W$^+$W$^-$  &1.64 & W$^+$W$^-$ $\rightarrow$$\mu^+\nu_\mu$$\mu^-\bar{\nu_\mu}$ \\
    \hline 
  tZq  &0.0758 & tZq$\rightarrow$W$^+$b$\mu^+ \mu^-$ q$\rightarrow$$\mu^+ \nu_\mu$b $\mu^+\mu^-$ q \\
    \hline 
  t$\bar{t}$t$\bar{t}$  & 0.0091&t$\bar{t}$t$\bar{t}$ $\rightarrow$ W$^+$b   W$^- \bar{b}$  W$^+$b  W$^- \bar{b}$   $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$b   $\mu^- \bar{\nu_\mu} \bar{b}$ \\
    \hline 
  W$^+$W$^-$Z  & 0.1651& W$^+$W$^-$Z$\rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
    \hline 
 ZZZ  &0.0139 & ZZZ$\rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$  \\
    \hline 
  W$^+$ZZ  & 0.0556&W$^+$ZZ$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
  \hline 
 W$^+$Z &4.42965 &W$^+$Z$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
 \hline
ZZ &  1.256 &ZZ$\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
 \hline
\end{tabular}
}
\end{center}
\tiny{
\begin{itemize}
	\item Rare SM: tttt,WWW,WWZ,WZZ,WW,tZq
	\item WZ:WZ,ZZ
\end{itemize}}
\end{frame}

\begin{frame}
\frametitle{Boosted decision tree (BDT)}
\begin{itemize}
\item A decision tree takes a set of input features and splits input data recursively based on
those features.
Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
\item The BDT training is performed using several event variables for signal and background. 
	\item BDT training uses MC samples for  t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V),
	because t$\bar{t}$V is one of the biggest backgrounds
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{BDT Variables}
\begin{itemize}
\item	Trailing lepton $p_{t}$
\item 	Total charge of tight leptons
\item 	min $\Delta$R (lepton pairs)
\item 	$\Delta\phi$ between highest $p_t$ lepton pair
\item 	Number of jets with |$\eta$| < 2.4
\item	Number of non b-tagged jets with |$\eta$| > 1.0
\item	Maximum |$\eta$| for jets
\item	$\Delta\eta$ (most forward light jet, closest lepton)
\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Uncertainty values}
Common uncertainties for MC :
\begin{itemize}
	\item Muon identificacion 6$\%$
	\item Dimuon Trigger  1$\%$ 
	\item Luminosity measurement: ~2.6$\%$.
\end{itemize}
\begin{table}
			\renewcommand{\arraystretch}{0.1}
	\begin{tabular}{|c|M{2.7cm}|M{2.3cm}|}
\hline
\scriptsize{Background}& \scriptsize{Sources of systematic uncertainty}& \scriptsize{Total Systematic Uncertainty} \\
\hline
\rule{0pt}{3pt}t$\bar{t}$H  &{\begin{itemize} \tiny{ 
 	\item PDF 4$\%$ \\
 	\item QCD scale 5.8$\%$ \\
 	\item Higgs BR  1$\%$ }
\end{itemize}}  & 9.36$\%$ \\
 \hline  
 t$\bar{t}$Z&{\begin{itemize} \tiny{ 
 			\item PDF 4$\%$ \\
 			\item QCD scale 10$\%$ \\
 			 }
 \end{itemize}} & 12.36 $\%$ \\
 \hline
 t$\bar{t}$W&{\begin{itemize} \tiny{ 
 			\item PDF 4$\%$ \\
 			\item QCD scale 12$\%$ \\
 		}
 \end{itemize}} &14.03 $\%$ \\
 \hline
\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\begin{table}
		\renewcommand{\arraystretch}{0.1}
	\begin{tabular}{|c|M{2.7cm}|M{2.3cm}|}
\hline
\scriptsize{Background}& \scriptsize{Sources of systematic uncertainty}& \scriptsize{Total Systematic Uncertainty} \\
		\hline
	 \tiny{Rares SM} & {\begin{itemize} \tiny{
				\item Rare SM 50$\%$ }
	\end{itemize}}&50.36 $\%$ \\
	\hline
	\tiny{WZ} & {\begin{itemize}\tiny{
				\item Sample modelling and statistics 50$\%$ }
	\end{itemize}} & 50.36$\%$ \\
	\hline 
	\tiny{Non prompt leptons} &{\begin{itemize} \tiny{
				\item Fake rate estimation 50$\%$
				\item Closure 7$\%$ }
	\end{itemize}} 		 & 50.48$\%$ \\
	\hline 
	\end{tabular}
\end{table}

\end{frame}

\begin{frame}
\section{Fitting}
\frametitle{Fitting}
	\begin{center}
	\begin{figure}
		\includegraphics[width=10.5cm]{figures/fit-box.png}
		\caption*{}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Likelihood model}
The likelihood function is the product of Poisson probabilities for all bins
\begin{align}
L(\mu,\theta)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)}
\end{align}

\begin{itemize}
	\item	N=number of bins
	\item	$\mu$=parameter of signal
	\item	s=signal
	\item	b=background
	\item	n=number of events
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Results}
\framesubtitle{Likelihood scan}
To test a hypothesized value of $\mu$ we consider the profile likelihood ratio
\begin{align}
\lambda(\mu)=\frac{L(\mu,\hat{\hat{\theta}})}{L(\hat{\mu},\hat{\theta})}
\end{align}
\small{
	\begin{itemize}
		\item Here $\hat{\hat{\theta}} $ in the numerator denotes the value of $\theta$ that maximizes L for the specified $\mu$,
		it is the conditional maximum-likelihood (ML) estimator of $\hat{\theta}$ (and thus is a function of $\mu$).
		The denominator is the maximized (unconditional) likelihood function, i.e., $\hat{\mu}$ and $\hat{\theta}$ are
		their ML estimators\cite{3}. 
		\item The presence of the nuisance parameters broadens the profile likelihood as a
		function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
		of information about $\mu$ due to the systematic uncertainties\cite{3}\cite{4}. 
	\end{itemize}
}
\end{frame}

\begin{frame}
\frametitle{Statistical test}
It is convenient to use the statistic
\begin{align}
t_\mu=-2\ln{\lambda(\mu)} 
\end{align}
as the basis of a statistical test. Higher values of $t_\mu$ thus correspond to increasing
incompatbility between the data and $\mu$.
We may define a test of a hypothesized value of $\mu$ by using the statistic $t_\mu$ directly
as measure of discrepancy between the data and the hypothesis, with higher values of
$t_\mu$ correspond to increasing disagreement\cite{4}
\end{frame}

\begin{frame}
\frametitle{Results}
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/kin.png}
		\caption*{\tiny{Pre-fit signal and background yields for tH process. In the
			box below each distribution, the ratio of the observed and predicted event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}\hfill \quad
\begin{minipage}{0.4\textwidth}
	\begin{center}
	\begin{figure}
		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
		\caption*{\tiny{Post-fit signal and background yields for tH process. In the
			box below each distribution, the ratio of the observed and predicted event yields is shown}}
	\end{figure}
\end{center}
\end{minipage}
\end{frame}

\begin{frame}
\section{Results}
\frametitle{Results}
\begin{table}
	\caption{Prefit and postfit table for each yield.}
\begin{tabular}{|c|c|c|}
	\hline
	Process  & Number of events prefit    & Number of events Postfit \\
	\hline
	tH & 2.13   & 5.33$\pm$27.39\\
	\hline
	t$\bar{t}$H  &  24.18 $\pm$ 2.26 & 24.81 $\pm$ 2.24 \\
	\hline
	t$\bar{t}$W  &  68.03 $\pm$ 9.54 & 76.99 $\pm$ 8.76\\
	\hline
	t$\bar{t}$Z  & 25.89 $\pm$ 3.20 & 26.74 $\pm$ 3.18\\
	\hline
	Rares SM & 18.33 $\pm$ 9.23 & 20.31 $\pm$ 9.26\\
	\hline
	WZ & 15.07 $\pm$ 7.59 & 15.94 $\pm$ 7.46\\
	\hline
	fakes  & 80.94 $\pm$ 40.86  & 100.16 $\pm$ 29.32\\
	\hline
\end{tabular}	
\end{table}

 Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
\end{frame}

\begin{frame}
\frametitle{Results}
		\begin{figure}
			\begin{minipage}{0.4\textwidth}
				\centering
			\includegraphics[width=5.5cm,height=5cm]{figures/kt-1/kin-kt-1.png}
			\captionof*{figure}{\tiny{Pre-fit signal and background yields for tH process for $k_t$=-1.\\
					In the box below each distribution, the ratio of the observed and predicted event yields is shown}}
\end{minipage}\hfill \quad
\begin{minipage}{0.4\textwidth}
	\centering
			\includegraphics[width=5.5cm,height=5cm]{figures/kt-1/simple-kt-1.png}
			\captionof*{figure}{\tiny{Post-fit signal and background yields for tH process for $k_t$=-1. \\ 
					In the box below each distribution, the ratio of the observed and predicted event yields is shown}}
\end{minipage}
		\end{figure}
\end{frame}

\begin{frame}
\frametitle{Results}

\begin{table}
\caption{Prefit and postfit table for each yield. $k_{t}$ =-1.}
	\begin{tabular}{|c|c|c|}
		\hline
		Process  & Number of events prefit    & Number of events Postfit \\
		\hline
		tH & 26.2 & 1.83 $\pm$ 26.63\\
		\hline
		t$\bar{t}$H  & 24.18 $\pm$ 2.26& 24.82 $\pm$ 2.27\\
		\hline
		t$\bar{t}$W  & 68.03  $\pm$ 9.54 & 77.07 $\pm$ 8.99\\
		\hline
		t$\bar{t}$Z  & 25.89  $\pm$  3.20& 26.76 $\pm$ 3.18\\
		\hline
		Rares SM & 17.17  $\pm$ 8.64 & 18.90 $\pm$ 8.37\\
		\hline
		WZ & 16.23  $\pm$ 8.17& 17.54 $\pm$ 8.15\\
		\hline
		fakes  & 80.94   $\pm$ 40.86& 102.97 $\pm$ 29.51\\
		\hline
	\end{tabular}	
\end{table}
 Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
\end{frame}

\begin{frame}
\frametitle{ Test statistic $q_{\mu}$ for upper limits}
For purposes of establishing an upper limit on the strength parameter $\mu$ , we consider two
closely related test statistics. First, we may define
\begin{align*} 
q_{\mu}=
\begin{dcases}
-2\ln\lambda(\mu) \qquad \hat{\mu} \leq \mu	\\
0  \qquad \qquad \qquad \hat{\mu}< 0
\end{dcases}
\end{align*}
 The reason for setting $q_\mu = 0$
for $\hat{\mu}>\mu $ is that when setting an upper limit, one would not regard data with $\hat{\mu}>\mu $ as
representing less compatibility with $\mu$ than the data obtained, and therefore this is not taken
as part of the rejection region of the test. From the definition of the test statistic one sees that
higher values of $q_\mu$ represent greater incompatibility between the data and the hypothesized
value of $\mu$.
\end{frame}

\begin{frame}
\framesubtitle{Test statistic $q_{\mu}$ for upper limits}
\begin{minipage}{0.5\textwidth}
	\begin{center}
		\begin{figure}
			\includegraphics[width=6cm,height=5cm]{figures/Likelihood.png}
			\caption*{Likelihood scan for k$_t$=1 (SM)}
		\end{figure}
	\end{center}
\end{minipage}\hfill
\begin{minipage}{0.5\textwidth}
	\begin{center}
		\begin{figure}
			\includegraphics[width=6cm,height=5cm]{figures/kt-1/Likelihood-kt-1.png}
			\caption*{Likelihood scan for k$_t$=-1}
		\end{figure}
	\end{center}
\end{minipage}
\end{frame}

\begin{frame}
\frametitle{Test statistic $q_{\mu}$ for upper limits}

\begin{table}
	\caption*{Table for estimation of $\mu$ for fitting and upper limit with luminosity of 35.9 fb$^{-1}$ with95$\%$ of confidence }
	\begin{tabular}{|c|c|c|}
		\hline
		Model	&$\mu$ &$\mu$ upper limit  \\
		\hline
		SM ($k_t=1$)& 2.497 $\pm$ 12.9&	28.047    \\
		\hline
	$k_t=-1$	&0.0693 $\pm$1.02  &1.97 \\
		\hline
	\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{P value}
To quantify the level of disagreement we compute the P-value
\begin{align}
P_\mu =\int_{t_\mu}^{\infty}f(t_\mu |\mu) dt_\mu
\end{align}
where $t_\mu$  is the value of the statistic $t_\mu$ observed from the data and $f(t\mu |\mu)$ denotes
the PDF (Probability density function) of t$\	mu$ under the assumption of the signal strength $\mu$\cite{4}
\begin{align}
f(t\mu |\mu)=\frac{1}{\sqrt{2\pi}} \frac{1}{\sqrt{t_\mu}}e^\frac{-t_\mu}{2}
\end{align}
\end{frame}

\nologo{
\begin{frame}
\frametitle{P Value and significance }
%(1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.)
\begin{center}
	\begin{tabular}{cc}
		\includegraphics[width=6cm,height=4cm]{figures/nos.png} & \includegraphics[width=4cm,height=5cm]{figures/normal-curve.jpg}\\
		P value and significance for $t_\mu$ & \tiny{A Gaussian distribution with significances indicated.}
	\end{tabular}
\end{center}
\end{frame}
}

\begin{frame}
\frametitle{Luminosity}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.5]{figures/lumi-table.png}
		\caption*{Graph of luminosity of LHC measured and expected through years\cite{6}}
	\end{figure}
\end{center}
\end{frame}
\nologo{
	\begin{frame}
	\frametitle{Extrapolation of luminosity for SM }
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/35.9fb/kin.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/kin.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/kin-300.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/kin-3000.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

\nologo{
	\begin{frame}
	\frametitle{Likelihood scan for SM }
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/35.9fb/Likelihood.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/Likelihood.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/Likelihood.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/Likelihood.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

\nologo{
	\begin{frame}
	\frametitle{Extrapolation of luminosity for $k_t=-1$}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/35.9fb/kin.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/kin.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/kin-300.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/kin-3000.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

\nologo{
	\begin{frame}
	\frametitle{Likelihood scan for  $k_t=-1$}
	\begin{center}
		\begin{tabular}{cc}
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/35.9fb/Likelihood-kt-1.png} &
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/Likelihood.png}\\ 
			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/Likelihood.png}&
			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/Likelihood.png}\\
			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
		\end{tabular}
	\end{center}
\end{frame}
}

\begin{frame}
\frametitle{Results}
\begin{table}
	\caption*{Estimation of $\mu$ and upper limits  for extrapolations}
\tiny{
	\begin{tabular}{|p{1cm}|c|c|c|c|}
		\hline
		Luminosity (fb$^{-1}$)	&$\mu$ &$\mu$ for $k_t=-1$ &$\mu$ upper limit &$\mu$ upper limit for $k_t=-1$ \\
		\hline
		35.9 & 1.00 $\pm$  8.32 & 1.00 $\pm$  0.249&	22.328 & 2.777   \\
		\hline
		150& 1.00 $\pm$  6.44 & 1.00 $\pm$  0.544  &12.619 &0.915 \\
		\hline
		300&1.00 $\pm$  4.83 &1.00 $\pm$  0.407 & 9.427&0.649 \\
		\hline
		3000&1.00 $\pm$  1.54 & 1.00 $\pm$  0.151&	 3.442 & 0.25
		\\
		\hline
	\end{tabular}
}
\end{table}
%upper limit 35.9 asimov 22.328
%mu asimov 35.9 1.0000e+00 +/-  8.32e+00
%mu kt-1 asimov 1.0000e+00 +/-  2.49e-01
%mu kt-1 limit  2.777
\end{frame}

\begin{frame}
\section{Conclusions}
\frametitle{Conclusions}
\begin{itemize}
	\item We analyzed the tH process produced from PP collisions for the production of $\mu\mu$ final states   
	\item We discussed about events selections for the 2016 and by using BDT process, separate signal and background data. 
	\item The creation of a model with systematic uncertainties to make a minimization (fit) and obtain a fit which is compatible with Standard Model.
	\item Generation of likelihood scan for the exclusion of data and obtain the probability of detection of a Higgs boson.
	\item Generating simulations for predict results with higher luminosities, according to the future experiments.

%	\item With future experiments, We can get more event data, and so increase the probability of detect Higgs boson in the tH channel.
\end{itemize}
\end{frame}
	\begin{thebibliography}{99}
	\begin{frame}
	\section{References}
	\frametitle{References}
	\bibliographystyle{amsalpha}
	\bibitem{1}Gross F. \textit{Relativistic quantum mechanics and field theory}, 1994 ,WllEY-VCH Verlag GmbH \& Co. KGaA
	\bibitem{2} Griffiths, D. \textit{Introduction to Elementary Particles}, $2^\frac{\circ}{}$ edition, 2008,WllEY-VCH Verlag GmbH \& Co. KGaA
		\bibitem{2}The CMS collaboration, \textit{Search for production of a Higgs boson and a single top
	quark in multilepton final states in proton collisions at 13 TeV}, CMS-PAS-HIG-17-005 .arXiv:1811.09696
	\bibitem{3}Verkerke W \textit{Dealing with systematic uncertainties} 2014. From
\url{https://indico.cern.ch/event/287744/contributions/1641261/attachments/535763/738679/Verkerke_Statistics_3.pdf}
\end{frame}

\begin{frame}
\bibitem{5} ATLAS and CMS
Collaborations, \textit{Combined measurement of the Higgs boson mass in
	pp collisions at $\sqrt{s}$= 7 and 8 TeV with the ATLAS and CMS experiments}, Phys. Rev. Lett.
114 (2015) doi:10.1103/PhysRevLett.114.191803, arXiv:1503.07589
\bibitem{4} Cowan G. , Cranmer K., Gross E. , Vitells O.\textit{ Asymptotic formulae for
	likelihood-based tests of new physics} 2013 , arXiv:1007.1727
\bibitem{7}CMS collaboration \textit{Search for tHq production in multilepton final states at 13 TeV} ,2017,CMS AN-16-378
\bibitem{6}CMS collaboration \textit{High-Luminosity Large Hadron Collider (HL-LHC)}, 2017,CERN-2017-007-M

\end{frame}
\end{thebibliography}

\begin{frame}
\section{Supportive slides}
\huge{Back up}
\end{frame}

\begin{frame}
\frametitle{Main backgrounds}
In the leptonic channels, the main backgrounds are expected to
arise from the production of top quarks
\begin{itemize}
	\item In the dominant t$\bar{t}$ mode, where 
	same-sign dilepton signatures can occur when a non-prompt lepton from heavy-flavor
	decay passes the signal selection, or in associated production with a W/Z or Higgs boson.
	\item Processes with single top quarks also contribute, mostly in the associated production with a Z
	boson (tZ) or when produced with both a W and a Z boson (WZ)

\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Main backgrounds}
\begin{itemize}
\item t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V): Backgrounds are estimated directly from simulated events% which are corrected for data/MC differences and
%inefficiencies in the same way as signal events. 
\item WZ: Diboson production with leptonic Z decays and additional jet radiation in the final state can
lead to signatures very similar to that of the signal. Due to the larger cross section, the main
contribution arises from WZ production.
\item t$\bar{t}$H: tHq production which decays to same sign deleptons.
\item Rare SM (tZ,VVV,WW,tttt): Due to small event yields, all these process are grouped as one.
\item Non prompt leptons b quark decays and spurious lepton signatures from hadronic jets.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Sources of uncertainty on event yields}
\begin{itemize}
	\item Luminosity measurement: ~2.6$\%$.
	\item Data/MC scale factors for lepton selection (ID, iso) and trigger efficiencies ~5$\%$ per lepton.
	\item Choice of PDF set:
	\begin{itemize}
		\item 3.7$\%$ for tHq
		\item ~4$\%$ for tHW t$\bar{t}$W, t$\bar{t}$Z, t$\bar{t}$H 
		\item Scale uncertainties: 12$\%$, 4 for t$\bar{t}$W, 10$\%$ for t$\bar{t}$Z, +5.8/-9.2$\%$ for t$\bar{t}$H.
	\end{itemize}
	\item Background: WZ, ZZ sample modelling and statistics: ~50$\%$.
	\item Rare SM (tZ,tri-bosons, WWqq, tttt) : 50$\%$
	\item Fake rate estimation:
	The predicted event yield has a normalization uncertainty of ~30-50$\%$ \cite{7}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{BDT parameters}

\begin{itemize}
\item Gradient boosted (BDTG)
\item No. of trees = 800
\item No. of cuts = 50
\item Maximum depth = 3
\item Found to be most discriminating, minimal overtraining.
\end{itemize}
\end{frame}

\begin{frame}
\begin{center}
	\begin{figure}
		\includegraphics[scale=0.5]{figures/sk.png}
	\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{List of histograms used in the analysis}
Data taken from the file \texttt{plots-thq-2lss-kinMVA.root} 2016 CERN 
\begin{alltt}
thqMVA\_ttv\_2lss\_40\_tZq \\
thqMVA\_ttv\_2lss\_40\_ttZ\\
thqMVA\_ttv\_2lss\_40\_VVV\\
thqMVA\_ttv\_2lss\_40\_ttW\\
thqMVA\_ttv\_2lss\_40\_data\_fakes\\
thqMVA\_ttv\_2lss\_40\_ttH\\
thqMVA\_ttv\_2lss\_40\_tHW\_hww\\
thqMVA\_ttv\_2lss\_40\_WWss\\
thqMVA\_ttv\_2lss\_40\_tttt\\
thqMVA\_ttv\_2lss\_40\_WZ\\
thqMVA\_ttv\_2lss\_40\_tHq\_hww\\
\end{alltt}
\end{frame}

\begin{frame}
\frametitle{Backgrounds and signal histograms}
\textbf{tHq: Signal (tH)}\\
\begin{itemize}
\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_tHq\_hww \end{alltt}
\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_tHW\_hww \end{alltt}
\end{itemize}
\textbf{Backgrounds} \\
t$\bar{t}$W
\begin{itemize}
\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_ttW\end{alltt}
\end{itemize}
t$\bar{t}$Z
\begin{itemize}
\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_ttZ\end{alltt}
\end{itemize}
WZ
\begin{itemize}
\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_WZ	\end{alltt} 
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Backgrounds and signal histograms}
\textbf{Backgrounds} \\
tZ, VVV,tttt,WW:
\begin{itemize}
	\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_tZq\end{alltt}
	\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_WWss \end{alltt}
	\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_VVV\end{alltt}
	\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_tttt\end{alltt}
\end{itemize}
t$\bar{t}$H 
\begin{itemize}
	\item\begin{alltt} thqMVA\_ttv\_2lss\_40\_ttH\end{alltt}
\end{itemize}
Non prompt leptons (fakes)
\begin{itemize}
	\item\begin{alltt} thqMVA\_ttv\_2lss\_40\_data\_fakes\end{alltt}
\end{itemize} 
\end{frame}

\begin{frame}

Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake

Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons  
fakes are estimated data

\footnote[1]{Due to existence of many uncertainties, it is neccesary to sum all the uncertainties. When there is no Correlation, the uncertanties must be summed as the square root of the squares of each uncertainty}
\end{frame}

\begin{frame}
\frametitle{Sources of systematic uncertainty}
Detector-simulation related uncertainty
\begin{itemize}
\item Calibrations (electron, jet energy scale)
\item Efficiencies (particle ID, reconstruction)
\item Resolutions (jet energy, muon momentum)
\end{itemize}
Theoretical uncertainties
\begin{itemize}
\item  Factorization/Normalization scale of MC generators
\item Choice of MC generator (ME and/or PS, e.g. Herwig vs Pythia)
\end{itemize}
Monte Carlo Statistical uncertainties
\begin{itemize}\item Statistical uncertainty of simulated samples\cite{2} \end{itemize}
\end{frame}

\begin{frame}
\frametitle{Observed events }
\begin{itemize}
	\item After applying the event pre-selection on the dataset, 280 events are observed in the same-sign $\mu\mu$ channel
	\item The events are then sorted into ten categories depending on the output of the two BDT classifiers
	according to an optimized binning strategy, resulting in a one-dimensional histogram with ten
	bins.
	\item In each point, the tH and t$\bar{t}$H production cross sections and the Higgs decay branching ratios are modified with the Higgs-top ($\kappa_t$) and Higgs-vector boson ($\kappa_v$ ) coupling strength.
	\item  The Higgs-tau coupling strength modifier ($\kappa_\tau$ ) is assumed to be equal to $\kappa_t$ . 
	\item All other parameters are assumed to be at the values predicted by the standard model\cite{1}	.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{$\alpha$ values for post fit}
\begin{alltt}
Floating Parameter		\qquad		FinalValue +/- Error \\
$-----------------------------------------------------------------------$			
Lumi \quad	\qquad	\qquad		\qquad	\qquad	1.0082e+00 +/-  2.42e-02\\
alpha\_sample\_tth\_sys	\quad	1.9100e-01 +/-  9.94e-01\\
alpha\_sample\_ttw\_sys	\quad	8.7537e-01 +/-  9.18e-01\\
alpha\_sample\_ttz\_sys	\quad	2.0012e-01 +/-  9.95e-01\\
alpha\_sample\_tz\_sys\qquad	1.6749e-01 +/-  1.00e+00\\
alpha\_sample\_wz\_sys\qquad	 1.2732e-01 +/-  9.84e-01 \\
alpha\_sample\_fakes\_sys	4.5030e-01 +/-  7.17e-01\\
mu 	\qquad	\qquad	\qquad	\qquad	\qquad	2.4975e+00 +/-  1.29e+01
\end{alltt}
\end{frame}

\begin{frame}
\frametitle{$\alpha$ values for post fit thq $k_t$=-1}
\begin{alltt}
Floating Parameter			\qquad		FinalValue +/- Error \\
$-----------------------------$
Lumi \quad	\qquad	\qquad		\qquad	\qquad 1.0085e+00 +/-  2.40e-02\\
alpha\_sample\_tth\_sys	\quad	1.9290e-01 +/-  1.00e+00 \\
alpha\_sample\_ttw\_sys	\quad	8.7911e-01 +/-  9.42e-01\\
alpha\_sample\_ttz\_sys	\quad	2.0370e-01 +/-  9.94e-01\\
alpha\_sample\_tz\_sys\qquad	1.8269e-01 +/-  9.69e-01\\
alpha\_sample\_wz\_sys\qquad	1.4244e-01 +/-  9.99e-01\\
alpha\_sample\_fakes\_sys	1.4243e-01 +/-  9.98e-01\\
mu \qquad	\qquad	\qquad	\qquad	\qquad 6.9361e-02 +/-  1.02e+00
\end{alltt}
\end{frame}

\begin{frame}
\frametitle{Results}
\framesubtitle{Likelihood scan}
\begin{itemize}
	\item Likelihood function (often simply the likelihood) is a function of the
	parameters of a statistical model, given specific observed data.
	\item Likelihood functions play a key role in frequentist inference,
	especially methods of estimating a parameter from a set of
	statistics.
	\item In informal contexts, "likelihood" is often used as a synonym for
	probability.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Statistical test}
\begin{center}
	\begin{figure}
\includegraphics[scale=0.25]{figures/tmu.png}
\caption{Statistic test plot $f(t_\mu)$ vs $t_\mu$ with $t_\mu=-2\ln{\lambda(\mu)}$}
\end{figure}
\end{center}
\end{frame}

\begin{frame}
\frametitle{Luminosity scale}
\framesubtitle{150 fb}
\begin{multicols}{2}
\begin{center}
	\begin{figure}
		\includegraphics[width=6cm,height=6cm]{figures/150fb/kin.png}
		\caption*{Prefit }
	\end{figure}
\end{center}
\columnbreak
\begin{center}
	\begin{figure}
		\includegraphics[width=6cm,height=6cm]{figures/150fb/simple.png}
		\caption*{Post fit }
	\end{figure}
\end{center}
\end{multicols}
\end{frame}

\begin{frame}
\frametitle{Luminosity scale}
\framesubtitle{150 fb}
\begin{table}
	\begin{tabular}{|c|c|c|}
		\hline
event  & N prefit    & N Postfit \\
\hline
tH & 8.89972 $\pm$  0.885511 & 8.89972$\pm$57.2784\\
\hline
ttH  & 101.031 $\pm$  9.45& 101.031$\pm$9.27757\\
\hline
ttW  & 284.248$\pm$39.8961  & 284.248$\pm$31.3604\\
\hline
ttZ  & 108.175$\pm$  13.3806 & 108.175$\pm$13.1161\\
\hline
tZ & 71.7409$\pm$34.1567  & 71.7409$\pm$31.8423\\
\hline
WZ & 67.8134 $\pm$ & 67.8134$\pm$31.8861\\
\hline
fakes  & 338.189$\pm$  170.744  & 338.189$\pm$84.302\\
\hline
	\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Luminosity scale}
\framesubtitle{300 fb}
\begin{multicols}{2}
	\begin{center}
		\begin{figure}
			\includegraphics[width=6cm,height=6cm]{figures/300fb/kin-300.png}
				\caption*{Prefit }
		\end{figure}
	\end{center}
	\columnbreak
	\begin{center}
		\begin{figure}
			\includegraphics[width=6cm,height=6cm]{figures/300fb/simple.png}
				\caption*{post fit }
		\end{figure}
	\end{center}
\end{multicols}
\end{frame}

\begin{frame}
\frametitle{Luminosity scale}
\framesubtitle{300 fb}
Table of yields for background and signal
\begin{table}
	\begin{tabular}{|c|c|c|}
			\hline
tH & 17.7994 $\pm$ & 17.7994$\pm$85.9204\\
\hline
ttH  & 202.061$\pm$ 18.9162 & 202.061$\pm$18.4728\\
\hline
ttW  & 568.496$\pm$79.7922 & 568.496$\pm$56.3133\\
\hline
ttZ  & 216.351$\pm$ 26.7611 & 216.351$\pm$26.099\\
\hline
tZ & 143.482$\pm$72.2699 & 143.482$\pm$58.5044\\
\hline
WZ & 135.627 $\pm$68.3133& 135.627$\pm$60.7892\\
\hline
fakes  & 676.379$\pm$ 341.488 & 676.379$\pm$133.725\\
	\hline
	\end{tabular}
\end{table}
\end{frame}

\begin{frame}
\frametitle{Luminosity scale}
\framesubtitle{3000 fb}
\begin{multicols}{2}
	\begin{center}
		\begin{figure}
			\includegraphics[width=6cm,height=6cm]{figures/3000fb/kin-3000.png}
				\caption*{Prefit }
		\end{figure}
	\end{center}
	\columnbreak
	\begin{center}
		\begin{figure}
			\includegraphics[width=6cm,height=6cm]{figures/3000fb/simple.png}
				\caption*{Post fit }
		\end{figure}
	\end{center}
\end{multicols}
\end{frame}

\begin{frame}
\frametitle{Luminosity scale}
\framesubtitle{3000 fb}
Table of yields for background and signal
\begin{table}
	\begin{tabular}{|c|c|c|}
		\hline
event  & N prefit    & N Postfit \\
\hline
tH & 5076.72 $\pm$505.128 & 5076.72$\pm$643.706\\
\hline
ttH  & 2020.61$\pm$189.162 & 2020.61$\pm$183.997\\
\hline
ttW  & 5684.96$\pm$  797.922& 5684.96$\pm$561.487\\
\hline
ttZ  & 2163.51$\pm$267.611 & 2163.51$\pm$256.289\\
\hline
tZ & 1434.82$\pm$722.699 & 1434.82$\pm$303.361\\
\hline
WZ & 1356.27$\pm$ 683.133& 1356.27$\pm$383.271\\
\hline
fakes  & 6763.79 $\pm$3414.88 & 6763.79$\pm$591.597\\
	\hline
	\end{tabular}
\end{table}
\end{frame}

\end{document}

### 2019-10-29 presentacion_hiram/presentacion-tesis.tex
nuevo

@@
 	%\subtitle{}
-%	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
+	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
 	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
@@
 \tiny{\renewcommand{\arraystretch}{1.5}
-\begin{tabular}{|c|c|c|c|c|c|}
-	\hline 
-Particle	&Mass (MeV/$c^2$)  &Charge  & spin &Lifetime (s)  & Distance in lifetime (meters) \\ 
-	\hline 
-Up (u)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable &  -\\ 
-	\hline 
-Charm (c)	& 1280 &$\frac{2}{3}$  &  $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ &  5.21$\times 10^{-3}$ \\ 
-	\hline 
-Top	(t)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$  & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$   \\ 
-	\hline 
-Down (d)	& 4.6 &$-\frac{1}{3}$  & $\frac{1}{2}$  & Stable & - \\ 
-	\hline 
-Strange (s)	& 96 &$-\frac{1}{3}$  & $\frac{1}{2}$  &$1.24 \times 10^{-8}$  & 58.7 \\ 
-	\hline 
-Bottom (b)	& 4180 &$-\frac{1}{3}$  &  $\frac{1}{2}$ &$1.3 \times 10^{-12}$   & 6.16 $\times 10^{-3}$\\ 
-	\hline 
-W 	& 80379 &$\pm$1  & 1 & 3$\times$ 10$^{-25}$ &  1.42$\times 10^{-15}$\\ 
-	\hline 
-Z & 91187.6 &0  & 1 & 3$\times$ 10$^{-25}$  &1.42$\times 10^{-15}$ \\ 
+\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
+	\hline 
+	Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
+	\hline 
+	Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
+	\hline 
+	Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
+	\hline 
+	Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
+	\hline 
+	Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
+	\hline 
+	Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
+	\hline
+
+	Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
+	\hline 
+	$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
+	\hline 
+	$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
 	\hline
@@
 	\hline
-Gluon (g)	& 0 &0  &  1&Stable  & - \\ 
-	\hline 
-Higgs (H)	& 125.18 &0  &  0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
-	\hline 
-Electron (-e)& 0.511 & -1 &   $\frac{1}{2}$& Stable & - \\ 
+	Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
+	\hline 
+	Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
+	\hline 
+	Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
 	\hline 
@@
 \begin{itemize}
-\item Classical definition: When two particles interact, cross section is the area transverse to their relative motion within
-which they must meet in order to scatter from each other.
-\item Quantum definition: Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
+\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
 \item Experimentally
@@
 \item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Cross section}
-\begin{center}\begin{center}
-
-	\end{center}
-	\begin{figure}
-		\includegraphics[scale=0.5]{figures/cs1.png}
-		\caption{Drawing of an idealized scattering process showing the differential solid angle $\Delta\Omega$ and the
-			scattering angle $\theta$}
-	\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{Cross section}
-The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
+\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
 L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
@@
 \end{align}
+\end{itemize}
 \end{frame}
@@
 
-\end{frame}
-
-\begin{frame}
-\frametitle{Higgs production cross section}
-\begin{center}
-\begin{figure}
-\includegraphics[scale=0.42]{figures/7-14xsec.eps}
-\caption{ Higgs boson production cross sections as a function of the centre-of-mass-energies}	
-\end{figure}
-\end{center}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Higgs Branching ratio}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.35]{figures/Higgs_BR_120-130_7.eps}
-		\caption{Standard Model Higgs boson decay branching ratios}	
-	\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
 \section{Higgs Branching ratios }
@@
 \frametitle{LHC}
-\begin{center}
-	\begin{figure}
-	\includegraphics[scale=0.25]{figures/CERN's-accelerator-complex2013.jpg}
-	\end{figure}
-\end{center}
+	\begin{figure}
+		\centering
+	\includegraphics[scale=0.2]{figures/CERN's-accelerator-complex2013.jpg}
+	\end{figure}
 \end{frame}
@@
 \frametitle{LHC parameters}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.5]{figures/lhc-t.png}
+\begin{minipage}[c]{0.48\textwidth}
+	\small
+	\begin{figure}
+	\centering
+	\includegraphics[scale=0.4]{figures/lhc-t.png}
 	\caption*{Table. LHC characteristics for run 2.}
 \end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{LHC}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{0.48\textwidth}
+	\small
 	\begin{table}
+		\centering
 		\caption*{Accelerator operation energies}
@@
 	\end{table}
+\end{minipage}
 \end{frame}
@@
 \begin{frame}
+\frametitle{LHC}
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[scale=0.6]{figures/csc.png}
+	\caption*{Slide view of the CMS in terms of pseudorapidity $\eta=-\ln\left[\tan\left(\frac{\theta}{2}\right)\right]$}
+\end{figure}
+\end{frame}
+
+\begin{frame}
 \frametitle{CMS integrated luminosity}
@@
 \begin{multicols}{2}
-\tiny{
-\begin{itemize}
-\item t$\rightarrow$W$^+$b$\rightarrow$ $l^+ \nu_\mu$b
-\item H$\rightarrow$ W$^+$W$^-$
+	\small{
+\begin{itemize}
+\item $t\rightarrow W$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
+\item $H\rightarrow$ $W^+$$W^-$
 
 \begin{list}{--}{}
-\item  \tiny{W$\rightarrow$ $l^\pm \nu$, where l can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
-\item   \tiny{W$\rightarrow$ q$\bar{q}$}
-\item \tiny{W bosons decay leptonically resulting in a signature of two same-sign leptons }
+\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
+\item   \small{$W\rightarrow$ $q\bar{q}$}
+\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
 \end{list}
 \item a light-flavor quark 
-\item  b quark jet  \cite{2}
+\item  A b-jet  
 \end{itemize}
@@
 \frametitle{Event selection}
-The main analysis strategy is to obtain a selection of events compatible with
-certain characteristics of the signal at pre-selection level.\\
-
-It is required:
-\begin{itemize}
-\item The events are selected those that contain two leptons ($l^+l^-$)  with the same sign.
-\item Transverse moment $p_{t}$ > 25 and 15 GeV, for the muons.
-\item A foward jet with $p_t$ > 40 GeV, | $\eta$ | > 2.4
-\item One or more b-jets with (| $\eta$ | <2.4)\cite{1}
+In order to detect signal events and reject background, the following selections are applied. 
+\begin{itemize}
+	\item The events must contain two muons with the same sign.
+	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
+	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
+	\item One or more b-tagged jets with $|\eta|$ < 2.4
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Previous results for t$\bar{t}$H+$tH$ production}
-\begin{multicols}{2}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.4]{figures/tth-table.png}
-		\caption*{}
-	\end{figure}
-\end{center}
-\columnbreak
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.3]{figures/bdt.png}
-		\caption*{\tiny{Post-fit categorized BDT classifier outputs as used in
-			the maximum likelihood fit for the $\mu\mu$ channel for
-			35.9 fb$^{-1}$.In the box below each distribution, the ratio
-			of the observed and predicted event yields is shown.\cite{2}
-		 }}
-	\end{figure}
-\end{center}
-\end{multicols}
-\end{frame}
-}
-\begin{frame}
-	\begin{center}
-		\begin{figure}
-			\includegraphics[scale=0.3]{figures/sc.png}
-			\caption{Observed and expected 95$\%$ C.L.
-upper limit on the $tH$ + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
-The expected limit is derived from a background-only MC dataset.}
-		\end{figure}
+\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
+
+\begin{minipage}[c]{0.45\textwidth}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.3]{figures/histo.png}
+	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{.45\textwidth}
+	\begin{figure}	\centering
+	\includegraphics[width=\textwidth]{figures/sc.png}
+	\caption*{\tiny{Observed and expected 95$\%$ C.L.
+upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
+The expected limit is derived from a background-only MC dataset.}}
+	\end{figure}
+\end{minipage}
+\end{frame}
+}
+
+\begin{frame}
+\begin{minipage}[b]{.48\textwidth}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{figures/kos.png}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.48\textwidth}
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{figures/kos2.png}
+	\end{figure}
+\end{minipage}
+\begin{center}
+\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
 \end{center}
@@
 \frametitle{Main backgrounds}
-\begin{center}
-\scriptsize{
-\begin{tabular}{|c|c|p{7cm}|}
-	\hline
-	Background & $\sigma$[pb] & Decay process \\
-	\hline
-t$\bar{t}$H	& 0.2151 & t$\bar{t}$H $\rightarrow$ W$^+$b W$^- \bar{b}$ W$^+$W$^-$ $\rightarrow$ $\mu^+ \nu_\mu$b$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
-\hline  
-t$\bar{t}$W  &0.2043 &t$\bar{t}$W  $\rightarrow$  W$^+$bW$^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
-\hline
- t$\bar{t}$Z & 0.2529 & t$\bar{t}$Z  $\rightarrow$ W$^+$b  W$^-$$\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$  \\
- \hline 
-  W$^+$W$^-$  &1.64 & W$^+$W$^-$ $\rightarrow$$\mu^+\nu_\mu$$\mu^-\bar{\nu_\mu}$ \\
-    \hline 
-  tZq  &0.0758 & tZq$\rightarrow$W$^+$b$\mu^+ \mu^-$ q$\rightarrow$$\mu^+ \nu_\mu$b $\mu^+\mu^-$ q \\
-    \hline 
-  t$\bar{t}$t$\bar{t}$  & 0.0091&t$\bar{t}$t$\bar{t}$ $\rightarrow$ W$^+$b   W$^- \bar{b}$  W$^+$b  W$^- \bar{b}$   $\rightarrow$ $\mu^+ \nu_\mu$b $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$b   $\mu^- \bar{\nu_\mu} \bar{b}$ \\
-    \hline 
-  W$^+$W$^-$Z  & 0.1651& W$^+$W$^-$Z$\rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
-    \hline 
- ZZZ  &0.0139 & ZZZ$\rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$  \\
-    \hline 
-  W$^+$ZZ  & 0.0556&W$^+$ZZ$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
-  \hline 
- W$^+$Z &4.42965 &W$^+$Z$\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
- \hline
-ZZ &  1.256 &ZZ$\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
- \hline
-\end{tabular}
-}
-\end{center}
-\tiny{
-\begin{itemize}
-	\item Rare SM: tttt,WWW,WWZ,WZZ,WW,tZq
-	\item WZ:WZ,ZZ
-\end{itemize}}
-\end{frame}
-
+\tiny
+\begin{table}
+	\caption{Main backgrounds and their same sign $\mu\mu$ decay process }
+\centering
+\begin{tabular}{|c|l|}
+	\hline
+	Background & Decay process \\
+	\hline
+	$t\bar{t}W$ &$t\bar{t}W$ $\rightarrow$ $W^+ b W^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
+	\hline
+	$t\bar{t} Z$ & $t\bar{t} Z$ $\rightarrow$ $W^+ b$ $W^-\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$ \\
+	\hline
+	$W^+ Z$ &$W^+ Z \rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
+	\hline 
+	$W^\pm$ $W^\pm$ & $W^+W^+$ $\rightarrow$$\mu^+\nu_\mu$$\mu^+ {\nu_\mu}$ \\
+	\hline 
+	$tZq$ & $tZq$ $\rightarrow$ $W^+$ $ b\mu^+ \mu^- q$ $\rightarrow$$\mu^+ \nu_\mu b$ $\mu^+\mu^- q$ \\
+	\hline 
+	$t\bar{t}t\bar{t}$ &$t\bar{t}t\bar{t}$ $\rightarrow$ $W^+ b$ $W^- \bar{b}$ $W^+ b$ $W^- \bar{b}$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ \\
+	\hline 
+	$W^+ W^- Z$ & $W^+ W^-$ $Z \rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
+	\hline 
+	$ZZZ$ & $ZZZ \rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$ \\
+	\hline 
+	$W^+ZZ$ &$W^+ZZ$ $\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
+	\hline 
+	$tZW^+$ & $tZW^+ \rightarrow$ $W^+b \mu^+ \mu^- \mu^+ \nu_\mu \rightarrow \mu^+ \nu_\mu b \mu^+ \mu^- \mu^+ \nu_\mu$\\
+	\hline
+	$ZZ$ & $ZZ\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
+	\hline
+	$t\bar{t}H$	& $t\bar{t}H$ $\rightarrow W^+b W^- \bar{b} W^+W^-$ $\rightarrow$ $\mu^+ \nu_\mu b$$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
+	\hline 
+\end{tabular}
+\label{back}
+\end{table} 
+\end{frame}
+
+\begin{frame}
+\frametitle{Signal and Backgrounds}
+\begin{table}
+	\centering
+	\caption*{{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
+			The uncertainties of yields include statistical and systematic \cite{2}}} 
+	\begin{tabular}{cc}
+		\hline
+		Process & Number of events \\
+		\hline
+		$t\bar{t}W$ & 68 $\pm$ 10 \\
+		$t\bar{t}Z$ & 25.9 $\pm$ 3.9\\
+		$WZ$ & 15.1$\pm$7.7\\
+		Rares & 20.9 $\pm$ 4.9\\
+		Fakes & 80.9 $\pm$9.4\\
+		$t\bar{t}H$ & 24.2 $\pm$ 2.1 \\
+		\hline
+		$tH$ (SM) & 2.14 $\pm$ 0.13\\
+		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
+	\end{tabular}	
+	\label{tth-table}
+\end{table}
+\end{frame}
+
+\begin{frame}
+\frametitle{Systematic uncertainties}
+\begin{itemize}
+	\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
+	\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
+	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+	\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
+	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
+\end{itemize}
+
+\end{frame}
 \begin{frame}
@@
 \item The BDT training is performed using several event variables for signal and background. 
-	\item BDT training uses MC samples for  t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V),
-	because t$\bar{t}$V is one of the biggest backgrounds
 \end{itemize}
@@
 \begin{frame}
-\frametitle{Uncertainty values}
-Common uncertainties for MC :
-\begin{itemize}
-	\item Muon identificacion 6$\%$
-	\item Dimuon Trigger  1$\%$ 
-	\item Luminosity measurement: ~2.6$\%$.
-\end{itemize}
-\begin{table}
-			\renewcommand{\arraystretch}{0.1}
-	\begin{tabular}{|c|M{2.7cm}|M{2.3cm}|}
-\hline
-\scriptsize{Background}& \scriptsize{Sources of systematic uncertainty}& \scriptsize{Total Systematic Uncertainty} \\
-\hline
-\rule{0pt}{3pt}t$\bar{t}$H  &{\begin{itemize} \tiny{ 
- 	\item PDF 4$\%$ \\
- 	\item QCD scale 5.8$\%$ \\
- 	\item Higgs BR  1$\%$ }
-\end{itemize}}  & 9.36$\%$ \\
- \hline  
- t$\bar{t}$Z&{\begin{itemize} \tiny{ 
- 			\item PDF 4$\%$ \\
- 			\item QCD scale 10$\%$ \\
- 			 }
- \end{itemize}} & 12.36 $\%$ \\
- \hline
- t$\bar{t}$W&{\begin{itemize} \tiny{ 
- 			\item PDF 4$\%$ \\
- 			\item QCD scale 12$\%$ \\
- 		}
- \end{itemize}} &14.03 $\%$ \\
- \hline
-\end{tabular}
-\end{table}
-\end{frame}
-
-\begin{frame}
-\begin{table}
-		\renewcommand{\arraystretch}{0.1}
-	\begin{tabular}{|c|M{2.7cm}|M{2.3cm}|}
-\hline
-\scriptsize{Background}& \scriptsize{Sources of systematic uncertainty}& \scriptsize{Total Systematic Uncertainty} \\
-		\hline
-	 \tiny{Rares SM} & {\begin{itemize} \tiny{
-				\item Rare SM 50$\%$ }
-	\end{itemize}}&50.36 $\%$ \\
-	\hline
-	\tiny{WZ} & {\begin{itemize}\tiny{
-				\item Sample modelling and statistics 50$\%$ }
-	\end{itemize}} & 50.36$\%$ \\
-	\hline 
-	\tiny{Non prompt leptons} &{\begin{itemize} \tiny{
-				\item Fake rate estimation 50$\%$
-				\item Closure 7$\%$ }
-	\end{itemize}} 		 & 50.48$\%$ \\
-	\hline 
-	\end{tabular}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
 \section{Fitting}
@@
 \begin{align}
-L(\mu,\theta)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)}
+	L(\mu,\alpha)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)} \prod_{k=1}^M e^{\frac{-\alpha^2_k}{2}}
 \end{align}
-
-\begin{itemize}
-	\item	N=number of bins
-	\item	$\mu$=parameter of signal
-	\item	s=signal
-	\item	b=background
-	\item	n=number of events
-\end{itemize}
+	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, $\mu$ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
+	$b_j$ is the sum of different background processes $k$
+\begin{align}
+b_j=\sum_k^M b_j^k(1+ \alpha_k \sigma_k)
+\end{align}
+$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background.
+$\sigma_k$ for the backgrounds are shown in the Table of yields.
 \end{frame}
@@
 \frametitle{Results}
-\framesubtitle{Likelihood scan}
-To test a hypothesized value of $\mu$ we consider the profile likelihood ratio
-\begin{align}
-\lambda(\mu)=\frac{L(\mu,\hat{\hat{\theta}})}{L(\hat{\mu},\hat{\theta})}
-\end{align}
-\small{
-	\begin{itemize}
-		\item Here $\hat{\hat{\theta}} $ in the numerator denotes the value of $\theta$ that maximizes L for the specified $\mu$,
-		it is the conditional maximum-likelihood (ML) estimator of $\hat{\theta}$ (and thus is a function of $\mu$).
-		The denominator is the maximized (unconditional) likelihood function, i.e., $\hat{\mu}$ and $\hat{\theta}$ are
-		their ML estimators\cite{3}. 
-		\item The presence of the nuisance parameters broadens the profile likelihood as a
-		function of $\mu$ relative to what one would have if their values were fixed. This reflects the loss
-		of information about $\mu$ due to the systematic uncertainties\cite{3}\cite{4}. 
-	\end{itemize}
-}
-\end{frame}
-
-\begin{frame}
-\frametitle{Statistical test}
-It is convenient to use the statistic
-\begin{align}
-t_\mu=-2\ln{\lambda(\mu)} 
-\end{align}
-as the basis of a statistical test. Higher values of $t_\mu$ thus correspond to increasing
-incompatbility between the data and $\mu$.
-We may define a test of a hypothesized value of $\mu$ by using the statistic $t_\mu$ directly
-as measure of discrepancy between the data and the hypothesis, with higher values of
-$t_\mu$ correspond to increasing disagreement\cite{4}
+	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
+The minimization is performed by using the package ROOFIT.
+In the next slides, it shows the results of the model fitting using the Asimov data for the SM and the $k_t=-1$.
 \end{frame}
@@
 	\begin{figure}
-		\includegraphics[width=5.5cm,height=5cm]{figures/kin.png}
-		\caption*{\tiny{Pre-fit signal and background yields for tH process. In the
-			box below each distribution, the ratio of the observed and predicted event yields is shown}}
+		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
+		\caption*{\tiny{Post-fit signal and background yields for tH process in the SM. In the
+			box below each distribution, the ratio of the observed and  event yields is shown}}
 	\end{figure}
@@
 	\begin{figure}
-		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
-		\caption*{\tiny{Post-fit signal and background yields for tH process. In the
-			box below each distribution, the ratio of the observed and predicted event yields is shown}}
+		\includegraphics[width=5.5cm,height=5cm]{figures/simple-kt-1.png}
+		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. In the
+			box below each distribution, the ratio of the observed and event yields is shown}}
 	\end{figure}
@@
 \end{table}
-
  Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
-\end{frame}
-
-\begin{frame}
-\frametitle{Results}
-		\begin{figure}
-			\begin{minipage}{0.4\textwidth}
-				\centering
-			\includegraphics[width=5.5cm,height=5cm]{figures/kt-1/kin-kt-1.png}
-			\captionof*{figure}{\tiny{Pre-fit signal and background yields for tH process for $k_t$=-1.\\
-					In the box below each distribution, the ratio of the observed and predicted event yields is shown}}
-\end{minipage}\hfill \quad
-\begin{minipage}{0.4\textwidth}
-	\centering
-			\includegraphics[width=5.5cm,height=5cm]{figures/kt-1/simple-kt-1.png}
-			\captionof*{figure}{\tiny{Post-fit signal and background yields for tH process for $k_t$=-1. \\ 
-					In the box below each distribution, the ratio of the observed and predicted event yields is shown}}
-\end{minipage}
-		\end{figure}
 \end{frame}
@@
 \begin{frame}
-\frametitle{ Test statistic $q_{\mu}$ for upper limits}
-For purposes of establishing an upper limit on the strength parameter $\mu$ , we consider two
-closely related test statistics. First, we may define
-\begin{align*} 
-q_{\mu}=
-\begin{dcases}
--2\ln\lambda(\mu) \qquad \hat{\mu} \leq \mu	\\
-0  \qquad \qquad \qquad \hat{\mu}< 0
-\end{dcases}
-\end{align*}
- The reason for setting $q_\mu = 0$
-for $\hat{\mu}>\mu $ is that when setting an upper limit, one would not regard data with $\hat{\mu}>\mu $ as
-representing less compatibility with $\mu$ than the data obtained, and therefore this is not taken
-as part of the rejection region of the test. From the definition of the test statistic one sees that
-higher values of $q_\mu$ represent greater incompatibility between the data and the hypothesized
-value of $\mu$.
-\end{frame}
-
-\begin{frame}
-\framesubtitle{Test statistic $q_{\mu}$ for upper limits}
+\frametitle{Results}
+\framesubtitle{Likelihood scan}
+Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
+Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.\\
+
+We can define the likelihood ratio
+\begin{align}
+\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
+\end{align}
+Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
+\end{frame}
+
+\begin{frame}
+\frametitle{Results}
+\framesubtitle{Likelihood scan}
 \begin{minipage}{0.5\textwidth}
@@
 
-\begin{frame}
-\frametitle{Test statistic $q_{\mu}$ for upper limits}
-
-\begin{table}
-	\caption*{Table for estimation of $\mu$ for fitting and upper limit with luminosity of 35.9 fb$^{-1}$ with95$\%$ of confidence }
-	\begin{tabular}{|c|c|c|}
-		\hline
-		Model	&$\mu$ &$\mu$ upper limit  \\
-		\hline
-		SM ($k_t=1$)& 2.497 $\pm$ 12.9&	28.047    \\
-		\hline
-	$k_t=-1$	&0.0693 $\pm$1.02  &1.97 \\
-		\hline
-	\end{tabular}
-\end{table}
-\end{frame}
-
-\begin{frame}
-\frametitle{P value}
-To quantify the level of disagreement we compute the P-value
-\begin{align}
-P_\mu =\int_{t_\mu}^{\infty}f(t_\mu |\mu) dt_\mu
-\end{align}
-where $t_\mu$  is the value of the statistic $t_\mu$ observed from the data and $f(t\mu |\mu)$ denotes
-the PDF (Probability density function) of t$\	mu$ under the assumption of the signal strength $\mu$\cite{4}
-\begin{align}
-f(t\mu |\mu)=\frac{1}{\sqrt{2\pi}} \frac{1}{\sqrt{t_\mu}}e^\frac{-t_\mu}{2}
-\end{align}
-\end{frame}
-
 \nologo{
 	\begin{frame}
-\frametitle{P Value and significance }
-%(1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.)
+	\frametitle{Extrapolation of luminosity for SM }
 	\begin{center}
 		\begin{tabular}{cc}
-		\includegraphics[width=6cm,height=4cm]{figures/nos.png} & \includegraphics[width=4cm,height=5cm]{figures/normal-curve.jpg}\\
-		P value and significance for $t_\mu$ & \tiny{A Gaussian distribution with significances indicated.}
-	\end{tabular}
-\end{center}
-\end{frame}
-}
-
-\begin{frame}
-\frametitle{Luminosity}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.5]{figures/lumi-table.png}
-		\caption*{Graph of luminosity of LHC measured and expected through years\cite{6}}
-	\end{figure}
-\end{center}
-\end{frame}
+			\includegraphics[width=5.5cm,height=3cm]{figures/simple.png} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/simple-150.png}\\ 
+			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/simple-300.png}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/simple-3000.png}\\
+			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
+		\end{tabular}
+	\end{center}
+\end{frame}
+}
+
 \nologo{
 	\begin{frame}
-	\frametitle{Extrapolation of luminosity for SM }
+	\frametitle{Likelihood scan for SM }
 	\begin{center}
 		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/35.9fb/kin.png} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/kin.png}\\ 
-			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/kin-300.png}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/kin-3000.png}\\
-			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-\nologo{
-	\begin{frame}
-	\frametitle{Likelihood scan for SM }
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/35.9fb/Likelihood.png} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/Likelihood.png} &
 			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/Likelihood.png}\\ 
@@
 		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/35.9fb/kin.png} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/kin.png}\\ 
+			\includegraphics[width=5.5cm,height=3cm]{figures/simple-kt-1.png} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/simple-150-kt-1.png}\\ 
 			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/kin-300.png}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/kin-3000.png}\\
+			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/simple-300-kt-1.png}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/simple-3000-kt-1.png}\\
 			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
@@
 \frametitle{Results}
-\begin{table}
-	\caption*{Estimation of $\mu$ and upper limits  for extrapolations}
+\framesubtitle{Upper limit}
+To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
+\begin{align}
+q(\mu,\alpha)= -2\ln{\lambda} 
+\end{align}
+High values of $q$ represent greater incompatibility between the data and the fit model.
+$q$ is a random variable with a $\chi^2$ distribution.
+\end{frame}
+
+\begin{frame}
+\frametitle{Results}
+\framesubtitle{Upper limit}
 \tiny{
-	\begin{tabular}{|p{1cm}|c|c|c|c|}
-		\hline
-		Luminosity (fb$^{-1}$)	&$\mu$ &$\mu$ for $k_t=-1$ &$\mu$ upper limit &$\mu$ upper limit for $k_t=-1$ \\
-		\hline
-		35.9 & 1.00 $\pm$  8.32 & 1.00 $\pm$  0.249&	22.328 & 2.777   \\
-		\hline
-		150& 1.00 $\pm$  6.44 & 1.00 $\pm$  0.544  &12.619 &0.915 \\
-		\hline
-		300&1.00 $\pm$  4.83 &1.00 $\pm$  0.407 & 9.427&0.649 \\
-		\hline
-		3000&1.00 $\pm$  1.54 & 1.00 $\pm$  0.151&	 3.442 & 0.25
-		\\
-		\hline
-	\end{tabular}
-}
+\begin{table}[ht!]
+	\caption*{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit & $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit \\
+		\hline
+		35.9 & 1.0 $\pm$ 7.7 & 17 & 1.0 $\pm$ 0.5 & 2.3 \\
+		\hline
+		150& 1.0 $\pm$ 6.7& 11 & 1.0 $\pm$ 0.4 &1.8\\
+		\hline
+		300&1.0 $\pm$ 4.3 &8.7 & 1.0 $\pm$ 0.3 &1.5 \\
+		\hline
+		3000&1.0 $\pm$ 1.7 & 4.3 &	 1.0 $\pm$ 0.1 & 1.1\\
+		\hline
+	\end{tabular}
+	\label{upper}
 \end{table}
-%upper limit 35.9 asimov 22.328
-%mu asimov 35.9 1.0000e+00 +/-  8.32e+00
-%mu kt-1 asimov 1.0000e+00 +/-  2.49e-01
-%mu kt-1 limit  2.777
+}
 \end{frame}
@@
 \begin{itemize}
-	\item We analyzed the tH process produced from PP collisions for the production of $\mu\mu$ final states   
-	\item We discussed about events selections for the 2016 and by using BDT process, separate signal and background data. 
-	\item The creation of a model with systematic uncertainties to make a minimization (fit) and obtain a fit which is compatible with Standard Model.
+	\item We analyzed the $tH$ process produced from PP collisions for the production of $\mu\mu$ final states   
+	\item We discussed about events selections for the 2016 Run 2 from CMS.
+	\item The creation of an Asimov model with systematic uncertainties to make a minimization (fit) and obtain a fit which is compatible with Standard Model.
 	\item Generation of likelihood scan for the exclusion of data and obtain the probability of detection of a Higgs boson.
 	\item Generating simulations for predict results with higher luminosities, according to the future experiments. 
-
-%	\item With future experiments, We can get more event data, and so increase the probability of detect Higgs boson in the tH channel.
-\end{itemize}
-\end{frame}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Conclusions}
+\begin{itemize}
+\item The results of the analysis for the SM case indicates that it is impossible to detect a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
+\item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
+\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical and not related with the SM.
+\item It requires a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
+\end{itemize}
+\end{frame}
+
 	\begin{thebibliography}{99}
-	\begin{frame}
+		\bibliographystyle{unsrt}
+	\begin{frame}
+	\small
 	\section{References}
@@
 		\bibitem{2}The CMS collaboration, \textit{Search for production of a Higgs boson and a single top
-	quark in multilepton final states in proton collisions at 13 TeV}, CMS-PAS-HIG-17-005 .arXiv:1811.09696
+	quark in multilepton final states in proton collisions at 13 TeV}, CMS-HIG-18-009, Phys. Rev. D 99, 092005
 	\bibitem{3}Verkerke W \textit{Dealing with systematic uncertainties} 2014. From
@@
 \begin{frame}
+\small
 \bibitem{5} ATLAS and CMS
@@
 \begin{frame}
-\frametitle{Main backgrounds}
-In the leptonic channels, the main backgrounds are expected to
-arise from the production of top quarks
-\begin{itemize}
-	\item In the dominant t$\bar{t}$ mode, where 
-	same-sign dilepton signatures can occur when a non-prompt lepton from heavy-flavor
-	decay passes the signal selection, or in associated production with a W/Z or Higgs boson.
-	\item Processes with single top quarks also contribute, mostly in the associated production with a Z
-	boson (tZ) or when produced with both a W and a Z boson (WZ)
-
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Main backgrounds}
-\begin{itemize}
-\item t$\bar{t}$W$^\pm$ and t$\bar{t}$Z (t$\bar{t}$V): Backgrounds are estimated directly from simulated events% which are corrected for data/MC differences and
-%inefficiencies in the same way as signal events. 
-\item WZ: Diboson production with leptonic Z decays and additional jet radiation in the final state can
-lead to signatures very similar to that of the signal. Due to the larger cross section, the main
-contribution arises from WZ production.
-\item t$\bar{t}$H: tHq production which decays to same sign deleptons.
-\item Rare SM (tZ,VVV,WW,tttt): Due to small event yields, all these process are grouped as one.
-\item Non prompt leptons b quark decays and spurious lepton signatures from hadronic jets.
-\end{itemize}
-\end{frame}
-
-\begin{frame}
 \frametitle{Sources of uncertainty on event yields}
@@
 
-\begin{frame}
-\frametitle{BDT parameters}
-
-\begin{itemize}
-\item Gradient boosted (BDTG)
-\item No. of trees = 800
-\item No. of cuts = 50
-\item Maximum depth = 3
-\item Found to be most discriminating, minimal overtraining.
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.5]{figures/sk.png}
-	\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{List of histograms used in the analysis}
-Data taken from the file \texttt{plots-thq-2lss-kinMVA.root} 2016 CERN 
-\begin{alltt}
-thqMVA\_ttv\_2lss\_40\_tZq \\
-thqMVA\_ttv\_2lss\_40\_ttZ\\
-thqMVA\_ttv\_2lss\_40\_VVV\\
-thqMVA\_ttv\_2lss\_40\_ttW\\
-thqMVA\_ttv\_2lss\_40\_data\_fakes\\
-thqMVA\_ttv\_2lss\_40\_ttH\\
-thqMVA\_ttv\_2lss\_40\_tHW\_hww\\
-thqMVA\_ttv\_2lss\_40\_WWss\\
-thqMVA\_ttv\_2lss\_40\_tttt\\
-thqMVA\_ttv\_2lss\_40\_WZ\\
-thqMVA\_ttv\_2lss\_40\_tHq\_hww\\
-\end{alltt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Backgrounds and signal histograms}
-\textbf{tHq: Signal (tH)}\\
-\begin{itemize}
-\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_tHq\_hww \end{alltt}
-\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_tHW\_hww \end{alltt}
-\end{itemize}
-\textbf{Backgrounds} \\
-t$\bar{t}$W
-\begin{itemize}
-\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_ttW\end{alltt}
-\end{itemize}
-t$\bar{t}$Z
-\begin{itemize}
-\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_ttZ\end{alltt}
-\end{itemize}
-WZ
-\begin{itemize}
-\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_WZ	\end{alltt} 
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Backgrounds and signal histograms}
-\textbf{Backgrounds} \\
-tZ, VVV,tttt,WW:
-\begin{itemize}
-	\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_tZq\end{alltt}
-	\item \begin{alltt} thqMVA\_ttv\_2lss\_40\_WWss \end{alltt}
-	\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_VVV\end{alltt}
-	\item \begin{alltt}thqMVA\_ttv\_2lss\_40\_tttt\end{alltt}
-\end{itemize}
-t$\bar{t}$H 
-\begin{itemize}
-	\item\begin{alltt} thqMVA\_ttv\_2lss\_40\_ttH\end{alltt}
-\end{itemize}
-Non prompt leptons (fakes)
-\begin{itemize}
-	\item\begin{alltt} thqMVA\_ttv\_2lss\_40\_data\_fakes\end{alltt}
-\end{itemize} 
-\end{frame}
-
-\begin{frame}
-
-Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake
-
-Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons  
-fakes are estimated data
-
-\footnote[1]{Due to existence of many uncertainties, it is neccesary to sum all the uncertainties.
+%Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake
+
+%Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons  
+%fakes are estimated data
+
+%\footnote[1]{Due to existence of many uncertainties, it is neccesary to sum all the uncertainties.
 When there is no Correlation, the uncertanties must be summed as the square root of the squares of each uncertainty}
-\end{frame}
 
@@
 \begin{itemize}\item Statistical uncertainty of simulated samples\cite{2} \end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Observed events }
-\begin{itemize}
-	\item After applying the event pre-selection on the dataset, 280 events are observed in the same-sign $\mu\mu$ channel
-	\item The events are then sorted into ten categories depending on the output of the two BDT classifiers
-	according to an optimized binning strategy, resulting in a one-dimensional histogram with ten
-	bins.
-	\item In each point, the tH and t$\bar{t}$H production cross sections and the Higgs decay branching ratios are modified with the Higgs-top ($\kappa_t$) and Higgs-vector boson ($\kappa_v$ ) coupling strength.
-	\item  The Higgs-tau coupling strength modifier ($\kappa_\tau$ ) is assumed to be equal to $\kappa_t$ . 
-	\item All other parameters are assumed to be at the values predicted by the standard model\cite{1}	.
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{$\alpha$ values for post fit}
-\begin{alltt}
-Floating Parameter		\qquad		FinalValue +/- Error \\
-$-----------------------------------------------------------------------$			
-Lumi \quad	\qquad	\qquad		\qquad	\qquad	1.0082e+00 +/-  2.42e-02\\
-alpha\_sample\_tth\_sys	\quad	1.9100e-01 +/-  9.94e-01\\
-alpha\_sample\_ttw\_sys	\quad	8.7537e-01 +/-  9.18e-01\\
-alpha\_sample\_ttz\_sys	\quad	2.0012e-01 +/-  9.95e-01\\
-alpha\_sample\_tz\_sys\qquad	1.6749e-01 +/-  1.00e+00\\
-alpha\_sample\_wz\_sys\qquad	 1.2732e-01 +/-  9.84e-01 \\
-alpha\_sample\_fakes\_sys	4.5030e-01 +/-  7.17e-01\\
-mu 	\qquad	\qquad	\qquad	\qquad	\qquad	2.4975e+00 +/-  1.29e+01
-\end{alltt}
-\end{frame}
-
-\begin{frame}
-\frametitle{$\alpha$ values for post fit thq $k_t$=-1}
-\begin{alltt}
-Floating Parameter			\qquad		FinalValue +/- Error \\
-$-----------------------------$
-Lumi \quad	\qquad	\qquad		\qquad	\qquad 1.0085e+00 +/-  2.40e-02\\
-alpha\_sample\_tth\_sys	\quad	1.9290e-01 +/-  1.00e+00 \\
-alpha\_sample\_ttw\_sys	\quad	8.7911e-01 +/-  9.42e-01\\
-alpha\_sample\_ttz\_sys	\quad	2.0370e-01 +/-  9.94e-01\\
-alpha\_sample\_tz\_sys\qquad	1.8269e-01 +/-  9.69e-01\\
-alpha\_sample\_wz\_sys\qquad	1.4244e-01 +/-  9.99e-01\\
-alpha\_sample\_fakes\_sys	1.4243e-01 +/-  9.98e-01\\
-mu \qquad	\qquad	\qquad	\qquad	\qquad 6.9361e-02 +/-  1.02e+00
-\end{alltt}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Statistical test}
-\begin{center}
-	\begin{figure}
-\includegraphics[scale=0.25]{figures/tmu.png}
-\caption{Statistic test plot $f(t_\mu)$ vs $t_\mu$ with $t_\mu=-2\ln{\lambda(\mu)}$}
-\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{Luminosity scale}
-\framesubtitle{150 fb}
-\begin{multicols}{2}
-\begin{center}
-	\begin{figure}
-		\includegraphics[width=6cm,height=6cm]{figures/150fb/kin.png}
-		\caption*{Prefit }
-	\end{figure}
-\end{center}
-\columnbreak
-\begin{center}
-	\begin{figure}
-		\includegraphics[width=6cm,height=6cm]{figures/150fb/simple.png}
-		\caption*{Post fit }
-	\end{figure}
-\end{center}
-\end{multicols}
-\end{frame}
-
-\begin{frame}
-\frametitle{Luminosity scale}
-\framesubtitle{150 fb}
-\begin{table}
-	\begin{tabular}{|c|c|c|}
-		\hline
-event  & N prefit    & N Postfit \\
-\hline
-tH & 8.89972 $\pm$  0.885511 & 8.89972$\pm$57.2784\\
-\hline
-ttH  & 101.031 $\pm$  9.45& 101.031$\pm$9.27757\\
-\hline
-ttW  & 284.248$\pm$39.8961  & 284.248$\pm$31.3604\\
-\hline
-ttZ  & 108.175$\pm$  13.3806 & 108.175$\pm$13.1161\\
-\hline
-tZ & 71.7409$\pm$34.1567  & 71.7409$\pm$31.8423\\
-\hline
-WZ & 67.8134 $\pm$ & 67.8134$\pm$31.8861\\
-\hline
-fakes  & 338.189$\pm$  170.744  & 338.189$\pm$84.302\\
-\hline
-	\end{tabular}
-\end{table}
-\end{frame}
-
-\begin{frame}
-\frametitle{Luminosity scale}
-\framesubtitle{300 fb}
-\begin{multicols}{2}
-	\begin{center}
-		\begin{figure}
-			\includegraphics[width=6cm,height=6cm]{figures/300fb/kin-300.png}
-				\caption*{Prefit }
-		\end{figure}
-	\end{center}
-	\columnbreak
-	\begin{center}
-		\begin{figure}
-			\includegraphics[width=6cm,height=6cm]{figures/300fb/simple.png}
-				\caption*{post fit }
-		\end{figure}
-	\end{center}
-\end{multicols}
-\end{frame}
-
-\begin{frame}
-\frametitle{Luminosity scale}
-\framesubtitle{300 fb}
-Table of yields for background and signal
-\begin{table}
-	\begin{tabular}{|c|c|c|}
-			\hline
-tH & 17.7994 $\pm$ & 17.7994$\pm$85.9204\\
-\hline
-ttH  & 202.061$\pm$ 18.9162 & 202.061$\pm$18.4728\\
-\hline
-ttW  & 568.496$\pm$79.7922 & 568.496$\pm$56.3133\\
-\hline
-ttZ  & 216.351$\pm$ 26.7611 & 216.351$\pm$26.099\\
-\hline
-tZ & 143.482$\pm$72.2699 & 143.482$\pm$58.5044\\
-\hline
-WZ & 135.627 $\pm$68.3133& 135.627$\pm$60.7892\\
-\hline
-fakes  & 676.379$\pm$ 341.488 & 676.379$\pm$133.725\\
-	\hline
-	\end{tabular}
-\end{table}
-\end{frame}
-
-\begin{frame}
-\frametitle{Luminosity scale}
-\framesubtitle{3000 fb}
-\begin{multicols}{2}
-	\begin{center}
-		\begin{figure}
-			\includegraphics[width=6cm,height=6cm]{figures/3000fb/kin-3000.png}
-				\caption*{Prefit }
-		\end{figure}
-	\end{center}
-	\columnbreak
-	\begin{center}
-		\begin{figure}
-			\includegraphics[width=6cm,height=6cm]{figures/3000fb/simple.png}
-				\caption*{Post fit }
-		\end{figure}
-	\end{center}
-\end{multicols}
-\end{frame}
-
-\begin{frame}
-\frametitle{Luminosity scale}
-\framesubtitle{3000 fb}
-Table of yields for background and signal
-\begin{table}
-	\begin{tabular}{|c|c|c|}
-		\hline
-event  & N prefit    & N Postfit \\
-\hline
-tH & 5076.72 $\pm$505.128 & 5076.72$\pm$643.706\\
-\hline
-ttH  & 2020.61$\pm$189.162 & 2020.61$\pm$183.997\\
-\hline
-ttW  & 5684.96$\pm$  797.922& 5684.96$\pm$561.487\\
-\hline
-ttZ  & 2163.51$\pm$267.611 & 2163.51$\pm$256.289\\
-\hline
-tZ & 1434.82$\pm$722.699 & 1434.82$\pm$303.361\\
-\hline
-WZ & 1356.27$\pm$ 683.133& 1356.27$\pm$383.271\\
-\hline
-fakes  & 6763.79 $\pm$3414.88 & 6763.79$\pm$591.597\\
-	\hline
-	\end{tabular}
-\end{table}
+\frametitle{NLL}
+
 \end{frame}

### 2019-10-29 tesis_hiram/Chapter4/chapter4.tex
nuevo

@@
 	\end{align}
-	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, µ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
+	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, $\mu$ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
 	$b_j$ is the sum of different background processes $k$

### 2019-10-29 presentacion_hiram/presentacion-tesis.tex
nuevo

@@
 \frametitle{NLL}
+The negative log-likelihood function is defined as $loss=-\log(y)$ and produces a high value when the values of the output layer are evenly distributed and low.
+In other words, there's a high loss when the classification is unclear.
+It also produces relative high values when the classification is wrong.
+When the value of the output layer matches that of the expected value, the negative log-likelihood function produces a very low value.
 

### 2019-10-30 presentacion_hiram/presentacion-tesis.tex
Add files via upload

--- 2019-10-29 presentacion_hiram/presentacion-tesis.tex
@@
 \tableofcontents
-\frametitle{Contenido}
+
 \end{frame}
@@
 \begin{itemize}
-\item Through this project we will investigate the production of Higgs boson in association with a
+\item Through this project it was studied the production of Higgs boson in association with a
 single top quark ($tH$) in proton-proton collisions. 
@@
 experiment.
-
-\item Understanding the production of the Higgs boson, as well as its decays are an important part
-of the physical program of the CERN international laboratory experiments that try to complete
-the tests to verify the Standard Model, the theory of the fundamental particles
-\item Making predictions for futures measurements.
+\item Standard Model and the Higgs production mechanism
+\item A brief introduction to the LHC and CMS
+\item Event selection and reconstruction
+\item Creation and application of a statistical model for the analysis of events 
+\item Making predictions for the future experiments.
 \end{itemize}
@@
 \begin{frame}
-\section{Higgs theory}
+\section{Introduction}
+\subsection{Standard Model}
 \frametitle{Standard Model}
-\begin{center}
-\begin{figure}
-	\includegraphics[width=9cm,height=6.5cm]{figures/sm1.png}
-\end{figure}
-\end{center}
+\begin{tabular}[cc]
+\begin{figure}
+\centering
+\includegraphics[scale=0.2]{figures/sm1.png}
+\end{figure} & \begin{figure}
+\includegraphics[scale=0.2]{figures/sm.png}
+\end{figure}
+\end{tabular}
 \end{frame}
@@
 
-\begin{frame}
-\frametitle{Electroweak SM Lagrangian}
-The Standard Model is a theory of fields for particles with spins 0, $\frac{1}{2}$ and 1. 
-The  SM lagrangian 	
-\begin{align*}
-\mathcal{L}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{higgs} + \mathcal{L}_\text{yukawa}
-\end{align*}
-donde 
-\begin{itemize}
-	\item $\mathcal{L}_\text{gauge}$=$ -\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[G^{i\mu\nu}G^i_{\mu\nu}\right]$ 
-	\begin{itemize}
-		\item  $F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu $
-		\item  $G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu $
-	\end{itemize}
-	\item $\mathcal{L}_f=i\bar{\Psi}_L \cancel{D}{\Psi}_L+i\bar{\psi}_R \cancel{D}{\psi}_R  $ is the kinematic term for fermions 
-\scriptsize{
-	\begin{itemize}
-		\item $D_\mu {\Psi}_L=\left(\partial_\mu+igW_\mu+ig'Y_LB_\mu\right)\Psi_L$
-		\item $D_\mu \psi_R=\left(\partial_\mu +ig' Y_RB_\mu\right)\psi_R $
-		\item g and g' are boson coupling constants.
+%\begin{frame}
+%\subframetitle{Higgs mechanism}
+%\frametitle{Electroweak SM Lagrangian}
+%The Standard Model is a theory of fields for particles with spins 0, $\frac{1}{2}$ and 1. 
+%The  SM lagrangian 	
+%\begin{align*}
+%\mathcal{L}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{higgs} + \mathcal{L}_\text{yukawa}
+%\end{align*}
+%donde 
+%\begin{itemize}
+%	\item $\mathcal{L}_\text{gauge}$=$ -\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[G^{i\mu\nu}G^i_{\mu\nu}\right]$ 
+%	\begin{itemize}
+%		\item  $F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu $
+%		\item  $G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu $
+%	\end{itemize}
+%	\item $\mathcal{L}_f=i\bar{\Psi}_L \cancel{D}{\Psi}_L+i\bar{\psi}_R \cancel{D}{\psi}_R  $ is the kinematic term for fermions 
+%\scriptsize{
+%	\begin{itemize}
+%		\item $D_\mu {\Psi}_L=\left(\partial_\mu+igW_\mu+ig'Y_LB_\mu\right)\Psi_L$
+%		\item $D_\mu \psi_R=\left(\partial_\mu +ig' Y_RB_\mu\right)\psi_R $
+%		\item g and g' are boson coupling constants.
 %\footnote{\tiny{L(R) refers to Left and right fields.
 %Y is the  weak hypercharge,Y=T$^3$-Q.Q is charge of particle field and T is weak isospin. $T^3=\pm 1/2$ for left handed doublets and $T^3=0$ for right handed singlets.} }
-\item $W_\mu=\sigma^iW^i_\mu$, where $\sigma^i$ are the pauli matrices.
-	\end{itemize}
-}
-\end{itemize}
+%\item $W_\mu=\sigma^iW^i_\mu$, where $\sigma^i$ are the pauli matrices.
+%	\end{itemize}
+%}
+%\end{itemize}
 %\begin{equation}
@@
 %The matrix C in the last term is the charge conjugation matrix acting on the spinors, h is a matrix of Yukawa couplings
-\end{frame}
-
-\begin{frame}
+%\end{frame}
+
+\begin{frame}
+\subframetitle{Higgs mechanism}
+
 \frametitle{Electroweak SM Lagrangian}
@@
 \begin{align}
-\mathcal{L}_{yukawa}=\Gamma^u_{mn}q_{m\text{,}L} \tilde{\phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \phi e_{n\text{,}R}+h.c
+\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
 \end{align}
@@
 v+h
-\end{array} \right) \rightarrow  \Phi=\frac{1}{2}\left(\begin{array}{c}
-0 \\
-v
-\end{array} \right) %\equiv v
+\end{array} \right) \label{vmin}
 \end{align*}
 \scriptsize{
-By using it on the first part of 
-the lagrangian it is obtained for u quark} 
+By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
 \begin{align*}
-\mathcal{L}_{yukawa}=\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
+\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
 \end{align*}
-\scriptsize{
-from here the mass of $u$ quark}
+from which the masses for the fermions shown to be proportional to the Yukawa couplings
 \begin{align*}
@@
 \begin{frame}
-\section{$tH$ mechanisms}
+\subsection{Higgs production mechanisms}
 \frametitle{Higgs production mechanisms}
@@
 \begin{frame}
-\section{Production cross section}
+\subsection{Production cross section}
 \frametitle{Cross section}
@@
 \begin{frame}
-\section{Higgs Branching ratios }
 \frametitle{Higgs Branching ratios per channel}
@@
 \begin{frame}
+\section{LHC and CMS}
+\subsection{LHC}
 \frametitle{LHC}
@@
 \begin{minipage}[c]{0.48\textwidth}
-	\small
-	\begin{figure}
-	\centering
-	\includegraphics[scale=0.4]{figures/lhc-t.png}
-	\caption*{Table. LHC characteristics for run 2.}
-\end{figure}
+	\smaller
+\begin{table}
+\centering
+\begin{tabular}{|c|c|}
+			\hline
+			Quantity & Number \\
+			\hline
+			Circumference &  26 659 m \\
+			\hline
+			Number of magnets& 9593 \\
+			\hline
+			Nominal energy, protons & 6.5 TeV\\
+			\hline
+			Nominal energy, protons collisions &  13 TeV\\
+			\hline
+			Number of collisions per second &1 billion\\
+			\hline
+			No. of bunches per proton beam &  2808\\
+			\hline
+\end{tabular}
+\end{table}
 \end{minipage}
@@
 \begin{minipage}[c]{0.48\textwidth}
-	\small
+	\smaller
 	\begin{table}
@@
 \begin{frame}
+\subsection{CMS dectector}
 \frametitle{CMS detector}
@@
 \begin{frame}
+\section{Event selection and reconstruction}
+\subsection{Topology of $tH$}
 \frametitle{Topology of events tH}
@@
 \begin{frame}
+\subsection{Event selection}
 \frametitle{Event selection}
@@
 \begin{frame}
+\subsection{Previous results}
 \frametitle{Previous results for $t\bar{t}H$+$tH$ production}
@@
 
-\begin{frame}
+\begin{frame}\subsection{Main backgrounds}
 \frametitle{Main backgrounds}
@@
 \begin{frame}
+\subsection{Systematic uncertainties}
 \frametitle{Systematic uncertainties}
@@
 \begin{frame}
+\subsection{BDT}
 \frametitle{Boosted decision tree (BDT)}
@@
 \frametitle{BDT Variables}
+\small{
+\begin{itemize}
+\item A decision tree takes a set of input features and splits input data recursively based on
+those features.
+Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
+\item The BDT training is performed using several event variables for signal and background. 
+\end{itemize}
+BDT Variables}
+\tiny{
 \begin{itemize}
@@
 \item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\section{Fitting}
+\end{itemize} }
+\end{frame}
+
+\begin{frame}
+\section{Statistical analysis}
 \frametitle{Fitting}
@@
 \begin{frame}
+\subsection{Likelihood model}
 \frametitle{Likelihood model}
+\small{
+To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
+The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.\\
 The likelihood function is the product of Poisson probabilities for all bins
@@
 $\sigma_k$ for the backgrounds are shown in the Table of yields.
+}
 \end{frame}
@@
 \begin{frame}
+\subsection{Results}
 \frametitle{Results}
@@
 \frametitle{Results}
-\begin{table}
-	\caption{Prefit and postfit table for each yield.}
-\begin{tabular}{|c|c|c|}
-	\hline
-	Process  & Number of events prefit    & Number of events Postfit \\
-	\hline
-	tH & 2.13   & 5.33$\pm$27.39\\
-	\hline
-	t$\bar{t}$H  &  24.18 $\pm$ 2.26 & 24.81 $\pm$ 2.24 \\
-	\hline
-	t$\bar{t}$W  &  68.03 $\pm$ 9.54 & 76.99 $\pm$ 8.76\\
-	\hline
-	t$\bar{t}$Z  & 25.89 $\pm$ 3.20 & 26.74 $\pm$ 3.18\\
-	\hline
-	Rares SM & 18.33 $\pm$ 9.23 & 20.31 $\pm$ 9.26\\
-	\hline
-	WZ & 15.07 $\pm$ 7.59 & 15.94 $\pm$ 7.46\\
-	\hline
-	fakes  & 80.94 $\pm$ 40.86  & 100.16 $\pm$ 29.32\\
-	\hline
-\end{tabular}	
-\end{table}
- Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
-\end{frame}
-
-\begin{frame}
-\frametitle{Results}
-
-\begin{table}
-\caption{Prefit and postfit table for each yield. $k_{t}$ =-1.}
-	\begin{tabular}{|c|c|c|}
-		\hline
-		Process  & Number of events prefit    & Number of events Postfit \\
-		\hline
-		tH & 26.2 & 1.83 $\pm$ 26.63\\
-		\hline
-		t$\bar{t}$H  & 24.18 $\pm$ 2.26& 24.82 $\pm$ 2.27\\
-		\hline
-		t$\bar{t}$W  & 68.03  $\pm$ 9.54 & 77.07 $\pm$ 8.99\\
-		\hline
-		t$\bar{t}$Z  & 25.89  $\pm$  3.20& 26.76 $\pm$ 3.18\\
-		\hline
-		Rares SM & 17.17  $\pm$ 8.64 & 18.90 $\pm$ 8.37\\
-		\hline
-		WZ & 16.23  $\pm$ 8.17& 17.54 $\pm$ 8.15\\
-		\hline
-		fakes  & 80.94   $\pm$ 40.86& 102.97 $\pm$ 29.51\\
-		\hline
-	\end{tabular}	
+	\begin{table}[ht!]
+		\centering
+		\caption{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
+		\begin{tabular}{ccc}
+			\hline
+			Process & SM & $k_{t}$=-1 \\
+			\hline
+			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
+			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
+			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
+			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
+			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
+			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
+			\hline
+			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
+		\end{tabular}
+		\label{table1}
 	\end{table}

### 2019-10-30 presentacion_hiram/presentacion-tesis.tex
nuevo

@@
 \begin{document}
-	\author{
-		Departamento de Investigacion en F\'isica \\
+	\author{Departamento de Investigacion en F\'isica \\
 		Maestr\'ia en Ciencias (F\'isica)\\
@@
 \tableofcontents
-
 \end{frame}
@@
 \frametitle{Standard Model}
-\begin{tabular}[cc]
-\begin{figure}
-\centering
-\includegraphics[scale=0.2]{figures/sm1.png}
-\end{figure} & \begin{figure}
-\includegraphics[scale=0.2]{figures/sm.png}
-\end{figure}
-\end{tabular}
+\begin{table}
+	\centering
+\begin{tabular}{cc}
+\includegraphics[width=6cm,height=5cm]{figures/sm1.png} & \includegraphics[width=5cm,height=5cm]{figures/sm.png}
+\end{tabular}
+\end{table}
 \end{frame}
@@
 \hline 
-
 Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
@@
 \begin{frame}
-\subframetitle{Higgs mechanism}
-
+\subsection{Higgs mechanism}
 \frametitle{Electroweak SM Lagrangian}
@@
 m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
-\end{align*}
+\end{align*}}
 \end{frame}
@@
 \includegraphics[scale=0.4]{figures/tq.png} 
-\caption{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
+\caption*{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
 \label{th}
@@
 \begin{minipage}[c]{0.48\textwidth}
-	\smaller
+	\tiny
 \begin{table}
+	\caption*{Characteristics of LHC}
 \centering
@@
 \begin{minipage}[c]{0.48\textwidth}
-	\smaller
+	\tiny
 	\begin{table}
@@
 		\includegraphics[scale=0.08]{figures/cms.png}
-		\caption{Compact muon solenoid}
+		\caption*{Compact muon solenoid}
 	\end{figure}
@@
 		\includegraphics[scale=0.3]{figures/cms_lumi.png}
-		\caption{Integrated luminosity for CMS experiment }
+		\caption*{Integrated luminosity for CMS experiment }
 	\end{figure}
@@
 \begin{table}
-	\caption{Main backgrounds and their same sign $\mu\mu$ decay process }
+	\caption*{Main backgrounds and their same sign $\mu\mu$ decay process }
 \centering
@@
 		\centering
-		\caption{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
+		\caption*{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
 		\begin{tabular}{ccc}
@@
 
-\begin{frame}
-\frametitle{NLL}
-
-\end{frame}
-
 \end{document}

### 2019-10-30 project_ashish/paper.tex
ashish proyect

%% 
%% Copyright 2016 Icm Ltd
\documentclass[final,3p]{CSP}
\usepackage{amssymb}
\usepackage{changepage}
\begin{document}

\begin{frontmatter}

\title{THESIS PROJECT PROTOCOL}

\author[]{Ashish Sehrawat}
%\author[]{Director: Dr. Jose Feliciano Benitez Rubio}

%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
%\cortext[mycorrespondingauthor]{Corresponding author}
%\ead{support@Icm.com}

\address[mymainaddress]{Universidad de Sonora}
%\address[mysecondaryaddress]{360 Park Avenue South, New York}

%\begin{keyword}\rm
%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
%The paper...
%\end{adjustwidth}
%\end{keyword}

\begin{keyword}\rm
\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Title:}}  
Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider.
\end{adjustwidth}
\end{keyword}

\begin{abstract}\rm
% \begin{adjustwidth}{2cm}{2cm}{
\itshape\textbf{Abstract:}
The abstract
%\end{adjustwidth}
\end{abstract}

\end{frontmatter}

\section{BACKGROUND}
\cite{Dirac1953888}

-SM, Higgs, couplings, previous Higgs measurements, previous tH searches

\section{PROPOSAL}
- what we will do:  search for tH events, using which channels.

\section{GENERAL OBJECTIVE}
- motivation, tH production crossection, sign of k_t, search for BSM, ..

%\section{SPECIFIC OBJECTIVES}
%- details

\section{HYPOTHESIS}
- what we expect to find

\section{METHODOLOGY}
- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis

\section{EXPECTED RESULTS}
- a limit, also predictions for future runs

\bibliographystyle{unsrt}
\cleardoublepage
\bibliography{paper}

\appendix
\section{SKILLS THAT WILL BE DEVELOPED}

\section{CALENDAR OF ACTIVITIES}

\end{document}

### 2019-10-31 plotting/comvar.c
Add files via upload

@@ -1,0 +1,102 @@
+#include <cstdlib>
+#include <iostream>
+#include <map>
+#include <string>
+
+#include "TChain.h"
+#include "TFile.h"
+#include "TTree.h"
+#include "TString.h"
+#include "TObjString.h"
+#include "TSystem.h"
+#include "TROOT.h"
+
+#include "TMVA/Factory.h"
+#include "TMVA/DataLoader.h"
+#include "TMVA/Tools.h"
+#include "TMVA/TMVAGui.h"
+
+void comvar()
+{
+
+
+
+  TChain*t1=new TChain("demo/tuple");
+  TChain*t2=new TChain("demo/tuple");
+
+
+  //t1.Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_0.root");
+  //t2.Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_0.root");
+  //t1.Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_1.root");
+  //t2.Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_1.root");
+  //t1.Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_2.root");
+  //t2.Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_2.root");
+  
+  t1->Add("/home/ashish/RunIISummer16MiniAODv3_tuples/_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_3.root");
[…]

### 2019-10-31 plotting/overlappingareaintegral.c

@@ -1,0 +1,95 @@
+#include <cstdlib>
+#include <iostream>
+#include <map>
+#include <string>
+
+#include "TChain.h"
+#include "TFile.h"
+#include "TTree.h"
+#include "TString.h"
+#include "TObjString.h"
+#include "TSystem.h"
+#include "TROOT.h"
+
+#include "TMVA/Factory.h"
+#include "TMVA/DataLoader.h"
+#include "TMVA/Tools.h"
+#include "TMVA/TMVAGui.h"
+#include "TMath.h"
+
+void overlappingareaintegral()
+{
+
+
+
+  TChain*t1=new TChain("demo/tuple");
+  TChain*t2=new TChain("demo/tuple");
+
+
+  //t1->Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_0.root");
+  //t2->Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_0.root");
+  //t1->Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_1.root");
+  //t2->Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_1.root");
+  //t1->Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_2.root");
+  //t2->Add("/home/ashish/data/RunIISummer16MiniAODv3_tuples/TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_2.root");
+  
+  t1->Add("/home/ashish/RunIISummer16MiniAODv3_tuples/_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_3.root");
[…]

### 2019-10-31 plotting/soliton.c

@@ -1,0 +1,98 @@
+//#include "TFile.h"
+//#include "TTree.h"
+
+void soliton()
+{
+
+
+TFile *f = new TFile("/home/ashish/TMVA_n.root");
+
+TH1D * h1 = new TH1D("h1","ROC Curve", 1000, 0, 1);
+h1 = (TH1D*)f->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
+h1->SetLineColor(48); //Brown
+h1->Draw();
+
+
+TFile *f1 = new TFile("/home/ashish/TMVA_n1.root");
+
+TH1D * h2 = new TH1D("h2","ROC Curve1", 1000, 0, 1);
+h2 = (TH1D*)f1->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
+h2->SetLineColor(2); //Red
+h2->Draw("same");
+
+
+TFile *f2 = new TFile("/home/ashish/TMVA_n2.root");
+
+TH1D * h3 = new TH1D("h3","ROC Curve1", 1000, 0, 1);
+h3 = (TH1D*)f2->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
+h3->SetLineColor(50); //Flourescent Green
+h3->Draw("same");
+
+TFile *f3 = new TFile("/home/ashish/TMVA_n3.root");
+
+TH1D * h4 = new TH1D("h4","ROC Curve1", 1000, 0, 1);
+h4 = (TH1D*)f3->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
+h4->SetLineColor(4); //Blue
+h4->Draw("same");
+
+
+
+TFile *f4 = new TFile("/home/ashish/TMVA_n4.root");
+
+TH1D * h5 = new TH1D("h5","ROC Curve1", 1000, 0, 1);
+h5 = (TH1D*)f4->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
+h5->SetLineColor(6); //Magenta
+h5->Draw("same");
+
+
+//TFile *f5 = new TFile("/home/ashish/TMVA_n5.root");
+
+//TH1D * h6 = new TH1D("h6","ROC Curve1", 1000, 0, 1);
+//h6 = (TH1D*)f5->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
[…]

### 2019-10-31 plotting/what.c

@@ -1,0 +1,146 @@
+
+//#include "TFile.h"
+//#include "TTree.h"
+
+
+void what()
+
+{
+
+//TFile*f = new TFile("/home/ashish/TMVA.root");
+//f->ls();
+
+//TDirectoryFile*d=(TDirectoryFile*)(dataset->Get("Method_BDT"));
+//d->ls();
+//TDirectoryFile*t=(TDirectoryFile*)d->Get("BDTG");
+//t->ls();
+
+//TH1D*h = new TH1D("h1","Signal Distribution", 10, -1, 1);
+//h=(TH1D*)f->Get("MVA_BDTG_S");
+//f->Draw("MVA_BDTG_S>>h1");
+
+//f->Draw("MVA_BDTG_S>>h1");
+//h1->Draw();
+
+TFile *f = new TFile("/home/ashish/TMVA_n4.root");
+
+//gDirectory->pwd();
+f->ls();
+
+
+TChain*t1=new TChain("dataset/TrainTree");
+TChain*t2=new TChain("dataset/TestTree");
+
+
+TH1D * h1 = new TH1D("h1","Signal Distribution", 100, -1, 1);
+TH1D * h2 = new TH1D("h2","Background Distribution", 100, -1, 1);
+TH1D * h3 = new TH1D("h3","",100,-1,1);
+
+h1 = (TH1D*)f->Get("dataset/Method_BDT/BDTG/MVA_BDTG_S");
+h1->SetLineColor(2);
+h1->Draw();
+
+h2 = (TH1D*)f->Get("dataset/Method_BDT/BDTG/MVA_BDTG_B");
+h2->SetLineColor(4);
+h2->Draw("same");
+
+
+
+for (int i = 1; i <= h3->GetNbinsX(); i++) h3->Fill(h3->GetBinCenter(i), TMath::Min(h1->GetBinContent(i), h2->GetBinContent(i)));
+
+cout << h3->Integral()<<endl;
+cout << h3->Integral("width")<<endl;
+
+ TCanvas*c2 = new TCanvas("h3","");
+ //gStyle->SetOptStat("nemMrRuoisSkK");
+
+ h3->SetNameTitle("h3", "minimum(h1, h2)"); 
+   
+ h3->Draw();
+ 
+ c2->Print("BDTcommonarea.pdf");
+
[…]

### 2019-10-31 plotting/TMVAClassification1.C
Add files via upload

@@ -1,0 +1,596 @@
+/// \file
+/// \ingroup tutorial_tmva
+/// \notebook -nodraw
+/// This macro provides examples for the training and testing of the
+/// TMVA classifiers.
+///
+/// As input data is used a toy-MC sample consisting of four Gaussian-distributed
+/// and linearly correlated input variables.
+/// The methods to be used can be switched on and off by means of booleans, or
+/// via the prompt command, for example:
+///
+///     root -l ./TMVAClassification.C\(\"Fisher,Likelihood\"\)
+///
+/// (note that the backslashes are mandatory)
+/// If no method given, a default set of classifiers is used.
+/// The output file "TMVA.root" can be analysed with the use of dedicated
+/// macros (simply say: root -l <macro.C>), which can be conveniently
+/// invoked through a GUI that will appear at the end of the run of this macro.
+/// Launch the GUI via the command:
+///
+///     root -l ./TMVAGui.C
+///
+/// You can also compile and run the example with the following commands
+///
+///     make
+///     ./TMVAClassification <Methods>
+///
+/// where: `<Methods> = "method1 method2"` are the TMVA classifier names
+/// example:
+///
+///     ./TMVAClassification Fisher LikelihoodPCA BDT
+///
+/// If no method given, a default set is of classifiers is used
+///
+/// - Project   : TMVA - a ROOT-integrated toolkit for multivariate data analysis
+/// - Package   : TMVA
+/// - Root Macro: TMVAClassification
+///
+/// \macro_output
+/// \macro_code
+/// \author Andreas Hoecker
+
+
+#include <cstdlib>
+#include <iostream>
+#include <map>
+#include <string>
+
+#include "TChain.h"
+#include "TFile.h"
+#include "TTree.h"
+#include "TString.h"
+#include "TObjString.h"
+#include "TSystem.h"
+#include "TROOT.h"
+
+#include "TMVA/Factory.h"
+#include "TMVA/DataLoader.h"
+#include "TMVA/Tools.h"
+#include "TMVA/TMVAGui.h"
+
+int TMVAClassification( )
+{
[…]

### 2019-10-31 plotting/soliton.c
Delete soliton.c

@@ -1,98 +1,0 @@
-//#include "TFile.h"
-//#include "TTree.h"
-
-void soliton()
-{
-
-
-TFile *f = new TFile("/home/ashish/TMVA_n.root");
-
-TH1D * h1 = new TH1D("h1","ROC Curve", 1000, 0, 1);
-h1 = (TH1D*)f->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
-h1->SetLineColor(48); //Brown
-h1->Draw();
-
-
-TFile *f1 = new TFile("/home/ashish/TMVA_n1.root");
-
-TH1D * h2 = new TH1D("h2","ROC Curve1", 1000, 0, 1);
-h2 = (TH1D*)f1->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
-h2->SetLineColor(2); //Red
-h2->Draw("same");
-
-
-TFile *f2 = new TFile("/home/ashish/TMVA_n2.root");
-
-TH1D * h3 = new TH1D("h3","ROC Curve1", 1000, 0, 1);
-h3 = (TH1D*)f2->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
-h3->SetLineColor(50); //Flourescent Green
-h3->Draw("same");
-
-TFile *f3 = new TFile("/home/ashish/TMVA_n3.root");
-
-TH1D * h4 = new TH1D("h4","ROC Curve1", 1000, 0, 1);
-h4 = (TH1D*)f3->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
-h4->SetLineColor(4); //Blue
-h4->Draw("same");
-
-
-
-TFile *f4 = new TFile("/home/ashish/TMVA_n4.root");
-
-TH1D * h5 = new TH1D("h5","ROC Curve1", 1000, 0, 1);
-h5 = (TH1D*)f4->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
-h5->SetLineColor(6); //Magenta
-h5->Draw("same");
-
-
-//TFile *f5 = new TFile("/home/ashish/TMVA_n5.root");
-
-//TH1D * h6 = new TH1D("h6","ROC Curve1", 1000, 0, 1);
-//h6 = (TH1D*)f5->Get("dataset/Method_BDT/BDTG/MVA_BDTG_rejBvsS");
[…]

### 2019-10-31 fit_2lss_2016/compare_variables.C
nuevo

@@ -1,0 +1,44 @@
+
+void compare_variables(){
+
+  TChain t1("demo/tuple");
+  TChain t2("demo/tuple");
+  TChain t3("demo/tuple");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+  t2.Add("_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_0.root");
+  t3.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+
+
+  TCanvas C;
+  C.Print("compare_variables.pdf[");
+
+  ///compare one variable
+  TH1F H1("H1","",20,0,5);
+  TH1F H2("H2","",20,0,5);
+  TH1F H3("H3","",20,0,5);
+
+  t1.Draw("abs(fj_eta)>>H1");
+  t2.Draw("abs(fj_eta)>>H2");
+  t3.Draw("abs(fj_eta)>>H3");
+  H1.Scale(2.14/H1.Integral());
+  H2.Scale(237.1/H2.Integral());
+  H3.Scale(26.22/H3.Integral());
+  C.Clear();
+  H1.Draw("hist");
+  H2.Draw("histsame");
+  H3.Draw("histsame");
+  C.Print("compare_variables.pdf");
+
+  //compare correlations
+  C.Clear();
+  C.Divide(1,2);
+  C.cd(1);
+  t1.Draw("l1_eta:b1_eta");
+  C.cd(2);
+  t2.Draw("l1_eta:b1_eta");
+  //C.Print("compare_variables.pdf");
+
+
+  C.Print("compare_variables.pdf]");
+
+}

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 
-\title{THESIS PROJECT PROTOCOL}
+\title{THESIS PROJECT PROPOSAL}
 
@@
 
+The standard model (SM) of particle physics is so far the best theoretical model describing the interaction of elementary particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
+Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary particle interact with each other.
+The standard model (SM) of particle physics is divided into two categories, bosonic sector and fermionic sector.
+Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the fermionic sector contain particles called fermions which make up all the matter in our universe.
+SM has three generations of matter(fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino, second generation consist of charm quark, strange quark, muon and muon neutrino and the third generation of matter particles has top quark, bottom quark, tau and tau neutrino.
+The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which mediate strong force, electromagnetic force and weak force respectively.
+There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking.
+Higgs boson can be produced at the particle colliders like the Large Hadron Collider in Geneva.
+There are various production modes of Higgs boson like the vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq).
+Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons.
+The Higgs boson can also decay to other particles and these decay channels have different branching fractions.
+Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons.
+It can also decay to Z boson and a photon.
+It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in Higgs-portal dark matter models.
+
 \section{PROPOSAL}

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the fermionic sector contain particles called fermions which make up all the matter in our universe.
-SM has three generations of matter(fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino, second generation consist of charm quark, strange quark, muon and muon neutrino and the third generation of matter particles has top quark, bottom quark, tau and tau neutrino.
+SM has three generations of matter (fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino, second generation consist of charm quark, strange quark, muon and muon neutrino and the third generation of matter particles has top quark, bottom quark, tau and tau neutrino.
 The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which mediate strong force, electromagnetic force and weak force respectively.
@@
 Higgs boson can be produced at the particle colliders like the Large Hadron Collider in Geneva.
-There are various production modes of Higgs boson like the vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq).
+There are various production modes of Higgs boson like the gluon gluon fusion(ggF), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq).
 Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons.
@@
 It can also decay to Z boson and a photon.
-It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in Higgs-portal dark matter models.
+It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 
-The standard model (SM) of particle physics is so far the best theoretical model describing the interaction of elementary particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak nuclear force.
-Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary particle interact with each other.
-The standard model (SM) of particle physics is divided into two categories, bosonic sector and fermionic sector.
-Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the fermionic sector contain particles called fermions which make up all the matter in our universe.
-SM has three generations of matter (fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino, second generation consist of charm quark, strange quark, muon and muon neutrino and the third generation of matter particles has top quark, bottom quark, tau and tau neutrino.
-The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which mediate strong force, electromagnetic force and weak force respectively.
-There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking.
-Higgs boson can be produced at the particle colliders like the Large Hadron Collider in Geneva.
-There are various production modes of Higgs boson like the gluon gluon fusion(ggF), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq).
-Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons.
-The Higgs boson can also decay to other particles and these decay channels have different branching fractions.
-Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons.
-It can also decay to Z boson and a photon.
-It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
+The standard model (SM) of particle physics is so far the best theoretical model describing the interaction of elementary 
+particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
+nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
+particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
+and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
+fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
+matter (fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino,
+second generation consist of charmquark, strange quark, muon and muon neutrino and the third generation of matter particles has
+top quark,bottom quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which 
+mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the standard model called
+the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be produced at the particle
+colliders like the Large Hadron Collider(LHC) in Geneva. There are various production modes of Higgs boson like the gluon gluon 
+fusion(ggH), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top
+quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). Each production channel has its
+own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons. The Higgs boson can also
+decay to other particles and these decay channels have different branching fractions. Higgs boson can decay to a pair of W
+bosons, Z bosons, photons, bottom quarks, muons and electrons. It can also decay to Z boson and a photon. It is also interesting
+to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering 
+cross section like in the Higgs-portal dark matter models.
+
+The main production mode of higgs bosons at LHC is gluon gluon fusion(ggH).
+As bosons like gluons and photons are massless, they do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons can only proceed via loop diagrams which involve vector bosons or heavy quarks in the loop.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
-matter (fermions) particles.The first generation of fermions consists of up quark, down quark, electron and electron neutrino,
-second generation consist of charmquark, strange quark, muon and muon neutrino and the third generation of matter particles has
-top quark,bottom quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, W^+,W^-,Z^0 which 
-mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the standard model called
-the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be produced at the particle
-colliders like the Large Hadron Collider(LHC) in Geneva. There are various production modes of Higgs boson like the gluon gluon 
-fusion(ggH), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or Z), Higgs production with top
-quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). Each production channel has its
-own importance to probe the properties and the coupling strength of Higgs boson to fermions and bosons. The Higgs boson can also
-decay to other particles and these decay channels have different branching fractions. Higgs boson can decay to a pair of W
-bosons, Z bosons, photons, bottom quarks, muons and electrons. It can also decay to Z boson and a photon. It is also interesting
-to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering 
-cross section like in the Higgs-portal dark matter models.
+matter (fermions) particles.The first generation of fermions consists of up(u) quark, down(d) quark, electron and electron neutrino,second generation consist of charm(c) quark, strange(s) quark, muon and muon neutrino and the third generation of matter
+particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
+W^+,W^-,Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
+standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be 
+produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva. There are various production modes of Higgs 
+boson like the gluon gluon  fusion(ggH), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or 
+Z), Higgs production with topquark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). 
+Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and 
+bosons. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. Higgs 
+boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. It can also decay to Z boson and a 
+photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on 
+dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
 
-The main production mode of higgs bosons at LHC is gluon gluon fusion(ggH).
-As bosons like gluons and photons are massless, they do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons can only proceed via loop diagrams which involve vector bosons or heavy quarks in the loop.
+The main production mode of higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
+do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons can only proceed via 
+loop diagrams which involve vector bosons or heavy quarks in the loop.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 
-The main production mode of higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
-do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons can only proceed via 
-loop diagrams which involve vector bosons or heavy quarks in the loop.
+The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
+do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possiblwe at 
+tree level and can only proceed via loop diagrams which involve vector bosons or heavy quarks in the loop.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 bosons. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. Higgs 
-boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. It can also decay to Z boson and a 
+boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to Z boson and a 
 photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on 
@@
 The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
-do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possiblwe at 
-tree level and can only proceed via loop diagrams which involve vector bosons or heavy quarks in the loop.
+do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
+tree level and can only proceed via loop diagrams which involve vector bosons or heavy quarks(t,b,c) in the loop.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 boson like the gluon gluon  fusion(ggH), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or 
-Z), Higgs production with topquark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). 
+Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). 
 Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 
-The standard model (SM) of particle physics is so far the best theoretical model describing the interaction of elementary 
+The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
 particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
@@
 bosons. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. Higgs 
-boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to Z boson and a 
-photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on 
-dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
+boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to Z 
+boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put 
+upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
-tree level and can only proceed via loop diagrams which involve vector bosons or heavy quarks(t,b,c) in the loop.
+tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
-do not directly interact with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
+do not interact directly with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
 tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop.

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
-W^+,W^-,Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
+W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
 standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be 
@@
 Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and 
-bosons. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. Higgs 
-boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to Z 
-boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put 
-upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
-
-The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are massless, they 
-do not interact directly with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are not possible at 
-tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop.
+bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are 
+massless, they do not interact directly with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are 
+not possible at tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop. The Higgs boson 
+can also decay to other particles and these decay channels have different branching fractions. Higgs boson can decay to a pair of 
+W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to Z boson and a photon. It is also 
+interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon 
+scattering cross section like in the Higgs-portal dark matter models.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva. There are various production modes of Higgs 
-boson like the gluon gluon  fusion(ggH), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or 
+boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or 
 Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). 
 Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and 
-bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggH). As bosons like gluons and photons are 
-massless, they do not interact directly with the Higgs boson and processes like ggH or Higgs boson decay to pair of photons are 
+bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As bosons like gluons and photons are 
+massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs boson decay to pair of photons are 
 not possible at tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop. The Higgs boson 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be 
-produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva. There are various production modes of Higgs 
-boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), higgs production in association with vector boson(VH, V=W or 
-Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with a single top quark and a quark jet(tHq). 
-Each production channel has its own importance to probe the properties and the coupling strength of Higgs boson to fermions and 
-bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As bosons like gluons and photons are 
-massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs boson decay to pair of photons are 
-not possible at tree level and can only proceed via loop diagrams which involve W boson or top quark in the loop. The Higgs boson 
-can also decay to other particles and these decay channels have different branching fractions. Higgs boson can decay to a pair of 
-W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to Z boson and a photon. It is also 
-interesting to investigate some invisible decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon 
-scattering cross section like in the Higgs-portal dark matter models.
+produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva,Switzerland.
+
+There are various production modes of Higgs boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), higgs production 
+in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 
+a single top quark and a quark jet(tHq). Each production channel has its own importance to probe the properties and the coupling 
+strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As 
+bosons like gluons and photons are massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs 
+boson decay to pair of photons are not possible at tree level and can only proceed via loop diagrams which involve W boson or top 
+quark in the loop. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. 
+Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to 
+Z boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put 
+upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
+
+The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
+quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
+hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
+undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
+bottom(b) quark and W boson.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
-bottom(b) quark and W boson.
+bottom(b) quark and W boson. Using b-jet tagging algorithms, the ejt originating from b-quark can be reconstructed to identity 
+top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks like 
+top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly to 
+the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the Higgs 
+boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. There 
+are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which are 
+Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
+quark with a Higgs boson(tH).
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 
-There are various production modes of Higgs boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), higgs production 
+There are various production modes of Higgs boson like the gluon gluon  fusion(ggF), vector boson fusion(VBF), Higgs production 
 in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
-standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking. Higgs boson can be 
-produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva,Switzerland.
+standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
+can be produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva,Switzerland.
 
@@
 undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
-bottom(b) quark and W boson. Using b-jet tagging algorithms, the ejt originating from b-quark can be reconstructed to identity 
-top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks like 
-top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly to 
-the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the Higgs 
-boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. There 
-are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which are 
-Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
-quark with a Higgs boson(tH).
+bottom(b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
+the top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks 
+like top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly 
+to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the 
+Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. 
+There are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which 
+are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
+quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.
 

### 2019-10-31 project_ashish/paper.tex
Update paper.tex

@@
 the top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks 
-like top,bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most strongly 
-to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark with the 
-Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new physics. 
-There are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top quark which 
-are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production of single top 
-quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.
+like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most 
+strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark 
+with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new 
+physics. There are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top 
+quark which are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production 
+of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new 
-physics. There are two processes at LHC which will allow us to directly proble the Yukawa coupling between Higgs Boson and top 
-quark which are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production 
+physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between Higgs Boson and top 
+quark are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production 
 of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark 
-with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication to new 
+with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication of new 
 physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between Higgs Boson and top 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 bottom(b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
-the top quark. In SM, the coupling of the Higgs boson to fermions is proportional to the mass of the fermions. Thus heavy quarks 
-like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, top quark couple most 
-strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa coupling of the top quark 
-with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might give an indication of new 
-physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between Higgs Boson and top 
-quark are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and the production 
-of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than t\bar{t}H production.
+the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and leptons is proportional to the mass of the 
+fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, 
+top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa 
+coupling of the top quark with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might 
+give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
+Higgs Boson and top quark are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and 
+the production of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than 
+t\bar{t}H production.
+The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark.
+These two processes in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with Higgs boson Y_t and the coupling of W boson to the Higgs boson.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
-matter (fermions) particles.The first generation of fermions consists of up(u) quark, down(d) quark, electron and electron neutrino,second generation consist of charm(c) quark, strange(s) quark, muon and muon neutrino and the third generation of matter
+matter (fermions) particles.The first generation of fermions consists of up(u) quark, down(d) quark, electron and electron 
+neutrino,second generation consist of charm(c) quark, strange(s) quark, muon and muon neutrino and the third generation of matter 
 particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
@@
 fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, 
-top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling Y_t. That is why the Yukawa 
-coupling of the top quark with the Higgs boson Y_t has lot of importance as any deviation from standard model prediction might 
+top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling y_t. That is why the Yukawa 
+coupling of the top quark with the Higgs boson y_t has lot of importance as any deviation from standard model prediction might 
 give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
@@
 the production of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than 
-t\bar{t}H production.
-The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark.
-These two processes in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with Higgs boson Y_t and the coupling of W boson to the Higgs boson.
+t\bar{t}H production. The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark. These two processes 
+in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with 
+Higgs boson y_t and the coupling of W boson to the Higgs boson. IF the Yukawa coupling between top quark and Higgs boson y_t 
+deviate from the SM prediction or even a negative sign of y_t would cause a strong increase in the tH production cross section 
+which is a special property of tH production channel making it an interesting production channel to probe using LHC 2016,2017 and 2018 data.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with 
-Higgs boson y_t and the coupling of W boson to the Higgs boson. IF the Yukawa coupling between top quark and Higgs boson y_t 
-deviate from the SM prediction or even a negative sign of y_t would cause a strong increase in the tH production cross section 
-which is a special property of tH production channel making it an interesting production channel to probe using LHC 2016,2017 and 2018 data.
+Higgs boson y_t and the coupling of W boson to the Higgs boson. If the Yukawa coupling between top quark and Higgs boson y_t 
+deviate from the SM prediction or even if y_t has a negative sign, both would cause a strong increase in the tH production cross section which is a special property of tH production channel making it an interesting production channel to probe using LHC 2016,2017 and 2018 data.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
-matter (fermions) particles.The first generation of fermions consists of up(u) quark, down(d) quark, electron and electron 
-neutrino,second generation consist of charm(c) quark, strange(s) quark, muon and muon neutrino and the third generation of matter 
+matter (fermions) particles.The first generation of fermions consists of up (u) quark, down (d) quark, electron and electron 
+neutrino,second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third generation of matter 
 particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
@@
 There are various production modes of Higgs boson like the gluon gluon fusion(ggF), vector boson fusion(VBF), Higgs production 
-in association with vector boson(VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 
-a single top quark and a quark jet(tHq). Each production channel has its own importance to probe the properties and the coupling 
+in association with vector boson (VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 
+a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the properties and the coupling 
 strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As 
@@
 Higgs boson y_t and the coupling of W boson to the Higgs boson. If the Yukawa coupling between top quark and Higgs boson y_t 
-deviate from the SM prediction or even if y_t has a negative sign, both would cause a strong increase in the tH production cross section which is a special property of tH production channel making it an interesting production channel to probe using LHC 2016,2017 and 2018 data.
+deviate from the SM prediction or even if y_t has a negative sign, both would cause a strong increase in the tH production cross 
+section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
+2016,2017 and 2018 data.
+
+The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of
+free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
+interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling, three mixing angles and the CP-violating phase 
+of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields.
+In order to identify which new physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, experiments.
+This
+approach requires studying each model individually, and calculating every possible observable. There is another approach immitating 
+Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual theory and by 
+completing it by a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below the mass of the 
+new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to the SM
+Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-energy 
+remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely on the 
+symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator coefficients, 
+which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model 
+predictions if these higher dimensional operators are present in low energy effective SM theory.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
-interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling, three mixing angles and the CP-violating phase 
-of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields.
-In order to identify which new physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, experiments.
-This
-approach requires studying each model individually, and calculating every possible observable. There is another approach immitating 
-Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual theory and by 
-completing it by a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below the mass of the 
-new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to the SM
-Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-energy 
-remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely on the 
-symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator coefficients, 
-which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model 
-predictions if these higher dimensional operators are present in low energy effective SM theory.
+interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, three mixing angles and the 
+CP-violating phase of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings 
+which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond 
+the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields. In order to identify which new 
+physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, 
+experiments. This approach requires studying each model individually, and calculating every possible observable. There is another 
+approach immitating Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual 
+theory and by completing it by a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
+the mass of the new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to 
+the SM Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-
+energy remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
+on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
+coefficients,which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the 
+standard model predictions if these higher dimensional operators are present in low energy effective SM theory.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
-can be produced at the particle colliders like the Large Hadron Collider(LHC) in Geneva,Switzerland.
+can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva,Switzerland.
 
-There are various production modes of Higgs boson like the gluon gluon fusion(ggF), vector boson fusion(VBF), Higgs production 
-in association with vector boson (VH, V=W or Z), Higgs production with top quark and top anti-quark(ttH) and Higgs production with 
+There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs production 
+in association with vector boson (VH, V=W or Z), Higgs production with top quark and top anti-quark (ttH) and Higgs production with 
 a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the properties and the coupling 
-strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion(ggF). As 
+strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion (ggF). As 
 bosons like gluons and photons are massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs 
@@
 undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
-bottom(b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
+bottom (b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
 the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and leptons is proportional to the mass of the 
@@
 give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
-Higgs Boson and top quark are Higgs boson production in association with top quark pair(t\bar{t}tH) via strong interaction and 
-the production of single top quark with a Higgs boson(tH). As tH occur via electroweak interaction, it is more rare than 
+Higgs Boson and top quark are Higgs boson production in association with top quark pair (t\bar{t}tH) via strong interaction and 
+the production of single top quark with a Higgs boson (tH). As tH occur via electroweak interaction, it is more rare than 
 t\bar{t}H production. The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark. These two processes 
@@
 approach immitating Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual 
-theory and by completing it by a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
+theory and by completing it with a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
 the mass of the new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to 
@@
 on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
-coefficients,which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the 
+coefficients, which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the 
 standard model predictions if these higher dimensional operators are present in low energy effective SM theory.

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
-coefficients, which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the 
-standard model predictions if these higher dimensional operators are present in low energy effective SM theory.
+coefficients, which is to be set from experiments.
+
+The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
+operators are present in low energy effective SM theory.
+We can consider anomalous Higgs and Higgs-gauge effective operators like -\frac{1}{3}(\phi^{\dagger}\phi)^3 and \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM.
+In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators.
+Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

--- 2019-11-01 project_ashish/paper.tex
@@
 on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
-coefficients, which is to be set from experiments. The Higgs boson and fermion (quarks and leptons) coupling will deviate from the 
-standard model predictions if these higher dimensional operators are present in low energy effective SM theory.
+coefficients, which is to be set from experiments.
+
+The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
+operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective operators like -
+\frac{1}{3}(\phi^{\dagger}\phi)^3 and \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) to calculate 
+the deviation of Higgs boson-fermion couplings from SM. In the effective beyond standard model theory, there are dimension 5 and 
+dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon 
+minus lepton number symmetry conservation processes.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
-Higgs Boson and top quark are Higgs boson production in association with top quark pair (t\bar{t}tH) via strong interaction and 
+Higgs Boson and top quark are Higgs boson production in association with top quark pair (t\bar{t} H) via strong interaction and 
 the production of single top quark with a Higgs boson (tH). As tH occur via electroweak interaction, it is more rare than 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 
+The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of
+free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
+interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, three mixing angles and the 
+CP-violating phase of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings 
+which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond 
+the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields. In order to identify which new 
+physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, 
+experiments. This approach requires studying each model individually, and calculating every possible observable. There is another 
+approach immitating Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual 
+theory and by completing it with a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
+the mass of the new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to 
+the SM Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-
+energy remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
+on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
+coefficients, which is to be set from experiments.
+
+The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
+operators are present in low energy effective SM theory.
+We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and
+(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM.
+The first operator shift the minimum of the Higgs potential.
+Also as there is a rescaling of the Higgs field due to the introduction of these operators in the potential term, Higgs-Fermion couplings are modified.
+In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators.
+Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
+
 The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
@@
 2016,2017 and 2018 data.
-
-The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of
-free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
-interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, three mixing angles and the 
-CP-violating phase of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings 
-which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond 
-the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields. In order to identify which new 
-physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, 
-experiments. This approach requires studying each model individually, and calculating every possible observable. There is another 
-approach immitating Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual 
-theory and by completing it with a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
-the mass of the new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to 
-the SM Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-
-energy remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
-on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
-coefficients, which is to be set from experiments.
-
-The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
-operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective operators like -
-\frac{1}{3}(\phi^{\dagger}\phi)^3 and \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) to calculate 
-the deviation of Higgs boson-fermion couplings from SM. In the effective beyond standard model theory, there are dimension 5 and 
-dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon 
-minus lepton number symmetry conservation processes.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
-operators are present in low energy effective SM theory.
-We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and
-(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM.
-The first operator shift the minimum of the Higgs potential.
-Also as there is a rescaling of the Higgs field due to the introduction of these operators in the potential term, Higgs-Fermion couplings are modified.
-In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators.
-Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
+operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators 
+like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
+(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The 
+first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of 
+these operators in the potential term, Higgs-Fermion couplings are modified. In the effective beyond standard model theory, there are 
+dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator 
+dominate baryon minus lepton number symmetry conservation processes.
 
@@
 section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
-2016,2017 and 2018 data.
+2016, 2017 and 2018 data.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of 
-these operators in the potential term, Higgs-Fermion couplings are modified. In the effective beyond standard model theory, there are 
-dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator 
-dominate baryon minus lepton number symmetry conservation processes.
+these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified.
+In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators.
+Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
-can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva,Switzerland.
+can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
 
@@
 
-The Higgs boson and fermion (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
+The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
 operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators 
@@
 first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of 
-these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified.
-In the effective beyond standard model theory, there are dimension 5 and dimension 6 operators.
-Dimension 5 operators are odd under baryon minus lepton number symmetry and dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
+these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified. In the effective beyond standard model 
+theory, there are dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and 
+dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 
+It is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large Hadron Collider of the 
+CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and 
+Higgs boson, is part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far. It is 
+proposed to study sensitivity with the current data in the channel where the events are identified with two muons of the same sign. The 
+impact of uncertainties will be studied and projections will be made to the future phases of the LHC.
+
 \section{GENERAL OBJECTIVE}

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 (\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The 
-first operator shift the minimum of the Higgs potential. Also as there is a rescaling of the Higgs field due to the introduction of 
+first operator shift the minimum of the Higgs potential. Also as there will be rescaling of the Higgs field due to the introduction of 
 these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified. In the effective beyond standard model 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and 
-Higgs boson, is part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far. It is 
-proposed to study sensitivity with the current data in the channel where the events are identified with two muons of the same sign. The 
-impact of uncertainties will be studied and projections will be made to the future phases of the LHC.
+Higgs boson.
+It is a part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far.
+It is proposed to study sensitivity with the current data in the channel where the events are identified with two muons of the same sign.
+The impact of uncertainties will be studied and projections will be made to the future phases of the LHC.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 
-It is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large Hadron Collider of the 
-CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and 
-Higgs boson.
+In this project, it is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large Hadron Collider of the CERN laboratory.
+The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and Higgs boson.
 It is a part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far.
@@
 The impact of uncertainties will be studied and projections will be made to the future phases of the LHC.
+For these studies the data of the run two (2015-2018) of the LHC identifying the signal events with two muons from the same sign.
+It is also expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began in 2026.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
-2016, 2017 and 2018 data.
+2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} which will tell us the 
+deviation of y_t from the SM prediction.
 
@@
 
-In this project, it is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large Hadron Collider of the CERN laboratory.
-The measurement of this process complements other measurements of the yukawa coupling parameter of the top quark and Higgs boson.
-It is a part of the physics program of CMS international collaborations and ATLAS and it has not been observed so far.
-It is proposed to study sensitivity with the current data in the channel where the events are identified with two muons of the same sign.
-The impact of uncertainties will be studied and projections will be made to the future phases of the LHC.
-For these studies the data of the run two (2015-2018) of the LHC identifying the signal events with two muons from the same sign.
-It is also expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began in 2026.
+In this project, it is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large 
+Hadron Collider of the CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter 
+of the top quark and Higgs boson. It is a part of the physics program of CMS international collaborations and ATLAS and it has not been 
+observed so far. It is proposed to study sensitivity with the current data in the channel where the events are identified with two muons 
+of the same sign. The impact of uncertainties will be studied and projections will be made to the future phases of the LHC. For these 
+studies the data of the run two (2015-2018) of the LHC identifying the signal events with two muons from the same sign. It is also 
+expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began in 2026.
 
@@
 - motivation, tH production crossection, sign of k_t, search for BSM, ..
+
+There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \percent of the universe, another 
+25 \percent includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
+decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
+particles. Through this project we will investigate the production of the Higgs boson in association with a single top-type quartz (tH) 
+in proton-proton collisions with the CMS experiment of the LHC. The distribution of events in one of the decay channels and the 
+sensitivity that we get with the current data.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 
-There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \percent of the universe, another 
-25 \percent includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
+There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \% of the universe, another 
+25 \% includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
 decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
@@
 in proton-proton collisions with the CMS experiment of the LHC. The distribution of events in one of the decay channels and the 
-sensitivity that we get with the current data.
+sensitivity that we get with the current data. The main objective is to search for new processes such as tH Higgs production mode in the 
+CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of 
+adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.
+
+Some of the objectives in this project include:
+• study one or more decay channels,
+• verify that simulation of signal events is adequate,
+• study the extraction of signal strength through adjustments to the data,
+• study the impact of statistical and systematic uncertainties.
 
@@
 - what we expect to find
+
+Production studies in the tH channel have already started with the collaborations CMS and ATLAS with publications based on data from the 
+2011-2012 run and some data from the second run of 2015-2016. In these results it was not found signal evidence and upper limits have 
+been set for the effective section. With the more sensitive analysis an upper limit is calculated for the effective section of a signal 
+composed of tH and ttH that corresponds 3.1 times that expected in the SM. In this analysis the reconstruction methods do not allow to 
+distinguish between tH and ttH because the effective section of ttH is much larger than that of tH and some events pass the
+selections designed for tH, the fraction of tH events over tH + ttH is 5 \%. In BSM models the fraction could change up to 50 \%, for 
+example with \kappa_t = -1. It could help to obtain better limits for the production of tH. The data that has been used so far 
+correspond to only 20 \% of the final data of the run that which ends in 2018. The uncertainty for the signal in the current analysis is 
+mostly statistical nature, therefore adding the total data in a new analysis the next year, sensitivity can be improved with an 
+approximate factor of 2.2. Additionally, in subsequent phases of the LHC 2021-2023 and 2026-2038 the number of data fold and then 
+multiply by 10 respectively. With these additions It is expected that the signal from the Higgs boson can be observed on the tH 
+production channel. The current results can be used to project sensitivity in the third run and the high brightness phase and thus 
+contribute to the planning of the updates of the detector.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 
+Aspects of simulation of signal production are studied based on generators that simulate the interactions of quarks and gluons taking 
+into account the probability distributions of each type of particle. These are packages of software that are controlled with 
+configuration files that define various aspects such as decay channels, energy in the center of mass and refinements in the development 
+of the jets that are generated by the Strong interaction of the quarks. The reconstruction and selection of tH events requires the use 
+of central software of the CMS collaboration. This software contains the algorithms that reconstruct the charged and neutral particles 
+starting from the energy deposits in the different parts of the detector. These particles include leptons, photons and hadrons, 
+whichThey have a life time that allows them to leave the interaction region. These particles are used to identify the production of the 
+top and the Higgs. In the case of the top, it usually decays to a cuark b and a boson W. Subsequently the W decays to two Leptons or two 
+quarks. Reconstruction requires finding a type b and two jet leptons. Improvements in this reconstruction can be done by studying the 
+distributions of transverse momentum, the angular distributions of the different particles, and others properties.
+
 \section{EXPECTED RESULTS}
 - a limit, also predictions for future runs
+
+The expected results of this project are the following:
+• Improve data adjustments and study the effects of uncertainties.
+• Improve the sensitivity to the tH signal in the data of the second CMS run.
+• Limit calculations in the effective section incorporating data from the second
+run of the LHC.
+• Calculate projections of signal sensitivity for the different phases of the LHC.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
-particles. Through this project we will investigate the production of the Higgs boson in association with a single top-type quartz (tH) 
-in proton-proton collisions with the CMS experiment of the LHC. The distribution of events in one of the decay channels and the 
-sensitivity that we get with the current data. The main objective is to search for new processes such as tH Higgs production mode in the 
-CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of 
-adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.
+particles. Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) 
+in proton-proton collisions with the CMS experiment of the LHC.
+We will study the distribution of events in one of the decay channels and the sensitivity that we get with the current data.
+The main objective is to search for new processes such as tH Higgs production mode in the CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.
 
@@
 \section{SKILLS THAT WILL BE DEVELOPED}
+The following are skills that will be developed based on the work on this project:
+- understand particle physics from an experimental point of view.
+- analyze and manipulate data using modern programming languages such as C++, Python and ROOT.
+- data analysis techniques.
+- use high performance computing.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
-2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} which will tell us the 
+2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} will tell us the 
 deviation of y_t from the SM prediction.
@@
 into account the probability distributions of each type of particle. These are packages of software that are controlled with 
-configuration files that define various aspects such as decay channels, energy in the center of mass and refinements in the development 
-of the jets that are generated by the Strong interaction of the quarks. The reconstruction and selection of tH events requires the use 
-of central software of the CMS collaboration. This software contains the algorithms that reconstruct the charged and neutral particles 
-starting from the energy deposits in the different parts of the detector. These particles include leptons, photons and hadrons, 
-whichThey have a life time that allows them to leave the interaction region. These particles are used to identify the production of the 
-top and the Higgs. In the case of the top, it usually decays to a cuark b and a boson W. Subsequently the W decays to two Leptons or two 
-quarks. Reconstruction requires finding a type b and two jet leptons. Improvements in this reconstruction can be done by studying the 
-distributions of transverse momentum, the angular distributions of the different particles, and others properties.
+configuration files that define various aspects of such as decay channels, energy in the center of mass and refinements in the development of the jets that are generated by the strong interaction of the quarks.
+The reconstruction and selection of tH events requires the use of central software of the CMS collaboration.
+This software contains the algorithms that reconstruct the charged and neutral particles starting from the energy deposits in the different parts of the detector.
+These particles include leptons, photons and hadrons which have a life time that allows them to leave the interaction region.
+These particles are used to identify the production of the top and the Higgs boson.
+In the case of the top quark, it usually decays to a bottom (b) quark and a W boson.
+Subsequently the W decays to two leptons or two quarks.
+Reconstruction requires finding a type b and two jet leptons.
+Improvements in this reconstruction can be done by studying the distributions of transverse momentum, the angular distributions of the different particles, and others properties.
 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 
+Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. These had 
+eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was discovered in 1995 
+in the Tevatrón collider of the Fermilab laboratory, this proton collider operated with an energy of 1.8 TeV at the center of mass up to 
+2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV and then 
+at 8 and 13 TeV.
+
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect particles known as 
+muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed
+a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to 
+bend them in opposite directions and measure your momentum.
+A silicon tracker, made of about 75 million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+
 There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs production 
@@
 the SM Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-
-energy remnant of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
+energy residue of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
 on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 

### 2019-11-01 project_ashish/paper.tex
Update paper.tex

@@
 eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was discovered in 1995 
-in the Tevatrón collider of the Fermilab laboratory, this proton collider operated with an energy of 1.8 TeV at the center of mass up to 
+in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass energy of 1.8 TeV untill 
 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV and then 
@@
 a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to 
-bend them in opposite directions and measure your momentum.
-A silicon tracker, made of about 75 million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 million electronic sensors individual 
+arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision. The muons are not 
+detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the 
+solenoid. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the 
+discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of 
+the Higgs boson of the standard model (SM).
 

### 2019-11-02 project_ashish/paper.tex
Update paper.tex

@@
 section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
-2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} will tell us the 
+2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} which will tell us the 
 deviation of y_t from the SM prediction. 
+The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. As there 
+strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the sign and 
+the magnitude of any coupling beoynd the SM between Higgs-top caused by higher dimensional operators in effective SM theory.
 

### 2019-11-02 project_ashish/paper.tex
Update paper.tex

@@
 deviation of y_t from the SM prediction.
+
 The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. As there 
-strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the sign and 
-the magnitude of any coupling beoynd the SM between Higgs-top caused by higher dimensional operators in effective SM theory.
+is strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the sign 
+and the magnitude of any coupling beyond the SM between Higgs boson and top quark caused by higher dimensional operators in effective SM 
+theory.
 

### 2019-11-02 project_ashish/paper.tex
Update paper.tex

@@
 operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators 
-like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
+like -\frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
 (\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The 

### 2019-11-02 project_ashish/paper.tex
Update paper.tex

@@
 
-The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. As there 
-is strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the sign 
-and the magnitude of any coupling beyond the SM between Higgs boson and top quark caused by higher dimensional operators in effective SM 
-theory.
+The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. The 
+anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential. As 
+there is strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the 
+sign and the magnitude of any coupling beyond the SM between Higgs boson and top quark induced by higher dimensional operators in 
+effective SM theory.
 
@@
 particles. Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) 
-in proton-proton collisions with the CMS experiment of the LHC.
-We will study the distribution of events in one of the decay channels and the sensitivity that we get with the current data.
-The main objective is to search for new processes such as tH Higgs production mode in the CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.
+in proton-proton collisions with the CMS experiment of the LHC. We will study the distribution of events in one of the decay channels 
+and the sensitivity that we get with the current data. The main objective is to search for new processes such as tH Higgs production 
+mode in the CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, 
+techniques of adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic 
+uncertainties.
 
@@
 into account the probability distributions of each type of particle. These are packages of software that are controlled with 
-configuration files that define various aspects of such as decay channels, energy in the center of mass and refinements in the development of the jets that are generated by the strong interaction of the quarks.
-The reconstruction and selection of tH events requires the use of central software of the CMS collaboration.
-This software contains the algorithms that reconstruct the charged and neutral particles starting from the energy deposits in the different parts of the detector.
-These particles include leptons, photons and hadrons which have a life time that allows them to leave the interaction region.
-These particles are used to identify the production of the top and the Higgs boson.
-In the case of the top quark, it usually decays to a bottom (b) quark and a W boson.
-Subsequently the W decays to two leptons or two quarks.
-Reconstruction requires finding a type b and two jet leptons.
-Improvements in this reconstruction can be done by studying the distributions of transverse momentum, the angular distributions of the different particles, and others properties.
+configuration files that define various aspects of such as decay channels, energy in the center of mass and refinements in the 
+development of the jets that are generated by the strong interaction of the quarks. The reconstruction and selection of tH events 
+requires the use of central software of the CMS collaboration. This software contains the algorithms that reconstruct the charged and 
+neutral particles starting from the energy deposits in the different parts of the detector. These particles include leptons, photons and 
+hadrons which have a life time that allows them to leave the interaction region. These particles are used to identify the production of 
+the top and the Higgs boson. In the case of the top quark, it usually decays to a bottom (b) quark and a W boson. Subsequently the W 
+decays to two leptons or two quarks. Reconstruction requires finding a type b and two jet leptons. Improvements in this reconstruction 
+can be done by studying the distributions of transverse momentum, the angular distributions of the different particles, and others 
+properties.
 

### 2019-11-04 compare_variables.C
new

@@ -1,0 +1,52 @@
+
+void compare_variables(){
+
+  TChain t1("demo/tuple");
+  TChain t2("demo/tuple");
+  TChain t3("demo/tuple");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+  t2.Add("_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_0.root");
+  t3.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+
+
+  TCanvas C;
+  C.Print("compare_variables.pdf");
+
+  ///compare one variable
+  TH1F H1("H1","",20,0,5);
+  TH1F H2("H2","",20,0,5);
+  TH1F H3("H3","",20,0,5);
+
+H1.SetLineColor(kGreen-3);
+H2.SetLineColor(kRed-3);
+H3.SetLineColor(kBlue-3);
+ t1.Draw("fj_eta>>H1");
+ t2.Draw("fj_eta>>H2");
+ t3.Draw("fj_eta>>H3");
+  H1.Scale(2.14/H1.Integral());
+  H2.Scale(68.0/H2.Integral());
+  H3.Scale(26.22/H3.Integral());
+  C.Clear();
+  H2.Draw("hist");
+  H1.Draw("histsame");
+  H3.Draw("histsame");
+  H2.SetAxisRange(0,10,"Y");
+  H2.SetAxisRange(0,5,"X");
+  H2.SetYTitle("Events");
+  H2.SetStats(0);
+  H2.SetTitle("#eta Distribution");
+  C.Print("compare_variables.pdf");
+
+  //compare correlations
+  C.Clear();
+  C.Divide(1,2);
+  C.cd(1);
+  t1.Draw("l1_eta:b1_eta");
+  C.cd(2);
+  t2.Draw("l1_eta:b1_eta");
+  //C.Print("compare_variables.pdf");
+
+
+ // C.Print("compare_variables.pdf");
+
+}

### 2019-11-05 BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/compare_variables.C
new

@@ -1,0 +1,52 @@
+
+void compare_variables(){
+
+  TChain t1("demo/tuple");
+  TChain t2("demo/tuple");
+  TChain t3("demo/tuple");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+  t2.Add("_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_0.root");
+  t3.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+
+
+  TCanvas C;
+  C.Print("compare_variables.pdf");
+
+  ///compare one variable
+  TH1F H1("H1","",20,0,5);
+  TH1F H2("H2","",20,0,5);
+  TH1F H3("H3","",20,0,5);
+
+H1.SetLineColor(kGreen-3);
+H2.SetLineColor(kRed-3);
+H3.SetLineColor(kBlue-3);
+ t1.Draw("fj_eta>>H1");
+ t2.Draw("fj_eta>>H2");
+ //t3.Draw("fj_eta>>H3");
+  H1.Scale(1.0/H1.Integral());
+  H2.Scale(1.0/H2.Integral());
+  H3.Scale(1.0/H3.Integral());
+  C.Clear();
+  H2.Draw("hist");
+  H1.Draw("histsame");
+  //H3.Draw("histsame");
+  H2.SetAxisRange(0,0.5,"Y");
+  H2.SetAxisRange(0,5,"X");
+  H2.SetYTitle("Events normalized to unit area");
+  H2.SetStats(0);
+  H2.SetXTitle("#eta");
+  C.Print("compare_variables.pdf");
+
+  //compare correlations
+  C.Clear();
+  C.Divide(1,2);
+  C.cd(1);
+  t1.Draw("l1_eta:b1_eta");
+  C.cd(2);
+  t2.Draw("l1_eta:b1_eta");
+  //C.Print("compare_variables.pdf");
+
+
+ // C.Print("compare_variables.pdf");
+
+}

### 2019-11-05 project_ashish/ashish thesis proposal.tex
Add files via upload

\documentclass{article}
\documentclass{article}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{apacite}
\date{}
\begin{document}

\title{THESIS PROJECT PROPOSAL}
\author{Ashish Sehrawat$^1$, Dr. Jose Feliciano Benitez Rubio$^2$}

\maketitle
\title{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}\\
\address[mymainaddress]{Universidad de Sonora}
\begin{abstract}
Add Abstract
\end{abstract}

\section{Background}
 SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\
The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland. \\
Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV and then at 8 and 13 TeV.\\
The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect 
particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers 
of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify 
the charge of the particles to bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 
million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles 
bent with very high precision. The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors 
are outside to detect them once they have crossed the solenoid. In 2012, the ATLAS and CMS collaborations, with detectors at 
two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all 
measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
production in association with vector boson (VH, V = W or Z), Higgs production with top quark and top anti-quark (ttH) and Higgs 
production with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
properties and the coupling strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is 
gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
and processes like ggF or Higgs boson decay to pair of photons are not possible at tree level and can only proceed via loop 
diagrams which involve W boson or top quark in the loop. The Higgs boson can also decay to other particles and these decay 
channels have different branching fractions. Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, 
muons and electrons. Higgs boson can also decay to Z boson and a photon. It is also interesting to investigate some invisible 
decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the 
Higgs-portal dark matter models. \\ 
The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
number of free-parameters like fine structure constant $\alpha$, Weinberg angle or weak mixing angle $\theta_W$, the coupling 
constant of strong interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, 
three mixing angles and the CP-violating phase of the CKM matrix which tells us how quarks of 
different color charge mix with 
each other, nine yukawa couplings which determine the mass of nine charged fermions and fine 
tunings related to the origin of 
masses robustly suggests new physics beyond Stanard model (BSM). There are lot of specific 
BSM theories and most of these 
models involve heavy fields. In order to identify which new physics lies beyond the 
electroweak (EW) scale, the new parameters 
of such theories may be constrained by the actual, low energy, experiments. This approach 
requires studying each model 
individually, and calculating every possible observable. There is another approach immitating 
Fermi$’s$ treatment of beta decay 
which consists of considering the SM as the first order approximation of the actual theory 
and by completing it with a series 
of higher dimensional operators. When the electroweak symmetry breaking takes place well 
below the mass of the new particles, 
the BSM physics is taken into account at the EW scale and below by adding higher dimensional 
operators to the SM Lagrangian. 
They are built out of SM fields and supposed to be invariant under its gauge group. Those 
operators are the low-energy residue 
of the high energy theory. This approach does not pretend to guess the complete high-energy 
model and it is based solely on 
the symmetry of the  theory. The operators are general and the only model dependence is 
encoded in the size of the operator 
coefficients, which is to be set from experiments. \\
The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
model predictions if these higher 
dimensional operators are present in low energy effective SM theory. We can consider 
anomalous Higgs and Higgs-gauge effective 
dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
(\phi^{\dagger} \phi) 
\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
(D^{\mu} \phi)$ to calculate the 
deviation of Higgs boson-fermion couplings from SM. The first operator shift the minimum of 
the Higgs potential. Also as there 
will be rescaling of the Higgs field due to the introduction of these operators in the 
potential term, Higgs-fermion (quarks 
and leptons) couplings are modified. In the effective beyond standard model theory, there are 
dimension 5 and dimension 6 
operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and 
dimension 6 operator dominate baryon 
minus lepton number symmetry conservation processes. \\
The production of Higgs boson in association with single top quark is one of the rare Higgs 
boson production mode. As the top 
quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
top quark decay before 
hardronization which allow the possibility to reconstruct top quark from its decay products 
unlike the lighter quarks which 
undergo hardronization and are seen as bundles of particles in detector called jets. The most 
probable decay of top quark is 
into bottom (b) quark and W boson \cite{nishiwaki2014tth}. Using b-jet tagging algorithms, the jet originating from 
b-quark can be reconstructed to 
identity the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and 
leptons is proportional to the mass 
of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
which means that out of all known 
quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
coupling $y_t$. That is why the 
Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
deviation from standard model prediction might give an indication of new physics. The two 
processes at LHC which will allow us to directly probe the Yukawa 
coupling between Higgs Boson and top quark are Higgs boson production in association with top 
quark pair (t$\bar{t}$H) via 
strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
occur via electroweak interaction, it 
is more rare than t$\bar{t}$H production. The Higgs boson in the tH channel can be radiated 
off by a W boson or by a top 
quark. These two processes in standard model have destructive interference which allow us to 
probe the relative sign between 
the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
boson. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
production cross section which is a special property of tH production channel making it an 
interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
us the deviation of $y_t$ from the SM prediction \cite{sirunyan2019search}. 
The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
quark associated production mode. 
The anomalous coupling will arise when we add interaction terms (dimension 6 operators in 
effective SM theory) in the Higgs 
potential. As there is strong destructive inteference in the t-channel for the standard model 
couplings, this production mode 
is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs 
boson and top quark induced by 
higher dimensional operators in effective SM theory.

\section{PROPOSAL}
- what we will do:  search for tH events, using which channels.\\

\onehalfspacing In this project, it is proposed to study the production channel of the Higgs boson associated 
with a single top quark in the Large Hadron Collider of the CERN laboratory. The measurement 
of this process complements other measurements of the yukawa coupling parameter of the top 
quark and Higgs boson. It is a part of the physics program of CMS international 
collaborations and ATLAS and it has not been observed so far. It is proposed to study 
sensitivity with the current data in the channel where the events are identified with two 
muons of the same sign. The impact of uncertainties will be studied and projections will be 
made to the future phases of the LHC. For these studies the data of the run two (2015-2018) 
of the LHC identifying the signal events with two muons from the same sign. It is also 
expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began 
in 2026.

\section{GENERAL OBJECTIVE}
- motivation, tH production crossection, sign of $k_t$, search for BSM, ..\\

There is currently a great enigma in physics since we know that ordinary matter comprises 
only $5\%$ of the universe, another 
$25\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
well as its decays like the invisible decay modes are an important part of the physics 
program of CERN laboratory experiments to verify the Standard Model and look for new 
particles. Through this project we will investigate the production of the Higgs boson in 
association with a single top quark (tH) in proton-proton collisions with the CMS experiment 
of the LHC. We will study the distribution of events in one of the decay channels and the 
sensitivity that we get with the current data. The main objective is to search for new 
processes such as tH Higgs production mode in the CMS experiment which require to study 
different aspects such as the model of the noises that are made by simulation, techniques of 
adjustments to the data that incorporate the different noises and the signal, and estimates 
of statistical and systematic uncertainties.
Some of the objectives in this project include:\\
\begin{itemize}
\item study one or more decay channels.\\
\item verify that simulation of signal events is adequate.\\
\item study the extraction of signal strength through adjustments to the data.\\
\item study the impact of statistical and systematic uncertainties.\\
\end{itemize}

\section{HYPOTHESIS}
- what we expect to find\\

Production studies in the tH channel have already started with the collaborations CMS and 
ATLAS with publications based on data from the 2011-2012 run and some data from the second 
run of 2015-2016. In these results it was not found signal evidence and upper limits have 
been set for the effective section. With the more sensitive analysis an upper limit is 
calculated for the effective section of a signal composed of tH and ttH that corresponds 3.1 
times that expected in the SM. In this analysis the reconstruction methods do not allow to 
distinguish between tH and t$\bar{t}$H because the effective section of t$\bar{t}$H is much 
larger than that of tH and some events pass the selections designed for tH, the fraction of 
tH events over tH + t$\bar{t}$H is 5. In BSM models the fraction could change up to 50, for 
example with $\kappa_t = -1$. It could help to obtain better limits for the production of tH. 
The data that has been used so far correspond to only 20 of the final data of the run that 
which ends in 2018. The uncertainty for the signal in the current analysis is mostly 
statistical nature, therefore adding the total data in a new analysis the next year, 
sensitivity can be improved with an approximate factor of 2.2. Additionally, in subsequent 
phases of the LHC 2021-2023 and 2026-2038 the number of data fold and then multiply by 10 
respectively. With these additions It is expected that the signal from the Higgs boson can be 
observed on the tH production channel. The current results can be used to project sensitivity 
in the third run and the high brightness phase and thus contribute to the planning of the 
updates of the detector.

\section{METHODOLOGY}
- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, 
backgrounds, statistical analysis\\

Aspects of simulation of signal production are studied based on generators that simulate the 
interactions of quarks and gluons taking into account the probability distributions of each 
type of particle. These are packages of software that are controlled with configuration files 
that define various aspects of such as decay channels, energy in the center of mass and 
refinements in the development of the jets that are generated by the strong interaction of 
the quarks. The reconstruction and selection of tH events requires the use of central 
software of the CMS collaboration. This software contains the algorithms that reconstruct the 
charged and neutral particles starting from the energy deposits in the different parts of the 
detector. These particles include leptons, photons and hadrons which have a life time that 
allows them to leave the interaction region. These particles are used to identify the 
production of the top and the Higgs boson. In the case of the top quark, it usually decays to 
a bottom (b) quark and a W boson. Subsequently the W decays to two leptons or two quarks. 
Reconstruction requires finding a type b and two jet leptons. Improvements in this 
reconstruction can be done by studying the distributions of transverse momentum, the angular 
distributions of the different particles, and others properties.

\section{EXPECTED RESULTS}
- a limit, also predictions for future runs\\

The expected results of this project are the following:\\
\begin{itemize}

\item Improve data adjustments and study the effects of uncertainties.\\
\item Improve the sensitivity to the tH signal in the data of the second CMS run.\\
\item Limit calculations in the effective section incorporating data from the second
run of the LHC.\\
\item Calculate projections of signal sensitivity for the different phases of the LHC.
\end{itemize}

\appendix
\section{SKILLS THAT WILL BE DEVELOPED}
The following are skills that will be developed based on the work on this project:
- understand particle physics from an experimental point of view.
- analyze and manipulate data using modern programming languages such as C++, Python and 
ROOT.
- data analysis techniques.
- use high performance computing.

\section{CALENDAR OF ACTIVITIES}

\bibliography{References}
\bibliographystyle{apacite}

\section{figures}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 1}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 7}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 8}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 9}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.jpg}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms6.jpg}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
  \caption{Important production processes of the Higgs boson in proton collisions}
   \label{figure 11}
\end{figure}

\end{document}

### 2019-11-05 BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/compare_variables.C
new

@@ -4,37 +4,164 @@ void compare_variables(){
   TChain t1("demo/tuple");
   TChain t2("demo/tuple");
   TChain t3("demo/tuple");
+  TChain t4("demo/tuple");
+  TChain t5("demo/tuple");
+  TChain t6("demo/tuple");
+  TChain t7("demo/tuple");
+  TChain t8("demo/tuple");
+  TChain t9("demo/tuple");
+  TChain t10("demo/tuple");
+  TChain t11("demo/tuple");
+  TChain t12("demo/tuple");
+  TChain t13("demo/tuple");
+  TChain t14("demo/tuple");
+  TChain t15("demo/tuple");
+  TChain t16("demo/tuple");
+  TChain t17("demo/tuple");
+  TChain t18("demo/tuple");
+  TChain t19("demo/tuple");
+  TChain t20("demo/tuple");
+
   t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
-  t2.Add("_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_0.root");
-  t3.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+  t2.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_1.root");
+  t3.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_2.root");
+  t4.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_3.root");
[…]

### 2019-11-05 project_ashish/paper.tex

--- 2019-11-02 project_ashish/paper.tex
@@
 
-The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
-particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the weak
-nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which elementary 
-particle interact with each other. The standard model (SM) of particle physics is divided into two categories, bosonic sector 
-and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of nature and the
-fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three generations of 
-matter (fermions) particles.The first generation of fermions consists of up (u) quark, down (d) quark, electron and electron 
-neutrino,second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third generation of matter 
-particles has top(t) quark,bottom(b) quark, tau and tau neutrino. The bosonic sector consist of gauge bosons like gluon, photon, 
-W^+ W^- Z^0 which mediate strong force, electromagnetic force and weak force respectively. There is one more particle in the 
-standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism. Higgs boson 
-can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
-
-Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. These had 
-eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was discovered in 1995 
-in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass energy of 1.8 TeV untill 
-2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 colliding protons at 7 TeV and then 
-at 8 and 13 TeV.
-
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect particles known as 
-muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed
-a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to 
-bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 million electronic sensors individual 
-arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision. The muons are not 
-detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the 
-solenoid. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the 
-discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of 
-the Higgs boson of the standard model (SM).
-
-There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs production 
-in association with vector boson (VH, V=W or Z), Higgs production with top quark and top anti-quark (ttH) and Higgs production with 
-a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the properties and the coupling 
-strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is gluon gluon fusion (ggF). As 
-bosons like gluons and photons are massless, they do not interact directly with the Higgs boson and processes like ggF or Higgs 
-boson decay to pair of photons are not possible at tree level and can only proceed via loop diagrams which involve W boson or top 
-quark in the loop. The Higgs boson can also decay to other particles and these decay channels have different branching fractions. 
-Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, muons and electrons. Higgs boson can also decay to 
-Z boson and a photon. It is also interesting to investigate some invisible decay modes of Higgs boson which can be used to put 
-upper bounds on dark matter-nucleon scattering cross section like in the Higgs-portal dark matter models.
-
-The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large number of
-free-parameters like fine structure constant \alpha, Weinberg angle or weak mixing angle \theta_W, the coupling constant of strong 
-interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, three mixing angles and the 
-CP-violating phase of the CKM matrix which tells us how quarks of different color charge mix with each other, nine yukawa couplings 
-which determine the mass of nine charged fermions and fine tunings related to the origin of masses robustly suggests new physics beyond 
-the SM (BSM).There are lot of specific beyond BSM theories and most of these models involve heavy fields. In order to identify which new 
-physics lies beyond the electroweak (EW) scale, the new parameters of such theories may be constrained by the actual, low energy, 
-experiments. This approach requires studying each model individually, and calculating every possible observable. There is another 
-approach immitating Fermi’s treatment of beta decay which consists of considering the SM as the first order approximation of the actual 
-theory and by completing it with a series of higher dimensional operators. When the electroweak symmetry breaking takes place well below 
-the mass of the new particles, the BSM physics is taken into account at the EW scale and below by adding higher dimensional operators to 
-the SM Lagrangian. They are built out of SM fields and supposed to be invariant under its gauge group. Those operators are the low-
-energy residue of the high energy theory. This approach does not pretend to guess the complete high-energy model and it is based solely 
-on the symmetry of the  theory. The operators are general and the only model dependence is encoded in the size of the operator 
-coefficients, which is to be set from experiments.
-
-The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard model predictions if these higher dimensional 
-operators are present in low energy effective SM theory. We can consider anomalous Higgs and Higgs-gauge effective dimension 6 operators 
-like \frac{1}{3}(\phi^{\dagger}\phi)^3, \frac{1}{2} \partial_{\mu} (\phi^{\dagger} \phi) \partial^{\mu}(\phi^{\dagger} \phi) and 
-(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} (D^{\mu} \phi) to calculate the deviation of Higgs boson-fermion couplings from SM. The 
-first operator shift the minimum of the Higgs potential. Also as there will be rescaling of the Higgs field due to the introduction of 
-these operators in the potential term, Higgs-fermion (quarks and leptons) couplings are modified. In the effective beyond standard model 
-theory, there are dimension 5 and dimension 6 operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and 
-dimension 6 operator dominate baryon minus lepton number symmetry conservation processes.
-
-The production of Higgs boson in association with single top quark is one of the rare Higgs boson production mode. As the top 
-quark is the heaviest fundamental particle in the standard model, due to its large mass, the top quark decay before 
-hardronization which allow the possibility to reconstruct top quark from its decay products unlike the lighter quarks which 
-undergo hardronization and are seen as bundles of particles in detector called jets. The most probable decay of top quark is into 
-bottom (b) quark and W boson. Using b-jet tagging algorithms, the jet originating from b-quark can be reconstructed to identity 
-the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and leptons is proportional to the mass of the 
-fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson which means that out of all known quarks, 
-top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa coupling y_t. That is why the Yukawa 
-coupling of the top quark with the Higgs boson y_t has lot of importance as any deviation from standard model prediction might 
-give an indication of new physics. The two processes at LHC which will allow us to directly probe the Yukawa coupling between 
-Higgs Boson and top quark are Higgs boson production in association with top quark pair (t\bar{t} H) via strong interaction and 
-the production of single top quark with a Higgs boson (tH). As tH occur via electroweak interaction, it is more rare than 
-t\bar{t}H production. The Higgs boson in the tH channel can be radiated off by a W boson or by a top quark. These two processes 
-in standard model have destructive interference which allow us to probe the relative sign between the coupling of top quark with 
-Higgs boson y_t and the coupling of W boson to the Higgs boson. If the Yukawa coupling between top quark and Higgs boson y_t 
-deviate from the SM prediction or even if y_t has a negative sign, both would cause a strong increase in the tH production cross 
-section which is a special property of tH production channel making it an interesting production channel to probe using LHC 
-2016, 2017 and 2018 data. The coupling strength modifier \kappa_t is defined as \kappa_t = \frac{y_t}{y^{SM}_t} which will tell us the 
-deviation of y_t from the SM prediction.
-
-The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. As there 
-is strong destructive inteference in the t-channel for the standard model couplings, this production mode is sensitive to both the sign 
-and the magnitude of any coupling beyond the SM between Higgs boson and top quark caused by higher dimensional operators in effective SM 
-theory.
+SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\
+\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
+particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
+weak nuclear force. Gravitational force is neglected as the strength of this force is very weak at the scales over which 
+elementary particle interact with each other. The standard model (SM) of particle physics is divided into two categories, 
+bosonic sector and fermionic sector. Bosonic sector contain particles called bosons which mediate the fundamental forces of 
+nature and the fermionic sector contain particles called fermions which make up all the matter in our universe. SM has three 
+generations of matter (fermions) particles. The first generation of fermions consists of up (u) quark, down (d) quark, electron 
+and electron neutrino, second generation consist of charm (c) quark, strange (s) quark, muon and muon neutrino and the third 
+generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
+bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong force, electromagnetic force and weak force respectively.
+There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism.
+Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
+\\
+Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
+These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
+discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
+energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
+colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.\\
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect 
+particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers 
+of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify 
+the charge of the particles to bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles 
+bent with very high precision. The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors 
+are outside to detect them once they have crossed the solenoid. In 2012, the ATLAS and CMS collaborations, with detectors at 
+two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all 
+measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
+production in association with vector boson (VH, V = W or Z), Higgs production with top quark and top anti-quark (t$\bar{t}$H) and Higgs 
+production with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
+properties and the coupling strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is 
+gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
+and processes like ggF or Higgs boson decay to pair of photons are not possible at tree level and can only proceed via loop 
+diagrams which involve W boson or top quark in the loop. The Higgs boson can also decay to other particles and these decay 
+channels have different branching fractions. Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, 
+muons and electrons. Higgs boson can also decay to Z boson and a photon. It is also interesting to investigate some invisible 
+decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the 
+Higgs-portal dark matter models. \\ 
+The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
+number of free-parameters like fine structure constant $\alpha$, Weinberg angle or weak mixing angle $\theta_W$, the coupling 
+constant of strong interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, 
+three mixing angles and the CP-violating phase of the CKM matrix which tells us how quarks of 
+different color charge mix with 
+each other, nine yukawa couplings which determine the mass of nine charged fermions and fine 
+tunings related to the origin of 
+masses robustly suggests new physics beyond Stanard model (BSM). There are lot of specific 
+BSM theories and most of these 
+models involve heavy fields. In order to identify which new physics lies beyond the 
+electroweak (EW) scale, the new parameters 
+of such theories may be constrained by the actual, low energy, experiments. This approach 
+requires studying each model 
+individually, and calculating every possible observable. There is another approach immitating 
+Fermi$’$s treatment of beta decay 
+which consists of considering the SM as the first order approximation of the actual theory 
+and by completing it with a series 
+of higher dimensional operators. When the electroweak symmetry breaking takes place well 
+below the mass of the new particles, 
+the BSM physics is taken into account at the EW scale and below by adding higher dimensional 
+operators to the SM Lagrangian. 
+They are built out of SM fields and supposed to be invariant under its gauge group. Those 
+operators are the low-energy residue 
+of the high energy theory. This approach does not pretend to guess the complete high-energy 
+model and it is based solely on 
+the symmetry of the  theory. The operators are general and the only model dependence is 
+encoded in the size of the operator 
+coefficients, which is to be set from experiments. \\
+The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
+model predictions if these higher 
+dimensional operators are present in low energy effective SM theory. We can consider 
+anomalous Higgs and Higgs-gauge effective 
+dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
+(\phi^{\dagger} \phi) 
+\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
+(D^{\mu} \phi)$ to calculate the 
+deviation of Higgs boson-fermion couplings from SM. The first operator shift the minimum of 
+the Higgs potential. Also as there 
+will be rescaling of the Higgs field due to the introduction of these operators in the 
+potential term, Higgs-fermion (quarks 
+and leptons) couplings are modified. In the effective beyond standard model theory, there are 
+dimension 5 and dimension 6 
+operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and 
+dimension 6 operator dominate baryon 
+minus lepton number symmetry conservation processes. \\
+The production of Higgs boson in association with single top quark is one of the rare Higgs 
+boson production mode. As the top 
+quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
+top quark decay before 
+hardronization which allow the possibility to reconstruct top quark from its decay products 
+unlike the lighter quarks which 
+undergo hardronization and are seen as bundles of particles in detector called jets. The most 
+probable decay of top quark is 
+into bottom (b) quark and W boson \cite{nishiwaki2014tth}. Using b-jet tagging algorithms, the jet originating from 
+b-quark can be reconstructed to 
+identity the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and 
+leptons is proportional to the mass 
+of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
+which means that out of all known 
+quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
+coupling $y_t$. That is why the 
+Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 
+deviation from standard model prediction might give an indication of new physics. The two 
+processes at LHC which will allow us to directly probe the Yukawa 
+coupling between Higgs Boson and top quark are Higgs boson production in association with top 
+quark pair (t$\bar{t}$H) via 
+strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
+occur via electroweak interaction, it 
+is more rare than t$\bar{t}$H production. The Higgs boson in the tH channel can be radiated 
+off by a W boson or by a top 
+quark. These two processes in standard model have destructive interference which allow us to 
+probe the relative sign between 
+the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
+boson. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
+prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
+production cross section which is a special property of tH production channel making it an 
+interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
+strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
+us the deviation of $y_t$ from the SM prediction \cite{sirunyan2019search}. 
+The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
+quark associated production mode. 
+The anomalous coupling will arise when we add interaction terms (dimension 6 operators in 
+effective SM theory) in the Higgs 
+potential. As there is strong destructive inteference in the t-channel for the standard model 
+couplings, this production mode 
+is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs 
+boson and top quark induced by 
+higher dimensional operators in effective SM theory.
 
@@
 
-In this project, it is proposed to study the production channel of the Higgs boson associated with a single top quark in the Large 
-Hadron Collider of the CERN laboratory. The measurement of this process complements other measurements of the yukawa coupling parameter 
-of the top quark and Higgs boson. It is a part of the physics program of CMS international collaborations and ATLAS and it has not been 
-observed so far. It is proposed to study sensitivity with the current data in the channel where the events are identified with two muons 
-of the same sign. The impact of uncertainties will be studied and projections will be made to the future phases of the LHC. For these 
-studies the data of the run two (2015-2018) of the LHC identifying the signal events with two muons from the same sign. It is also 
-expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began in 2026.
+\onehalfspacing In this project, it is proposed to study the production channel of the Higgs boson associated 
+with a single top quark in the Large Hadron Collider of the CERN laboratory. The measurement 
+of this process complements other measurements of the yukawa coupling parameter of the top 
+quark and Higgs boson. It is a part of the physics program of CMS international 
+collaborations and ATLAS and it has not been observed so far. It is proposed to study 
+sensitivity with the current data in the channel where the events are identified with two 
+muons of the same sign. The impact of uncertainties will be studied and projections will be 
+made to the future phases of the LHC. For these studies the data of the run two (2015-2018) 
+of the LHC identifying the signal events with two muons from the same sign. It is also 
+expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began 
+in 2026.
 
@@
 
-There is currently a great enigma in physics since we know that ordinary matter comprises only 5 \% of the universe, another 
-25 \% includes what we call dark matter. Understanding the production of the Higgs boson, as well as its decays like the invisible 
-decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new 
-particles. Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) 
-in proton-proton collisions with the CMS experiment of the LHC.
-We will study the distribution of events in one of the decay channels and the sensitivity that we get with the current data.
-The main objective is to search for new processes such as tH Higgs production mode in the CMS experiment which require to study different aspects such as the model of the noises that are made by simulation, techniques of adjustments to the data that incorporate the different noises and the signal, and estimates of statistical and systematic uncertainties.
-
-Some of the objectives in this project include:
-• study one or more decay channels,
-• verify that simulation of signal events is adequate,
-• study the extraction of signal strength through adjustments to the data,
-• study the impact of statistical and systematic uncertainties.
+\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises 
+only $5\%$ of the universe, another 
+$25\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
+well as its decays like the invisible decay modes are an important part of the physics 
+program of CERN laboratory experiments to verify the Standard Model and look for new 
+particles. Through this project we will investigate the production of the Higgs boson in 
+association with a single top quark (tH) in proton-proton collisions with the CMS experiment 
+of the LHC. We will study the distribution of events in one of the decay channels and the 
+sensitivity that we get with the current data. The main objective is to search for new 
+processes such as tH Higgs production mode in the CMS experiment which require to study 
+different aspects such as the model of the noises that are made by simulation, techniques of 
+adjustments to the data that incorporate the different noises and the signal, and estimates 
+of statistical and systematic uncertainties.
+Some of the objectives in this project include:\\
+\begin{itemize}
+\item study one or more decay channels.\\
+\item verify that simulation of signal events is adequate.\\
+\item study the extraction of signal strength through adjustments to the data.\\
+\item study the impact of statistical and systematic uncertainties.\\
+\end{itemize}
 
@@
 
-Production studies in the tH channel have already started with the collaborations CMS and ATLAS with publications based on data from the 
-2011-2012 run and some data from the second run of 2015-2016. In these results it was not found signal evidence and upper limits have 
-been set for the effective section. With the more sensitive analysis an upper limit is calculated for the effective section of a signal 
-composed of tH and ttH that corresponds 3.1 times that expected in the SM. In this analysis the reconstruction methods do not allow to 
-distinguish between tH and ttH because the effective section of ttH is much larger than that of tH and some events pass the
-selections designed for tH, the fraction of tH events over tH + ttH is 5 \%. In BSM models the fraction could change up to 50 \%, for 
-example with \kappa_t = -1. It could help to obtain better limits for the production of tH. The data that has been used so far 
-correspond to only 20 \% of the final data of the run that which ends in 2018. The uncertainty for the signal in the current analysis is 
-mostly statistical nature, therefore adding the total data in a new analysis the next year, sensitivity can be improved with an 
-approximate factor of 2.2. Additionally, in subsequent phases of the LHC 2021-2023 and 2026-2038 the number of data fold and then 
-multiply by 10 respectively. With these additions It is expected that the signal from the Higgs boson can be observed on the tH 
-production channel. The current results can be used to project sensitivity in the third run and the high brightness phase and thus 
-contribute to the planning of the updates of the detector.
+\onehalfspacing Production studies in the tH channel have already started with the collaborations CMS and 
+ATLAS with publications based on data from the 2011-2012 run and some data from the second 
+run of 2015-2016. In these results it was not found signal evidence and upper limits have 
+been set for the effective section. With the more sensitive analysis an upper limit is 
+calculated for the effective section of a signal composed of tH and ttH that corresponds 3.1 
+times that expected in the SM. In this analysis the reconstruction methods do not allow to 
+distinguish between tH and t$\bar{t}$H because the effective section of t$\bar{t}$H is much 
+larger than that of tH and some events pass the selections designed for tH, the fraction of 
+tH events over tH + t$\bar{t}$H is 5. In BSM models the fraction could change up to 50, for 
+example with $\kappa_t = -1$. It could help to obtain better limits for the production of tH. 
+The data that has been used so far correspond to only 20 of the final data of the run that 
+which ends in 2018. The uncertainty for the signal in the current analysis is mostly 
+statistical nature, therefore adding the total data in a new analysis the next year, 
+sensitivity can be improved with an approximate factor of 2.2. Additionally, in subsequent 
+phases of the LHC 2021-2023 and 2026-2038 the number of data fold and then multiply by 10 
+respectively. With these additions It is expected that the signal from the Higgs boson can be 
+observed on the tH production channel. The current results can be used to project sensitivity 
+in the third run and the high brightness phase and thus contribute to the planning of the 
+updates of the detector.
 
@@
 
-Aspects of simulation of signal production are studied based on generators that simulate the interactions of quarks and gluons taking 
-into account the probability distributions of each type of particle. These are packages of software that are controlled with 
-configuration files that define various aspects of such as decay channels, energy in the center of mass and refinements in the development of the jets that are generated by the strong interaction of the quarks.
-The reconstruction and selection of tH events requires the use of central software of the CMS collaboration.
-This software contains the algorithms that reconstruct the charged and neutral particles starting from the energy deposits in the different parts of the detector.
-These particles include leptons, photons and hadrons which have a life time that allows them to leave the interaction region.
-These particles are used to identify the production of the top and the Higgs boson.
-In the case of the top quark, it usually decays to a bottom (b) quark and a W boson.
-Subsequently the W decays to two leptons or two quarks.
-Reconstruction requires finding a type b and two jet leptons.
-Improvements in this reconstruction can be done by studying the distributions of transverse momentum, the angular distributions of the different particles, and others properties.
+\onehalfspacing Aspects of simulation of signal production are studied based on generators that simulate the 
+interactions of quarks and gluons taking into account the probability distributions of each 
+type of particle. These are packages of software that are controlled with configuration files 
+that define various aspects of such as decay channels, energy in the center of mass and 
+refinements in the development of the jets that are generated by the strong interaction of 
+the quarks. The reconstruction and selection of tH events requires the use of central 
+software of the CMS collaboration. This software contains the algorithms that reconstruct the 
+charged and neutral particles starting from the energy deposits in the different parts of the 
+detector. These particles include leptons, photons and hadrons which have a life time that 
+allows them to leave the interaction region. These particles are used to identify the 
+production of the top and the Higgs boson. In the case of the top quark, it usually decays to 
+a bottom (b) quark and a W boson. Subsequently the W decays to two leptons or two quarks. 
+Reconstruction requires finding a type b and two jet leptons. Improvements in this 
+reconstruction can be done by studying the distributions of transverse momentum, the angular 
+distributions of the different particles, and others properties.
 
@@
 
+\section{figures}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 1}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 2}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 3}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
+  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
+Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
+show instant brightness while the line shows brightness accumulated}
+   \label{figure 4}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
+  \caption{Higgs boson production in association with single top quark in proton collisions}
+   \label{figure 5}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 6}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 7}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 8}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms10.png}
+  \caption{Elementary particles in standatd model of particle physics}
+   \label{figure 9}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
+  \caption{Important production processes of the Higgs boson in proton collisions}
+   \label{figure 10}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
+  \caption{Higgs boson production in association with top quark top anti-quark in proton collisions}
+   \label{figure 11}
+\end{figure}
+
 \end{document}
+
+\end{document}

### 2019-11-06 project_ashish/paper.tex
changes

@@
 
-\author[]{Ashish Sehrawat}
-%\author[]{Director: Dr. Jose Feliciano Benitez Rubio}
+\author[]{Ashish Sehrawat$^a$}
+\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}
 
@@
 \address[mymainaddress]{Universidad de Sonora}
-%\address[mysecondaryaddress]{360 Park Avenue South, New York}
+%\address[mysecondaryaddress]{Universidad de Sonora}
 
-%\begin{keyword}\rm
-%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
-%The paper...
-%\end{adjustwidth}
-%\end{keyword}
+\begin{keyword}\rm
+\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
+Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
+\end{adjustwidth}
+\end{keyword}
 
@@
 \section{BACKGROUND}
-\cite{Dirac1953888}
 
--SM, Higgs, couplings, previous Higgs measurements, previous tH searches
-
-SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\
+-SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\
 \onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
@@
 individually, and calculating every possible observable. There is another approach immitating 
-Fermi$’$s treatment of beta decay 
+Fermi's treatment of beta decay 
 which consists of considering the SM as the first order approximation of the actual theory 
@@
 \section{GENERAL OBJECTIVE}
-- motivation, tH production crossection, sign of k_t, search for BSM, ..
+- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
 
@@
 only $5\%$ of the universe, another 
-$25\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
+$27\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
 well as its decays like the invisible decay modes are an important part of the physics 
@@
 
-%\section{SPECIFIC OBJECTIVES}
-%- details
+\section{SPECIFIC OBJECTIVES}
+- details
 
@@
 
-\section{figures}
+\newpage
+\cleanpage
 
@@
 \end{document}
-
-\end{document}

### 2019-11-07 project_ashish/paper.tex
Hi modified files

@@
 tunings related to the origin of 
-masses robustly suggests new physics beyond Stanard model (BSM). There are lot of specific 
+masses robustly suggests new physics beyond Standard model (BSM). There are lot of specific 
 BSM theories and most of these 
@@
 potential term, Higgs-fermion (quarks 
-and leptons) couplings are modified. In the effective beyond standard model theory, there are 
+and leptons) couplings are modified. In the effective standard model theory, there are 
 dimension 5 and dimension 6 
@@
    \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
-  \caption{Important production processes of the Higgs boson in proton collisions}
+  \caption{Important production processes of the Higgs boson in proton collisions.}
    \label{figure 1}
@@
    \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
-  \caption{Important production processes of the Higgs boson in proton collisions}
+  \caption{Important production processes of the Higgs boson in proton collisions.}
    \label{figure 2}
@@
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
-  \caption{Important production processes of the Higgs boson in proton collisions}
-   \label{figure 3}
-\end{figure}
+%\begin{figure}
+ % \centering
+  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
+ % \caption{Important production processes of the Higgs boson in proton collisions}
+  % \label{figure 3}
+%\end{figure}
 
@@
 Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
-show instant brightness while the line shows brightness accumulated}
+show instant brightness while the line shows brightness accumulated.}
    \label{figure 4}
@@
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
-  \caption{Higgs boson production in association with single top quark in proton collisions}
-   \label{figure 5}
-\end{figure}
+%\begin{figure}
+ % \centering
+  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
+  %\caption{Higgs boson production in association with single top quark in proton collisions}
+  % \label{figure 5}
+%\end{figure}
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
-  \caption{Important production processes of the Higgs boson in proton collisions}
-   \label{figure 6}
-\end{figure}
+%\begin{figure}
+ % \centering
+  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
+ % \caption{Important production processes of the Higgs boson in proton collisions}
+  % \label{figure 6}
+%\end{figure}
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
-  \caption{Important production processes of the Higgs boson in proton collisions}
-   \label{figure 7}
-\end{figure}
+%\begin{figure}
+ % \centering
+  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
+ % \caption{Important production processes of the Higgs boson in proton collisions}
+  % \label{figure 7}
+%\end{figure}
 
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
-  \caption{Important production processes of the Higgs boson in proton collisions}
-   \label{figure 8}
-\end{figure}
+%\begin{figure}
+ % \centering
+  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
+ % \caption{Important}
+  % \label{figure 8}
+%\end{figure}
 
@@
    \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms10.png}
-  \caption{Elementary particles in standatd model of particle physics}
+  \caption{Elementary particles in standard model of particle physics.}
    \label{figure 9}
@@
    \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
-  \caption{Important production processes of the Higgs boson in proton collisions}
+  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
    \label{figure 10}
+\end{figure}
+
+%\begin{figure}
+ % \centering
+  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
+ % \caption{Higgs boson production in association with top quark top anti-quark in proton collisions}
+  % \label{figure 11}
+%\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
+  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
+   \label{figure 12}
 \end{figure}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
-  \caption{Higgs boson production in association with top quark top anti-quark in proton collisions}
-   \label{figure 11}
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
+  \caption{Standard model Higgs boson production cross section in various production modes.}
+   \label{figure 13}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
+  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
+   \label{figure 14}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd3.png}
+  \caption{Standard model Higgs boson branching ratios in various decay channels.}
+   \label{figure 15}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd4.png}
+  \caption{Various LHC run and corresponding integrated luminosities.}
+   \label{figure 16}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
+  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
+   \label{figure 17}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
+  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
+   \label{figure 18}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
+  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
+   \label{figure 19}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
+  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
+   \label{figure 20}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
+  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
+energy.}
+   \label{figure 21}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
+  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
+   \label{figure 22}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
+  \caption{Lowest order Feynman diagrams for s-channel tH production.}
+   \label{figure 22}
 \end{figure}

### 2019-11-07 project_ashish/paper.tex
modified file

@@
 -SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\
+
 \onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
@@
 There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism.
-Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
-\\
+Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.\\
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd11.png}
+  \caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
+   \label{figure 1}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
+  \caption{Important production processes of Standard model the Higgs boson in proton collisions.}
+   \label{figure 2}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
+  \caption{Important production processes of the Higgs boson in proton collisions.}
+   \label{figure 3}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
+  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+   \label{figure 4}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
+  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
+Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
+show instant brightness while the line shows brightness accumulated.}
+   \label{figure 5}
+\end{figure}
+
 Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
@@
 energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
-colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.\\
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect 
-particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers 
-of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify 
-the charge of the particles to bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 
-million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles 
-bent with very high precision. The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors 
-are outside to detect them once they have crossed the solenoid. In 2012, the ATLAS and CMS collaborations, with detectors at 
-two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all 
-measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
+It is designed to detect particles known as muons very accurately.
+The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
+Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
+A silicon tracker, made of about 75
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).\\
+
 There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
@@
 Higgs-portal dark matter models. \\
+
 The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
@@
 coefficients, which is to be set from experiments. \\
+
 The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
@@
 minus lepton number symmetry conservation processes. \\
+
 The production of Higgs boson in association with single top quark is one of the rare Higgs 
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
-  \caption{Important production processes of the Higgs boson in proton collisions.}
-   \label{figure 1}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
-  \caption{Important production processes of the Higgs boson in proton collisions.}
-   \label{figure 2}
-\end{figure}
-
-%\begin{figure}
- % \centering
-  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/newtHq.png}
- % \caption{Important production processes of the Higgs boson in proton collisions}
-  % \label{figure 3}
-%\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
-  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
-Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
-show instant brightness while the line shows brightness accumulated.}
-   \label{figure 4}
-\end{figure}
-
-%\begin{figure}
- % \centering
-  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
-  %\caption{Higgs boson production in association with single top quark in proton collisions}
-  % \label{figure 5}
-%\end{figure}
-
-%\begin{figure}
- % \centering
-  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms1.png}
- % \caption{Important production processes of the Higgs boson in proton collisions}
-  % \label{figure 6}
-%\end{figure}
-
-%\begin{figure}
- % \centering
-  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms2.png}
- % \caption{Important production processes of the Higgs boson in proton collisions}
-  % \label{figure 7}
-%\end{figure}
-
-%\begin{figure}
- % \centering
-  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms3.png}
- % \caption{Important}
-  % \label{figure 8}
-%\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms10.png}
-  \caption{Elementary particles in standard model of particle physics.}
-   \label{figure 9}
-\end{figure}
-
-\begin{figure}
-  \centering
    \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
@@
 \end{figure}
-
-%\begin{figure}
- % \centering
-  % \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
- % \caption{Higgs boson production in association with top quark top anti-quark in proton collisions}
-  % \label{figure 11}
-%\end{figure}
 
@@
    \label{figure 15}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd4.png}
-  \caption{Various LHC run and corresponding integrated luminosities.}
-   \label{figure 16}
 \end{figure}

### 2019-11-07 project_ashish/paper.tex
commit

@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/pg.png}
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
   \caption{Important production processes of Standard model the Higgs boson in proton collisions.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/tq.png}
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
   \caption{Important production processes of the Higgs boson in proton collisions.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
@@
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/lum6.png}
+  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
   \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
@@
    \label{figure 5}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
+  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+   \label{figure 6}
 \end{figure}
@@
 \section{PROPOSAL}
+
 - what we will do:  search for tH events, using which channels.
@@
 \section{GENERAL OBJECTIVE}
+
 - motivation, tH production crossection, sign of $k_t$, search for BSM, ..

### 2019-11-07 project_ashish/paper.tex
commit

@@
    \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
-  \caption{Important production processes of Standard model the Higgs boson in proton collisions.}
+  \caption{Important production processes of Standard model Higgs boson in proton collisions.}
    \label{figure 2}
@@
    \label{figure 6}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
+  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
+   \label{figure 7}
 \end{figure}

### 2019-11-07 project_ashish/paper.tex
commit

@@
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms5.png}
+  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
   \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
@@
 The production of Higgs boson in association with single top quark is one of the rare Higgs 
-boson production mode. As the top 
+boson production mode \cite{Khachatryan_2016}. As the top 
 quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
@@
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production. The Higgs boson in the tH channel can be radiated 
+is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
 off by a W boson or by a top 
@@
 the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
-boson. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
+boson \cite{choudhury2019search}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
 prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
@@
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction \cite{sirunyan2019search}. 
+us the deviation of $y_t$ from the SM prediction. 
 The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
@@
 boson and top quark induced by 
-higher dimensional operators in effective SM theory.
+higher dimensional operators in effective SM theory \cite{sirunyan2019search}.
 

### 2019-11-07 project_ashish/paper.tex
commit

@@
 bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong force, electromagnetic force and weak force respectively.
-There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism.
+There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
 Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.\\
@@
 quarks, top quark couple most strongly to the Higgs boson. So, it has a large value of Yukawa 
-coupling $y_t$. That is why the 
+coupling $y_t$ \cite{Aad_2016}. That is why the 
 Yukawa coupling of the top quark with the Higgs boson $y_t$ has lot of importance as any 

### 2019-11-08 project_ashish/paper.tex
commit

@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
-  \caption{Important production processes of Standard model Higgs boson in proton collisions.}
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/cms12.png}
+  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
    \label{figure 2}
@@
   \centering
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
+  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
+   \label{figure 3}
+\end{figure}
+
+\begin{figure}
+  \centering
    \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
-  \caption{Important production processes of the Higgs boson in proton collisions.}
-   \label{figure 3}
+  \caption{Higgs production using the top quark (left) and W boson (right).}
+   \label{figure 4}
 \end{figure}
@@
   \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-   \label{figure 4}
+   \label{figure 5}
 \end{figure}
@@
 show instant brightness while the line shows brightness accumulated.}
-   \label{figure 5}
+   \label{figure 6}
 \end{figure}
@@
   \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
-   \label{figure 6}
+   \label{figure 7}
 \end{figure}
@@
   \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
-   \label{figure 7}
+   \label{figure 8}
 \end{figure}
@@
 million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid \cite{Chatrchyan:2008aa}.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
@@
   \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
-   \label{figure 10}
+   \label{figure 9}
 \end{figure}
@@
   \caption{Leading order Feynman Diagrams for various Higgs production modes.}
-   \label{figure 12}
+   \label{figure 10}
 \end{figure}
@@
   \caption{Standard model Higgs boson production cross section in various production modes.}
-   \label{figure 13}
+   \label{figure 11}
 \end{figure}
@@
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-   \label{figure 14}
+   \label{figure 12}
 \end{figure}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd3.png}
+   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd3.png}
   \caption{Standard model Higgs boson branching ratios in various decay channels.}
-   \label{figure 15}
+   \label{figure 13}
 \end{figure}
@@
   \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
-   \label{figure 17}
+   \label{figure 14}
 \end{figure}
@@
   \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
-   \label{figure 18}
+   \label{figure 15}
 \end{figure}
@@
   \caption{ATLAS-CMS combined measurements of coupling modifiers.}
-   \label{figure 19}
+   \label{figure 16}
 \end{figure}
@@
   \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
-   \label{figure 20}
+   \label{figure 17}
 \end{figure}
@@
 energy.}
-   \label{figure 21}
+   \label{figure 18}
 \end{figure}
@@
   \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
-   \label{figure 22}
+   \label{figure 19}
 \end{figure}
@@
   \caption{Lowest order Feynman diagrams for s-channel tH production.}
-   \label{figure 22}
+   \label{figure 20}
 \end{figure}

### 2019-11-08 project_ashish/paper.tex
commit

@@
 There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
+All the standard model particles are shown in Figure 1.
 Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.\\
@@
 A silicon tracker, made of about 75
-million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid \cite{Chatrchyan:2008aa}.
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 2.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).\\
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+The luminosity performance of LHC is shown in Figure 6.
+\\
 
@@
 channels have different branching fractions. Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, 
-muons and electrons. Higgs boson can also decay to Z boson and a photon. It is also interesting to investigate some invisible 
+muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 3. It is also interesting to investigate some invisible 
 decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the 
@@
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
+is more rare than t$\bar{t}$H production \cite{sirunyan2018search}.
+THe Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 8.
+The Higgs boson in the tH channel can be radiated
 off by a W boson or by a top 
-quark. These two processes in standard model have destructive interference which allow us to 
+quark as shown in Figure 4 and 7. These two processes in standard model have destructive interference which allow us to 
 probe the relative sign between 
@@
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction. 
+us the deviation of $y_t$ from the SM prediction as shown in Figure 5. 
 The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 

### 2019-11-08 project_ashish/paper.tex
commit

@@
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
-  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
-Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
+  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates for prolonged stops (LS) of the LHC and luminosities. Points
 show instant brightness while the line shows brightness accumulated.}

### 2019-11-08 project_ashish/paper.tex
commit

@@
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
-  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
+  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
    \label{figure 8}

### 2019-11-08 project_ashish/paper.tex
commit

@@
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
-  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates for prolonged stops (LS) of the LHC and luminosities. Points
+  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
 show instant brightness while the line shows brightness accumulated.}
@@
 So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
-The luminosity performance of LHC is shown in Figure 6.
+LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 \times 10^{33} $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
+LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 6.
 \\

### 2019-11-08 project_ashish/paper.tex
commit

@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd11.png}
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd11.png}
   \caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cms12.png}
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
   \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
   \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
   \caption{Higgs production using the top quark (left) and W boson (right).}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
@@
   \centering
-  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
   \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
@@
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
+  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
   \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
@@
   \centering
-  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
   \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms7.jpg}
   \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd.png}
   \caption{Leading order Feynman Diagrams for various Higgs production modes.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd1.png}
   \caption{Standard model Higgs boson production cross section in various production modes.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd2.png}
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd3.png}
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd3.png}
   \caption{Standard model Higgs boson branching ratios in various decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd5.png}
   \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd6.png}
   \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling modifiers.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th.png}
   \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th1.png}
   \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th2.png}
   \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th3.png}
   \caption{Lowest order Feynman diagrams for s-channel tH production.}

### 2019-11-08 BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/compare_variables.C
new

@@ -35,18 +35,18 @@ void compare_variables(){
   C.Print("compare_variables.pdf");
 
 
+
   ///compare one variable
-  TH1F H1("H1","",20,-5,5);
-  TH1F H2("H2","",20,-5,5);
+  TH1F H1("H1","",5,-3,3);
+  TH1F H2("H2","",5,-3,3);
 
 
- t1.Draw("fj_eta>>H1");
- t2.Draw("fj_eta>>H2");
 
- //t3.Draw("fj_eta>>H3");
+ t1.Draw("(l1_ch+l2_ch)>>H1","(l1_ch+l2_ch)!=0>>H1");
+ t2.Draw("(l1_ch+l2_ch)>>H2","(l1_ch+l2_ch)!=0>>H2");
+
   H1.Scale(1.0/H1.Integral());
   H2.Scale(1.0/H2.Integral());
-
 
   H1.SetLineColor(kBlue);
   H2.SetLineColor(kRed);
@@ -54,16 +54,16 @@ void compare_variables(){
   C.Clear();
 
   H1.Draw("hist");
-    H2.Draw("histsame");
+  H2.Draw("histsame");
 
   //
-  H1.SetAxisRange(0,0.15,"Y");
-  H1.SetAxisRange(-6,6,"X");
+  //H1.SetAxisRange(0,0.2,"Y");
+  H1.SetAxisRange(-4,4,"X");
   H1.SetYTitle("Events normalized to unit area");
   H1.SetStats(0);
-  H1.SetXTitle("Forward Jet #eta");
+  H1.SetXTitle("Number of untagged jets with |#eta|>1.0");
 
-  auto legend = new TLegend(0.7,0.7,0.84,0.84);
+  auto legend = new TLegend(0.75,0.75,0.89,0.89);
   legend->AddEntry("H1","tHq","l");
   legend->AddEntry("H2","t#bar{t}W","l");
   legend->SetBorderSize(0);
@@ -71,8 +71,8 @@ void compare_variables(){
   legend->SetEntrySeparation(0.5);
   legend->Draw();
 
-  C.Print("compare_variables.eps");
   C.Print("compare_variables.png");
+  C.Print("compare_variables.eps");
   C.Print("compare_variables.pdf");
   //compare correlations
   C.Clear();

### 2019-11-08 project_ashish/paper.tex
Update paper.tex

--- 2019-11-08 project_ashish/paper.tex
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd11.png}
+   \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/cd11.png}
   \caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cms12.png}
+   \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/cms12.png}
   \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
+   \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/pg.png}
   \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
+   \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/tq.png}
   \caption{Higgs production using the top quark (left) and W boson (right).}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
@@
   \centering
-  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
+  \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/lum6.png}
   \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
@@
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
+  \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cms.png}
   \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
@@
   \centering
-  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
+  \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/cms5.png}
   \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cms7.jpg}
   \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cd.png}
   \caption{Leading order Feynman Diagrams for various Higgs production modes.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cd1.png}
   \caption{Standard model Higgs boson production cross section in various production modes.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cd2.png}
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd3.png}
+   \includegraphics[scale=0.5]{/tHqCMSAnalysis/project_ashish/cd3.png}
   \caption{Standard model Higgs boson branching ratios in various decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cd5.png}
   \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cd6.png}
   \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling modifiers.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/th.png}
   \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/th1.png}
   \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/th2.png}
   \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
+   \includegraphics[width=\columnwidth]{/tHqCMSAnalysis/project_ashish/th3.png}
   \caption{Lowest order Feynman diagrams for s-channel tH production.}

### 2019-11-08 project_ashish/paper.tex
Update paper.tex

--- 2019-11-08 project_ashish/paper.tex
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd11.png}
+   \includegraphics[scale=0.5]{./cd11.png}
   \caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cms12.png}
+   \includegraphics[scale=0.5]{./cms12.png}
   \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
+   \includegraphics[scale=0.5]{./pg.png}
   \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
+   \includegraphics[scale=0.5]{./tq.png}
   \caption{Higgs production using the top quark (left) and W boson (right).}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[scale=0.5]{./cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
@@
   \centering
-  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
+  \includegraphics[scale=0.5]{./lum6.png}
   \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
@@
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
+  \includegraphics[width=\columnwidth]{./cms.png}
   \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
@@
   \centering
-  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
+  \includegraphics[scale=0.5]{./cms5.png}
   \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
+   \includegraphics[width=\columnwidth]{./cms7.jpg}
   \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
+   \includegraphics[width=\columnwidth]{./cd.png}
   \caption{Leading order Feynman Diagrams for various Higgs production modes.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
+   \includegraphics[width=\columnwidth]{./cd1.png}
   \caption{Standard model Higgs boson production cross section in various production modes.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
+   \includegraphics[width=\columnwidth]{./cd2.png}
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd3.png}
+   \includegraphics[scale=0.5]{./cd3.png}
   \caption{Standard model Higgs boson branching ratios in various decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
+   \includegraphics[width=\columnwidth]{./cd5.png}
   \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
+   \includegraphics[width=\columnwidth]{./cd6.png}
   \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
+   \includegraphics[width=\columnwidth]{./cd7.png}
   \caption{ATLAS-CMS combined measurements of coupling modifiers.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
+   \includegraphics[width=\columnwidth]{./th.png}
   \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
+   \includegraphics[width=\columnwidth]{./th1.png}
   \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
+   \includegraphics[width=\columnwidth]{./th2.png}
   \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
+   \includegraphics[width=\columnwidth]{./th3.png}
   \caption{Lowest order Feynman diagrams for s-channel tH production.}

### 2019-11-09 BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/compare_variables.C
distribution

@@ -37,13 +37,11 @@ void compare_variables(){
 
 
   ///compare one variable
-  TH1F H1("H1","",5,-3,3);
-  TH1F H2("H2","",5,-3,3);
+  TH1F H1("H1","",50,0,7);
+  TH1F H2("H2","",50,0,7);
 
-
-
- t1.Draw("(l1_ch+l2_ch)>>H1","(l1_ch+l2_ch)!=0>>H1");
- t2.Draw("(l1_ch+l2_ch)>>H2","(l1_ch+l2_ch)!=0>>H2");
+  t1.Draw("deta_fj_l>>H1");
+  t2.Draw("deta_fj_l>>H2");
 
   H1.Scale(1.0/H1.Integral());
   H2.Scale(1.0/H2.Integral());
@@ -57,13 +55,13 @@ void compare_variables(){
   H2.Draw("histsame");
 
   //
-  //H1.SetAxisRange(0,0.2,"Y");
-  H1.SetAxisRange(-4,4,"X");
+  H1.SetAxisRange(0,0.1,"Y");
+  H1.SetAxisRange(0,8,"X");
   H1.SetYTitle("Events normalized to unit area");
   H1.SetStats(0);
-  H1.SetXTitle("Number of untagged jets with |#eta|>1.0");
+  H1.SetXTitle("#Delta#eta between forward light jet and closest lepton");
 
-  auto legend = new TLegend(0.75,0.75,0.89,0.89);
+  auto legend = new TLegend(0.8,0.7,0.86,0.8);
   legend->AddEntry("H1","tHq","l");
   legend->AddEntry("H2","t#bar{t}W","l");
   legend->SetBorderSize(0);

### 2019-11-09 project_ashish/paper.tex
commit

--- 2019-11-08 project_ashish/paper.tex
@@
 
-\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
+The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
 particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
@@
 
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
-   \label{figure 2}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
-  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
-   \label{figure 3}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
-  \caption{Higgs production using the top quark (left) and W boson (right).}
-   \label{figure 4}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
-  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-   \label{figure 5}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
-  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
-show instant brightness while the line shows brightness accumulated.}
-   \label{figure 6}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
-  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
-   \label{figure 7}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
-  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
-   \label{figure 8}
-\end{figure}
-
-Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
-discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
-energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
-colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
-It is designed to detect particles known as muons very accurately.
-The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
-A silicon tracker, made of about 75
-million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 2.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
-LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 \times 10^{33} $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
-All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
-LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 6.
-\\
-
 There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
@@
 channels have different branching fractions. Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, 
-muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 3. It is also interesting to investigate some invisible 
+muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 2. It is also interesting to investigate some invisible 
 decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the 
-Higgs-portal dark matter models. \\
+Higgs-portal dark matter models.\\
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
+  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
+   \label{figure 2}
+\end{figure}
 
@@
 encoded in the size of the operator 
-coefficients, which is to be set from experiments. \\
+coefficients, which is to be set from experiments.\\
 
@@
 dimension 6 operator dominate baryon 
-minus lepton number symmetry conservation processes. \\
+minus lepton number symmetry conservation processes.\\
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
+  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+   \label{figure 3}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
+  \caption{Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
+   \label{figure 4}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms13.png}
+  \caption{Scan of $−2Δln(L)$ versus $κ_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
+   \label{figure 5}
+\end{figure}
+
+Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
+These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
+discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
+energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
+colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
+It is designed to detect particles known as muons very accurately.
+The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
+Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
+A silicon tracker, made of about 75
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 6.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 \times 10^{33} $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
+LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 7.
+\\
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
+  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
+   \label{figure 6}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
+  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
+show instant brightness while the line shows brightness accumulated.}
+   \label{figure 7}
+\end{figure}
 
@@
 is more rare than t$\bar{t}$H production \cite{sirunyan2018search}.
-THe Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 8.
+The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 8.
 The Higgs boson in the tH channel can be radiated
 off by a W boson or by a top 
-quark as shown in Figure 4 and 7. These two processes in standard model have destructive interference which allow us to 
+quark as shown in Figure 8 and 9. These two processes in standard model have destructive interference which allow us to 
 probe the relative sign between 
@@
 
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
+  \caption{Higgs production using the top quark (left) and W boson (right).}
+  \label{figure 8}
+
+  \begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
+  \caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+   \label{figure 9}
+\end{figure}
+
 \section{PROPOSAL}
@@
 
-\onehalfspacing In this project, it is proposed to study the production channel of the Higgs boson associated 
+In this project, it is proposed to study the production channel of the Higgs boson associated 
 with a single top quark in the Large Hadron Collider of the CERN laboratory. The measurement 
@@
 
-\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises 
+There is currently a great enigma in physics since we know that ordinary matter comprises 
 only $5\%$ of the universe, another 
@@
 
-\onehalfspacing Production studies in the tH channel have already started with the collaborations CMS and 
+Production studies in the tH channel have already started with the collaborations CMS and 
 ATLAS with publications based on data from the 2011-2012 run and some data from the second 
@@
 
-\onehalfspacing Aspects of simulation of signal production are studied based on generators that simulate the 
+Aspects of simulation of signal production are studied based on generators that simulate the 
 interactions of quarks and gluons taking into account the probability distributions of each 

### 2019-11-09 presentacion_hiram/presentacion-tesis.tex
distribution

@@
 \newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
+		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
 \begin{document}
@@
 \begin{frame}
-\subsection{Higgs production mechanisms}
+\subsection{Higgs production mechanisms and decays}
 \frametitle{Higgs production mechanisms}
@@
 \begin{frame}
-\subsection{Production cross section}
 \frametitle{Cross section}
@@
 \begin{frame}
+\frametitle{Backgrounds}
+\begin{itemize}
+	\item Backgrounds are considered information in the data that is not the signal. 
+	\item Backgrounds share certain characteristics of the signal.
+	\item Backgrounds are a big factor in the statistical of the signal.
+\end{itemize}
+\end{frame}
+
+\begin{frame}
 \subsection{Event selection}
@@
 \end{frame}
+
 \begin{frame}
 \subsection{BDT}
-\frametitle{Boosted decision tree (BDT)}
-\begin{itemize}
-\item A decision tree takes a set of input features and splits input data recursively based on
-those features.
-Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
-\item The BDT training is performed using several event variables for signal and background. 
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{BDT Variables}
+\frametitle{BDT}
 \small{
@@
 \end{frame}
+
+\nologo{
+	\begin{frame}
+	\Fontvi
+	\begin{center}
+		\begin{tabular}{cc}
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
+			{Distribution of selected events as a function of $|\eta|$ of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
+			{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\eta|$ between a forward jet and a b-tagged jet } \\
+		\end{tabular}
+	\end{center}
+\end{frame}
+}
+
+\nologo{
+	\begin{frame}
+
+		\Fontvi
+	\begin{center}
+		\begin{tabular}{cc}
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\ 
+			{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of jet events for $|\eta|$>1} \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-sch}\\
+			{Distribution of events of $|\Delta\phi|$ between the higher pt pair of leptons } & {Distribution of events of the sum of same sign leptons charge.} \\
+		\end{tabular}
+	\end{center}
+\end{frame}
+}
 
@@
 \begin{frame}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.5]{figures/compare_variables}
+	\caption*{Signal and background kinematic distributions}
+\end{figure}
+\end{frame}
+
+\begin{frame}
 \frametitle{Results}

### 2019-11-09 BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/compare_variables.C

@@ -30,18 +30,18 @@ void compare_variables(){
 
 
   TCanvas C;
-  C.Print("compare_variables.eps");
-  C.Print("compare_variables.png");
-  C.Print("compare_variables.pdf");
+  C.Print("compare_variables-pt-sub.eps");
+  C.Print("compare_variables-pt-sub.png");
+  C.Print("compare_variables-pt-sub.pdf");
 
 
 
   ///compare one variable
-  TH1F H1("H1","",50,0,7);
-  TH1F H2("H2","",50,0,7);
+  TH1F H1("H1","",40,0,200);
+  TH1F H2("H2","",40,0,200);
 
-  t1.Draw("deta_fj_l>>H1");
-  t2.Draw("deta_fj_l>>H2");
+  t1.Draw("l2_pt>>H1");
+  t2.Draw("l2_pt>>H2");
 
   H1.Scale(1.0/H1.Integral());
   H2.Scale(1.0/H2.Integral());
@@ -55,11 +55,11 @@ void compare_variables(){
   H2.Draw("histsame");
 
   //
-  H1.SetAxisRange(0,0.1,"Y");
-  H1.SetAxisRange(0,8,"X");
+  //H1.SetAxisRange(0,0.05,"Y");
+  H1.SetAxisRange(0,150,"X");
   H1.SetYTitle("Events normalized to unit area");
   H1.SetStats(0);
-  H1.SetXTitle("#Delta#eta between forward light jet and closest lepton");
+  H1.SetXTitle("pT of subleading lepton");
 
   auto legend = new TLegend(0.8,0.7,0.86,0.8);
   legend->AddEntry("H1","tHq","l");
@@ -69,9 +69,9 @@ void compare_variables(){
   legend->SetEntrySeparation(0.5);
   legend->Draw();
 
-  C.Print("compare_variables.png");
-  C.Print("compare_variables.eps");
-  C.Print("compare_variables.pdf");
+  C.Print("compare_variables-pt-sub.png");
+  C.Print("compare_variables-pt-sub.eps");
+  C.Print("compare_variables-pt-sub.pdf");
   //compare correlations
   C.Clear();
   C.Divide(1,2);

### 2019-11-10 project_ashish/paper1.tex
Add files via upload

--- 2019-11-09 project_ashish/paper.tex
@@
 \usepackage{changepage}
+\usepackage{float}
 \begin{document}
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd11.png}
+	\includegraphics[scale=0.4]{./cd11.png}
 	\caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
@@
 \end{figure}
+
+ \newpage
 
@@
 
-\begin{figure}
+\begin{figure}[H]
 	\centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
+	\includegraphics[scale=0.5]{./pg.png}
 	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
@@
 
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
-  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-   \label{figure 3}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
-  \caption{Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
-   \label{figure 4}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms13.png}
-  \caption{Scan of $−2Δln(L)$ versus $κ_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
-   \label{figure 5}
-\end{figure}
-
-Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
-These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
-discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
-energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
-colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
-It is designed to detect particles known as muons very accurately.
-The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
-A silicon tracker, made of about 75
-million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 6.
-In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
-LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 \times 10^{33} $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
-All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
-LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 7.
-\\
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
-   \label{figure 6}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
-  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
-show instant brightness while the line shows brightness accumulated.}
-   \label{figure 7}
-\end{figure}
-
 The production of Higgs boson in association with single top quark is one of the rare Higgs 
@@
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{sirunyan2018search}.
-The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 8.
+is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 3.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./cms5.png}
+	\caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
+	\label{figure 3}
+\end{figure}
+
  The Higgs boson in the tH channel can be radiated 
 off by a W boson or by a top 
-quark as shown in Figure 8 and 9. These two processes in standard model have destructive interference which allow us to 
+quark as shown in Figure 4 and 5.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./tq.png}
+	\caption{Higgs production using the top quark (left) and W boson (right).}
+	\label{figure 4}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\columnwidth]{./cms.png}
+	\caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+	\label{figure 5}
+\end{figure}
+
+ These two processes in standard model have destructive interference which allow us to 
 probe the relative sign between 
@@
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction as shown in Figure 5. 
+us the deviation of $y_t$ from the SM prediction as shown in Figure 6.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./cd7.png}
+	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+	\label{figure 6}
+\end{figure}
+
 The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
@@
 
-\begin{figure}
+Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
+These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
+discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
+energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
+colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
+It is designed to detect particles known as muons very accurately.
+The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
+Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
+A silicon tracker, made of about 75
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 7.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+
+\begin{figure}[H]
 	\centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
-  \caption{Higgs production using the top quark (left) and W boson (right).}
+	\includegraphics[scale=0.36]{./cms12.png}
+	\caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
+	\label{figure 7}
+\end{figure}
+
+ LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
+LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 8.
+\\
+
+ \begin{figure}[H]
+ 	\centering
+ 	\includegraphics[scale=0.45]{./lum6.png}
+ 	\caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
+Points show instant brightness while the line shows brightness accumulated.}
  	\label{figure 8}
+ \end{figure}
 
-  \begin{figure}
+ Earlier searches for Higgs boson production production in association with single top quark have been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
+Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure 9.
+Multilepton final state and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
+The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges of about [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
+
+ \begin{figure}[H]
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
-  \caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+   \includegraphics[width=\columnwidth]{./cms13.png}
+  \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines)..}
    \label{figure 9}
@@
 
-- what we will do:  search for tH events, using which channels.
+- what we will do:  search for tH events, using which channels.\\
 
@@
 of the LHC identifying the signal events with two muons from the same sign. It is also 
-expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that began 
+expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that will begin 
 in 2026.
@@
 
-- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
+- motivation, tH production crossection, sign of $k_t$, search for BSM, ..\\
 
@@
 \section{HYPOTHESIS}
-- what we expect to find
+- what we expect to find\\
 
@@
 \section{METHODOLOGY}
-- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis
+- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis\\
 
@@
 \section{EXPECTED RESULTS}
-- a limit, also predictions for future runs
+- a limit, also predictions for future runs\\
 
@@
 \cleardoublepage
-\bibliography{paper}
+\bibliography{paper1}
 
@@
 \newpage
-\cleanpage
 
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms7.jpg}
+   \includegraphics[width=\columnwidth]{./cms7.jpg}
   \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
-   \label{figure 9}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd.png}
-  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
    \label{figure 10}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd1.png}
-  \caption{Standard model Higgs boson production cross section in various production modes.}
+   \includegraphics[width=\columnwidth]{./cd.png}
+  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
    \label{figure 11}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd2.png}
-  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
+   \includegraphics[width=\columnwidth]{./cd1.png}
+  \caption{Standard model Higgs boson production cross section in various production modes.}
    \label{figure 12}
@@
   \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd3.png}
-  \caption{Standard model Higgs boson branching ratios in various decay channels.}
+   \includegraphics[width=\columnwidth]{./cd2.png}
+  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
    \label{figure 13}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd5.png}
-  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
+   \includegraphics[scale=0.5]{./cd3.png}
+  \caption{Standard model Higgs boson branching ratios in various decay channels.}
    \label{figure 14}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd6.png}
-  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
+   \includegraphics[width=\columnwidth]{./cd5.png}
+  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
    \label{figure 15}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
-  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
+   \includegraphics[width=\columnwidth]{./cd6.png}
+  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
    \label{figure 16}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th.png}
-  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
+   \includegraphics[width=\columnwidth]{./cd7.png}
+  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
    \label{figure 17}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th1.png}
-  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
-energy.}
+   \includegraphics[width=\columnwidth]{./th.png}
+  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
    \label{figure 18}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th2.png}
-  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
+   \includegraphics[width=\columnwidth]{./th1.png}
+  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
+energy.}
    \label{figure 19}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th3.png}
-  \caption{Lowest order Feynman diagrams for s-channel tH production.}
+   \includegraphics[width=\columnwidth]{./th2.png}
+  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
    \label{figure 20}
@@
 
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{./th3.png}
+  \caption{Lowest order Feynman diagrams for s-channel tH production.}
+   \label{figure 21}
+\end{figure}
+
 \end{document}

### 2019-11-10 project_ashish/paper1.tex
Add files via upload
Update paper1.tex

@@
 	\includegraphics[scale=0.4]{./tq.png}
-	\caption{Higgs production using the top quark (left) and W boson (right).}
+	\caption{Higgs boson production using the top quark (left) and W boson (right).}
 	\label{figure 4}
@@
    \includegraphics[width=\columnwidth]{./cms13.png}
-  \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines)..}
+  \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
    \label{figure 9}

### 2019-11-11 project_ashish/paper1.tex
Update paper1.tex

@@
 production cross section which is a special property of tH production channel making it an 
-interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
+interesting production channel to probe using LHC 2016, 2017 and 2018 data \cite{farina2013lifting} . The coupling 
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 

### 2019-11-11 project_ashish/paper1.tex
Update paper1.tex

--- 2019-11-10 project_ashish/paper1.tex
@@
 production cross section which is a special property of tH production channel making it an 
-interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
+interesting production channel to probe using LHC 2016, 2017 and 2018 data \cite{farina2013lifting}. The coupling 
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 

### 2019-11-11 tesis_hiram/Chapter1/chapter1.tex
final
tesis-arreglo1

@@
 Particle physics is a field of study of physics that studies the particles that create matter and its interactions to very small scale, even smaller than atoms.
-The particles analized in particle physics are the fundamental particles that compose the matter and the responsibles for all forces of nature.
-All thoses particles and their properties are grouped in a theory called the Standard Model.
+The particles analyzed in particle physics are the fundamental particles that compose the matter and the responsible for all forces of nature.
+All those particles and their properties are grouped in a theory called the Standard Model.
 Standard Model (SM) is a theory that describes the fundamental forces (except gravity) and classify the elementary particles in bosons (entire spin) and fermions (half spin).
-The SM, created almost 50 years ago, has been the most successul theory in explain the phenomena in the subatomic world.
+The SM, created almost 50 years ago, has been the most successful theory in explain the phenomena in the subatomic world.
 \\
@@
 The discovery of Higgs boson in proton proton collisions marked a new era in the particle physics due to its characteristic of giving the matter the property of mass, according to previous theories and predictions.
-Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and differents Higgs production processes.
+Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes.
 Also the impact of Higgs is also important in cosmology, where theoretical investigations relate the Higgs boson and the cosmic inflation.\\
@@
 In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes.
-In this work, we will analize the production of Higgs boson in association with a
+In this work, we will analyze the production of Higgs boson in association with a
 single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC. 
@@
 The last group of the family are the bosons,which have a spin 1 and 0. 
-There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsibles for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism.
+There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism.
 Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}.
@@
 \\
-Since quarks and gluons only exist in bound states, it is imposible to observe isolated quarks except the top quark, which decays before it has time to form a
+Since quarks and gluons only exist in bound states, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
 bound state. As two quarks are separated, the strong force between them increases
@@
 
-The production of top quark can be generated in differents ways.
+The production of top quark can be generated in different ways.
 In tevatron and LHC, the production of $t\bar{t}$ comes from ggF (gluon gluon fusion) via strong force.
-Even it is posible to create a single top quark in the LHC via electroweak interactions (with a W boson)\cite{th1}.
+Even it is possible to create a single top quark in the LHC via electroweak interactions (with a W boson)\cite{th1}.
 The top quark, due to its big mass, always decays into a W boson and a b quark.
-But since the W boson have various decays, the top quark can generate many posible particles, acording to W boson decays.
+But since the W boson have various decays, the top quark can generate many possible particles, according to W boson decays.
 Some posible decays of top quark is the decay to a lepton such as muon, electron or tau and their neutrinos.
@@
 Another process is vector boson fusion (VBF), where two fermions interact via a vector boson ($W$ or $Z$ ) and create a Higgs along with other particles.
-There is also the vector higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}.
+There is also the vector Higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}.
 These processes are shown in the figure \ref{psu} \\
@@
 The decay $H \rightarrow$ $\mu^+\mu^-$ has a very low branching ratio.
-This decay is very rare but not imposible to detect in the future.
+This decay is very rare but not impossible to detect in the future.
 In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$\\

### 2019-11-11 tesis_hiram/Chapter2/chapter2.tex
tesis-arreglo1

@@
 This detector was designed in the early 1990s, based on the mass limit of the Higgs boson, and put on operation in 2008, it has a big solenoid that generates a great magnetic field of 4 teslas with the objective to separate particles after a particle collision.
- The detector is 21 metres long, 15 meters wide, 15 meters high, it has a diameter of 5.9 m with a weight of 12000 ton.
+ The detector is 21 meters long, 15 meters wide, 15 meters high, it has a diameter of 5.9 m with a weight of 12000 ton.
 The reason for such a strong magnetic field is to obtain a better momentum resolution.
@@
 
-The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillanting crystals (emits light when particles interact with the crystal).
+The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillating crystals (emits light when particles interact with the crystal).
 These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps.
 The barrel section of the ECAL covers the range $|\eta| < 1.479$.
-The crystals in the barrel have a pyramid shape and their crosss section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
+The crystals in the barrel have a pyramid shape and their cross section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
 The crystal length is 230 mm.
@@
 HCAL is located in the barrel and the endcaps, surrounding the ECAL and affected by the magnetic field generated by the solenoid.
-The Barrel section (HB) and endcap section (HE) cover the pseudorapity 0 < $|\eta|$ < 1.3 and 1.3 < $|\eta|$ < 3.0 respectively.\\
+The Barrel section (HB) and endcap section (HE) cover the pseudorapidity 0 < $|\eta|$ < 1.3 and 1.3 < $|\eta|$ < 3.0 respectively.\\
 
@@
 There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
-steel absorbers and embedded radiation hard quartz fibers, which collects 
+steel absorber and embedded radiation hard quartz fibers, which collects 
 Cherenkov light\cite{cms-manual}.% that is when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 

### 2019-11-11 tesis_hiram/Chapter3/chapter3.tex
tesis-arreglo1

@@
 This event yields will be used to estimate the signal sensitivity.
-The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertanties are described in table \ref{tth-table}.
+The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertainties are described in table \ref{tth-table}.
 

### 2019-11-11 project_ashish/paper2.tex
Rename paper.tex to paper2.tex

--- 2019-11-09 project_ashish/paper.tex
@@
 
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
+  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
+   \label{figure 2}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
+  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
+   \label{figure 3}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
+  \caption{Higgs production using the top quark (left) and W boson (right).}
+   \label{figure 4}
+\end{figure}
+
+\begin{figure}
+  \centering
+   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
+  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+   \label{figure 5}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
+  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
+show instant brightness while the line shows brightness accumulated.}
+   \label{figure 6}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
+  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+   \label{figure 7}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
+  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
+   \label{figure 8}
+\end{figure}
+
+Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
+These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
+discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
+energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
+colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
+It is designed to detect particles known as muons very accurately.
+The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
+Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
+A silicon tracker, made of about 75
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 2.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 \times 10^{33} $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
+LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 6.
+\\
+
 There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
@@
 Higgs-portal dark matter models.\\
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/pg.png}
-  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
-   \label{figure 2}
-\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cd7.png}
-  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-   \label{figure 3}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms5.png}
-  \caption{Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
-   \label{figure 4}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms13.png}
-  \caption{Scan of $−2Δln(L)$ versus $κ_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
-   \label{figure 5}
-\end{figure}
-
 Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
@@
 \\
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/cms12.png}
-  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
-   \label{figure 6}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/lum6.png}
-  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities. Points
-show instant brightness while the line shows brightness accumulated.}
-   \label{figure 7}
-\end{figure}
 
@@
 higher dimensional operators in effective SM theory \cite{sirunyan2019search}.
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
-  \caption{Higgs production using the top quark (left) and W boson (right).}
-  \label{figure 8}
-
-  \begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
-  \caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
-   \label{figure 9}
-\end{figure}
 
@@
 
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms13.png}
+  \caption{Lowest order Feynman diagrams for s-channel tH production.}
+   \label{figure 20}
+\end{figure}
+
 \end{document}

### 2019-11-11 project_ashish/paper.tex
Update and rename paper1.tex to paper.tex

@@
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{sirunyan2018search}.
-The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 8.
+is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 3.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./cms5.png}
+	\caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
+	\label{figure 3}
+\end{figure}
+
  The Higgs boson in the tH channel can be radiated 
 off by a W boson or by a top 
-quark as shown in Figure 8 and 9. These two processes in standard model have destructive interference which allow us to 
+quark as shown in Figure 4 and 5.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./tq.png}
+	\caption{Higgs boson production using the top quark (left) and W boson (right).}
+	\label{figure 4}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=\columnwidth]{./cms.png}
+	\caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+	\label{figure 5}
+\end{figure}
+
+ These two processes in standard model have destructive interference which allow us to 
 probe the relative sign between 
@@
 production cross section which is a special property of tH production channel making it an 
-interesting production channel to probe using LHC 2016, 2017 and 2018 data. The coupling 
+interesting production channel to probe using LHC 2016, 2017 and 2018 data \cite{farina2013lifting}. The coupling 
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction as shown in Figure 5. 
+us the deviation of $y_t$ from the SM prediction as shown in Figure 6.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./cd7.png}
+	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+	\label{figure 6}
+\end{figure}
+
 The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
@@
 
-\begin{figure}
+Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
+These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
+discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
+energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
+colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
+It is designed to detect particles known as muons very accurately.
+The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
+Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
+A silicon tracker, made of about 75
+million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 7.
+In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+
+\begin{figure}[H]
 	\centering
-   \includegraphics[scale=0.5]{/home/ashish/tHqCMSAnalysis/project_ashish/tq.png}
-  \caption{Higgs production using the top quark (left) and W boson (right).}
+	\includegraphics[scale=0.36]{./cms12.png}
+	\caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
+	\label{figure 7}
+\end{figure}
+
+ LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
+LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 8.
+\\
+
+ \begin{figure}[H]
+ 	\centering
+ 	\includegraphics[scale=0.45]{./lum6.png}
+ 	\caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
+Points show instant brightness while the line shows brightness accumulated.}
  	\label{figure 8}
+ \end{figure}
 
-  \begin{figure}
+ Earlier searches for Higgs boson production production in association with single top quark have been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
+Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure 9.
+Multilepton final state and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
+The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges of about [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
+
+ \begin{figure}[H]
   \centering
-  \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/cms.png}
-  \caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+   \includegraphics[width=\columnwidth]{./cms13.png}
+  \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
    \label{figure 9}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th.png}
+   \includegraphics[width=\columnwidth]{./th.png}
   \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th1.png}
+   \includegraphics[width=\columnwidth]{./th1.png}
   \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th2.png}
+   \includegraphics[width=\columnwidth]{./th2.png}
   \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
@@
   \centering
-   \includegraphics[width=\columnwidth]{/home/ashish/tHqCMSAnalysis/project_ashish/th3.png}
+   \includegraphics[width=\columnwidth]{./th3.png}
   \caption{Lowest order Feynman diagrams for s-channel tH production.}

### 2019-11-11 project_ashish/paper.tex
Update paper.tex

@@
 
+\begin{figure}
+  \centering
+   \includegraphics[width=\columnwidth]{./cd2.png}
+  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
+   \label{figure 13}
+\end{figure}
+
 The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
@@
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 3.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.4]{./cms5.png}
-	\caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
-	\label{figure 3}
-\end{figure}
-
- The Higgs boson in the tH channel can be radiated 
-off by a W boson or by a top 
-quark as shown in Figure 4 and 5.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.4]{./tq.png}
-	\caption{Higgs boson production using the top quark (left) and W boson (right).}
-	\label{figure 4}
-\end{figure}
+is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
+off by a W boson or by a top quark as shown in Figure 4 and 5.
 
@@
 	\label{figure 7}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./cd7.png}
+	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+	\label{figure 6}
 \end{figure}
@@
   \centering
-   \includegraphics[width=\columnwidth]{./cd2.png}
-  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-   \label{figure 13}
-\end{figure}
-
-\begin{figure}
-  \centering
    \includegraphics[scale=0.5]{./cd3.png}

### 2019-11-11 project_ashish/paper.tex
Update paper.tex

@@
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-   \label{figure 13}
+   \label{figure 3}
 \end{figure}
@@
 is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
-off by a W boson or by a top quark as shown in Figure 4 and 5.
+off by a W boson or by a top quark as shown in Figure 4.
 
@@
 	\caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
-	\label{figure 5}
+	\label{figure 4}
 \end{figure}
@@
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction as shown in Figure 6.
+us the deviation of $y_t$ from the SM prediction as shown in Figure 5.
 
@@
 	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-	\label{figure 6}
+	\label{figure 5}
 \end{figure}
@@
 million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 7.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 6.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
@@
 	\caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
-	\label{figure 7}
+	\label{figure 6}
 \end{figure}
@@
 	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-	\label{figure 6}
+	\label{figure 7}
 \end{figure}

### 2019-11-11 project_ashish/paper3.tex
Add files via upload

--- 2019-11-11 project_ashish/paper1.tex
@@
 	\centering
-	\includegraphics[scale=0.5]{./pg.png}
+	\includegraphics[width=\columnwidth]{./pg.png}
 	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
 	\label{figure 2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+   \includegraphics[width=\columnwidth]{./cd2.png}
+  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
+   \label{figure 3}
 \end{figure}
@@
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Feynman diagrams for SM Higgs boson in association with top quark and top anti-quark is shown in Figure 3.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.4]{./cms5.png}
-	\caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quark decaying to W boson and bottom quark and  W boson decaying to leptons.}
-	\label{figure 3}
-\end{figure}
-
- The Higgs boson in the tH channel can be radiated 
-off by a W boson or by a top 
-quark as shown in Figure 4 and 5.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.4]{./tq.png}
-	\caption{Higgs boson production using the top quark (left) and W boson (right).}
-	\label{figure 4}
-\end{figure}
+is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
+off by a W boson or by a top quark as shown in Figure 4.
 
@@
 us the deviation of $y_t$ from the SM prediction as shown in Figure 6.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[scale=0.4]{./cd7.png}
-	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-	\label{figure 6}
-\end{figure}
 
@@
 million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 7.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 5.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
@@
 	\caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
+	\label{figure 6}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[scale=0.4]{./cd7.png}
+	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
 	\label{figure 7}
@@
   \centering
-   \includegraphics[width=\columnwidth]{./cms13.png}
+   \includegraphics[width=0.5 \columnwidth]{./cms13.png}
   \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
@@
   \centering
-   \includegraphics[width=\columnwidth]{./cd7.png}
-  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
-   \label{figure 17}
-\end{figure}
-
-\begin{figure}
-  \centering
    \includegraphics[width=\columnwidth]{./th.png}
   \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
-   \label{figure 18}
+   \label{figure 17}
 \end{figure}
@@
 energy.}
-   \label{figure 19}
+   \label{figure 18}
 \end{figure}
@@
   \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
-   \label{figure 20}
+   \label{figure 19}
 \end{figure}
@@
   \caption{Lowest order Feynman diagrams for s-channel tH production.}
-   \label{figure 21}
+   \label{figure 20}
 \end{figure}

### 2019-11-11 presentacion_hiram/presentacion-tesis.tex
tesis-arreglo1

@@
 \begin{frame}
+\tiny
 \tableofcontents
@@
 experiment.
-\item Standard Model and the Higgs production mechanism
+%\item Standard Model and the Higgs production mechanism
 \item A brief introduction to the LHC and CMS
-\item Event selection and reconstruction
+\item Event selection and reconstruction of the tH signal
 \item Creation and application of a statistical model for the analysis of events 
@@
 \begin{align}
-\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
+\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}%+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
 \end{align}
@@
 
-\nologo{
+{\nologo
 \begin{frame}
@@
 \frametitle{Higgs production mechanisms}
+
 \begin{center}
@@
 }
+
+{\nologo
 \begin{frame}
@@
 \end{frame} 
+}
 
@@
 \item In a proton proton collision, the production cross section of the single top plus Higgs boson process is driven by a
-destructive interference of two main diagrams (see Fig. \ref{th}.), where the Higgs couples to either
+destructive interference of two main diagrams, where the Higgs couples to either
 the W boson or the top quark. 
@@
 \frametitle{Backgrounds}
+\subsection{Backgrounds}
 \begin{itemize}
@@
 	\item Backgrounds share certain characteristics of the signal.
-	\item Backgrounds are a big factor in the statistical of the signal.
+	\item Backgrounds are a big factor in the statistical study of the signal.
 \end{itemize}
@@
 
+{\nologo
 \begin{frame}
@@
 \end{frame}
+}
 
@@
 \end{frame}
-
-\nologo{
-	\begin{frame}
-	\Fontvi
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
-			{Distribution of selected events as a function of $|\eta|$ of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
-			{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\eta|$ between a forward jet and a b-tagged jet } \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-\nologo{
-	\begin{frame}
-
-		\Fontvi
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\ 
-			{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of jet events for $|\eta|$>1} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-sch}\\
-			{Distribution of events of $|\Delta\phi|$ between the higher pt pair of leptons } & {Distribution of events of the sum of same sign leptons charge.} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
 
@@
 
-\nologo{
+{\nologo
 	\begin{frame}
@@
 	\small
-	\section{References}
+%	\section{References}
 	\frametitle{References}
@@
 \begin{frame}
-\section{Supportive slides}
+%\section{Supportive slides}
 \huge{Back up}
@@
 
+{\nologo
+	\begin{frame}
+
+	\Fontvi
+	\begin{center}
+		\begin{tabular}{cc}
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\ 
+			{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of jet events for $|\eta|$>1} \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-sch}\\
+			{Distribution of events of $|\Delta\phi|$ between the higher pt pair of leptons } & {Distribution of events of the sum of same sign leptons charge.} \\
+		\end{tabular}
+	\end{center}
+\end{frame}
+}
+
+{\nologo
+	\begin{frame}
+	\Fontvi
+	\begin{center}
+		\begin{tabular}{cc}
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
+			{Distribution of selected events as a function of $|\eta|$ of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
+			{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\eta|$ between a forward jet and a b-tagged jet } \\
+		\end{tabular}
+	\end{center}
+\end{frame}
+}
+
 \end{document}

### 2019-11-12 project_ashish/paper.tex
Update paper.tex

--- 2019-11-11 project_ashish/paper.tex
@@
 	\centering
-	\includegraphics[scale=0.5]{./pg.png}
+	\includegraphics[width=\columnwidth]{./pg.png}
 	\caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
@@
 
-\begin{figure}
+\begin{figure}[H]
   \centering
@@
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
-   \label{figure 13}
+   \label{figure 3}
 \end{figure}
+
+\newpage
 

### 2019-11-12 project_ashish/paper3.tex
Add files via upload

@@
 \end{figure}
-
+ \newpage
 The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 

### 2019-11-12 presentacion_hiram/presentacion-tesis.tex
new

@@
 
-\begin{frame}
-\section{Overview and motivation}
-\frametitle{Overview}
-\begin{itemize}
-\item Through this project it was studied the production of Higgs boson in association with a
-single top quark ($tH$) in proton-proton collisions. 
-This mechanism of production of the Higgs boson has not been observed before by any
-experiment.
+%\begin{frame}
+%\section{Overview and motivation}
+%\frametitle{Overview}
+%\begin{itemize}
+%\item Through this project it was studied the production of Higgs boson in association with a
+%single top quark ($tH$) in proton-proton collisions. 
+%This mechanism of production of the Higgs boson has not been observed before by any
+%experiment.
 %\item Standard Model and the Higgs production mechanism
-\item A brief introduction to the LHC and CMS
-\item Event selection and reconstruction of the tH signal
-\item Creation and application of a statistical model for the analysis of events 
-\item Making predictions for the future experiments.
-\end{itemize}
-\end{frame}
+%\item A brief introduction to the LHC and CMS
+%\item Event selection and reconstruction of the tH signal
+%\item Creation and application of a statistical model for the analysis of events 
+%\item Making predictions for the future experiments.
+%\end{itemize}
+%\end{frame}
 
@@
 
-\begin{frame}
-\frametitle{Backgrounds}
-\subsection{Backgrounds}
-\begin{itemize}
-	\item Backgrounds are considered information in the data that is not the signal. 
-	\item Backgrounds share certain characteristics of the signal.
-	\item Backgrounds are a big factor in the statistical study of the signal.
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\subsection{Event selection}
-\frametitle{Event selection}
-In order to detect signal events and reject background, the following selections are applied. 
-\begin{itemize}
-	\item The events must contain two muons with the same sign.
-	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
-	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
-	\item One or more b-tagged jets with $|\eta|$ < 2.4
-\end{itemize}
-\end{frame}
-
-{\nologo
-\begin{frame}
-\subsection{Previous results}
-\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
-
-\begin{minipage}[c]{0.45\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.3]{figures/histo.png}
-	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[c]{.45\textwidth}
-	\begin{figure}	\centering
-	\includegraphics[width=\textwidth]{figures/sc.png}
-	\caption*{\tiny{Observed and expected 95$\%$ C.L.
-upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
-The expected limit is derived from a background-only MC dataset.}}
-	\end{figure}
-\end{minipage}
-\end{frame}
-}
-
-{\nologo
-\begin{frame}
-\begin{minipage}[b]{.48\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{figures/kos.png}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.48\textwidth}
-	\begin{figure}
-		\centering
-		\includegraphics[width=\textwidth]{figures/kos2.png}
-	\end{figure}
-\end{minipage}
-\begin{center}
-\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
-\end{center}
-\end{frame}
-}
+%\begin{frame}
+%\frametitle{Backgrounds}
+%\subsection{Backgrounds}
+%\begin{itemize}
+%	\item Backgrounds are considered information in the data that is not the signal. 
+%	\item Backgrounds share certain characteristics of the signal.
+%	\item Backgrounds are a big factor in the statistical study of the signal.
+%\end{itemize}
+%\end{frame}
 
@@
 \begin{frame}
-\frametitle{Signal and Backgrounds}
+\subsection{Event selection}
+\frametitle{Event selection}
+In order to detect signal events and reject background, the following selections are applied. 
+\begin{itemize}
+	\item The events must contain two muons with the same sign.
+	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
+	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
+	\item One or more b-tagged jets with $|\eta|$ < 2.4
+\end{itemize}
+\end{frame}
+
+{\nologo
+\begin{frame}
+\subsection{Previous results}
+\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
+
+\begin{minipage}[c]{0.45\textwidth}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.3]{figures/histo.png}
+	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{.45\textwidth}
+	\tiny
 \begin{table}
@@
 \end{table}
-\end{frame}
+%	\begin{figure}	\centering
+%	\includegraphics[width=\textwidth]{figures/sc.png}
+%	\caption*{\tiny{Observed and expected 95$\%$ C.L.
+upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
+The expected limit is derived from a background-only MC dataset.}}
+%	\end{figure}
+\end{minipage}
+\end{frame}
+}
+
+{\nologo
+\begin{frame}
+\begin{minipage}[b]{.48\textwidth}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{figures/kos.png}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.48\textwidth}
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{figures/kos2.png}
+	\end{figure}
+\end{minipage}
+\begin{center}
+\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
+\end{center}
+\end{frame}
+}
 
@@
 \small{
-\begin{itemize}
-\item A decision tree takes a set of input features and splits input data recursively based on
+ A decision tree takes a set of input features and splits input data recursively based on
 those features.
-Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.
-\item The BDT training is performed using several event variables for signal and background. 
-\end{itemize}
+Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data. \\
+
 BDT Variables}
@@
 \frametitle{Likelihood model}
-\small{
-To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
-The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.\\
-The likelihood function is the product of Poisson probabilities for all bins
+{\small \begin{itemize}
+\item To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one. 
+\item The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.\\
+\item The likelihood function is the product of Poisson probabilities for all bins
 \begin{align}
@@
 	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, $\mu$ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
-	$b_j$ is the sum of different background processes $k$
+\end{itemize}}
+\end{frame}
+
+\begin{frame}
+\frametitle{Likelihood model}
+{\small
+\begin{itemize}
+	\item $b_j$ is the sum of different background processes $k$
 	\begin{align}
@@
 $\sigma_k$ for the backgrounds are shown in the Table of yields.
-}
-\end{frame}
-
-\begin{frame}
-\frametitle{Results}
-	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
+		\item The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
 The minimization is performed by using the package ROOFIT.
 In the next slides, it shows the results of the model fitting using the Asimov data for the SM and the $k_t=-1$.
+\end{itemize}}
 \end{frame}
@@
 \framesubtitle{Likelihood scan}
-Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
-Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.\\
-
-We can define the likelihood ratio
+{\small
+	\begin{itemize}
+\item Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
+Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
+
+\item We can define the likelihood ratio
 \begin{align}
@@
 Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
+
+\item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
+\begin{align}
+q(\mu,\alpha)= -2\ln{\lambda} 
+\end{align}
+\item High values of $q$ represent greater incompatibility between the data and the fit model.
+$q$ is a random variable with a $\chi^2$ distribution.
+\end{itemize}
+}
 \end{frame}
@@
 }
-
-\begin{frame}
-\frametitle{Results}
-\framesubtitle{Upper limit}
-To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
-\begin{align}
-q(\mu,\alpha)= -2\ln{\lambda} 
-\end{align}
-High values of $q$ represent greater incompatibility between the data and the fit model.
-$q$ is a random variable with a $\chi^2$ distribution.
-\end{frame}
 

### 2019-11-13 project_ashish/paper.tex
Add files via upload
Update paper.tex

@@
   \centering
-   \includegraphics[width=\columnwidth]{./cd2.png}
+   \includegraphics[scale=0.5]{./cd2.png}
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
@@
 \end{figure}
-
 \newpage
@@
 All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
-LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023 as shown in Figure 8.
+LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023.
 \\
 
- \begin{figure}[H]
- 	\centering
- 	\includegraphics[scale=0.45]{./lum6.png}
- 	\caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instant brightness while the line shows brightness accumulated.}
- 	\label{figure 8}
- \end{figure}
-
  Earlier searches for Higgs boson production production in association with single top quark have been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
-Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure 9.
+Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure 7.
 Multilepton final state and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
@@
   \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
-   \label{figure 9}
+   \label{figure 7}
 \end{figure}
@@
 expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that will begin 
-in 2026.
+in 2026 as shown in Figure 8.
 
+ \begin{figure}[H]
+ 	\centering
+ 	\includegraphics[scale=0.45]{./lum6.png}
+ 	\caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
+Points show instant brightness while the line shows brightness accumulated.}
+ 	\label{figure 8}
+ \end{figure}
 \section{GENERAL OBJECTIVE}
@@
 \cleardoublepage
-\bibliography{paper1}
+\bibliography{paper}
 

### 2019-11-13 project_ashish/paper.tex
Update paper.tex

@@
 	\includegraphics[width=\columnwidth]{./cms.png}
-	\caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+	\caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
 	\label{figure 4}
@@
 	\caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
-	\label{figure 6}
+	\label{figure 5}
 \end{figure}
@@
 	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-	\label{figure 7}
+	\label{figure 6}
 \end{figure}
@@
  	\includegraphics[scale=0.45]{./lum6.png}
- 	\caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
+ 	\caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
 Points show instant brightness while the line shows brightness accumulated.}

### 2019-11-13 project_ashish/paper.tex
Update paper.tex

@@
 
-\newpage
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./cms7.jpg}
-  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
-   \label{figure 10}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./cd.png}
-  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
-   \label{figure 11}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./cd1.png}
-  \caption{Standard model Higgs boson production cross section in various production modes.}
-   \label{figure 12}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[scale=0.5]{./cd3.png}
-  \caption{Standard model Higgs boson branching ratios in various decay channels.}
-   \label{figure 14}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./cd5.png}
-  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
-   \label{figure 15}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./cd6.png}
-  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
-   \label{figure 16}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./th.png}
-  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
-   \label{figure 17}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./th1.png}
-  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
-energy.}
-   \label{figure 18}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./th2.png}
-  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
-   \label{figure 19}
-\end{figure}
-
-\begin{figure}
-  \centering
-   \includegraphics[width=\columnwidth]{./th3.png}
-  \caption{Lowest order Feynman diagrams for s-channel tH production.}
-   \label{figure 20}
-\end{figure}
-
 \end{document}

### 2019-11-13 project_ashish/paper.tex
Update paper.tex

@@
 
--SM, Higgs, couplings, previous Higgs measurements, previous tH searches\\
+-SM, Higgs, couplings, previous Higgs measurements, previous tH searches
 
@@
 All the standard model particles are shown in Figure 1.
-Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.\\
+Higgs boson can be produced at the particle colliders like the Large Hadron Collider (LHC) in Geneva, Switzerland.
 
@@
 decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the 
-Higgs-portal dark matter models.\\
+Higgs-portal dark matter models.
 
@@
 encoded in the size of the operator
-coefficients, which is to be set from experiments.\\
+coefficients, which is to be set from experiments.
 
@@
 dimension 6 operator dominate baryon 
-minus lepton number symmetry conservation processes.\\
+minus lepton number symmetry conservation processes.
 
@@
 LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023.
-\\
 
@@
 
-- what we will do:  search for tH events, using which channels.\\
+- what we will do:  search for tH events, using which channels.
 
@@
 
-- motivation, tH production crossection, sign of $k_t$, search for BSM, ..\\
+- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
 
@@
 of statistical and systematic uncertainties.
-Some of the objectives in this project include:\\
+Some of the objectives in this project include:
 \begin{itemize}
-\item study one or more decay channels.\\
-\item verify that simulation of signal events is adequate.\\
-\item study the extraction of signal strength through adjustments to the data.\\
-\item study the impact of statistical and systematic uncertainties.\\
+\item study one or more decay channels.
+\item verify that simulation of signal events is adequate.
+\item study the extraction of signal strength through adjustments to the data.
+\item study the impact of statistical and systematic uncertainties.
 \end{itemize}
@@
 \section{HYPOTHESIS}
-- what we expect to find\\
+- what we expect to find
 
@@
 \section{METHODOLOGY}
-- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis\\
+- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis
 
@@
 \section{EXPECTED RESULTS}
-- a limit, also predictions for future runs\\
+- a limit, also predictions for future runs
 

### 2019-11-14 presentacion_hiram/presentacion-tesis.tex
new

@@
 		Maestr\'ia en Ciencias (F\'isica)\\
-		Hiram Ernesto Dami\'an}
+		Hiram Ernesto Dami\'an\\
+	Director:\\
+Jos\'e Feliciano Ben\'itez Rubio}
 	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
@@
 \frametitle{$\mu\mu$ same sign decay rate}
-\tiny{Table of decay chains for tH.  Expected number of final events assuming 560 produced $tH$ events.l represents $\mu^{\pm},e^- , \tau^\pm$. }
+\tiny{Table of decay chains for tH.  Expected number of $tH$ final states events for 35.9 fb$^{-1}$.l represents $\mu^{\pm},e^- , \tau^\pm$. }
 \begin{table}
@@
 \end{itemize}
-\end{frame}
-
-{\nologo
-\begin{frame}
-\subsection{Previous results}
-\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
-
-\begin{minipage}[c]{0.45\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.3]{figures/histo.png}
-	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[c]{.45\textwidth}
-	\tiny
-\begin{table}
-	\centering
-	\caption*{{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
-			The uncertainties of yields include statistical and systematic \cite{2}}} 
-	\begin{tabular}{cc}
-		\hline
-		Process & Number of events \\
-		\hline
-		$t\bar{t}W$ & 68 $\pm$ 10 \\
-		$t\bar{t}Z$ & 25.9 $\pm$ 3.9\\
-		$WZ$ & 15.1$\pm$7.7\\
-		Rares & 20.9 $\pm$ 4.9\\
-		Fakes & 80.9 $\pm$9.4\\
-		$t\bar{t}H$ & 24.2 $\pm$ 2.1 \\
-		\hline
-		$tH$ (SM) & 2.14 $\pm$ 0.13\\
-		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
-	\end{tabular}	
-	\label{tth-table}
-\end{table}
-%	\begin{figure}	\centering
-%	\includegraphics[width=\textwidth]{figures/sc.png}
-%	\caption*{\tiny{Observed and expected 95$\%$ C.L.
-upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
-The expected limit is derived from a background-only MC dataset.}}
-%	\end{figure}
-\end{minipage}
-\end{frame}
-}
-
-{\nologo
-\begin{frame}
-\begin{minipage}[b]{.48\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{figures/kos.png}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.48\textwidth}
-	\begin{figure}
-		\centering
-		\includegraphics[width=\textwidth]{figures/kos2.png}
-	\end{figure}
-\end{minipage}
-\begin{center}
-\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
-\end{center}
-\end{frame}
-}
-
-\begin{frame}
-\subsection{Systematic uncertainties}
-\frametitle{Systematic uncertainties}
-\begin{itemize}
-	\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
-	\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
-	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
-	\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
-\end{itemize}
-
 \end{frame}
@@
 \end{itemize} }
+\end{frame}`
+
+{\nologo
+	\begin{frame}
+	\Fontvi
+	\begin{center}
+		\begin{tabular}{cc}
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
+			{Distribution of selected events as a function of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub}\\
+			{Distribution of jet events for $|\eta|$>1 } & {Distribution of events of pt of the sub leading leptons} \\
+		\end{tabular}
+	\end{center}
+\end{frame}
+}
+
+{\nologo
+\begin{frame}
+\Fontvi
+\begin{center}
+	\begin{tabular}{cc}
+	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
+\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\ 
+{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
+		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
+		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
+		{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
+	\end{tabular}
+\end{center}
+\end{frame}
+}
+
+{\nologo
+\begin{frame}
+\subsection{Previous results}
+\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
+\begin{minipage}[c]{0.45\textwidth}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.3]{figures/histo.png}
+	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}[c]{.45\textwidth}
+	\small
+\begin{table}
+	\centering
+	\caption*{\tiny{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
+The uncertainties of yields include statistical and systematic \protect \footnotemark} }
+	\begin{tabular}{cc}
+		\hline
+		Process & Number of events \\
+		\hline
+		$t\bar{t}W$ & 68 $\pm$ 10 \\
+		$t\bar{t}Z$ & 25.9 $\pm$ 3.9\\
+		$WZ$ & 15.1$\pm$7.7\\
+		Rares & 20.9 $\pm$ 4.9\\
+		Fakes & 80.9 $\pm$9.4\\
+		$t\bar{t}H$ & 24.2 $\pm$ 2.1 \\
+		\hline
+		$tH$ (SM) & 2.14 $\pm$ 0.13\\
+		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
+	\end{tabular}	
+	\label{tth-table}
+\end{table}
+%	\begin{figure}	\centering
+%	\includegraphics[width=\textwidth]{figures/sc.png}
+%	\caption*{\tiny{Observed and expected 95$\%$ C.L.
+upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
+The expected limit is derived from a background-only MC dataset.}}
+%	\end{figure}
+\end{minipage}
+\footnotetext{\tiny The CMS collaboration, \textit{Search for production of a Higgs boson and a single top
+			quark in multilepton final states in proton collisions at 13 TeV}, CMS-HIG-18-009, Phys. Rev. D 99, 092005}
+\end{frame}
+}
+
+{\nologo
+\begin{frame}
+\frametitle{Distribution of events in the BDT discriminant}
+\begin{minipage}[b]{.48\textwidth}
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{figures/kos.png}
+\end{figure}
+\end{minipage}
+\hfill
+\begin{minipage}[b]{.48\textwidth}
+	\begin{figure}
+		\centering
+		\includegraphics[width=\textwidth]{figures/kos2.png}
+	\end{figure}
+\end{minipage}
+\begin{center}
+\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
+\end{center}
+\end{frame}
+}
+
+\begin{frame}
+\subsection{Systematic uncertainties}
+\frametitle{Systematic uncertainties}
+\begin{itemize}
+	\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
+	\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
+	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+	\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
+	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
+\end{itemize}
+
 \end{frame}
@@
 \frametitle{Results}
-\framesubtitle{Likelihood scan}
+\framesubtitle{Likelihood scan for an integrated luminosity of 35.9 fb$^{-1}$}
 \begin{minipage}{0.5\textwidth}
@@
 
-\begin{frame}
-\section{Conclusions}
-\frametitle{Conclusions}
-\begin{itemize}
-	\item We analyzed the $tH$ process produced from PP collisions for the production of $\mu\mu$ final states   
-	\item We discussed about events selections for the 2016 Run 2 from CMS.
-	\item The creation of an Asimov model with systematic uncertainties to make a minimization (fit) and obtain a fit which is compatible with Standard Model.
-	\item Generation of likelihood scan for the exclusion of data and obtain the probability of detection of a Higgs boson.
-	\item Generating simulations for predict results with higher luminosities, according to the future experiments. 
-\end{itemize}
-\end{frame}
+%\begin{frame}
+%\section{Conclusions}
+%\frametitle{Conclusions}
+%\begin{itemize}
+%	\item We analyzed the $tH$ process produced from PP collisions for the production of $\mu\mu$ final states   
+%	\item We discussed about events selections for the 2016 Run 2 from CMS.
+%	\item The creation of an Asimov model with systematic uncertainties to make a minimization (fit) and obtain a fit which is compatible with Standard Model.
+%	\item Generation of likelihood scan for the exclusion of data and obtain the probability of detection of a Higgs boson.
+%	\item Generating simulations for predict results with higher luminosities, according to the future experiments. 
+%\end{itemize}
+%\end{frame}
 
@@
 \item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
-\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical and not related with the SM.
+\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical.
 \item It requires a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
@@
 
-{\nologo
-	\begin{frame}
-
-	\Fontvi
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\ 
-			{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of jet events for $|\eta|$>1} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-sch}\\
-			{Distribution of events of $|\Delta\phi|$ between the higher pt pair of leptons } & {Distribution of events of the sum of same sign leptons charge.} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-{\nologo
-	\begin{frame}
-	\Fontvi
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
-			{Distribution of selected events as a function of $|\eta|$ of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
-			{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\eta|$ between a forward jet and a b-tagged jet } \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
 \end{document}

### 2019-11-14 tesis_hiram/Abstract/resumen.tex
new

\thispagestyle{empty}
 \vspace*{2.2cm}
\begin{center}
\Large \textbf{Resumen}
\end{center} 
\vspace{1.5cm}
\selectlanguage{spanish}
	\begin{poliabstract}
	Presento un estudio sobre la producci\'on de un boson de Higgs y un top quark ($tH$) en un canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN. Estudiando este proceso, se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente. La sensibilidad esperada es calculada usando un grupo de datos tipo Asimov para 35.9 fb$^{-1}$ para colisiones de prot\'on-prot\'on y esos datos son extrapolados a niveles altos de luminosidad, de acuerdo a la fase de alta luminosidad en el LHC. La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con un acoplamiento invertido de Yukawa $k_t$=-1, donde $k_t$ es el par\'ametro de acoplamiento de top-Higgs, para compararlo con el modelo est\'andar.
\end{poliabstract}

### 2019-11-14 project_ashish/paper.tex

@@
-%% 
-%% Copyright 2016 Icm Ltd
 \documentclass[final,3p]{CSP}
@@
 \usepackage{float}
+\usepackage{fancyhdr}
+%\usepackage[margin=1in,headsep=.2in]{geometry}
+
+\pagestyle{fancy}
+\fancyhf{}
+\rhead{Thesis Project Proposal}
+\lhead{Ashish Sehrawat}
+\rfoot{Page \thepage}
+
+\setlength{\headsep}{0.2in}
+
 \begin{document}
 
-\begin{frontmatter}
-
-\title{THESIS PROJECT PROPOSAL}
-
-\author[]{Ashish Sehrawat$^a$}
-\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}
-
-%\author[mysecondaryaddress]{Global Customer Service\corref{mycorrespondingauthor}}
+%\begin{frontmatter}
+%\title{THESIS PROJECT PROPOSAL}  
+%\author[]{Ashish Sehrawat$^a$}
+%\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}
 %\cortext[mycorrespondingauthor]{Corresponding author}
 %\ead{support@Icm.com}
+%\address[mymainaddress]{Universidad de Sonora}
+%\begin{keyword}\rm
+%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
+%Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
+%\end{adjustwidth}
+%\end{keyword}
+%\begin{keyword} \rm
+%\end{keyword}
+%\begin{abstract}\rm
+%\end{abstract}
+%\end{frontmatter}
 
-\address[mymainaddress]{Universidad de Sonora}
-%\address[mysecondaryaddress]{Universidad de Sonora}
+\begin{titlepage}
+	\centering
+        {\scshape\Large THESIS PROJECT PROPOSAL\par}
 
-\begin{keyword}\rm
-\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
-Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
+	\vspace{2cm}
+        \begin{adjustwidth}{2cm}{2cm}{
+            TITLE:\par
+            \large{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}\par}
         \end{adjustwidth}
-\end{keyword}
 
-\begin{keyword}\rm
-\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Title:}}  
-Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider.
+	\vspace{0.5cm}
+        \begin{adjustwidth}{2cm}{2cm}{
+            RESEARCH LINE: \par
+            Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas \par}
         \end{adjustwidth}
-\end{keyword}
 
-\begin{abstract}\rm
-% \begin{adjustwidth}{2cm}{2cm}{
-\itshape\textbf{Abstract:}
-The abstract
-%\end{adjustwidth}
-\end{abstract}
+        \vspace{4cm}
+        {\underline{\hspace{8cm}}\par}
+	{\scshape\large Ashish Sehrawat\par}
+        {Student\par}
 
-\end{frontmatter}
+        \vspace{1cm}
+        {\underline{\hspace{8cm}}\par}
+	{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio\par}
+        {Director\par}
 
+        \vspace{1cm}
+        {Program: Doctorado en Ciencias (F\'{i}sica) \par}
+        {Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS) \par}
+        {Universidad de Sonora \par}
+
+        \vfill
+	{\today}
+
+\end{titlepage}
+
+\newpage
+{
+\hspace{0pt}
+\vfill
+\centering
+
+  \begin{adjustwidth}{2cm}{2cm}{\large Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider\par}
+    \vspace{1cm}
+    \centering
+    {\itshape\textbf{Abstract:}\par}
+    The abstract \par
+  \end{adjustwidth}
+
+\hspace{0pt}
+\vfill
+}
+
+%\centering Ashish Sehrawat
+%\newline \newline
+%\centering Director: Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio
+%\newline \newline
+%Posgrado en Ciencias (Fis\'{i}ca)
+%\newline 
+%Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS)
+%\newline 
+%Universidad de Sonora
+%\newline \newline
+%\today
+
+\newpage
 \section{BACKGROUND}
@@
 The expected results of this project are the following:
-• Improve data adjustments and study the effects of uncertainties.
-• Improve the sensitivity to the tH signal in the data of the second CMS run.
-• Limit calculations in the effective section incorporating data from the second
-run of the LHC.
-• Calculate projections of signal sensitivity for the different phases of the LHC.
+- Improve data adjustments and study the effects of uncertainties.
+- Improve the sensitivity to the tH signal in the data of the second CMS run.
+- Limit calculations in the effective section incorporating data from the second run of the LHC.
+- Calculate projections of signal sensitivity for the different phases of the LHC.
 
-\bibliographystyle{unsrt}
-\cleardoublepage
-\bibliography{paper}
-
-\appendix
 \section{SKILLS THAT WILL BE DEVELOPED}
@@
 
+\bibliographystyle{unsrt}
+\cleardoublepage
+\bibliography{paper}
+
 \end{document}

### 2019-11-14 project_ashish/paper.tex
fixed format

@@
 \usepackage{float}
+
 \usepackage{fancyhdr}
-%\usepackage[margin=1in,headsep=.2in]{geometry}
-
 \pagestyle{fancy}
 \fancyhf{}
-\rhead{Thesis Project Proposal}
-\lhead{Ashish Sehrawat}
+
+\def\Student{Ashish Sehrawat}
+\def\Title{THESIS PROJECT PROPOSAL}
+\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
+\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
+\def\Director{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio}
+\def\ProjectTitle{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}
+
+%%header and footer
+\lhead{\Student}
+\rhead{\Title}
+\lfoot{\Dept}
 \rfoot{Page \thepage}
-
 \setlength{\headsep}{0.2in}
+\renewcommand{\footrulewidth}{0.4pt}% default is 0pt
 
@@
 
-%\begin{frontmatter}
-%\title{THESIS PROJECT PROPOSAL}  
-%\author[]{Ashish Sehrawat$^a$}
-%\author[]{Dr. Jose Feliciano Benitez Rubio$^b$}
-%\cortext[mycorrespondingauthor]{Corresponding author}
-%\ead{support@Icm.com}
-%\address[mymainaddress]{Universidad de Sonora}
-%\begin{keyword}\rm
-%\begin{adjustwidth}{2cm}{2cm}{\itshape\textbf{Keyword:}}  
-%Higgs boson, Higgs boson production, Higgs boson decay, Higgs boson coupling, 
-%\end{adjustwidth}
-%\end{keyword}
-%\begin{keyword} \rm
-%\end{keyword}
-%\begin{abstract}\rm
-%\end{abstract}
-%\end{frontmatter}
-
+%%%%Title Page
 \begin{titlepage}
   \centering
-        {\scshape\Large THESIS PROJECT PROPOSAL\par}
+  \hspace{0pt}
+  \vfill
+        {\scshape\Large \Title \par}
 
@@
             TITLE:\par
-            \large{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}\par}
+            {\large \ProjectTitle \par}
+          }
         \end{adjustwidth}
@@
         {\underline{\hspace{8cm}}\par}
-	{\scshape\large Ashish Sehrawat\par}
+	{\scshape\large \Student \par}
         {Student\par}
@@
         {\underline{\hspace{8cm}}\par}
-	{Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio\par}
+	{\Director \par}
         {Director\par}
@@
         \vspace{1cm}
-        {Program: Doctorado en Ciencias (F\'{i}sica) \par}
-        {Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS) \par}
+        {\Prog \par}
+        {\Dept \par}
         {Universidad de Sonora \par}
 
+        \vspace{4cm}
+	{\today}
+
+\hspace{0pt}
 \vfill
-	{\today}
 
@@
 
+%%%%% white page for print out
+\shipout\null
+
+%%%% Abstract Page
 \newpage
-{
 \hspace{0pt}
 \vfill
-\centering
 
-  \begin{adjustwidth}{2cm}{2cm}{\large Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider\par}
+\begin{adjustwidth}{1cm}{1cm}
+
+  \begin{center}
+    {\Large \ProjectTitle \par}
     \vspace{1cm}
-    \centering
-    {\itshape\textbf{Abstract:}\par}
+    {\itshape\textbf{Abstract}\par}
+  \end{center}
+
   The abstract \par
+
 \end{adjustwidth}
@@
 \vfill
-}
 
-%\centering Ashish Sehrawat
-%\newline \newline
-%\centering Director: Dr. Jos\'{e} Feliciano Ben\'{i}tez Rubio
-%\newline \newline
-%Posgrado en Ciencias (Fis\'{i}ca)
-%\newline 
-%Departamento de Investigac\'{i}on en Fis\'{i}ca (DIFUS)
-%\newline 
-%Universidad de Sonora
-%\newline \newline
-%\today
-
+%%%%%% Begin the body
 \newpage

### 2019-11-14 tesis_hiram/Chapter1/chapter1.tex

@@
 Mesons, are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
-Baryons are fermions made of 3 quarks. Examples of baryons are protons and neutrons. Both particles can interact via strong force.
+Baryons are fermions made of 3 quarks.
+Examples of baryons are protons and neutrons.
+Both particles can interact via strong force.
+Since quarks and gluons only exist in bound states, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
+bound state\cite{gross.griff}.
 \\
@@
 The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down, strange and bottom quarks have charge of $-\frac{1}{3}$.
-Among them, the top quark is the most massive of all, while the up and down are the least massive.
-The lepton and quarks have their respective antiparticle, which have the same mass, but inverted charge.\\ 
+Among them, the top quark is the most massive of all, while the up and down are the least massive.\\
 Some of the particles in the SM are not stable, so they decays and form particles with lower masses.
@@
 \\
-Since quarks and gluons only exist in bound states, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
-bound state. As two quarks are separated, the strong force between them increases
-which is equivalent to the potential energy increasing. This energy transforms into
-quark-anti-quark pairs. \\
 
 The table \ref{SM table} contains the characteristics of each particle in the SM.
-Note the distance column refers to particles moving with speeds near light speed.
+The second column shows the masses of the particles, where the most massive particle is the top quark with 173 GeV.
+There are particles with mass equal to zero, such as the gluons, photons and the neutrinos.
+\\
+The third column corresponds to the charge of the particles.
+For the quarks, there are two different charges: $\frac{2}{3}$ for $u$,$c$ and $t$ and $-\frac{1}{3}$ for $d$,$s$ and $b$.
+For the leptons, the charge is negative, except for neutrinos, which charge is zero.
+The bosons have a integer charge; $\pm 1$ for $W$ and 0 for $Z$, $\gamma$, $H$ and $g$.	\\
+The next column is the spin, where for fermions (quarks and leptons) is $\frac{1}{2}$ and for bosons is 1\footnote{In general, the fermions have non integer spin and the bosons have integer spin}.
+The Higgs boson is the only boson with spin 0.\\
+The next one is the lifetime of the particle, where it shows how long the particles exist before decay.
+Stable lifetime means that the particles do not decay or can exist until they can interact with detectors.\\
+The last column is the distance of particles moving with speeds near light speed.
 This column visualize the distance traveled in the predicted lifetime of the particle.
 And also give us a perspective of how hard is the detection of the particles due to lifetime.
-Stable lifetime means that the particles do not decay or can exist until they can interact with detectors.
 \\
@@
 \begin{table}[!htbp]
-\caption{Table of particles in SM\cite{pd}. Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
+\caption{Table of particles in SM, where it shows the masses, charges,spin, lifetime and distance traveled in a lifetime .
+Stable means no decay, or lifetime almost infinite\cite{pd}.
+Particles speeds at c=0.998}
 \renewcommand{\arraystretch}{1.5}
@@
 	\hline 
-$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 
+Tau ($\tau$)	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 
 	\hline 

### 2019-11-14 tesis_hiram/Chapter5/chapter5.tex

@@
 Recently CMS published a search for $tH$ process using 35.9 fb$^{-1}$ from Run 2 in 2018.
-\\
+Using this information, it was studied the expected sensibility using an Asimov data and systematic uncertainties for final states of same sign pairs of muons \\
 
-MC simulation and real data or even only MC can be used to study sensitivity different signal processes.
-In this work we used the information published by CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
-In the SM case, the signal strength for the signal $tH$ is very low in comparison to
-the backgrounds, resulting in large uncertainties.
+In the SM case, the signal strength for the signal $tH$ is 2.2 that is very low in comparison to
+the backgrounds, resulting in large uncertainties. The uncertainty is around eight times than the signal strength. 
 For the inverted coupling scenario ($k_t$=-1), the uncertainty for the model after the fit was better than the
-SM case, this is due to the larger expected number of signal events. However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels.
+SM case, this is due to the larger expected number of signal events. In this case 26.2 with an uncertainty of around 50$\%$.
 \\
@@
 In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb$^{-1}$.\\
+
+In the SM, same sign $\mu\mu$ final states of the $tH$ process, it shows that is impossible to give evidence of the existence of a Higgs boson due to high uncertainties.
+The expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
+For the $k_t$=-1, the uncertainty is low due to higher number of events for tH process and it is possible to give evidence of a Higgs
+boson, but this model is purely theoretical.\\
+
+However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels.
+The search can include channels, such as three lepton in the final state or a pair of leptons with different sign.
+By adding more channels, the number of events increases and can give us better statistics.

### 2019-11-14 project_ashish/paper.tex
fix background

@@
 \usepackage{float}
+\usepackage{afterpage}
 
@@
 
--SM, Higgs, couplings, previous Higgs measurements, previous tH searches
-
 The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
@@
 
- \newpage
+% \newpage
 
@@
 
+\afterpage{
 \begin{figure}[H]
@@
 \end{figure}
-\newpage
+\clearpage
+}
+% \newpage
 
@@
 strength modifier $\kappa_t$ is defined as $\kappa_t = \frac{y_t}{y^{SM}_t}$ which will tell 
-us the deviation of $y_t$ from the SM prediction as shown in Figure 6.
+us the deviation of $y_t$ from the SM prediction.
 
@@
 million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure 5.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
 So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+
+\afterpage{
 
@@
 	\caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
-	\label{figure 5}
+	\label{figure5}
 \end{figure}
+
+ \begin{figure}[H]
+ 	\centering
+ 	\includegraphics[scale=0.45]{./lum6.png}
+ 	\caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
+Points show instant brightness while the line shows brightness accumulated.}
+ 	\label{figure6}
+ \end{figure}
+
+\clearpage
+}
+
+\afterpage{
 
@@
 	\caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
-	\label{figure 6}
+	\label{figureKappas}
 \end{figure}
-
- LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ in 10-12 years.
-All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ in its first 10-12 years of life \cite{collaborations2019report}.
-LHC will reach an integrated luminosity of about 300 $fb^{-1}$ by 2023.
-
- Earlier searches for Higgs boson production production in association with single top quark have been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
-Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure 7.
-Multilepton final state and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
-The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges of about [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
 
@@
   \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
-   \label{figure 7}
+   \label{figureKt}
 \end{figure}
+
+\clearpage
+}
+
+LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+Figure~\ref{figureKappas} shows a summary of the current measurments of the Higgs coupling parameters with the LHC Run 1 dataset.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
+
+Earlier searches for Higgs boson production production in association with single top quark have been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
+Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt}.
+Multilepton final state and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
+The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges of about [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
 
@@
 expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that will begin 
-in 2026 as shown in Figure 8.
+in 2026.
 
- \begin{figure}[H]
- 	\centering
- 	\includegraphics[scale=0.45]{./lum6.png}
- 	\caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instant brightness while the line shows brightness accumulated.}
- 	\label{figure 8}
- \end{figure}
 \section{GENERAL OBJECTIVE}

### 2019-11-14 presentacion_hiram/presentacion-tesis.tex
new

@@
 \begin{document}
-	\author{Departamento de Investigacion en F\'isica \\
+	\author{\tiny
+			L.F. Hiram Ernesto Dami\'an\\
+			\vspace{5px}
+				Director:\\
+					\vspace{5px}
+			Jos\'e Feliciano Ben\'itez Rubio\\
+				\vspace{5px}
 				Maestr\'ia en Ciencias (F\'isica)\\
-		Hiram Ernesto Dami\'an\\
-	Director:\\
-Jos\'e Feliciano Ben\'itez Rubio}
+					\vspace{5px}
+			 Departamento de Investigacion en F\'isica }
 	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
@@
 	\institute{Universidad de Sonora}
-	%\date{}
+	\date{\small November 15$^{th}$ 2019}
 	%\subject{}
@@
 	\includegraphics[scale=0.2]{figures/CERN's-accelerator-complex2013.jpg}
+	\caption*{LHC complex}
+	\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{LHC}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.6]{figures/lhc-u.png}
+	\caption*{Underground view of LHC complex}
 \end{figure}
@@
 \begin{frame}
-\frametitle{LHC}
+\frametitle{CMS detector}
 \begin{figure}[ht!]
@@
 	\caption*{Slide view of the CMS in terms of pseudorapidity $\eta=-\ln\left[\tan\left(\frac{\theta}{2}\right)\right]$}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+\frametitle{CMS detector}
+\begin{figure}
+	\centering
+	\includegraphics[scale=0.4]{figures/pp.png}
+	\caption*{\small A typical CMS event display of the Higgs boson decaying to four leptons with 2 muons (in red) and 2 electrons (in green) as final state signatures.}
 \end{figure}
@@
 	those features.
-	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data. \\
-
+	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.\\
+	\vspace{10px}
 	BDT Variables}
@@
 \end{itemize} }
-\end{frame}`
+\end{frame}
 
@@
 		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}\\ 
-			{Distribution of selected events as a function of the jet with largest value of $|\eta|$} & {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub}\\
-			{Distribution of jet events for $|\eta|$>1 } & {Distribution of events of pt of the sub leading leptons} \\
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
+			  {Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
+			  	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
+			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
+			 {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
 		\end{tabular}
@@
 	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
+\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
+{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
+		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
 		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
-{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
-		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\
-		{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
+		{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
 	\end{tabular}
@@
 		\includegraphics[width=5.5cm,height=5cm]{figures/simple-kt-1.png}
-		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. In the
-			box below each distribution, the ratio of the observed and event yields is shown}}
+		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. 
+	In the box below each distribution, the ratio of the observed and event yields is shown}}
 	\end{figure}
@@
 Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
-
 \item We can define the likelihood ratio
@@
 Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
-
 \item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
@@
 	\begin{frame}
-	\small
+	\tiny
 %	\section{References}
@@
 \url{https://indico.cern.ch/event/287744/contributions/1641261/attachments/535763/738679/Verkerke_Statistics_3.pdf}
-\end{frame}
-
-\begin{frame}
-\small
 \bibitem{5} ATLAS and CMS
@@
 \bibitem{6}CMS collaboration \textit{High-Luminosity Large Hadron Collider (HL-LHC)}, 2017,CERN-2017-007-M
-
 \end{frame}
@@
 
-\begin{frame}
+%\begin{frame}
 %\section{Supportive slides}
-\huge{Back up}
-\end{frame}
-
-\begin{frame}
-\frametitle{Sources of uncertainty on event yields}
-\begin{itemize}
-	\item Luminosity measurement: ~2.6$\%$.
-	\item Data/MC scale factors for lepton selection (ID, iso) and trigger efficiencies ~5$\%$ per lepton.
-	\item Choice of PDF set:
-	\begin{itemize}
-		\item 3.7$\%$ for tHq
-		\item ~4$\%$ for tHW t$\bar{t}$W, t$\bar{t}$Z, t$\bar{t}$H 
-		\item Scale uncertainties: 12$\%$, 4 for t$\bar{t}$W, 10$\%$ for t$\bar{t}$Z, +5.8/-9.2$\%$ for t$\bar{t}$H.
-	\end{itemize}
-	\item Background: WZ, ZZ sample modelling and statistics: ~50$\%$.
-	\item Rare SM (tZ,tri-bosons, WWqq, tttt) : 50$\%$
-	\item Fake rate estimation:
-	The predicted event yield has a normalization uncertainty of ~30-50$\%$ \cite{7}
-\end{itemize}
-
-\end{frame}
+%\huge{Back up}
+%\end{frame}
+
+%\begin{frame}
+%\frametitle{Sources of uncertainty on event yields}
+%\begin{itemize}
+%	\item Luminosity measurement: ~2.6$\%$.
+%	\item Data/MC scale factors for lepton selection (ID, iso) and trigger efficiencies ~5$\%$ per lepton.
+%	\item Choice of PDF set:
+%	\begin{itemize}
+%		\item 3.7$\%$ for tHq
+%		\item ~4$\%$ for tHW t$\bar{t}$W, t$\bar{t}$Z, t$\bar{t}$H 
+%		\item Scale uncertainties: 12$\%$, 4 for t$\bar{t}$W, 10$\%$ for t$\bar{t}$Z, +5.8/-9.2$\%$ for t$\bar{t}$H.
+%	\end{itemize}
+%	\item Background: WZ, ZZ sample modelling and statistics: ~50$\%$.
+%	\item Rare SM (tZ,tri-bosons, WWqq, tttt) : 50$\%$
+%	\item Fake rate estimation:
+%	The predicted event yield has a normalization uncertainty of ~30-50$\%$ \cite{7}
+%\end{itemize}
+%\end{frame}
 
@@
 
-\begin{frame}
-\frametitle{Sources of systematic uncertainty}
-Detector-simulation related uncertainty
-\begin{itemize}
-\item Calibrations (electron, jet energy scale)
-\item Efficiencies (particle ID, reconstruction)
-\item Resolutions (jet energy, muon momentum)
-\end{itemize}
-Theoretical uncertainties
-\begin{itemize}
-\item  Factorization/Normalization scale of MC generators
-\item Choice of MC generator (ME and/or PS, e.g. Herwig vs Pythia)
-\end{itemize}
-Monte Carlo Statistical uncertainties
-\begin{itemize}\item Statistical uncertainty of simulated samples\cite{2} \end{itemize}
-\end{frame}
-
-\begin{frame}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.5]{figures/compare_variables}
-	\caption*{Signal and background kinematic distributions}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{Results}
-\framesubtitle{Likelihood scan}
-\begin{itemize}
-	\item Likelihood function (often simply the likelihood) is a function of the
-	parameters of a statistical model, given specific observed data.
-	\item Likelihood functions play a key role in frequentist inference,
-	especially methods of estimating a parameter from a set of
-	statistics.
-	\item In informal contexts, "likelihood" is often used as a synonym for
-	probability.
-\end{itemize}
-\end{frame}
+%\begin{frame}
+%\frametitle{Sources of systematic uncertainty}
+%Detector-simulation related uncertainty
+%\begin{itemize}
+%\item Calibrations (electron, jet energy scale)
+%%\item Efficiencies (particle ID, reconstruction)
+%\item Resolutions (jet energy, muon momentum)
+%\end{itemize}
+%Theoretical uncertainties
+%\begin{itemize}
+%\item  Factorization/Normalization scale of MC generators
+%\item Choice of MC generator (ME and/or PS, e.g. Herwig vs Pythia)
+%\end{itemize}
+%Monte Carlo Statistical uncertainties
+%\begin{itemize}\item Statistical uncertainty of simulated samples\cite{2} \end{itemize}
+%\end{frame}
+
+%\begin{frame}
+%\begin{figure}
+%	\centering
+%	\includegraphics[scale=0.5]{figures/compare_variables}
+%	\caption*{Signal and background kinematic distributions}
+%\end{figure}
+%\end{frame}
+
+%\begin{frame}
+%\frametitle{Results}
+%\framesubtitle{Likelihood scan}
+%\begin{itemize}
+%	\item Likelihood function (often simply the likelihood) is a function of the
+%	parameters of a statistical model, given specific observed data.
+%	\item Likelihood functions play a key role in frequentist inference,
+%	especially methods of estimating a parameter from a set of
+%	statistics.
+%	\item In informal contexts, "likelihood" is often used as a synonym for
+%	probability.
+%\end{itemize}
+%\end{frame}
 

### 2019-11-15 project_ashish/paper.tex
proposal, objetivo, hypthesis

@@
   \centering
-   \includegraphics[scale=0.5]{./cd2.png}
+   \includegraphics[scale=0.7]{./cd2.png}
   \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
@@
 
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=\columnwidth]{./cms.png}
+	\caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
+	\label{figure 4}
+\end{figure}
+
 The production of Higgs boson in association with single top quark is one of the rare Higgs 
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=\columnwidth]{./cms.png}
-	\caption{Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
-	\label{figure 4}
-\end{figure}
-
  These two processes in standard model have destructive interference which allow us to 
@@
 
-The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top 
-quark associated production mode. 
-The anomalous coupling will arise when we add interaction terms (dimension 6 operators in 
-effective SM theory) in the Higgs 
-potential. As there is strong destructive inteference in the t-channel for the standard model 
-couplings, this production mode 
-is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs 
-boson and top quark induced by 
-higher dimensional operators in effective SM theory \cite{sirunyan2019search}.
+The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. 
+The anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential.
+As there is strong destructive inteference in the t-channel for the standard model  couplings, this production mode is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs  boson and top quark induced by  higher dimensional operators in effective SM theory \cite{sirunyan2019search}.
 
@@
 \afterpage{
-
-\begin{figure}[H]
+  \begin{figure}[ht]
     \centering
-	\includegraphics[scale=0.36]{./cms12.png}
+    \includegraphics[width=0.7\columnwidth]{./cms12.png}
     \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
@@
 
- \begin{figure}[H]
+  \begin{figure}[ht]
     \centering
- 	\includegraphics[scale=0.45]{./lum6.png}
+    \includegraphics[width=0.9\columnwidth]{./lum6.png}
     \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
@@
   \end{figure}
-
   \clearpage
@@
 \afterpage{
-
- \begin{figure}[H]
+  \begin{figure}[ht]
     \centering
@@
 
- \begin{figure}[H]
+  \begin{figure}[ht]
     \centering
@@
   \end{figure}
-
 \clearpage
@@
 LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-Figure~\ref{figureKappas} shows a summary of the current measurments of the Higgs coupling parameters with the LHC Run 1 dataset.
 All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
@@
 
-Earlier searches for Higgs boson production production in association with single top quark have been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
+Figure~\ref{figureKappas} shows a summary of the current measurments of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and $tt$H production modes.
+
+Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
 Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt}.
@@
 
+\newpage
 \section{PROPOSAL}
 
-- what we will do:  search for tH events, using which channels.
-
-In this project, it is proposed to study the production channel of the Higgs boson associated 
-with a single top quark in the Large Hadron Collider of the CERN laboratory. The measurement 
-of this process complements other measurements of the yukawa coupling parameter of the top 
-quark and Higgs boson. It is a part of the physics program of CMS international 
-collaborations and ATLAS and it has not been observed so far. It is proposed to study 
-sensitivity with the current data in the channel where the events are identified with two 
-muons of the same sign. The impact of uncertainties will be studied and projections will be 
-made to the future phases of the LHC. For these studies the data of the run two (2015-2018) 
-of the LHC identifying the signal events with two muons from the same sign. It is also 
-expected to estimate projections for the high brightness phase of the LHC (HL-LHC) that will begin 
-in 2026.
+In this project, it is proposed to search for the production of Higgs boson associated with a single top quark in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
+It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign or with three leptons of electron or muon type.
+Leptons of tau type are not considered due to complications in their identificaiton in the detector.
+%The impact of uncertainties will be studied and projections will be  made to the future phases of the LHC.
+For these studies the data of the LHC Run 2 (2015-2018) will be used corresponding to an integrated luminosity of about 150 fb$^{-1}$, this is 4 times larger than the dataset used for current results.
+It is also expected to estimate projections of the sensitivity to the High Luminosity phase of the LHC (HL-LHC) (2026-2036) which will accumulate up to 100 times the data used for current measurements.
 
@@
 
-- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
+%- motivation, tH production crossection, sign of $k_t$, search for BSM, ..
 
-There is currently a great enigma in physics since we know that ordinary matter comprises 
-only $5\%$ of the universe, another 
-$27\%$ includes what we call dark matter. Understanding the production of the Higgs boson, as 
-well as its decays like the invisible decay modes are an important part of the physics 
-program of CERN laboratory experiments to verify the Standard Model and look for new 
-particles. Through this project we will investigate the production of the Higgs boson in 
-association with a single top quark (tH) in proton-proton collisions with the CMS experiment 
-of the LHC. We will study the distribution of events in one of the decay channels and the 
-sensitivity that we get with the current data. The main objective is to search for new 
-processes such as tH Higgs production mode in the CMS experiment which require to study 
-different aspects such as the model of the noises that are made by simulation, techniques of 
-adjustments to the data that incorporate the different noises and the signal, and estimates 
-of statistical and systematic uncertainties.
+There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another  $27\%$ includes what we call Dark Matter.
+Understanding the production of the Higgs boson, as well as its decays like the invisible decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
+Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.
+The tH  production process has not been observed so far.
+The measurement  of this process complements other measurements of the yukawa coupling parameter of the top  quark and Higgs boson and is a part of the physics program of CMS  and ATLAS international collaborations.
+Through these measurements we seek to complete the measurements of the Standard Model parameters to high precision or to find evidence of deviations which point to new particles which may explain current enigmas like the origin of Dark Matter.
+
+\section{HYPOTHESIS}
+%%  - what we expect to find
+
+Studies in the tH channel have already started with the collaborations CMS and ATLAS with publications based on data from the 2011-2012 run and some data from the second run of 2015-2016.
+In these results it was not found evidence of signal and upper limits have been set on the production cross-section.
+The current results combine three types of searches: H$\rightarrow WW/ZZ/\tau\tau \rightarrow$leptons, H$\rightarrow\gamma\gamma$, and H$\rightarrow b\bar{b}$.
+%The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
+The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{ref:tH2019}, the limit is 26 times larger than the expected value.
+In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, this result almost rules out this model.
+
+With this project we propose to incorporate the full Run 2 dataset corresponding to 150 pb$^{-1}$.
+A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
+These means the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be almost fully excluded.
+
+Additionally, in subsequent phases of the LHC (2021-2023 and 2026-2038) the amount of data will increase by a factor of up to 100, which implies the upper limit for the SM case will reduce to about 2.6 times the expected cross-section.
+This implies that even for the HL-LHC it will be difficult to observe the tH production, but at the same time more and more phase space of BSM models will be excluded.
+
+In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}$H production because the cross-section of $t\bar{t}$H is much larger than that of tH and some events pass the selections designed for tH.
+The fraction of tH events over tH + $t\bar{t}$H is currently only 5$\%$ with the analysis techniques used.
+We expect to improve the analysis techniques using multi-variate techniques, for example boosted decision trees or other algorithms, to improve the identification of signal events over the rest of the backgrounds.
+This will provide additional improvements in the limits and a possible observation of the SM signal as well as stringent exclusions for BSM models.
+
+\section{SPECIFIC OBJECTIVES}
+- details
+
 Some of the objectives in this project include:
 \begin{itemize}
+\item We will study the distribution of events in one of the decay channels and the  sensitivity that we get with the current data.
 \item study one or more decay channels.
@@
 \end{itemize}
-
-\section{SPECIFIC OBJECTIVES}
-- details
-
-\section{HYPOTHESIS}
-- what we expect to find
-
-Production studies in the tH channel have already started with the collaborations CMS and 
-ATLAS with publications based on data from the 2011-2012 run and some data from the second 
-run of 2015-2016. In these results it was not found signal evidence and upper limits have 
-been set for the effective section. With the more sensitive analysis an upper limit is 
-calculated for the effective section of a signal composed of tH and ttH that corresponds 3.1 
-times that expected in the SM. In this analysis the reconstruction methods do not allow to 
-distinguish between tH and t$\bar{t}$H because the effective section of t$\bar{t}$H is much 
-larger than that of tH and some events pass the selections designed for tH, the fraction of 
-tH events over tH + t$\bar{t}$H is 5. In BSM models the fraction could change up to 50, for 
-example with $\kappa_t = -1$. It could help to obtain better limits for the production of tH. 
-The data that has been used so far correspond to only 20 of the final data of the run that 
-which ends in 2018. The uncertainty for the signal in the current analysis is mostly 
-statistical nature, therefore adding the total data in a new analysis the next year, 
-sensitivity can be improved with an approximate factor of 2.2. Additionally, in subsequent 
-phases of the LHC 2021-2023 and 2026-2038 the number of data fold and then multiply by 10 
-respectively. With these additions It is expected that the signal from the Higgs boson can be 
-observed on the tH production channel. The current results can be used to project sensitivity 
-in the third run and the high brightness phase and thus contribute to the planning of the 
-updates of the detector.
 

### 2019-11-15 tesis_hiram/Chapter2/chapter2.tex
new

@@
 \end{figure}
-In the barrel, there photo detectors called avalanche photo diodes (APD), made of silicon with a active area of 5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.
+In the barrel, there are photo detectors called avalanche photo diodes (APD), made of silicon with a active area of 5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.
 At the endcap, the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$), allowing to operate in the magnetic field.

### 2019-11-15 project_ashish/paper.tex

@@
 %The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
-The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{ref:tH2019}, the limit is 26 times larger than the expected value.
+The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{ref:tH2019,ref:tHMultilep}, the limit is 26 times larger than the expected value.
 In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, this result almost rules out this model.
@@
 \section{SPECIFIC OBJECTIVES}
-- details
 
-Some of the objectives in this project include:
+The measurement of the tH production mechanism is a collaborative effort in the LHC experiment due to the various channels that need to be combined.
+This project focuses on the channels with leptons in the final state: two-lepton ($\ell\ell$)or three-lepton ($\ell\ell\ell$).
+The $\ell\ell$ sub-channel uses events with same sign dimuon ($\mu^\pm\mu^\pm$) or electron-muon ($e^\pm\mu^\pm$).
+The $\ell\ell\ell$ sub-channel uses events in the topologies: $\mu\mu\mu$, $\mu\mu e$, $\mu e e$ and $e e e$ , where no charge requirements are made.
+The leptons are generated from the decays of the $W$ and $Z$ bosons or $\tau$ leptons from decays of the Higgs or top quarks.
+Furthermore, light-quark and b-quark jets are generated from the initial state collision and from the decay of the top quark, these must be used in the signal identification.
+
+In order to complete a journal publication of a  measurement of tH production using one of these channels, several aspects  must be worked on:
 \begin{itemize}
-\item We will study the distribution of events in one of the decay channels and the  sensitivity that we get with the current data.
-\item study one or more decay channels.
-\item verify that simulation of signal events is adequate.
-\item study the extraction of signal strength through adjustments to the data.
-\item study the impact of statistical and systematic uncertainties.
+\item Simulation of the signal events using Monte Carlo generators which implement the theoretical model.
+\item Implementation of event reconstruction and selection algorithms which select high quality signal events and reduce the background events to a minimum.
+\item Studies of lepton and jet identification algorithms which improve the background rejection.
+\item For this search, due to the small signal over background ratio, a multi-variate algorith is employed which combines different event variables and exploits the correlations to construct a final discrimiant.
+This algorithm must be trained using simulated signal and background events.
+\item A model for the observed data must be constructed from the known background processes.
+These processes are normally simulated individually and then summed together with the signal to construct the final statistical model.
+\item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
+\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal and in the abscence as a limit.
+Further analysis is required to place constraints on paramater space of BSM models.
 \end{itemize}
+
+In addition to the above objectives, members of the experimental collaboration are expected to participate in the detector operation and upgrade activities (or service work).
+During shut-down periods, these activities include testing and installation of new detectors.
+During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
+Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities and meet a minimum requirement per year.
 

### 2019-11-15 project_ashish/paper.tex
method

@@
 \def\ProjectTitle{Study of the Higgs boson production in association with a single top quark in proton collisions at the Large Hadron Collider}
+\def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
 
@@
             RESEARCH LINE: \par
-            Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas \par}
+            \ResearchLine \par}
         \end{adjustwidth}
@@
 During regular data-taking periods, activities include monitoring the data acquisition systems and data quality through comparisons of new data and old data.
-Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities and meet a minimum requirement per year.
+In addition to the data analysis plans described before, another objective is to contribute in one of the developments of the CMS detector to  prepare for the HL-LHC phase.
+%
+
+Finally, the results of this project will be presented at national or international conferences and a publication in a scientific journal will be accomplished.
 
 \section{METHODOLOGY}
-- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis
+%- methods used in the search: which dataset,  lepton reconstruction, selections, jets, BDT, backgrounds, statistical analysis
 
-Aspects of simulation of signal production are studied based on generators that simulate the 
-interactions of quarks and gluons taking into account the probability distributions of each 
-type of particle. These are packages of software that are controlled with configuration files 
-that define various aspects of such as decay channels, energy in the center of mass and 
-refinements in the development of the jets that are generated by the strong interaction of 
-the quarks. The reconstruction and selection of tH events requires the use of central 
-software of the CMS collaboration. This software contains the algorithms that reconstruct the 
-charged and neutral particles starting from the energy deposits in the different parts of the 
-detector. These particles include leptons, photons and hadrons which have a life time that 
-allows them to leave the interaction region. These particles are used to identify the 
-production of the top and the Higgs boson. In the case of the top quark, it usually decays to 
-a bottom (b) quark and a W boson. Subsequently the W decays to two leptons or two quarks. 
-Reconstruction requires finding a type b and two jet leptons. Improvements in this 
-reconstruction can be done by studying the distributions of transverse momentum, the angular 
-distributions of the different particles, and others properties.
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=0.6\columnwidth]{./topology.png}
+	\caption{Topology of a tH signal event in a proton-proton collision.
+The decay products from the top quark include a b-jet and a W boson decaying to a lepton and neutrino.
+In this diagram the Higgs decays to a pair of W bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically.
+In addition there is a forward jet from initial collision of the quarks.}
+	\label{figureTopology}
+\end{figure}
+
+The methods for a measurement of the coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.
+
+Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
+However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years of analysis.
+Calibration and maintenance of all parts of the detector is necessary in order to achieve close to 100\% particle detection efficiency and noise levels to a minimum.
+This work is acchieved by participating in the detetector operation groups and performing data acquisition shifts during run time.  
+Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities.
+
+The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{ref:madgraph} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
+Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
+A separate simulation of the detector is employed using \textsc{GEANT}~\cite{ref:geant} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
+The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.
+
+The event reconstruction is designed to capture the distinguishing features of the signal topology.
+In the channels which are the focus of this project we require that there be at least two leptons of electron or muon type, however also jets need to be identified as shown in the figure.
+The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
+Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{ref:cmssw} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
+A new data structure at this level defines new datasets stored in computing centers around the world which are available to students and scientists at all research institutions.
+
+The \textsc{CMSSW} datasets are processed using computing clusters which use parallel computing systems such as \textsc{Condor} which allows hundreds of jobs to be run at the same time by individual users and save the output in \textsc{ROOT} format which allows visualization and further optimization of the event selection.
+In this level of reconstruction, the particle lists are used to filter out  events and construct composite particles  and new event variables.
 

### 2019-11-16 project_ashish/paper.tex
Update paper.tex

@@
 	\centering
-	\includegraphics[scale=0.4]{./cd11.png}
+	\includegraphics[width= 0.5 \columnwidth]{./sm.png}
 	\caption{Elementary particles in standard model of particle physics with their mass, spin and charge.}
@@
 
-The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{ref:madgraph} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
+The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{alwall2014automated} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
 Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
-A separate simulation of the detector is employed using \textsc{GEANT}~\cite{ref:geant} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
+A separate simulation of the detector is employed using \textsc{GEANT}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
 The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.

### 2019-11-16 project_ashish/paper.tex
Update paper.tex

@@
 %The most sensitive channel is  with leptons, however this channel is a combination of two sub-channels: two-lepton and three-lepton.
-The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{ref:tH2019,ref:tHMultilep}, the limit is 26 times larger than the expected value.
+The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
 In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, this result almost rules out this model.

### 2019-11-16 project_ashish/paper.tex
Update paper.tex

@@
 The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
-Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{ref:cmssw} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
+Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{Bayatian:2006nff} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
 A new data structure at this level defines new datasets stored in computing centers around the world which are available to students and scientists at all research institutions.

### 2019-11-18 project_ashish/paper.tex
Update paper.tex
method, results, calendar

@@
 \def\ResearchLine{Astrof\'{i}sica, Cosmolog\'{i}a y F\'{i}sica de Part\'{i}culas}
+
+\newcommand{\SubItem}[1]{
+    {\setlength\itemindent{15pt} \item[-] #1}
+}
 
@@
 It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign or with three leptons of electron or muon type.
-Leptons of tau type are not considered due to complications in their identificaiton in the detector.
+Leptons of tau type are not considered due to complications in their identification in the detector.
 %The impact of uncertainties will be studied and projections will be  made to the future phases of the LHC.
@@
 
+\afterpage{
 \begin{figure}[ht]
 	\centering
-	\includegraphics[width=0.6\columnwidth]{./topology.png}
+	\includegraphics[width=0.5\columnwidth]{./topology.png}
 	\caption{Topology of a tH signal event in a proton-proton collision.
@@
 \end{figure}
+\clearpage
+}
 
@@
 Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
-A separate simulation of the detector is employed using \textsc{GEANT}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
+A separate simulation of the detector is employed using \textsc{Geant}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
 The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.
@@
 Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{Bayatian:2006nff} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
-A new data structure at this level defines new datasets stored in computing centers around the world which are available to students and scientists at all research institutions.
 
-The \textsc{CMSSW} datasets are processed using computing clusters which use parallel computing systems such as \textsc{Condor} which allows hundreds of jobs to be run at the same time by individual users and save the output in \textsc{ROOT} format which allows visualization and further optimization of the event selection.
-In this level of reconstruction, the particle lists are used to filter out  events and construct composite particles  and new event variables.
+The Tracker subdetector of CMS shown in Figure~\ref{figure5} is composed of silicon sensors which detect minimum ionizing charged particles coming from the interaction region.
+The Tracker onsists of an inner Pixel detector with layers of pixel sensors and an outer Strip detector.
+The Pixel system consists of 66 Million pixels while the Strip system of 9.6 Million strip sensors.
+The Tracker provides a precision measurement of the track curvature (momentum) and position at the interaction region.
+
+Electrons are reconstructed from clusters of energy in the Electromagnetic calorimeter (ECAL)  .
+The ECAL is made of rectangular transparent crystals which cause a shower of secondary photons and electrons.
+The energy deposited in the crystal is read out and determines the energy of the primary electron.
+The cluster must match to a track in the Tracker subdetector.
+Photons are similar to electrons, but a track must not be matched in this case.
+
+Muons are identified by tracks which exit the inner subdetectors and cross the solenoid into the Muon chambers.
+Drift Tubes (DT's) in the barrel region or Cathode Strip Chambers (CSC's) in the forward region use ionizing gas to detect the passage of muon tracks.
+The track in the Muon chambers is matched to the track in the Tracker to provide a measurement of the muon momentum.
+
+Jets are reconstructed from energetic clusters found in both the ECAL and the Hadronic calorimeter (HCAL).
+Pions, kaons, and other hadrons create showers of secondary particles in the dense metal plates of the HCAL, the ionization energy of secondary particles is read out with scintillating plastics interleaved with the metal plates.
+Jets originate at the interaction region from collisions of quarks and gluons which create showers of mesons and baryons (mainly pions).
+Jets which originate from b quarks are important in this study because they identify the decay of a top quark, b-jets are identified with a multivariate algorithm which searches for secondary vertices in the Tracker and electrons or muons (from decays of B-mesons) within the cone of the jet.
+
+A new data structure with the above particle reconstruction defines new  datasets (\textsc{CMSSW}) stored in computing centers around the world which are available to students and scientists at all research institutions.
+These  datasets are processed using computing clusters which use high-performance computing systems, normally using \textsc{Condor}~\cite{ref:condor} to link the processing nodes, which allows hundreds of jobs to be run at the same time by individual users and save the output in \textsc{Root} format \cite{ref:root}.
+In this processing, the particle lists are used to require certain event selections and filter out uninteresting events.
+
+In the search for tH events using the dimuon channel the following event selections are applied:
+\begin{itemize}
+\item exactly two muons with the same sign,
+\item leading muon with at least 25 GeV,
+\item sub-leading muon with at least 15 GeV,
+\item at least one b-tagged jet,
+  \item and at least one non-b-tagged jet.
+\end{itemize}
+
+\textsc{Root} is a \textsc{c++} based software that allows visualization of event distributions and variable correlations.
+Further optimization of the event selections is performed by considering the different processes which contribute to the background.
+In this search several SM processes contribute to the background due to their decays to leptons: $pp\rightarrow ZZ, WZ, WW, ZZZZ, t\bar{t}W, t\bar{t}Z, t\bar{t}H, tWZ, tZq,$ and $t\bar{t}t\bar{t}$.
+These backgrounds must be determined from MC simulation and normalized to their predicted SM crossections.
+
+Due to the small signal over noise ratio in this search, a multivariate algorithm is trained to help separate signal events from background events.
+A typical algorithm used is the Boosted Decision Tree~\cite{ref:tmva}, which takes as input several event variables related to the signal topology.
+In the previous search for tH these variables included:
+\begin{itemize}
+\item rapidity of the most forward jet,
+\item momentum of the sub-leading lepton,
+\item number of central jets,
+\item number of forward jets,
+\item and other angular variables between the jets and leptons.
+\end{itemize}
+The multivariate algorithm takes into account the correlations between the variables and combines the information into a single discriminant.
+
+Due to the maximum separation of the signal and background in the multivariate discriminant, this distribution is used for the statisical analysis of the events.
+A fit is applied using the \textsc{RooFit} software package~\cite{ref:roofit} which constructs a model for the data consisting of the sum of the backgrounds and the signal simulations.
+A likelihood function is constructed from a Poison function using the expected and measured number of events.
+Systematic uncertainties are incorporated as nuissance parameters using gaussian probability functions, these account for uncertaintes in the normalization and shapes of the background.
+The signal strength extracted from this fit determines if there is any evidence for a signal.
+In the absence of a signal an upper limit is placed on the signal strength using the likelihood function and subsequently translated into a limit in the tH production cross-section and the Higgs coupling parameters.
 
 \section{EXPECTED RESULTS}
-- a limit, also predictions for future runs
+%- a limit, also predictions for future runs
 
-The expected results of this project are the following:
-- Improve data adjustments and study the effects of uncertainties.
-- Improve the sensitivity to the tH signal in the data of the second CMS run.
-- Limit calculations in the effective section incorporating data from the second run of the LHC.
-- Calculate projections of signal sensitivity for the different phases of the LHC.
-
-\section{SKILLS THAT WILL BE DEVELOPED}
-The following are skills that will be developed based on the work on this project:
-- understand particle physics from an experimental point of view.
-- analyze and manipulate data using modern programming languages such as C++, Python and ROOT.
-- data analysis techniques.
-- use high performance computing.
+The results from this project include the following items:
+\begin{itemize}
+\item The student will become part of an international collaboration.
+\item A leading contribution in one of the search channels for the tH process using the data from the Run II of the LHC, resulting in a publication in a scientific journal.
+\item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
+\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics.
+\item A presentation of a poster or a talk in an international physics conference.
+\item An academic stay at a scientific center like CERN or Fermilab.
+\item A high quality thesis.
+\end{itemize}
 
@@
 
+\begin{itemize}
+\item {\bf Semester 1 (2019-2)}:
+  \SubItem{ Readings on Standard Model theory}
+  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
+  \SubItem{ Initial planning of the analysis strategy}
+\item {\bf Semester 2 (2020-1)}:
+  \SubItem{ Course I on particle physics and/or particle detection}
+  \SubItem{ Basic Linux computing skills (\textsc{Bash, Emacs, Root})}
+  \SubItem{ Readings on SM and tH literature}
+  \SubItem{ Computing accounts at CERN and Fermilab}
+  \SubItem{ Studies of the tH event selections}
+  \SubItem{ CMS service work for authorship}
+  \SubItem{ Possible summer stay at CERN or Fermilab}
+\item {\bf Semester 3 (2020-2)}:
+  \SubItem{ Course II on particle physics and/or particle detection.}
+  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Development of a Multivariate algorithm for the event selections}
+  \SubItem{ Studies of the background processes}
+  \SubItem{ CMS service work for authorship}
+\item {\bf Semester 4 (2021-1)}:
+  \SubItem{ CMS service work for authorship}
+  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Development of a Multivariate algorithm for the event selections}
+  \SubItem{ Studies of the tH background processes}
+  \SubItem{ Development of the statistical model and signal extraction}
+  \SubItem{ Possible summer stay at CERN or Fermilab}
+\item {\bf Semester 5 (2021-2)}:
+  \SubItem{ Studies of the tH event selections}
+  \SubItem{ Development of a Multivariate algorithm for the event selections}
+  \SubItem{ Studies of the tH background processes}
+  \SubItem{ Development of the statistical model and signal extraction}
+  \SubItem{ Presentation of poster or talk at national or international conference}
+\item {\bf Semester 6 (2022-1)}:
+  \SubItem{ Development of software for the statistical analysis and interpretation of the results}
+  \SubItem{ Review process of the results within the CMS collaboration}
+  \SubItem{ Presentation of poster or talk at national or international conference}
+  \SubItem{ Writing of the paper publication}
+  \SubItem{ Writing of the thesis}
+\end{itemize}
+
+\cleardoublepage
 \bibliographystyle{unsrt}
-\cleardoublepage
 \bibliography{paper}

### 2019-11-19 tesis_hiram/Abstract/abstract.tex
new

@@
+\thispagestyle{empty}
+\vspace*{2.2cm}
+\begin{center}
+	\Large \textbf{Abstract}
+\end{center} 
+\vspace{1.5cm}
+
 % ************************** Thesis Abstract *****************************
 % Use `abstract' as an option in the document class to print only the titlepage and the abstract.
-\begin{abstract}
+\begin{center}
+	\justifying
 I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
@@
 The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter, for comparison with the Standard Model.
-\end{abstract}
+\end{center}

### 2019-11-19 tesis_hiram/Abstract/resumen.tex
new

@@
 \vspace{1.5cm}
-\selectlanguage{spanish}
-	\begin{poliabstract}
+
+%\renewcommand{\absnamepos}{empty} % originally center
+\begin{center}
+	\justifying
 Presento un estudio sobre la producci\'on de un boson de Higgs y un top quark ($tH$) en un canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
@@
 La sensibilidad esperada es calculada usando un grupo de datos tipo Asimov para 35.9 fb$^{-1}$ para colisiones de prot\'on-prot\'on y esos datos son extrapolados a niveles altos de luminosidad, de acuerdo a la fase de alta luminosidad en el LHC.
-La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con un acoplamiento invertido de Yukawa $k_t$=-1, donde $k_t$ es el par\'ametro de acoplamiento de top-Higgs, para compararlo con el modelo est\'andar.
-\end{poliabstract}
+La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con un acoplamiento invertido de Yukawa $k_t$=-1, donde $k_t$ es el par\'ametro de acoplamiento de top-Higgs, para compararlo con el Modelo Est\'andar.
+\end{center}

### 2019-11-19 tesis_hiram/Chapter1/chapter1.tex
new

@@
 \renewcommand{\baselinestretch}{1.5}
-\nocite{*}
+
 \begin{chapter}{Introduction}
@@
 Since quarks and gluons only exist in bound states, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
-bound state\cite{gross.griff}.
+bound state \cite{gross}.
 \\
@@
 \begin{table}[!htbp]
-\caption{Table of particles in SM, where it shows the masses, charges,spin, lifetime and distance traveled in a lifetime .
+\caption[Table of particles in SM]{Table of particles in SM, where it shows the masses, charges,spin, lifetime and distance traveled in a lifetime .
 Stable means no decay, or lifetime almost infinite\cite{pd}.

### 2019-11-19 tesis_hiram/Chapter2/chapter2.tex
new

@@
 \centering
-	\caption{Accelerator operation energies\cite{cern3,cern1}}
+	\caption[Accelerator operation energies]{Accelerator operation energies\cite{cern3,cern1}}
 	\begin{tabular}{|c|c|}

### 2019-11-19 tesis_hiram/Chapter4/chapter4.tex
tesis-arreglo1
new

@@
 The uncertainty of the signal strength is estimated by applying a fit to the Asimov dataset, where the model
-	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and gaussian constraints for the systematical uncertainties in the model.
+	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and Gaussian constraints for the systematical uncertainties in the model.
 
@@
 	$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background.
-$\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.
+$\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.\\
+
 	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
-The minimization is performed by using the package ROOFIT \cite{roofit}.
+The minimization is performed by using programming language ROOT.
+ROOT is a scientific software toolkit, based on the C++ language, which main objective is the handling of data processing, statistical analysis, including visualization and storage.
+The package ROOFIT is used here, because of its implementations of modeling probability distributions and statistical tools\cite{roofit}.
 In the figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models.
@@
 
-	However, the uncertainty of $\mu$ for the SM case is still very big, with a error of 170$\%$ in the 3000 fb$^{-1}$ case, indicating that it is necessary to increase the luminosity even higher to get better results to reduce the uncertainty on $\mu$ for a possible observation of the signal.
+	However, the uncertainty of $\mu$ for the SM case is 170$\%$ for  in the 3000 fb$^{-1}$ case, making impossible to get an evidence of a Higgs boson in the $tH$ process for the same sign muon channel.
+Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.\\
 	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results; upper limits in this models are small.
 This is caused by the fact that the number of events for the $tH$ signal is greater.
-For 3000 fb$^{-1}$ the uncertainty on $\mu$ is $~10\%$, this indicates that for large integrated luminosities this model can be fully ruled out.
+For 3000 fb$^{-1}$ the uncertainty on $\mu$ is $~10\%$, and it has an upper limit that rounds between 0.9-1.1.
+In the likelihood scan, the statistical test $q$ gets very high values at $\mu$>1.1.
+This indicates that for large integrated luminosities this model can be fully ruled out.
+This can be visualized in the likelihood scan of  3000 fb$^{-1}$, where the curve is very closed and values of $q$ are very high, giving incompatibility of the model with data.
 
@@
 			\hline
-			3000&1.0 $\pm$ 1.7 & 4.3 &	 1.0 $\pm$ 0.1 & 1.1\\
+			3000&1.0 $\pm$ 1.7 & 4.3 &	 1.0 $\pm$ 0.1 & 0.9-1.1\\
 			\hline

### 2019-11-19 tesis_hiram/Chapter5/chapter5.tex
new

@@
 Recently CMS published a search for $tH$ process using 35.9 fb$^{-1}$ from Run 2 in 2018.
-Using this information, it was studied the expected sensibility using an Asimov data and systematic uncertainties for final states of same sign pairs of muons \\
+Using this information, it was studied the expected sensibility using an Asimov data and systematic uncertainties for final states of same sign pairs of muons.
+\\
 
-In the SM case, the signal strength for the signal $tH$ is 2.2 that is very low in comparison to
-the backgrounds, resulting in large uncertainties. The uncertainty is around eight times than the signal strength. 
+In the SM case, the uncertainty for the $tH$ signal strength $\mu$ is around seven times than the value of $\mu$, resulting in large uncertainties. 
 For the inverted coupling scenario ($k_t$=-1), the uncertainty for the model after the fit was better than the
-SM case, this is due to the larger expected number of signal events. In this case 26.2 with an uncertainty of around 50$\%$.
+SM case, this is due to the larger expected number of signal events. In this case, it is obtained an uncertainty of around 50$\%$.
 \\
@@
 We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
-In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb$^{-1}$.\\
+In the case of the inverted coupling scenario, a possible evidence of the signal can be observed with an upper limit of $\mu$ between 0.9 and 1.1 at  3000 fb$^{-1}$.
+For  3000 fb$^{-1}$, the statistical test shows that the model of $k_t$=-1 can be rule out.
 

### 2019-11-19 presentacion-tesis.tex
new

--- 2019-11-14 presentacion_hiram/presentacion-tesis.tex
@@
 \usepackage{tikz} 
+\usepackage{pgfplots}
 \usetikzlibrary{patterns}
@@
 \item The $tH$ study explores the relative sign of top-Higgs  and W-Higgs couplings.\\ Small deviations from SM predictions could be associated with physics beyond the
-standard model (BSM) such as String Theory and  Supersymmetry.
+standard model (BSM) such as Supersymmetry.
 \end{itemize}
@@
 \begin{frame}
+\frametitle{Electroweak SM Lagrangian}
+	\begin{figure}[ht!]
+		\centering
+		\begin{tikzpicture}[scale=1.2]
+		\begin{axis}[
+		hide axis,
+		%axis lines=middle,
+		%      axis on top,
+		%      axis line style={blue,dashed,thick},
+		%      ymin=-2,ymax=2,
+		%      xmin=-2,xmax=2,
+		%      zmin=-2,zmax=2,
+		samples=30,
+		domain=0:360,
+		y domain=0:1.25,clip=false
+		]
+		\addplot3 [surf, shader=flat, draw=black, fill=white, z buffer=sort]
+		({sin(x)*y}, {cos(x)*y}, {(y^2-1)^2});
+		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:1,0,0)
+		node[below,font=\footnotesize]{$\Phi_{\text{IM}}$};
+		\draw[blue,thick,-stealth] (axis cs:1,0,0) -- (axis cs:1.3,0,0)
+		node[above,font=\footnotesize]{};
+		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,-1,0)
+		node[left=2mm,font=\footnotesize]{$\Phi_{\text{RE}}$};
+		\draw[blue,thick,-stealth] (axis cs:0,-1,0) -- (axis cs:0,-1.5,0)
+		node[right=1mm,font=\footnotesize]{};
+		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,0,1)
+		%node[left=2mm,font=\footnotesize]{$\phi_{\text{RE}}$}
+		;
+		\draw[blue,thick,-stealth] (axis cs:0,0,1) -- (axis cs:0,0,1.3)
+		node[right,font=\footnotesize]{$V(\Phi)$};
+		\end{axis}
+		\end{tikzpicture}
+		\caption*{\small Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu^2<0$ and $\lambda>0$, also called the mexican hat potential.}
+		\label{hat}
+	\end{figure}
+\end{frame}
+\begin{frame}
 \frametitle{SM Lagrangian}

### 2019-11-19 project_ashish/paper.tex
commit

@@
 \usepackage{afterpage}
-
+\usepackage{setspace}
 \usepackage{fancyhdr}
@@
 \newpage
-\hspace{0pt}
+\hspace{2pt}
 \vfill
@@
 
-  The abstract \par
+  \vspace{1 cm}
+
+ \onehalfspacing The research project propose to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state.
+The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $pb^{-1}$.
+Increasing the collider luminosity is expected to increase the number of event without changing the cross section for this Higgs boson production mode.
+The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations.
+Previous measurements using dataset with an integrated luminosity 36 $fb^{-1}$ has put an upper limit of 2.04 pb on the production cross section which is far from standard model predicted value of 0.077 pb.
+We plan to obtain more stringent upper limits on the production cross section and get constraints on the Higgs top quark coupling parameter $y_t$.
+\par
 
@@
 
-\hspace{0pt}
+\hspace{2pt}
 \vfill
@@
 
-The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
+\onehalfspacing The standard model (SM) of particle physics is so far the best theoretical model to describe the interaction of elementary 
 particles using three of the four fundamental forces of nature which are electromagnetic force, strong nuclear force and the 
@@
 generation of matter particles has top (t) quark, bottom (b) quark, tau and tau neutrino. The bosonic sector consist of gauge 
-bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong force, electromagnetic force and weak force respectively.
+bosons like gluon, photon, $W^{\pm}$, $Z^0$ which mediate strong nuclear force, electromagnetic force and weak nuclear force respectively.
 There is one more particle in the standard model called the Higgs Boson which gives mass to SM particles via electroweak symmetry breaking mechanism \cite{Chatrchyan:2012xdj}.
@@
 There are various production modes of Higgs boson like the gluon gluon fusion (ggF), vector boson fusion (VBF), Higgs 
-production in association with vector boson (VH, V = W or Z), Higgs production with top quark and top anti-quark (t$\bar{t}$H) and Higgs 
-production with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
-properties and the coupling strength of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is 
+production in association with vector boson (VH, V = $W^{\pm}$ or Z), Higgs production with top quark and top anti-quark ($t\bar{t}H$) and Higgs 
+production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
+various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is 
 gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
 and processes like ggF or Higgs boson decay to pair of photons are not possible at tree level and can only proceed via loop 
-diagrams which involve W boson or top quark in the loop. The Higgs boson can also decay to other particles and these decay 
-channels have different branching fractions. Higgs boson can decay to a pair of W bosons, Z bosons, photons, bottom quarks, 
-muons and electrons. Higgs boson can also decay to Z boson and a photon. The important SM Higgs Boson production modes are shown in Figure 2. It is also interesting to investigate some invisible 
-decay modes of Higgs boson which can be used to put upper bounds on dark matter-nucleon scattering cross section like in the 
-Higgs-portal dark matter models.
+diagrams which involve $W^{\pm}$ boson, top quark or bottom quark in the loop. The Higgs boson can also decay to other particles and these decay 
+channels have different branching ratios which are computed using the partial decay widths. Higgs boson can decay to a pair of $W^{\pm}$ bosons, Z bosons, photons, bottom quarks, 
+muons and electrons.
+Higgs boson can also decay to Z boson and a photon.
+The important SM Higgs Boson production modes are shown in Figure 2.
+The production cross section and branching ratios of various decay channels of Higgs boson are shown in Figure 3.
 
-\afterpage{
+%\afterpage{
 \begin{figure}[H]
@@
 }
-% \newpage
+ \newpage
 
 The Standard Model (SM) of particle physics has successfully described most of the experimental data till now but a very large 
-number of free-parameters like fine structure constant $\alpha$, Weinberg angle or weak mixing angle $\theta_W$, the coupling 
-constant of strong interaction, electroweak symmetry breaking energy scale, Higgs potential self coupling or the Higgs mass, 
-three mixing angles and the CP-violating phase of the CKM matrix which tells us how quarks of 
-different color charge mix with 
-each other, nine yukawa couplings which determine the mass of nine charged fermions and fine 
+number of free-parameters and the fine tuning related to these parameters suggest new physics beyond SM as mentioned below.
+\begin{itemize}
+\item{Fine structure constant $\alpha$},
+\item{Weinberg angle or the weak mixing angle $\theta_W$},
+\item{The coupling constant of strong interaction $\alpha_s$},
+\item{Electroweak symmetry breaking energy scale v},
+\item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
+\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different color charge mix with each other},
+\item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
+\end{itemize}
+ The fine 
 tunings related to the origin of 
-masses robustly suggests new physics beyond Standard model (BSM). There are lot of specific 
+masses and the free parameters in SM robustly suggests new physics beyond Standard model (BSM). There are lot of specific 
 BSM theories and most of these 
@@
 electroweak (EW) scale, the new parameters 
-of such theories may be constrained by the actual, low energy, experiments. This approach 
+of such theories may be constrained by the actual low energy experiments. This approach 
 requires studying each model 
-individually, and calculating every possible observable. There is another approach immitating 
+individually, and calculating every possible observable.
+
+There is another approach immitating 
 Fermi's treatment of beta decay 
@@
 operators to the SM Lagrangian. 
-They are built out of SM fields and supposed to be invariant under its gauge group. Those 
+They are built out of SM fields and supposed to be invariant under its gauge group which is $SU(3)_C \times SU(2)_L \times U(1)_Y$. Those 
 operators are the low-energy residue 
@@
 encoded in the size of the operator
-coefficients, which is to be set from experiments.
-
-The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
+coefficients, which is to be set from experiments. The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
 model predictions if these higher 
@@
 (D^{\mu} \phi)$ to calculate the 
-deviation of Higgs boson-fermion couplings from SM. The first operator shift the minimum of 
+deviation of Higgs boson-fermion couplings from SM. The first operator $-\frac{1}{3}(\phi^{\dagger}\phi)^3$ shift the minimum of 
 the Higgs potential. Also as there 
@@
 potential term, Higgs-fermion (quarks 
-and leptons) couplings are modified. In the effective standard model theory, there are 
-dimension 5 and dimension 6 
-operators. Dimension 5 operators are odd under baryon minus lepton number symmetry and 
-dimension 6 operator dominate baryon 
-minus lepton number symmetry conservation processes.
+and leptons) couplings will be modified. The yukawa coupling of top quark with Higgs boson will be modified due to the presence of such higher dimensional operators.
 
@@
 The production of Higgs boson in association with single top quark is one of the rare Higgs 
-boson production mode \cite{Khachatryan_2016}. As the top 
+boson production mode \cite{Khachatryan:2015ota}. As the top 
 quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
@@
 undergo hardronization and are seen as bundles of particles in detector called jets. The most 
-probable decay of top quark is 
+probable decay of the top quark is 
 into bottom (b) quark and W boson \cite{nishiwaki2014tth}. Using b-jet tagging algorithms, the jet originating from 
 b-quark can be reconstructed to 
-identity the top quark. In SM, the coupling of the Higgs boson to fermions like quarks and 
-leptons is proportional to the mass 
+identity the top quark. In SM, the couplings of the Higgs boson to fermions (quarks and leptons) known as Yukawa couplings are proportional to the mass 
 of the fermions. Thus heavy quarks like top, bottom and charm couple strongly to Higgs boson 
@@
 processes at LHC which will allow us to directly probe the Yukawa 
-coupling between Higgs Boson and top quark are Higgs boson production in association with top 
-quark pair (t$\bar{t}$H) via 
+coupling between Higgs boson and top quark are Higgs boson production in association with top 
+quark pair ($t\bar{t}H$) via 
 strong interaction and the production of single top quark with a Higgs boson (tH). As tH 
 occur via electroweak interaction, it 
-is more rare than t$\bar{t}$H production \cite{sirunyan2018search}. The Higgs boson in the tH channel can be radiated 
+is more rare than t$\bar{t}$H production \cite{Sirunyan:2018ygk}. The Higgs boson in the tH channel can be radiated 
 off by a W boson or by a top quark as shown in Figure 4.
@@
 the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
-boson \cite{choudhury2019search}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
+boson $g_{HWW}$ \cite{Sirunyan:2018lzm}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
 prediction or even if $y_t$ has a negative sign, both would cause a strong increase in the tH 
@@
 The anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential.
-As there is strong destructive inteference in the t-channel for the standard model  couplings, this production mode is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs  boson and top quark induced by  higher dimensional operators in effective SM theory \cite{sirunyan2019search}.
+As there is strong destructive inteference in the t-channel for the standard model  couplings, this production mode is sensitive to both the sign and the magnitude of any coupling beyond the SM between Higgs  boson and top quark induced by  higher dimensional operators in effective beyond SM theory \cite{sirunyan2019search}.
 
@@
 colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years.
-The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN.
+The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC).
 It is designed to detect particles known as muons very accurately.
 The CMS detector has the form of a cylindrical onion, with several concentric layers of components.
-Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum.
+Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure momentum.
 A silicon tracker, made of about 75
-million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
+million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
+The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
@@
 
-\afterpage{
-  \begin{figure}[ht]
+%\afterpage{
+  \begin{figure}[H]
     \centering
-    \includegraphics[width=0.7\columnwidth]{./cms12.png}
-    \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
+    \includegraphics[width=0.6\columnwidth]{./cms12.png}
+    \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers.}
     \label{figure5}
@@
 
-  \begin{figure}[ht]
+  \begin{figure}[H]
     \centering
@@
     \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instant brightness while the line shows brightness accumulated.}
+Points show instantaneous luminosity while the line shows luminosity accumulated.}
     \label{figure6}
@@
 
-\afterpage{
-  \begin{figure}[ht]
+%\clearpage
+}
+LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
+The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
+Figure~\ref{figureKappas} shows a summary of the current measurements of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and ${t\bar{t}H}$ production modes \cite{Tanabashi:2018oca}.
+Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
+Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt} \cite{Sirunyan:2018lzm}.
+Multilepton final states like ee, $\mu\mu$ and $e\mu$ and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
+The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
+\newpage
+%\afterpage{
+  \begin{figure}[H]
     \centering
-    \includegraphics[scale=0.4]{./cd7.png}
+    \includegraphics[scale=0.4]{./couplings.png}
     \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
@@
 
-  \begin{figure}[ht]
+  \begin{figure}[H]
     \centering
-    \includegraphics[width=0.5 \columnwidth]{./cms13.png}
-    \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
+    \includegraphics[width=0.4 \columnwidth]{./cms13.png}
+    \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the 2016 LHC data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
     \label{figureKt}
   \end{figure}
-\clearpage
-}
-
-LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
-The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  placein parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
-This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
-
-Figure~\ref{figureKappas} shows a summary of the current measurments of the Higgs coupling parameters with the LHC Run 1 dataset (2011,2012)  using ggF, VBF, VH, and $tt$H production modes.
-
-Higgs boson production in association with single top quark has been studied to derive constraints on the magnitude and relative sign of Higgs boson couplings to top quarks and vector bosons.
-Constaints on $\kappa_t$ can be derived using a likelihood ratio scan of $L(\kappa_t)/L(\hat{\kappa_t})$ where $\hat{\kappa_t}$ is the best fit value of $\kappa_t$ as shown in Figure~\ref{figureKt}.
-Multilepton final state and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
-The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges of about [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
 
@@
 
-In this project, it is proposed to search for the production of Higgs boson associated with a single top quark in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
-It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign or with three leptons of electron or muon type.
+\onehalfspacing In this project, it is proposed to search for the production of Higgs boson associated with a single top quark in the CMS detector based at the Large Hadron Collider of the CERN laboratory.
+It is proposed to study the sensitivity with the current data in the channel where the events are identified with two muons of the same sign, electron muon or with three leptons of electron or muon type.
 Leptons of tau type are not considered due to complications in their identification in the detector.
@@
 
-There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another  $27\%$ includes what we call Dark Matter.
-Understanding the production of the Higgs boson, as well as its decays like the invisible decay modes are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
-Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.
+\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark Matter and the rest $68\%$ is dark energy.
+Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
+Through this project we will investigate the production of the Higgs boson in association with a single top quark (tH) in proton-proton collisions with the CMS experiment at the LHC.
 The tH  production process has not been observed so far.
-The measurement  of this process complements other measurements of the yukawa coupling parameter of the top  quark and Higgs boson and is a part of the physics program of CMS  and ATLAS international collaborations.
-Through these measurements we seek to complete the measurements of the Standard Model parameters to high precision or to find evidence of deviations which point to new particles which may explain current enigmas like the origin of Dark Matter.
+The measurement of this process complements other measurements of the yukawa coupling parameter $y_t$ of the top quark and Higgs boson and is a part of the physics program of CMS and ATLAS international collaborations.
+Through these measurements we seek to complete the measurements of the Standard Model parameters to high precision and also to find evidence of deviations in yukawa couplings which point to new particles which may explain current enigmas like the origin of Dark Matter.
 
@@
 
-Studies in the tH channel have already started with the collaborations CMS and ATLAS with publications based on data from the 2011-2012 run and some data from the second run of 2015-2016.
-In these results it was not found evidence of signal and upper limits have been set on the production cross-section.
+\onehalfspacing Studies about the tH Higgs boson production channel have already started within the CMS and ATLAS collaboration and publications are based on data from the 2011-2012 run and some data from the second run of 2015-2016.
+In these results, there was no evidence of signal and upper limits were set on the production cross-section.
 The current results combine three types of searches: H$\rightarrow WW/ZZ/\tau\tau \rightarrow$leptons, H$\rightarrow\gamma\gamma$, and H$\rightarrow b\bar{b}$.
@@
 The currently published result uses 36 fb$^{-1}$ of collision data and obtains an upper limit of 2.04 pb while only 0.077 pb are expected in the SM \cite{sirunyan2019search}, the limit is 26 times larger than the expected value.
-In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, this result almost rules out this model.
+In BSM models, for example with $\kappa_t = -1$,  the expected cross-section increases up to 0.834 pb due to quantum interference effects; in this case also the observed upper limit changes to 0.86 pb at 95$\%$ confidence level, the current data almost rules out this model.
 
@@
 A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
-These means the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be almost fully excluded.
+This mean that the limit for the SM case will improve to about 13 times the expected cross-section, while for the modified model ($\kappa_t = -1$) we expect to be excluded.
 
@@
 
-In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}$H production because the cross-section of $t\bar{t}$H is much larger than that of tH and some events pass the selections designed for tH.
-The fraction of tH events over tH + $t\bar{t}$H is currently only 5$\%$ with the analysis techniques used.
+In this search the reconstruction methods do not allow to separate $t$H from $t\bar{t}H$ production because the cross-section of $t\bar{t}H$ is much larger than that of tH and some events pass the selections designed for tH.
+The fraction of tH events over tH + $t\bar{t}H$ is currently only 5$\%$ with the analysis techniques used.
 We expect to improve the analysis techniques using multi-variate techniques, for example boosted decision trees or other algorithms, to improve the identification of signal events over the rest of the backgrounds.
@@
 
+%\newpage
 \section{SPECIFIC OBJECTIVES}
 
-The measurement of the tH production mechanism is a collaborative effort in the LHC experiment due to the various channels that need to be combined.
-This project focuses on the channels with leptons in the final state: two-lepton ($\ell\ell$)or three-lepton ($\ell\ell\ell$).
+\onehalfspacing The measurement of the tH production mechanism is a collaborative effort in the LHC experiment due to the various channels that need to be combined.
+This project focuses on the channels with leptons in the final state: two-lepton ($\ell\ell$) or three-lepton ($\ell\ell\ell$).
 The $\ell\ell$ sub-channel uses events with same sign dimuon ($\mu^\pm\mu^\pm$) or electron-muon ($e^\pm\mu^\pm$).
-The $\ell\ell\ell$ sub-channel uses events in the topologies: $\mu\mu\mu$, $\mu\mu e$, $\mu e e$ and $e e e$ , where no charge requirements are made.
+The $\ell\ell\ell$ sub-channel uses events in the topologies: $\mu\mu\mu$, $\mu\mu e$, $\mu e e$ and $e e e$, where no charge requirements are made.
 The leptons are generated from the decays of the $W$ and $Z$ bosons or $\tau$ leptons from decays of the Higgs or top quarks.
@@
 \item Studies of lepton and jet identification algorithms which improve the background rejection.
-\item For this search, due to the small signal over background ratio, a multi-variate algorith is employed which combines different event variables and exploits the correlations to construct a final discrimiant.
+\item For this search, due to the small signal over background ratio, a multi-variate algorithm is employed which combines different event variables and exploits the correlations to construct a final discriminant.
 This algorithm must be trained using simulated signal and background events.
@@
 \item An algorithm is developed that adjusts the model to the observed data distribution and incorporates several systematic uncertainties due to differences between simulation and real data.
-\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal and in the abscence as a limit.
+\item The signal strength observed from the statistical analysis must be interpreted as evidence of a signal or in the absence as a limit.
 Further analysis is required to place constraints on paramater space of BSM models.
@@
 
-In addition to the above objectives, members of the experimental collaboration are expected to participate in the detector operation and upgrade activities (or service work).
+In addition to the above objectives, members of the CMS collaboration are expected to participate in the detector operation and upgrade activities (or service work).
 During shut-down periods, these activities include testing and installation of new detectors.
@@
 
-\afterpage{
-\begin{figure}[ht]
+%\afterpage{
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.5\columnwidth]{./topology.png}
+%	\caption{Topology of a tH signal event in a proton-proton collision.
+The decay products from the top quark include a b-jet and a W boson decaying to a lepton and neutrino.
+In this diagram the Higgs decays to a pair of W bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically.
+In addition there is a forward jet from initial collision of the quarks.}
+%	\label{figureTopology}
+%\end{figure}
+%\clearpage
+}
+
+\onehalfspacing The methods for a measurement of the coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.
+
+Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
+However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years to do analysis.
+Calibration and maintenance of all parts of the detector is necessary in order to achieve close to $100\%$ particle detection efficiency and noise levels to a minimum.
+This work is achieved by participating in the detector operation groups and performing data acquisition shifts during run time.
+Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities.
+
+The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{alwall2014automated} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
+
+\begin{figure}[H]
 	\centering
@@
 \end{figure}
-\clearpage
-}
-
-The methods for a measurement of the coupling of the Higgs boson and the top quark in proton collisions are extensive and require several stages.
-
-Accelerating the protons to extremely high energies and causing them to collide at high rates in order to produce rare but interesting events is the work of a separate accelerator group.
-However, the members of the CMS collaboration must monitor the quality and rate of proton collisions at the interaction point at the center of the detector in order to collect a high quality dataset which can be stored for many years of analysis.
-Calibration and maintenance of all parts of the detector is necessary in order to achieve close to 100\% particle detection efficiency and noise levels to a minimum.
-This work is acchieved by participating in the detetector operation groups and performing data acquisition shifts during run time.  
-Presence at CERN or at a remote control center like Fermilab is required in order to perform these activities.
-
-The reconstruction and selection of signal events is studied using the \textsc{MadGraph}~\cite{alwall2014automated} Monte Carlo generator which implements the theoretical model and predict the amount and distribution of events for a given LHC dataset.
 Figure~\ref{figureTopology} shows the main features of the topology of a tH event, including the subsequent decay products of the top quark and Higgs boson, these are the particles which are generated at the interaction point before entering the detector components.
-A separate simulation of the detector is employed using \textsc{Geant}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles and the response and efficiency of each sensor in the CMS detector.
+A separate simulation of the detector is employed using \textsc{Geant}~\cite{agostinelli2003geant4} which simulates the trajectory of the stable particles, response and efficiency of each sensor in the CMS detector.
 The information obtained from this chain is saved as raw data similar to the one obtained from the real experiment and is later reconstructed in the same way.
@@
 The event reconstruction is designed to capture the distinguishing features of the signal topology.
-In the channels which are the focus of this project we require that there be at least two leptons of electron or muon type, however also jets need to be identified as shown in the figure.
+In the channels which are the focus of this project, we require that there exist at least two leptons of electron or muon type, however also jets need to be identified as shown in the Figure 9.
 The event reconstruction begins with the identification of the different types of particles: photon, electrons, muons, taus, and jets.
-Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{Bayatian:2006nff} which is maintained by the collaboration and which includes basic calibration of the particle energy and momenta.
+Particle lists are formed for each kind using a general purpose event reconstruction software called \textsc{CMSSW}~\cite{Bayatian:922757} which is maintained by the collaboration and which includes basic calibration of the various particle energy and momenta.
 
 The Tracker subdetector of CMS shown in Figure~\ref{figure5} is composed of silicon sensors which detect minimum ionizing charged particles coming from the interaction region.
-The Tracker onsists of an inner Pixel detector with layers of pixel sensors and an outer Strip detector.
-The Pixel system consists of 66 Million pixels while the Strip system of 9.6 Million strip sensors.
+The Tracker consists of an inner Pixel detector with layers of pixel sensors and an outer Strip detector.
+The Pixel system consists of 66 Million pixels while the Strip system comprises of 9.6 Million strip sensors.
 The Tracker provides a precision measurement of the track curvature (momentum) and position at the interaction region.
 
-Electrons are reconstructed from clusters of energy in the Electromagnetic calorimeter (ECAL)  .
+Electrons are reconstructed from clusters of energy in the Electromagnetic calorimeter (ECAL).
 The ECAL is made of rectangular transparent crystals which cause a shower of secondary photons and electrons.
@@
 A new data structure with the above particle reconstruction defines new  datasets (\textsc{CMSSW}) stored in computing centers around the world which are available to students and scientists at all research institutions.
-These  datasets are processed using computing clusters which use high-performance computing systems, normally using \textsc{Condor}~\cite{ref:condor} to link the processing nodes, which allows hundreds of jobs to be run at the same time by individual users and save the output in \textsc{Root} format \cite{ref:root}.
+These  datasets are processed using computing clusters which use high-performance computing systems, normally using HTCondor~\cite{HTCondor} to link the processing nodes, which allows hundreds of jobs to run at the same time by individual users and save the output in \textsc{Root} format \cite{brun2003root}.
 In this processing, the particle lists are used to require certain event selections and filter out uninteresting events.
@@
 In this search several SM processes contribute to the background due to their decays to leptons: $pp\rightarrow ZZ, WZ, WW, ZZZZ, t\bar{t}W, t\bar{t}Z, t\bar{t}H, tWZ, tZq,$ and $t\bar{t}t\bar{t}$.
-These backgrounds must be determined from MC simulation and normalized to their predicted SM crossections.
+These backgrounds must be determined from MC simulation and normalized to their predicted SM cross sections.
 
 Due to the small signal over noise ratio in this search, a multivariate algorithm is trained to help separate signal events from background events.
-A typical algorithm used is the Boosted Decision Tree~\cite{ref:tmva}, which takes as input several event variables related to the signal topology.
+A typical algorithm used is the Boosted Decision Tree~\cite{hoecker2007tmva}, which takes as input several event variables related to the signal topology.
 In the previous search for tH these variables included:
@@
 Due to the maximum separation of the signal and background in the multivariate discriminant, this distribution is used for the statisical analysis of the events.
-A fit is applied using the \textsc{RooFit} software package~\cite{ref:roofit} which constructs a model for the data consisting of the sum of the backgrounds and the signal simulations.
-A likelihood function is constructed from a Poison function using the expected and measured number of events.
-Systematic uncertainties are incorporated as nuissance parameters using gaussian probability functions, these account for uncertaintes in the normalization and shapes of the background.
+A fit is applied using the \textsc{RooFit} software package~\cite{verkerke2008roofit} which constructs a model for the data consisting of the sum of the backgrounds and the signal simulations.
+A likelihood function is constructed from a Poisson function using the expected and measured number of events.
+Systematic uncertainties are incorporated as nuisance parameters using gaussian probability functions, these account for uncertaintes in the normalization and shapes of the background.
 The signal strength extracted from this fit determines if there is any evidence for a signal.
-In the absence of a signal an upper limit is placed on the signal strength using the likelihood function and subsequently translated into a limit in the tH production cross-section and the Higgs coupling parameters.
+In the absence of a signal an upper limit is placed on the signal strength using the likelihood function and subsequently translated into a limit in the tH production cross section and the Higgs coupling parameters.
 
@@
 
-The results from this project include the following items:
+\onehalfspacing The results from this project include the following items:
 \begin{itemize}
@@
 \item Participation in the CMS detector Phase II upgrade through development and possible installation of particle detectors possibly resulting in a technical report.
-\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics.
-\item A presentation of a poster or a talk in an international physics conference.
+\item A presentation of a poster or a talk in one of the national conferences of the Division of Paticles and Fields of the Mexican Society of Physics or a presentation of a poster or a talk in an international physics conference.
 \item An academic stay at a scientific center like CERN or Fermilab.
@@
 \section{CALENDAR OF ACTIVITIES}
-
+\onehalfspacing
 \begin{itemize}
@@
 \cleardoublepage
+\onehalfspacing
 \bibliographystyle{unsrt}

### 2019-11-20 project_ashish/paper.tex
commit

@@
 \clearpage
-}
+
  \newpage
@@
   \clearpage
-}
 
 %\clearpage
-}
+
 LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
@@
 %\clearpage
-}
 

### 2019-11-20 tesis_hiram/Abstract/abstract.tex
fix bugs

@@
 % Use `abstract' as an option in the document class to print only the titlepage and the abstract.
-\begin{center}
-	\justifying
+%\begin{center}
+%	\justifying
 I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
 process I explore a Higgs production mechanism which has not yet been observed
-experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the LHC high luminosity phase.
-The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter, for comparison with the Standard Model.
-\end{center}
+experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the  high luminosity phase of the LHC (HL-LHC).
+The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
+%\end{center}

### 2019-11-20 tesis_hiram/Abstract/resumen.tex
fix bugs

@@
 %\renewcommand{\absnamepos}{empty} % originally center
-\begin{center}
-	\justifying
-Presento un estudio sobre la producci\'on de un boson de Higgs y un top quark ($tH$) en un canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
-Estudiando este proceso, se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
-La sensibilidad esperada es calculada usando un grupo de datos tipo Asimov para 35.9 fb$^{-1}$ para colisiones de prot\'on-prot\'on y esos datos son extrapolados a niveles altos de luminosidad, de acuerdo a la fase de alta luminosidad en el LHC.
-La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con un acoplamiento invertido de Yukawa $k_t$=-1, donde $k_t$ es el par\'ametro de acoplamiento de top-Higgs, para compararlo con el Modelo Est\'andar.
-\end{center}
+%\begin{center}
+%	\justifying
+Presento un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
+Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.
+La sensibilidad esperada es calculada usando  datos de tipo Asimov para 35.9 fb$^{-1}$ de colisiones de prot\'on-prot\'on y es extrapolada la fase de alta luminosidad del LHC (HL-LHC).
+La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar.
+%\end{center}

### 2019-11-21 project_ashish/paper.tex
commit

@@
 \usepackage{float}
+\usepackage{hyperref}
+\usepackage{url}
 \usepackage{afterpage}
+\usepackage{natbib}
 \usepackage{setspace}
@@
 \onehalfspacing The research project propose to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state.
-The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $pb^{-1}$.
-Increasing the collider luminosity is expected to increase the number of event without changing the cross section for this Higgs boson production mode.
+The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$.
+Increasing the collider luminosity is expected to increase the number of event for this Higgs boson production mode.
 The measurement of this production mode has ramifications for other measurements related to coupling parameter $y_t$ of the top quark and the Higgs boson which is part of the physics program of the international CMS and ATLAS collaborations.
@@
 production in association with a single top quark and a quark jet (tHq). Each production channel has its own importance to probe the 
-various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs bosons at LHC is 
+various properties like spin, parity and the coupling strength parameters of Higgs boson to fermions and bosons. The main production mode of Higgs boson at LHC is 
 gluon gluon fusion (ggF). As bosons like gluons and photons are massless, they do not interact directly with the Higgs boson 
@@
    \includegraphics[scale=0.7]{./cd2.png}
-  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
+  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels \cite{Tanabashi:2018oca}.}
    \label{figure 3}
@@
 \item{ Higgs potential self coupling $\lambda$ or the Higgs mass $m_H$},
-\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different color charge mix with each other},
+\item{Three weak mixing angles and the CP-violating phase $\delta$ of the CKM matrix which tells us how quarks of different flavor mix with each other},
 \item{Nine yukawa couplings $y_i$ (i = 1 to 9) which determine the mass of nine charged fermions}.
@@
  The fine 
-tunings related to the origin of 
-masses and the free parameters in SM robustly suggests new physics beyond Standard model (BSM). There are lot of specific 
+tunings related to the Higgs 
+mass and the free parameters in SM suggests new physics beyond Standard model (BSM). There are lot of specific 
 BSM theories and most of these 
-models involve heavy fields. In order to identify which new physics lies beyond the 
+models involve new heavy particles. In order to identify which new physics lies beyond the 
 electroweak (EW) scale, the new parameters 
-of such theories may be constrained by the actual low energy experiments. This approach 
-requires studying each model 
-individually, and calculating every possible observable.
+of such theories may be constrained by the actual low energy experiments.
 
@@
 operators to the SM Lagrangian. 
-They are built out of SM fields and supposed to be invariant under its gauge group which is $SU(3)_C \times SU(2)_L \times U(1)_Y$. Those 
-operators are the low-energy residue 
-of the high energy theory. This approach does not pretend to guess the complete high-energy 
-model and it is based solely on 
-the symmetry of the  theory. The operators are general and the only model dependence is 
-encoded in the size of the operator
-coefficients, which is to be set from experiments. The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
-model predictions if these higher 
-dimensional operators are present in low energy effective SM theory. We can consider 
-anomalous Higgs and Higgs-gauge effective 
-dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
-(\phi^{\dagger} \phi) 
-\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
-(D^{\mu} \phi)$ to calculate the 
-deviation of Higgs boson-fermion couplings from SM. The first operator $-\frac{1}{3}(\phi^{\dagger}\phi)^3$ shift the minimum of 
-the Higgs potential. Also as there 
-will be rescaling of the Higgs field due to the introduction of these operators in the 
-potential term, Higgs-fermion (quarks 
-and leptons) couplings will be modified. The yukawa coupling of top quark with Higgs boson will be modified due to the presence of such higher dimensional operators.
+They are built out of SM fields and supposed to be invariant under its gauge group which is $SU(3)_C \times SU(2)_L \times U(1)_Y$.
+%Those 
+%operators are the low-energy residue 
+%of the high energy theory. This approach does not pretend to guess the complete high-energy 
+%model and it is based solely on 
+%the symmetry of the  theory. The operators are general and the only model dependence is 
+%encoded in the size of the operator
+%coefficients, which is to be set from experiments. The Higgs boson and fermions (quarks and leptons) coupling will deviate from the standard 
+%model predictions if these higher 
+%dimensional operators are present in low energy effective SM theory. We can consider 
+%anomalous Higgs and Higgs-gauge effective 
+%dimension 6 operators like $-\frac{1}{3}(\phi^{\dagger}\phi)^3$, $\frac{1}{2} \partial_{\mu} 
+%(\phi^{\dagger} \phi) 
+%\partial^{\mu}(\phi^{\dagger} \phi)$ and $(\phi^{\dagger} \phi)(D_{\mu} \phi)^{\dagger} 
+%(D^{\mu} \phi)$ to calculate the 
+%deviation of Higgs boson-fermion couplings from SM. The first operator $-\frac{1}{3}(\phi^{\dagg%er}\phi)^3$ shift the minimum of 
+%the Higgs potential. Also as there 
+%will be rescaling of the Higgs field due to the introduction of these operators in the 
+%potential term, Higgs-fermion (quarks 
+%and leptons) couplings will be modified.
+The yukawa coupling of top quark with Higgs boson will be modified due to the presence of such higher dimensional operators.
 
@@
 The production of Higgs boson in association with single top quark is one of the rare Higgs 
-boson production mode \cite{Khachatryan:2015ota}. As the top 
+boson production mode \cite{sirunyan2019search}. As the top 
 quark is the heaviest fundamental particle in the standard model, due to its large mass, the 
@@
 probable decay of the top quark is 
-into bottom (b) quark and W boson \cite{nishiwaki2014tth}. Using b-jet tagging algorithms, the jet originating from 
+into bottom (b) quark and $W^{\pm}$ boson \cite{{Tanabashi:2018oca}}. Using b-jet tagging algorithms, the jet originating from 
 b-quark can be reconstructed to 
@@
 is more rare than t$\bar{t}$H production \cite{Sirunyan:2018ygk}. The Higgs boson in the tH channel can be radiated 
-off by a W boson or by a top quark as shown in Figure 4.
+off by a $W^{\pm}$ boson or by a top quark as shown in Figure 4.
 
@@
 probe the relative sign between 
-the coupling of top quark with Higgs boson $y_t$ and the coupling of W boson to the Higgs 
+the coupling of top quark with Higgs boson $y_t$ and the coupling of $W^{\pm}$ boson to the Higgs 
 boson $g_{HWW}$ \cite{Sirunyan:2018lzm}. If the Yukawa coupling between top quark and Higgs boson $y_t$ deviate from the SM 
@@
 
-The LHC is sensitive to an anamolous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. 
+The LHC is sensitive to an anomalous Higgs coupling to the top quark in the Higgs boson-top quark associated production mode. 
 The anomalous coupling will arise when we add interaction terms (dimension 6 operators in effective SM theory) in the Higgs potential.
@@
 million electronic sensors arranged in concentric layers, identifies the tracks taken by these charged particles bent with very high precision \cite{Chatrchyan:2008aa}.
-The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
+The muons are detected by special subdetectors placed outside to detect them once they have crossed the solenoid as shown in Figure~\ref{figure5}.
 In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV.
-So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).
+So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the Standard Model (SM).
 
@@
     \includegraphics[width=0.6\columnwidth]{./cms12.png}
-    \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers.}
+    \caption{Transverse view of the CMS detector showing the silicon tracker, electromagnetic calorimeter, hadron calorimeter, superconducting solenoid and muon chambers \cite{Chatrchyan:2008aa}.}
     \label{figure5}
@@
     \caption{Projected performance of the LHC until 2038, which shows the preliminary dates for prolonged stops (LS) of the LHC and luminosities.
-Points show instantaneous luminosity while the line shows luminosity accumulated.}
+Points show instantaneous luminosity while the line shows luminosity accumulated \cite{collaborations2019report}.}
     \label{figure6}
@@
 
-LHC during the first run in 2011 and 2012 reached a peak luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
-All the hadron colliders in the world have so far produced a total integrated luminosity of about 10 $fb^{-1}$, while the LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
+LHC during the first run in 2011 and 2012 reached a peak instantaneous luminosity of 7.7 $\times$ $10^{33}$ $cm^{-2}s^{-1}$ which was more than 75$\%$ of its design luminosity and delivered an integrated luminosity of about 25 $fb^{-1}$ to each ATLAS and CMS.
+ The LHC will deliver about 300 $fb^{-1}$ by 2024 \cite{collaborations2019report}.
 The goal of subsequently run of LHC has been to obtain datasets at higher values of luminosities for precision measurements of the properties of Higgs boson, in order to test the Standard Model pattern of couplings to elementary particles.
-In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (Long shutdown 3), with some of the modification anticipated in 2019-2020 (LS2).
+In order to minimize the machine downtimes and maximize the productive use of the LHC for physics, the replacement of the inner triplet magnets (the one responsible to squeeze the beam at collision) and  of  all  hardware  changes  needed  to  enable  an  ambitious  luminosity  upgrade  will  take  place in parallel during one shutdown, at around 2023-25 (LS3), with some of the modification anticipated in 2019-2020 (LS2).
 This new phase of the LHC life has been named as High Luminosity LHC (HL-LHC) and has the scope of attaining the astonishing threshold of 3000 $fb^{-1}$ by the year 2036 as shown in Figure~\ref{figure6}.
@@
 Multilepton final states like ee, $\mu\mu$ and $e\mu$ and final states with single lepton with a pair of bottom quarks were combined with Higgs decay to two photons to get the final result.
-The data favour positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
+The data slightly favor positive value of top quark yukawa coupling for SM Higgs boson and excludes ranges outside the intervals [-0.9,-0.5] and [1.0,2.1] times $y^{SM}_t$ at the 95 $\%$ confidence level.
 \newpage
@@
     \includegraphics[scale=0.4]{./couplings.png}
-    \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
+    \caption{ATLAS-CMS combined measurements of coupling strength modifiers \cite{Tanabashi:2018oca}.}
     \label{figureKappas}
@@
     \includegraphics[width=0.4 \columnwidth]{./cms13.png}
-    \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the 2016 LHC data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines).}
+    \caption{Scan of -2 $\Delta$ ln(L) versus $\kappa_t$ for the 2016 LHC data (black line) and the individual channels (blue, red, and green), compared to Asimov data sets corresponding to the SM expectations (dashed lines) \cite{sirunyan2019search}.}
     \label{figureKt}
@@
 
-\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark Matter and the rest $68\%$ is dark energy.
+\onehalfspacing There is currently a great enigma in physics since we know that ordinary matter comprises only $5\%$ of the universe, another $27\%$ includes Dark matter and the rest $68\%$ is Dark energy.
 Understanding the production of the Higgs boson, as well as its decays are an important part of the physics program of CERN laboratory experiments to verify the Standard Model and look for new particles.
@@
 
-With this project we propose to incorporate the full Run 2 dataset corresponding to 150 pb$^{-1}$.
+With this project we propose to incorporate the full Run 2 dataset corresponding to 150 fb$^{-1}$.
 A factor of 4 increase in number of collision events will improve the limits by a factor of approximately 2 due to the nature of statistical uncertainties.
@@
 \item Studies of lepton and jet identification algorithms which improve the background rejection.
-\item For this search, due to the small signal over background ratio, a multi-variate algorithm is employed which combines different event variables and exploits the correlations to construct a final discriminant.
+\item Due to the small signal over background ratio, a multi-variate algorithm is employed which combines different event variables and exploits the correlations to construct a final discriminant.
 This algorithm must be trained using simulated signal and background events.
@@
 	\caption{Topology of a tH signal event in a proton-proton collision.
-The decay products from the top quark include a b-jet and a W boson decaying to a lepton and neutrino.
-In this diagram the Higgs decays to a pair of W bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically.
+The decay products from the top quark include a b-jet and a $W^{\pm}$ boson decaying to a lepton and neutrino.
+In this diagram the Higgs decays to a pair of $W^{\pm}$ bosons, one decays to a lepton and neutrino while the other one can decay leptonically or hadronically.
 In addition there is a forward jet from initial collision of the quarks.}

### 2019-11-21 tesis_hiram/Chapter1/chapter1.tex
new
correccion

--- 2019-11-14 tesis_hiram/Chapter1/chapter1.tex
@@
 single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC. 
+\\
+
 The motivation of the work is this mechanism of production of the Higgs boson has not been observed before by any experiment.
@@
 %The SM is used to study the tH channel and compare it with other Higgs production mechanisms results.
-\\
 Many channels are yet out of
@@
 proposals are yet to be put on test.
-It is possible that studies on the Higgs boson give evidence of small deviations from the SM and test new physics that are beyond SM such as String Theory and Supersymmetry.
+It is possible that studies on the Higgs boson give evidence of small deviations from the SM and test new physics that are beyond SM such as String Theory and Super-symmetry.
 \\
@@
 
- Quarks combine to form composite particles called hadrons. Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons. \\
-Mesons, are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
+ Quarks combine to form composite particles called hadrons.
+Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons.
+Mesons, are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).
+Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
 Baryons are fermions made of 3 quarks.
@@
 Both particles can interact via strong force.
-Since quarks and gluons only exist in bound states, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
-bound state\cite{gross.griff}.
+Since quarks and gluons only exist in bound, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
+bound state \cite{gross}.
 \\
@@
 The quarks up, charm and top have in common a charge of $\frac{2}{3}$, while the down, strange and bottom quarks have charge of $-\frac{1}{3}$.
-Among them, the top quark is the most massive of all, while the up and down are the least massive.\\
+Among them, the top quark is the most massive of all, while the up and down are the least massive.
 Some of the particles in the SM are not stable, so they decays and form particles with lower masses.
@@
 
-The last group of the family are the bosons,which have a spin 1 and 0. 
+The last group of the family are the bosons, which have a spin 1 and 0. 
 There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism.
 Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}.
-\\
 The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
@@
 
-There are experiments that detects particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab in United States of America, KEK in Japan, etc.
+There are experiments that detect particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab in United States of America, KEK in Japan, etc.
 More information about the LHC will be described in the next chapters.
@@
 
-The table \ref{SM table} contains the characteristics of each particle in the SM.
+The Table \ref{SM table} contains the characteristics of each particle in the SM.
 The second column shows the masses of the particles, where the most massive particle is the top quark with 173 GeV.
 There are particles with mass equal to zero, such as the gluons, photons and the neutrinos.
-\\
 The third column corresponds to the charge of the particles.
@@
 For the leptons, the charge is negative, except for neutrinos, which charge is zero.
-The bosons have a integer charge; $\pm 1$ for $W$ and 0 for $Z$, $\gamma$, $H$ and $g$.	\\
+The bosons have a integer charge; $\pm 1$ for $W$ and 0 for $Z$, $\gamma$, $H$ and $g$.	
 The next column is the spin, where for fermions (quarks and leptons) is $\frac{1}{2}$ and for bosons is 1\footnote{In general, the fermions have non integer spin and the bosons have integer spin}.
-The Higgs boson is the only boson with spin 0.\\
+The Higgs boson is the only boson with spin 0.
 The next one is the lifetime of the particle, where it shows how long the particles exist before decay.
-Stable lifetime means that the particles do not decay or can exist until they can interact with detectors.\\
+Stable lifetime means that the particles do not decay or can exist until they can interact with detectors.
 The last column is the distance of particles moving with speeds near light speed.
@@
 \begin{table}[!htbp]
-\caption{Table of particles in SM, where it shows the masses, charges,spin, lifetime and distance traveled in a lifetime .
-Stable means no decay, or lifetime almost infinite\cite{pd}.
-Particles speeds at c=0.998}
+\caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of 0.998*c).
+Stable means no decay, or lifetime almost infinite\cite{pd}.}
 \renewcommand{\arraystretch}{1.5}
@@
 \hline 
-Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
+Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance (meters) \\ 
 	\hline 
@@
 	\hline 
-$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
+$\nu_e$, $\nu_\mu$, $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
 	\hline 
@@
 The Higgs boson was discovered recently on year 2012 in the experiments ATLAS and CMS at CERN.
-The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV,where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
+The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV, where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
 \\
@@
 On 1995, in the Tevatron at Fermilab in Illinois, the top quark was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
-Since then,the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.\\
+Since then, the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.
 However, the top quark often receives special attention in new physics models because its mass requires near unity coupling to the Higgs boson\cite{top}.
-As shown in table \ref{SM table}, the top quark lifetime is so small that they decay before they can hadronise, that is to say, the process to create hadrons from quarks and gluons.\\
+As shown in Table \ref{SM table}, the top quark lifetime is so small that they decay before they can hadronise, that is to say, the process to create hadrons from quarks and gluons.\\
 
@@
 	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
-\cite{ew1}\cite{ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\
+\cite{ew1,ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\
 \\
@@
 \begin{align}
-  u_R,d_R,e^-_R 
+  u_R, d_R, e^-_R 
 \end{align}
@@
 The cross section is important in the evaluation of events for specific processes.
-In order to get the number of events for a specific process, the reaction rate $N$ is determined by the total cross section $\sigma$ and the luminosity L.\\
+In order to get the number of events for a specific process, the reaction rate $N$ is determined by the total cross section $\sigma$ and the luminosity L.
 %L is called luminosity, that is the number of particle interactions can be produced in a detector per second. 
@@
 
-In the table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
+In the Table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
 
@@
 \section{Higgs decay rates}
-In particle physics,two importatns properties are the lifetime and the decay rates of a particle.
+In particle physics, two important properties are the lifetime and the decay rates of a particle.
 The lifetime is related to the total decay rate $\Gamma$, that is the probability per unit of time a particle decay,
@@
 Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
-Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds,it has the same dimension as mass (or energy)\footnote{Cleaves H.J.
+Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds, it has the same dimension as mass (or energy)\footnote{Cleaves H.J.
 (2011) Branching Ratio.

### 2019-11-21 tesis_hiram/Chapter2/chapter2.tex
correccion

@@
 \\
-According to figure \ref{efi}, the efficiency of the tracker is around 98 $\%$ for $|\eta|<2$. The resolution of the tracker for muons with $p_t$=100 GeV is around 1-2 $\%$.\\
+According to figure \ref{efi}, the efficiency of the tracker is around 98 $\%$ for $|\eta|<2$. The resolution of the tracker for muons with $p_t$=100 GeV is around 1-2 $\%$.
 Of course, this is a first stage of the measurement of particle momentum because the other detectors are used to increase and improve the measurement and reconstruction of the particle path.
@@
 As its name says, the ECAL is mainly used for the electron detection, but also detects, photons, and neutral pions.
-The charged particles reach the crystals that provokes the photo diodes detect energy.\\
+The charged particles reach the crystals that provokes the photo diodes detect energy.
 The resolution of the ECAL is estimated by using a test beam and registering the energy signals. The resolution for electrons with energies of 120 GeV, it has obtained a resolution of 0.5$\%$.
@@
 The outer barrel hadron calorimeter (HO) consists of layers of scintillator with thickness of 10 mm, located outside of the
-magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.\\
+magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.
 There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
@@
 The RPC are located in the barrel and endcap regions that covers the range o $|\eta|<1.6$. The main purpose is to trigger events with muons. 
-RPC's are structured with a double gas filled gap and readout strips between the gaps.\\
+RPC's are structured with a double gas filled gap and readout strips between the gaps
  The gas mix used in the RPC consist of 95.2$\%$ Freon

### 2019-11-21 tesis_hiram/Chapter4/chapter4.tex
correccion

@@
 \chapter{Statistical Analysis}
-	To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
+	To estimate the sensitivity of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
 The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.
@@
 \\
+
 	%log es usado para evitar valores extremadamente pequenos debido a los productos de los exponenciales
@@
 Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC, is expected to collect 3000 fb$^{-1}$.
-Therefore, is interesting to study the sensibility of the signal strength to higher luminosities.
+Therefore, is interesting to study the sensitivity of the signal strength to higher luminosities.
 	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
@@
 	However, the uncertainty of $\mu$ for the SM case is 170$\%$ for  in the 3000 fb$^{-1}$ case, making impossible to get an evidence of a Higgs boson in the $tH$ process for the same sign muon channel.
-Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.\\
+Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.
 	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results; upper limits in this models are small.
@@
 	\begin{table}[ht!]
-		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
+		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
 		\begin{tabular}{|c|c|c|c|c|}
 			\hline
-			Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit & $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit \\
+			\multirow{2}{*}{Luminosity (fb$^{-1}$)}  &\multicolumn{2}{c|}{SM ($k_t$=1)} &\multicolumn{2}{c|}{$k_t$=-1 scenario}\\
+
+		          \hhline{~----}	&$\mu$  &$\mu$ upper limit & $\mu$ &$\mu$ upper limit or interval\\
 			\hline

### 2019-11-21 tesis_hiram/Chapter5/chapter5.tex
correccion

--- 2019-10-16 tesis_hiram/Chapter5/chapter5.tex
@@
 \chapter{Conclusion and outlook}
-In this work, we explored the sensitivity to the tH production process.
-The $tH$ process is one of the processes that comes from the proton-proton collisions in the LHC.
+In this work, we explored the sensitivity to the production process of Higgs plus single top.
+The $tH$ process is interesting channel in proton-proton collisions in the LHC.
 This process has not been observed experimentally.
-Recently CMS published a search for $tH$ process using 35.9 fb$^{-1}$ from Run 2 in 2018.
+Recently CMS published a search for $tH$ production using 35.9 fb$^{-1}$ from Run 2 .
+Using information from this dataset, we studied the expected sensitivity using an Asimov data and systematic uncertainties for the final state with same sign pairs of muons.
 \\
 
-MC simulation and real data or even only MC can be used to study sensitivity different signal processes.
-In this work we used the information published by CMS to study the expected sensitivity using an Asimov data and systematic uncertainties in the final state of a pair of same sign muons.
-In the SM case, the signal strength for the signal $tH$ is very low in comparison to
-the backgrounds, resulting in large uncertainties.
-For the inverted coupling scenario ($k_t$=-1), the uncertainty for the model after the fit was better than the
-SM case, this is due to the larger expected number of signal events. However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels.
+Using this dataset for 35.9 fb$^{-1}$, the uncertainty for the $tH$ signal strength $\mu$ is around eight times than the value of $\mu$ for the SM.
+In this case, we estimated an upper limit on $\mu$ of 17 at 95$\%$ confidence level.
+For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$, this is due to the larger expected number of signal events
 \\
@@
 We also studied the sensitivity for larger integrated luminosities expected in future runs of the LHC.
-We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
-In the case of the inverted coupling scenario, a possible signal can be observed with 10$\%$ uncertainty at 3000 fb$^{-1}$.\\
+We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit on $\mu$ is placed at 4.3.
+In the case of the inverted coupling scenario, a possible signal can be observed with an uncertainty of 10$\%$ at 3000 fb$^{-1}$.\\
+
+However, these results use only the dimuon channel, the sensitivity can be improved by combining more search channels.
+The search can include additional channels, such as three lepton in the final state or Higgs decays to a pair of photons.
+By adding more channels, the number of events increases and can give us better statistics.
+
+ %Alternatively, this scenario will be ruled out. For  3000 fb$^{-1}$, the statistical test shows that the model of $k_t$=-1 can be rule out.
+
+%In the SM, same sign $\mu\mu$ final states of the $tH$ process, it shows that is impossible to give evidence of the existence of a Higgs boson due to high uncertainties.
+The expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
+%For the $k_t$=-1, the uncertainty is low due to higher number of events for tH process and it is possible to give evidence of a Higgs
+%boson, but this model is purely theoretical.\\

### 2019-11-21 tesis_hiram/Chapter1/chapter1.tex
n

@@
 %*******************************************************************************
-\renewcommand{\baselinestretch}{1.5}
+%\renewcommand{\baselinestretch}{1.5}
 
@@
 The SM, created almost 50 years ago, has been the most successful theory in explain the phenomena in the subatomic world.
-\\
 
@@
 Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes.
-Also the impact of Higgs is also important in cosmology, where theoretical investigations relate the Higgs boson and the cosmic inflation.\\
+Also the impact of Higgs is also important in cosmology, where theoretical investigations relate the Higgs boson and the cosmic inflation.
 
@@
 single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.
-\\
 
@@
 It is possible that studies on the Higgs boson give evidence of small deviations from the SM and test new physics that are beyond SM such as String Theory and Super-symmetry.
-\\
+
 %********************************** % Third Section *************************************
-
 \section{The Standard Model} %Section - 1.3 
@@
 The gravitational force is yet to be included due to the scale of interaction with respect to the other 3.
-All the matter is composed of three kinds of particles: leptons, quarks and bosons, also called mediators.\\
+All the matter is composed of three kinds of particles: leptons, quarks and bosons, also called mediators.
 
@@
 \\
-\\
-
  Quarks combine to form composite particles called hadrons.
@@
 bound state \cite{gross}.
-\\
 
@@
 There are 6 of them: up (1968), down (1968), strange (1968), charm (theorized in 1970, discovered 1974), bottom (theorized 1973, discovered 1977), top (theorized 1973, discovered 1995).
-\\
 
@@
 \begin{center}
-  \begin{figure}[!htbp]
+  \begin{figure}[ht]
     \centering
@@
 } 
-
 The last group of the family are the bosons, which have a spin 1 and 0. 
@@
 Those bosons act as mediators in decays and creation of complex
-particles, as mesons and baryons.\\
-
+particles, as mesons and baryons.
 %In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force.
@@
 
+There are experiments that detect particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab in United States of America, KEK in Japan, etc.
+More information about the LHC will be described in the next chapters.
+\pagebreak
 \begin{center}
-  \begin{figure}[!htbp]
+	\begin{figure}[ht]
 		\centering
@@
 \end{center}
-
-There are experiments that detect particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab in United States of America, KEK in Japan, etc.
-More information about the LHC will be described in the next chapters.
-\\
-
 The Table \ref{SM table} contains the characteristics of each particle in the SM.
@@
 And also give us a perspective of how hard is the detection of the particles due to lifetime.
-\\
 
-\begin{table}[!htbp]
+\begin{table}[htp]
 \caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of 0.998*c).
@@
 \renewcommand{\arraystretch}{1.5}
-\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
+\begin{tabular}{|c|c|c|c|p{2.5cm}|p{2.5cm}|}
 \hline 
-Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance (meters) \\ 
+Particle& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance (m) \\ 
 	\hline 
@@
 	\hline 
-
 Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
@@
 \end{table}
+
 \newpage
@@
 They formulated the Higgs mechanism that explain the generation of mass for the particles.
-\\
 
@@
 The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV, where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
-\\
 The mass of this boson has been measured and its production and decay
 rates are consistent with the SM prediction. The mass of the Higgs boson measured is 
-approximately 125 MeV. The Higgs boson lifetime is 1.56 $\times$ $10^{-22}$. That is why the Higgs boson was very difficult to detect in the particle detectors. \\
-
-\pagebreak
+approximately 125 MeV. The Higgs boson lifetime is 1.56 $\times$ $10^{-22}$. That is why the Higgs boson was very difficult to detect in the particle detectors.
 
@@
 However, the top quark often receives special attention in new physics models because its mass requires near unity coupling to the Higgs boson\cite{top}.
-As shown in Table \ref{SM table}, the top quark lifetime is so small that they decay before they can hadronise, that is to say, the process to create hadrons from quarks and gluons.\\
+As shown in Table \ref{SM table}, the top quark lifetime is so small that they decay before they can hadronise, that is to say, the process to create hadrons from quarks and gluons.
 
 One of interesting the properties of top quark is its mass.
-The top quark mass is a free parameter in the SM and was extracted using indirect measurements and relying on SM calculations. The measured value of top quark mass is of 173 Gev\cite{pd}.
+The top quark mass is a free parameter in the SM and was extracted using indirect measurements and relying on SM calculations.
+The measured value of top quark mass is of 173 Gev\cite{pd}.
 The top quark mass is a very important
-parameter that puts a constraint in the Higgs boson mass and also takes an important role in electroweak symmetry breaking\cite{top}.\\
+parameter that puts a constraint in the Higgs boson mass and also takes an important role in electroweak symmetry breaking\cite{top}.
 
@@
 
-\pagebreak
-
 \section{Higgs mechanism}
@@
 that describes the weak and electromagnetic interactions
-due to the exchange of spin 1 gauge fields($W^{\pm}$,$Z$) for the weak part and a photon for the electromagnetic part. The Higgs mechanism give bosons and fermions their mass.
-
+due to the exchange of spin 1 gauge fields($W^{\pm}$,$Z$) for the weak part and a photon for the electromagnetic part.
+The Higgs mechanism give bosons and fermions their mass.
 The lagrangian for the electroweak part of SM
@@
 \cite{ew1,ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\
-\\
 
@@
 \end{align}
-
 %The charge of particle Q is given by $Q=T^3+Y$ with $Y$ the hypercharge and $T$ the third component of the weak isospin.
@@
 \end{align}
-
 where $D_\mu$ is a operator 
@@
 \end{align}
-
  %is Higgs field which is a complex scalar field that exists in a vacuum and the potential is symmetric under rotations in $\Phi$ space. 
@@
 and parameters $\lambda $ and $\mu^2$ are parameters of the potential. The Higgs potential for $\mu^2 <0$ and $\lambda>0$ can be visualized in the figure \ref{hat}
-
 %The $\lambda $ term describes self-interactions among the scalar fields.
@@
 %\end{figure}
-
-\begin{figure}[ht!]
+\begin{figure}[ht]
   \centering
@@
 \end{figure}
-
 Electroweak symmetry breaking refers to the choice of ground state
@@
 \end{align}
-where $v=-\frac{\mu^2}{\sqrt{2}}$ is called the vacuum expectation value.\\
-
+where $v=-\frac{\mu^2}{\sqrt{2}}$ is called the vacuum expectation value.
 %Now, since the potential depends on $\Phi^\dagger \Phi$, We can select $\Phi$ in the form 
@@
 \end{align}
-
 we define the physical vector boson $W^-_\mu$. $W^+_\mu$ and $Z$ 
@@
 \end{align}
-
 %From equation \ref{smo}, we can express $W^1_\mu$ and $W^2_\mu$ in terms of $W^{+}_\mu$ and $W^{-}_\mu$
@@
 %\end{align}
-
 %and the mass term
@@
 \end{align}
-
 %and the photon that in this case is the field A
@@
 %\end{align}
-
 The last part of the lagrangian is the Yukawa lagrangian
@@
 	% \Phi =\sqrt{-\frac{\mu^2}{2\lambda}}=\frac{v}{\sqrt{2}}  \qquad \lambda >0
-	$ is necessary for the correct transformation in the case of up quarks. \\
-h.c refers to hermitian conjugate terms. } The indices m and n mean sum over the families. \\
+	$ is necessary for the correct transformation in the case of up quarks. 
+h.c refers to hermitian conjugate terms. } The indices m and n mean sum over the families. 
 %It is required to have two representations of Higgs fields
 %with $Y=\frac{1}{2}$ and $\frac{1}{2}$ to give masses to quarks and electrons.
-
 By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
@@
 There is also the vector Higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}.
-These processes are shown in the figure \ref{psu} \\
+These processes are shown in the figure \ref{psu}
 
@@
 
-\begin{figure}[htbp]
+\begin{figure}[ht]
 \centering
@@
 tH process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens to new discoveries.
-\\
 
@@
  Cross sections are expressed in barns, where 1 barn=$10^{-34}$ cm$^{2}$.
-\\
+
 The cross section is important in the evaluation of events for specific processes.
@@
 The unit of measurement of luminosity is cm$^{-2}$s$^{-1}$. Therefore, The reaction rate is 
-
 \begin{align} \label{nr}
@@
 In practice, the luminosity is measured by counting the number of events for a well known process.
-
 \begin{table}[ht]
@@
 For the processes tH and $t\bar{t}$H, they have the smallest cross section, so the probability for the processes is low and generates a small number of events.
+\footnotetext{\small Taken from \url{ https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWGCrossSectionsFigures}}
 \pagebreak
-\footnotetext{Taken from \url{ https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWGCrossSectionsFigures}}
+
 \section{Higgs decay rates}
@@
 with N the original number of particles before the decay. From here is evident that number of particles left in a decay is 
-
 \begin{align}
@@
 The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV, but has not yet been measured due to the detector resolution\cite{cms-manual}.
-\\
-\begin{table}[!htbp] 
+
+\begin{table}[ht] 
 \caption[SM Higgs boson branching ratios for $M_H$ =125 GeV]{SM Higgs boson branching ratios for $M_H$ =125 GeV \protect \cite{pd}}
@@
 This decay is very rare but not impossible to detect in the future.
-In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$\\
+In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$.
 
@@
 Any deviation from the SM can lead to a large enhancement of the event rate.
- $\kappa_t$ and $\kappa_V$ are the coupling parameters, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson. \\
+ $\kappa_t$ and $\kappa_V$ are the coupling parameters, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson.
 
@@
 \pagebreak
-
 \end{chapter}

### 2019-11-21 tesis_hiram/Chapter2/chapter2.tex
n

@@
 The LHC is a 27 kilometer ring composed of superconducting magnets with accelerating structures to boost the energy of the particles.
-\\
 
@@
 A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
-\\
 
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[ht]
 \centering
-\includegraphics[width=17cm,height=11cm]{Chapter1/cern.jpg}
+\includegraphics[width=16cm,height=10cm]{Chapter1/cern.jpg}
 \caption[Large hadron collider from CERN]{Large hadron collider from CERN\cite{cern1}} \label{lhc}
@@
 
-\begin{table}[!htbp]
+\begin{table}[ht]
 \centering
@@
 Besides of the particles created by the quarks of the proton, gluons are also radiated and create new particles and photons are radiated too.
-\\
 During the collision time, the main detectors of LHC capture the energy 
 and save the data in supercomputers. Those high end computers starts to measure the signals in order to assign a type of events.
-\\
 
@@
 With the exploration of theses theories, people hope for a discovery that guide them toward a unified theory, so the importance to accelerate particles to higher energy scales.
-\\
+
 The LHC has a schedule where there is a period of experiments that last for three or four years. Ending the experimental time, the engineers of the LHC start the maintenance.
 
-\begin{figure}[!htbp]
+\begin{figure}[ht]
 \centering
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[ht]
 	\centering
@@
 \end{figure}
-There are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easy, the complex is buried 100 meters underground.\\
+There are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easy, the complex is buried 100 meters underground.
 
@@
 The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter, a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
-\\
 
@@
 Muons can be produced in interesting events like Higgs, $W^{\pm}$ and $Z$ boson decays.%Search for evidence and give proof of super symmetry for show evidence of BSM (Beyond Standard Model).
-Detection of massive vector bosons $W^\pm$ and Z via $e^+e^-$ and $\mu^+ \mu^-$ decays.\\
+Detection of massive vector bosons $W^\pm$ and Z via $e^+e^-$ and $\mu^+ \mu^-$ decays.
 %Search for extra dimensions from BSM theory that could be related to production of particles and quantum gravity.
@@
 This experiment along the ATLAS experiment discovered the Higgs boson in 2012.
-\\
 
@@
 The outer radius of the tracker is 110 cm, and its total length is 540 cm.
-The tracker coverage is $|\eta|<2.4$\footnote{$\eta$, called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.\\
+The tracker coverage is $|\eta|<2.4$\footnote{$\eta$, called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.
 
@@
 %different modules in each blade.
-\\
 
- %The outer radius of the tracker is 110 cm, and its total length is 540 cm. \\
+ %The outer radius of the tracker is 110 cm, and its total length is 540 cm. 
  %Here, silicon microstrip detectors are placed in the r axis (cylindrical coordinates), between 20 and 110 cm.
@@
 A full coverage of the Tracker is shown in figure \ref{pixel2}
-\\
 
@@
 For muons the efficiency of the tracker is shown in \ref{efi}
-\begin{figure}[!htbp]
+\begin{figure}[ht]
 	\centering
@@
 \end{figure}
-\\
+
 According to figure \ref{efi}, the efficiency of the tracker is around 98 $\%$ for $|\eta|<2$. The resolution of the tracker for muons with $p_t$=100 GeV is around 1-2 $\%$.
@@
 The crystal length is 230 mm.
-The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}\\
+The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}
 
@@
 mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
-\\
-\begin{figure}[!htbp]
+
+\begin{figure}[ht]
 	\centering
@@
 At the endcap, the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$), allowing to operate in the magnetic field.
-VPT have a size of 25 mm in diameter, glued to the back of each crystal.\\
+VPT have a size of 25 mm in diameter, glued to the back of each crystal.
 
@@
 against minimum ionizing particles, and improves the position determination of electrons and photons.
-\\
 
@@
 HCAL is located in the barrel and the endcaps, surrounding the ECAL and affected by the magnetic field generated by the solenoid.
-The Barrel section (HB) and endcap section (HE) cover the pseudorapidity 0 < $|\eta|$ < 1.3 and 1.3 < $|\eta|$ < 3.0 respectively.\\
+The Barrel section (HB) and endcap section (HE) cover the pseudorapidity 0 < $|\eta|$ < 1.3 and 1.3 < $|\eta|$ < 3.0 respectively.
 
@@
 Each wedge has 17 active layers composed of scintillator tiles with 16 layers of absorber metal (brass and stainless steel).
-Each tile has a size of $\Delta \eta × \Delta \phi$ = 0.087 $\times$ 0.087.
+Each tile has a size of $\Delta \eta \times \Delta \phi$ = 0.087 $\times$ 0.087.
 Light of scintillator is collected by a single wave
 length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm.
-\\
 
@@
 \cite{cms-manual}
-\\
-\begin{figure}[!htbp]
+
+\begin{figure}[ht]
 	\centering
@@
 %The length of the fibers are 1.65 m and 1.43 m, which are alterned with a 5 mm of separation.
-\\
 
@@
 The DT's, CSC's and RPC's are shown in the figure \ref{dt}.
- \\
 
@@
 There are 250 chambers in 4 layers inside the magnet return yoke, with radii of approximately 4.0, 4.9, 5.9 and 7.0 m from the beam axis and 12 sections covering 30$^\circ$ in $\phi$ each one.
-\\
-\begin{figure}[!htbp]
+
+\begin{figure}[ht]
 	\centering
@@
 %Together with DT, cover the $|\eta|< 2.4$. These systems can each identify the collision crossing that generated the muon and trigger on (recolect) the transverse momentum ($p_T$).
-\\
 
@@
  The gas mix used in the RPC consist of 95.2$\%$ Freon
-($C_2 H_2 F_4$ ), 4.5$\%$ isobutane ($C_4 H_{10}$), and 0.3$\%$ sulphur hexafluoride (SF$_6$ )\cite{cms7}.\\
+($C_2 H_2 F_4$ ), 4.5$\%$ isobutane ($C_4 H_{10}$), and 0.3$\%$ sulphur hexafluoride (SF$_6$ )\cite{cms7}.
 
@@
 	\centering
-	\includegraphics[width=0.4\linewidth]{Chapter2/mu-efi}
+	\includegraphics[width=0.6\linewidth]{Chapter2/mu-efi}
 	\caption[Muon reconstruction efficiency in terms of $\eta$ and $p_t$]{Muon reconstruction efficiency in terms of $\eta$ and $p_t$\cite{cms-manual}}

### 2019-11-21 tesis_hiram/Chapter4/chapter4.tex
n

@@
 The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.
-The uncertainty of the signal strength is estimated by applying a fit to the Asimov dataset, where the model
-	is constructed from the sum of the individual backgrounds and signal. The fit is implemented using a Poisson likelihood and Gaussian constraints for the systematical uncertainties in the model.
+The uncertainty of the signal strength is estimated by applying a fit to the Asimov dataset, where the model is constructed from the sum of the individual backgrounds and signal.
+The fit is implemented using a Poisson likelihood and Gaussian constraints for the systematical uncertainties in the model.
 
@@
 	$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background.
-$\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.\\
+$\sigma_k$ for the backgrounds are shown in the Table \ref{tth-table}.
 
@@
 In the figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models.
-\\
 
@@
 After the fit, $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed.
+
 	\pagebreak
 
-		\begin{figure}[!htbp]
+		\begin{figure}[ht]
 		\centering
@@
 	\end{figure}
-
-	\begin{table}[ht!]
+	\begin{table}[ht]
 		\centering
@@
 	\end{table}
-
 	\begin{table}[ht!]
@@
 	\pagebreak
+
 	\section{Limit calculation}
 	Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
-	Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.\\
+	Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
 
@@
 	Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model. 
-
+	\pagebreak
 	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
@@
 For this analysis we assume the systematic uncertainties assigned to the background are the same.
-	\\
 
@@
 This is caused by the increased events available for the fit.
-\\
 
@@
 However, the likelihood scan parabolas are very closed and that indicates a decrease in the uncertainty of $\mu$ more notable than SM case.
-	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}\\
+	Of course, as the previous section, we estimate the upper limit for these cases and they are shown in the Table \ref{upper}
 
@@
 
-	\begin{table}[ht!]
+	\begin{table}[ht]
 		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
@@
 			\multirow{2}{*}{Luminosity (fb$^{-1}$)}  &\multicolumn{2}{c|}{SM ($k_t$=1)} &\multicolumn{2}{c|}{$k_t$=-1 scenario}\\
-
 		          \hhline{~----}	&$\mu$  &$\mu$ upper limit & $\mu$ &$\mu$ upper limit or interval\\
@@
 
-	\pagebreak
-
-		\begin{figure}[ht!]
+		\begin{figure}[ht]
 		\centering
@@
 
-	\begin{figure}[!htbp]
+	\begin{figure}[ht]
 		\centering
-		\begin{minipage}[b]{0.55\textwidth}
+		\begin{minipage}[b]{0.7\textwidth}
 			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
@@
 		\hfill
-		\begin{minipage}[b]{0.55\textwidth}
+		\begin{minipage}[b]{0.7\textwidth}
 			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
@@
 
-	\begin{figure}[!htbp]
+	\begin{figure}[ht]
 		\centering

### 2019-11-21 project_ashish/paper.tex

@@
 
-\onehalfspacing The research project propose to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state.
+\onehalfspacing This research project proposes to study the unobserved production channel of the Higgs boson in associated with a single top quark (tH) using Higgs boson decay to multilepton final state.
 The dataset collected during the Run II (2015-2018) of Large Hadron Collider (LHC) will be used corresponding to an integrated luminosity of 150 $fb^{-1}$.

### 2019-11-22 tesis_hiram/Abstract/abstract.tex
n

@@
 %	\justifying
-I present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
-process I explore a Higgs production mechanism which has not yet been observed
+We present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
+process, we explore a Higgs production mechanism which has not yet been observed
 experimentally. The expected sensitivity is estimated by using an Asimov dataset for 35.9 fb$^{-1}$ of proton-proton collisions and is extrapolated to the high luminosity phase of the LHC (HL-LHC).
-The sensivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
+The sensitivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
 %\end{center}

### 2019-11-22 tesis_hiram/Abstract/resumen.tex
n

@@
 %	\justifying
-Presento un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
+Se presenta un estudio sobre la producci\'on del boson de Higgs y un top quark ($tH$) en el canal de 2 muones con el mismo signo $\mu^\pm \mu^\pm$ usando datos publicados por el experimento CMS en el CERN.
 Estudiando este proceso se explora este mecanismo de producci\'on del boson de Higgs que a\'un no se ha detectado experimentalmente.

### 2019-11-22 tesis_hiram/Acknowledgement/acknowledgement.tex
algo
fixes
n

@@
 And I would like to acknowledge Dr.
-Jos\'e Feliciano Ben\'itez Rubio for his contributions and advices in order to develop  and write this thesis.
+Jos\'e Feliciano Ben\'itez Rubio for his contributions and advises in order to develop  and write this thesis.
 Also thank Dr.
-Dr.
 Javier Murillo and  Dr.
-Cristina Oropeza for their observations and advices in my formation.
-DR. Susana Alv\'arez for support
+Cristina Oropeza for their observations and advises in my formation.
+Dr. Susana Alv\'arez for support during the process of the thesis. Acknowledgments to CONACYT for supporting this thesis with financial aid.
 

### 2019-11-22 tesis_hiram/Chapter1/chapter1.tex
n

@@
 
-\section{General objetive and motivations}
+\section{General objective and motivations}
 
-Particle physics is a field of study of physics that studies the particles that create matter and its interactions to very small scale, even smaller than atoms.
-The particles analyzed in particle physics are the fundamental particles that compose the matter and the responsible for all forces of nature.
-All those particles and their properties are grouped in a theory called the Standard Model.
-Standard Model (SM) is a theory that describes the fundamental forces (except gravity) and classify the elementary particles in bosons (entire spin) and fermions (half spin).
-The SM, created almost 50 years ago, has been the most successful theory in explain the phenomena in the subatomic world.
+Particle physics is a field of physics that studies the particles that create matter and their interactions to very small scale, even smaller than atoms.
+The particles analyzed in particle physics are the fundamental particles that compose matter and the responsible for all forces of nature.
+All those particles and their properties are grouped in a theory called the Standard Model (SM).
+SM is a theory that describes the fundamental forces (except gravity) and classifies the elementary particles in bosons (integer spin) and fermions (half spin).
+The SM, created almost 50 years ago, has been the most successful theory in explaining the phenomena in the subatomic world.
 
 One of the particles of the SM, the Higgs Boson, was recently discovered in 2012 in the ATLAS and CMS experiments at CERN.
-The discovery of Higgs boson in proton proton collisions marked a new era in the particle physics due to its characteristic of giving the matter the property of mass, according to previous theories and predictions.
-Since then, people around the world are working in the Large Hadron Collider at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes.
-Also the impact of Higgs is also important in cosmology, where theoretical investigations relate the Higgs boson and the cosmic inflation.
+The discovery of Higgs boson in proton proton (pp) collisions marked a new era in particle physics due to its characteristic of giving matter the property of mass, according to previous theories and predictions.
+Since then, people around the world are working in the Large Hadron Collider (LHC) at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes.
+Also the impact of Higgs boson is also important in cosmology, where theoretical investigations relate the Higgs boson to the cosmic inflation.
 
-In the recent years, there have been many studies in the Higgs production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of Higgs in those processes.
-In this work, we will analyze the production of Higgs boson in association with a
+In the recent years, there have been many studies in the Higgs boson production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of the Higgs boson in those processes.
+In this work, we will analyze the production of a Higgs boson in association with a
 single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.
 
-The motivation of the work is this mechanism of production of the Higgs boson has not been observed before by any experiment.
-The exploration of Higgs production on the tH channel is subject relatively new.
+The motivation of the work is that this production mechanism of the Higgs boson has not been observed before by any experiment.
+The exploration of Higgs production on the tH channel is a relatively new subject.
 %The SM is used to study the tH channel and compare it with other Higgs production mechanisms results.
@@
 reach experimentally. At the same time, many theoretical
-proposals are yet to be put on test.
+proposals are yet to be put to test.
 It is possible that studies on the Higgs boson give evidence of small deviations from the SM and test new physics that are beyond SM such as String Theory and Super-symmetry.
@@
     \includegraphics[scale=0.3]{Chapter1/sm1.png}
-    \caption{Standard Model to date \protect \footnotemark}
+    \caption[Standard Model to date]{Standard Model to date \protect \footnotemark}
     \label{sm1}

### 2019-11-23 tesis_hiram/Chapter1/chapter1.tex
p

@@
 Since then, people around the world are working in the Large Hadron Collider (LHC) at CERN in order to detect the Higgs bosons in higher energies and different Higgs production processes.
-Also the impact of Higgs boson is also important in cosmology, where theoretical investigations relate the Higgs boson to the cosmic inflation.
+Also the Higgs boson is also important in cosmology, where theoretical investigations relate the Higgs boson to the cosmic inflation.
 
-In the recent years, there have been many studies in the Higgs boson production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of the Higgs boson in those processes.
+In recent years, there have been many studies in the Higgs boson production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of the Higgs boson in those processes.
 In this work, we will analyze the production of a Higgs boson in association with a
-single top quark (tH) in proton-proton collisions with the CMS experiment of the LHC.
+single top quark (tH) in pp collisions with the CMS experiment of the LHC.
 
@@
 \section{The Standard Model} %Section - 1.3 
-The SM, created in the decade of seventies, is a successful theory that explains the structure of matter and the interactions of three of the four fundamental forces which are electromagnetic, strong and weak forces.
-The gravitational force is yet to be included due to the scale of interaction with respect to the other 3.
-All the matter is composed of three kinds of particles: leptons, quarks and bosons, also called mediators.
+The SM, created in the decade of the seventies, is a successful theory that explains the structure of matter and the interactions of three of the four fundamental forces which are electromagnetic, strong and weak.
+The gravitational force is yet to be included due to the scale of the interaction with respect to the other 3.
+All matter is composed of three kinds of particles: leptons, quarks and bosons, also called mediators.
 
 For the leptons we have electrons ($e$), muons ($\mu$), and taus ($\tau$) with charge -1 and their neutrinos $\nu_e, \nu_\mu, \nu_\tau$, are chargeless particles.
-Leptons have their respective antiparticle; same structure with opposite charge.
+%Leptons have their respective antiparticle; same structure with opposite charge.
  All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$\cite{griff}.% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless.
@@
 Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons.
-Mesons, are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).
+Mesons are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).
 Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
@@
 Examples of baryons are protons and neutrons.
-Both particles can interact via strong force.
+Both types of particles can interact via the strong force.
 Since quarks and gluons only exist in bound, it is impossible to observe isolated quarks except the top quark, which decays before it has time to form a
@@
 Quarks were first theorized by Murray Gell-Mann and 
-George Zweig in 1964, were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until scattering experiments at the Stanford Linear Accelerator Center in 1968\cite{griff}.
+George Zweig in 1964.
+They were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until scattering experiments at the Stanford Linear Accelerator Center in 1968\cite{griff}.
 There are 6 of them: up (1968), down (1968), strange (1968), charm (theorized in 1970, discovered 1974), bottom (theorized 1973, discovered 1977), top (theorized 1973, discovered 1995).
@@
 Other particles do not decay or their lifetimes are very long.
-The final states can be represented with a Feynman diagram according to the SM vertices\cite{mark}.
+All the particles in the SM are shown in the figure \ref{sm1}.
+%The final states can be represented with a Feynman diagram according to the SM vertices\cite{mark}.
 
@@
 \end{center}
- \footnotetext{Taken from \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}
-} 
-The last group of the family are the bosons, which have a spin 1 and 0. 
-There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for electromagnetic force; gluon which also massless, is related to strong force and Higgs boson, recently discovered, is in charge of give the property of mass to particles via Higgs mechanism.
-Bosons let other particles to interact, even themselves, which is shown in the figure \ref{sm}.
-The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluon can only interact with quarks and itself.
+ \footnotetext{Taken from \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}} 
+The last group of the family are the bosons, which have either spin 1 or 0. 
+There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for the electromagnetic force; gluons which are also massless, is related to the strong force and Higgs boson, recently discovered, is in charge of giving the property of mass to particles via the Higgs mechanism.
+Bosons let other particles interact, even themselves, which is shown in figure \ref{sm}.
+The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluons can only interact with quarks and with itself.
 Those bosons act as mediators in decays and creation of complex
@@
 More information about the LHC will be described in the next chapters.
-\pagebreak
-\begin{center}
+
 	\begin{figure}[ht]
@@
 		\includegraphics[scale=0.35]{Chapter1/sm.png}
-		\caption{Particle interactions in Standard model}
+		\caption{Particle interactions in Standard model \footnote{Taken from \url{https://commons.wikimedia.org/wiki/File:Elementary_particle_interactions_in_the_Standard_Model.png}.
+Created by Eric Drexler.}}
 		\label{sm}
 	\end{figure}
-\end{center}
-The Table \ref{SM table} contains the characteristics of each particle in the SM.
+
+Table \ref{SM table} contains the characteristics of each particle in the SM.
 The second column shows the masses of the particles, where the most massive particle is the top quark with 173 GeV.
@@
 The Higgs boson is the only boson with spin 0.
-The next one is the lifetime of the particle, where it shows how long the particles exist before decay.
-Stable lifetime means that the particles do not decay or can exist until they can interact with detectors.
+The next one is the lifetime of the particle, where it shows how long the particles exist before decay. Stable lifetime means that the particles do not decay or lifetime almost infinite.
 The last column is the distance of particles moving with speeds near light speed.
-This column visualize the distance traveled in the predicted lifetime of the particle.
-And also give us a perspective of how hard is the detection of the particles due to lifetime.
+This column illustrates the distance traveled in the predicted lifetime of the particle.
+And also give us a perspective of how hard the detection of  particles due to their lifetime is.
 
 \begin{table}[htp]
-\caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of 0.998*c).
-Stable means no decay, or lifetime almost infinite\cite{pd}.}
+\caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of $v$=0.998c)\cite{pd}.}
 \renewcommand{\arraystretch}{1.5}
@@
 	\hline 
-Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
+Up quark ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
 	\hline 
-Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
+Charm quark ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
 	\hline 
-Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
+Top	quark ($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
 	\hline 
-Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
+Down quark ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
 	\hline 
-Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
+Strange quark ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
 	\hline 
-Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
+Bottom quark ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
 	\hline 
@@
 	\hline 
-$\nu_e$, $\nu_\mu$, $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
+$\nu_e$, $\nu_\mu$, $\nu_\tau$& 2 $\times$ 10$^{-6}$ & 0 & $\frac{1}{2}$ & Stable & -\\
 	\hline 
@@
 First theorized in 1964 by a group of theoretical physicist composed by Peter Higgs, Fran\c cois Englert, Robert Brout, Gerald Guralnik, C.
-Richard Hagen, and Tom Kibble in separated groups.
-They formulated the Higgs mechanism that explain the generation of mass for the particles.
+Richard Hagen, and Tom Kibble in separate groups.
+They formulated the Higgs mechanism that explains the generation of mass for the particles.
 
-The theory also explains Higgs bosons give the mass to the particles via Higgs Field and the mass of Higgs boson itself.
+The theory also explains Higgs bosons give the mass to the particles via the Higgs Field and the mass of the Higgs boson itself.
 The Higgs boson was discovered recently on year 2012 in the experiments ATLAS and CMS at CERN.
-The experiment was a proton proton collision with center of mass energy of 7 and 8 TeV, where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd}.
+The experiment was conducted using proton-proton collisions with center of mass energy of 7 and 8 TeV, where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd,Aad_2012}.
 The mass of this boson has been measured and its production and decay
-rates are consistent with the SM prediction. The mass of the Higgs boson measured is 
-approximately 125 MeV. The Higgs boson lifetime is 1.56 $\times$ $10^{-22}$. That is why the Higgs boson was very difficult to detect in the particle detectors.
+rates are consistent with the SM prediction.
+The mass of the Higgs boson measured is 125.18 $\pm$ 0.16 GeV\cite{pd}.
+The Higgs boson lifetime is 1.56 $\times$ $10^{-22}$ s.
+That is why the Higgs boson was very difficult to detect in particle detectors.
 
 \section{Top quark}
-The top quark is the most massive particle with a charge of 2/3 with spin of 1/2.
+The top quark is the most massive particle with a charge of 2/3 and spin of 1/2.
 First proposed by M.
@@
 Maskawa in 1973 to explain observed CP violations in Kaon decay\cite{griff}.
-On 1995, in the Tevatron at Fermilab in Illinois, the top quark was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
+In 1995, in the Tevatron at Fermilab in Illinois, the top quark was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
 Since then, the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.
@@
 
-One of interesting the properties of top quark is its mass.
+One of the interesting properties of top quark is its mass.
 The top quark mass is a free parameter in the SM and was extracted using indirect measurements and relying on SM calculations.
-The measured value of top quark mass is of 173 Gev\cite{pd}.
+The measured value of the top quark mass is of 173 Gev\cite{pd}.
 The top quark mass is a very important
@@
 The production of top quark can be generated in different ways.
-In tevatron and LHC, the production of $t\bar{t}$ comes from ggF (gluon gluon fusion) via strong force.
+In Tevatron and LHC, the production of $t\bar{t}$ comes mainly from ggF (gluon gluon fusion) via strong force.
 Even it is possible to create a single top quark in the LHC via electroweak interactions (with a W boson)\cite{th1}.
 The top quark, due to its big mass, always decays into a W boson and a b quark.
-But since the W boson have various decays, the top quark can generate many possible particles, according to W boson decays.
-Some posible decays of top quark is the decay to a lepton such as muon, electron or tau and their neutrinos.
+But since the W boson has various decays, the top quark can generate many possible particles, according to W boson decays.
+Some possible decay of the top quark is the decay to a lepton such as muon, electron or tau and their neutrinos.
 %The antitop, antiparticle of top quark, can decay to W$^{-1} \bar{b}$ and its decay is the same as top, but with inverse signal.
@@
 \end{align}
-
-$W^i$ (i=1,2,3) are three SU(2) gauge bosons and B is a U(1) gauge boson.\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
+$W^i$ (i=1,2,3) are three SU(2) gauge bosons, B is a U(1) gauge boson and $g$  is a couping constant for $W$ gauge boson.\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
 	+1 \quad \text{for even permutation} \\
@@
 	0 \quad \text{i=j, or j=k, or k=i } 
-	\end{dcases}$.} In the end, those gauge bosons, after introduce the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
+	\end{dcases}$.} In the end, those gauge bosons, after introducing the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
 \cite{ew1,ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\
 
-The second term refers to kinematic energy of fermions 
+The second term refers to kinetic energy of fermions 
 \begin{align}
@@
 refer to the left (right) handed particles.\footnote{$\bar{\psi}$ denotes the adjoint spinor $\bar{\psi}=\psi^\dagger \gamma^0$.
-$\cancel{D}=\gamma^\mu D_\mu$. $\gamma$ are the Dirac matrices}. 
+$\cancel{D}=\gamma^\mu D_\mu$. $\gamma$ are the Dirac matrices}
 The gauge covariant derivatives are given by
@@
 \end{align}
-where $\sigma^i$ are the Pauli matrices. L and R refers to left and right handed fields.
+where $\sigma^i$ are the Pauli matrices and $g'$ is the coupling constant for $B$ gauge boson. %L and R refers to left and right handed fields.
 The left handed fields for the first family are defined by the following doublets
@@
 \end{align}
-where $D_\mu$ is a operator 
+where $D_\mu$ is an operator 
  \begin{align}
@@
 \end{array} \right) $ is a SU(2) doublet of scalar fields. V is symmetrical under rotations in $\Phi$ space
-and parameters $\lambda $ and $\mu^2$ are parameters of the potential. The Higgs potential for $\mu^2 <0$ and $\lambda>0$ can be visualized in the figure \ref{hat}
+and parameters $\lambda $ and $\mu^2$ are parameters of the potential. The Higgs potential for $\mu^2 <0$ and $\lambda>0$ can be visualized in figure \ref{hat}
 %The $\lambda $ term describes self-interactions among the scalar fields.
@@
 \end{align}
-we define the physical vector boson $W^-_\mu$. $W^+_\mu$ and $Z$ 
+
+we define the physical vector boson $W^-_\mu$, $W^+_\mu$ and $Z_\mu$ 
 \begin{align} 
@@
 \end{align*}
-from which the masses for the fermions shown to be proportional to the Yukawa couplings
+from which the masses for the fermions are shown to be proportional to the Yukawa couplings
 \begin{align*}
@@
 During a particle collision, there are various ways that the Higgs boson can be created.
-The most common is the gluon gluon fusion process ($gg$F) which is the process which involve two gluons mediated by the exchange of a virtual, heavy top
+The most common is the gluon gluon fusion process ($gg$F) which is the process which involves two gluons mediated by the exchange of a virtual, heavy top.
 quarks.
@@
 This process is a rare expected process with a very small production rate\cite{pd}.
-In the figure \ref{thw}, is another way to produce $tH$, in association with a $W$.
+In figure \ref{thw}, another way to produce $tH$, in association with a $W$ is shown.
 
@@
 \includegraphics[scale=0.5]{Chapter1/pg.png}
-\caption{Different Higgs production mechanism, from the most likely to least likely}
+\caption[Different Higgs production mechanism, from the most likely to least likely]{Different Higgs production mechanism, from the most likely to least likely \cite{gamma}\cite{timo}}
 \label{psu}
@@
 \includegraphics[scale=0.7]{Chapter1/thw.png}
-\caption{$tHW$ mechanism}
+\caption[$tHW$ mechanism]{$tHW$ mechanism\cite{th1}}
 \label{thw}
@@
 
-In tH process, Higgs boson is radiated from a single top quark as shown in \ref{psu}.
-tH process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens to new discoveries.
+In the tH process, a Higgs boson is radiated from a single top quark as shown in figure \ref{psu}.
+The $tH$ process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens the path to new discoveries.
 
@@
 %L is called luminosity, that is the number of particle interactions can be produced in a detector per second. 
-The unit of measurement of luminosity is cm$^{-2}$s$^{-1}$. Therefore, The reaction rate is 
+The unit of measurement of luminosity is cm$^{-2}$s$^{-1}$. Therefore, the reaction rate is 
 \begin{align} \label{nr}
@@
 
-In the Table \ref{crt} shows the Higgs production cross section for pp collision and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
+ Table \ref{crt} shows the Higgs production cross section for pp collisions and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
 
@@
 \caption[Cross section for different processes generated in a pp collision]{
-Cross section for different processes generated in a pp collision \protect \footnotemark }
+Cross section for different processes generated in a pp collision  \cite{dcrosse}}
  \label{csp}
@@
 
-Here we can see ggF process have the biggest cross section of all Higgs mechanism and generates the greatest number of events possibles.
+Here we can see that the ggF process has the biggest cross section of all Higgs mechanism and generates the greatest number of events possibles.
 For the processes tH and $t\bar{t}$H, they have the smallest cross section, so the probability for the processes is low and generates a small number of events.
-\footnotetext{\small Taken from \url{ https://twiki.cern.ch/twiki/bin/view/LHCPhysics/LHCHXSWGCrossSectionsFigures}}
 \pagebreak
@@
 In particle physics, two important properties are the lifetime and the decay rates of a particle.
-The lifetime is related to the total decay rate $\Gamma$, that is the probability per unit of time a particle decay,
+The lifetime is related to the total decay rate $\Gamma$, that is the probability per unit of time a particle will decay,
 \begin{align}
@@
 
-The number of particles decreases over time exponentially and this can be measured. With this, it is possible determinate the mean lifetime\cite{griff}
+The number of particles decreases over time exponentially and this can be measured. With this, it is possible determine the mean lifetime\cite{griff}
 \begin{align}
@@
 \end{align}
-In case of the decay rate to a specific process, it is necessary get the branching fraction of the process. 
+In case of the decay rate to a specific process, it is necessary to get the branching fraction of the process. 
 The branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.
@@
 \end{align}
-Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
-Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds, it has the same dimension as mass (or energy)\footnote{Cleaves H.J.
+Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle.
+%Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds, it has the same dimension as mass (or energy)\footnote{Cleaves H.J.
 (2011) Branching Ratio.
@@
 Springer, Berlin, Heidelberg}.
-The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ is about 4 MeV, but has not yet been measured due to the detector resolution\cite{cms-manual}.
+The lifetime of the Higgs boson is predicted to be 1.56 $\times$ $10^{-22}$ seconds and corresponds to $\Gamma_H$ of about 4 MeV, but has not yet been measured due to the detector resolution\cite{cms-manual}.
 
@@
 \end{table}
-The decay $H \rightarrow$ $b\bar{b}$ have a branching ratio a bit more than 50$\%$, therefore is the most likely decay Higgs boson can decay.
+The decay $H \rightarrow$ $b\bar{b}$ has a branching ratio a bit more than 50$\%$, therefore is the most likely decay .
 Due to this, $H\rightarrow b\bar{b}$ is a very studied process and most likely to detect a Higgs boson in the data after reconstruction.
@@
 diagrams in figure \ref{newth} provides a unique opportunity to study the relative sign of the coupling.
-In SM, the two diagrams interfere negatively and thereby suppress the production cross section.
+In the SM, the two diagrams interfere negatively and thereby suppress the production cross section.
 Any deviation from the SM can lead to a large enhancement of the event rate.

### 2019-11-23 tesis_hiram/Chapter2/chapter2.tex
p

@@
 
-The Large Hadron Collider (LHC) is one the largest and most powerful particle accelerator in the world.
+The Large Hadron Collider (LHC) is the largest and most powerful particle accelerator in the world.
 It came on operation on 10 September 2008 and it is the most recent addition from the European Organization for Nuclear Research (CERN).
@@
 The LHC is designed to accelerate particles to high energies and generate collisions. There are several
-experiments installed along the LHC ring.
+experiments installed along the LHC ring as shown in figure \ref{lhc}.
 One of them is ATLAS, located on Point 1 between the two injection lines, which is a general purpose detector.
@@
 
-Inside the accelerator, two high energy particles beams travel at
+Inside the accelerator, two high energy particle beams travel at
 close to the speed of light before they collide. 
@@
 two tubes kept at ultrahigh vacuum. 
-By using of superconducting electromagnets that generates a powerful magnetic field, the beams are guided around the accelerator ring. 
+By using superconducting electromagnets that generate a powerful magnetic field, the beams are guided around the accelerator ring. 
 The electromagnets are built from coils of special electric cable that operates in a superconducting state, efficiently conducting electricity without resistance or loss of energy.
-For that, it is required to have magnets to a temperature of $‑271.3$ C.
+For that, it is required to have magnets at a temperature of $‑271.3$ C.
 To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}
@@
 \includegraphics[width=16cm,height=10cm]{Chapter1/cern.jpg}
-\caption[Large hadron collider from CERN]{Large hadron collider from CERN\cite{cern1}} \label{lhc}
+\caption[Large hadron collider from CERN]{CERN accelerator complex \cite{cern1}} \label{lhc}
 \end{figure}
@@
 \pagebreak
-Inside the detectors, collided protons generates an amount of particles such as pion and kaons, which are the most commons, created by the jet particles that were created after the collision.
-Besides of the particles created by the quarks of the proton, gluons are also radiated and create new particles and photons are radiated too.
+Inside the detectors, colliding protons generate an amount of particles such as pions and kaons, which are the most common, created by the jet particles that were produced after the collision.
+Besides the particles created by the quarks of the proton, gluons are also radiated and create new particles and photons are radiated too.
 During the collision time, the main detectors of LHC capture the energy 
@@
 The main objective of the LHC is to study the nature of electroweak symmetry breaking for the Higgs mechanism of the SM. 
-Alternatives to the Standard Model that involves different symmetries are also put on test.
-With the exploration of theses theories, people hope for a discovery that guide them toward a unified theory, so the importance to accelerate particles to higher energy scales.
+Alternatives to the Standard Model that involves different symmetries are also put to test.
+With the exploration of theses theories, people hope for a discovery that guides them towards a unified theory, so the importance to accelerate particles to higher energy scales.
 
@@
 \includegraphics[scale=0.5]{Chapter2/lum6.png}
-\caption[LHC schedule, including future plans for increase the center of mass energy and luminosity.
+\caption[LHC schedule, including future plans for increasing the center of mass energy and luminosity.
 The periods labeled LS are the maintenance periods]{LHC schedule, including future plans for increase the center of mass energy and luminosity.
@@
 \end{figure}
-From the figure \ref{lhc-lumi}, shows the Large Hadron Collider forecast for the increase of luminosity for the next years.
-Red dots are peak luminosity expected to reach and blue line is integrated luminosity.
+Figure \ref{lhc-lumi} shows the Large Hadron Collider forecast for the increase of luminosity for the next years.
+Red dots represent the expected peak luminosity and blue line shows the expected luminosity.
 In the year 2018, the maximum integrated luminosity is around 150 $fb^{-1}$\cite{cern3}.
-From 2019 to 2021 the second phase of maintenance, where engineers increase the performance of the accelerator, give maintenance to the system and introduce new components to the complex.
-After that period, the LHC starts new collision period at even higher energies in order to explore new particle phenomena.
+From 2019 to 2021 the second phase of maintenance will take place, where engineers increase the performance of the accelerator, give maintenance to the system and introduce new components to the complex.
+After that period, the LHC will start a new collision period at even higher energies in order to explore new particle phenomena.
 
@@
 The Compact Muon Solenoid (CMS) is a detector with multiple uses in the LHC and part of the main experiments at CERN.
-Located underground in the France- Switzerland border, in the city of Cessy, France.
-This detector was designed in the early 1990s, based on the mass limit of the Higgs boson, and put on operation in 2008, it has a big solenoid that generates a great magnetic field of 4 teslas with the objective to separate particles after a particle collision.
+It is located underground in the France- Switzerland border, in the city of Cessy, France.
+This detector was designed in the early 1990s, based on the mass limit of the Higgs boson, and put on operation in 2008.
+It has a big solenoid that generates a great magnetic field of 4 teslas with the objective of separating particles after a particle collision.
  The detector is 21 meters long, 15 meters wide, 15 meters high, it has a diameter of 5.9 m with a weight of 12000 ton.
@@
  The magnetic flux is returned via a 1.5 m thick iron yoke instrumented with four stations of muon
- chambers.
+ chambers. %Characteristics of the solenoid are shown in table \ref{tab:my_label}.
 
@@
 \end{figure}
-There are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easy, the complex is buried 100 meters underground.
+There are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easily, the complex is buried 100 meters underground.
 
@@
 The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter, a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
+All these parts are illustrated in figure \ref{cms}.
 
@@
 
- The objectives of the CMS experiment are numerous. One of them is
-identification of muons by measuring the momenta and scattering angle.
+ The objectives of the CMS experiment are numerous.
+One of them is the identification of muons by measuring the momenta and scattering angle.
 Muons can be produced in interesting events like Higgs, $W^{\pm}$ and $Z$ boson decays.%Search for evidence and give proof of super symmetry for show evidence of BSM (Beyond Standard Model).
@@
 The outer radius of the tracker is 110 cm, and its total length is 540 cm.
-The tracker coverage is $|\eta|<2.4$\footnote{$\eta$, called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$}.
+The tracker coverage is $|\eta|<2.4$\footnote{$\eta$, called pseudorapidity, is a coordinate where $\eta=-\ln{\tan{\frac{\theta}{2}}}$ with $\theta$ is the angle between the particle momentum $p$ and the direction of the beam axis}.
 
@@
 %The barrel section of the silicon tracker is divided in inner and outer barrel, where the inner section is shorter than outer barrel along with 3 inner disk between the transition region between barrel and endcap sections because avoids shallow track crossing angles.
-The Pixel endcap has 2 disks on each side placed at 34.6 and 46.5 cm in the z axis. Each disk covers radii from 6 to 15 cm and is divided into 24 blades with 7 modules each blade.
+The Pixel endcap has 2 disks on each side placed at 34.6 and 46.5 cm in the z axis. Each disk covers radii from 6 to 15 cm and is divided into 24 blades with 7 modules each.
 They are assembled in a turbine-like geometry that contains a total of 672 pixel modules. %with 7
@@
 The Strip Detector is divided in 4 sections: Tracker inner barrel (TIB), tracker outer barrel (TOB), tracker encap (TEC) and tracker inner disk (TID).
-The region that cover the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.
-The first two are composed of silicon sensors layers of 4 and 6 layers respectively.
-The TEC has 9 disk extending in the region 120 cm > $|z|$ > 280 cm.
+The region that covers the barrel section is $|z|<65$ cm for TIB and $|z|<110$cm for TOB.
+The first two are composed of silicon sensor layers of 4 and 6 layers respectively.
+The TEC has 9 disks extending in the region 120 cm > $|z|$ > 280 cm.
 The
@@
 
-The Strip Detector have almost 15 400 modules, mounted on
-carbon-fiber structures and housed inside by a temperature controlled outer support tube. The operating temperature must be around -$\ang{20}$C. 
+The Strip Detector has almost 15 400 modules, mounted on
+carbon-fiber structures and housed inside a temperature controlled outer support tube. The operating temperature must be around -$\ang{20}$C. 
 The total area of the pixel detector is around 1 $m^2$ and the silicon strips is 200 m$^2$. 
@@
 \end{figure}
-During the particle collision, it generates a lot of different particles that pass first through the inner tracker, interacting with the sensors layers and registering the particle path.
+The particle collision generates a lot of different particles that pass first through the inner tracker, interacting with the sensor layers and registering the particle path.
 By reconstructing the path of the particles, it is possible to generate a track, which allows to measure the momentum of the particle by calculating its curvature.
@@
 The most important objects of study are the momentum and the vertex (origin of the track).
-The efficiency of the tracker is estimated by using samples of muons and pions with $p_t$ of 1,10 and 100 GeV.
-For muons the efficiency of the tracker is shown in \ref{efi}
+The efficiency of the tracker is estimated by using samples of muons and pions with $p_t$ that is the transverse momentum (component of momentum transverse to beam line) of 1,10 and 100 GeV.
+For muons the efficiency of the tracker is shown in figure \ref{efi}
 \begin{figure}[ht]
@@
 
-The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillating crystals (emits light when particles interact with the crystal).
-These calorimeters are mounted in the central barrel and closed by 7324 crystals in the both endcaps.
+The electromagnetic calorimeter or ECAL is a calorimeter composed of 61200 lead tungstate (PbWO$_4$) crystals that act as scintillating crystals (emit light when particles interact with the crystal).
+These calorimeters are mounted in the central barrel and closed by 7324 crystals in both endcaps.
 The barrel section of the ECAL covers the range $|\eta| < 1.479$.
-The crystals in the barrel have a pyramid shape and their cross section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
+The crystals in the barrel have a pyramidal shape and their cross section is 22$\times$22 mm$^2$ at the front face and 26$\times$26 mm$^2$ at rear face.
 The crystal length is 230 mm.
-The EB (barrel section of ECAL) has a inner radius of 129 cm\cite{cms-manual}
+The EB (barrel section of ECAL) has an inner radius of 129 cm\cite{cms-manual}
 
-The endcaps cover have the range 1.479 < $|\eta|$ < 3.0. The distance between the interaction point and the endcap is 3.144 m. The endcap has identically shaped crystals grouped in
-mechanical units of 5×5 crystals. The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for front face cross section is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
+The endcaps cover the range 1.479 < $|\eta|$ < 3.0.
+The distance between the interaction point and the endcap is 3.144 m.
+The endcap has identically shaped crystals grouped in mechanical units of 5×5 crystals.
+The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for the face is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
+The ECAL is illustrated in figure \ref{ecal}.
 
@@
 \end{figure}
-In the barrel, there are photo detectors called avalanche photo diodes (APD), made of silicon with a active area of 5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.
-At the endcap, the photo detectors are vacuum photo diodes (VPT), made of with an anode of copper mesh (10 $\mu m$), allowing to operate in the magnetic field.
+In the barrel, there are photo detectors called avalanche photo diodes (APD), made of silicon with an active area of 5 $\times$ 5 mm$^2$ with 2 glued to the back of each crystal.
+At the endcap, the photo detectors are vacuum photo diodes (VPT), made of an anode of copper mesh (10 $\mu m$), allowing operation in the magnetic field.
 VPT have a size of 25 mm in diameter, glued to the back of each crystal.
@@
 The charged particles reach the crystals that provokes the photo diodes detect energy.
-The resolution of the ECAL is estimated by using a test beam and registering the energy signals. The resolution for electrons with energies of 120 GeV, it has obtained a resolution of 0.5$\%$.
+The resolution of the ECAL is estimated by using a test beam and registering the energy signals. The resolution for electrons with energies of 120 GeV is 0.5$\%$.
 
@@
 \subsection{Hadron calorimeter}
-The hadron calorimeter (HCAL) along the ECAL, form a complete calorimeter that allows to measure the jets and missing transverse energy.
+The hadron calorimeter (HCAL) together with the ECAL, form a complete calorimeter that allows to measure jets and missing transverse energy.
 HCAL is located in the barrel and the endcaps, surrounding the ECAL and affected by the magnetic field generated by the solenoid.
 The Barrel section (HB) and endcap section (HE) cover the pseudorapidity 0 < $|\eta|$ < 1.3 and 1.3 < $|\eta|$ < 3.0 respectively.
+Figure \ref{hcal} shows the structure of the HCAL.
 
@@
 Light of scintillator is collected by a single wave
-length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm to an outer radius of 2876.5 mm.
+length shifting fiber (WLS) for each scintillator tile. The wedge has a inner radius of 1777 mm and an outer radius of 2876.5 mm.
 
 HE is composed by brass absorber plates, with the thickness of 78 mm, and a total of 19 scintillator layers with a thickness of 3.7 mm. HE is sectioned in 5 in $\phi$ to match the barrel wedges.
-.
 %HO scintillators follow the HCAL barrel tower geometry in $\eta$ and angle $\phi$, that is, the geometry of the barrel muon system.
@@
 magnet coil that cover the region -1.26 < $|\eta|$ < 1.26.
-There is also a foward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
-steel absorber and embedded radiation hard quartz fibers, which collects 
+There is also a forward calorimeter (HF) located at 11.2 m from the interaction point, that cover the region of 2.9 < $|\eta|$ < 5. They are made of
+steel absorber and embedded radiation hard quartz fibers, which collect
 Cherenkov light\cite{cms-manual}.% that is when a charged particle travels through matter faster than light can, resulting in a blue light emmision of the material. 
@@
 
-The HCAL measures the energy of hadrons, such as the pions and kaons. 
+The HCAL measures the energy of hadrons, such as pions and kaons. 
 The energy resolution of the HCAL was estimated using a test beam of pions. For 100 GeV pions, the resolution obtained is 12$\%$.
@@
 The barrel detector is built with 4 layers of 250 chambers inside the magnet return yoke.\cite{cms-manual}
-The Muon Detector has three main subdetectors: the drift tubes chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
-The DT's, CSC's and RPC's are shown in the figure \ref{dt}.
+The Muon Detector has three main subdetectors: the drift tube chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
+The DT's, CSC's and RPC's are shown in figure \ref{dt}.
 
@@
 Those cells have a transverse size of 42 $\times$ 13 mm$^2$ with a 50 $\mu m$ diameter anode wire at the center that operates at voltages of over 3600 V.
-The gas used in this cells is a mix of Ar and CO$_2$ with a proportion of 85 $\%$ and 15 $\%$.
-There are 250 chambers in 4 layers inside the magnet return yoke, with radii of approximately 4.0, 4.9, 5.9 and 7.0 m from the beam axis and 12 sections covering 30$^\circ$ in $\phi$ each one.
+The gas used in this cells is a mix of Ar and CO$_2$ with a proportion of 85 $\%$ and 15 $\%$, respectively.
+There are 250 chambers in 4 layers inside the magnet return yoke, with radii of approximately 4.0, 4.9, 5.9 and 7.0 m from the beam axis and 12 sections covering 30$^\circ$ in $\phi$ each.
 
@@
 The CSC's are located in the endcap regions 0.9 < $|\eta|$ < 2.4. The CSC's are installed on the face of steel disks perpendicular to the beam. 
-Each CSC has a trapezoidal shape and consist of 6 gas gaps between 7 metal plates, where each gap contains copper cathode strips and anode wires running almost perpendicularly to
+Each CSC has a trapezoidal shape and consists of 6 gas gaps between 7 metal plates, where each gap contains copper cathode strips and anode wires running almost perpendicularly to
 the strips, with a diameter of 50 $\mu m$ separated by 3.16 mm. 
@@
 
-The RPC are located in the barrel and endcap regions that covers the range o $|\eta|<1.6$. The main purpose is to trigger events with muons. 
+The RPC are located in the barrel and endcap regions that covers the range of $|\eta|<1.6$. The main purpose is to trigger events with muons. 
 RPC's are structured with a double gas filled gap and readout strips between the gaps

### 2019-11-23 tesis_hiram/Chapter3/chapter3.tex
correccion
n
p

@@
 \chapter{Event reconstruction and selection}
-During the proton collision, many types of processes happen whose information are saved in the CMS data storage system.
+During the proton collision, many types of processes happen whose information is saved in the CMS data storage system.
 But the events are only saved if they fulfill certain conditions compatible with the signal.
 For the tH process, the search is based on the presence of a pair of muons with the same sign.
-The rest of the processes that also generates a pair of muons with the same sign will be considered backgrounds.
+The rest of the processes that also generate a pair of muons with the same sign will be considered backgrounds.
 \section{Signal Event Topology} 
@@
 This is the main process that generates events with two same sign muons.
-The tH process topology is shown in the figure \ref{jet}.\\
+The tH process topology is shown in  figure \ref{jet}.
 
@@
 Additional jets or leptons can be generated from the other $W$ boson.
-\\
 
@@
 %In graphics, these low probability processes would be very small figures that barely manifest.
-
+\pagebreak
 %For the tH process, the largest contribution comes from Higgs decays to WW (about 75$\%$), followed
@@
 
-	\begin{figure}[!htbp]
+	\begin{figure}[ht]
 		\centering
-		\includegraphics[scale=0.9]{Chapter1/jet.png}
+		\includegraphics[scale=1]{Chapter1/jet.png}
 		\caption{Topology of $t$H process which generates two same sign muons, a forward jet and a b-jet.} 
@@
 The hadronization results in a jet of particles.
-
-\pagebreak
-
-\section{Backgrounds}
-Several processes contribute to the background in this search:
-\begin{itemize}
-		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muons comes from a top and the other comes from the vector boson.
-			\item $\bm{W^{+}Z}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
-		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
-		\item $\bm{tZq}$: Processes with single top quarks associated with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
-	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
-	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
-		\item$\bm{W^{+}W^{-}Z}$, $\bm{ZZZ}$ and $\bm{W^{+}ZZ}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
-	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
-	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
-			\item $\bm{t\bar{t}H}$: This Higgs production mechanism is considered a background in this analysis. The muons in this cases comes from one top and Higgs decays. 
-	\item $\bm{Fakes}$:This background refers to events where two muons come from $b$ meson decays in jets.
-\end{itemize}
-Table \ref{back} show the decay chains and production cross section for background.
-Due to small expected event yields, the processes $W^\pm$ $W^\pm$,$tZq$,$t\bar{t}t\bar{t}$ $VVV$, $tZW^+$ and $ZZ$ are grouped as one called Rares in the results below.
-
-\pagebreak
-
-\begin{table}[!ht]
+\begin{table}[ht]
 	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
@@
 
-\begin{table}[!ht]
+\pagebreak
+
+\section{Backgrounds}
+Several processes contribute to the background in this search:
+\begin{itemize}
+		\item $\bm{t\bar{t}W^{\pm}}$ and $\bm{t\bar{t}Z}$ $\bm{(t\bar{t}V)}$: One muon comes from a top and the other comes from the vector boson.
+			\item $\bm{W^{+}Z}$: Diboson production with leptonic decays. One muon comes from $W$ boson and the other from $Z$ boson.
+		\item $\bm{W^{\pm}W^{\pm}}$:A pair of same sign $W$ bosons generate a muon each one.
+		\item $\bm{tZq}$: Processes with single top quarks associated with a Z boson, where $Z\rightarrow \mu^+ \mu^-$, also contribute to the background.
+	\item $\bm{t\bar{t}t\bar{t}}$:In these type of events, one $t$ decays to $Wb$ and $W$ decays to a muon. The second muon comes from the other top decay.
+	%Backgrounds are estimated directly from simulated events$\%$ which are corrected for data/MC differences and $\%$ inefficiencies in the same way as signal events. 
+		\item$\bm{W^{+}W^{-}Z}$, $\bm{ZZZ}$ and $\bm{W^{+}ZZ}$ ($\bm{VVV}$): The leptonic decays of the $W$ or $Z$ bosons generate at least two same sign muons.
+	\item $\bm{tZW^{+}}$:One muon comes from the $Z$ while the other same sign muon can come from $t$ or $W$. 
+	\item $\bm{ZZ}$: Each muon comes from $Z$ boson decays.
+			\item $\bm{t\bar{t}H}$: This Higgs production mechanism is considered a background in this analysis. The muons in this case comes from one top and Higgs decays. 
+	\item $\bm{Fakes}$:This background refers to events where two muons come from $b$ meson decays in jets.
+\end{itemize}
+Table \ref{back} shows the decay chains and production cross sections for the backgrounds.
+Due to small expected event yields, the processes $W^\pm$ $W^\pm$,$tZq$,$t\bar{t}t\bar{t}$, $VVV$, $tZW^+$ and $ZZ$ are grouped as one called Rares in the results below.
+
+\begin{table}[ht]
 	\caption{Main backgrounds and their same sign $\mu\mu$ decay process }
@@
 %background contribution comes from WZ production.
-\pagebreak
 
@@
 	\item The events must contain two muons with the same sign.
-	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
+	\item Transverse momentum $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
 	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
@@
 For the SM signal $tH$, the number of expected events is 2.14, while for the inverted coupling scenario ($k_t=-1$) the cross section is enhanced by a factor of approximately 10.
-This event yields will be used to estimate the signal sensitivity.
-The yields include statistical uncertainties due to the simulated samples using Monte Carlo (MC) samples and systematic uncertainties are described in table \ref{tth-table}.
+These event yields will be used to estimate the signal sensitivity.
+The yields include statistical uncertainties due to the  Monte Carlo (MC) samples and systematic uncertainties as described in table \ref{tth-table}.
 
-\section{Systematic uncertanties}
-\begin{itemize}
-\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
-\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
-\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
-\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
-\end{itemize}
-
-%control region: event selection with 3 leptons for compare simulation with real data. yield difference in that region is 50. Is taken and for wz is 50
-%selection that allows to isolate a background respect to other backgrounds, that background allows to compare with real data
-
-\pagebreak
-%The fake rate corresponds to non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks).
-But due to jet signature is reconstructed as leptons, some particular signatures or errors in reconstruction, passed as leptons and then they called fakes leptons.
-Rare SM is a group of other processes: t$\bar{t}$t$\bar{t}$,WWW,WWZ,WZZ,WW,$t$Zq.
-Due to low number of events, they grouped the events as one histogram.
-\section{Multivariable discriminant}
-Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminant, which separates signal from backgrounds, is necessary to optimize the signal sensitivity.
-The multivariable discriminant is a Boosted Decision Tree (BDT) that takes a set of input features and splits input data recursively based on those features.
-The features can be a mix of categorical and continuous data.
-The BDT training is performed using several event variables.
-\\
-
-In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds.
-The variables used for the BDT were the following:
-
-\begin{itemize}
-\item Number of jets with pT > 25 GeV, $|\eta|$ < 2.4
-\item Maximum $|\eta|$ of forward jet
-\item Sum of lepton charges
-\item Number of jets with $|\eta|$ > 1.0
-\item $\Delta\eta$ between forward jet and b-jet with highest $p_t$
-\item $\Delta\eta$ between forward jet and b-jet with lower $p_t$
-\item $\Delta\eta$ between forward jet and closest muon
-\item $\Delta\phi$ of highest $p_t$ same-sign muon pair
-\item min $\Delta$R (muon pairs)\footnote{$\Delta R = \sqrt{ \Delta\eta^2 + \Delta\phi^2}$, where $\Delta R$ is the distance in the $\eta \phi$ plane}
-\item $p_t$ of muon with lower momentum
-\end{itemize}
-
-Figure \ref{bdt2} shows the BDT distribution for signal and backgrounds.
-\pagebreak
-%Closure: hay jets en los eventos de tt (gluon-gluon -> tt + gluon ) que se pasan como muones. jet -> muon = fake
-
-%Fakes: proceso de QCD que genera muchos jets (por ejemplo gluon-gluon -> gluons, quarks) : jet -> muons fakes are estimated data
-
-%bdt trained with fakes is not possible, due no simulation with that process
-
-\begin{table}[ht!]
+\begin{table}[ht]
 	\centering
@@
 
-\begin{figure}[!htbp]
+\pagebreak
+
+\section{Systematic uncertanties}
+\begin{itemize}
+\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
+\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
+\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
+\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
+\end{itemize}
+
+%control region: event selection with 3 leptons for compare simulation with real data. yield difference in that region is 50. Is taken and for wz is 50
+%selection that allows to isolate a background respect to other backgrounds, that background allows to compare with real data
+
+\pagebreak
+%The fake rate corresponds to non-prompt leptons.% Non prompt leptons are leptons that passed the selection, and usually comes from decays from b-jets (hadronized quarks).
+But due to jet signature is reconstructed as leptons, some particular signatures or errors in reconstruction, passed as leptons and then they called fakes leptons.
+Rare SM is a group of other processes: t$\bar{t}$t$\bar{t}$,WWW,WWZ,WZZ,WW,$t$Zq.
+Due to low number of events, they grouped the events as one histogram.
+\section{Multivariable discriminant}
+Due to small signal to background ratio caused by the small cross section of $tH$, a multivariable discriminant, which separates signal from backgrounds, is necessary to optimize the signal sensitivity.
+The multivariable discriminant is a Boosted Decision Tree (BDT) that takes a set of input features and splits input data recursively based on those features\cite{tmva}.
+The features can be a mix of categorical and continuous data.
+The BDT training is performed using several event variables.
+
+In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds.
+The variables used for the BDT were the following:
+
+\begin{itemize}
+\item Number of jets with $p_t$ > 25 GeV, $|\eta|$ < 2.4
+\item Maximum $|\eta|$ of forward jet
+\item Sum of lepton charges
+\item Number of jets with $|\eta|$ > 1.0
+\item $\Delta\eta$ between forward jet and b-jet with highest $p_t$
+\item $\Delta\eta$ between forward jet and b-jet with lower $p_t$
+\item $\Delta\eta$ between forward jet and closest muon
+\item $\Delta\phi$ of highest $p_t$ same-sign muon pair
+\item min $\Delta$R (muon pairs)\footnote{$\Delta R = \sqrt{ \Delta\eta^2 + \Delta\phi^2}$, where $\Delta R$ is the distance in the $\eta \phi$ plane}
+\item $p_t$ of muon with lower momentum
+\end{itemize}
+
+Figure \ref{bdt2} shows the BDT distribution for signal and backgrounds.
+\pagebreak
+%Closure: hay jets en los eventos de tt (gluon-gluon -> tt + gluon ) que se pasan como muones. jet -> muon = fake
+
+%Fakes: proceso de QCD que genera muchos jets (por ejemplo gluon-gluon -> gluons, quarks) : jet -> muons fakes are estimated data
+
+%bdt trained with fakes is not possible, due no simulation with that process
+
+\begin{figure}[ht]
 	\centering
-	\begin{minipage}[b]{0.48\textwidth}
+	\begin{minipage}[b]{0.6\textwidth}
 		\includegraphics[width=\textwidth]{Chapter3/kos.png}
@@
 	\hfill
-	\begin{minipage}[b]{0.48\textwidth}
+	\begin{minipage}[b]{0.6\textwidth}
 		\includegraphics[width=\textwidth]{Chapter3/kos2.png}

### 2019-11-23 tesis_hiram/Chapter4/chapter4.tex
n
p

@@
 	To estimate the sensitivity of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one.
-The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.
+The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events\cite{asimov}.
 The uncertainty of the signal strength is estimated by applying a fit to the Asimov dataset, where the model is constructed from the sum of the individual backgrounds and signal.
@@
 The package ROOFIT is used here, because of its implementations of modeling probability distributions and statistical tools\cite{roofit}.
-In the figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models.
+Figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models.
 
@@
 	As mentioned before, for the $k_t$=-1 the number of events for signal is more than ten times compared to SM.
-This improves the sensitivity to the signal.
+This improves the sensitivity of the signal.
 Due to the small number of signal events the uncertainty for the SM is large compared to the $k_t$=-1 scenario, where the uncertainty is around 50$\%$.
@@
 
-	In the Table \ref{parameters}, shows the $\mu$ and $\alpha$ parameters.
+ Table \ref{parameters}, shows the $\mu$ and $\alpha$ parameters.
 For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.
-After the fit, $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't changed for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't changed.
+After the fit, $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't change for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't change.
 
@@
 	In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in Fig. \ref{chi}, where $\alpha$=0.05 in this case. 
-	It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in \ref{scanl}.
+	It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in figure \ref{scanl}.
 In the SM case, the scan has a wider shape in comparison to the $k_t$=-1.
@@
 	Using the above technique, we find an expected upper limit $\mu < $17.0 for SM model and $\mu < $ 2.3 for $k_t$=-1 model. 
+		\begin{figure}[ht]
+		\centering
+		\begin{minipage}[b]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
+		\end{minipage}
+		\hfill
+		\begin{minipage}[b]{0.49\textwidth}
+			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
+		\end{minipage}
+		\caption{Likelihood scan for SM (up) and $k_t$=-1 (Down).}
+		\label{scanl}
+	\end{figure}
 	\pagebreak
 	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
-	\section{Extrapolation for higher luminosities}
+	\section{Extrapolation to higher luminosities}
 	In the past section, it was shown that the signal strength with an integrated luminosity of 35.9 fb$^{-1}$ is not significant.
-The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 finished in 2018.
-Run 3 that starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for finally the high luminosity phase of LHC, is expected to collect 3000 fb$^{-1}$.
-Therefore, is interesting to study the sensitivity of the signal strength to higher luminosities.
+The LHC has already collected data for integrated luminosity of 150 fb$^{-1}$ for run 2 which finished in 2018.
+Run 3 starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for the high luminosity phase of LHC, expected to collect 3000 fb$^{-1}$.
+Therefore, it is interesting to study the sensitivity of the signal strength at higher luminosities.
 	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
@@
 
-	In the figures \ref{hm}, it is shown an estimated prediction of the signal and background events for higher luminosities.
-As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in the chapter 1.
+	In figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosities is shown.
+As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in Chapter 1.
 But even with the increase of number of events, the statistical uncertainty of the data is too large with respect to the expected signal.
@@
 
-	The same method is used for the model $k_t$=-1 in the figure \ref{hm1}.
+	The same method is used for the model $k_t$=-1 in figure \ref{hm1}.
 In this case, the number of events for the signal is more appreciable in comparison with the SM model.
@@
 Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.
-	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results; upper limits in this models are small.
+	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results.
 This is caused by the fact that the number of events for the $tH$ signal is greater.
@@
 		\centering
-		\includegraphics[scale=0.65]{Chapter4/chi_squared.png}
+		\includegraphics[scale=0.5]{Chapter4/chi}
 		\caption{Illustration of the $\chi^2$ distribution with number of degrees of freedom of 7 used for the limit estimation}
@@
 
-	\begin{figure}[ht]
-		\centering
-		\begin{minipage}[b]{0.7\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
-		\end{minipage}
-		\hfill
-		\begin{minipage}[b]{0.7\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
-		\end{minipage}
-		\caption{Likelihood scan for SM (up) and $k_t$=-1 (Down).}
-		\label{scanl}
-	\end{figure}
 	\pagebreak

### 2019-11-23 tesis_hiram/Chapter5/chapter5.tex
n
p

@@
 \chapter{Conclusion and outlook}
-In this work, we explored the sensitivity to the production process of Higgs plus single top.
-The $tH$ process is interesting channel in proton-proton collisions in the LHC.
+In this work, we explored the sensitivity of the production process of Higgs plus single top.
+The $tH$ process is an interesting channel in proton-proton collisions in the LHC.
 This process has not been observed experimentally.
@@
 Using information from this dataset, we studied the expected sensitivity using an Asimov data and systematic uncertainties for the final state with same sign pairs of muons.
-\\
 
@@
 For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$, this is due to the larger expected number of signal events
-\\
 
@@
 We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit on $\mu$ is placed at 4.3.
-In the case of the inverted coupling scenario, a possible signal can be observed with an uncertainty of 10$\%$ at 3000 fb$^{-1}$.\\
+In the case of the inverted coupling scenario, a possible signal can be observed with an uncertainty of 10$\%$ at 3000 fb$^{-1}$.
 

### 2019-11-23 tesis_hiram/Chapter1/chapter1.tex
n

@@
 %Leptons have their respective antiparticle; same structure with opposite charge.
- All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$\cite{griff}.% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless.
+ All of them have a spin (intrinsic angular momentum) of $\frac{1}{2}$\cite{griff}.
+% In case of neutrinos, so far experimentalists have found these have very small masses, but in the theoretical scheme, they are massless.
 \\
@@
 Quarks cannot be found in isolation, they always exist in form of hadrons that can be mesons or baryons.
-Mesons are bosons made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).
+Mesons are made up of a quark-antiquark pair, such as pion ($\pi$) and kaon ($K$).
 Mesons were theorized by Yukawa in 1937 and discovered in 1947 by Powell\cite{griff}.
-Baryons are fermions made of 3 quarks.
+Baryons are made of 3 quarks.
 Examples of baryons are protons and neutrons.
@@
     \includegraphics[scale=0.3]{Chapter1/sm1.png}
-    \caption[Standard Model to date]{Standard Model to date \protect \footnotemark}
+    \caption[Standard Model to date]{Standard Model to date\cite{smtable}}
     \label{sm1}
@@
 \end{center}
- \footnotetext{Taken from \url{https://upload.wikimedia.org/wikipedia/commons/0/00/Standard_Model_of_Elementary_Particles.svg}} 
 The last group of the family are the bosons, which have either spin 1 or 0. 
@@
 
-There are experiments that detect particles around the world, such as the large hadron collider (LHC) in Europe, the Fermilab in United States of America, KEK in Japan, etc.
+There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc.
 More information about the LHC will be described in the next chapters.
@@
 		\includegraphics[scale=0.35]{Chapter1/sm.png}
-		\caption{Particle interactions in Standard model \footnote{Taken from \url{https://commons.wikimedia.org/wiki/File:Elementary_particle_interactions_in_the_Standard_Model.png}.
-Created by Eric Drexler.}}
+		\caption[Particle interactions in Standard model]{Particle interactions in Standard model\cite{smi}}
 		\label{sm}
@@
 Maskawa in 1973 to explain observed CP violations in Kaon decay\cite{griff}.
-In 1995, in the Tevatron at Fermilab in Illinois, the top quark was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
+In 1995, in the Tevatron at Fermilab in Illinois, the top quark was discovered via proton antiproton collisions with center of mass energy between 1.8 to 1.96 TeV in the CDF and D0 experiments.
+The top quark production process was via ggF, which generated a pair of $t\bar{t}$\cite{top}.
 Since then, the properties of the top quark have been studied at the Tevatron Collider at Fermilab, and by the ATLAS and CMS experiments at the Large Hadron Collider (LHC) at CERN.

### 2019-11-23 tesis_hiram/Chapter2/chapter2.tex
n

@@
 
-The Large Hadron Collider (LHC) is the largest and most powerful particle accelerator in the world.
+The LHC is the largest and most powerful particle accelerator in the world.
 It came on operation on 10 September 2008 and it is the most recent addition from the European Organization for Nuclear Research (CERN).
@@
 At point 5 is another general purpose detector: the compact muon solenoid (CMS).
-A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7.\cite{cern1,cern2}
+A particle detector optimized for heavy ion physics, ALICE, is located at Point 2 and LHCb, a detector designed for B physics, is located at Point 7\cite{cern1,cern2}.
 
@@
 For that, it is required to have magnets at a temperature of $‑271.3$ C.
-To reach such temperatures, a system of liquid helium is connected to the accelerator.\cite{cern2}
+To reach such temperatures, a system of liquid helium is connected to the accelerator\cite{cern2}.
 
@@
 After this stage, the beam is ready to be injected into
-the LHC through one of two injection lines with 6.5 TeV.\cite{cern3}
+the LHC through one of two injection lines with 6.5 TeV\cite{cern3}.
 
-\begin{table}[ht]
-\centering
-	\caption[Accelerator operation energies]{Accelerator operation energies\cite{cern3,cern1}}
-	\begin{tabular}{|c|c|}
-		\hline
-		Accelerator & Energy \\
-		\hline
-		Linac 2 & 50 MeV \\
-		\hline
-		PS Booster & 1.4 GeV \\
-		\hline
-		Proton Scyncroton (PS) & 25 GeV\\
-		\hline
-		SPS & 450 GeV\\
-		\hline
-		LHC & 6.5 TeV\\
-		\hline
-	\end{tabular}
-\end{table}
+%\begin{table}[ht]
+%\centering
+%	\caption[Accelerator operation energies]{Accelerator operation energies\cite{cern3,cern1}}
+%	\begin{tabular}{|c|c|}
+%		\hline
+%		Accelerator & Energy \\
+%		\hline
+%		Linac 2 & 50 MeV \\
+%		\hline
+%		PS Booster & 1.4 GeV \\
+%		\hline
+%		Proton Scyncroton (PS) & 25 GeV\\
+%		\hline
+%		SPS & 450 GeV\\
+%		\hline
+%		LHC & 6.5 TeV\\
+%		\hline
+	%\end{tabular}
+%\end{table}
 \pagebreak
@@
 One of them is the identification of muons by measuring the momenta and scattering angle.
-Muons can be produced in interesting events like Higgs, $W^{\pm}$ and $Z$ boson decays.%Search for evidence and give proof of super symmetry for show evidence of BSM (Beyond Standard Model).
+Muons can be produced in interesting events like Higgs, $W^{\pm}$ and $Z$ boson decays.
+%Search for evidence and give proof of super symmetry for show evidence of BSM (Beyond Standard Model).
 Detection of massive vector bosons $W^\pm$ and Z via $e^+e^-$ and $\mu^+ \mu^-$ decays.

### 2019-11-23 tesis_hiram/Chapter3/chapter3.tex
n

@@
 	\end{minipage}
-\caption[Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right)]{Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right) \cite{th1}}
+\caption[Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right)]{Distribution of BDT discriminant for signal and background in the case of SM (Up) and inverted coupling scenario (Down) \cite{th1}}
 \label{bdt2}

### 2019-11-23 tesis_hiram/Chapter4/chapter4.tex
n

@@
 	$q$ is a random variable with a $\chi^2$ distribution \cite{asimov}.
-	In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in Fig. \ref{chi}, where $\alpha$=0.05 in this case. 
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[scale=0.5]{Chapter4/chi}
+		\caption{Illustration of the $\chi^2$ distribution %with 7 degrees of freedom 
+			used for the limit estimation}
+		\label{chi}
+	\end{figure}
+
+In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in figure \ref{chi}, where $\alpha$=0.05 in this case.
 It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in figure \ref{scanl}.
@@
 		\begin{minipage}[b]{0.49\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/Likelihood.png}
+			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/Likelihood.png}
 		\end{minipage}
@@
 		\begin{minipage}[b]{0.49\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/Likelihood-kt-1.png}
+			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/Likelihood-kt-1.png}
 		\end{minipage}
-		\caption{Likelihood scan for SM (up) and $k_t$=-1 (Down).}
+		\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
 		\label{scanl}
@@
 
-	However, the uncertainty of $\mu$ for the SM case is 170$\%$ for  in the 3000 fb$^{-1}$ case, making impossible to get an evidence of a Higgs boson in the $tH$ process for the same sign muon channel.
-Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.
-	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results.
-This is caused by the fact that the number of events for the $tH$ signal is greater.
-For 3000 fb$^{-1}$ the uncertainty on $\mu$ is $~10\%$, and it has an upper limit that rounds between 0.9-1.1.
-In the likelihood scan, the statistical test $q$ gets very high values at $\mu$>1.1.
-This indicates that for large integrated luminosities this model can be fully ruled out.
-This can be visualized in the likelihood scan of  3000 fb$^{-1}$, where the curve is very closed and values of $q$ are very high, giving incompatibility of the model with data.
-
 		\begin{table}[ht]
@@
 
-		\begin{figure}[ht]
-		\centering
-		\includegraphics[scale=0.5]{Chapter4/chi}
-		\caption{Illustration of the $\chi^2$ distribution with number of degrees of freedom of 7 used for the limit estimation}
-		\label{chi}
-	\end{figure}
+	However, the uncertainty of $\mu$ for the SM case is 170$\%$ for  in the 3000 fb$^{-1}$ case, making impossible to get an evidence of a Higgs boson in the $tH$ process for the same sign muon channel.
+Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.
+	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results.
+This is caused by the fact that the number of events for the $tH$ signal is greater.
+For 3000 fb$^{-1}$ the uncertainty on $\mu$ is $~10\%$, and it has an upper limit that rounds between 0.9-1.1.
+In the likelihood scan, the statistical test $q$ gets very high values at $\mu$>1.1.
+This indicates that for large integrated luminosities this model can be fully ruled out.
+This can be visualized in the likelihood scan of  3000 fb$^{-1}$, where the curve is very closed and values of $q$ are very high, giving incompatibility of the model with data.
 
@@
 		\hfill
-		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/150fb/Likelihood.png}
+		\begin{minipage}[b]{0.5\textwidth}
+			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/150fb/Likelihood.png}
 		\end{minipage}
@@
 		\hfill
-		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/300fb/Likelihood.png}
+		\begin{minipage}[b]{0.5\textwidth}
+			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/300fb/Likelihood.png}
 		\end{minipage}
@@
 		\hfill
-		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/3000fb/Likelihood.png}
+		\begin{minipage}[b]{0.5\textwidth}
+			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/3000fb/Likelihood.png}
 		\end{minipage}
@@
 		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/kt-1/150fb/Likelihood.png}
+			\includegraphics[width=\textwidth,,height=0.31\textheight]{Chapter4/kt-1/150fb/Likelihood.png}
 		\end{minipage}
@@
 		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/kt-1/300fb/Likelihood.png}
+			\includegraphics[width=\textwidth,height=0.31\textheight]{Chapter4/kt-1/300fb/Likelihood.png}
 		\end{minipage}
@@
 		\begin{minipage}[b]{0.48\textwidth}
-			\includegraphics[width=\textwidth]{Chapter4/kt-1/3000fb/Likelihood.png}
+			\includegraphics[width=\textwidth,,height=0.31\textheight]{Chapter4/kt-1/3000fb/Likelihood.png}
 		\end{minipage}

### 2019-11-24 tesis_hiram/Abstract/abstract.tex
correccion

@@
 % Use `abstract' as an option in the document class to print only the titlepage and the abstract.
-%\begin{center}
-%	\justifying
+
 We present a study on the production of a Higgs boson plus a single top quark ($tH$) in same sign dimuon channel $\mu^\pm \mu^\pm$ using data published by the CMS experiment at CERN. By studying this
@@
 The sensitivity is also studied for the model with inverted Yukawa coupling $k_t$=-1, where $k_t$ is the top-Higgs coupling parameter modifier, for comparison with the Standard Model.
-%\end{center}
+For the SM, we obtained an upper limit of 17 on the signal strength with a confidence level of 95$\%$ with respect to the expected value using an integrated luminosity of 35.9 fb$^{-1}$, while with 3000 fb$^{-1}$ we obtained an upper limit of 4.3.
+In the modified model with $k_t$=-1, we obtained an upper limit of 2.3 using 35.9 fb$^{-1}$, while in the 3000 fb$^{-1}$ case a possible signal could be measured with an uncertainty of 10$\%$.

### 2019-11-24 tesis_hiram/Abstract/resumen.tex
correccion

@@
 La sensibilidad de la se\~nal es tambi\'en estudiada para el modelo con acoplamiento de Yukawa invertido $k_t$=-1, donde $k_t$ es el modificador del par\'ametro de acoplamiento de top-Higgs, en comparaci\'on con el Modelo Est\'andar.
+Para el modelo SM, se obtuvo un l\'imite de 17 en la fuerza de la se\~nal a un nivel de confianza de 95$\%$ con respecto al valor esperado usando 35.9 fb$^{-1}$ de luminosidad integrada, mientras que con 3000 fb$^{-1}$ se obtiene un l\'imite de 4.3.
+Para el modelo modificado con $k_t$=-1, se obtiene un l\'imite de 2.3 usando 35.9 fb$^{-1}$ , mientras que con 3000 fb$^{-1}$  se podr\'ia medir la fuerza de una posible se\~nal con 10$\%$ de incertidumbre.
 %\end{center}

### 2019-11-24 tesis_hiram/Chapter1/chapter1.tex
n
correccion

@@
 Particle physics is a field of physics that studies the particles that create matter and their interactions to very small scale, even smaller than atoms. 
-The particles analyzed in particle physics are the fundamental particles that compose matter and the responsible for all forces of nature.
+Particle physics studies the fundamental building blocks of matter (fermions) and their interactions via force carriers (bosons). 
+%The particles analyzed in particle physics are the fundamental particles that compose matter and the responsible for all forces of nature.
 All those particles and their properties are grouped in a theory called the Standard Model (SM).
@@
 
-In recent years, there have been many studies in the Higgs boson production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}$H and people have obtained consistent results in the search of the Higgs boson in those processes.
+In recent years, there have been many studies of Higgs production processes at CERN in pp collisions, such as gluon fusion (ggF), VBF, WH, ZH and $t\bar{t}H$. 
 In this work, we will analyze the production of a Higgs boson in association with a
@@
 George Zweig in 1964.
-They were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until scattering experiments at the Stanford Linear Accelerator Center in 1968\cite{griff}.
+They were introduced as parts of an ordering scheme for hadrons, and there was little evidence for their physical existence until fixed target scattering experiments were conducted at the Stanford Linear Accelerator Center in 1968\cite{griff}.
 There are 6 of them: up (1968), down (1968), strange (1968), charm (theorized in 1970, discovered 1974), bottom (theorized 1973, discovered 1977), top (theorized 1973, discovered 1995).
@@
 There are 5 bosons: $W^{\pm}$, $Z$ with neutral charge are responsible for weak force; photon, a massless particle, is responsible for the electromagnetic force; gluons which are also massless, is related to the strong force and Higgs boson, recently discovered, is in charge of giving the property of mass to particles via the Higgs mechanism.
-Bosons let other particles interact, even themselves, which is shown in figure \ref{sm}.
+Bosons let other particles interact, even themselves, which is shown in Figure \ref{sm}.
 The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluons can only interact with quarks and with itself.
-Those bosons act as mediators in decays and creation of complex
-particles, as mesons and baryons.
+%Those bosons act as mediators in decays and creation of complex
+%particles, as mesons and baryons.
+
 %In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force.
@@
 
-There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc.
+%There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc.
 More information about the LHC will be described in the next chapters.
@@
 \begin{table}[htp]
-\caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of $v$=0.998c)\cite{pd}.}
+\caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of $v$=0.998c)\cite{pd}.
+In the case of $s$,$c$ and $b$ quarks, the lifetime corresponds to the K$^\pm$, D$^{\pm}$ and B$^{\pm}$ meson lifetime.}
 \renewcommand{\arraystretch}{1.5}
@@
 	\hline 
-Up quark ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
+Up quark ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & Stable & -\\ 
 	\hline 
@@
 	\hline 
-Strange quark ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
+Strange quark ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.2 \times 10^{-8}$ & 58.7 \\ 
 	\hline 
-Bottom quark ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
+Bottom quark ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.6 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
 	\hline 
-$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
+$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.4$\times 10^{-15}$\\ 
 	\hline 
-$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
+$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.4$\times 10^{-15}$ \\ 
 \hline
@@
 	\hline 
-Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
+Higgs ($H$)	& 125.18 &0 & 0& 1.5 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
 	\hline 
@@
 	\hline 
-$\nu_e$, $\nu_\mu$, $\nu_\tau$& 2 $\times$ 10$^{-6}$ & 0 & $\frac{1}{2}$ & Stable & -\\
+$\nu_e$, $\nu_\mu$, $\nu_\tau$&  $<$ 2.0 $\times$ 10$^{-6}$ & 0 & $\frac{1}{2}$ & Stable & -\\
 	\hline 
@@
 Richard Hagen, and Tom Kibble in separate groups.
-They formulated the Higgs mechanism that explains the generation of mass for the particles.
-
-The theory also explains Higgs bosons give the mass to the particles via the Higgs Field and the mass of the Higgs boson itself.
-The Higgs boson was discovered recently on year 2012 in the experiments ATLAS and CMS at CERN.
-The experiment was conducted using proton-proton collisions with center of mass energy of 7 and 8 TeV, where investigators worked on the data and detecting various decay modes that generates final states such as WW, $\gamma \gamma$, ZZ, b$\bar{b}$ and $\tau \tau$ \cite{higgsd,Aad_2012}.
+They formulated the Higgs mechanism that explains the generation of mass for the fermions and massive bosons.
+The Higgs boson was discovered recently in year 2012 in the experiments ATLAS and CMS at CERN.
+The experiment was conducted using proton-proton collisions with center of mass energy of 7 and 8 TeV, where investigators analyzed the data in the $\gamma \gamma$ and $ZZ$ final states\cite{higgsd,Aad_2012}.
 The mass of this boson has been measured and its production and decay
@@
  \end{align}
-where the F and G are 
+where the F and G are\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
+	+1 \quad \text{for even permutation} \\
+	-1 \quad \text{for odd permutation}\\
+	0 \quad \text{i=j, or j=k, or k=i } 
+	\end{dcases}$.} 
 \begin{align}
@@
 \end{align}
-$W^i$ (i=1,2,3) are three SU(2) gauge bosons, B is a U(1) gauge boson and $g$  is a couping constant for $W$ gauge boson.\footnote{$\epsilon^{ijk}$ represents the Levi-Civita tensor, where $\epsilon^{ijk}= \begin{dcases}
-	+1 \quad \text{for even permutation} \\
-	-1 \quad \text{for odd permutation}\\
-	0 \quad \text{i=j, or j=k, or k=i } 
-	\end{dcases}$.} In the end, those gauge bosons, after introducing the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
+$W^i$ (i=1,2,3) are three SU(2) gauge bosons, B is a U(1) gauge boson and $g$  is a couping constant for $W$ gauge boson.
+In the end, a superposition of these gauge bosons, after introducing the Higgs mechanism, become the $W^\pm$, $Z$ and $\gamma$ vector boson
 \cite{ew1,ew2}. %Z bosons and photons will be formed by a combination of W and B fields.\\
@@
     \end{tikzpicture}
-    \caption{Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu^2<0$ and $\lambda>0$ also called the mexican hat potential.}
+    \caption{Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu^2<0$ and $\lambda>0$}
     \label{hat}
@@
 \end{align}
-from the coeficients, we get the $W$ and $Z$ mass 
+from the coefficients, we get the $W$ and $Z$ mass 
 \begin{align}
@@
 %\end{align}
-The last part of the lagrangian is the Yukawa lagrangian
-\begin{align}
-\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
-\end{align}
-The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between Higgs doublet $\Phi$ and the fermions.\footnote{Here $
+The last part of the lagrangian is the Yukawa lagrangian\footnote{Here $
 	\tilde{\Phi}=i\sigma^2 \Phi^\dagger =\left(\begin{array}{c}
@@
 	% \Phi =\sqrt{-\frac{\mu^2}{2\lambda}}=\frac{v}{\sqrt{2}}  \qquad \lambda >0
-	$ is necessary for the correct transformation in the case of up quarks. 
-h.c refers to hermitian conjugate terms. } The indices m and n mean sum over the families. 
+	$ is necessary for the correct transformation in the case of up-type quarks. 
+	h.c refers to hermitian conjugate terms. } 
+\begin{align}
+\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
+\end{align}
+The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between Higgs doublet $\Phi$ and the fermions. The indices m and n mean sum over the families. 
 %It is required to have two representations of Higgs fields
 %with $Y=\frac{1}{2}$ and $\frac{1}{2}$ to give masses to quarks and electrons.
-By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
+By using \ref{vmin} on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
 \begin{align*}
@@
 \includegraphics[scale=0.5]{Chapter1/pg.png}
-\caption[Different Higgs production mechanism, from the most likely to least likely]{Different Higgs production mechanism, from the most likely to least likely \cite{gamma}\cite{timo}}
+\caption[Higgs production mechanism]{Different Higgs production mechanism, from the most likely to least likely \cite{gamma}\cite{timo}}
 \label{psu}
@@
 
-\begin{figure}[ht]
-\centering
-\includegraphics[scale=0.7]{Chapter1/thw.png}
-\caption[$tHW$ mechanism]{$tHW$ mechanism\cite{th1}}
-\label{thw}
-\end{figure}
+%\begin{figure}[ht]
+%\centering
+%\includegraphics[scale=0.7]{Chapter1/thw.png}
+%\caption[$tHW$ mechanism]{$tHW$ mechanism\cite{th1}}
+%\label{thw}
+%\end{figure}
 
-In the tH process, a Higgs boson is radiated from a single top quark as shown in figure \ref{psu}.
-The $tH$ process is a new field of study, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens the path to new discoveries.
+In the tH process, a Higgs boson is radiated from a single top quark as shown in Figure \ref{psu}.
+The $tH$ process has gained interest recently\cite{th1}, given that there are few experiments and its production rate (probability) is small, so the detection of Higgs bosons in this channel opens the path to new discoveries.
 
@@
  Cross sections are expressed in barns, where 1 barn=$10^{-34}$ cm$^{2}$.
+The cross section is important in the evaluation of events for specific processes.
+In order to get the number of events for a specific process, the reaction rate $N$ is determined by the total cross section $\sigma$ and the luminosity L\footnote{The unit of measurement of instantaneous luminosity is cm$^{-2}$s$^{-1}$.
+}.
+%L is called luminosity, that is the number of particle interactions can be produced in a detector per second.
 
-The cross section is important in the evaluation of events for specific processes.
-In order to get the number of events for a specific process, the reaction rate $N$ is determined by the total cross section $\sigma$ and the luminosity L.
-%L is called luminosity, that is the number of particle interactions can be produced in a detector per second. 
-The unit of measurement of luminosity is cm$^{-2}$s$^{-1}$. Therefore, the reaction rate is 
+Therefore, the reaction rate is 
 \begin{align} \label{nr}
@@
 In practice, the luminosity is measured by counting the number of events for a well known process.
+\begin{figure}[ht]
+	\centering%
+	\includegraphics[width=12cm,height=7cm]{Chapter1/7-14xsec.eps}
+	\caption[Cross section for different processes generated in a pp collision]{
+		Cross section for different processes generated in a pp collision  \cite{dcrosse}}
+	\label{csp}
+\end{figure}
+
 \begin{table}[ht]
 \centering
-\caption[Higgs boson production cross sections in pp collisions for $\sqrt{s}=13$TeV (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2]{	Higgs boson production cross sections in pp collisions for $\sqrt{s}=13$TeV (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2 \protect \cite{pd}}
+\caption[Higgs boson production cross sections in pp collisions number of events for  35.9 fb$^{-1}$ ]{	Higgs boson production cross sections in pp collisions for $\sqrt{s}=13$TeV (in pico barn) and number of events for an integrated luminosity of 35.9 fb$^{-1}$ for Run 2  \cite{pd}}
 \begin{tabular}{|c|c|c|}
@@
  Table \ref{crt} shows the Higgs production cross section for pp collisions and the number of events produced using a integrated luminosity of $35.9 fb^{-1}$, that is the luminosity measured for the Run 2 from LHC on 2016\cite{pd}.
-
-\begin{figure}
-\centering
-\includegraphics[width=12cm,height=7cm]{Chapter1/7-14xsec.eps}
-\caption[Cross section for different processes generated in a pp collision]{
-Cross section for different processes generated in a pp collision  \cite{dcrosse}}
- \label{csp}
-\end{figure}
-
+Figure \ref{csp} shows the cross sections for each Higgs mechanism process  that comes from pp collisions in relation to colliding energy.
 Here we can see that the ggF process has the biggest cross section of all Higgs mechanism and generates the greatest number of events possibles.
@@
 \end{table}
-The decay $H \rightarrow$ $b\bar{b}$ has a branching ratio a bit more than 50$\%$, therefore is the most likely decay .
-Due to this, $H\rightarrow b\bar{b}$ is a very studied process and most likely to detect a Higgs boson in the data after reconstruction.
+The decay $H \rightarrow$ $b\bar{b}$ has a branching ratio a bit more than 50$\%$.
 The decay $H \rightarrow$ $\mu^+\mu^-$ has a very low branching ratio.
 This decay is very rare but not impossible to detect in the future.
-In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$.
+%In this work the majority of the Higgs decays detected are from $WW$, $ZZ$, $\tau \tau$.
 
@@
 either from the top quark or from the exchanged $W$ boson in the two dominant leading order
-diagrams in figure \ref{newth} provides a unique opportunity to study the relative sign of the coupling.
+diagrams shown in Figure \ref{newth} provides a unique opportunity to study the relative sign of the Higgs top coupling.
+In practice, we do not directly measure the Yukawa couplings. Instead, modifier parameters $k_t$ and $k_V$ are introduced in the analysis to represent deviations from the Yukawa coupling values. 
 In the SM, the two diagrams interfere negatively and thereby suppress the production cross section.
-Any deviation from the SM can lead to a large enhancement of the event rate.
- $\kappa_t$ and $\kappa_V$ are the coupling parameters, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson.
+Any deviation from the SM coupling parameters can lead to a large enhancement of the event rate. 
+In this project we consider a modified model with $k_t$=-1, which leads to a constructive interference and a $tH$ cross section more than ten times. 
+ %$\kappa_t$ and $\kappa_V$ are the modifier of the coupling parameters discussed in section 1.5, where $\kappa_t$ is for the top and $\kappa_V$ for $W$ boson.
 
@@
 	\includegraphics[scale=0.5]{Chapter1/newtHq.png}
-	\caption[$tH$ mechanism.
-Higgs radiated from a top quark (left).
-Higgs radiated from a W boson (right)]{$tH$ mechanism.
-Higgs radiated from a top quark (left).
-Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
+	\caption[$tH$ mechanism]{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right) \protect \cite{bb}} \label{newth}
 \end{figure}

### 2019-11-24 tesis_hiram/Chapter2/chapter2.tex
correccion

@@
 The LHC is designed to accelerate particles to high energies and generate collisions. There are several
-experiments installed along the LHC ring as shown in figure \ref{lhc}.
+experiments installed along the LHC ring as shown in Figure \ref{lhc}.
 One of them is ATLAS, located on Point 1 between the two injection lines, which is a general purpose detector.
@@
 
-\pagebreak
-
-\begin{figure}[ht]
-\centering
-\includegraphics[width=16cm,height=10cm]{Chapter1/cern.jpg}
-\caption[Large hadron collider from CERN]{CERN accelerator complex \cite{cern1}} \label{lhc}
-\end{figure}
-
 Protons in the LHC start out as hydrogen atoms stripped of their electrons. The first accelerating stage the protons are subjected to is a linear accelerator, Linac2,
@@
 
+\afterpage{
+\begin{figure}
+	\centering
+	\includegraphics[width=16cm,height=15cm]{Chapter1/cern.jpg}
+	\caption[CERN accelerator complex]{CERN accelerator complex \cite{cern1}} \label{lhc}
+\end{figure}
+\clearpage}
 %\begin{table}[ht]
@@
 %\end{table}
-\pagebreak
+
 Inside the detectors, colliding protons generate an amount of particles such as pions and kaons, which are the most common, created by the jet particles that were produced after the collision.
 Besides the particles created by the quarks of the proton, gluons are also radiated and create new particles and photons are radiated too.
-During the collision time, the main detectors of LHC capture the energy 
-and save the data in supercomputers. Those high end computers starts to measure the signals in order to assign a type of events.
+Within a short time, the main detectors of LHC capture 
+and save the data using high performance computing.
 
@@
 Alternatives to the Standard Model that involves different symmetries are also put to test.
-With the exploration of theses theories, people hope for a discovery that guides them towards a unified theory, so the importance to accelerate particles to higher energy scales.
+With the exploration of theses theories, people hope for a discovery that guides them towards a unified theory, so the importance to accelerate particles to higher energy scales and high intensity experiments.
 
@@
 \includegraphics[scale=0.5]{Chapter2/lum6.png}
-\caption[LHC schedule, including future plans for increasing the center of mass energy and luminosity.
-The periods labeled LS are the maintenance periods]{LHC schedule, including future plans for increase the center of mass energy and luminosity.
-The periods labeled LS are the maintenance periods\cite{cern3}.}
+\caption[LHC schedule]{LHC schedule, including future plans for increase the center of mass energy and luminosity. The periods labeled LS are the maintenance periods\cite{cern3}.}
 \label{lhc-lumi}
@@
 The reason for such a strong magnetic field is to obtain a better momentum resolution.
- The magnetic flux is returned via a 1.5 m thick iron yoke instrumented with four stations of muon
- chambers. %Characteristics of the solenoid are shown in table \ref{tab:my_label}.
-
-\begin{figure}[ht]
-	\centering
-	\includegraphics[width=10cm,height=6cm]{Chapter2/cms2.png}
-	\caption[View of Compact muon solenoid (CMS)]{View of Compact muon solenoid (CMS)\cite{cms-manual}}\label{cms}
-\end{figure}
-There are many layers of detectors to register different kinds of energy signals. But since muons go through materials very easily, the complex is buried 100 meters underground.
-
-The CMS experiment is composed of several detector layers that allow identify and save different types of energy signals and it is saved in a powerful supercomputers that separate and classify the data according to certains variables.
-The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter, a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
-All these parts are illustrated in figure \ref{cms}.
-
+More characteristics of the solenoid are shown in Table \ref{tab:my_label}.
  \begin{table}[ht]
@@
 
+ %The magnetic flux is returned via a 1.5 m thick iron yoke instrumented with four stations of muon
+ %chambers. 
+\begin{figure}[ht]
+	\centering
+	\includegraphics[width=10cm,height=6cm]{Chapter2/cms2.png}
+	\caption[View of Compact muon solenoid (CMS)]{View of Compact muon solenoid (CMS)\cite{cms-manual}}\label{cms}
+\end{figure}
+%There are many layers of detectors to register different kinds of energy signals. %But since muons go through materials very easily, the complex is buried 100 meters underground. 
+The CMS experiment is composed of several detector layers that allow identify and save different types of energy signals and it is saved in a powerful supercomputers that separate and classify the data according to certains variables.
+The general parts of the CMS are the Silicon Tracker, an Electromagnetic Calorimeter, a Hadron Calorimeter, the solenoid (superconducting magnet) and the Muon Detector.
+All these parts are illustrated in Figure \ref{cms}.
 %The trigger or event selection process must reduce the approximately 1 billion interactions per second to more less than 100 events per second for storage and subsequent analysis.\\
@@
 million silicon strips \cite{cms-manual}.
-A full coverage of the Tracker is shown in figure \ref{pixel2}
+A full coverage of the Tracker is shown in Figure \ref{pixel2}
 
@@
 The efficiency of the tracker is estimated by using samples of muons and pions with $p_t$ that is the transverse momentum (component of momentum transverse to beam line) of 1,10 and 100 GeV.
-For muons the efficiency of the tracker is shown in figure \ref{efi}
+For muons the efficiency of the tracker is shown in Figure \ref{efi}
 \begin{figure}[ht]
@@
 
-According to figure \ref{efi}, the efficiency of the tracker is around 98 $\%$ for $|\eta|<2$. The resolution of the tracker for muons with $p_t$=100 GeV is around 1-2 $\%$.
+According to Figure \ref{efi}, the efficiency of the tracker is around 98 $\%$ for $|\eta|<2$. The resolution of the tracker for muons with $p_t$=100 GeV is around 1-2 $\%$.
 Of course, this is a first stage of the measurement of particle momentum because the other detectors are used to increase and improve the measurement and reconstruction of the particle path.
@@
 The crystal cross section for the rear face is 30 $\times$ 30 mm$^2$, and for the face is 28.62 $\times$ 28.62 mm$^2$ with length of 220 mm.
-The ECAL is illustrated in figure \ref{ecal}.
+The ECAL is illustrated in Figure \ref{ecal}.
 
@@
 As its name says, the ECAL is mainly used for the electron detection, but also detects, photons, and neutral pions.
-The charged particles reach the crystals that provokes the photo diodes detect energy.
+The charged particles reach the crystals, create a shower of secondary electrons and photons.
+The light from the secondary particles is detected by  photo diodes.
 The resolution of the ECAL is estimated by using a test beam and registering the energy signals. The resolution for electrons with energies of 120 GeV is 0.5$\%$.
@@
 	\includegraphics[width=10cm,height=6cm]{Chapter2/hcal.png}
-	\caption[View of the CMS HCAL showing the different layers and tower regions.
-In the endcap, the towers are defined with two longitudinal segments as shown by the colors]{View of the CMS HCAL showing the different layers and tower regions.
+	\caption[View of the HCAL ]{View of the CMS HCAL showing the different layers and tower regions.
 In the endcap, the towers are defined with two longitudinal segments as shown by the colors\cite{cms-manual}}\label{hcal}
@@
 The Muon Detector has three main subdetectors: the drift tube chambers (DT), the cathode strips chambers (CSC) and the resistive plate chamber (RPC). 
-The DT's, CSC's and RPC's are shown in figure \ref{dt}.
+The DT's, CSC's and RPC's are shown in Figure \ref{dt}.
 
@@
 	\includegraphics[width=11cm,height=7cm]{Chapter2/csc}
-	\caption[Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$]{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$\cite{cms-manual}.}
+	\caption[CMS Muon detector]{Cross section of a quadrant of the CMS with axis parallel to the beam (z axis) horizontally and the radius of the detector in terms of the $\eta$, illustrating the muon detector and its components \cite{cms-manual}.}
 	\label{dt}
@@
 The main purpose of the Muon System Detector is to identify muon tracks. 
-The efficiency of the muon system is estimated by using single muon samples simulated with $p_t$=10, 50, 100, 500 and 1000 GeV. The results are shown in the figure \ref{mu-efi}.
+The efficiency of the muon system is estimated by using single muon samples simulated with $p_t$=10, 50, 100, 500 and 1000 GeV. The results are shown in figure \ref{mu-efi}.
 \begin{figure}

### 2019-11-24 tesis_hiram/Chapter3/chapter3.tex
correccion

@@
 The Higgs decays to a pair of opposite sign $W$ bosons, where one of the bosons can decay to a $\mu$ and its neutrino.
+$b$ quark creates a b-jet.
 This is the main process that generates events with two same sign muons.
 The tH process topology is shown in  figure \ref{jet}.
-
-Figure \ref{jet}, also shows a b-jet that comes from the tH process.
-Finally there is a forward quark jet (highest $\eta$ value) generated from the initial collision.
-Additional jets or leptons can be generated from the other $W$ boson.
+ Finally there is a forward quark jet (highest $\eta$ value) generated from the initial collision. Additional jets or leptons can be generated from the other $W$ boson.
 
@@
 		\includegraphics[scale=1]{Chapter1/jet.png}
-		\caption{Topology of $t$H process which generates two same sign muons, a forward jet and a b-jet.} 
+		\caption[Topology of $tH$]{Topology of $tH$ process which generates two same sign muons, a forward jet and a b-jet.} 
 		\label{jet}
@@
 \begin{table}[ht]
-	\caption{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$. $l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
+	\caption[Expected number of events for $tH$ decay chain with 35.9 fb$^{-1}$ of integrated luminosity at center of mass energy of $\sqrt{s}$=13 TeV ]{Expected number of events for different $tH$ decay chains assuming integrated luminosity of 35.9 fb$^{-1}$.
+$l$ represents $\mu^{\pm},e^\pm, \tau^\pm$.}
 	\begin{tabular}{|l|c|c|}
@@
 \end{itemize}
-Table \ref{back} shows the decay chains and production cross sections for the backgrounds.
+Table \ref{back} shows the decay chains for the backgrounds.
 Due to small expected event yields, the processes $W^\pm$ $W^\pm$,$tZq$,$t\bar{t}t\bar{t}$, $VVV$, $tZW^+$ and $ZZ$ are grouped as one called Rares in the results below.
@@
 \section{Event Selection}
-In order to detect signal events and reject background, the following selections are applied. 
+In order to detect signal events and reject background, the following selections are applied, according to the CMS publication\cite{th1} 
 \begin{itemize}
@@
 %Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
-The number of events that passed the event selection are shown in table \ref{tth-table} which corresponds to a integrated luminosity of 35.9 fb$^{-1}$ \cite{th1}.
+The number of expected events after the event selection predicted by the Monte Carlo simulations used in the CMS publication are shown in table \ref{tth-table} which corresponds to a integrated luminosity of 35.9 fb$^{-1}$\cite{th1}.
 The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes.
@@
 	\centering
-	\caption[Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
-The uncertainties of yields include statistical and systematic]{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
+	\caption[Event yields for signal and backgrounds after the event selection]{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
 The uncertainties of yields include statistical and systematic\cite{th1}}
@@
 \section{Systematic uncertanties}
+The uncertainties of the yields shown in Table \ref{tth-table} include systematic uncertainties due to the following sources, described in the CMS publication\cite{th1} and summarized here:
 \begin{itemize}
@@
 \item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
-\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+\item In the Rare background, a $50\%$ of uncertainty is assigned.
 \item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
+\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters (e.g.
+the strong coupling constant $\alpha_s$ and Parton Distribution Functions (PDF) ) used in that simulation.
 \end{itemize}
@@
 	\end{minipage}
-\caption[Distribution of BDT discriminant for signal and background in the case of SM (left) and inverted coupling scenario (right)]{Distribution of BDT discriminant for signal and background in the case of SM (Up) and inverted coupling scenario (Down) \cite{th1}}
+\caption[Distribution of BDT for signal and backgrounds ]{Distribution of BDT discriminant for signal and background in the case of SM (Up) and inverted coupling scenario (Down) \cite{th1}}
 \label{bdt2}

### 2019-11-24 tesis_hiram/Chapter4/chapter4.tex
correccion

@@
 
-	The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
+	The fit is applied by minimizing the negative logarithm of the likelihood function (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
 The minimization is performed by using programming language ROOT.
@@
 The package ROOFIT is used here, because of its implementations of modeling probability distributions and statistical tools\cite{roofit}.
-Figure \ref{simple} and Table \ref{table1}, shows the results of the model fitting using the Asimov data for both models.
+Figure \ref{simple} and Table \ref{table1}, shows the results of the fit to the Asimov data.
 
@@
 For the pre-fit, values of $\alpha$ are set to zero and $\mu$ is set to 1.
-After the fit, $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds didn't change for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also didn't change.
+After the fit, $\alpha$ parameters set to zero indicates that in the fit, the values of the backgrounds did not change for the SM and the $\mu$ parameter set to 1 indicates that the signal strength also did not change.
 
@@
 		\end{minipage}
-		\caption{Post fit signal and background yields for tH process for SM (Left) and $k_t=-1$ (Right).
+		\caption[Post-fit Signal and Backgrounds for $tH$ process]{Post-fit signal and background yields for $tH$ process for SM (Left) and $k_t=-1$ (Right).
 			%In the box below each distribution, the ratio of the observed and predicted event yields is shown
@@
 		\centering
-		\caption{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
+		\caption[Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$]{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$.
+The uncertainty given is the combined statistical plus systematic.}
 		\begin{tabular}{ccc}
@@
 		\includegraphics[scale=0.5]{Chapter4/chi}
-		\caption{Illustration of the $\chi^2$ distribution %with 7 degrees of freedom 
-			used for the limit estimation}
+		\caption[$\chi^2$ Distribution]{Illustration of the $\chi^2$ distribution with 7 degrees of freedom used for the limit estimation}
 		\label{chi}
@@
 		\end{minipage}
-		\caption{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
+		\caption[Likelihood scan for SM and $k_t$=-1]{Likelihood scan for SM (Left) and $k_t$=-1 (Right).}
 		\label{scanl}
@@
 	%%sigma son las probabilidades que corresponden a 1sigma=68, 2sigma=95, 3sigma=98 y sigma son los limites de la integral de una gaussiana
-	\section{Extrapolation to higher luminosities}
+	\section{Extrapolation to higher luminosity}
 	In the past section, it was shown that the signal strength with an integrated luminosity of 35.9 fb$^{-1}$ is not significant.
@@
 Run 3 starts in 2021 and is expected an integrated luminosity of 300fb$^{-1}$ and for the high luminosity phase of LHC, expected to collect 3000 fb$^{-1}$.
-Therefore, it is interesting to study the sensitivity of the signal strength at higher luminosities.
+Therefore, it is interesting to study the sensitivity of the signal strength at higher luminosity.
 	An extrapolation (scale) is applied to the Asimov data and the statistical uncertainty is adjusted accordingly.
@@
 
-	In figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosities is shown.
+	In figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosity is shown.
 As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in Chapter 1.
 But even with the increase of number of events, the statistical uncertainty of the data is too large with respect to the expected signal.
-In the likelihood scan for higher luminosities, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
+In the likelihood scan for higher luminosity, as the luminosity increases, the relative uncertainty on the signal strength $\mu$ decreases.
 This is caused by the increased events available for the fit.
@@
 		\begin{table}[ht]
-		\caption{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
+		\caption[Results of $\mu$ and upper limits for SM and $k_t$=-1]{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
 		\begin{tabular}{|c|c|c|c|c|}
@@
 	However, the uncertainty of $\mu$ for the SM case is 170$\%$ for  in the 3000 fb$^{-1}$ case, making impossible to get an evidence of a Higgs boson in the $tH$ process for the same sign muon channel.
-Even at higher luminosities, the uncertainty of $\mu$ in SM case is still very big.
-	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosities giving better results.
+Even at higher luminosity, the uncertainty of $\mu$ in SM case is still very big.
+	In the $k_t$=-1 model the uncertainty of $\mu$ decreases with higher luminosity giving better results.
 This is caused by the fact that the number of events for the $tH$ signal is greater.
@@
 In the likelihood scan, the statistical test $q$ gets very high values at $\mu$>1.1.
-This indicates that for large integrated luminosities this model can be fully ruled out.
+This indicates that for large luminosity this model can be fully ruled out.
 This can be visualized in the likelihood scan of  3000 fb$^{-1}$, where the curve is very closed and values of $q$ are very high, giving incompatibility of the model with data.

### 2019-11-24 tesis_hiram/Chapter5/chapter5.tex
correccion

@@
 This process has not been observed experimentally.
-Recently CMS published a search for $tH$ production using 35.9 fb$^{-1}$ from Run 2 .
-Using information from this dataset, we studied the expected sensitivity using an Asimov data and systematic uncertainties for the final state with same sign pairs of muons.
+Recently CMS published a search for $tH$ production using 35.9 fb$^{-1}$ from Run 2\cite{th1}.
+Using information from this publication, we studied the expected sensitivity using an Asimov data and systematic uncertainties for the final state with same sign pairs of muons.
 
-Using this dataset for 35.9 fb$^{-1}$, the uncertainty for the $tH$ signal strength $\mu$ is around eight times than the value of $\mu$ for the SM.
+For an integrated luminosity of 35.9 fb$^{-1}$, we obtained an expected uncertainty for the $tH$ signal strength $\mu$ is around eight times than the value of $\mu$ for the SM.
 In this case, we estimated an upper limit on $\mu$ of 17 at 95$\%$ confidence level.
-For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$, this is due to the larger expected number of signal events
+For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$, this is due to the larger expected number of signal events.
 
-We also studied the sensitivity for larger integrated luminosities expected in future runs of the LHC.
-We find that for the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit on $\mu$ is placed at 4.3.
+We also studied the sensitivity for larger integrated luminosity expected in future runs of the LHC.
+We find that for the SM scenario the expected uncertainty even at the largest integrated luminosity is not enough to observe the signal and only an upper limit on $\mu$ is placed at 4.3.
 In the case of the inverted coupling scenario, a possible signal can be observed with an uncertainty of 10$\%$ at 3000 fb$^{-1}$.

### 2019-11-25 tesis_hiram/Chapter1/chapter1.tex
b

@@
 
-\begin{chapter}{Introduction}
+\chapter{Introduction}
 
@@
 Other particles do not decay or their lifetimes are very long.
-All the particles in the SM are shown in the figure \ref{sm1}.
+All the particles in the SM are shown in the Figure \ref{sm1}.
 %The final states can be represented with a Feynman diagram according to the SM vertices\cite{mark}.
@@
 The $W$,$Z$ and Higgs bosons, can interact with the most of the particles, while the gluons can only interact with quarks and with itself.
-%Those bosons act as mediators in decays and creation of complex
-%particles, as mesons and baryons.
-
-%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force.
-In case of its existance, it should have a spin 2 and mass 0.
-
-%There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc.
-More information about the LHC will be described in the next chapters.
-
+\afterpage{
 	\begin{figure}[ht]
 	\centering
-		\includegraphics[scale=0.35]{Chapter1/sm.png}
+	\includegraphics[scale=0.3]{Chapter1/sm.png}
 	\caption[Particle interactions in Standard model]{Particle interactions in Standard model\cite{smi}}
@@
 \end{figure}
+\clearpage}
+%Those bosons act as mediators in decays and creation of complex
+%partiles, as mesons and baryons.
+%In case of gravity, exist a theoretical particle, called graviton, that is the fundamental particle associated with the gravitational force.
+In case of its existance, it should have a spin 2 and mass 0.
+%There are experiments that detect particles around the world, such as the LHC in Europe, the Fermilab in United States of America, KEK in Japan, etc.
+More information about the LHC will be described in the next chapters.
 
@@
 \caption[Table of particles in SM]{SM particle properties: mass, charges, spin, lifetime and distance traveled in a lifetime (assuming speed of $v$=0.998c)\cite{pd}.
-In the case of $s$,$c$ and $b$ quarks, the lifetime corresponds to the K$^\pm$, D$^{\pm}$ and B$^{\pm}$ meson lifetime.}
+In the case of $s$,$c$ and $b$ quarks, the lifetime corresponds to the $K^\pm$, $D^{\pm}$ and $B^{\pm}$ meson lifetime.}
 \renewcommand{\arraystretch}{1.5}
@@
 \end{array} \right) $ is a SU(2) doublet of scalar fields. V is symmetrical under rotations in $\Phi$ space
-and parameters $\lambda $ and $\mu^2$ are parameters of the potential. The Higgs potential for $\mu^2 <0$ and $\lambda>0$ can be visualized in figure \ref{hat}
+and parameters $\lambda $ and $\mu^2$ are parameters of the potential. The Higgs potential for $\mu^2 <0$ and $\lambda>0$ can be visualized in Figure \ref{hat}
 %The $\lambda $ term describes self-interactions among the scalar fields.
@@
 There is also the vector Higgs process (VH), where the creation of particles using vector boson comes from a interaction between fermions and anti fermions\cite{pd}.
-These processes are shown in the figure \ref{psu}
+These processes are shown in the Figure \ref{psu}
 
@@
 In this process, the creation of a Higgs boson comes from a intection via $t\bar{t}$.
-In the figure \ref{psu}, the $t\bar{t}H$ starts with 2 gluons which decay to two $t\bar{t}$ pairs and after that, the interaction $t\bar{t}$ generates a Higgs.
+In the Figure \ref{psu}, the $t\bar{t}H$ starts with 2 gluons which decay to two $t\bar{t}$ pairs and after that, the interaction $t\bar{t}$ generates a Higgs.
 The last process, subject of study in this thesis, is the top Higgs ($tH$) process.
 This process is a rare expected process with a very small production rate\cite{pd}.
-In figure \ref{thw}, another way to produce $tH$, in association with a $W$ is shown.
+In Figure \ref{thw}, another way to produce $tH$, in association with a $W$ is shown.
 
@@
 For the processes tH and $t\bar{t}$H, they have the smallest cross section, so the probability for the processes is low and generates a small number of events.
-\pagebreak
 
@@
 \pagebreak
-\end{chapter}

### 2019-11-25 tesis_hiram/Chapter3/chapter3.tex
b

@@
 This is the main process that generates events with two same sign muons.
-The tH process topology is shown in  figure \ref{jet}.
+The tH process topology is shown in  Figure \ref{jet}.
  Finally there is a forward quark jet (highest $\eta$ value) generated from the initial collision. Additional jets or leptons can be generated from the other $W$ boson.
@@
 		\centering
-		\includegraphics[scale=1]{Chapter1/jet.png}
+		\includegraphics[scale=1.3]{Chapter1/jet.png}
 		\caption[Topology of $tH$]{Topology of $tH$ process which generates two same sign muons, a forward jet and a b-jet.} 
@@
 %Also it is possible to obtain a study of three leptons, given the mentioned decays can produce them. 
-The number of expected events after the event selection predicted by the Monte Carlo simulations used in the CMS publication are shown in table \ref{tth-table} which corresponds to a integrated luminosity of 35.9 fb$^{-1}$\cite{th1}.
+The number of expected events after the event selection predicted by the Monte Carlo simulations used in the CMS publication are shown in Table \ref{tth-table} which corresponds to a integrated luminosity of 35.9 fb$^{-1}$\cite{th1}.
 The backgrounds with the most events are $t\bar{t} W^\pm$, $t\bar{t}Z$ and Fakes.
@@
 These event yields will be used to estimate the signal sensitivity.
-The yields include statistical uncertainties due to the  Monte Carlo (MC) samples and systematic uncertainties as described in table \ref{tth-table}.
+The yields include statistical uncertainties due to the  Monte Carlo (MC) samples and systematic uncertainties as described in Table \ref{tth-table}.
 
@@
 The BDT training is performed using several event variables.
-
 In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds.

### 2019-11-25 tesis_hiram/Chapter4/chapter4.tex
b

@@
 		\centering
-		\caption[Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$]{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$.
+		\caption[Post-fit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$]{Post-fit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$.
 The uncertainty given is the combined statistical plus systematic.}
@@
 
-In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in figure \ref{chi}, where $\alpha$=0.05 in this case.
-It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in figure \ref{scanl}.
+In order to find the upper limit value of $\mu$, we search for the largest value of $\mu$ such that $q$ remains below the shaded region shown in Figure \ref{chi}, where $\alpha$=0.05 in this case.
+It is useful to scan $q$ as function of $\mu$, which is normally a parabolic function as shown in Figure \ref{scanl}.
 In the SM case, the scan has a wider shape in comparison to the $k_t$=-1.
@@
 
-	In figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosity is shown.
+	In Figure \ref{hm}, an estimated prediction of the signal and background events for higher luminosity is shown.
 As the luminosity increases, the number of events for both signal and backgrounds also increases, as previously explained in Chapter 1.
@@
 
-	The same method is used for the model $k_t$=-1 in figure \ref{hm1}.
+	The same method is used for the model $k_t$=-1 in Figure \ref{hm1}.
 In this case, the number of events for the signal is more appreciable in comparison with the SM model.
@@
 		\end{minipage}
-		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in SM model.}
+		\caption{Fit and likelihood scan for 150 fb$^{-1}$, 300 fb$^{-1}$ and 3000 fb$^{-1}$ in SM}
 		\label{hm}

### 2019-11-25 presentacion_hiram/presentacion-tesis.tex
n

@@
 	\institute{Universidad de Sonora}
-	\date{\small November 15$^{th}$ 2019}
+	\date{\small November 25$^{th}$ 2019}
 	%\subject{}
@@
 \end{table}
-\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
+\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at $v$=0.998c}
 \end{frame}
@@
 \begin{itemize}
-	\item $\Phi$ is higgs field which is a complex scalar field. $\Phi$
+	\item $\Phi$ is Higgs field which is a complex scalar field. $\Phi$
 	%\item  W$_\mu$ and B$_\mu$ are gauge bosons
@@
 
+\begin{frame}
+\frametitle{Electroweak SM Lagrangian}
+	\begin{figure}[ht!]
+		\centering
+		\begin{tikzpicture}[scale=1.2]
+		\begin{axis}[
+		hide axis,
+		%axis lines=middle,
+		%      axis on top,
+		%      axis line style={blue,dashed,thick},
+		%      ymin=-2,ymax=2,
+		%      xmin=-2,xmax=2,
+		%      zmin=-2,zmax=2,
+		samples=30,
+		domain=0:360,
+		y domain=0:1.25,clip=false
+		]
+		\addplot3 [surf, shader=flat, draw=black, fill=white, z buffer=sort]
+		({sin(x)*y}, {cos(x)*y}, {(y^2-1)^2});
+		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:1,0,0)
+		node[below,font=\footnotesize]{$\Phi_{\text{IM}}$};
+		\draw[blue,thick,-stealth] (axis cs:1,0,0) -- (axis cs:1.3,0,0)
+		node[above,font=\footnotesize]{};
+		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,-1,0)
+		node[left=2mm,font=\footnotesize]{$\Phi_{\text{RE}}$};
+		\draw[blue,thick,-stealth] (axis cs:0,-1,0) -- (axis cs:0,-1.5,0)
+		node[right=1mm,font=\footnotesize]{};
+		\draw[blue,thick,dashed] (axis cs:0,0,0) -- (axis cs:0,0,1)
+		%node[left=2mm,font=\footnotesize]{$\phi_{\text{RE}}$}
+		;
+		\draw[blue,thick,-stealth] (axis cs:0,0,1) -- (axis cs:0,0,1.3)
+		node[right,font=\footnotesize]{$V(\Phi)$};
+		\end{axis}
+		\end{tikzpicture}
+		\caption*{\small Higgs potential $V(\Phi^\dagger \Phi)$ for $\mu^2<0$ and $\lambda>0$, also called the mexican hat potential.}
+		\label{hat}
+	\end{figure}
+\end{frame}
 \begin{frame}
@@
 \begin{frame}
-	\Fontvi
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
-			  {Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
-			  	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
-			 {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-{\nologo
-\begin{frame}
-\Fontvi
-\begin{center}
-	\begin{tabular}{cc}
-	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
-\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
-{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
-		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
-		{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
-	\end{tabular}
-\end{center}
-\end{frame}
-}
-
-{\nologo
-\begin{frame}
 \subsection{Previous results}
@@
 
-%\begin{frame}
-%\section{Supportive slides}
-%\huge{Back up}
-%\end{frame}
+\begin{frame}
+\section{Supportive slides}
+\huge{Back up}
+\end{frame}
+
+{\nologo
+	\begin{frame}
+		\Fontvi
+		\begin{center}
+			\begin{tabular}{cc}
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
+				{Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
+				{Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
+			\end{tabular}
+		\end{center}
+	\end{frame}
+}
+
+{\nologo
+	\begin{frame}
+		\Fontvi
+		\begin{center}
+			\begin{tabular}{cc}
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
+				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
+				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
+			\end{tabular}
+		\end{center}
+	\end{frame}
+}
 

### 2019-11-25 presentacion_hiram/presentacion-tesis.tex
revision
remove theme
nuevo

@@
 \usepackage[makeroom]{cancel}
-\usetheme{Frankfurt}
+%\usetheme{Frankfurt}
 \usepackage{tikz} 
@@
 \begin{frame}
+\section{Introduction}
+\subsection{Standard Model}
+\frametitle{Standard Model}
+\begin{table}
+	\centering
+\begin{tabular}{cc}
+\includegraphics[width=6cm,height=5cm]{figures/sm1.png} & \includegraphics[width=5cm,height=5cm]{figures/sm.png}
+\end{tabular}
+\end{table}
+\end{frame}
+
+\begin{frame}
 \frametitle{Motivation  for single top Higgs (tH)}
@@
 \end{itemize}
-\end{frame}
-
-\begin{frame}
-\section{Introduction}
-\subsection{Standard Model}
-\frametitle{Standard Model}
-\begin{table}
-	\centering
-\begin{tabular}{cc}
-\includegraphics[width=6cm,height=5cm]{figures/sm1.png} & \includegraphics[width=5cm,height=5cm]{figures/sm.png}
-\end{tabular}
-\end{table}
-\end{frame}
-
-\begin{frame}
-\frametitle{Particles Properties}
-Table of particles in SM
-\begin{table}
-\tiny{\renewcommand{\arraystretch}{1.5}
-\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
-\hline 	
-Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
-\hline 
-Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
-\hline 	
-Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
-\hline 
-Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
-\hline 
-Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
-\hline 
-Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
-\hline 
-Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
-\hline 
-$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
-\hline 
-$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
-\hline
-Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
-\hline
-Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
-\hline 
-Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
-\hline 
-Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
-\hline 
-Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
-\hline 
-$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 	
-\hline 
-$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
-\hline 
-\end{tabular} 
-}
-\end{table}
-\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at $v$=0.998c}
 \end{frame}
@@
 
+\begin{frame}
+\frametitle{Particles Properties}
+Table of particles in SM
+\begin{table}
+\tiny{\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
+\hline 	
+Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
+\hline 
+Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
+\hline 	
+Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
+\hline 
+Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
+\hline 
+Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
+\hline 
+Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
+\hline 
+Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
+\hline 
+$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
+\hline 
+$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
+\hline
+Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
+\hline
+Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
+\hline 
+Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
+\hline 
+Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
+\hline 
+Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
+\hline 
+$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 	
+\hline 
+$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
+\hline 
+\end{tabular} 
+}
+\end{table}
+\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at $v$=0.998c}
+\end{frame}
+
 {\nologo
@@
 }
+
+\begin{frame}
+\frametitle{Cross section}
+\begin{itemize}
+\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
+\begin{align}
+N_R=\sigma \text{L}
+\end{align}
+%\item Experimentally
+%\begin{align}
+%d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
+%\end{align}
+\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
+\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
+L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Higgs production Cross section}
+\begin{table}
+	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
+		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
+	\begin{tabular}{|c|c|c|}
+		\hline
+		Production mechanism &
+		$\sigma$ (picobarns pb)
+		&Number of events \\
+		\hline
+		ggF &
+		48.93 &
+		1756587\\
+		\hline
+		VBF &
+		3.78&
+		135702\\
+		\hline
+		WH & 1.35 & 48465\\
+		\hline
+		ZH &0.88 & 31592\\
+		\hline
+		t$\bar{t}$H &
+		0.50&
+		18183\\
+		\hline
+		$tH$ &
+		0.074&
+		2665\\
+		\hline
+	\end{tabular}
+\end{table}
+
+\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Branching ratio}
+\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.
+\footnotemark.}
+\begin{align}
+\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
+\end{align}
+\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
+Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
+\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
+\end{frame}
+
+\begin{frame}
+\frametitle{Higgs Branching ratios per channel}
+\begin{table}
+	\caption*{SM Higgs boson branching ratios for  $M_H$ =125 GeV}
+\begin{center}
+\begin{tabular}{|c|c|}
+	\hline
+	Higgs decay & Branching ratio (BR)\\
+	\hline
+	H $\rightarrow$ b$\bar{b}$ &
+	$50.82\%$ \\
+	\hline
+	H $\rightarrow$ $W^+W^-$ &
+	$21.5\%$ \\
+	\hline
+	H $\rightarrow$ $\tau^+ \tau^-$ &
+	$6.27\%$\\
+\hline
+	H $\rightarrow$ ZZ &
+$2.61\%$\\
+\hline
+	H $\rightarrow$ $\gamma\gamma$ &
+$0.227\%$\\
+\hline
+	H $\rightarrow$ Z$\gamma$ &
+$0.153\%$\\
+\hline
+	H $\rightarrow$ $\mu^+\mu^-$ &
+$0.0217\%$\\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\end{frame}
 
@@
 \begin{frame}
-\frametitle{Cross section}
-\begin{itemize}
-\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
-\item Experimentally
-\begin{align}
-d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
-\end{align}
-\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
-\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
-L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
-\begin{align}
-N_R=\sigma \text{L}
-\end{align}
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Higgs production Cross section}
-\begin{table}
-	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
-		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
-	\begin{tabular}{|c|c|c|}
-		\hline
-		Production mechanism &
-		$\sigma$ (picobarns pb)
-		&Number of events \\
-		\hline
-		ggF &
-		48.93 &
-		1756587\\
-		\hline
-		VBF &
-		3.78&
-		135702\\
-		\hline
-		WH & 1.35 & 48465\\
-		\hline
-		ZH &0.88 & 31592\\
-		\hline
-		t$\bar{t}$H &
-		0.50&
-		18255\\
-		\hline
-		$tH$	(only)&
-		0.015&
-		560.39\\
-		\hline
-	\end{tabular}
-\end{table}
-
-\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Branching ratio}
-\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.
-\footnotemark.}
-\begin{align}
-\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
-\end{align}
-\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
-Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
-\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
-\end{frame}
-
-\begin{frame}
-\frametitle{Higgs Branching ratios per channel}
-\begin{table}
-	\caption*{SM Higgs boson branching ratios for  $M_H$ =125 GeV}
-\begin{center}
-\begin{tabular}{|c|c|}
-	\hline
-	Higgs decay & Branching ratio (BR)\\
-	\hline
-	H $\rightarrow$ b$\bar{b}$ &
-	$50.82\%$ \\
-	\hline
-	H $\rightarrow$ $W^+W^-$ &
-	$21.5\%$ \\
-	\hline
-	H $\rightarrow$ $\tau^+ \tau^-$ &
-	$6.27\%$\\
-\hline
-	H $\rightarrow$ ZZ &
-$2.61\%$\\
-\hline
-	H $\rightarrow$ $\gamma\gamma$ &
-$0.227\%$\\
-\hline
-	H $\rightarrow$ Z$\gamma$ &
-$0.153\%$\\
-\hline
-	H $\rightarrow$ $\mu^+\mu^-$ &
-$0.0217\%$\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
 \frametitle{$\mu\mu$ same sign decay rate}
@@
 \hline 
-\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  1.173  \\
-\hline
-\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.899 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.203 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.105  \\
+\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  5.58  \\
+\hline
+\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.89 \\
+\hline
+\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.96 \\
+\hline
+\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.50  \\
 \hline
 \tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
-\tiny{1.681 $\times$10$^{-4}$} & 0.094 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.017\\
-\hline
-\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.011\\
-\hline 
-\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.008  \\
+\tiny{1.681 $\times$10$^{-4}$} & 0.44 \\
+\hline
+\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.08\\
+\hline
+\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.05\\
+\hline 
+\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.04  \\
 \hline
@@
 \begin{frame}
+\frametitle{CMS integrated luminosity}
+\begin{center}
+	\begin{figure}
+		\includegraphics[scale=0.3]{figures/cms_lumi.png}
+		\caption*{Integrated luminosity for CMS experiment }
+	\end{figure}
+\end{center}
+\end{frame}
+
+\begin{frame}
 \subsection{CMS dectector}
@@
 \end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{CMS integrated luminosity}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.3]{figures/cms_lumi.png}
-		\caption*{Integrated luminosity for CMS experiment }
-	\end{figure}
-\end{center}
 \end{frame}
@@
 \item   \small{$W\rightarrow$ $q\bar{q}$}
-\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
+%\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
 \end{list}
-\item a light-flavor quark 
+\item A light-flavor quark (Forward jet)
 \item  A b-jet  
@@
 \end{multicols}
+\end{frame}
+
+\begin{frame}
+\subsection{Event selection}
+\frametitle{Event selection}
+In order to detect signal events and reject background, the following selections are applied. 
+\begin{itemize}
+	\item The events must contain two muons with the same sign.
+	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
+	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
+	\item One or more b-tagged jets with $|\eta|$ < 2.4
+\end{itemize}
 \end{frame}
@@
 \end{table} 
-\end{frame}
-
-\begin{frame}
-\subsection{Event selection}
-\frametitle{Event selection}
-In order to detect signal events and reject background, the following selections are applied. 
-\begin{itemize}
-	\item The events must contain two muons with the same sign.
-	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
-	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
-	\item One or more b-tagged jets with $|\eta|$ < 2.4
-\end{itemize}
 \end{frame}
@@
 \subsection{Systematic uncertainties}
-\frametitle{Systematic uncertainties}
+\frametitle{Systematic uncertainties on the yields}
 \begin{itemize}
@@
 \item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
-	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
+\item In the Rare background, a $50\%$ of uncertainty is assigned.
 \item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
+\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters (e.g.
+the strong coupling constant $\alpha_s$ and Parton Distribution Functions (PDF) ) used in that simulation.
 \end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\section{Statistical analysis}
-\frametitle{Fitting}
-	\begin{center}
-	\begin{figure}
-		\includegraphics[width=10.5cm]{figures/fit-box.png}
+\end{frame}
+
+%\begin{frame}
+%\section{Statistical analysis}
+%\frametitle{Fitting}
+%	\begin{center}
+%	\begin{figure}
+%		\includegraphics[width=10.5cm]{figures/fit-box.png}
 		\caption*{}
-	\end{figure}
-\end{center}
-\end{frame}
+%	\end{figure}
+%\end{center}
+%\end{frame}
 
@@
 \framesubtitle{Upper limit}
-\tiny{
-\begin{table}[ht!]
-	\caption*{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
+		\begin{table}[ht]
+		\caption[Results of $\mu$ and upper limits for SM and $k_t$=-1]{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
 		\begin{tabular}{|c|c|c|c|c|}
 			\hline
-		Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit & $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit \\
+			\multirow{2}{*}{Luminosity (fb$^{-1}$)}  &\multicolumn{2}{c|}{SM ($k_t$=1)} &\multicolumn{2}{c|}{$k_t$=-1 scenario}\\
+			\hhline{~----}	&$\mu$  &$\mu$ upper limit & $\mu$ &$\mu$ upper limit or interval\\
 			\hline
@@
 			\hline
-		3000&1.0 $\pm$ 1.7 & 4.3 &	 1.0 $\pm$ 0.1 & 1.1\\
+			3000&1.0 $\pm$ 1.7 & 4.3 & 1.0 $\pm$ 0.1 & 0.9-1.1\\
 			\hline
@@
 	\end{table}
+
 }
@@
 \begin{itemize}
-\item The results of the analysis for the SM case indicates that it is impossible to detect a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
+\item The results of the analysis for the SM case indicates that it is impossible to give an evidence of a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
 \item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.

### 2019-11-26 presentacion_hiram/presentacion-tesis.tex
new
Fix bug
n

--- 2019-11-14 presentacion_hiram/presentacion-tesis.tex
@@
-\documentclass[11pt]{beamer}
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-\usepackage{lmodern}
-\usepackage{amsmath}
-\usepackage{hyperref}
-\usepackage{array}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{epstopdf}
-\usepackage{caption}
-\usepackage{multicol}
-\usepackage{listings}
-\usepackage{alltt}
-\usepackage{mathtools}
-\usepackage[makeroom]{cancel}
-\usetheme{Frankfurt}
-\usepackage{tikz} 
-\usetikzlibrary{patterns}
-\usetikzlibrary{plotmarks}
-\titlegraphic{\vspace{8cm}}% to push the other text to the top
-\addtobeamertemplate{navigation symbols}{}{%
-	\usebeamerfont{footline}%
-	\usebeamercolor[fg]{footline}%
-	\hspace{1em}%
-	\insertframenumber/\inserttotalframenumber
-	\setbeamercolor{footline}{fg=blue}
-	\setbeamerfont{footline}{series=\bfseries}
-}
-\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
-		\newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
-\begin{document}
-	\author{\tiny
-			L.F. Hiram Ernesto Dami\'an\\
-			\vspace{5px}
-				Director:\\
-					\vspace{5px}
-			Jos\'e Feliciano Ben\'itez Rubio\\
-				\vspace{5px}
-				Maestr\'ia en Ciencias (F\'isica)\\
-					\vspace{5px}
-			 Departamento de Investigacion en F\'isica }
-	\title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
-	%\subtitle{}
-	\logo{\includegraphics[scale=0.1]{unison-logo.png}}
-	\newcommand{\nologo}{\setbeamertemplate{logo}{}}
-	\institute{Universidad de Sonora}
-	\date{\small November 15$^{th}$ 2019}
-	%\subject{}
-	\newcommand{\subf}[2]{%
-		{\small\begin{tabular}[t]{@{}c@{}}
-				#1\\#2
-		\end{tabular}}%
-	}
-	%\setbeamercovered{transparent}
-	%\setbeamertemplate{navigation symbols}{}
-\begin{frame}
-\titlepage
-\end{frame}
+#include "minimize.C"
+#include "ModelInfo.C"
 
-\begin{frame}
-\tiny
-\tableofcontents
-\end{frame}
+#include "RooMinimizerFcn.h"
+#include "RooRealVar.h"
 
-%\begin{frame}
-%\section{Overview and motivation}
-%\frametitle{Overview}
-%\begin{itemize}
-%\item Through this project it was studied the production of Higgs boson in association with a
-%single top quark ($tH$) in proton-proton collisions. 
-%This mechanism of production of the Higgs boson has not been observed before by any
-%experiment.
-%\item Standard Model and the Higgs production mechanism
-%\item A brief introduction to the LHC and CMS
-%\item Event selection and reconstruction of the tH signal
-%\item Creation and application of a statistical model for the analysis of events 
-%\item Making predictions for the future experiments.
-%\end{itemize}
-%\end{frame}
+#include "TGraph.h"
+#include "TAxis.h"
+#include "TString.h"
+#include "TLine.h"
 
-\begin{frame}
-\frametitle{Motivation  for single top Higgs (tH)}
-\begin{itemize}
-\item Coupling measurement is essential to establish the nature of the Higgs
-\item The exploration of Higgs production on the $tH$ channel is subject relatively new. Measurements of CMS and ATLAS are compatible with SM predictions.
-\item The $tH$ study explores the relative sign of top-Higgs  and W-Higgs couplings.\\ Small deviations from SM predictions could be associated with physics beyond the
-standard model (BSM) such as String Theory and  Supersymmetry.
-\end{itemize}
-\end{frame}
+#include <iostream>
 
-\begin{frame}
-\section{Introduction}
-\subsection{Standard Model}
-\frametitle{Standard Model}
-\begin{table}
-	\centering
-\begin{tabular}{cc}
-\includegraphics[width=6cm,height=5cm]{figures/sm1.png} & \includegraphics[width=5cm,height=5cm]{figures/sm.png}
-\end{tabular}
-\end{table}
-\end{frame}
+using namespace std;
 
-\begin{frame}
-\frametitle{Particles Properties}
-Table of particles in SM
-\begin{table}
-\tiny{\renewcommand{\arraystretch}{1.5}
-\begin{tabular}{|c|c|c|c|c|p{2.5cm}|}
-\hline 	
-Particle	& Mass (MeV/$c^2$) &Charge & spin &Lifetime (s) & Distance in lifetime (meters) \\ 
-\hline 
-Up ($u$)	& 2.2 & $\frac{2}{3}$ & $\frac{1}{2}$ & stable & -\\ 
-\hline 	
-Charm ($c$)	& 1280 &$\frac{2}{3}$ & $\frac{1}{2}$ & $ 1.1 \times 10^{-12}$ & 5.21$\times 10^{-3}$ \\ 
-\hline 
-Top	($t$)& 173100 & $\frac{2}{3}$ & $\frac{1}{2}$ & 5$\times$10$^{-25}$ &2.37$\times 10^{-15}$  \\ 
-\hline 
-Down ($d$)	& 4.6 &$-\frac{1}{3}$ & $\frac{1}{2}$ & Stable & - \\ 
-\hline 
-Strange ($s$)	& 96 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.24 \times 10^{-8}$ & 58.7 \\ 
-\hline 
-Bottom ($b$)	& 4180 &$-\frac{1}{3}$ & $\frac{1}{2}$ &$1.3 \times 10^{-12}$  & 6.16 $\times 10^{-3}$\\ 
-\hline 
-$W$ 	& 80379 &$\pm$1 & 1 & 3$\times$ 10$^{-25}$ & 1.42$\times 10^{-15}$\\ 
-\hline 
-$Z$ & 91187.6 &0 & 1 & 3$\times$ 10$^{-25}$ &1.42$\times 10^{-15}$ \\ 
-\hline
-Photon ($\gamma$) & 0 &0 & 1&Stable & - \\ 
-\hline
-Gluon ($g$)	& 0 &0 & 1&Stable & - \\ 
-\hline 
-Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
-\hline 
-Electron ($e$)& 0.511 & -1 &  $\frac{1}{2}$& Stable & - \\ 
-\hline 
-Muon ($\mu$)	& 105.7 & -1 & $\frac{1}{2}$ & 2.2$\times$10$^{-6}$ & 10419.85 \\ 
-\hline 
-$\tau$	& 1776.86 &-1 & $\frac{1}{2}$ & 2.9$\times$10$^{-13}$ & 1.37$\times 10^{-3}$\\ 	
-\hline 
-$\nu_e$	$\nu_\mu$ $\nu_\tau$& 0 & 0 & $\frac{1}{2}$ & Stable & -\\
-\hline 
-\end{tabular} 
-}
-\end{table}
-\tiny{Stable means no decay, or lifetime almost infinite. Particles speeds at 0.998c}
-\end{frame}
+void scanLikelihood(string version, string parName="mu", double range=2, int nrPoints=20)
+{
+  //Use a convenient helper struct to make opening the workspace and grabbing the objects easier
+  //See macros/ModelInfo.C
+  ModelInfo info(Form("_combined_%s_model.root",version.c_str(),version.c_str()),
+		 "combined",
+		 "ModelConfig",
+		 "obsData");
 
-%\begin{frame}
-%\subframetitle{Higgs mechanism}
-%\frametitle{Electroweak SM Lagrangian}
-%The Standard Model is a theory of fields for particles with spins 0, $\frac{1}{2}$ and 1. 
-%The  SM lagrangian 	
-%\begin{align*}
-%\mathcal{L}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{higgs} + \mathcal{L}_\text{yukawa}
-%\end{align*}
-%donde 
-%\begin{itemize}
-%	\item $\mathcal{L}_\text{gauge}$=$ -\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[G^{i\mu\nu}G^i_{\mu\nu}\right]$ 
-%	\begin{itemize}
-%		\item  $F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu $
-%		\item  $G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu $
-%	\end{itemize}
-%	\item $\mathcal{L}_f=i\bar{\Psi}_L \cancel{D}{\Psi}_L+i\bar{\psi}_R \cancel{D}{\psi}_R  $ is the kinematic term for fermions 
-%\scriptsize{
-%	\begin{itemize}
-%		\item $D_\mu {\Psi}_L=\left(\partial_\mu+igW_\mu+ig'Y_LB_\mu\right)\Psi_L$
-%		\item $D_\mu \psi_R=\left(\partial_\mu +ig' Y_RB_\mu\right)\psi_R $
-%		\item g and g' are boson coupling constants.
-%\footnote{\tiny{L(R) refers to Left and right fields.
-%Y is the  weak hypercharge,Y=T$^3$-Q.Q is charge of particle field and T is weak isospin. $T^3=\pm 1/2$ for left handed doublets and $T^3=0$ for right handed singlets.} }
-%\item $W_\mu=\sigma^iW^i_\mu$, where $\sigma^i$ are the pauli matrices.
-%	\end{itemize}
-%}
-%\end{itemize}
-%\begin{equation}
-%\begin{split}
-%\mathcal{L}=-\frac{1}{2}\text{Tr}\left[F^{\mu\nu}F_{\mu\nu} \right]+\bar{\Psi_L}i\gamma^\mu D_\mu \Psi_L  
-%+\text{Tr}\left[(D_\mu \Phi)^\dagger (D^\mu \Phi)\right]+\mu^2 \Phi^\dagger \Phi  \\
-%-\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2 & +\left(\frac{1}{2}\Psi_L^T Ch \Phi \Psi_L +h.c \right)
-%\end{split}
-%\end{equation}
-%The matrix C in the last term is the charge conjugation matrix acting on the spinors, h is a matrix of Yukawa couplings
-%\end{frame}
-
-\begin{frame}
-\subsection{Higgs mechanism}
-\frametitle{Electroweak SM Lagrangian}
-Higgs lagrangian 
-\begin{align}
-\mathcal{L}_{\text{Higgs}}=(D_\mu \Phi)^\dagger (D^\mu \Phi)-V(\Phi^\dagger \Phi)
-\end{align}
-
-with
-\begin{itemize}
-	\item $D_\mu \Phi = \left(\partial_\mu+(ig/2)\sigma^iW^i_\mu-i\frac{1}{2} g' B_\mu \right) \Phi $
-	\item $V(\Phi^\dagger \Phi)=-\mu^2 \Phi^\dagger \Phi +\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2, \quad \mu^2>0  $ 
-	\item $\Phi=\left(\begin{array}{c}
-	\phi^+ \\
-	\phi^0
-	\end{array} \right)  $ is a SU(2) doublet.
-	\item $\sigma^i$ are the Pauli matrices.
-\end{itemize}
-
-\begin{itemize}
-	\item $\Phi$ is higgs field which is a complex scalar field. $\Phi$
-	%\item  W$_\mu$ and B$_\mu$ are gauge bosons
-	%\item g and g are boson coupling constants.
-	\item $\lambda $ and $\mu^2$ are Higgs potential parameters
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{SM Lagrangian}
-Yukawa lagrangian
-\begin{align}
-\mathcal{L}_\text{yukawa}=\sum_{m,n}^{3}  \Gamma^u_{mn}\bar{q}_{m\text{,}L} \tilde{\Phi} u_{n\text{,}R}%+\Gamma^d_{mn}\bar{q}_{m\text{,}L} \Phi d_{n\text{,}R}+\Gamma^e_{mn}\bar{l}_{m\text{,}L} \Phi e_{n\text{,}R}+h.c
-\end{align}
-\scriptsize{where h.c is hermitian conjugate. m and n are flavors of quarks and leptons.
-\\
-The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between higgs doublet $\phi$ and the fermions.\\
-Choosing}
-\begin{align*}
-\Phi=-\frac{1}{2}\left(\begin{array}{c}
-0 \\
-v+h
-\end{array} \right) \label{vmin}
-\end{align*}
-\scriptsize{
-By using \ref{vmin} it on $\mathcal{L}_\text{yukawa}$, it is obtained for $u$ quark
-\begin{align*}
-\frac{\Gamma^u_{uu}v}{\sqrt{2}}(\bar{u_L}u_R+\bar{u_R}u_L)
-\end{align*}
-from which the masses for the fermions shown to be proportional to the Yukawa couplings
-\begin{align*}
-m_u=-\frac{\Gamma^u_{uu}v}{\sqrt{2}}
-\end{align*}}
-\end{frame}
-
-{\nologo
-\begin{frame}
-\subsection{Higgs production mechanisms and decays}
-\frametitle{Higgs production mechanisms}
-
-\begin{center}
-\includegraphics[scale=0.4]{figures/pg.png}
-\end{center}
-\small{Different Higgs production mechanism, from the most likely to least likely}
-\end{frame}
+  //Grab the parameter you want to scan the NLL over
+  RooArgSet params(*info.mc->GetNuisanceParameters(),*info.mc->GetParametersOfInterest());
+  RooRealVar* par = info.w->var(parName.c_str());
+  if (!par)
+  {
+    cout << "ERROR::Parameter doesn't exist: " << parName << endl;
+    params.Print("v");
+    exit(1);
   }
 
-{\nologo
-\begin{frame}
-\frametitle{$tH$ production mechanisms}
-\begin{center}
-\begin{figure} 
-\includegraphics[scale=0.4]{figures/tq.png} 
-\caption*{$tH$ mechanism. Higgs radiated from a top quark (left). Higgs radiated from a W boson (right)} 
-\label{th}
-\end{figure}
-\end{center}
-\end{frame} 
+  //Configure MINUIT
+  ROOT::Math::MinimizerOptions::SetDefaultMinimizer("Minuit2");
+  ROOT::Math::MinimizerOptions::SetDefaultStrategy(0);
+  ROOT::Math::MinimizerOptions::SetDefaultPrintLevel(1);
+
+  //Make sure your parameters are floating
+  TIterator* itr = params.createIterator();
+  RooRealVar* var;
+  while ((var=(RooRealVar*)itr->Next()))
+  {
+    var->setConstant(0);
   }
 
-\begin{frame}
-\frametitle{$tH$ production mechanisms}
-\begin{itemize}
-\item In a proton proton collision, the production cross section of the single top plus Higgs boson process is driven by a
-destructive interference of two main diagrams, where the Higgs couples to either
-the W boson or the top quark. 
-\item  A second process, where the Higgs and top quark
-are accompanied by a W boson ($tH$W) has similar behavior, albeit with a weaker interference
-pattern.
-\item However, in the presence of new physics, there may be relative opposite signs between the $tH$
-and WH couplings which lead to constructive interference and enhance the cross sections by
-an order of magnitude or more.
-\end{itemize}
-\end{frame}
+  //Build the NLL
+  RooNLLVar* nll = (RooNLLVar*)info.mc->GetPdf()->createNLL(*info.data, Constrain(params),
+							    GlobalObservables(*info.mc->GetGlobalObservables()),
+							    RooFit::Offset(1));
 
-\begin{frame}
-\frametitle{Cross section}
-\begin{itemize}
-\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
-\item Experimentally
-\begin{align}
-d\sigma=\frac{\text{number of particles scattered into solid angle} \Delta\Omega}{\text{(number of particles incident)(scattering centers/area)}}
-\end{align}
-\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$ 
-\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
-L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
-\begin{align}
-N_R=\sigma \text{L}
-\end{align}
-\end{itemize}
-\end{frame}
+  //Do an unconditional fit (all parameters floating)
+  minimize(nll);
 
-\begin{frame}
-\frametitle{Higgs production Cross section}
-\begin{table}
-	\caption*{Higgs boson production cross sections  in pp collisions for $\sqrt{s}=13$TeV  (in
-		pico barn).Integrated luminosity of 35.9 fb$^{-1}$ for Run 2\footnotemark}
-	\begin{tabular}{|c|c|c|}
-		\hline
-		Production mechanism &
-		$\sigma$ (picobarns pb)
-		&Number of events \\
-		\hline
-		ggF &
-		48.93 &
-		1756587\\
-		\hline
-		VBF &
-		3.78&
-		135702\\
-		\hline
-		WH & 1.35 & 48465\\
-		\hline
-		ZH &0.88 & 31592\\
-		\hline
-		t$\bar{t}$H &
-		0.50&
-		18255\\
-		\hline
-		$tH$	(only)&
-		0.015&
-		560.39\\
-		\hline
-	\end{tabular}
-\end{table}
+  //Save the value of the NLL and the best fit value of the parameter at this point
+  double nll_best = nll->getVal();
+  double muhat = par->getVal();
 
-\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
+  //Instantiate the arrays you'll use to save the scanned points
+  double* x_ary = new double[nrPoints+1];
+  double* y_ary = new double[nrPoints+1];
 
-\end{frame}
+  //Loop over each point in the scan, do a dit, and save the NLL and the parameter point
+  int counter=0;
+  bool passedMinimum = false;
+  for (int i=0;i<nrPoints;i++)
+  {
+    //Value of the parameter at this point in the scan
+    //double val = muhat - range + i / double(nrPoints-1) * 2*range;
+    double xmin=0;
+   double xmax=40;
 
-\begin{frame}
-\frametitle{Branching ratio}
-\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.
-\footnotemark.}
-\begin{align}
-\text{BR} =\frac{\Gamma_i}{\sum_{i}\Gamma_i}
-\end{align}
-\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
-Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
-\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
-\end{frame}
-
-\begin{frame}
-\frametitle{Higgs Branching ratios per channel}
-\begin{table}
-	\caption*{SM Higgs boson branching ratios for  $M_H$ =125 GeV}
-\begin{center}
-\begin{tabular}{|c|c|}
-	\hline
-	Higgs decay & Branching ratio (BR)\\
-	\hline
-	H $\rightarrow$ b$\bar{b}$ &
-	$50.82\%$ \\
-	\hline
-	H $\rightarrow$ $W^+W^-$ &
-	$21.5\%$ \\
-	\hline
-	H $\rightarrow$ $\tau^+ \tau^-$ &
-	$6.27\%$\\
-\hline
-	H $\rightarrow$ ZZ &
-$2.61\%$\\
-\hline
-	H $\rightarrow$ $\gamma\gamma$ &
-$0.227\%$\\
-\hline
-	H $\rightarrow$ Z$\gamma$ &
-$0.153\%$\\
-\hline
-	H $\rightarrow$ $\mu^+\mu^-$ &
-$0.0217\%$\\
-\hline
-\end{tabular}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{$\mu\mu$ same sign decay rate}
-\tiny{Table of decay chains for tH.  Expected number of $tH$ final states events for 35.9 fb$^{-1}$.l represents $\mu^{\pm},e^- , \tau^\pm$. }
-\begin{table}
-\renewcommand{\arraystretch}{0.55}
-\begin{tabular}{|p{8cm}|p{1.3cm}|c|}
-\hline
-Decay chain &BR&Events\\
-\hline 
-\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b$\mu^+\nu_\mu$  $q \bar{q}'$ } &\tiny{2.096 $\times$10$^{-3}$} &  1.173  \\
-\hline
-\tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.899 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.203 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$bW$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b $\mu^+ \nu_\mu$  $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau}$ b$\mu^+ \nu_\mu$  $q \bar{q}$} &\tiny{1.890$\times$10$^{-4}$}&0.105  \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu$b $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$  &
-\tiny{1.681 $\times$10$^{-4}$} & 0.094 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$b W$^+$W$^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}$b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau}$  b$ \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\tiny{3.045$\times$10$^{-5}$}& 0.017\\
-\hline
-\tiny{$tH \rightarrow$ W$^+$bZZ $\rightarrow$ $q \bar{q}$bZZ $\rightarrow$ $q \bar{q} $ b $\mu^+ \mu^- \mu^+ \mu^-$} & \tiny{1.966$\times$10$^{-5}$} &0.011\\
-\hline 
-\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ $\rightarrow$  $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} $b $\mu^+ \nu_\mu \bar{\nu_\tau} $  $q\bar{q}' \nu_\tau$ } &\tiny{1.549 $\times$10$^{-5}$} &  0.008  \\
-\hline
-%\tiny{$tH \rightarrow$W$^+$bZ$\gamma$ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- \gamma$} & \tiny{6.888$\times$10$^{-6}$}&0.003\\
-%\hline 
-%\tiny{$tH \rightarrow$W$^+$bZZ $\rightarrow$ $\mu^+ \nu_\mu$ b $\mu^+ \mu^- l^+l^-$} &\tiny{3.962$\times$10$^{-6}$ }&0.002\\
-%\hline 
-%%\tiny{$tH \rightarrow$ $\tau \nu_\tau $bZ$\gamma$ $\rightarrow$ $\mu^- \bar{\nu_\mu} \nu_\tau \nu_\tau$ b $\mu^+ \mu^- \gamma$} & 6.347$\times$10$^{-7}$ & 0.0003\\
-%%\hline 
-\end{tabular}
-\end{table}
-\end{frame}
-
-\begin{frame}
-\section{LHC and CMS}
-\subsection{LHC}
-\frametitle{LHC}
-	\begin{figure}
-		\centering
-	\includegraphics[scale=0.2]{figures/CERN's-accelerator-complex2013.jpg}
-	\caption*{LHC complex}
-	\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{LHC}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.6]{figures/lhc-u.png}
-	\caption*{Underground view of LHC complex}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{LHC parameters}
-\begin{minipage}[c]{0.48\textwidth}
-	\tiny
-\begin{table}
-	\caption*{Characteristics of LHC}
-\centering
-\begin{tabular}{|c|c|}
-			\hline
-			Quantity & Number \\
-			\hline
-			Circumference &  26 659 m \\
-			\hline
-			Number of magnets& 9593 \\
-			\hline
-			Nominal energy, protons & 6.5 TeV\\
-			\hline
-			Nominal energy, protons collisions &  13 TeV\\
-			\hline
-			Number of collisions per second &1 billion\\
-			\hline
-			No. of bunches per proton beam &  2808\\
-			\hline
-\end{tabular}
-\end{table}
-\end{minipage}
-\hfill
-\begin{minipage}[c]{0.48\textwidth}
-	\tiny
-	\begin{table}
-		\centering
-		\caption*{Accelerator operation energies}
-		\begin{tabular}{|c|c|}
-			\hline
-			Accelerator & Energy \\
-			\hline
-			Linac 2 &  50 MeV \\
-			\hline
-			PS Booster & 1.4 GeV \\
-			\hline
-			Proton Scyncroton (PS) & 25 GeV\\
-			\hline
-			SPS &  450 GeV\\
-			\hline
-			LHC & 6.5 TeV\\
-			\hline
-		\end{tabular}
-	\end{table}
-\end{minipage}
-\end{frame}
-
-\begin{frame}
-\subsection{CMS dectector}
-\frametitle{CMS detector}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.08]{figures/cms.png}
-		\caption*{Compact muon solenoid}
-	\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\frametitle{CMS detector}
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[scale=0.6]{figures/csc.png}
-	\caption*{Slide view of the CMS in terms of pseudorapidity $\eta=-\ln\left[\tan\left(\frac{\theta}{2}\right)\right]$}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{CMS detector}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.4]{figures/pp.png}
-	\caption*{\small A typical CMS event display of the Higgs boson decaying to four leptons with 2 muons (in red) and 2 electrons (in green) as final state signatures.}
-\end{figure}
-\end{frame}
-
-\begin{frame}
-\frametitle{CMS integrated luminosity}
-\begin{center}
-	\begin{figure}
-		\includegraphics[scale=0.3]{figures/cms_lumi.png}
-		\caption*{Integrated luminosity for CMS experiment }
-	\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\section{Event selection and reconstruction}
-\subsection{Topology of $tH$}
-\frametitle{Topology of events tH}
-The characteristics of the signal $tH$:
-
-\begin{multicols}{2}
-	\small{
-\begin{itemize}
-\item $t\rightarrow W$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
-\item $H\rightarrow$ $W^+$$W^-$
-
-\begin{list}{--}{}
-\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
-\item   \small{$W\rightarrow$ $q\bar{q}$}
-\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
-\end{list}
-\item a light-flavor quark 
-\item  A b-jet  
-\end{itemize}
-}
-\columnbreak
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.5]{figures/jet.png}
-\end{figure}
-\end{multicols}
-\end{frame}
-
-%\begin{frame}
-%\frametitle{Backgrounds}
-%\subsection{Backgrounds}
-%\begin{itemize}
-%	\item Backgrounds are considered information in the data that is not the signal. 
-%	\item Backgrounds share certain characteristics of the signal.
-%	\item Backgrounds are a big factor in the statistical study of the signal.
-%\end{itemize}
-%\end{frame}
-
-\begin{frame}\subsection{Main backgrounds}
-\frametitle{Main backgrounds}
-\tiny
-\begin{table}
-	\caption*{Main backgrounds and their same sign $\mu\mu$ decay process }
-	\centering
-	\begin{tabular}{|c|l|}
-		\hline
-		Background & Decay process \\
-		\hline
-		$t\bar{t}W$ &$t\bar{t}W$ $\rightarrow$ $W^+ b W^- \bar{b}$ $\mu^+\nu_\mu$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu$\\
-		\hline
-		$t\bar{t} Z$ & $t\bar{t} Z$ $\rightarrow$ $W^+ b$ $W^-\bar{b} \mu^+ \mu^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}\mu^+ \mu^-$ \\
-		\hline
-		$W^+ Z$ &$W^+ Z \rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^-$ \\
-		\hline 
-		$W^\pm$ $W^\pm$ & $W^+W^+$ $\rightarrow$$\mu^+\nu_\mu$$\mu^+ {\nu_\mu}$ \\
-		\hline 
-		$tZq$ & $tZq$ $\rightarrow$ $W^+$ $ b\mu^+ \mu^- q$ $\rightarrow$$\mu^+ \nu_\mu b$ $\mu^+\mu^- q$ \\
-		\hline 
-		$t\bar{t}t\bar{t}$ &$t\bar{t}t\bar{t}$ $\rightarrow$ $W^+ b$ $W^- \bar{b}$ $W^+ b$ $W^- \bar{b}$ $\rightarrow$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ $\mu^+ \nu_\mu b$ $\mu^- \bar{\nu_\mu} \bar{b}$ \\
-		\hline 
-		$W^+ W^- Z$ & $W^+ W^-$ $Z \rightarrow$ $\mu^+ \nu_\mu$ $\mu^- \bar{\nu_\mu} \mu^+ \mu^-$\\
-		\hline 
-		$ZZZ$ & $ZZZ \rightarrow$ $\mu^+ \mu^-\mu^+ \mu^-l^+ l^-$ \\
-		\hline 
-		$W^+ZZ$ &$W^+ZZ$ $\rightarrow$ $\mu^+ \nu_\mu \mu^+ \mu^- l^+l^-$ \\
-		\hline 
-		$tZW^+$ & $tZW^+ \rightarrow$ $W^+b \mu^+ \mu^- \mu^+ \nu_\mu \rightarrow \mu^+ \nu_\mu b \mu^+ \mu^- \mu^+ \nu_\mu$\\
-		\hline
-		$ZZ$ & $ZZ\rightarrow$ $\mu^+ \mu^- \mu^+ \mu^-$ \\
-		\hline
-		$t\bar{t}H$	& $t\bar{t}H$ $\rightarrow W^+b W^- \bar{b} W^+W^-$ $\rightarrow$ $\mu^+ \nu_\mu b$$\mu^- \bar{\nu_\mu}\bar{b}$ $\mu^+\nu_\mu$ $\mu^-\bar{\nu_\mu}$\\
-		\hline 
-	\end{tabular}
-	\label{back}
-\end{table} 
-\end{frame}
-
-\begin{frame}
-\subsection{Event selection}
-\frametitle{Event selection}
-In order to detect signal events and reject background, the following selections are applied. 
-\begin{itemize}
-	\item The events must contain two muons with the same sign.
-	\item Transverse moment $p_{t}$ > 25 GeV for the highest $p_t$ muon and $p_{t}$ > 15 GeV for the lowest $p_t$ muon.
-	\item A forward jet with $p_t$ > 40 GeV and $|\eta|$ > 2.4
-	\item One or more b-tagged jets with $|\eta|$ < 2.4
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\subsection{BDT}
-\frametitle{BDT}
-\small{
-	A decision tree takes a set of input features and splits input data recursively based on
-	those features.
-	Boosting is a method of combining many weak learners (trees) into a strong classifier. The features can be a mix of categorical and continuous data.\\
-	\vspace{10px}
-	BDT Variables}
-\tiny{
-	\begin{itemize}
-		\item	Trailing lepton $p_{t}$
-		\item 	Total charge of tight leptons
-		\item 	min $\Delta$R (lepton pairs)
-		\item 	$\Delta\phi$ between highest $p_t$ lepton pair
-		\item 	Number of jets with |$\eta$| < 2.4
-		\item	Number of non b-tagged jets with |$\eta$| > 1.0
-		\item	Maximum |$\eta$| for jets
-		\item	$\Delta\eta$ (most forward light jet, closest lepton)
-		\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
-		\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
-\end{itemize} }
-\end{frame}
-
-{\nologo
-	\begin{frame}
-	\Fontvi
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
-			  {Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
-			  	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
-			 {Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
-		\end{tabular}
-	\end{center}
-\end{frame}
+ double val= i*(xmax-xmin)/nrPoints;
+    //Save the unconditional point we had earlier at the appropriate point in the array
+    if (val > muhat && !passedMinimum)
+    {
+      passedMinimum = true;
+      x_ary[counter] = muhat;
+      y_ary[counter] = 0;
+      counter++;
     }
 
-{\nologo
-\begin{frame}
-\Fontvi
-\begin{center}
-	\begin{tabular}{cc}
-	\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
-\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
-{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
-		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-		\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
-		{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
-	\end{tabular}
-\end{center}
-\end{frame}
+    //Fix the parameter to its point in the scan and do the fit there
+    par->setVal(val);
+    par->setConstant(1);
+    minimize(nll);
+
+    //Save the -2*log(L(par) / L(par_hat))
+    double dnllx2 = 2*(nll->getVal()-nll_best);
+    x_ary[counter] = val;
+    y_ary[counter] = dnllx2;
+    counter++;
+    cout << "On point " << i+1 << " / " << nrPoints << ". " << parName << "=" << val << ", -2lnLambda=" << dnllx2 << " (best fit = " << muhat << ")" << endl;
   }
 
-{\nologo
-\begin{frame}
-\subsection{Previous results}
-\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
-\begin{minipage}[c]{0.45\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[scale=0.3]{figures/histo.png}
-	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[c]{.45\textwidth}
-	\small
-\begin{table}
-	\centering
-	\caption*{\tiny{Event yields for signal and backgrounds after the event selection for a integrated luminosity of 35.9 fb$^{-1}$.
-The uncertainties of yields include statistical and systematic \protect \footnotemark} }
-	\begin{tabular}{cc}
-		\hline
-		Process & Number of events \\
-		\hline
-		$t\bar{t}W$ & 68 $\pm$ 10 \\
-		$t\bar{t}Z$ & 25.9 $\pm$ 3.9\\
-		$WZ$ & 15.1$\pm$7.7\\
-		Rares & 20.9 $\pm$ 4.9\\
-		Fakes & 80.9 $\pm$9.4\\
-		$t\bar{t}H$ & 24.2 $\pm$ 2.1 \\
-		\hline
-		$tH$ (SM) & 2.14 $\pm$ 0.13\\
-		$tH$ ($k_t=-1$) &26.2 $\pm$ 2.2
-	\end{tabular}	
-	\label{tth-table}
-\end{table}
-%	\begin{figure}	\centering
-%	\includegraphics[width=\textwidth]{figures/sc.png}
-%	\caption*{\tiny{Observed and expected 95$\%$ C.L.
-upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
-The expected limit is derived from a background-only MC dataset.}}
-%	\end{figure}
-\end{minipage}
-\footnotetext{\tiny The CMS collaboration, \textit{Search for production of a Higgs boson and a single top
-			quark in multilepton final states in proton collisions at 13 TeV}, CMS-HIG-18-009, Phys. Rev. D 99, 092005}
-\end{frame}
+  //Graph the results
+  TCanvas *cs = new TCanvas("cs","cs",10,10,1200,900);
+  TGraph* graph = new TGraph(nrPoints+1, x_ary, y_ary);
+  graph->Draw("alp*");
+  graph->GetXaxis()->SetTitle(parName.c_str());
+  graph->GetYaxis()->SetTitle("-2 ln #lambda(#mu)");
+ graph->SetTitle();
+ graph->GetXaxis()->SetLimits(0,50);
+ graph->GetYaxis()->SetRangeUser(0,10);
+ graph->Draw("lp*");
+
+  TLine l;
+  l.SetLineStyle(2);
+  l.SetLineWidth(2);
+  l.SetLineColor(kRed);
+  l.DrawLine(0,1,50,1);
+  l.SetLineColor(kBlue);
+  l.DrawLine(0,4,50,4);
+  l.SetLineColor(kGreen+4);
+  l.DrawLine(0,9,50,9);
+
+TLatex lat ;
+lat.SetTextSize(0.03);
+lat.DrawLatex(45,1,"1#sigma (68.9#/%");
+
+TLatex lat2;
+lat.SetTextSize(0.03);
+lat.DrawLatex(45,4,"2#sigma");
+lat.DrawLatex(45,9,"3#sigma");
+
+cs->SaveAs("Likelihood.png");
+//cs->SaveAs("Likelihood-kt-1.png");
+
+/////////////////////////////////////////////////////////
+TCanvas *tm1 = new TCanvas("tm1","tm1",100,100,1200,900);
+tm1->Range(0,0,10,1);
+TH1F *hoto = new TH1F("hoto",";t_{#mu};f(t_{#mu})",1,0,10.9);
+TF1 *fa2 = new TF1("fa2","((1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.))",0,10);
+//fa2->SetParameters(x_ary);
+//fa2->SetTitle(" p-value for t_{#mu}  k_{t}=1 ;t_{#mu};P(t_{#mu})");
+hoto->SetStats(0);
+fa2->SetTitle();
+fa2->SetLineColor(kBlack);
+hoto->Draw();
+hoto->GetXaxis()->SetRangeUser(0,10.9);
+hoto->GetYaxis()->SetRangeUser(0,1.1);
+fa2->DrawIntegral("same");
+
+TF1 *fa3 = new TF1("fa3","((1/sqrt(2.*pi))*(1/sqrt(x))*exp(-x/2.))",0,10);
+fa3->SetLineColor(kBlue);
+fa3->Draw("same");
+///////////////////////////////////////////
+TLine l2;
+l2.SetLineStyle(2);
+l2.SetLineWidth(2);
+l2.SetLineColor(kRed);
+l2.DrawLine(1,0,1,1);
+l2.SetLineColor(kBlue);
+l2.DrawLine(4,0,4,1);
+l2.SetLineColor(kGreen+4);
+l2.DrawLine(9,0,9,1);
+lat.DrawLatex(1,1,"1#sigma");
+lat.DrawLatex(4,1,"2#sigma");
+lat.DrawLatex(9,1,"3#sigma");
+//////////////////////////////////////////////////////
+TArrow *ar1 = new TArrow(0,-0.03,1,-0.03,0.008,"<>");
+lat2.SetTextSize(0.03);
+lat2.SetTextColor(2);
+lat2.DrawLatex(0.32,-0.1,"68.3%");
+ar1->SetLineColor(2);
+ar1->Draw();
+///////////////////////////////////////////////////////
+TArrow *ar2 = new TArrow(0,-0.05,4,-0.05,0.01,"<>");
+ar2->SetLineColor(4);
+ar2->Draw();
+lat2.SetTextSize(0.03);
+lat2.SetTextColor(4);
+lat2.DrawLatex(4.32,-0.1,"95.4%");
+////////////////////////////////////////////////////////
+TArrow *ar3 = new TArrow(0,-0.07,9,-0.07,0.01,"<>");
+ar3->SetLineColor(kGreen+4);
+ar3->Draw();
+lat2.SetTextSize(0.03);
+lat2.SetTextColor(kGreen+4);
+lat2.DrawLatex(9.32,-0.1,"99.7%");
+
+TGaxis *axis5 = new TGaxis(10.9,0,10.9,1.1,0,1.1,510,"+L");
+//axis5->SetLabelFont(0.5); // Absolute font size in pixel (precision 3)
+axis5->SetLabelSize(0.04);
+axis5->SetTitle("P_{#mu}");
+axis5->Draw();
+
+cout<<fa3->Integral(0,4)<<endl;
+
+tm1->SaveAs("nos.png");
+
+//TCanvas *tm2 = new TCanvas("tm2","tm2",100,100,1200,900);
+//fa2->SetLineColor(kRed);
+//fa2->SetTitle();
+//fa2->GetXaxis()->SetTitle("t_{#mu}");
+//fa2->GetYaxis()->SetTitle("f(t_{#mu})");
+//fa2->GetXaxis()->SetLimits(0,10);
+//fa2->Draw();
+//tm2->SaveAs("tmu.png");
+
 }
-
-{\nologo
-\begin{frame}
-\frametitle{Distribution of events in the BDT discriminant}
-\begin{minipage}[b]{.48\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{figures/kos.png}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.48\textwidth}
-	\begin{figure}
-		\centering
-		\includegraphics[width=\textwidth]{figures/kos2.png}
-	\end{figure}
-\end{minipage}
-\begin{center}
-\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
-\end{center}
-\end{frame}
-}
-
-\begin{frame}
-\subsection{Systematic uncertainties}
-\frametitle{Systematic uncertainties}
-\begin{itemize}
-	\item The uncertainties on $t\bar{t}W$ and $t\bar{t}Z$ event yields are mainly due to the uncertainties of their production cross sections. 
-	\item The uncertainty on $WZ$ background is estimated using real data events in a three lepton control region. 
-	\item In the Rare backgrounds, which are not measured, a $50\%$ of uncertainty is assigned.
-	\item The uncertainty on the Fakes background is estimated using real data in a control region, defined by the muon identification criteria. 
-	\item For the Higgs processes $tH$ and $ttH$, the uncertainty are due to the theoretical parameters used in that simulation.
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\section{Statistical analysis}
-\frametitle{Fitting}
-	\begin{center}
-	\begin{figure}
-		\includegraphics[width=10.5cm]{figures/fit-box.png}
-		\caption*{}
-	\end{figure}
-\end{center}
-\end{frame}
-
-\begin{frame}
-\subsection{Likelihood model}
-\frametitle{Likelihood model}
-{\small \begin{itemize}
-\item To estimate the sensibility of the $tH$ signal, we define an Asimov dataset, made by replacing the ensemble of simulated backgrounds and signal by a single one. 
-\item The statistical uncertainty of the Asimov data is calculated as $\sqrt{n}$, with $n$ the number of events.\\
-\item The likelihood function is the product of Poisson probabilities for all bins
-\begin{align}
-	L(\mu,\alpha)=\prod_{j=1}^{N}\frac{(\mu s_j +b_j)^{n_j}}{n_j !}e^{-(\mu s_j+b_j)} \prod_{k=1}^M e^{\frac{-\alpha^2_k}{2}}
-\end{align}
-	where $N$ is the total number of bins, $n_j$ is the number of events in a bin $j$, $s_j$ is the number of signal events, $\mu$ is a parameter that modifies the signal strength and $b_j$ is the number of background events.
-\end{itemize}}
-\end{frame}
-
-\begin{frame}
-\frametitle{Likelihood model}
-{\small
-\begin{itemize}
-	\item $b_j$ is the sum of different background processes $k$
-	\begin{align}
-	b_j=\sum_k^M b_j^k(1+ \alpha_k \sigma_k)
-	\end{align}
-	$\alpha_k$ is the parameter that modifies the expected background prediction and $\sigma_k$ is the systematic uncertainty of the associated background.
-$\sigma_k$ for the backgrounds are shown in the Table of yields.
-		\item The fit is applied by minimizing the $-\log{L}$ (NLL) with respect to the parameter $\mu$ and $\alpha_k$.
-The minimization is performed by using the package ROOFIT.
-In the next slides, it shows the results of the model fitting using the Asimov data for the SM and the $k_t=-1$.
-\end{itemize}}
-\end{frame}
-
-\begin{frame}
-\subsection{Results}
-\frametitle{Results}
-\begin{minipage}{0.4\textwidth}
-	\begin{center}
-	\begin{figure}
-		\includegraphics[width=5.5cm,height=5cm]{figures/simple.png}
-		\caption*{\tiny{Post-fit signal and background yields for tH process in the SM. In the
-			box below each distribution, the ratio of the observed and  event yields is shown}}
-	\end{figure}
-\end{center}
-\end{minipage}\hfill \quad
-\begin{minipage}{0.4\textwidth}
-	\begin{center}
-	\begin{figure}
-		\includegraphics[width=5.5cm,height=5cm]{figures/simple-kt-1.png}
-		\caption*{\tiny{Post-fit signal and background yields for tH process in the $k_t$=-1. 
-	In the box below each distribution, the ratio of the observed and event yields is shown}}
-	\end{figure}
-\end{center}
-\end{minipage}
-\end{frame}
-
-\begin{frame}
-\section{Results}
-\frametitle{Results}
-	\begin{table}[ht!]
-		\centering
-		\caption*{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
-		\begin{tabular}{ccc}
-			\hline
-			Process & SM & $k_{t}$=-1 \\
-			\hline
-			$t\bar{t}W$ & 68$\pm$8.9& 68 $\pm$8.9 \\
-			$t\bar{t}Z$ & 25.9$\pm$3.8&25.9$\pm$3.8\\
-			$WZ$ & 15.1$\pm$7.4& 15.1$\pm$7.4\\
-			Rares & 20.8$\pm$4.8& 20.8$\pm$4.8 \\
-			Fakes & 80.9$\pm$9.0& 80.9$\pm$8.9 \\
-			$t\bar{t}H$ & 24.2$\pm$2.0 & 24.2$\pm$2.0 \\
-			\hline
-			$tH$& 2.1$\pm$16.5 &26.2$\pm$13.1 
-		\end{tabular}
-		\label{table1}
-	\end{table}
- Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
-\end{frame}
-
-\begin{frame}
-\frametitle{Results}
-\framesubtitle{Likelihood scan}
-{\small
-	\begin{itemize}
-\item Due to the large background, the signal strength for the Asimov data with 35.9 fb$^{-1}$ is consistent with zero.
-Therefore, we estimate an upper limit on the signal strength at 95$\%$ confidence level.
-\item We can define the likelihood ratio
-\begin{align}
-\lambda(\mu,\alpha)=\frac{L(\mu,\alpha)}{L(\hat{\mu},\hat{\alpha})}
-\end{align}
-Where $\hat{\alpha}$ and $\hat{\mu}$ are the parameters obtained in the previous section which correspond to the minimal of the NLL.
-\item To determine an upper limit on the strength parameter $\mu$, we use the following statistical test
-\begin{align}
-q(\mu,\alpha)= -2\ln{\lambda} 
-\end{align}
-\item High values of $q$ represent greater incompatibility between the data and the fit model.
-$q$ is a random variable with a $\chi^2$ distribution.
-\end{itemize}
-}
-\end{frame}
-
-\begin{frame}
-\frametitle{Results}
-\framesubtitle{Likelihood scan for an integrated luminosity of 35.9 fb$^{-1}$}
-\begin{minipage}{0.5\textwidth}
-	\begin{center}
-		\begin{figure}
-			\includegraphics[width=6cm,height=5cm]{figures/Likelihood.png}
-			\caption*{Likelihood scan for k$_t$=1 (SM)}
-		\end{figure}
-	\end{center}
-\end{minipage}\hfill
-\begin{minipage}{0.5\textwidth}
-	\begin{center}
-		\begin{figure}
-			\includegraphics[width=6cm,height=5cm]{figures/kt-1/Likelihood-kt-1.png}
-			\caption*{Likelihood scan for k$_t$=-1}
-		\end{figure}
-	\end{center}
-\end{minipage}
-\end{frame}
-
-{\nologo
-	\begin{frame}
-	\frametitle{Extrapolation of luminosity for SM }
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/simple.png} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/simple-150.png}\\ 
-			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/simple-300.png}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/simple-3000.png}\\
-			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-{\nologo
-	\begin{frame}
-	\frametitle{Likelihood scan for SM }
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/Likelihood.png} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/150fb/Likelihood.png}\\ 
-			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/300fb/Likelihood.png}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/3000fb/Likelihood.png}\\
-			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-{\nologo
-	\begin{frame}
-	\frametitle{Extrapolation of luminosity for $k_t=-1$}
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/simple-kt-1.png} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/simple-150-kt-1.png}\\ 
-			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/simple-300-kt-1.png}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/simple-3000-kt-1.png}\\
-			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-{\nologo
-	\begin{frame}
-	\frametitle{Likelihood scan for  $k_t=-1$}
-	\begin{center}
-		\begin{tabular}{cc}
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/35.9fb/Likelihood-kt-1.png} &
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/150fb/Likelihood.png}\\ 
-			\scriptsize{35.9 fb$^{-1}$} & \scriptsize{150 fb$^{-1}$} \\
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/300fb/Likelihood.png}&
-			\includegraphics[width=5.5cm,height=3cm]{figures/kt-1/3000fb/Likelihood.png}\\
-			\scriptsize{300 fb$^{-1}$} & \scriptsize{3000 fb$^{-1}$} \\
-		\end{tabular}
-	\end{center}
-\end{frame}
-}
-
-\begin{frame}
-\frametitle{Results}
-\framesubtitle{Upper limit}
-\tiny{
-\begin{table}[ht!]
-	\caption*{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models.}
-	\begin{tabular}{|c|c|c|c|c|}
-		\hline
-		Luminosity (fb$^{-1}$)	&$\mu$ (SM) &$\mu$ (SM) upper limit & $\mu$ ($k_t$=-1) &$\mu$ ($k_t$=-1) upper limit \\
-		\hline
-		35.9 & 1.0 $\pm$ 7.7 & 17 & 1.0 $\pm$ 0.5 & 2.3 \\
-		\hline
-		150& 1.0 $\pm$ 6.7& 11 & 1.0 $\pm$ 0.4 &1.8\\
-		\hline
-		300&1.0 $\pm$ 4.3 &8.7 & 1.0 $\pm$ 0.3 &1.5 \\
-		\hline
-		3000&1.0 $\pm$ 1.7 & 4.3 &	 1.0 $\pm$ 0.1 & 1.1\\
-		\hline
-	\end{tabular}
-	\label{upper}
-\end{table}
-}
-\end{frame}
-
-%\begin{frame}
-%\section{Conclusions}
-%\frametitle{Conclusions}
-%\begin{itemize}
-%	\item We analyzed the $tH$ process produced from PP collisions for the production of $\mu\mu$ final states   
-%	\item We discussed about events selections for the 2016 Run 2 from CMS.
-%	\item The creation of an Asimov model with systematic uncertainties to make a minimization (fit) and obtain a fit which is compatible with Standard Model.
-%	\item Generation of likelihood scan for the exclusion of data and obtain the probability of detection of a Higgs boson.
-%	\item Generating simulations for predict results with higher luminosities, according to the future experiments. 
-%\end{itemize}
-%\end{frame}
-
-\begin{frame}
-\frametitle{Conclusions}
-\begin{itemize}
-\item The results of the analysis for the SM case indicates that it is impossible to detect a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
-\item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
-\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical.
-\item It requires a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
-\end{itemize}
-\end{frame}
-
-	\begin{thebibliography}{99}
-		\bibliographystyle{unsrt}
-	\begin{frame}
-	\tiny
-%	\section{References}
-	\frametitle{References}
-	\bibliographystyle{amsalpha}
-	\bibitem{1}Gross F. \textit{Relativistic quantum mechanics and field theory}, 1994 ,WllEY-VCH Verlag GmbH \& Co. KGaA
-	\bibitem{2} Griffiths, D. \textit{Introduction to Elementary Particles}, $2^\frac{\circ}{}$ edition, 2008,WllEY-VCH Verlag GmbH \& Co. KGaA
-		\bibitem{2}The CMS collaboration, \textit{Search for production of a Higgs boson and a single top
-	quark in multilepton final states in proton collisions at 13 TeV}, CMS-HIG-18-009, Phys. Rev. D 99, 092005
-	\bibitem{3}Verkerke W \textit{Dealing with systematic uncertainties} 2014. From
-\url{https://indico.cern.ch/event/287744/contributions/1641261/attachments/535763/738679/Verkerke_Statistics_3.pdf}
-\bibitem{5} ATLAS and CMS
-Collaborations, \textit{Combined measurement of the Higgs boson mass in
-	pp collisions at $\sqrt{s}$= 7 and 8 TeV with the ATLAS and CMS experiments}, Phys. Rev. Lett.
-114 (2015) doi:10.1103/PhysRevLett.114.191803, arXiv:1503.07589
-\bibitem{4} Cowan G. , Cranmer K., Gross E. , Vitells O.\textit{ Asymptotic formulae for
-	likelihood-based tests of new physics} 2013 , arXiv:1007.1727
-\bibitem{7}CMS collaboration \textit{Search for tHq production in multilepton final states at 13 TeV} ,2017,CMS AN-16-378
-\bibitem{6}CMS collaboration \textit{High-Luminosity Large Hadron Collider (HL-LHC)}, 2017,CERN-2017-007-M
-\end{frame}
-\end{thebibliography}
-
-%\begin{frame}
-%\section{Supportive slides}
-%\huge{Back up}
-%\end{frame}
-
-%\begin{frame}
-%\frametitle{Sources of uncertainty on event yields}
-%\begin{itemize}
-%	\item Luminosity measurement: ~2.6$\%$.
-%	\item Data/MC scale factors for lepton selection (ID, iso) and trigger efficiencies ~5$\%$ per lepton.
-%	\item Choice of PDF set:
-%	\begin{itemize}
-%		\item 3.7$\%$ for tHq
-%		\item ~4$\%$ for tHW t$\bar{t}$W, t$\bar{t}$Z, t$\bar{t}$H 
-%		\item Scale uncertainties: 12$\%$, 4 for t$\bar{t}$W, 10$\%$ for t$\bar{t}$Z, +5.8/-9.2$\%$ for t$\bar{t}$H.
-%	\end{itemize}
-%	\item Background: WZ, ZZ sample modelling and statistics: ~50$\%$.
-%	\item Rare SM (tZ,tri-bosons, WWqq, tttt) : 50$\%$
-%	\item Fake rate estimation:
-%	The predicted event yield has a normalization uncertainty of ~30-50$\%$ \cite{7}
-%\end{itemize}
-%\end{frame}
-
-%Closure:  hay jets en los eventos de tt  (gluon-gluon -> tt + gluon ) que se pasan como muones.  jet -> muon =  fake
-
-%Fakes:   proceso de QCD  que genera muchos  jets (por ejemplo  gluon-gluon -> gluons, quarks)  :    jet -> muons  
-%fakes are estimated data
-
-%\footnote[1]{Due to existence of many uncertainties, it is neccesary to sum all the uncertainties.
-When there is no Correlation, the uncertanties must be summed as the square root of the squares of each uncertainty}
-
-%\begin{frame}
-%\frametitle{Sources of systematic uncertainty}
-%Detector-simulation related uncertainty
-%\begin{itemize}
-%\item Calibrations (electron, jet energy scale)
-%%\item Efficiencies (particle ID, reconstruction)
-%\item Resolutions (jet energy, muon momentum)
-%\end{itemize}
-%Theoretical uncertainties
-%\begin{itemize}
-%\item  Factorization/Normalization scale of MC generators
-%\item Choice of MC generator (ME and/or PS, e.g. Herwig vs Pythia)
-%\end{itemize}
-%Monte Carlo Statistical uncertainties
-%\begin{itemize}\item Statistical uncertainty of simulated samples\cite{2} \end{itemize}
-%\end{frame}
-
-%\begin{frame}
-%\begin{figure}
-%	\centering
-%	\includegraphics[scale=0.5]{figures/compare_variables}
-%	\caption*{Signal and background kinematic distributions}
-%\end{figure}
-%\end{frame}
-
-%\begin{frame}
-%\frametitle{Results}
-%\framesubtitle{Likelihood scan}
-%\begin{itemize}
-%	\item Likelihood function (often simply the likelihood) is a function of the
-%	parameters of a statistical model, given specific observed data.
-%	\item Likelihood functions play a key role in frequentist inference,
-%	especially methods of estimating a parameter from a set of
-%	statistics.
-%	\item In informal contexts, "likelihood" is often used as a synonym for
-%	probability.
-%\end{itemize}
-%\end{frame}
-
-\end{document}

### 2019-11-26 presentacion_hiram/presentacion-tesis.tex
n

--- 2019-11-25 presentacion_hiram/presentacion-tesis.tex
@@
 \usepackage{multicol}
+\usepackage{multirow}
+\usepackage{hhline}
 \usepackage{listings}
@@
 \newcommand\Fontvi{\fontsize{4}{7.2}\selectfont}
-\begin{document}
+
  \author{\tiny
@@
  %\setbeamertemplate{navigation symbols}{}
+
+\begin{document}
+
 \begin{frame}
@@
 \end{frame}
-
-%\begin{frame}
-%\section{Overview and motivation}
-%\frametitle{Overview}
-%\begin{itemize}
-%\item Through this project it was studied the production of Higgs boson in association with a
-%single top quark ($tH$) in proton-proton collisions. 
-%This mechanism of production of the Higgs boson has not been observed before by any
-%experiment.
-%\item Standard Model and the Higgs production mechanism
-%\item A brief introduction to the LHC and CMS
-%\item Event selection and reconstruction of the tH signal
-%\item Creation and application of a statistical model for the analysis of events 
-%\item Making predictions for the future experiments.
-%\end{itemize}
-%\end{frame}
 
@@
 \end{frame}
-
-%\begin{frame}
-%\subframetitle{Higgs mechanism}
-%\frametitle{Electroweak SM Lagrangian}
-%The Standard Model is a theory of fields for particles with spins 0, $\frac{1}{2}$ and 1. 
-%The  SM lagrangian 	
-%\begin{align*}
-%\mathcal{L}=\mathcal{L}_\text{gauge}+\mathcal{L}_f +\mathcal{L}_\text{higgs} + \mathcal{L}_\text{yukawa}
-%\end{align*}
-%donde 
-%\begin{itemize}
-%	\item $\mathcal{L}_\text{gauge}$=$ -\frac{1}{4}\left[F^{\mu\nu}F_{\mu\nu}\right]-\frac{1}{4}\left[G^{i\mu\nu}G^i_{\mu\nu}\right]$ 
-%	\begin{itemize}
-%		\item  $F^{\mu \nu}=\partial_\mu B_\nu -\partial_\nu B_\mu $
-%		\item  $G^{i\mu\nu}=\partial_\mu W^i_\nu -\partial_\nu W^i_\mu -g\epsilon^{ijk}W^j_\mu W^k_\nu $
-%	\end{itemize}
-%	\item $\mathcal{L}_f=i\bar{\Psi}_L \cancel{D}{\Psi}_L+i\bar{\psi}_R \cancel{D}{\psi}_R  $ is the kinematic term for fermions 
-%\scriptsize{
-%	\begin{itemize}
-%		\item $D_\mu {\Psi}_L=\left(\partial_\mu+igW_\mu+ig'Y_LB_\mu\right)\Psi_L$
-%		\item $D_\mu \psi_R=\left(\partial_\mu +ig' Y_RB_\mu\right)\psi_R $
-%		\item g and g' are boson coupling constants.
-%\footnote{\tiny{L(R) refers to Left and right fields.
-%Y is the  weak hypercharge,Y=T$^3$-Q.Q is charge of particle field and T is weak isospin. $T^3=\pm 1/2$ for left handed doublets and $T^3=0$ for right handed singlets.} }
-%\item $W_\mu=\sigma^iW^i_\mu$, where $\sigma^i$ are the pauli matrices.
-%	\end{itemize}
-%}
-%\end{itemize}
-%\begin{equation}
-%\begin{split}
-%\mathcal{L}=-\frac{1}{2}\text{Tr}\left[F^{\mu\nu}F_{\mu\nu} \right]+\bar{\Psi_L}i\gamma^\mu D_\mu \Psi_L  
-%+\text{Tr}\left[(D_\mu \Phi)^\dagger (D^\mu \Phi)\right]+\mu^2 \Phi^\dagger \Phi  \\
-%-\frac{1}{2}  \lambda (\Phi^\dagger \Phi)^2 & +\left(\frac{1}{2}\Psi_L^T Ch \Phi \Psi_L +h.c \right)
-%\end{split}
-%\end{equation}
-%The matrix C in the last term is the charge conjugation matrix acting on the spinors, h is a matrix of Yukawa couplings
-%\end{frame}
 
@@
 \hline 
-Higgs ($H$)	& 125.18 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
+Higgs ($H$)	& 125180 &0 & 0& 1.56 $\times$ $10^{-22}$ & 7.39$\times 10^{-13}$ \\ 
 \hline 
@@
 \item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
-L is called luminosity and it is measured in cm$^{-1}$s$^{-1}$.\cite{6}
+L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
 \end{itemize}
@@
 \hline
+\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.96 \\
+\hline
 \tiny{$tH \rightarrow $W$^+$bW$^+$W$^-$ $\rightarrow$ $\mu^+\nu_\mu$b$\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\tiny{3.37 $\times$ 10$^{-4}$} &0.89 \\
-\hline
-\tiny{$tH \rightarrow$ W$^+$b $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu$ b $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\tiny{3.637$\times$10$^{-4}$}&0.96 \\
 \hline
@@
 \section{Event selection and reconstruction}
-\subsection{Topology of $tH$}
-\frametitle{Topology of events tH}
+\subsection{Characteristics of $tH$}
+\frametitle{Characteristics of $tH$}
 The characteristics of the signal $tH$:
@@
 \end{frame}
-
-%\begin{frame}
-%\frametitle{Backgrounds}
-%\subsection{Backgrounds}
-%\begin{itemize}
-%	\item Backgrounds are considered information in the data that is not the signal. 
-%	\item Backgrounds share certain characteristics of the signal.
-%	\item Backgrounds are a big factor in the statistical study of the signal.
-%\end{itemize}
-%\end{frame}
 
@@
 \end{table}
-%	\begin{figure}	\centering
-%	\includegraphics[width=\textwidth]{figures/sc.png}
-%	\caption*{\tiny{Observed and expected 95$\%$ C.L.
-upper limit on the tH + t$\bar{t}$H cross section times H $\rightarrow$ WW $+$ $\tau\tau$ $+$ ZZ branching fraction for different 20 values of the coupling ratio $\kappa_t /\kappa_v$ .
-The expected limit is derived from a background-only MC dataset.}}
-%	\end{figure}
+
 \end{minipage}
@@
 %		\includegraphics[width=10.5cm]{figures/fit-box.png}
-		\caption*{}
+%		\caption*{}
+		%\caption*{}
 %	\end{figure}
@@
  \begin{table}[ht]
+ {  \tiny
  		\caption[Results of $\mu$ and upper limits for SM and $k_t$=-1]{Results of $\mu$ and upper limits for Asimov extrapolations for SM  and $k_t$=-1 models at 95$\%$ confidence level.}
@@
  		\label{upper}
+                }
  	\end{table}
-
-}
  \end{frame}
@@
 \begin{itemize}
-\item The results of the analysis for the SM case indicates that it is impossible to give an evidence of a Higgs boson using same sign dimuon channel in the $tH$ process due to the low number of events and a huge uncertainty.
-\item For the SM scenario the expected uncertainty even at the largest luminosities is not enough to observe the signal and only an upper limit can be placed.
-\item For the $k_t$=-1, the uncertainty is low due to higher number of events for $tH$ process and it is possible to detect a Higgs boson, but this model is purely theoretical.
-\item It requires a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
+\item The results of the analysis for the SM case indicates that it is impossible to give an evidence of a Higgs boson using same sign dimuon channel in the $tH$ process due to large statistical uncertainty.
+\item For the SM scenario the limit in the signal strength for 3000 fb$^{-1}$ is 4.3 at 95$\%$ of confidence level.
+\item For the inverted coupling scenario ($k_t$ =-1), the uncertainty after the fit was around 50$\%$ for a luminosity of 35.9 fb$^{-1}$. This is due to the larger expected number of signal events.
+\item For the modified $k_t$=-1 model for 3000 fb$^{-1}$, it is possible to measure a hypothetical signal with 10$\%$ of uncertainty.
+\item It is required a new analysis that includes more channels such as three leptons in the final state for improve the sensibility of the signal.
 \end{itemize}

### 2019-11-26 tesis_hiram/Chapter1/chapter1.tex
fixes
fix crossection
th yields
kt

@@
     \includegraphics[scale=0.3]{Chapter1/sm1.png}
-    \caption[Standard Model to date]{Standard Model to date\cite{smtable}}
+    \caption[Standard Model to date]{List of particles in the Standard Model and their properties\cite{smtable}}
     \label{sm1}
@@
 \section{Higgs mechanism}
+\label{sec:higgsmechanism}
 In the SM, mathematically the particles are described in form of fields. The SM for electroweak interactions is described as a gauge theory with a symmetry group SU(2)$\otimes$U(1)
@@
 \hline
-$tH$	& 0.015 & 560.39\\
+$tH$	& 0.074 & 2655\\
 \hline
@@
 diagrams shown in Figure \ref{newth} provides a unique opportunity to study the relative sign of the Higgs top coupling.
-In practice, we do not directly measure the Yukawa couplings. Instead, modifier parameters $k_t$ and $k_V$ are introduced in the analysis to represent deviations from the Yukawa coupling values. 
+In practice, we do not directly measure the Yukawa couplings.
+Instead, modifier parameters $k_t$ and $k_V$ are introduced in the analysis to represent deviations from the Yukawa coupling values described in Section~\ref{sec:higgsmechanism}. 
 In the SM, the two diagrams interfere negatively and thereby suppress the production cross section.

### 2019-11-26 tesis_hiram/Chapter3/chapter3.tex
th yields
disclaimer

@@
 The rest of the processes that also generate a pair of muons with the same sign will be considered backgrounds.
+
+The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}, the Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
+
 \section{Signal Event Topology} 
@@
 
- %The W bosons can also decay to quarks that generate jets. 
 Due to the small cross section of the $tH$ process, the amount of $tH$ events is low compared to other Higgs production processes. 
 Table \ref{tdecay} shows several processes that generate same sign muon events for $t$H. These numbers do not consider the detection efficiency.
- %But also tH process can generate the final states from $\tau$ decays but with a low probability.
-Some of them have probability near zero, but not impossible.
-%In graphics, these low probability processes would be very small figures that barely manifest.
-\pagebreak
-%For the tH process, the largest contribution comes from Higgs decays to WW (about 75$\%$), followed
- %y $\tau \tau$ (about 20$\%$) and ZZ (about 5$\%$).
 
@@
 \end{figure}
-%Quarks and gluons only exist in bound states.
-Because of it, we cannot isolate quarks except the top quark because of their decay times that don't form a bound state.
-When two quarks are separated, the strong force interacting between them increases.
-The energy transforms into quark anti-quark pairs.
-The hadronization results in a jet of particles.
+
 \begin{table}[ht]
@@
 		\hline 
-		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$ $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} & 1.173 \\
+		\small{$tH \rightarrow$ $W^+bW^+ W^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\mu^+\nu_\mu$ $q \bar{q}'$ } &\small{2.096 $\times$10$^{-3}$} & 5.58 \\
 		\hline
-		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.899 \\
+		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.96 \\
 		\hline
-		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\mu^+ \nu_\mu b$ $ \mu^+ \nu_\mu \bar{\nu_\tau} l^-\bar{\nu_l} \nu_\tau$} &\small{3.637$\times$10$^{-4}$}&0.203 \\
+		\small{$tH \rightarrow W$$^+ b$$W^+$ $W^-$ $\rightarrow$ $\mu^+\nu_\mu b$ $\mu^+\nu_\mu$ $l^- \bar{\nu_l}$ } &\small{3.37 $\times$ 10$^{-4}$} &0.89 \\
 		\hline
-		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$ $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$ $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.105 \\
+		\small{$tH \rightarrow$ $W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu$ $q\bar{q}$ $\rightarrow$ $\mu^+ \nu_\mu$ $\bar{\nu_\tau}$ $\bar{\nu_\tau} b\mu^+ \nu_\mu$ $q \bar{q}$} &\small{1.890$\times$10$^{-4}$}&0.50 \\
 		\hline
 		\small{$tH \rightarrow W^+ b \tau^+ \tau^-$ $\rightarrow$ $\mu^+$ $\nu_\mu b$ $\nu_\tau$ $\mu^+$ $\nu_\mu \bar{\nu_\tau}$} $q \bar{q}$ &
-		\small{1.681 $\times$10$^{-4}$} & 0.094 \\
+		\small{1.681 $\times$10$^{-4}$} & 0.44 \\
 		\hline
-		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.017\\
+		\small{$tH \rightarrow W^+ b$ $W^+ W^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$ $\rightarrow$ $\mu^+\nu_\mu$ $ \bar{\nu_\tau} \bar{\nu_\tau} b \mu^+ \nu_\mu l^- \bar{\nu_l}$} &\small{3.045$\times$10$^{-5}$}& 0.08\\
 		\hline
-		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q} b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.011\\
+		\small{$tH \rightarrow W^+ bZZ$ $\rightarrow$ $q \bar{q} bZZ$ $\rightarrow$ $q \bar{q} b \mu^+ \mu^- \mu^+ \mu^-$} & \small{1.966$\times$10$^{-5}$} &0.05\\
 		\hline 
-		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ $\rightarrow$ $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} & 0.008 \\
+		\small{$tH \rightarrow$ $W^+ b$ $\tau^+ \tau^-$ $\rightarrow$ $\tau^+ \bar{\nu_\tau}b$ $\mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ $\rightarrow$ $\mu^+ \nu_\mu \bar{\nu_\tau}\bar{\nu_\tau} b \mu^+ \nu_\mu \bar{\nu_\tau} $ $q\bar{q}' \nu_\tau$ } &\small{1.549 $\times$10$^{-5}$} & 0.04 \\
 		\hline
@@
 The features can be a mix of categorical and continuous data.
-The BDT training is performed using several event variables.
-In this analysis, the BDT discriminant was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds.
-The variables used for the BDT were the following:
+The BDT training is performed using several event variables and was trained to discriminate against $t\bar{t}V$ background, because this background is one of the largest backgrounds.
+The variables used for the BDT~\cite{th1} were the following:
 

### 2019-11-27 tesis_hiram/Chapter3/chapter3.tex
n

@@
 
-The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}, the Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
+The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}.
+Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
 

### 2019-11-27 tesis_hiram/Chapter3/chapter3.tex
fixes

@@
 The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}.
-Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
+%Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
+Monte Carlo simulations and event yields shown below, and used in the statistical analysis described in the next chapter, are obtained from this publication.
 

### 2019-12-03 plotting/TMVAClassification2.C
n

@@ -1,0 +1,541 @@
+/// \file
+/// \ingroup tutorial_tmva
+/// \notebook -nodraw
+/// This macro provides examples for the training and testing of the
+/// TMVA classifiers.
+///
+/// As input data is used a toy-MC sample consisting of four Gaussian-distributed
+/// and linearly correlated input variables.
+/// The methods to be used can be switched on and off by means of booleans, or
+/// via the prompt command, for example:
+///
+///     root -l ./TMVAClassification.C\(\"Fisher,Likelihood\"\)
+///
+/// (note that the backslashes are mandatory)
+/// If no method given, a default set of classifiers is used.
+/// The output file "TMVA.root" can be analysed with the use of dedicated
+/// macros (simply say: root -l <macro.C>), which can be conveniently
+/// invoked through a GUI that will appear at the end of the run of this macro.
+/// Launch the GUI via the command:
+///
+///     root -l ./TMVAGui.C
+///
+/// You can also compile and run the example with the following commands
+///
+///     make
+///     ./TMVAClassification <Methods>
+///
+/// where: `<Methods> = "method1 method2"` are the TMVA classifier names
+/// example:
+///
+///     ./TMVAClassification Fisher LikelihoodPCA BDT
+///
+/// If no method given, a default set is of classifiers is used
+///
+/// - Project   : TMVA - a ROOT-integrated toolkit for multivariate data analysis
+/// - Package   : TMVA
+/// - Root Macro: TMVAClassification
+///
+/// \macro_output
+/// \macro_code
+/// \author Andreas Hoecker
+
+
+#include <cstdlib>
+#include <iostream>
+#include <map>
+#include <string>
+
+#include "TChain.h"
+#include "TFile.h"
+#include "TTree.h"
+#include "TString.h"
+#include "TObjString.h"
+#include "TSystem.h"
+#include "TROOT.h"
+
+#include "TMVA/Factory.h"
+#include "TMVA/DataLoader.h"
+#include "TMVA/Tools.h"
+#include "TMVA/TMVAGui.h"
+
+int TMVAClassification( )
+{
+   // The explicit loading of the shared libTMVA is done in TMVAlogon.C, defined in .rootrc
+   // if you use your private .rootrc, or run from a different directory, please copy the
+   // corresponding lines from .rootrc
+
+   // Methods to be processed can be given as an argument; use format:
+   //
[…]

### 2019-12-05 presentacion_hiram/presentacion-tesis.tex
n

@@
 \usepackage[makeroom]{cancel}
-%\usetheme{Frankfurt}
+\usetheme{Rochester}
+%\usecolortheme{dove}
+%\usetheme{Pittsburgh}
 \usepackage{tikz} 
@@
 
- \author{\tiny
+ \author{\scriptsize
+ 	Universidad de Sonora\\
+ 	\vspace{5px}
+ 	Divisi\'on de Ciencias Exactas y Naturales\\
+ 	\vspace{5px}
+ 	Departamento de Investigaci\'on en F\'isica\\
+ 	   \vspace{5px}
    L.F. Hiram Ernesto Dami\'an\\
+   Defensa de tesis para obtener el grado de \\
+      Maestr\'ia en Ciencias (F\'isica)\\
          \vspace{5px}
@@
    Jos\'e Feliciano Ben\'itez Rubio\\
-   \vspace{5px}
-   Maestr\'ia en Ciencias (F\'isica)\\
-   \vspace{5px}
-   Departamento de Investigacion en F\'isica }
+   \vspace{5px}}
  \title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
@@
  \newcommand{\nologo}{\setbeamertemplate{logo}{}}
- \institute{Universidad de Sonora}
  \date{\small November 25$^{th}$ 2019}
@@
 \begin{frame}
+	\frametitle{Table of contents}
 \tiny
@@
 \begin{frame}
-\subsection{Higgs mechanism}
+\subsection{Electroweak SM Lagrangian}
 \frametitle{Electroweak SM Lagrangian}
@@
 \begin{itemize}
-\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
+	\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.
 	\begin{align}
@@
 	\end{align}
+\item Cross section describes the likelihood of two particles interacting under certain conditions\cite{1}\cite{6}
 %\item Experimentally
@@
 \item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$
-\item The reaction rate $N_R$ is determined by the total cross section $\sigma$ and the incident flux L.\\
-L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
+
+\item L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
 \end{itemize}
@@
 \end{table}
-
 \footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
-
 \end{frame}
@@
 \frametitle{Branching ratio}
-\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.
-\footnotemark.}
+\small{In particle physics, the branching ratio for a decay process is the ratio of the number of particles which decay via a specific decay mode with respect to the total number of particles which decay via all decay modes.}
 \begin{align}
@@
 \end{align}
-\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.
-Since the dimension of $\Gamma$ is the inverse of time, in our system of natural units, it is measured in inverse seconds} .%it has the same dimension as mass (or energy).}
-\footnote[0]{\tiny{Cleaves H.J. (2011) Branching Ratio. In: Gargaud M. et al. (eds) Encyclopedia of Astrobiology. Springer, Berlin, Heidelberg} }
+\small{Where $\Gamma=\sum_i\Gamma_i$ is the total decay width (sum of all partial widths) of the particle and is related to lifetime of the particle: $\Gamma=1/\tau$.}
+%it has the same dimension as mass (or energy).}
 \end{frame}
@@
 	\begin{frame}
+		\Fontvi
+		\begin{center}
+			\begin{tabular}{cc}
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
+				{Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
+				{Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
+			\end{tabular}
+		\end{center}
+	\end{frame}
+}
+
+{\nologo
+	\begin{frame}
+		\Fontvi
+		\begin{center}
+			\begin{tabular}{cc}
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
+				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
+				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
+				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
+			\end{tabular}
+		\end{center}
+	\end{frame}
+}
+
+{\nologo
+\begin{frame}
 \subsection{Previous results}
@@
 %\begin{frame}
-%\section{Statistical analysis}
+\section{Statistical analysis}
 %\frametitle{Fitting}
@@
 \begin{frame}
-\section{Results}
 \frametitle{Results}
@@
 \begin{frame}
+	\subsection{Extrapolation to higher luminosity}
 \frametitle{Results}
@@
 \begin{frame}
+	\section{Conclusions}
 \frametitle{Conclusions}
@@
 
-\begin{frame}
-\section{Supportive slides}
-\huge{Back up}
-\end{frame}
-
-{\nologo
-	\begin{frame}
-		\Fontvi
-		\begin{center}
-			\begin{tabular}{cc}
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
-				{Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
-				{Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
-			\end{tabular}
-		\end{center}
-	\end{frame}
-}
-
-{\nologo
-	\begin{frame}
-		\Fontvi
-		\begin{center}
-			\begin{tabular}{cc}
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
-				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
-				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
-			\end{tabular}
-		\end{center}
-	\end{frame}
-}
+%\begin{frame}
+%\section{Supportive slides}
+%\huge{Back up}
+%\end{frame}
 

### 2019-12-05 plotting/TMVAClassification2.C
n

@@ -59,7 +59,7 @@
 #include "TMVA/Tools.h"
 #include "TMVA/TMVAGui.h"
 
-int TMVAClassification( )
+int TMVAClassification2( )
 {
    // The explicit loading of the shared libTMVA is done in TMVAlogon.C, defined in .rootrc
    // if you use your private .rootrc, or run from a different directory, please copy the
@@ -156,8 +156,8 @@ int TMVAClassification( )
 
 
 
-   signalTree->Add("/home/hiram/Documents/tHqCMSAnalysis/BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_*.root");
-   background->Add("/home/hiram/Documents/tHqCMSAnalysis/BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_*.root");
+   signalTree->Add("../BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_*.root");
+   background->Add("../BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_*.root");
 
    // Create a ROOT output file where TMVA will store ntuples, histograms, etc.
    TString outfileName( "TMVA.root" );

### 2019-12-05 plotting/TMVAClassification2.C
n

@@ -190,6 +190,16 @@ int TMVAClassification2( )
    //dataloader->AddVariable( "myvar2 := var1-var2", "Expression 2", "", 'F' );
    dataloader->AddVariable( "abs(fj_eta)", "fwd jet |eta|", "", 'F' );
    dataloader->AddVariable( "l1_pt", "lead muon pT", "GeV", 'F' );
+  /////////////////////////////////////////////////////////////////
+   dataloader->AddVariable( "l2_pt", "sublead muon pT", "GeV", 'F' );
+   dataloader->AddVariable( "ncj", "Number of jets with pT>25", "GeV", 'F' );
+   dataloader->AddVariable( "dR_l1_l2", "minimum #Delta R", "", 'F' );
+   dataloader->AddVariable( "deta_fj_b1", "#eta fwd jet and b-jet", "", 'F' );
+   dataloader->AddVariable( "deta_fj_l", "#eta fwd jet and cl", "", 'F' );
+   dataloader->AddVariable( "nfj", "number untagged jets", "", 'F' );
+   dataloader->AddVariable( "dphi_l1_l2", "#phi lepton high pT", "", 'F' );
+   dataloader->AddVariable( "l1_ch+l2_ch", "sum of charges", "", 'F' );
+
 
    // You can add so-called "Spectator variables", which are not used in the MVA training,
    // but will appear in the final "TestTree" produced by TMVA. This TestTree will contain the

### 2019-12-06 presentacion_hiram/presentacion-tesis.tex
n

@@
  	Universidad de Sonora\\
- 	\vspace{5px}
+ 	\vspace{1px}
  	Divisi\'on de Ciencias Exactas y Naturales\\
- 	\vspace{5px}
+ 	\vspace{1px}
  	Departamento de Investigaci\'on en F\'isica\\
- 	   \vspace{5px}
-   L.F. Hiram Ernesto Dami\'an\\
+ 	   \vspace{1px}
+   \textbf{L.F. Hiram Ernesto Dami\'an}\\
    Defensa de tesis para obtener el grado de \\
       Maestr\'ia en Ciencias (F\'isica)\\
-         \vspace{5px}
+         \vspace{1px}
    Director:\\
-   \vspace{5px}
+   \vspace{1px}
    Jos\'e Feliciano Ben\'itez Rubio\\
-   \vspace{5px}}
+\vspace{1px}
+11 de Diciembre de 2019}
  \title{Study of Higgs plus single top production using events with a same sign dimuon  at the Large Hadron Collider}
  %\subtitle{}
+ \date{}
  \logo{\includegraphics[scale=0.1]{unison-logo.png}}
  \newcommand{\nologo}{\setbeamertemplate{logo}{}}
- \date{\small November 25$^{th}$ 2019}
  %\subject{}
@@
 \subsection{BDT}
-\frametitle{BDT}
+\frametitle{Multivariable discriminator algorithm}
 \small{
@@
 	\begin{frame}
+		\frametitle{Kinematic variables}
 		\Fontvi
@@
 	\begin{frame}
+	\frametitle{Kinematic variables}
 		\Fontvi
@@
 }
+
+{\nologo
+\begin{frame}
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[scale=0.5]{figures/bdt1}
+		\caption*{BDT training}
+	\end{figure}
+\end{frame}}
 
@@
 \subsection{Results}
-\frametitle{Results}
+\frametitle{Post -fit Results}
 \begin{minipage}{0.4\textwidth}
@@
 \begin{frame}
-\frametitle{Results}
+\frametitle{Post -fit Results}
 	\begin{table}[ht!]
@@
 	\subsection{Extrapolation to higher luminosity}
-\frametitle{Results}
-\framesubtitle{Likelihood scan}
+\frametitle{Likelihood scan}
 {\small
@@
 \begin{frame}
-\frametitle{Results}
-\framesubtitle{Likelihood scan for an integrated luminosity of 35.9 fb$^{-1}$}
+\frametitle{Likelihood scan for an integrated luminosity of 35.9 fb$^{-1}$}
 \begin{minipage}{0.5\textwidth}
@@
  \begin{frame}
- \frametitle{Results}
- \framesubtitle{Upper limit}
+ \frametitle{Upper limit}
  \begin{table}[ht]

### 2019-12-06 plotting/TMVAClassification2.C

@@ -126,8 +126,8 @@ int TMVAClassification2( )
    Use["SVM"]             = 0;
    //
    // Boosted Decision Trees
-   Use["BDT"]             = 1; // uses Adaptive Boost
-   Use["BDTG"]            = 0; // uses Gradient Boost
+   Use["BDT"]             = 0; // uses Adaptive Boost
+   Use["BDTG"]            = 1; // uses Gradient Boost
    Use["BDTB"]            = 0; // uses Bagging
    Use["BDTD"]            = 0; // decorrelation + Adaptive Boost
    Use["BDTF"]            = 0; // allow usage of fisher discriminant for node splitting

### 2019-12-06 plotting/bdt.C

@@ -1,0 +1,55 @@
+void bdt(){
+
+TFile *f= new TFile("TMVA.root");
+
+TTree *t = (TTree*)f->Get("dataset/TrainTree");
+TTree *t2= (TTree*)f->Get("dataset/TestTree");
+
+TH2F *cs =(TH2F*)f->Get("dataset/CorrelationMatrixS");
+TH2F *cb =(TH2F*)f->Get("dataset/CorrelationMatrixB");
+
+
+TH1F H1("H1","",60,-1,1); //signal
+ TH1F H2("H2","",60,-1,1); //background
+H1.SetLineColor(kRed);
+H2.SetLineColor(kBlue);
+
+t->Draw("BDTG>>H1","classID==0");
+t2->Draw("BDTG>>H1","classID==0");
+t->Draw("BDTG>>H2","classID==1");
+t2->Draw("BDTG>>H2","classID==1");
+H1.Scale(1.0/H1.Integral());
+H2.Scale(1.0/H2.Integral());
+
+TCanvas *C = new TCanvas("C","C",100,100,1200,900);
+H2.Draw("hist");
+H1.Draw("histsame");
+H2.SetStats(0);
+H2.SetXTitle("BDT Discriminant");
+H2.SetYTitle("Events normalized to unit area");
+auto legend = new TLegend(0.6,0.7,0.65,0.8);
+legend->AddEntry("H1","Signal","l");
+legend->AddEntry("H2","Background","l");
+legend->SetBorderSize(0);
+legend->SetTextSize(.05);
+legend->SetEntrySeparation(0.5);
+legend->Draw();
+
+C->Print("n.eps");
+C->Clear();
+  //TPad *pad1 = new TPad("pad1","This is pad1",0.2,0.2,0.8,0.8);
+  //pad1->Draw();
+  //pad1->cd();               // pad1 becomes the current pad]
+
+cs->Draw("colz");
+C->SaveAs("CMS.eps");
+
+C->Clear();
+  //TPad *pad2 = new TPad("pad2","This is pad1",0.1,0.1,0.9,0.9);
+  //pad2->Draw();
+  //pad1->cd();               // pad1 becomes the current pad]
+
+cb->Draw("colz");
+C->SaveAs("CMB.eps");
+
+}

### 2019-12-07 plotting/TMVAClassification2.C
n

@@ -160,7 +160,7 @@ int TMVAClassification2( )
    background->Add("../BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_*.root");
 
    // Create a ROOT output file where TMVA will store ntuples, histograms, etc.
-   TString outfileName( "TMVA.root" );
+   TString outfileName( "TMVA8.root" );
    TFile* outputFile = TFile::Open( outfileName, "RECREATE" );
 
    // Create the factory object. Later you can choose the methods
@@ -196,9 +196,9 @@ int TMVAClassification2( )
    dataloader->AddVariable( "dR_l1_l2", "minimum #Delta R", "", 'F' );
    dataloader->AddVariable( "deta_fj_b1", "#eta fwd jet and b-jet", "", 'F' );
    dataloader->AddVariable( "deta_fj_l", "#eta fwd jet and cl", "", 'F' );
-   dataloader->AddVariable( "nfj", "number untagged jets", "", 'F' );
+   //dataloader->AddVariable( "nfj", "number untagged jets", "", 'F' );
    dataloader->AddVariable( "dphi_l1_l2", "#phi lepton high pT", "", 'F' );
-   dataloader->AddVariable( "l1_ch+l2_ch", "sum of charges", "", 'F' );
+  //dataloader->AddVariable( "l1_ch+l2_ch", "sum of charges", "", 'F' );
 
 
    // You can add so-called "Spectator variables", which are not used in the MVA training,

### 2019-12-07 plotting/bdt.C

@@ -1,41 +1,106 @@
 void bdt(){
 
 TFile *f= new TFile("TMVA.root");
-
+TFile *d= new TFile("TMVA6.root");
+TFile *q= new TFile("TMVA8.root");
+/////////////////////////
+///4 variables//////
 TTree *t = (TTree*)f->Get("dataset/TrainTree");
 TTree *t2= (TTree*)f->Get("dataset/TestTree");
-
+/////////////////////////
+///6 variables//////
+TTree *t3 = (TTree*)d->Get("dataset/TrainTree");
+TTree *t4= (TTree*)d->Get("dataset/TestTree");
+/////////////////////////
+///8 variables//////
+TTree *t5 = (TTree*)q->Get("dataset/TrainTree");
+TTree *t6= (TTree*)q->Get("dataset/TestTree");
+//////////////////////////////////////////////
 TH2F *cs =(TH2F*)f->Get("dataset/CorrelationMatrixS");
 TH2F *cb =(TH2F*)f->Get("dataset/CorrelationMatrixB");
 
 
-TH1F H1("H1","",60,-1,1); //signal
- TH1F H2("H2","",60,-1,1); //background
+TH1F H1("H1","",40,-1,1); //signal
+TH1F H2("H2","",40,-1,1); //background
+
+TH1F H3("H3","",40,-1,1); //signal
+TH1F H4("H4","",40,-1,1); //background
+
+TH1F H5("H5","",40,-1,1); //signal
+TH1F H6("H6","",40,-1,1); //background
+
 H1.SetLineColor(kRed);
 H2.SetLineColor(kBlue);
+H3.SetLineColor(kRed+4);
+H4.SetLineColor(kBlue+4);
+H5.SetLineColor(kAzure+3);
+H6.SetLineColor(kGreen+3);
 
 t->Draw("BDTG>>H1","classID==0");
 t2->Draw("BDTG>>H1","classID==0");
 t->Draw("BDTG>>H2","classID==1");
 t2->Draw("BDTG>>H2","classID==1");
+
+t3->Draw("BDTG>>H3","classID==0");
+t4->Draw("BDTG>>H3","classID==0");
+t3->Draw("BDTG>>H4","classID==1");
+t4->Draw("BDTG>>H4","classID==1");
+
+t5->Draw("BDTG>>H5","classID==0");
+t6->Draw("BDTG>>H5","classID==0");
+t5->Draw("BDTG>>H6","classID==1");
[…]

### 2019-12-09 plotting/bdt.C
n

@@ -35,6 +35,13 @@ H3.SetLineColor(kRed+4);
 H4.SetLineColor(kBlue+4);
 H5.SetLineColor(kAzure+3);
 H6.SetLineColor(kGreen+3);
+  H1.SetLineWidth(6);
+  H2.SetLineWidth(6);
+  H3.SetLineWidth(6);
+  H4.SetLineWidth(6);
+  H5.SetLineWidth(6);
+  H6.SetLineWidth(6);
+
 
 t->Draw("BDTG>>H1","classID==0");
 t2->Draw("BDTG>>H1","classID==0");

### 2019-12-09 plotting/bdt.C
n

@@ -20,27 +20,27 @@ TH2F *cs =(TH2F*)f->Get("dataset/CorrelationMatrixS");
 TH2F *cb =(TH2F*)f->Get("dataset/CorrelationMatrixB");
 
 
-TH1F H1("H1","",40,-1,1); //signal
-TH1F H2("H2","",40,-1,1); //background
+TH1F H1("H1","",20,-1,1); //signal
+TH1F H2("H2","",20,-1,1); //background
 
-TH1F H3("H3","",40,-1,1); //signal
-TH1F H4("H4","",40,-1,1); //background
+TH1F H3("H3","",20,-1,1); //signal
+TH1F H4("H4","",20,-1,1); //background
 
-TH1F H5("H5","",40,-1,1); //signal
-TH1F H6("H6","",40,-1,1); //background
+TH1F H5("H5","",20,-1,1); //signal
+TH1F H6("H6","",20,-1,1); //background
 
-H1.SetLineColor(kRed);
-H2.SetLineColor(kBlue);
-H3.SetLineColor(kRed+4);
-H4.SetLineColor(kBlue+4);
-H5.SetLineColor(kAzure+3);
-H6.SetLineColor(kGreen+3);
-  H1.SetLineWidth(6);
-  H2.SetLineWidth(6);
-  H3.SetLineWidth(6);
-  H4.SetLineWidth(6);
-  H5.SetLineWidth(6);
-  H6.SetLineWidth(6);
+H1.SetLineColor(kBlack);
+H2.SetLineColor(kBlack);
+H3.SetLineColor(kRed);
+H4.SetLineColor(kRed);
+H5.SetLineColor(kAzure);
+H6.SetLineColor(kAzure);
+  H1.SetLineWidth(4);
+  H2.SetLineWidth(4);
+  H3.SetLineWidth(4);
+  H4.SetLineWidth(4);
+  H5.SetLineWidth(4);
+  H6.SetLineWidth(4);
 
 
 t->Draw("BDTG>>H1","classID==0");
@@ -72,35 +72,35 @@ H6.Scale(1.0/H6.Integral());
 TCanvas *C = new TCanvas("C","C",100,100,1200,900);
 H6.Draw("hist");
 H1.Draw("histsame");
-H3.Draw("histsame");
+//H3.Draw("histsame");
 H5.Draw("histsame");
 H2.Draw("histsame");
-H4.Draw("histsame");
+//H4.Draw("histsame");
 
 H6.SetStats(0);
 H6.SetXTitle("BDT Discriminant");
[…]

### 2019-12-11 presentacion_hiram/presentacion-tesis.tex
n

@@
 
+\setbeamercolor*{frametitle}{bg=white}
+
  \author{\scriptsize
@@
  	Departamento de Investigaci\'on en F\'isica\\
- 	   \vspace{1px}
+ 	   \vspace{5px}
    \textbf{L.F. Hiram Ernesto Dami\'an}\\
@@
       Maestr\'ia en Ciencias (F\'isica)\\
-         \vspace{1px}
+         \vspace{5px}
    Director:\\
@@
    Jos\'e Feliciano Ben\'itez Rubio\\
-\vspace{1px}
+\vspace{5px}
 11 de Diciembre de 2019}
@@
 \item The $tH$ study explores the relative sign of top-Higgs  and W-Higgs couplings.\\ Small deviations from SM predictions could be associated with physics beyond the
-standard model (BSM) such as Supersymmetry.
+standard model (BSM)..
 \end{itemize}
@@
 \\
-The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between higgs doublet $\phi$ and the fermions.\\
+The matrices $\Gamma_{mn}$ describe the so called Yukawa couplings between Higgs doublet $\phi$ and the fermions.\\
 Choosing}
@@
 
-\item L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
+\item L is called luminosity and it is measured in cm$^{2}$s$^{-1}$.\cite{6}
 \end{itemize}
@@
 \end{table}
-\footnotetext[1]{\tiny{Data taken from The cern collaborarion “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
+\footnotetext[1]{\tiny{Data taken from The CERN collaboration “Higgs Physics the HL-LHC and HE-LHC” 2019, CERN-LPCC-2018-04}}
 \end{frame}
@@
 	H $\rightarrow$ b$\bar{b}$ &
-	$50.82\%$ \\
+	$58.4\%$ \\
 	\hline
@@
 \begin{frame}
-\subsection{CMS dectector}
+\subsection{CMS detector}
 \frametitle{CMS detector}
@@
 \begin{itemize}
-\item $t\rightarrow W$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
+\item $t\rightarrow W^+$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
 \item $H\rightarrow$ $W^+$$W^-$
@@
 \begin{list}{--}{}
-\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu^\pm$,$e^-$  $\tau^\pm$} 
-\item   \small{$W\rightarrow$ $q\bar{q}$}
+\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu$,$e^-$  $\tau$} 
+\item   \small{$W\rightarrow$ $q\bar{q'}$}
 %\item \small{$W$ bosons decay leptonically resulting in a signature of two same-sign leptons }
@@
 \tiny{
-	\begin{itemize}
-		\item	Trailing lepton $p_{t}$
-		\item 	Total charge of tight leptons
+	\begin{enumerate}
+		\item	$p_t$ of the sub leading leptons
+		\item 	jets with largest value of $|\eta|$
+		\item 	Number of jets with high $p_t$ and |$\eta$| < 2.4
+		\item	Number of jets with |$\eta$| > 1.0
+		\item	$\Delta\eta$ (most forward jet, closest lepton)
+		\item	$\Delta\eta$ (most forward jet and b-tagged jet)
 		\item 	min $\Delta$R (lepton pairs)
 		\item 	$\Delta\phi$ between highest $p_t$ lepton pair
-		\item 	Number of jets with |$\eta$| < 2.4
-		\item	Number of non b-tagged jets with |$\eta$| > 1.0
-		\item	Maximum |$\eta$| for jets
-		\item	$\Delta\eta$ (most forward light jet, closest lepton)
-		\item	$\Delta\eta$ (most forward light jet, hardest loosely b-tagged jet)
-		\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
-\end{itemize} }
+	%	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
+\end{enumerate} }
 \end{frame}
@@
 		\centering
-		\includegraphics[scale=0.5]{figures/bdt1}
-		\caption*{BDT training}
+		\includegraphics[scale=0.48]{figures/bdt-8var}
+		\caption*{\scriptsize BDT training}
 	\end{figure}
@@
 \begin{frame}
-\subsection{Previous results}
-\frametitle{Previous results for $t\bar{t}H$+$tH$ production}
+\subsection{Event distributions and yields}
+\frametitle{Event distributions and yields}
 \begin{minipage}[c]{0.45\textwidth}
@@
 	\centering
-	\includegraphics[scale=0.3]{figures/histo.png}
-	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon, for training against $t\bar{t}V$ }}
+	\includegraphics[scale=0.18]{figures/kos.png}
+	\caption*{\tiny{Pre-fit classifier outputs for same sign dimuon }}
 \end{figure}
@@
 			quark in multilepton final states in proton collisions at 13 TeV}, CMS-HIG-18-009, Phys. Rev. D 99, 092005}
-\end{frame}
-}
-
-{\nologo
-\begin{frame}
-\frametitle{Distribution of events in the BDT discriminant}
-\begin{minipage}[b]{.48\textwidth}
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{figures/kos.png}
-\end{figure}
-\end{minipage}
-\hfill
-\begin{minipage}[b]{.48\textwidth}
-	\begin{figure}
-		\centering
-		\includegraphics[width=\textwidth]{figures/kos2.png}
-	\end{figure}
-\end{minipage}
-\begin{center}
-\small{SM signal and backgrounds (Left) and $k_t$=-1 model (Right).}
-\end{center}
 \end{frame}

### 2019-12-11 plotting/TMVAClassification2.C
n

@@ -189,14 +189,14 @@ int TMVAClassification2( )
    //dataloader->AddVariable( "myvar1 := var1+var2", 'F' );
    //dataloader->AddVariable( "myvar2 := var1-var2", "Expression 2", "", 'F' );
    dataloader->AddVariable( "abs(fj_eta)", "fwd jet |eta|", "", 'F' );
-   dataloader->AddVariable( "l1_pt", "lead muon pT", "GeV", 'F' );
+  // dataloader->AddVariable( "l1_pt", "lead muon pT", "GeV", 'F' );
   /////////////////////////////////////////////////////////////////
    dataloader->AddVariable( "l2_pt", "sublead muon pT", "GeV", 'F' );
    dataloader->AddVariable( "ncj", "Number of jets with pT>25", "GeV", 'F' );
    dataloader->AddVariable( "dR_l1_l2", "minimum #Delta R", "", 'F' );
    dataloader->AddVariable( "deta_fj_b1", "#eta fwd jet and b-jet", "", 'F' );
    dataloader->AddVariable( "deta_fj_l", "#eta fwd jet and cl", "", 'F' );
-   //dataloader->AddVariable( "nfj", "number untagged jets", "", 'F' );
+   dataloader->AddVariable( "nfj", "number untagged jets", "", 'F' );
    dataloader->AddVariable( "dphi_l1_l2", "#phi lepton high pT", "", 'F' );
   //dataloader->AddVariable( "l1_ch+l2_ch", "sum of charges", "", 'F' );
 

### 2019-12-11 plotting/bdt.C

@@ -1,7 +1,7 @@
 void bdt(){
 
-TFile *f= new TFile("TMVA.root");
-TFile *d= new TFile("TMVA6.root");
+TFile *f= new TFile("TMVA4.root");
+//TFile *d= new TFile("TMVA6.root");
 TFile *q= new TFile("TMVA8.root");
 /////////////////////////
 ///4 variables//////
@@ -9,8 +9,8 @@ TTree *t = (TTree*)f->Get("dataset/TrainTree");
 TTree *t2= (TTree*)f->Get("dataset/TestTree");
 /////////////////////////
 ///6 variables//////
-TTree *t3 = (TTree*)d->Get("dataset/TrainTree");
-TTree *t4= (TTree*)d->Get("dataset/TestTree");
+//TTree *t3 = (TTree*)d->Get("dataset/TrainTree");
+//TTree *t4= (TTree*)d->Get("dataset/TestTree");
 /////////////////////////
 ///8 variables//////
 TTree *t5 = (TTree*)q->Get("dataset/TrainTree");
@@ -31,16 +31,21 @@ TH1F H6("H6","",20,-1,1); //background
 
 H1.SetLineColor(kBlack);
 H2.SetLineColor(kBlack);
-H3.SetLineColor(kRed);
-H4.SetLineColor(kRed);
+//H3.SetLineColor(kRed);
+//H4.SetLineColor(kRed);
 H5.SetLineColor(kAzure);
 H6.SetLineColor(kAzure);
   H1.SetLineWidth(4);
   H2.SetLineWidth(4);
-  H3.SetLineWidth(4);
-  H4.SetLineWidth(4);
+  //H3.SetLineWidth(4);
+  //H4.SetLineWidth(4);
   H5.SetLineWidth(4);
   H6.SetLineWidth(4);
+
+ H1.SetLineStyle(kDashed);
+H2.SetLineStyle(kDashed);
+H5.SetLineStyle(kDashed);
+H6.SetLineStyle(kDashed);
 
 
 t->Draw("BDTG>>H1","classID==0");
@@ -48,10 +53,10 @@ t2->Draw("BDTG>>H1","classID==0");
 t->Draw("BDTG>>H2","classID==1");
 t2->Draw("BDTG>>H2","classID==1");
 
-t3->Draw("BDTG>>H3","classID==0");
-t4->Draw("BDTG>>H3","classID==0");
-t3->Draw("BDTG>>H4","classID==1");
[…]

### 2019-12-11 presentacion_hiram/presentacion-tesis.tex
n

@@
    \vspace{1px}
-   Jos\'e Feliciano Ben\'itez Rubio\\
+  Dr. Jos\'e Feliciano Ben\'itez Rubio\\
 \vspace{5px}
@@
 %\end{align}
-\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{-2}$
-
-\item L is called luminosity and it is measured in cm$^{2}$s$^{-1}$.\cite{6}
+\item Cross sections are expressed in barns , where 1 barn=$10^{-34}$ cm$^{2}$
+
+\item L is called luminosity and it is measured in cm$^{-2}$s$^{-1}$.\cite{6}
 \end{itemize}
@@
 		\item	$p_t$ of the sub leading leptons
-		\item 	jets with largest value of $|\eta|$
+		\item 	Maximum  $|\eta|$ of any  (untagged)  jet (forward jet)
 		\item 	Number of jets with high $p_t$ and |$\eta$| < 2.4
-		\item	Number of jets with |$\eta$| > 1.0
-		\item	$\Delta\eta$ (most forward jet, closest lepton)
-		\item	$\Delta\eta$ (most forward jet and b-tagged jet)
-		\item 	min $\Delta$R (lepton pairs)
-		\item 	$\Delta\phi$ between highest $p_t$ lepton pair
+		\item	Number of untagged jets with |$\eta$| > 1.0
+		\item	$|\Delta\eta|$ between a forward light jet and closest lepton
+		\item	$|\Delta\eta|$ between a forward light jet and a b-tagged jet
+		\item 	Minimum $\Delta$R between any two leptons
+		\item 	$\Delta\phi$ of the highest $p_t$ same-sign lepton pair
 	%	\item	$\Delta\eta$ (most forward light jet, 2nd hardest loosely b-tagged jet)
@@
 				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
-				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest pt)} & {Distribution of events of $\Delta\phi$ between the higher pt pair of leptons } \\
+				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest $p_t$)} & {Distribution of events of $\Delta\phi$ between the higher $p_t$ pair of leptons } \\
 			\end{tabular}
@@
 \begin{frame}
+	\frametitle{BDT Training Result}
 	\begin{figure}[ht]
@@
 		\includegraphics[scale=0.48]{figures/bdt-8var}
-		\caption*{\scriptsize BDT training}
 	\end{figure}
@@
 \subsection{Results}
-\frametitle{Post -fit Results}
+\frametitle{Post-fit Results}
 \begin{minipage}{0.4\textwidth}
@@
 \begin{frame}
-\frametitle{Post -fit Results}
+\frametitle{Post-fit Results}
 	\begin{table}[ht!]
 		\centering
-		\caption*{Postfit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
+		\caption*{Post-fit yields for the fit to the Asimov data corresponding to 35.9 fb$^{-1}$. The uncertainty given is the combined statistical plus systematic.}
 		\begin{tabular}{ccc}
@@
 	\end{table}
- Prefit uncertainty is statistical only. Postfit uncertainty is statistical + systematic.
-\end{frame}
-
-\begin{frame}
-	\subsection{Extrapolation to higher luminosity}
+ Pre-fit uncertainty is statistical only. Post-fit uncertainty is statistical + systematic.
+\end{frame}
+
+\begin{frame}
+	\subsection{Extrapolation to high luminosity}
 \frametitle{Likelihood scan}
@@
 	\begin{frame}
-	\frametitle{Extrapolation of luminosity for SM }
+	\frametitle{Extrapolation to high luminosity for SM }
 	\begin{center}
@@
 	\begin{frame}
-	\frametitle{Extrapolation of luminosity for $k_t=-1$}
+	\frametitle{Extrapolation to high luminosity for $k_t=-1$ scenario}
 	\begin{center}
@@
 	\begin{frame}
-	\frametitle{Likelihood scan for  $k_t=-1$}
+	\frametitle{Likelihood scan for $k_t=-1$ scenario}
 	\begin{center}

### 2019-12-11 presentacion_hiram/presentacion-tesis.tex
n

@@
 \begin{itemize}
-\item $t\rightarrow W^+$$^+$b$\rightarrow$ $l^+ \nu_\mu b$
+\item $t\rightarrow W^+$b$\rightarrow$ $l^+ \nu_\mu b$
 \item $H\rightarrow$ $W^+$$W^-$
@@
 \begin{list}{--}{}
-\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu$,$e^-$  $\tau$} 
+\item  \small{$W\rightarrow$ $l^\pm \nu$, where $l$ can be $\mu$, $e$, $\tau$} 
 \item   \small{$W\rightarrow$ $q\bar{q'}$}
@@
 		\item 	Maximum  $|\eta|$ of any  (untagged)  jet (forward jet)
-		\item 	Number of jets with high $p_t$ and |$\eta$| < 2.4
+		\item 	Number of jets with high $p_t$ >25 GeV and |$\eta$| < 2.4
 		\item	Number of untagged jets with |$\eta$| > 1.0
@@
 		\Fontvi
-		\begin{center}
+		\begin{table}
+			\centering
 			\begin{tabular}{cc}
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-pt-sub} &
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
-				{Distribution of events of pt of the sub leading leptons} &{Distribution of selected events as a function of the jet with largest value of $|\eta|$}\\
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-nfj}\\		
-				{Distribution of selected events with higher pt with a |$\eta$| < 2.4 } & {Distribution of jet events for $|\eta|$>1 } \\
-			\end{tabular}
-		\end{center}
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-pt-sub} &
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-abs-pj-eta}\\ 
+				{} &{}\\
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variablescompare_variables-ncj24}&
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-nfj}\\		
+				{} & { } \\
+			\end{tabular}
+		\end{table}
 	\end{frame}
@@
 			\begin{tabular}{cc}
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-cl} &
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
-				{Distribution of events of $|\Delta\eta|$ between a forward jet and the closest lepton} & {	Distribution of events as function of $|\Delta\eta|$ between a forward jet and a b-tagged jet } \\
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-dr}&
-				\includegraphics[width=5.5cm,height=3cm]{figures/distributions/compare_variables-phi}\\
-				{Distribution of events with a $\Delta R$ between the lepton pairs (highest and lowest $p_t$)} & {Distribution of events of $\Delta\phi$ between the higher $p_t$ pair of leptons } \\
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-eta-fj-cl} &
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-eta-fj-b1}\\ 
+				{} & {	} \\
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-dr}&
+				\includegraphics[width=5.5cm,height=3.5cm]{figures/distributions/compare_variables-phi}\\
+				{} & {} \\
 			\end{tabular}
@@
  \begin{table}[ht]
- {  \tiny
- 		\caption[Results of $\mu$ and upper limits for SM and $k_t$=-1]{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models at 95$\%$ confidence level.}
+ {  \scriptsize
+ 		\caption*{Results of $\mu$ and upper limits for Asimov extrapolations for SM and $k_t$=-1 models at 95$\%$ confidence level.}
  		\begin{tabular}{|c|c|c|c|c|}
@@
 
+\begin{frame}
+\Huge
+	Thank You
+\end{frame}
+
 %\begin{frame}

### 2019-12-11 tesis_hiram/compile-thesis.sh
clean

@@ -28,7 +28,8 @@ if [ $1 = $clean ]; then
 	rm -rf $thesis.pdf
 	rm -rf $thesis.ps
 	rm -rf $thesis.dvi
-	rm -rf *#* 
+	rm -rf *#*
+	rm -f ./*/*.aux
 	echo "Cleaning complete!"
 	exit
 else
@@ -63,7 +64,8 @@ if [ $1 = $clean ]; then
 	rm -rf $thesis.pdf
 	rm -rf $thesis.ps
 	rm -rf $thesis.dvi
-	rm -rf *#* 
+	rm -rf *#*
+	rm -f ./*/*.aux
 	echo "Cleaning complete!"
 	exit
 elif [ $1 = $compile ]; then

### 2019-12-11 fit_2lss_2016/compare_variables.C
clean

@@ -1,34 +1,77 @@
 
 void compare_variables(){
 
+
   TChain t1("demo/tuple");
   TChain t2("demo/tuple");
-  TChain t3("demo/tuple");
+
+
   t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_1.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_2.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_3.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_4.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_5.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_6.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_7.root");
+  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_8.root");
[…]

### 2019-12-11 fit_2lss_2016/make_workspace.C

@@ -16,7 +16,7 @@ TH1D *tzq =(TH1D*)f->Get("thqMVA_ttv_2lss_40_tZq");
 TH1D *ttz =(TH1D*)f->Get("thqMVA_ttv_2lss_40_ttZ");
 TH1D *tzw =(TH1D*)f->Get("thqMVA_ttv_2lss_40_tZW");
 TH1D *vvv =(TH1D*)f->Get("thqMVA_ttv_2lss_40_VVV");
-TH1D *sg =(TH1D*)f->Get("thqMVA_ttv_2lss_40_signal"); ///////**
+TH1D *sg =(TH1D*)f->Get("thqMVA_ttv_2lss_40_signal"); 
 TH1D *ttw =(TH1D*)f->Get("thqMVA_ttv_2lss_40_ttW");
 TH1D *fakes =(TH1D*)f->Get("thqMVA_ttv_2lss_40_data_fakes");
 TH1D *gstar =(TH1D*)f->Get("thqMVA_ttv_2lss_40_Gstar"); ///****
@@ -50,14 +50,16 @@ zz->Scale(1.16/zz->Integral()); //zz
 /////////////////////////////////////////////
 thq->Scale(1.43/thq->Integral());//thq
 thw->Scale(0.71/thw->Integral());//thw
-
+///////////////////////////////////////////
 //for kt=-1
+/////////////////////////////////////////
 //thq->Scale(18.5/thq->Integral());//thq
 //thw->Scale(7.72/thw->Integral());//thw
 
 ////////////////////////////////////////////
 //for higher luminosities
 //////////////////////////////////
+//
 //tzq->Scale(3000.0/35.9); //tzq
 //vvv->Scale(3000/35.9); //vvv
 //ww->Scale(3000/35.9); //wwss
@@ -236,9 +238,6 @@ axis5->SetLabelSize(15);
 axis5->Draw();
 
 auto legend = new TLegend(0.6,0.6,0.89,0.89);
-//legend->SetHeader("Test","C"); // option "C" allows to center the header
-//legend->AddEntry(hat,"Data","lep");
-//legend->AddEntry("th (k_t=-1)","f");
 legend->AddEntry(th,"tH (SM)","f");
 legend->AddEntry(tth,"t#bar{t}H","f");
 legend->AddEntry(ttw,"t#bar{t}W","f");
@@ -252,6 +251,7 @@ legend->Draw();
 pad1->RedrawAxis();
[…]

### 2019-12-11 presentacion_hiram/compile-thesis.sh

@@ -1,0 +1,94 @@
+#!/bin/bash
+# A script to compile the PhD Thesis - Krishna Kumar 
+# Distributed under GPLv2.0 License
+
+compile="compile";
+clean="clean";
+
+if test -z "$2"
+then
+if [ $1 = $clean ]; then
+	echo "Cleaning please wait ..."
+	rm -f *~
+	rm -rf *.aux
+	rm -rf *.bbl
+	rm -rf *.blg
+	rm -rf *.d
+	rm -rf *.fls
+	rm -rf *.ilg
+	rm -rf *.ind
+	rm -rf *.toc*
+	rm -rf *.lot*
+	rm -rf *.lof*
+	rm -rf *.log
+	rm -rf *.idx
+	rm -rf *.out*
+	rm -rf *.gz
+	rm -rf *.snm*
+	rm -rf *.nlo
+	rm -rf *.nls
+	rm -rf presentacion-tesis.pdf
+	rm -rf $presentacion-tesis.ps
+	rm -rf $presentacion-tesis.dvi
+	rm -rf *#*
+	rm -f ./*/*.aux
+	echo "Cleaning complete!"
+	exit
+else
+	echo "Shell script for compiling the PhD Thesis"
+	echo "Usage: sh ./compile-presentacion-tesis.sh [OPTIONS] [presentacion-tesis]"
+	echo "[option]  compile: Compiles the PhD Thesis"
+	echo "[option]  clean: removes temporary files no presentacion-tesis required"
+	exit
+fi
+fi
+
+presentacion-tesis=$2;
+
+if [ $1 = $clean ]; then
+	echo "Cleaning please wait ..."
+	rm -f *~
+	rm -rf *.aux
+	rm -rf *.bbl
+	rm -rf *.blg
+	rm -rf *.d
+	rm -rf *.fls
+	rm -rf *.ilg
+	rm -rf *.ind
+	rm -rf *.toc*
+	rm -rf *.lot*
+	rm -rf *.lof*
+	rm -rf *.log
+	rm -rf *.idx
+	rm -rf *.snm
+	rm -rf *.gz
+	rm -rf *.nav*
+	rm -rf *.out*
+	rm -rf *.nlo
+	rm -rf *.nls
+	rm -rf presentacion-tesis.pdf
+	rm -rf $presentacion-tesis.ps
+	rm -rf $presentacion-tesis.dvi
+	rm -rf *#*
+	rm -f ./*/*.aux
[…]

### 2019-12-11 compare_variables.C
clean

@@ -1,52 +1,0 @@
-
-void compare_variables(){
-
-  TChain t1("demo/tuple");
-  TChain t2("demo/tuple");
-  TChain t3("demo/tuple");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
-  t2.Add("_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_0.root");
-  t3.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
-
-
-  TCanvas C;
-  C.Print("compare_variables.pdf");
-
-  ///compare one variable
-  TH1F H1("H1","",20,0,5);
-  TH1F H2("H2","",20,0,5);
-  TH1F H3("H3","",20,0,5);
-
-H1.SetLineColor(kGreen-3);
-H2.SetLineColor(kRed-3);
-H3.SetLineColor(kBlue-3);
- t1.Draw("fj_eta>>H1");
- t2.Draw("fj_eta>>H2");
- t3.Draw("fj_eta>>H3");
-  H1.Scale(2.14/H1.Integral());
-  H2.Scale(68.0/H2.Integral());
-  H3.Scale(26.22/H3.Integral());
-  C.Clear();
-  H2.Draw("hist");
-  H1.Draw("histsame");
-  H3.Draw("histsame");
-  H2.SetAxisRange(0,10,"Y");
-  H2.SetAxisRange(0,5,"X");
-  H2.SetYTitle("Events");
-  H2.SetStats(0);
-  H2.SetTitle("#eta Distribution");
-  C.Print("compare_variables.pdf");
-
-  //compare correlations
-  C.Clear();
-  C.Divide(1,2);
-  C.cd(1);
-  t1.Draw("l1_eta:b1_eta");
-  C.cd(2);
-  t2.Draw("l1_eta:b1_eta");
-  //C.Print("compare_variables.pdf");
-
-
- // C.Print("compare_variables.pdf");
-
-}

### 2019-12-11 BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/compare_variables.C
clean

@@ -1,87 +1,0 @@
-
-void compare_variables(){
-
-
-  TChain t1("demo/tuple");
-  TChain t2("demo/tuple");
-
-
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_0.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_1.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_2.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_3.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_4.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_5.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_6.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_7.root");
-  t1.Add("_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_8.root");
[…]

### 2019-12-11 fit_2lss_2016/TMVAClassification2.C
clean

@@ -1,0 +1,551 @@
+/// \file
+/// \ingroup tutorial_tmva
+/// \notebook -nodraw
+/// This macro provides examples for the training and testing of the
+/// TMVA classifiers.
+///
+/// As input data is used a toy-MC sample consisting of four Gaussian-distributed
+/// and linearly correlated input variables.
+/// The methods to be used can be switched on and off by means of booleans, or
+/// via the prompt command, for example:
+///
+///     root -l ./TMVAClassification.C\(\"Fisher,Likelihood\"\)
+///
+/// (note that the backslashes are mandatory)
+/// If no method given, a default set of classifiers is used.
+/// The output file "TMVA.root" can be analysed with the use of dedicated
+/// macros (simply say: root -l <macro.C>), which can be conveniently
+/// invoked through a GUI that will appear at the end of the run of this macro.
+/// Launch the GUI via the command:
+///
+///     root -l ./TMVAGui.C
+///
+/// You can also compile and run the example with the following commands
+///
+///     make
+///     ./TMVAClassification <Methods>
+///
+/// where: `<Methods> = "method1 method2"` are the TMVA classifier names
+/// example:
+///
+///     ./TMVAClassification Fisher LikelihoodPCA BDT
+///
+/// If no method given, a default set is of classifiers is used
+///
+/// - Project   : TMVA - a ROOT-integrated toolkit for multivariate data analysis
+/// - Package   : TMVA
+/// - Root Macro: TMVAClassification
+///
+/// \macro_output
+/// \macro_code
+/// \author Andreas Hoecker
+
+
+#include <cstdlib>
+#include <iostream>
+#include <map>
+#include <string>
+
+#include "TChain.h"
+#include "TFile.h"
+#include "TTree.h"
+#include "TString.h"
+#include "TObjString.h"
+#include "TSystem.h"
+#include "TROOT.h"
+
+#include "TMVA/Factory.h"
+#include "TMVA/DataLoader.h"
+#include "TMVA/Tools.h"
+#include "TMVA/TMVAGui.h"
+
+int TMVAClassification2( )
+{
+   // The explicit loading of the shared libTMVA is done in TMVAlogon.C, defined in .rootrc
+   // if you use your private .rootrc, or run from a different directory, please copy the
+   // corresponding lines from .rootrc
+
[…]

### 2019-12-11 plotting/TMVAClassification2.C
clean

@@ -1,551 +1,0 @@
-/// \file
-/// \ingroup tutorial_tmva
-/// \notebook -nodraw
-/// This macro provides examples for the training and testing of the
-/// TMVA classifiers.
-///
-/// As input data is used a toy-MC sample consisting of four Gaussian-distributed
-/// and linearly correlated input variables.
-/// The methods to be used can be switched on and off by means of booleans, or
-/// via the prompt command, for example:
-///
-///     root -l ./TMVAClassification.C\(\"Fisher,Likelihood\"\)
-///
-/// (note that the backslashes are mandatory)
-/// If no method given, a default set of classifiers is used.
-/// The output file "TMVA.root" can be analysed with the use of dedicated
-/// macros (simply say: root -l <macro.C>), which can be conveniently
-/// invoked through a GUI that will appear at the end of the run of this macro.
-/// Launch the GUI via the command:
-///
-///     root -l ./TMVAGui.C
-///
-/// You can also compile and run the example with the following commands
-///
-///     make
-///     ./TMVAClassification <Methods>
-///
-/// where: `<Methods> = "method1 method2"` are the TMVA classifier names
-/// example:
-///
-///     ./TMVAClassification Fisher LikelihoodPCA BDT
-///
-/// If no method given, a default set is of classifiers is used
-///
-/// - Project   : TMVA - a ROOT-integrated toolkit for multivariate data analysis
-/// - Package   : TMVA
-/// - Root Macro: TMVAClassification
-///
-/// \macro_output
-/// \macro_code
-/// \author Andreas Hoecker
-
-
-#include <cstdlib>
-#include <iostream>
-#include <map>
-#include <string>
-
-#include "TChain.h"
-#include "TFile.h"
-#include "TTree.h"
-#include "TString.h"
-#include "TObjString.h"
-#include "TSystem.h"
-#include "TROOT.h"
-
-#include "TMVA/Factory.h"
-#include "TMVA/DataLoader.h"
-#include "TMVA/Tools.h"
-#include "TMVA/TMVAGui.h"
-
-int TMVAClassification2( )
-{
-   // The explicit loading of the shared libTMVA is done in TMVAlogon.C, defined in .rootrc
-   // if you use your private .rootrc, or run from a different directory, please copy the
-   // corresponding lines from .rootrc
-
[…]

### 2019-12-11 fit_2lss_2016/TMVAClassification2.C
clean

@@ -156,8 +156,8 @@ int TMVAClassification2( )
 
 
 
-   signalTree->Add("../BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_*.root");
-   background->Add("../BDTtraining/RunIISummer16MiniAODv3_tuples_3Oct2019/_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_*.root");
+   signalTree->Add("../data/RunIISummer16MiniAODv3_tuples_3Oct2019/_THQ_Hincl_13TeV-madgraph-pythia8_TuneCUETP8M1_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3-v2_MINIAODSIM_*.root");
+   background->Add("../data/RunIISummer16MiniAODv3_tuples_3Oct2019/_TTWJetsToLNu_TuneCUETP8M1_13TeV-amcatnloFXFX-madspin-pythia8_RunIISummer16MiniAODv3-PUMoriond17_94X_mcRun2_asymptotic_v3_ext1-v2_MINIAODSIM_*.root");
 
    // Create a ROOT output file where TMVA will store ntuples, histograms, etc.
    TString outfileName( "TMVA8.root" );
